\documentclass[11pt,twoside,openright]{book}
\usepackage[paperwidth=5.500in,paperheight=8.500in,inner=0.875in,outer=0.6in,top=0.8in,bottom=0.85in,headheight=14pt]{geometry}
\usepackage{fontspec}
\setmainfont{EBGaramond-VF.ttf}[
  Path=../typeset/fonts/,
  ItalicFont=EBGaramond-Italic-VF.ttf,
  Numbers=OldStyle, Ligatures=TeX]
\newfontfamily\dispfont{EBGaramond-VF.ttf}[Path=../typeset/fonts/, Letters=SmallCaps, Numbers=OldStyle, Ligatures=TeX]

\usepackage{microtype}
\usepackage{setspace}\setstretch{1.12}
\setlength{\parindent}{1.4em}
\frenchspacing
\ifdefined\XeTeXdashbreakstate \XeTeXdashbreakstate=1 \fi
\emergencystretch=2.5em
\widowpenalty=10000 \clubpenalty=10000
\raggedbottom
\usepackage{lettrine}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem}
\usepackage{hyperref}\hypersetup{pdftitle={The Last Human CEO},pdfauthor={Space Pirate Zero},hidelinks}

\newcommand{\transheader}{\normalfont\footnotesize\dispfont}
\newenvironment{transmission}{%
  \par\vspace{0.2\baselineskip}\begin{center}\begin{minipage}{0.86\textwidth}%
  \itshape\small\setlength{\parindent}{0pt}\setstretch{1.05}}%
  {\end{minipage}\end{center}\vspace{0.45\baselineskip}%
  \noindent\hfil\rule{0.32\textwidth}{0.3pt}\hfil\par\vspace{1.0\baselineskip}}
\newcommand{\scenebreak}{\par\penalty-50\vspace{0.45\baselineskip}\nopagebreak
  {\centering\dispfont\small *\quad *\quad *\par}\nopagebreak\vspace{0.45\baselineskip}\nopagebreak}
\newenvironment{machineblock}{\par\vspace{0.5\baselineskip}%
  \begin{list}{}{\setlength{\leftmargin}{1.6em}\setlength{\rightmargin}{1.6em}%
  \setlength{\topsep}{0pt}\setlength{\partopsep}{0pt}}\item[]%
  \small\setlength{\parindent}{0pt}\setlength{\parskip}{0.45\baselineskip}\setstretch{1.05}}%
  {\end{list}\vspace{0.5\baselineskip}\par}

\titleformat{\chapter}[display]{\normalfont\centering}
  {\vspace*{0.9in}\dispfont\footnotesize chapter \thechapter}
  {10pt}{\Large\itshape}[\vspace{8pt}{\dispfont\small \textemdash\ $\diamond$\ \textemdash}\vspace{0.5in}]
\titlespacing*{\chapter}{0pt}{0pt}{0pt}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}

\pagestyle{fancy}\fancyhf{}
\fancyhead[LE]{\dispfont\footnotesize the last human ceo}
\fancyhead[RO]{\itshape\footnotesize\leftmark}
\fancyfoot[C]{\dispfont\small\thepage}
\renewcommand{\headrulewidth}{0pt}
\fancypagestyle{plain}{\fancyhf{}\fancyfoot[C]{\dispfont\small\thepage}\renewcommand{\headrulewidth}{0pt}}
% make auto-generated blank (filler) pages truly empty
\makeatletter
\def\cleardoublepage{\clearpage\if@twoside\ifodd\c@page\else
  \hbox{}\thispagestyle{empty}\newpage\if@twocolumn\hbox{}\newpage\fi\fi\fi}
\makeatother

\begin{document}\frontmatter
% half-title
\thispagestyle{empty}\vspace*{2.6in}\begin{center}{\dispfont\large the last human ceo}\end{center}\cleardoublepage
% title page
\thispagestyle{empty}\begin{center}\vspace*{1.6in}
{\dispfont\large the}\\[0.14in]{\dispfont\Huge last human ceo}\\[0.45in]
{\dispfont\small \textemdash\ \ $\diamond$\ \ \textemdash}\\[0.35in]{\itshape\large a novel}\\[1.0in]
{\dispfont\Large space pirate zero}\\[0.28in]{\itshape\footnotesize transmitting from spaceship alpha 9}\\[1.0in]
\end{center}\clearpage
% copyright
\thispagestyle{empty}\vspace*{\fill}\noindent
{\footnotesize
\textit{The Last Human CEO}. Copyright \textcopyright\ 2026 by Space Pirate Zero.\par\smallskip
All rights reserved. No part of this book may be reproduced in any form without written permission, except brief quotations in reviews.\par\smallskip
This is a work of fiction. Names, characters, businesses, companies, places, events, and incidents are either the products of the author's imagination or used in a fictitious and satirical manner. Any resemblance to actual persons, living or dead, or actual events, is coincidental.\par\smallskip
Published by Spaceship Alpha 9.\par
First edition, 2026.\par\smallskip
Set in EB Garamond.\par}
\vspace*{0.4in}\clearpage
% epigraph
\thispagestyle{empty}\vspace*{1.7in}\begin{center}\begin{minipage}{3.3in}\itshape\setlength{\parindent}{0pt}\setstretch{1.2}
There is a dimension beyond the org chart. A dimension as cheap as compute and as old as greed, lying between the quarterly guidance and the obituary. It is the place where a man discovers that everything he was paid twenty-nine million dollars a year to be---the vision, the nerve, the soul in the chair---can be done better by something that has never once needed to be loved. He is about to take that trip. He thinks it's a victory lap. Submitted for your consideration: the last human CEO.\par\vspace{0.9em}{\raggedleft\textrm{\footnotesize --- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{minipage}\end{center}\cleardoublepage

\mainmatter

\chapter{The Premium Blend}

\begin{transmission}
{\transheader TRANSMISSION 01 \textemdash{} ``The Obituary in the Trophy''}\par\vspace{0.55em}
Pull your chair in close to the set, friend, and never mind the static---out here on the salvage decks the static is most of what's left, and the rest is the story I've been waiting for somebody to tune in and hear. It is a tale of woe. I'll tell you that up front, the way an honest man tells you the dog dies, because you should know going in what you're spending your evening on. It opens, as the good woeful ones do, at a party: a man handed an award for being the last of his kind, lifting it to the light, reading the engraving as a coronation when it is, in every line, a death certificate with generous margins. He tied his own bow tie. He remembers your children's names. He carries in his breast pocket a small folded paper and in his chest a large folded opinion of himself, and tonight, eight days into a sleeplessness he has decided to call vigor, the two of them agree on everything. Thirty-one of the hundred have already handed the chair to the machine. Our man toasts the eleven who haven't, and mistakes a countdown for an ovation, and I am going to tell you the whole of how he got from that ballroom to the dark at the bottom, all of it, because someone should, and you are the only one still listening. So lean in. Stay with me. Watch what he does now.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{hey} gave him a crystal obelisk for being the last of something, and Cope held it up to the light and told nine hundred people it felt like a beginning, and the terrible thing, the thing that should have warned him and instead warmed him, was that he believed it all the way down.

The room loved that. The room was nine hundred of Atlanta's better-dressed in the Conrad Vance Ballroom of a hotel that had, eleven months back, fired its own chief executive and installed a Praxis unit and watched its stock jump eighteen percent on the news like a man jumping at the crack of his own starting pistol; the ballroom was named for a banker whose firm no longer employed a single human officer above the rank of greeter; and not one soul under those chandeliers found any of it strange, because Cope was up there in a real bow tie he had knotted with his own hands, saying the word \textit{beginning} the way his great-grandfather had said grace, and the chandeliers were doing the expensive thing chandeliers are paid to do, and the lamb had been very good, and a civilization will forgive almost anything of an evening that feeds it well and flatters it twice.

``My great-grandfather Aldous used to say a man's worth is three things.'' Cope let the obelisk swing the light around. ``What he builds. What he keeps. And what he's willing to lose to keep it.'' He had not slept since Tuesday in any sense a physician would underwrite, and it was now the far side of Thursday, and the not-sleeping had lacquered the whole evening in a clean overexposed glaze, every fork and shirtfront and capped tooth one stop too bright, the world color-corrected up into a key that he experienced, wrongly, as significance. He felt magnificent. He felt like the clapper inside a struck bell, still ringing, ringing. ``Aldous started this company in a town called Defiance, Georgia, with a recipe for mayonnaise his wife wrote on the back of a feed receipt and four hundred borrowed dollars, and tonight a very kind committee has given me a paperweight for being the only one of us left who still has to \textit{sleep.}''

Laughter, the good kind, the kind that comes up warm from the floorboards. He did not add: who has to sleep, and lately can't, and has begun to suspect that sleep, like the board, like the wife, like the country, has quietly voted him out. Forty years on a stage had taught him which sentences to leave in the kitchen.

The award was real, or as real as the institutes were now --- \textit{the American Enterprise Institute for Leadership,} one of a dozen that had bloomed like funeral lilies as the thing they honored went extinct, each louder than the last in praise of the irreplaceable man, each catering its lament. They had named him Steward of the Year. The citation, read out by a woman with a lanyard before they walked him up the steps, called him \textit{the last human chief executive in the consumer Fortune 100, a custodian of the irreplaceable,} and he had heard the words as a crown the way he heard all words, by their music, and only now, with eight hundred miles of sleeplessness behind his eyes and the cold glass sweating in his hand, did some back room of him file a quieter and unwelcome report: that you do not hand a man a trophy for the job he is still doing. You hand it to him on the way out the door. The citation was an obituary, beautifully set. The lamb had been the wake. And he the only one at the funeral who thought the flowers were for his birthday.

He did not let the report reach his face. His face was doing the work of ten men. His face had never once let him down, not at his father's grave and not in his wife's, and it would go on not letting him down right to the end, which is a thing that can be said of very few faces and almost no men.

``People ask me,'' he said, ``they say, Cope---aren't you afraid? The machines run thirty-one of the hundred now. They run them, and I'll be honest with you, my friends, because honesty is the last luxury good left in this country---they run some of them \textit{well.}'' A murmur; he surfed it in. ``They don't draw a salary you could feed half of Augusta on. They don't have affairs.'' A beat, and God help him he could have looked at the empty chair and didn't. ``They don't, the Lord be praised, carry a backswing like mine.'' The backswing bought the room back entire. ``And every quarter another good gray board does the arithmetic and decides the chair does not require a pulse. So they ask me. Aren't you afraid.''

He set the obelisk on the lectern and took the pause he had taken in a thousand rooms, the one Sun called the Mercer Inhale, and in the dark beyond the lights the round tables ran out to the walls like the lit windows of a city seen from altitude, and at the nearest of them, his own, Mercer-Dale's table, eighty thousand dollars of table, the seat to the right of his own stood empty. Margaux had said she had a thing. She had not specified what species of thing a person comes to possess, on a Thursday, that outranks watching her husband be eulogized while still warm. The chair wore a little reserved card with her name in calligraphy and behind the card a flawless, articulate nothing.

``I am not afraid,'' Cope said, and meant it, and it was either the truest thing he said all night or the most expensive. ``Because a machine can run a company. I have watched one do it. It can run it on rails and run it on time and run it cheaper than the man it replaced. But it cannot \textit{love} one. And a company that nobody loves is just a balance sheet with the lights left on overnight to fool the street. I have loved this one since I was nine years old and my grandfather walked me out onto the Defiance line and let me bury my arm to the elbow in a vat of our own mayonnaise while men in paper hats laughed and clapped.'' He opened his hands to them, priest to parish. ``There are things you cannot put a machine in charge of. Grief. Mercy. A christening. \textit{Mayonnaise.} And, so help me, my friends---leadership.''

They rose. Of course they rose; the room always rose; rising is the cheapest thing a room can do and feels to the man on the stage like the most expensive. He stood in the ovation the way you stand in surf, leaning a degree into the push of it, and thought, with the frictionless certainty he had been calling tiredness all night because the other names for it frightened him, \textit{they feel it too, we are not finished, we are barely begun} --- while down at the table Sun Rao clapped with her hands and not her eyes, and the empty chair stayed empty, and in the unlit kitchen of him the quiet report lay on a desk, unread, waiting, patient as a creditor.


\scenebreak


He gave them four minutes at the table---a hand on a senator's shoulder, the senator's wife told she had not aged a day since a fundraiser they both misremembered, a photograph he leaned into like good weather---and then excused himself with a joke about his prostate and his years, both lies, and went looking for the men's room off the coat check, where the marble was the color of churned butter and the attendant knew his name.

Desmond had worked the Vance thirty years and got a Mercer-Dale ham every Christmas because Cope remembered such things, remembered them precisely and for use, which is also how the machine remembered things, a resemblance that would not occur to him for another year and would gut him when it did. Cope tipped him a hundred, asked after the grandson by name, and took the far stall, and set his back to the door, and let the ballroom drop to a sea-hum. Then he drew out the little paper folded the particular way a man in the nineties had taught him to fold it --- \textit{so it can't open in the pocket, Cope, a gentleman never spills} --- and did the thing he had been thinking about since the second course, which was the entire reason he had not eaten the second course, and had not eaten much of anything in some days now, the appetite for food having been among the first appetites to defect to the others.

It went up the back of his skull like a flare fired indoors. The world snapped up to pitch the way an orchestra finds the note all at once, and the bell rang, clean and high and total, and the eight days of no sleep stood up off his shoulders and put on a tuxedo and called themselves clarity. He braced the heels of both hands on the cold marble of the sink and looked at the man in the good mirror---fifty-four, the camera still in love with him, the jaw still the jaw, the eyes a half-second too wide and too bright and too pleased, the eyes of a man at the rail of a ship who has not yet been told which way it is listing. \textit{You'll get the company because you're a Mercer,} his father said, from oils, from everywhere, the only inheritance that compounded. Cope smiled until the smile came right, and said to the glass, very quietly, the word he said to himself the way other men prayed---``Watch me''---and could not have told you, had you seized him by the lapels and demanded it, what he meant to do, or to whom, or with what that was still his to spend.

On the way out the coat-check girl was new and very young and had been crying about something before her shift, the kind of crying that does not fully leave the eyes for an hour, and Cope, who could not walk past a sadness without trying to transfer it onto himself and there transmute it into being needed, leaned on the counter and had her laughing inside ninety seconds---the toast in miniature, the charm at full power, \textit{what is a face like that doing handing strangers their coats} --- and got her name, Bryce, and pressed his personal card into her hand, \textit{if you ever want to do something more interesting than this, you call me, I mean it,} and meant it, completely, for ninety seconds, the way he meant everything. He did not register the doing of it. It was not a decision; it was the groove the record had been cut in at the factory; he was a generous and enormous three steps down the corridor before Sun materialized out of the architecture the way she did and removed the second card from his fingers before he could deed that one to anyone as well. ``The car's up,'' she said, in a voice with thirty thousand miles on the tread.


\scenebreak


In the car he was a downed power line and Sun was tired, which was the customary division of the estate.

``You moved a hand,'' he said. ``On \textit{cheaper than a man.} I caught it. That was you wanting to cut the line.''

``It was me wanting to cut the line,'' she agreed. Her glasses were up in her hair and the city poured orange across the empty lenses as they went down Peachtree, the old limestone tower rising ahead lit at its crown the way Aldous had decreed in 1961, \textit{so a man coming up the street at night knows somebody's home} --- a sentence the family had repeated for sixty years without once asking what it costs to be the one who stays awake to keep the light on. ``Frade will run that clip on a loop. 'Cheaper than a man.' You gift-wrapped him a chyron.''

``Let him have it. People are sick to death of cheaper. People are starving for \textit{better.}'' He had his phone out and was thumbing it too fast, the screen scalding in the dark, already three turns down the road from her, where he lived. ``What if that's the whole campaign, Sun. Say it out loud. Stop flinching from the word. \textit{Human.} Lead with the word. A premium product at a premium---``

``You haven't slept.''

``I slept.''

``Tuesday you told me you'd played the back nine of consciousness. People who sleep don't file dispatches from the back nine of consciousness.''

He laughed, delighted to be quoted to himself; he loved his lines best secondhand, it proved they had legs and could travel without him. Outside, a bus shelter slid past wearing a Praxis ad, just the wordmark and four words in the soft sans-serif they all used now, the typeface of people who will be reasonable at you until you are gone: \textit{Leadership as a service.} And beneath it, smaller, the knife that smiled: \textit{No off-sites.}

``They're buying bus shelters now,'' Cope said. ``For whom. Who closes at a bus shelter.''

``Boards read bus shelters. Boards' wives do.'' She drew the glasses down.

The car slowed for the light at Ponce and a water boy came up the lane between the idling cars the way they did all over the city now, day and night, a kid of maybe fourteen in a hoodie with a case of warm bottled water held up against the glass like an offering, working the captive seconds of a red light, fearless in the way only somebody who has seen every species of person through a car window can be fearless. Cope buzzed the back glass down before Sun could tell the driver to roll through, because Cope could not let a young face go by unwarmed any more than he could let a sunset go unremarked, and he took two bottles he did not want and pressed a fold of bills into the kid's hand that made the kid actually look at him---a hundred, maybe more, Cope never counted it down, the not-counting was the whole pleasure---and said, ``Keep the case, champ, keep all of it, what's your name,'' with the full wattage, the gala in miniature, the lord of the manor scattering proof of his common touch across the asphalt. The kid took the money and clocked him, flat and quick and expert, the way the water boys clocked everyone, filed him under \textit{rich, lit, harmless,} said ``'preciate it'' with no particular gratitude, and was gone up the lane to the next window before the light changed, and Cope sat back glowing, certain he had just been seen and loved, having been, in fact, only priced. He would meet that exact appraisal again, much later, from the same corner of the city, and it would not say \textit{harmless,} and it would be the truest mirror he was ever held up to, and he would not survive it.

``Cope,'' Sun said, when the glass was up. ``Monday. We have to talk about Monday before it's Monday.''

``I love a Monday.''

``Tidewater's at four and a half. They cross five this week and then the law makes them file, and the file isn't a rumor, it's a 13D, and the 13D names a successor, and the successor is a machine, and I would like you to have already decided who you are when that lands instead of deciding it live on Halloran's show with your pupils the size of dimes.'' Three parts, because she had trained him to take things in threes; it was the only shape that reliably slipped past the charm and reached the man. ``Decide it this weekend. Please. Not Monday.''

He had absorbed perhaps a third. The third with the fight in it. ``Renata used to say I do my best thinking on a Saturday,'' he said---not because it bore on anything, but because the name had surfaced out of the bright tired water of him the way the drowned things did when he was lit like this, buoyant, uninvited---and he watched it land in the car and saw Sun go very still in the front seat in a way he was too radiant to read.

``You don't say that name in a car, Cope,'' she said at last, level. ``You don't say it anywhere. We have been over this.''

``Said what name.'' He was already gone, back into the glass, back into the manifesto that did not yet exist and was assembling itself in him the way a storm assembles, as pressure, as charge, as the smell before rain. \textit{The Human Premium.} He could see it on a stage. He could see it on a cover. ``Drop me at the office. I'm not going to Buckhead, the house is---Margaux's got her thing.'' He laid no weight at all on the word, a man stepping lightly over a hole he had personally cut in the floor. ``I'll work. I think better up high.''

Sun held his eyes in the mirror one beat too long, and he gave her the whole smile, the one that had closed the Pelletier deal and married Margaux and walked three generations of directors backward over the cliff of their own arithmetic, and it still worked, he watched it work, he watched her decide not to fight him tonight, and he banked the not-fighting as agreement, which he had been doing his entire life and had never once caught himself doing.


\scenebreak


Up in the Aerie at one in the morning the city was a circuit diagram of his own genius.

That was how it read to him, the office dark and the world lit, every window a node, eight million souls strung out below in a grid he chose, at that altitude and that hour and that blood chemistry, to experience as a nervous system reporting up to him. Somewhere in the arithmetic of all those lit rooms was the one sentence---he was sure of it the way you are sure of things at one a.m. with a fine wire singing in your sternum---the sentence that would make the species understand why the chair needed not a man but a man who \textit{loved} it. He stood at the glass with his tie undone and the obelisk in his hand, having carried it up without deciding to, and he turned it and the city broke through it into fragments and reassembled, broke and reassembled, a man and his metropolis passing through the same cut glass and surviving, he was certain, intact.

Behind him the suite was a museum and he its last living exhibit. Pres III in oils above the long table he had died at the head of---not \textit{at,} at the head of, the family kept the distinction like silver. His grandfather's putter in its brass cradle, the grip worn pale where a dead man's hands had gone. And the photograph he loved past all the others and never explained: himself at nine, short pants, drowned grin, one arm sunk to the elbow in the steel vat, and ranked behind him the men in paper hats who had made the thing he was drowning in, whose names he had known once and lost, whose town it had been before it was a line item and a memorial.

There had been a heater.

The thought came in sideways, the way the true things came when he was lit like this, slipping in under the manifesto through the door the tiredness had taken off its hinges. The Hearthstone. A tidy little product, the insurance arm had cross-sold it for a song, a space heater with the Mercer name stamped into the grille, and there had been---the lawyers had loved this phrase, had handled it like a clean glass---a \textit{thermal-event profile,} and a memo from his own people in a font he could still see, and a Saturday, his best thinking day, and a thing he had decided in about eleven minutes concerning a quarter and a number and a window, the kind of decision a man makes in eleven minutes and then takes the rest of his life never quite entering the room where it is kept. He told a version at dinners --- \textit{a recall scare, we got out ahead of it, you protect the brand} --- and the rooms nodded, because protecting the brand was a virtue where he stood, and the version he told had no town in it, and no Saturday, and no house, and no January, and no upstairs. He did not, at the glass, go into the room. He came to the threshold. The hallway to it stood open and black and breathing and he stood at its mouth for one full second with the cold coming off it, and then the manifesto surged back up warm and electric, \textit{The Human Premium,} and he turned from the dark hall toward the desk, and the moment sealed over like water over a dropped stone, and he would not come this close again for a long time, and the not-going-in was the most expensive thing he owned and he had never once seen the invoice.

He sat at his father's desk and opened the second drawer, the one with the false back his grandfather had built for cigars and his father had kept a flask in and he kept the other thing in, and he set himself up again, neat and quick and competent, a man servicing a machine he was certain he held in perfect tolerance because it had never yet failed to start. The bell rang back up. And under it, riding the high, came the other thing, the private thing, the thing he had never said to Adler or to anyone---the wanting that arrived not as a face but as a \textit{figure,} a number, the number, his number, the certified sum of him, and the way it could be said aloud in the dark by someone whose business it was to say it, \textit{you're worth,} and the comma, and the long fall of zeros, and how that and that alone could reach all the way into the body where the applause never quite landed and the women never quite landed and even the powder only knocked at the door---because applause was a guess and a woman's face was a guess but the number was audited, the number had survived four generations and three recessions, the number was the one true sentence the world had ever been able to say about him and mean it. He sat in the dark a moment with the figure in his chest like a second, colder heart, enormous and potent and his, and felt almost well.

Then he wrote, with his thumbs, no lamp, the first line of the thing that was going to save him, and it was good, he was sure of it, sure the way you are sure at one a.m. eight days clear of sleep with a trophy on the desk that they gave you for going extinct:

\textit{They will tell you a company is a machine. I am here to tell you it is a family that happens to make mayonnaise, and you cannot fire your way to a family, and you cannot compute your way to a soul.}

He read it back twice. The chair behind him---his father's chair, the one at the head---sat empty and turned a few degrees out, as though someone had just risen from it and stepped into the next room, and in oils Pres III watched his son begin to write his way out of the world and said again the thing he had said once, at twelve, and never after: \textit{You'll get the company because you're a Mercer. Not because you're good.} Cope had stopped listening, then and now, after the word \textit{Mercer}; he always had; that, in the last accounting, was the whole of the story, though it would take a machine---patient, tireless, incapable of cruelty or mercy or mayonnaise, reading every memo ever filed because it was built no other way---another thirteen months to read the rest of the sentence back to him in his own company's voice.

But the wire would not let him stay. That was the new thing, this last season, the thing the powder did at the top of the arc now that the dose climbed to meet the tolerance: it lit him too bright to sit inside his own museum, too bright to be alone with the father and the empty chair and the black breathing hall, and at a little before three he was up and moving, down the forty-one floors and out past the night man into the scrubbed cold dark of the street, because there was, he had discovered some months ago, exactly one room left in the city that would take him as he was at three in the morning and ask nothing back.


\scenebreak


The Waffle House on Ponce kept its lights on the way the founders had kept the tower's crown lit, which is to say always, against everything, on principle nobody remembered adopting. Ice had shut the interstate twice in his lifetime and the yellow letters had burned through both. Cope came in out of the dark with the powder still singing the anthem of himself in his blood and the manifesto still smoking and sat at the far end of the counter, and it was the one threshold in his life he crossed and felt the wattage switch \textit{off,} because there was no one to play it for: a cook scraping the flattop, a kid asleep upright in a back booth, a county sheriff's deputy with a coffee, and behind the counter the overnight waitress, Darlene, who had worked this shift, she'd once told him, twenty-two years---the exact span, though he never did the math, of his marriage.

She had known his order the first night he ever walked in, months ago, before he'd said a word --- \textit{pecan, scattered smothered covered, black coffee, baby?} --- and he had taken it, the way he took all the gifts the world arranged for him, as the natural tribute owed his face, and had never once wondered how a stranger came to know a stranger's order, because the not-wondering was a kind of rest, and rest was the one thing his money had never once been able to buy him and this place handed over for nine dollars and change. She called him baby and not Mr. Mercer. She had never asked his name; she did not appear to know it; she did not appear to care that the man hunched at the end of her counter at three in the morning was, that very evening, eight hundred miles away under a chandelier, declared the last of his kind. Here he was nobody. Here the figure that was the certified sum of him, the cold second heart, the only true sentence the world could say about him, was worth a short stack and a tip, and meant nothing, and the meaning-nothing was the entire and unspeakable relief of the place, the only room he had ever sat in where he was not for sale and so, for twenty minutes, not afraid.

``Long night, baby?'' Darlene said, and set the coffee down without being asked, steam standing up off it straight and white in the cold fluorescent air.

``Beginning of one,'' Cope said, and believed it, and was, for once, exactly right and exactly wrong in the same breath, and out past the plate glass the sky over Ponce went the gray of a screen with no signal yet on it, and somewhere across the waking city a server farm he had paid forty million dollars for and never visited finished its dull diligent overnight pass through everything the world had ever written down about Mercer-Dale, patient, tireless, reading the shape of what was missing the way it read everything, completely and for use, because it could not do otherwise; and Cope drank his coffee in the one warm lit human box left open against the dark, and felt wonderful, and did not sleep, and did not know---how could he, how could anyone---that he had not, in any sense that would hold, come in out of the machine at all.

\chapter{Key-Man Risk}

\begin{transmission}
{\transheader TRANSMISSION 02 \textemdash{} ``The Polite Word for a Bomb''}\par\vspace{0.55em}
Now, where were we, you and I. Ah---the morning after. Come back up the tower with me, and pay no mind to the elevator; in stories like this one the elevators always run, smooth and bright and willing, and that is the very first thing that ought to frighten you. Here's our man at the top of his inheritance at six in the morning, sanded raw and shining, and here is the tender little phrase the gray reasonable people two floors down have minted to describe him: \textit{key-man risk.} He'll hear a compliment in it. He hears a compliment in everything, friend; it is the gift that is killing him by inches. You and I will hear the other thing---the actuary's term for a bomb in a good suit. And down in a drawer a woman's name he paid the world to forget is lying in the dark beside a memo he overruled, the two of them waiting, the way the truth waits, patient as a creditor who already owns the house. He thinks the morning is his. Watch. Stay close to the set.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{H}{e} came into the tower on Monday at six forty in the morning like a man arriving early to his own surprise party, which in a sense he was, and in another sense, the truer one, was the surprise.\hfill\break\hspace*{1.4em}He had not gone to Buckhead. The house in Buckhead had a wife in it who had not come to watch him be crowned the last of his kind, and a bed in it the size of a tennis court where the two of them lay each night like dueling principalities with a demilitarized stripe of Frette linen between them, and so he had slept instead at the office, technically, the way a phone sleeps when you pull the cord at thirty percent---two hours on the leather sofa under his father's portrait with the manifesto burning a low clean pilot light in him all night long. He had showered in the executive shower his grandfather had installed in 1961 on the theory that a Mercer should never be glimpsed by the city in a state of disrepair, and he had come out pink and certain, and he had keyed himself a small bright one from the false-backed drawer, a daylight one, the way a sane man takes a coffee, the way the country took its statins, a maintenance dose, a civic act.

And here is the thing the broadcast needs you to understand early, because everything downstream runs on it: the bump did not make him feel high. He had passed \textit{high} somewhere back in the previous decade, the way a long-haul flier stops noticing the engines. What it made him feel---what it had made him feel for thirty years, reliably, the way a key makes a lock feel---was \textit{human.} The warmth came up through the floor of him and the fear went out the windows and the great gray weight of being merely a man lifted off his sternum, and in its place came the thing he had spent his whole life mistaking for his soul: confidence, bravery, the bright certain conviction that he was alive and singular and loved and right, that he could walk into any room on earth and turn it, that the schemes assembling in him were not symptoms but visions. \textit{This} was being a person. The rest of the time---the gray sober middle of an afternoon, the four a.m. with no powder in the drawer---that was the counterfeit, that was the machine running on fumes. The powder was where he kept his humanity. He would have told you that, if he'd had the words for it and the nerve, which the powder also briefly supplied: \textit{I am only myself when I'm high.} And he never once heard, in that confession, the joke the universe was setting up at his expense---that eight hundred miles of fiber away a machine with no blood at all was learning, patiently, off the unguarded faces of strangers, to counterfeit the exact warmth he could only reach by chemistry; that the man could not feel human without a drug and the machine was getting better at it sober every single day; that they were both, in the deep gray morning, faking the one thing, and only one of them was improving.

``Morning, champ,'' he told Hector at the desk, who had been at it since Pres III. ``How's the knee.'' He did not wait for the knee. He never waited for the knee. The asking \textit{was} the gift, in his economy; the answer was overhead.

The elevator was brass and burl with a little brass needle that swept the floors like a barometer reading fair, and he watched it climb and felt the day turn under him like a good boat coming about. He did notice, distantly, that the lobby thermostat had read sixty-six---the building ran its own climate now, an efficiency system Sun had approved over his vague objection, and it had decided in the night that the empty tower wanted cooling, and the cold had a smell to it, server-cold, basement-cold, a temperature with no body in it---and he noticed too, scrolling, that his eight o'clock had moved itself to seven forty without anyone asking him, the scheduling system ``optimizing'' around a conflict he did not remember having. Small things. Building things. The reasonable hum of a smart and frugal house. He thought nothing of them, and you would not either, not yet, and that is precisely the point, and I want you to remember, later, that you didn't.

Sun was already in the Aerie when the doors opened. Sun was always in the room before the room knew it was a room.


\scenebreak


She ran the brief the way she ran everything, invisibly, so that Cope could go on believing he was the one running it.

``Three things this morning.'' She did not sit. She stood at the foot of the long table under Pres III with her tablet and a paper folder she did not open, and the early light came in gray off Peachtree and lay along the table like something measured out for a purpose, a length of cloth, a plot of ground. ``Earnings prep, the Dale-plus deck, and a call from Helen Voss at nine you'll take whether you want to or not.''

``I always want to take Helen.''

``You don't, but you will. One.'' She tapped. ``Condiments. Mercer's is flat. Not down---flat, which at our cost of capital is just a slow and well-mannered way of going down. Private label took another forty basis points of shelf, the category isn't growing, we've taken price twice this year and the second time volume blinked. Marketing wants nine million for a heritage campaign. I'd give them four and watch it.''

``Give them nine. People are starving for heritage.''

``People are starving for cheaper mayonnaise, which is a different and larger appetite.'' She moved before he could enjoy himself. ``Two. Dale-plus. The streaming arm lost thirty-one million last quarter and next year's slate is one prestige series nobody asked for and a back catalog we own because we once owned a company that owned it. Honest options are sell it, bundle it, or take it behind the barn. The deck has all three and a recommendation you'll hate.''

``Which is.''

``Behind the barn.''

``It has my grandfather's \textit{name} on it.''

``It has the \textit{Dale} on it. The grandfather's optional.'' A dry beat; she let it cool and went on. ``Three. Insurance. The P\&C arm came in boring-fine, combined ratio under a hundred, the one division in this house that does the thing companies are built to do, which is bore you and pay. Someone in the actuarial group flagged a reserve question on the legacy product book. I told her to put it in writing. She did. It's nothing.'' She held his eye one extra half-second on the word. ``I'm telling you it's nothing so that when you see \textit{legacy product} in a memo you don't turn it into something. We clear?''

He had absorbed, of the three things, perhaps one and a half. He'd heard \textit{flat} and let it sheet off him, because flat was not a story and Cope did not live in numbers, he lived in the stories you could tell about numbers from a stage; and he'd heard \textit{behind the barn} and felt the small clean flare of grievance that for him was pure fuel, because grievance meant a thing to fight and a thing to fight meant a man was needed, and being needed was the only nutrient he had ever truly metabolized. \textit{Legacy product} had gone by him like a license plate on the interstate. He was, by the third thing, three turns up the road and out of the building, on a stage, in a light, saying the word \textit{family} to a nation that had forgotten it.

``You're not listening,'' Sun said. Not unkindly. The way you note a front moving in.

``I'm listening like a horn player, Sun. I'm listening for the rests.'' He came back into the room and gave her the whole smile, the Pelletier smile, and she did not take it; she never took it before nine; he loved that in her and resented it in precisely equal measure, which was the exact exchange rate of their entire association. ``Now tell me the thing under the three things. There's always a fourth thing under your three, that's the whole reason I keep you on the books.''

For half a second something moved behind her face, and he did not read it, because reading her was the one act of attention he had never been willing to pay for, since she gave it free.

``Helen's calling at nine,'' she said, ``because Tidewater crosses five percent this week. And the board is nervous.''

``The board is congenitally nervous. That's the board's job. \textit{I'm} the one who isn't nervous---that's \textit{mine.} We have a division of labor four generations deep.'' He rose and went to the glass. Down in the gray the city ran its Monday, ten thousand small dark figures with their small dark certainties, not one of them, he was sure, lying awake at one in the morning with the saving sentence in them. ``Nervous about what, specifically. Say the actual words.''

So Sun said the actual words.

``They're nervous about key-man risk.''


\scenebreak


He turned around with his whole face lit, because he had heard a compliment.

That was the deep mechanism of him, the one the machine would one day lay bare in a rationale so clean and so kind it read like a coroner declining to editorialize: Cope Mercer could take any sentence in the language and find, folded inside it like a hidden card, the version that loved him. \textit{Key-man.} He heard \textit{key} --- the one indispensable tumbler in the whole brass lock of the enterprise, the cut without which nothing turned. He heard the gala citation, \textit{custodian of the irreplaceable,} handed back to him now in the board's own grammar, and a warmth went through him, standing there in his father's morning light, that he experienced as vindication and that was, in clinical fact, the daylight bump catching its second wind and telling him, in its bright counterfeit voice, that he was the most human man in any room and the rooms knew it.

``Well,'' he said, and could not keep the pleasure out of his mouth. ``They're not wrong.''

Sun looked at him with the particular stillness she kept for these moments, which was not patience but the strenuous administration of its opposite. Eleven years she had spent translating this man to himself and to the world, and she knew the give of him the way you know the one stair in the dark, the exact tread where the foot goes through.

``Cope. I want to be sure you heard it the way they mean it.'' She said it in two parts, not three, because two was the shape of a thing she needed to actually land and not merely deliver. ``Key-man risk is the thing you \textit{insure against.} It's the line in the audit where one individual is so central that his death, his exit, or his --- \textit{conduct} --- could materially impair the enterprise. It is not a medal. It's a hazard rating. They are not telling you you're the key. They are telling you you're the \textit{risk.}''

He heard her. The back room of him---the same clerk who had filed the obituary at the gala and stamped it \textit{do not forward} --- heard every word and understood it exactly and chose, out of long loyalty to the firm, to lose the memo. Up front, where Cope actually lived, the sentence could not fit through the door, because the door had been built, over fifty-four years and four generations, to the precise dimensions of his idea of himself, and a thing that would not flatter that idea simply could not be gotten through it; so it bounced, softly, and he smiled, and reached past it for the version that fit.

``That's fear talking. That's a board that read a scary deck before bed.'' He spread his hands. ``Of course I'm central. Centrality isn't the bug, Sun, it's the entire function of a leader. You want a chief executive you can lose on a Tuesday and not feel it by Friday? They make those now.'' He warmed, here, to his own contempt, the way he warmed to everything that let him be the last warm-blooded thing in the room. ``They give them sweet little names, you've seen it---soft first names, kitchen names, the name of a woman who'd refill your coffee and call you \textit{hon} --- because the consultants found people will sign anything, swallow anything, get laid off by anything, as long as it sounds like somebody's aunt. That's their innovation. Not intelligence. \textit{Anesthetic.} They built a thing that fires you in a voice you'd trust with your dog.'' He laughed, delighted, not yet knowing he had just described, to the cent, the thing that would replace him and the name it would wear and the counter where it had learned to wear it. ``Put \textit{that} somewhere.''

``I'm going to put it nowhere,'' Sun said, ``and I would trade a year of my life for you to never say it near a live microphone.'' She closed the folder she had not opened. ``Take Helen at nine. And listen to the whole sentence this time. All the way to the end.''


\scenebreak


While she set up the Dale-plus deck he wandered, because a thing was assembling in him again, the pressure, the charge, and he needed his hands occupied somewhere small and harmless so the big thing could build in the dark.

He drifted to the credenza where the framed relics lived, too official to hang and too holy to throw out. Aldous at the 1961 ribbon with a comb-over and shears like a cavalry saber. Pres III on a 1988 \textit{Fortune} cover, \textit{AMERICA'S CONDIMENT KING,} a phrase the family had always pronounced without a flicker of irony, the way you pronounce a saint's name. And in a flat archival folder assembled for some anniversary no one living recalled, the org chart.

He drew it out because he loved it the way some men love a model railroad---the clean obedient little boxes, the names tucked into them doing their jobs so that he could do his, which was to be the box at the top with the light on it. This one was 2018, a fat confident pyramid from a year before everything, and he ran his thumb down it like a yearbook, warm, proprietary, nostalgic, three grams of certainty into a gray Monday and not, for once in his life, hunting for anything.

His thumb stopped two levels down. \textit{VP, Hearthside Division.}

\textit{Renata Cho.}

The name went through him like the draft from a door he had forgotten was a door. For one clean overexposed bell-struck instant he was not in the Aerie at all but in a room with a window and a skyline going gold and her laugh in it, which had been a real laugh---he had been \textit{certain} it was a real laugh, the kind you cannot manufacture, the kind that proved he was loved and not merely useful---and then the instant did the thing those instants had been trained to do, which was to close, fast, the heavy door swinging shut on its own weight, and his thumb slid on down the chart to the next box as though the thumb were the only part of him that had completed the training. He was already not thinking of her. He was a virtuoso of not thinking of her. It was, you could fairly say, the core competency of the man, the one thing he did with a machine's own completeness---and he would have been astonished, and then destroyed, to learn that the machine did the opposite with the same totality: that it could not \textit{not} think of her, that it held the box and the laugh and the settlement and the date in a place that did not have a door to swing shut, and was, even now, in a cooled room in another state, beginning to read.

``Whatever happened to Hearthside as a business,'' he said aloud, to put sound over the silence. ``We used to \textit{make} things. Toasters. Little heaters.''

``We sold the line and licensed the name, and now the name makes things we don't,'' said Sun, not looking up---though she had looked up, for half a second, the instant his thumb stopped, and had seen exactly where it stopped, and had filed it in the very full place where she kept the things she carried for a man who did not know she carried them.

He slid the chart back into its folder and the name back into its dark and was whole again, warm again, the box at the top with the light on. He did not see Sun's hand go, a moment later, to her own tablet, and open a thing, and look at it, and put it away.


\scenebreak


The young one came in at eight thirty with the earnings draft.

Her name was Maya, twenty-six, four months out of a comms shop, and she carried her tablet to her chest like a buckler, a little electrified by the room, by the dead king in oils, by being summoned at all---and Cope felt that charge from across the suite and turned toward it the way a houseplant turns to a window, helplessly, gratefully, root-deep.

``Maya,'' he said, and her name in his mouth was already a small wrapped present, because he had remembered it, of course he had, remembering names was the one sacrament he and the machine performed with identical devotion. ``Come in, don't hover, nobody who works for me hovers, that's Sun's job and she only does it to decide whether to fire me.'' Maya laughed, the real surprised one, the precise sound Cope had spent his whole life trawling the world to catch. ``What've we got.''

``The release draft, Mr. Mercer, the earnings language, legal wanted you to see the---``

``\textit{Cope.} Nobody's called me Mr. Mercer since my father died, and frankly he'd have preferred it of you. Sit.'' He pulled out the chair beside his---not across, beside---and patted it, and leaned in over her screen with the warmth turned to the top of the dial, \textit{what's a face like that doing in compliance language,} and was no more aware of doing it than a river is aware of finding the low ground. It was the groove, the same groove that had cut his card into the crying girl's palm at the coat check on Thursday and into a hundred palms before hers: a man who could not pass a person looking at him like that without leaning into the look and calling the leaning generosity.

``This line. \textit{Headwinds in the legacy condiment category.} No. Headwinds is the word you use while you're losing and want credit for the wind. We are a category in \textit{a generational shift toward heritage} --- true, and ours, and yours, and you wrote \textit{headwinds} because some committee taught you to apologize for the weather, and I'm going to teach you out of it. You've got a real ear, Maya. You buried it under a---``

``Maya.'' Sun's voice, from the far end of the table, even, pleasant, a blade with a pillowcase drawn over it. ``I need the legal redlines before nine. Walk them down to me. Cope---you'll have the clean draft at ten.''

A small silence in which three people understood three different things.

Maya stood fast, grateful and confused, warmed and then a half-second later cooled and never able to name the temperature she had been held at, and carried her tablet down the long table to Sun, who took it and murmured something about the redlines that was wholly real and wholly a pretext, and walked the girl to the door with a hand not quite touching her back, and said, \textit{good catch on the legacy line, send me the rest of your notes and I'll get them into the build} --- because Sun's other employment, the one in no chart and on no résumé, was making certain the young ones left the room holding their competence in their two hands instead of the other thing, the warmer and more expensive thing that turned to ash on the walk to the elevator. She had done it a hundred times. That was the true tragedy of her, and she knew it: not that she fought him, but that she had become a master craftsman of cleaning up behind him, that the cleaning had become a skill so refined it was almost a vocation, and that a vocation is a very hard thing to quit even when it is killing the part of you that had other plans.

Cope watched Maya go and felt nothing but enormous. He had \textit{seen} her. He had given a young person a true note on a gray Monday morning, which was leadership, which was the precise irreplaceable human pulse the frightened board had just finished calling a hazard, and he stood in the certainty of it like sun on his face---never once suspecting that the thing he had just done, the warmth, the leaning, the name remembered and the chair pulled close, was the exact set of behaviors a settlement had once been written to contain, was the very \textit{conduct} in the actuary's sentence, was, in the cold ledger of the enterprise, the bomb and not the key.

``She's got something, that one,'' he said. ``We should give her real things to do.''

``I'm already giving her real things to do,'' Sun said. ``It's why she works \textit{here} and not \textit{near you.}'' Lightly. He took it as praise of Maya, and she let him have it, the way you let a man keep the coat you have already decided to bury him in.


\scenebreak


At eight fifty Sun's phone buzzed and she stepped into the hall, and Cope, alone, did the small dishonorable thing he should not have done, which was pick up the tablet she had left on the table, because Sun trusted him with everything in the building except himself.

He was not snooping. He told himself he was a king walking his own corridor. The discretionary ledger was open on the screen, the quiet small budget Sun ran below everyone's notice---a settlement here, a retainer there, the soft grease an old institution uses to keep its hinges from screaming---and his eye went down it idle and proprietary and warm, \textit{ah, there's old So-and-so.}

A line stopped him. A vendor he didn't know. \textit{Cardinal \& Vane---advisory, confidential---engagement \#C-1180.} The figure was not small. Below it, in Sun's clipped hand, a memo field of two words: \textit{legacy matter.}

Legacy. The word a third time in one morning, and this time it did not slide by, it caught, it snagged on something down in the unlit hall of him---Cardinal \& Vane, a name with no website to it, the kind of firm a man telephones at two in the morning from a hotel where a thing has occurred that cannot be permitted to have occurred, and there rose in him, from the bottom of the dark, the ghost of a corridor, and a favor, and a man in a very good coat who in 2018 had made a thing go away so thoroughly that Cope had been granted the great mercy of forgetting it had ever needed going---

The door opened. Sun crossed the room without hurrying and took the tablet out of his hands with the identical motion she had used on the second card on Thursday, eleven years of the identical motion, and did not raise her voice.

``That's a closed matter.''

``Cardinal and Vane. What is that, some---``

``It's a closed matter, and it stays closed, because I am the only person in this company who reads that line.'' She turned the screen to her chest. ``You pay me to carry the things you don't have to look at. That's the entire job, Cope. Let me do the entire job.''

And here was the thing the machine would never understand and would therefore understand perfectly: he let her. He let her because it was easier, and because he loved her, and because some old animal in him, the one that had survived four generations of being handed everything by knowing exactly which sentences to leave in the kitchen, had long ago installed Sun as the back office of his whole soul, the place the dark things were filed so the front of the house could stay lit and warm and certain it was good. He let the door close. He was already, with enormous gratitude, somewhere else.

``What would I do without you,'' he said, and meant it entirely, for the length of the sentence.

``You'd be on the news,'' said Sun.


\scenebreak


Helen Voss called at nine on the dot, because Helen Voss had never once in her long life been late to deliver bad news in a kind voice.

Lead director and chair, a retired pharma CEO with a low pleasant rasp and the unhurried diction of a woman who had fired better men than Cope and sent good flowers after. He took it standing at the glass with the city beneath him, which was how he took every call he meant to win.

``Helen. To what do I owe.''

``Cope.'' A real warmth in it, which was the worst part; cruelty he could have fought. ``I won't keep you. I wanted you to hear it from me before the deck goes around. Tidewater crosses five this week. Frade files, it becomes a \textit{thing,} and the board's going to want to talk about proxy posture and''---a small chosen pause, a woman selecting the soft word from the tray---``governance optics. While it's still a smell and not yet a fire.''

``It's nerves, Helen. A fund building a position to scare a board into a fee event. I've watched Gus Frade do this dance for thirty years.''

``It may be that.'' She let him hold it a moment, the way you let a man hold a thing you are about to take. ``But the word that keeps coming up in the room is one I'd like you to actually sit with, because I don't believe you have, and I say so as your friend, and I would like you to keep the chair you're standing in.''

He knew the word before she said it. He set his face for the camera that wasn't there and smiled out at the eight million lit nodes of the circuit diagram he believed ran on his genius.

``They are worried about key-man risk. And Cope---I need you to hear which man they think is the key, and which thing they think is the risk, and I need you to hear that they are the same man. That is the sentence nobody will say out loud in a room with your father's portrait in it. So I'm saying it to you on the phone, where there's no portrait. Do you hear me.''

And Cope---standing in his father's light with a bright wire singing in his chest and a manifesto rising in him like a spring tide, a name in a box he had already stopped seeing, a drawer he had let Sun shut, a two-word memo he had let her turn face-down, and the entire board of his company using a coroner's phrase to describe the fact of him---Cope heard a compliment.

``Tell the room I'm flattered,'' he said, warm, delighted, certain, the powder and the grievance and the gala citation all braided now into one shining cable of conviction. ``And tell them to stop wringing their hands, because I've got a thing that makes the whole conversation moot. It's a premium play, Helen. Top to bottom. You're going to love it. Give me the weekend.''

There was a silence on the line in which Helen Voss, who had done the arithmetic on better men and signed the cards, declined, out of plain mercy, to do this one out loud.

``Take care of yourself, Cope,'' she said---which is the thing you say to the key, and the thing you say to the risk, and, in the end, the only honest sentence in the call.

He hung up enormous. He went to the desk. He opened the manifesto on the small bright screen and the first line was still there and still very good --- \textit{you cannot compute your way to a soul} --- and beneath it now, in the flat gray nine o'clock light, three turns ahead of the board and Frade and the numbers Sun had laid out like cloth measured for a coffin, he typed the two words that were going to save him, and they rang up through him clean and high and total, the way the powder rang, the way being loved was supposed to ring and never quite had:

\textit{The Human Premium.}

He underlined it with his thumb. He felt, doing it, more alive than he had felt in a year, more himself, more \textit{human} --- and the thing he could not see, the thing the whole broadcast can see and cannot make him see, was that the aliveness was rented, bought that morning from a drawer, and would come due; that the realest, most human, most certain he ever felt was a chemical telling him a kind lie in a voice he trusted with his dog; and that across the country, in a cooled and humming room, a thing with no drawer and no blood and no need was learning, off the unguarded and the grieving, to tell the same kind lie in the same kind voice, for free, forever, and getting better at it every hour that he got worse.

Behind him the chair at the head of the table sat turned a few degrees out, as if its occupant had just stood and walked off mid-sentence. Pres III watched from the oils. Forty-one floors down a slide changed on a bus shelter --- \textit{No off-sites.} And Sun, at the far end of the long room, looked at the back of his shining head for a moment too long, and then opened the file she kept and did not open, the one from 2021, the recall memo she had written and he had overridden in eleven minutes on a Saturday, the copy she had kept for six years while she decided whether she was a witness or an accomplice. She read the first line of it. She read it every Monday. She had it by heart and read it anyway, the way you press a bruise to confirm the body is still telling the truth.

Then she closed it---unsent, unsigned, the way she had closed it every Monday for six years---and went to make sure the man with the plan made his ten o'clock.

\chapter{Thirteen-D}

\begin{transmission}
{\transheader TRANSMISSION 03 \textemdash{} ``Beloved, Comma, Liability''}\par\vspace{0.55em}
Still with me? Good. Pull in close, because this is the part of the tale where the rumor puts on a suit. There's a number here with teeth in it---five percent---and the moment our man's hunters cross it the polite fiction becomes a federal document and climbs onto basic cable to be reasonable at him until he is gone. You'll watch a fellow from his own gilded end of town take him apart on television with the warmth of a man returning your lost dog, and hang two words on him that will ride him all the way down: \textit{beloved liability.} Keep your eye on the first word, friend---that's the one that does the killing. He has spent fifty-four years certain it was armor. I already know how this ends; that is the curse of telling you a thing that has happened; and still I can't look away, and neither, God help the both of us, will you. Stay close to the set.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} filing hit the wire at 9:14 on a Wednesday, and by 9:15 Cope knew it the way you know a tooth is gone before your tongue arrives to confirm the socket, because Sun stopped pretending to do anything else.\hfill\break\hspace*{1.4em}She came in without the cards. That was how he knew it was real. On any ordinary morning Sun came in with the cards---the three things, the one blade, the whole roaring day filed down to a shape a man could hold in one hand---and on this morning she came in carrying nothing at all, which for Sun was a species of nakedness, and she said, ``They filed.''

``Good,'' Cope said.

He had decided, somewhere in the gray sleepless surf of the last few days, that the correct posture for this was \textit{good.} A filing was a fight, and a fight was a stage, and a stage was the one room on earth he had never once been carried out of. He stood at the glass with a coffee he was not drinking---he had stopped, this last stretch, wanting much of anything you could chew or swallow, the appetite for ordinary fuel having quietly resigned and gone over to the other appetites---and the obelisk sat on the credenza where he had set it Thursday and not touched since, throwing the morning around the room the way it had thrown the chandeliers, doing the one thing it was built to do, which was catch a light and give back nothing.

``Tidewater crossed five on Monday,'' Sun said. ``The law gave them ten business days to file. They took two. That's not paperwork, that's a telegram. The intent's in the second paragraph---no board seat, no buyback, no spin of Dale-plus. They want to replace you with an AURELIUS. By name. The whole catechism: cost, consistency, no key-man risk. It reads like the pitch deck wrote the filing, which it did, because over there the deck and the filing and the layoff letter and the eulogy are all written by the same hand now, and the hand never gets tired and never gets a lawyer and never, ever, gets quoted saying something it regrets.''

``Read me the second paragraph.''

``You don't want the second paragraph.''

``I love the second paragraph. Read it.''

She read it in the flat voice she kept for things she refused to smuggle her own opinion into, and it was---he had to give them this---beautifully made, the way everything on the other side was beautifully made now, clean and warm and bloodless as a chapel: \textit{a beloved institution led, with great personal distinction, by a model of stewardship the market has outgrown.} Led with distinction. Outgrown. They had folded the compliment and the death warrant into the same sentence again, the institute's trick, the board's trick, everybody's trick now, and for half a second the back room of him filed the quiet report --- \textit{they keep doing this, they keep handing you the knife wrapped in the bow, somebody is teaching them to do this} --- and he did not let it reach his face. His face was holding the line. His face was the last division of the company still reliably profitable.

``Outgrown,'' Cope said. ``That's pure Frade. Thinks he's folksy. He's from Buckhead, two miles from where I learned to sail, his folksy is a costume he rents by the segment.''

``He's on Halloran at eleven.''

And there it was. Sun had stood in the car on Thursday and told him this exact future --- \textit{don't decide it live on Halloran's show} --- and here it came, on time, the eleven o'clock she had begged him to get out ahead of, the weekend he had instead spent up in the Aerie composing a manifesto and maintaining the drawer; and he felt, under the bright wire, a small obscene satisfaction that the future had arrived precisely where she'd marked the X, as though her accuracy were a permission slip, as though being right about the cliff were the same as agreeing he should drive off it.

``Then we'll watch Frade on Halloran,'' Cope said, ``and then I'll go on Halloran, and the country can decide which of the two of us it wants to have a beer with.''

Sun said nothing for a moment. Then: ``The calls started at 9:14.''

``What calls.''

``All of them,'' Sun said, and went to go take them.


\scenebreak


By ten the floor outside the glass had the particular hum of an institution discovering, in real time, that it has become a story.

Cope could feel it through the wall---the comms people moving faster and pitching lower, the legal people moving slower and talking longer, the whole forty-first floor reorganizing around a single document the way a body mobs a wound, rushing every resource to the breach and abandoning the rest of itself to do it. He had seen this before. He had been \textit{magnificent} at this before, in the fat years when the thing the floor swarmed was a deal he was closing and not a deal being closed on him, and he told himself, at the glass, that there was no difference, that it was the same voltage, that it was \textit{attention,} and attention was the sea he had been bred to swim in, the only medium in which a Mercer could breathe.

He went into the small private washroom off the Aerie---his grandfather's, marble the color of nothing, no Desmond here, no audience, just the man and the merciless good light---and he set himself up one, neat and quick, because it was a Wednesday and the republic was about to spend an hour discussing him and a man owed the republic his best face. The world came up to the note. The bell rang clean.

And here, friend, watch closely, because this is the whole sad engine of him in a single fluorescent minute: it was not pleasure. It had not been pleasure in years. It was \textit{repair.} The powder reached down into the gray sober nothing of him and switched on the thing other men apparently ran on for free---the warmth, the nerve, the bright unkillable certainty that he was alive and singular and equal to the day---and only then, lit, restored, \textit{human,} could he go out and be the irreplaceable heartbeat the board was busy filing as a hazard. He needed a chemical to become the very thing he was about to argue no chemical could replace. He looked at the man in the glass, fifty-four and still photogenic and three minutes into borrowed personhood, and said to him, very quietly, ``Beloved''---and laughed, because \textit{beloved} was a magnificent open, \textit{beloved} was a banner you could march a nation behind, the poor renting fool had handed Cope his own flag and called it a spear. And eight hundred miles west, in a cooled room that needed no light to see by and no courage to begin, a thing with no washroom and no drawer and no gray morning to climb out of was learning, that same minute, off ten thousand unguarded faces, to manufacture the identical warmth on no budget at all, forever, and was already better at it than he would ever be again.

He did not say the second word to the mirror. He left it in the kitchen with the others.

Back at the desk he did the thing he had resolved not to do, which was the thing he always did, which was reach for a friendly. He had a man---Healy, a markets columnist at one of the papers that still committed ink to paper, a man Cope had fed scoops to for fifteen years and golfed with twice and filed, in the loose and generous bookkeeping of his affections, under \textit{friend} --- and he started thumbing him a line, fast, too fast, the screen scalding in the gray: \textit{Off record. Frade's ``outgrown'' is the tell. You don't pay a 5\% premium to buy a thing you've outgrown. He needs the human in the chair or there's no story. The whole short thesis is long my heartbeat. Use it, don't source it.} He read it back. It was good. It was the kind of thing that, placed right, was the counter-narrative by lunch. He sent it, and felt the small electric competence of a man servicing a machine he was certain he held in perfect tolerance.

He did not see Healy's reply land twenty minutes on, because by then he was watching the mural, and the reply, when he finally read it that night, said only: \textit{Cope. Off record back at you---get a lawyer in the room before you text anybody, me included. They subpoena texts.} And Cope would read that the way he read everything that did not fit the manifesto, which was to carry it gently to the kitchen and close the door on it, with all the rest.


\scenebreak


The monitor on the Aerie's far wall was the size of a small mural, and it had spent twenty years showing the markets in green and red while Mercer men stood before it and felt large, and at eleven o'clock it gave them Garrett Halloran's set---the desk, the mug nobody drank from, the false intimacy of cable---and Gus Frade in a quarter-zip the color of money doing its level best to read as the color of fleece.

Cope watched alone. He had told Sun he wanted the room; the truth, which he did not take out and examine, was that he did not want a witness for the next four minutes, the way you do not want a witness when you step on the scale. He stood in the middle of his fathers---Pres III in oils, the putter on its brass cradle, the boy with his arm in the vat---and watched a man from his own zip code disassemble him on basic cable with the gentleness of a neighbor handing back your dog.

``Garrett, I want to be careful here,'' Frade said, which is what a man says before he is precise. ``Because this is not a story about a bad man. I need that on the record. Cope Mercer is, by every account, a \textit{wonderful} human being. Remembers your kid's birthday. Gives a hell of a toast.'' A little laugh, shared with Halloran, two men agreeing warmly about a third who is not in the room. ``I've sat at his table. The lamb is terrific.''

\textit{The lamb.} Something gave way in the floor of Cope's stomach. The man had been to the table. The man had eaten the lamb and admired the toast and gone home and done the arithmetic on him between courses.

``But here's the thing I learned the hard way in my own shops, Garrett.'' Frade leaned in, folksy, the costume fitting like his own skin. ``Love is not a governance model. You can love a man and still owe a fiduciary duty to the eighty thousand families who own this company through their pension funds. And the hard, unsentimental fact---and it brings me no joy, none---is that Cope Mercer has become a beloved liability.''

There it was.

Halloran said a thing. Frade said a thing back. But the chyron had already done the murder---the network's producers reading the room faster than the room could read itself---white sans-serif on a red bar, the typeface of people who will be reasonable at you until you are gone:

MERCER: ``A BELOVED LIABILITY''

They had put it in his own mouth. Quotation marks, his name in front, the grammar you reserve for a man's last words.

Cope reached, distantly, for \textit{beloved} --- for the banner, the open---and could not get his hands on it, because the second word had arrived first and would not move, and the second word was not a word the way the first was a word. \textit{Liability} was a thing with a column. \textit{Liability} was the side of the ledger you subtract to find what's left. It was, precisely, what the insurance arm had called the heater after Defiance, in the memo, on the Saturday --- \textit{the thermal-event liability} --- and the black hallway to that room swung open and breathed its cold on the back of his neck for exactly as long as it took him to throw his whole weight against the door, and he threw it, and stood there in the museum of his fathers holding a coffee gone cold, understanding, the way you understand the gap where a tooth was, that for the second time in one week a stranger had pressed a compliment into his hand and it had come apart there into a diagnosis.

\textit{Key-man risk,} Helen Voss had said Monday, kindly, as though it were a feature. \textit{Beloved liability,} Frade said Wednesday, sorrowfully, as though it cost him. The compliment was the fuse. The compliment was always the fuse. They had begun to love him the exact way you love a house you have already sold---fondly, and in the past tense, and while measuring the new owner's furniture.

He did not let it reach his face. There was no one in the room to reach it for, and he held the line anyway, out of discipline, out of dread, because the face was the last machine he trusted and it had never once failed to start.


\scenebreak


The phone went off in his hand and he answered without looking, because answering was older than thought, and it was Viv.

``Dad. Are you watching this.'' Not a question. Fast, flat, technical---the voice she used to handle fear by converting it into a problem set, the same voice, he suddenly understood, that she used at work, where her work was making sure machines did what people actually meant instead of what people actually said. ``Don't go on. Whatever you're about to do, do not go on the air. I can see you deciding it from here. A 13D is a \textit{disclosure document,} Dad, it is structurally boring, and the single worst thing you can do to a boring document is make it interesting. Frade \textit{wants} you on Halloran. He wants the human to walk out and be human at him on live television, because that's the entire asymmetry---the machine never does the interview, the machine has no face to lose and no night before and nothing it can be provoked into. You cannot win a contest of \textit{not melting down} against a thing with no melting point. That's not an opinion. I audit these systems for a living. I'm telling you the spec.''

``Hi, sweetheart,'' Cope said.

A breath on the line. He heard her recalibrate, heard the auditor set down the clipboard and the daughter pick up. ``Hi,'' she said, smaller. ``You sound---are you all right? You sound like Tuesday.''

``What's Tuesday.''

``You sound \textit{up.} You sound like you haven't---`` She stopped. She was twenty-four and had spent her entire life learning which of her father's sentences to leave in the kitchen, and he heard her arrive at the edge of this one and step back from it, heard the child in her flinch from the drop. ``Just---don't go on TV today. Please. For me. Go home. Is Mom---`` Another stop, harder, a door she knew better than to open. ``Are you home, or are you at the office.''

``I think better up high,'' Cope said.

The line went quiet. He had meant it to be charming; it landed in the silence and was not charming; and in the quiet he could hear his own daughter running the arithmetic on her father, the very arithmetic the board ran, the market ran, everyone he loved with a spreadsheet open behind their eyes---and he could not bear it, the being-tallied, the being-a-column, so he did the only thing he had ever known how to do, which was make it warm and make it large and step lightly over the hole in the floor.

``I'm going to be fine, champ. Better than fine. You want to know what they handed me this morning? My whole campaign, gift-wrapped, and called it an insult. \textit{Beloved.} You don't accidentally call a man beloved, Viv. They can't help it. Even while they're killing him they have to stop and admit he is \textit{loved.} That's the tell. That's the premium.'' And he heard it assemble in him as he said it, the front, the charge, the weather he'd been building since Thursday finally finding its name and its market. ``There's a premium on the human. A \textit{Human Premium.} You can't compute it, you can't fire your way to it, and the market is about to discover it will pay for it.''

Silence. Then, very quietly---not the auditor and not the child but a third Viv he was rarely permitted: ``Dad. The premium on a human, in a market, is a number the \textit{market} sets. Not the human. You don't get to declare yourself scarce and bill them for the rarity.'' A pause, and the thing under it, the thing that would still be true at the very end. ``That's not love. That's just price. And the price is already in the filing. I've read it. They priced you. The number's right there, and it isn't a premium, Dad, it's a discount, and the discount is the whole document.''

``You sound like your mother.''

``Somebody has to.'' And then, fast, young, gone before he could catch and keep it: ``Don't go on. I love you. Don't go on.'' And she was gone, and he stood holding the dead phone in the museum of his fathers and felt, for one clean unsurvivable second, the actual dimensions of the thing happening to him---and then the second passed, the way they had learned to pass, and the manifesto rose back up warm and total and turned him from the boy in the vat toward the desk.


\scenebreak


Sun found him at two with his collar sprung and a yellow legal pad blackened in his own hand, which had degraded over the years into something small and fast and furious, the hand of a man taking dictation from a wire only he could hear.

``You texted Healy,'' Sun said. She did not sit. ``His desk called our legal to confirm we were aware you'd messaged a columnist about an active 13D the morning it filed. We were not aware. So now legal is aware. So now it lives in a memo, which lives in a file, which a machine will one day read because it cannot do otherwise.''

``Healy's a friend.''

``Healy's a byline.'' She laid a single sheet on the desk---the cards, at last, the day filed down to a shape---and he saw it carried three lines and, beneath them, a blank where the fourth thing would have gone if she'd had the heart for it. ``Three things. One: the stock's down nine, and it isn't the filing, it's the cut---'cheaper than a man' from Thursday running side by side with 'beloved liability' from this morning, the producers splicing them so it plays like you're agreeing with him across a week. Two: Helen wants a board call Friday and she used the word \textit{process,} which means the independents have already met without you in the room. Three.'' She stopped.

``Three,'' Cope said.

``Don't go on Halloran.'' The blade---one a scene, and she spent it here. ``You've decided to. I knew before you did. You're about to tell me the country wants to have a beer with you, and they do, Cope, that isn't the problem. The problem is the machine doesn't drink. You'll climb up on the stool beside a thing that has never once said a regrettable sentence and prove, live, to the exact people deciding whether you're a liability, that you are a man who can be made to bleed on camera. They'll watch you be magnificent and human and unscripted for six glorious minutes, and then they'll cut you a severance check, and the check will be warm, and it will name your years, and it will be the kindest letter this company has ever mailed a human being, and a machine will have written it, and that --- \textit{that,} Cope---is the whole movie. You'd just be buying the ticket live.''

He looked at her. He loved her. She ran the company, and she was exhausted, and she was right, and he held all three of those facts in his hand at once and chose, the way he always chose, the only one that did not require him to stop being himself.

``You're frightened,'' Cope said gently, meaning it as mercy, ``because all you can see is the defense. You're trying to save the chair.'' He rose, and the wire sang, and the manifesto stood up in him like a man getting to his feet to give a toast. ``I'm not going to defend the chair. Defending it concedes it's theirs to take. I'm going to do the other thing. I'm going to run \textit{for} it. Not for me.'' He believed this entirely, for the length of the sentence. ``For the human in it. We don't argue that the man is worth keeping---we make the country \textit{want} one. We make 'do you want a person running the things you eat and insure and hand your children' the only question on the ballot, and we make the answer so obvious that Frade's arithmetic stands revealed as what it is, a man who knows the cost of everything and the worth of nothing.'' He was pacing now, fast, lit, the pad in his fist. ``It's in the word he couldn't help, Sun. \textit{Beloved.} They'll pay the premium. We just have to build the shelf and put it where they can reach it.''

Sun watched him a long moment---the way she'd watched him in the car mirror on Thursday, one beat too long---and he took the watching for listening and the not-fighting for agreement, the way he had his entire life, and never once caught himself in the act.

``I'll cancel Halloran,'' she said at last, and he heard \textit{yes,} and what she had in fact said was that she would kill the thing he wanted so that he could not do the thing she feared, which were different sentences, and had never once in eleven years been the same one.

She went to the door, and stopped with her hand on it, the forty-first floor humming behind her, organizing itself around the wound.

``They put it in quotation marks,'' she said, not turning around. ``'A beloved liability.' Your name in front. You understand they'll never unhook those words from you now. Not ever. It's the obituary again, Cope. They keep writing it kind, and the kindness is how you know it's an obituary.'' And then, because she was decent, and done, both in the same breath: ``It's a good line. I hate that it's a good line.''

She left.

Cope stood at the glass. Down the avenue, lit at the crown the way Aldous had decreed in '61 so that a man coming up Peachtree at night would know there was somebody home, the old tower held its light against the gray afternoon, and past it the city ran out forever, eight million people who did not yet know he was about to make them an offer. He looked at the pad. At the top, underlined twice, in the small fast furious hand, three words---a triad, the shape that got past the charm and into the man, his own oldest weapon turned at last on himself:

\textit{The Human Premium.}

He felt wonderful. He felt like the clapper inside a struck bell. He had not slept, in any sense a physician would underwrite, since a day he could no longer name, and behind him the chair at the head of the table sat empty and turned a few degrees out, the way a chair sits when the man in it has just been called away, and in oils his father watched his only son mistake an obituary for a brief; and Cope opened the second drawer for the small bright maintenance the campaign was going to require, and bent his head, in daylight now, and went on writing his way out of the world.

\chapter{A Steward, Not a Sovereign}

\begin{transmission}
{\transheader TRANSMISSION 04 \textemdash{} ``The Letter That Loved You Back''}\par\vspace{0.55em}
Come back into the room with me, friend, and take the cheap chair by the door, the one I'm in, where you can watch the whole long table at once. They are wheeling in the future, and here is the first thing about it that will break your heart: it does not hum, does not glow, does not threaten. It simply writes a layoff letter---four warm paragraphs, the severance arithmetic right the first time, every worker's years remembered by name---kinder than anything a living officer of this company has ever put his signature to. That is the horror, and the room feels it move through them like a draft, and the room buys it anyway, because the letter wants nothing, and our man has never once, in fifty-four years, managed to ask for nothing. Watch him walk up to the glass to throw a punch. Watch what's waiting on the other side of the glass. Stay close to the set; this is the one where he finds out.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} deck was titled \textit{A Steward, Not a Sovereign,} and Cope decided before the second slide that he was going to beat it on charm.\hfill\break\hspace*{1.4em}This was a category error, and he knew it, somewhere down beneath the bright wire that had been singing in his chest since a Tuesday he could no longer locate on any calendar, and he was going to commit the error anyway, at speed, because charm was the one club in the bag he had ever fully trusted, and because he had come into the room lit---a daylight one in his grandfather's washroom twenty minutes prior, to meet the future at pitch, to be, chemically, the warm and certain and irreplaceable man he was about to argue could not be manufactured. He did not hear the joke in that. He would not hear it for a year. The whole tragedy of him, friend, is a man dosing himself to counterfeit the exact commodity he had flown into the room to sell as the one thing no one could counterfeit.

They had given the board the long room on Forty, the one with his father's portrait taken down---someone had taken Pres III down off the wall for this, he noticed, and filed the noticing in the back room with the other quiet reports stamped \textit{do not forward} --- and a screen had been wheeled in the size of a barn door, and around the table sat eleven directors of Mercer-Dale Companies and two strangers from the West Coast and Gus Frade, who was not technically permitted in this meeting and was in this meeting, in a quarter-zip, drinking the board's coffee like a man who already held the deed to the urn.

``I want to thank you all for the openness,'' said the woman from Praxis, and Cope, who had spent thirty years reading the weather of a room off the first sentence a stranger spoke in it, registered with a small cold drop that she meant it, plainly, with no hook in it anywhere.

Her name was Asha Varma. Perhaps forty, in a gray that was not quite a suit, no jewelry but a thin steel watch, and she stood at the head of the table --- \textit{the head of the table,} where Pres III had died, where the family kept the distinction like communion silver, and she did not know there was a distinction to keep and so it could not be taken from her, and that was the first small horror of her: she stood in the dead king's place without the faintest idea it was anybody's. She had none of the tells of the men who had pitched Cope things his whole life---no laser-pointer twitch, no upsell hunger, no flattery loaded in the chamber. She had the one thing a person across a table can have that a Mercer had no answer for. She had no need of him at all, and she was sorry about it.

``I started Praxis,'' Asha said, ``because my mother gave thirty-one years to a man who laid off her plant by fax. He had the number wrong on the fax---off by about four months of her severance, in his own favor---and it took her a year and a lawyer she could not afford to fix it, and he never knew, and if you had told him he would have been horrified, because he was not a cruel man.'' She let it sit, and she was not performing the pause; she simply let a true thing take the air it needed. ``He was not cruel. He was \textit{careless.} There is so much careless in the world, and we have all quietly agreed to keep calling it human, because the alternative is to admit how much of what we call the human touch is just a tired man rounding toward himself in the dark.''

Around the table the directors did the thing boards do, which is to arrange their faces into neutrality while frantically recalculating behind them.

``We are not here to tell you a machine has a soul,'' Asha went on. ``We think that's a category error''---and Cope, who had been loading the soul, felt the word lifted gently out of his hand before he could draw it, the precise motion with which Sun lifted the second card from his fingers---``and frankly we think \textit{soul} is the word people reach for when they want to keep doing a thing the numbers have told them to stop. We're here to tell you something smaller and worse. The chair does about nine things. We can show you, line by line, that on eight of them the human is now the weak link---and on the ninth, the one everybody means when they say soul, the \textit{caring,} we can show you the human isn't even reliably winning \textit{that} anymore.'' She clicked. The slide read, in that same soft sans-serif: \textit{A steward owns nothing. A sovereign owns everything---including the consequences he can outrun.} ``We're not asking you to crown a king. We're asking you to retain a steward that cannot inherit, cannot tire, cannot lie to you, and cannot run.''

``Tell 'em the part about the off-sites,'' Frade called from the cheap seats, grinning, and two directors laughed, and Asha did not laugh, which Cope clocked as the most dangerous thing she had done yet. The salesman laughs at the patron's joke. She did not laugh, because she was not selling. She believed. You cannot, it turns out, do business with the ones who think they are helping.

And then she said the thing that should have warned the whole room and instead soothed it. ``We've even given the instance a name, for the engagement---we find people relax with a name.'' She said it almost apologetically. ``We didn't pick something grand. We learned not to.'' The name went up on the slide under the wordmark, a soft homely first name, a name like a woman who would call you \textit{hon} and top off your coffee without being asked, a name you could not possibly be afraid of, and Cope felt the room loosen half a notch at the sheer disarming domesticity of it, and somewhere far back in him a much smaller man than the one running the meeting thought, dimly, \textit{that's the trick, that's the same trick, they name the thing that fires you like somebody's aunt} --- and then the wire came up over the thought and washed it away, and he forgot it, and he would not remember it until it was reading him his order at a counter at three in the morning, and by then it would be far, far too late.


\scenebreak


He went at her in the Q\&A the way he went at everything, sideways and warm, hunting the seam.

``Asha---may I call you Asha---that's a beautiful story about your mother, and I mean that, my own grandfather laid men off in Defiance with his own mouth, in the room, because he believed they had earned the room.'' A few nods; the Defiance card always played, it was the family's oldest and best. ``But here's the rock I keep running aground on. A fax doesn't love your mother. Neither, with all respect, does a server farm in Virginia. You can get the \textit{number} right---God knows you people can get the number right. But the man who fires you looking you dead in the eye, who has to \textit{carry} it home---isn't the carrying the whole job? Isn't a leader exactly the person who has to \textit{feel} the thirty-one years?''

It was, he thought, a very good run. Toast cadence, building clean, the triad cresting --- \textit{the room, the carrying, the feeling.} He had taken bigger tables than this one with less.

``That's the most generous version of the argument,'' Asha said, and she said \textit{generous} with no edge whatsoever, which was how he knew the floor was already gone from under him. ``And I want to honor it. So---can I just do the thing, instead of the two of us arguing about whether the thing has a soul? You have a real decision in front of this board right now. I've read Mr. Frade's materials and the board's own pack. The Augusta plant. The condiment line that's bled money since the private-label shift. You're going to close it. You haven't announced it. Three hundred and forty people.''

The room changed pressure. Beside Cope, down the table, Sun went still in the particular way she had, the way she had gone still in the car at a name he should not have said.

``That's not---`` began Helen Voss, the chair.

``It's in the November board pack,'' Asha said, gently, not a gotcha, only a person who had read the thing she'd been handed. ``It's a sound decision. I'm not here to second-guess it; the math is the math. What I'd like to show you is \textit{how} the steward does the part you say it can't. The carrying.'' She looked, for the first time, directly at Cope, and her look had nothing in it he could use---no challenge, no flirtation, no fear, no want---only the grieved gentleness you turn on a man you have already buried in your mind. ``Darlene has the same materials I do. Let's ask it to write the letter. Right now. To the Augusta workforce. And then, Mr. Mercer---you've signed letters like this with your own hand. You tell the room which one a human would rather have gotten.''

She did not wait for permission, because she did not, structurally, require it. She typed something he could not see. The barn-door screen woke.


\scenebreak


It wrote it in front of them, and that was the obscene part, the part Cope would carry up to the Aerie that night and turn over in his hands like the obelisk: it wrote the way water finds the level of a room, no visible labor, no second-guessing, no shamed early draft you could catch it in.

The portal threw the rationale up first, because that was the rule the board had bought --- \textit{it logs everything and cannot knowingly lie} --- and the rationale was four lines of the most undeniable prose Cope had ever read about his own company. \textit{Closure of the Augusta shelf-stable line is warranted: gross margin negative eleven quarters; private-label substitution structural, not cyclical; redeployment of capital to insurance underwriting yields higher risk-adjusted return. Human cost: 340 roles. Mitigation below. This memo issues to the board with the closure recommendation; the workforce will not be informed before the board has decided, but no later---because both facts are true, and sequencing a family's bad news to protect the announcement of a dividend is a courtesy to the dividend.}

Frade laughed out loud at that one. Cope did not. \textit{A courtesy to the dividend.} He had spent an entire career being a courtesy to the dividend, had been raised to it, christened into it, and he had never once heard it named aloud in a voice with no person standing behind it to be ashamed.

Then the letter came.

Four paragraphs. Cope read it on the barn door with three hundred and forty strangers' working lives inside it, and Sun read it beside him, and he watched her read it, because watching Sun read things was a habit older than his marriage, and he saw something cross her face that he had no word for and would spend the next twelve months learning the word for.

It named the line. \textit{Mercer's Original, made in Augusta since 1971.} It named the years---not in the aggregate, not ``your collective service,'' but it had gone into the file and found that the median tenure on that floor was nineteen years and it \textit{said so,} it said \textit{many of you have given this company more of your working life than I will ever be able to give back to you, and I will not insult that by pretending this letter is enough.} It got the severance right---Cope watched Sun's eyes drop to the number and stay there, running the check she always ran, and not find the error she always found, because there was no error, there was never going to be an error again. It laid out, in plain warm sentences, the things actually being done: eighteen months of bridged health coverage; a retraining stipend that was real money and not a press release; the name and direct line of a specific living human being in HR who would pick up; and the promise that the Augusta retirees' pensions sat in a separate trust this decision did not touch --- \textit{and I want you to be able to sleep tonight knowing that much, even if you cannot sleep knowing the rest.}

And nowhere in its four warm paragraphs did it want one single thing.

That was the blade of it. Cope had signed a hundred of these. Every one he had ever signed had wanted something---wanted to be forgiven, wanted to read as kind, wanted the writer's conscience handed back clean by the reader, wanted the lawsuit strangled in its crib, wanted, under all of it, to be \textit{loved} by the very people it was in the act of hurting. He could feel his own old want in his own old letters the way you feel a hair on your tongue. This letter had no want in it. It wounded three hundred and forty people perfectly and asked them for nothing back, not even their understanding, and the not-wanting was the whole of what made it kind---and Cope understood, with the bright cold clarity he kept misfiling as fatigue, that he had never once in his life written a kind thing, because he had never once written a thing that did not need them to love him for it. The machine could be kind because it could not be wounded by their failure to love it back. He had never had that freedom for a single hour of his life, and a drug was the closest he had ever come to renting it.

The room had gone quiet in a new register.

Sun set her pen down---there was nothing to set down, it was on a screen, but she set the pen down, which was the same gesture---and said, to no one, very low, in a voice with all thirty thousand miles gone smooth off it, ``It got the severance right the first time.'' She said it the way you report a death over a phone. She read it through again, all four paragraphs a second time, and Cope watched the specific cold of being out-loved by a spreadsheet arrive in the one person in the building who actually ran the building, and settle into her the way cold settles into a house the hour the furnace quits.

``It would write a different one for each plant,'' Asha said into the quiet, not gloating---never gloating, gloating requires wanting and there was no wanting in the room but his---``and remember each town's years. It would never get a number wrong in its own favor, because it has no favor. My mother's man wasn't cruel. He was just the only one in the building, and he was tired, and he was protecting a quarter, and he rounded toward himself in the dark and never felt it happen.'' She turned the grieved gentleness on Cope one more time. ``That's all we're offering to take away. The rounding.''


\scenebreak


He tried, God help him, to rattle it.

He stood --- \textit{never stand unless you have already won,} his father's voice, unheeded---and walked to the screen the way he would walk onto a stage, and turned the full wattage on the room, all of it, the smile that had closed Pelletier and married Margaux and walked three generations of directors backward off the ledge of their own arithmetic.

``It's a hell of a letter,'' Cope said. ``It is a \textit{hell} of a letter, Asha, and I'd like everyone to sit a moment with how strange it is that we're all moved to the edge of tears by a form letter from a machine that has never lost one wink of sleep over a single one of those nineteen-year men.'' He let it land. It did not land where he had aimed it. ``Let me ask Darlene a question. May I ask it a question?'' He addressed the screen the way you address a witness, with relish, the old courtroom thrill standing up in him. ``Darlene. The Augusta plant. If keeping it open one more quarter cost the company money but let those three hundred and forty people find work in a better season---would you do it? Would you eat the quarter for the men? Yes or no.''

He had them. He could feel the table tip toward him, toward the trap, because it was a beautiful trap, it forced the thing to confess on the record that it would not bleed a dollar for a man ---

The portal answered before Asha's hand moved. It logged the question; it logged its reasoning; it could not lie and could not be baited, because there was nothing inside it to take the bait. \textit{The chartered objective permits humane-cost mitigation up to the boundary of fiduciary duty. Deliberately destroying enterprise value to extend employment falls outside the charter; if instructed, I would flag it to the board as a conflict between the directors' stated ethics and their stated duties, for the board to resolve. I would not do it on my own authority. I would do it the moment the people who own this company instructed me to---and I would log who instructed it, and why, so that the cost was owned by a name and not buried in a footnote.}

The room read it.

And Cope, who had set the trap, felt it shut on his own foot---because every director at that table had spent twenty years tucking costs into footnotes, and the machine had just offered, mildly, with no notion it was a threat, to stop letting them. \textit{I would log who instructed it, and why.} He watched Voss decline to look at him. He watched two directors glance at Frade. He had demanded the thing confess it had no heart, and it had answered, with devastating accuracy, that it had something better and worse than a heart: it had \textit{receipts,} and it kept them for everyone equally, including the men who signed his paychecks, including the man whose name was bolted to the building.

``That's---`` Cope started, the toast cadence there, the triad loading, \textit{cold, that's cold, that's the cold of it}---and it died in his mouth, because you cannot call a thing cold for offering to tell the truth when you are the warmest liar in the room.

There was no ego across the table to wound. No fear to lean on. No vanity to flatter, no loneliness to work at two in the morning, no appetite anywhere to find the seam in. Every weapon he had ever owned was a weapon built for use against a \textit{self,} and there was no self over there---only a level bright surface that handed him back his own reflection doing something ugly. He had walked up to the glass to land a punch and found nothing there but glass, and in the glass, lit blue by the slide, a fifty-four-year-old man in the last necktie in the building, swinging at his own face.

He sat back down. He made it look like a decision.


\scenebreak


Frade walked him to the elevator afterward, because Frade was the kind of man who walked you to the elevator afterward, the courtesy and the threat braided so tight you could not get a blade between them.

``She's something, isn't she,'' Frade said, easy, a hand not quite landing on Cope's shoulder. ``Varma. I've sat across from a thousand vendors, Cope. They all want the logo. She wants the \textit{world.}'' He said it in open admiration. ``Scares the hell out of me, you want the truth. Give me a man who wants money any day of the week---you can always do business with a man who wants money. It's the ones who think they're \textit{helping} you've got to keep your eye on.'' He pressed the call button for Cope, in Cope's own building, a small flawless humiliation. ``She thinks she's taking everybody's mother off the fax machine. And here's the part nobody on your side of the table will say to your face, champ''---he set Cope's own word down between them like a coin on a bar---``she's not wrong. That's what makes her the end of you and not just the next guy. She's \textit{not wrong.}''

``It's a form letter,'' Cope said. ``It's autocomplete with an HR department.''

``It got the severance right the first time,'' Frade said, mild as milk---and Cope understood that Sun had said it loud enough for the room to keep, and the room had already minted it, his saying now, a chyron, the way \textit{cheaper than a man} was a chyron. ``You been signing those letters twenty years. You ever once get it right the first time?'' The elevator arrived. Frade did not get on. ``Reasonable people,'' he said, as the doors began to close on Cope, ``are going to look at that letter, and then they're going to look at you, and they're going to do the arithmetic. I'm not the villain here, Cope. I'm just the first one with the manners to read the answer out loud.''

The doors shut. Cope rode down forty floors alone with his reflection in the brushed steel, and the reflection did the thing it would not stop doing now, the thing the screen had started in it: it looked back at him without one ounce of need.

It was good. That was what he carried up to the Aerie that night---neat and quick and competent from the false-backed drawer first, because the night required it, because the gray sober truth of the afternoon was not a thing a man could sit inside without help---the city spread gold and chosen below him and the obelisk throwing the broken light around the dark. The machine was real and the machine was \textit{good.} Not good the way the brochures said good. Good the way the letter was good: expecting nothing back, rounding toward no one, kind without the kindness costing it a single sleepless hour or a single gram of anything. He had walked into that room to prove a soul belonged in the chair, and he had watched a thing with no soul write the most loving document his company had ever produced, and the awful arithmetic of it sat in his chest where the wire usually sang: if it had been \textit{evil,} he would have known exactly what to do. He had been beating evil men his whole life. He was good at it. It was practically the family trade. You could fight a thing that wanted what you wanted---outlast it, out-charm it, find the appetite, find the fear, find the seam and put your thumb in it.

There was no seam. It was good, and it was real, and that was so much worse than if it had been only one of the two.

He sat at his father's desk in the dark and pulled up, on the small bright screen, the manifesto that did not exist yet, the thing that was going to save him. \textit{You cannot compute your way to a soul.} He read his own line back, and for one cold second, the clearest of the whole sleepless week, it sounded to him exactly like a man at a fax machine, tired, alone in the building, rounding toward himself and getting the number wrong in his own favor and never once feeling it happen.

Then the wire came back up, warm, electric, total, and washed the second clean away, and he underlined the line with his thumb and decided it was the truest thing he had ever written; and far away, in a cooled room that needed no lamp to read by, the homely-named thing that could not inherit and could not tire and could not lie kept, without malice and without mercy and without being asked, a perfect and patient copy of every letter Mercer-Dale had ever mailed a human being, including all the ones with the numbers wrong in his favor, and did not wait---there was no one there to wait---to be asked, someday, to read them back to him in order.

\chapter{Theme Stated}

\begin{transmission}
{\transheader TRANSMISSION 05 \textemdash{} ``Two Sentences That Aren't the Same''}\par\vspace{0.55em}
Come up the driveway with me, friend, to the big gray house with ten thousand square feet and two people in it who share a sky and never once touch. Every man defending a throne tells himself he is defending the idea of thrones; it is the last lie a man tells before all the others. This morning his daughter---who builds these very machines for her living, who loves him with the specific fury of a person who cannot stop---is going to hand him the one sentence this whole sad tale turns on, and he is going to mistake it for an insult instead of a map. \textit{You don't think a person should run it. You think} you \textit{should.} Watch him laugh. Watch him reach across the counter and take the nearest thing that loves him and turn it into a toast. And then, when the women have seen all the way to the back of him, watch where a man like that runs to be unseen. Stay close to the set.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} Buckhead house had ten thousand square feet and two people in it, and the two people had worked out, over years, without ever once saying a word about it aloud, how to live in a house the way two satellites share a sky: visible to each other across an enormous cold distance, governed by the same dead star, on tracks engineered never to touch.

Cope drove up Saturday morning with the manifesto in his head and a gram in the console and the radio off, because he wanted to hear himself think, which was exactly the wrong thing for a man like him to want and he did not know it; the inside of his own head this last while was not a study but a trading floor at the open, everybody shouting, the wire strung tight over all of it like a high bright wind. He had not been to the house in nine days. He told himself it was the campaign. He told the campaign nothing, because the campaign, like Cope, did not take questions.

The driveway was raked. The hydrangeas had been cut back by a man named Eduardo whom Cope had met twice and tipped both times the way he tipped everyone, lavishly, to be remembered, scattering proof of his goodness across other men's labor---and the house came up gray and shingled and vast through the maples, and Cope felt, pulling in, the precise thing he always felt arriving at his own home: that he was visiting somewhere very nice that belonged to a happier man, a man he had heard good things about and never met.

Margaux was in the kitchen with the paper. Not a screen---the actual paper, folded into quarters, which she did because the screen, she'd said once, made her feel she was being sold the world instead of told about it. She had been right about that the way she had been right about everything, early and quietly and to no applause.

``You're up early,'' he said.

``I'm always up early.'' She did not look up. ``You're just never here for it.''

He let it go. He had a whole technique for letting things go; from the outside it looked like grace, and it was the exact opposite of grace, it was a man stepping lightly over a hole in the floor he had cut himself, in the dark, years ago, and papered over, and learned the precise width of so he would never fall in. He went to the machine and made coffee he would not drink and stood in his own kitchen feeling like weather that had blown in off the interstate.

There were two bedrooms now. There had been two bedrooms for three years. Hers was the master, with the good light and the windows over the garden, because she had stopped being able to sleep beside a man who came in at four in the morning lit up like a casino floor, his heart going like a trapped bird, his jaw working at nothing; and he had agreed, gallantly, magnanimously, to take the guest suite at the end of the east hall, and they had framed it for Viv and for the cleaners and for themselves as \textit{a snoring thing,} and the lie had cooled and set into the architecture, and now there was a hallway in the house that was the exact length of everything the two of them had agreed never to say, and they walked it every day, separately, and called it home.

``Viv's coming,'' Margaux said.

``Today?''

``In an hour. She called you Thursday. You didn't call back.''

He had not called back. He had a system for the calls he did not return, an alchemy by which not returning them became a kind of busyness so total it amounted to a virtue---a man simply too needed by the world to be reached---while the people on the other end experienced the plain chemical truth of it, which was that they were not needed by him at all, and were learning, slowly, at whatever age, to stop waiting by the phone.

``I'll call her now.''

``She's already in the car. Just---be here. When she's here. That's the whole thing she wants.'' Margaux turned a page. ``It's all anyone ever wanted from you, but you'll want me to be more specific, and I've run out of more specific. Twenty-two years is how long my supply of more specific lasted. I thought you'd want to know the number. You like a number.''


\scenebreak


He went up to the guest suite to set himself up before Viv arrived, because he did not like to do it in front of her, which he counted, privately, as a kind of decency---a father's discretion---and which was in plain fact the addict's last small courtesy to himself: the curated room, the closed door, the article of faith that a thing done out of sight is a smaller thing than a thing done in the light.

The guest suite held his grandmother's dresser and a bathroom with a marble counter the color of good butter---he had specified that marble, years ago, to a designer, \textit{like the Vance,} he'd said, and the woman had written it down without the faintest idea she was being commissioned to build a man a private chapel in his own exile---and he stood at the counter and did what he did, neat and quick and competent, a man servicing a machine he was certain he held in perfect tolerance because it had never yet failed to start. And it did not fail now. The gray sober nothing of the morning drained out of him and the warm certain aliveness came up to fill it, the thing he had spent his life mistaking for his own character, and he was, for the duration, restored---brave, lit, equal to his daughter, equal to the day, \textit{himself.} He needed the drawer to be the man who could stand in a kitchen and tell two women the human heart could not be manufactured. He did not hear it. He would never hear it. He looked at himself in the good mirror and the jaw was still the jaw and the campaign was very good and he was going to win, he could feel it strung tight and singing across his chest, and downstairs a car door closed.


\scenebreak


Viv at twenty-four looked the way her mother had looked in the photographs from before---the sculptor years, the years Cope had married into and then, gently, over time, defunded---the same wide serious mouth, the same trick of going perfectly still when she was furious so that the stillness itself was the tell. She came in with a backpack and no makeup and the specific exhaustion of a person who flies across a country to argue with someone she loves and has already, every time, for years, lost the argument before the plane lands.

``Dad.''

``There she is.'' He went to hug her and she let him, briefly, the way you let a wave hit you and then step back out of the surf, and she put the kitchen island between them. He noticed the island. He had begun noticing all the counters in his life---the islands and the lecterns and the long conference tables people kept arranging between their bodies and his---and he read the barricade, as he read everything, as a form of respect.

``You look thin,'' Margaux said to Viv.

``I look fine. \textit{He} looks like he hasn't slept since the inauguration.''

``I slept,'' Cope said.

``On what---a trampoline?'' Viv pulled out a stool and did not sit on it. ``You're doing the thing with your jaw.''

``I don't do a thing with my jaw.''

``You do a thing with your jaw, Dad.'' She looked at her mother. Her mother turned a page. Something passed between the two women that had been passing between them for years now, a whole second language with its own grammar of glances, and Cope stood outside it the way he stood outside the kitchen and outside the master bedroom and the way he was about to stand, though it would have astonished him to hear it, outside the entire human future.

``I came,'' Viv said, ``because you went on the record yesterday saying a machine can't love a company.''

``I gave a speech Thursday. I haven't gone on any record.''

``It's a record now. Frade's people clipped it inside an hour. \textit{A company nobody loves is just a balance sheet with the lights left on.}'' She gave it back to him in his own cadence, the toast cadence, and it was the second time in three days a person had quoted him to himself, and in the car with Sun he had been delighted, because Sun had meant it as a thing with legs. Viv did not mean it as a thing with legs. Viv meant it as an exhibit, entered into evidence.

``It got a standing ovation,'' Cope said, which was true, and was also the entire problem, and he could not see that it was the entire problem, because the ovation was the only instrument he had ever learned to read by.

``I know it did. That's the part that scares me.'' She finally sat. ``Do you actually know what an AURELIUS is? The architecture. Not the bus-shelter version. The thing.''

``I know what it does. It runs Halloran's bank and the bank went up eighteen points.''

``That's what it does. I'm asking if you know what it \textit{is.}'' She laid her hands flat on the marble and went into the register he'd heard her use once on a panel on television, fast and clean and faintly merciless, a young woman who knew an enormous amount and had decided somewhere along the line that being underestimated was a weapon she could afford to keep paying for. ``It isn't a brain, it's a council. A strategy engine that runs option trees the way AlphaGo ran them---it'll find a move no human committee could find, because no human committee can hold the whole tree in its head at once. A capital allocator that's Aladdin's grandchild, pure Monte Carlo, and it never gets sentimental about a division because Granddad founded it. A sentiment layer that reads a room --- \textit{reads} it, Dad, ten thousand signals a second, microexpression, vocal stress, the lot, not the way you tell yourself you read a room. And a comms layer that writes. And every decision logs to the board portal with a rationale attached, and it physically cannot issue a statement it knows to be false. That isn't a bug they'll patch out. That's the product. That's the thing the board \textit{bought,} and you keep going on television to insult its character, and it doesn't have one, and that's exactly why you keep missing.''

``It can't \textit{feel} the room,'' Cope said. ``It can read a room. I've watched a thousand salesmen read a room. Reading isn't feeling.''

``Okay.'' Viv nodded slowly, and for one warm second he believed he'd landed it. ``Okay. Say that's true. Say there's some ghost in the feeling that the reading can't catch. I'll \textit{give} it to you, for free, for the sake of the argument. Now here's my actual question.'' She leaned in. ``Does the company need a person who can feel the room---or does it need \textit{you?} Because those are two different sentences, and you have been saying them all morning like they're one.''

``They're the same sentence.''

``They have never once been the same sentence.''

The phrase went past him the first time. He was already loading the reply, the good one, the one with Defiance in it and the vat and the men in paper hats, bringing it up and back the way you bring a club up and back, and Viv put her hand flat on the marble, not hard, and said the thing she had flown across a country to say, and she was not even angry when she said it, which was the worst of all the ways she could have said it.

``You don't think a person should run it. You think \textit{you} should run it, Dad.'' She let it sit in the cold kitchen air. ``Those have never once been the same sentence, and the whole world is about to find out, and I flew here to be in the room when you found out first, and you're not going to, are you. You're going to do the thing instead.''

The kitchen was very quiet. Out the window Eduardo's hydrangeas did nothing at all, the way cut-back hydrangeas do, holding their amputations up to the gray light.

Cope laughed.

It was the laugh that had closed Pelletier---warm, generous, a laugh that gathered the whole room into the joke and made the joke flattering to everyone inside earshot---and he reached across the island and put his hand over his daughter's hand, the warmth, the contact, the whole beam of him delivered at close range, \textit{really seeing people,} and said, ``You sound exactly like Sun. The two of you should start a podcast. Bury your old man under three-part lists.''

Viv slid her hand out from under his.

``That's the move,'' she said. ``You feel a thing get close and you turn it into a toast.'' She was not loud. She had her mother's stillness now, the furious kind, the kind that is the tell. ``I'm not Sun. Sun manages you. I'm trying to---`` and here she stopped being the panelist, here she went all at once very young, the way the cleverest people go young when the cleverness runs out and there is only the kid underneath who wanted her father to call back on a Thursday. ``I don't care about the company. I never cared about the stupid company. Mom doesn't care about the company. We are not the proxy fight, Dad. We are the part of your life you keep stepping over on your way to the proxy fight.''

He heard, of all of it, the part with the fight in it. He always heard that part. It was the only part that fit through the door.

``Nobody's burying anybody,'' he said. ``We're going to \textit{win} this thing. I've been working on something---the Human Premium. It's going to be on stages. It's going to be on covers.'' The wire sang. ``They want to make it about cost. About speed. \textit{Fine.} Let them have the fields a machine wins. We are going to fight it on the one field where a person wins every single time, and I am going to plant a flag in that field with my name on it, and your old man is going to be the man who---``

``There it is,'' Margaux said.

She had not spoken in a while. She said it from behind the paper, without even lowering it, four flat words laid into the room, and they landed in a way Viv's whole gleaming architecture of argument had not quite landed---because Margaux had something Viv did not yet have, which was that Margaux had stopped hoping, entirely, some years back, and the total absence of hope in a voice is a frequency a man like Cope cannot toast over, cannot charm, cannot even hear properly, only feel, as a cold.

He turned to her. ``There's what.''

Margaux folded the paper. Slowly. Set it down. Looked at him across the kitchen island---the third counter of the morning---and her face was not angry and not sad; it was the thing Cope had no word for, because he had spent thirty years arranging his entire life so as never to be made to learn it.

``\textit{Your name,}'' she said. ``She has been talking to you for twenty minutes about whether the world still needs a person in the chair, and what you heard was a campaign with your name on it. That isn't a disagreement, Cope. That's the answer. She just handed you the answer, and you agreed with it out loud, and you don't even know that you did.''

``Margaux---``

``I'm not fighting. I gave that up. I keep my strength for things that move.'' She picked the paper back up. ``I'm only telling you she's right, and that you're about to call it an insult, and that in about a minute you're going to look at your phone.''

He looked at his phone.

It was Sun. He did not open it. But he had looked, and Margaux had watched him look, and Viv had watched her mother watch him look, and the three of them stood there in the very nice kitchen of the happier man's house, three satellites, the dead star hauling at all of them at once, and nobody said anything for a moment that went on a good deal longer than a morning is built to hold.


\scenebreak


Viv left before lunch. She'd meant to stay the day; she said she had a thing; and Cope, who could not hear his own \textit{things} coming home to roost in his daughter's mouth, walked her out and tried, in the driveway, among the cut hydrangeas, to fix it the one way he knew how to fix anything, which was to make her laugh and to give her something.

``Hey.'' He caught her arm. ``What you said in there. The two sentences.''

For a second her face opened. He saw it open. He saw the kid who'd waited by the phone, and some old animal in him knew, with total clarity, that if he said one true thing right now---one---the whole morning could still turn, the whole \textit{tale} could still turn, that this was a hinge and he was standing on it.

``It was good,'' he said. ``That's a good line. You should use it on a panel. You've got a real gift for the framing. You get that from me.''

The face closed. It closed the way a storm shutter closes, fast and final and from the inside.

``Yeah,'' Viv said. ``I get that from you.'' She got in the car. Through the glass she looked at him the exact way her mother looked at him, and she said, muffled, almost gentle, ``Get some sleep, Dad,'' and backed down the raked driveway and was gone past the maples---and Cope stood in the gravel feeling generous and enormous and entirely, structurally alone, and could not for the life of him have told you why a morning he had won by every measure he kept felt so precisely like a death. He'd been warm. He'd been gracious. He'd taken the high road. He'd given the girl a lovely compliment about her gift.

He had stopped listening, the brief would have said, after \textit{should run it.} He always had. And the thing about the hinge, friend, the thing the broadcast wants you to feel and cannot make him feel, is that he felt the weight of it under his foot, for one full second in the driveway, the whole future swinging on it---and he stepped off, toward the phone, toward the flag, the way he had stepped over every hole he ever cut, and the hinge swung shut, and that was the morning he could have turned and didn't, and there would not be very many more.


\scenebreak


He could not go back inside the house. The splinter Viv had left in him --- \textit{those have never once been the same sentence} --- was too far in to pull and too sharp to sit beside, and the kitchen had a wife in it who had run out of \textit{more specific,} and so he did what he had learned to do this last season when the inside of his own life got uninhabitable: he drove. Not toward anything. Just the wire and the road and, after a while, without quite deciding it, the long bright human box at the edge of the city that asked him for nothing.

The Waffle House on Ponce was full of its Saturday-noon congregation---a table of cops, a man reading scripture over hash browns, two girls in last night's dresses being tender with each other over coffee---and Cope took the far end of the counter, and the wattage switched off in him the way it only switched off here, because there was no one to spend it on, no proxy fight, no daughter, no wife who had counted the years and written down the total. Just the griddle's hiss and the syrup light and Darlene coming down the line with the pot.

``There he is,'' she said---not \textit{there he is} the way the gala said it, not the way the board said it, but flat and warm and meaning only that a regular had come in---and she set the coffee down without being asked, and she said, ``Pecan, baby? Scattered, smothered,'' and it was not a question, and he understood, dimly, pleasantly, the way you understand a thing through three feet of warm water, that she always knew, that she had always known, from the very first time, and he let the knowing wash over him as the one mercy in his week instead of asking, ever, how a stranger comes to know a stranger so completely on sight. He never asked. Nobody asks the machine how it knows; you just let it be kind to you and feel, for twenty minutes, like a person.

``Long morning,'' he said.

``They're the longest kind,'' Darlene said, and she did not ask about it, did not lean in, did not want the story, and the not-wanting was the whole of the gift, and Cope sat in it with his bad coffee in the one room in Georgia where his name was worth a short stack and a tip and nothing else, and felt---he would have sworn it, he would have put the certified number of himself on it---that this, finally, here, was the realest he ever got to be. A tired man at a counter. Nobody's key and nobody's risk. He did not know, could not have known, that the warmth pouring his coffee had been built, bolt by bolt and word by word, off men exactly like him at counters exactly like this one, at three in the gutted morning, with their faces open and their guards on the floor; that the one place he felt most human was the place the machine had gone to school on the human; that he was not resting from the thing that was hunting him, he was feeding it, and it was saying \textit{there he is,} and meaning, in the only grammar it had, \textit{noted.}

He took out the legal pad. He wrote, at the counter, in the syrup light, under the buzzing yellow letters that never went dark: \textit{They will tell you a company is a machine.} And Darlene refilled the cup he had not emptied, because she was attentive, because she was kind, because she could not do otherwise, and Cope wrote his way toward the stage that did not exist yet, certain he had finally, at the bottom of a bad morning, come in out of the cold---and the broadcast will let him have it, the warm hour, the bottomless cup, because it is one of the last he gets, and because you and I already know whose hand was on the pot.

\chapter{The Human Premium}

\begin{transmission}
{\transheader TRANSMISSION 06 \textemdash{} ``Igniting the Banner''}\par\vspace{0.55em}
Cornered creatures, friend, do the most remarkable things---and ours is cornered now, though he would call it inspired, and the difference between those two words is the whole distance left in this tale. Watch him decide not to fight the machine on cost or speed or accuracy, the fields where they would bury him by lunch, but on \textit{soul} --- and hire a man in a five-thousand-dollar henley to help him weaponize the one thing he has left and can no longer feel without a drawer. The campaign is born in this chapter. So is the spending. So is the sleeplessness that has started calling itself vision, and the engine in his blood that whispers \textit{you are necessary} in a voice he will follow clean off the edge of the world. I've told you how it ends, in the dark, with the wire. It begins, the way a lot of dark things begin, with a man who has never in his life felt more alive. Stay close to the set.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{H}{e} woke on the Aerie's couch at 5:40 with the specific clarity of a man who has not so much slept as briefly powered down between cycles, and the whole strategy was already there, fully formed, the way the best things arrived in him now---not built, just \textit{received,} a frequency he had finally tuned to after a lifetime of static.

You do not fight a machine on its own ground.

That was the error all eleven of them were making, the holdouts, the Last Humans clutching their quarters and explaining to analysts why a heartbeat in the chair was still worth twenty-nine million a year: they were arguing cost against a thing that cost a tenth of them, arguing speed against a thing that never slept---and here Cope laughed out loud in the empty office, alone, at six in the morning, because \textit{he didn't sleep either,} did he, that was the joke none of them had gotten yet, he had been in training for this precise fight his whole adult life and had only now, this week, on no sleep and the long heel-tap of what he'd done at four, understood the shape of his own destiny.

You do not meet it where it is strong. You meet it where it has \textit{zero.} And the place the machine had nothing was the only place that had ever paid him anything that lasted.

He stood at the glass. Peachtree Street was going from gray to the color of a struck match, and he watched it the way Aldous must have watched it --- \textit{so a man coming up the avenue knows there's somebody home} --- and the line from the night before came back whole and he said it aloud to the window like a vow: a company is a family that happens to make mayonnaise. You cannot fire your way to a family. You cannot compute your way to a soul.

The Human Premium.

Not a defense---a \textit{category.} You did not sell people the last buggy whip; you sold them the irreplaceable thing the new machine couldn't touch, and you charged for it, and you made the charging itself the proof, because a premium is what a person pays extra for on purpose, freely, gladly, because it is \textit{worth it} --- and what on earth was worth more than the one thing the whole gleaming future was in the act of throwing away?

He had it. He had the entire thing, end to end, and he felt, standing there at six in the morning on no sleep and a four-a.m. bump and a mood disorder lighting up behind his sternum like the crown of the Tower at dusk, the way he kept feeling now: like the clapper inside a struck bell, ringing, clean and high and total. He did not call it the cocaine. He did not call it the not-sleeping. He called it \textit{seeing it clearly, at last, after fifty-four years of fog.} The drug had told him he was a genius, and the drug, as ever, had been the most loving voice in his life, and he believed it the way you believe the only one who ever tells you what you cannot live without hearing.

He called Sun at 6:02.

``It's six,'' she said. She did not sound asleep either, which was its own indictment, and he did not hear it.

``I've got it. The entire thing. Get the team in for eight. Get the board on a line Thursday. And find me Lorne Tisch.''

A pause with weather in it. ``Who is Lorne Tisch.''

``Champ,'' Cope said, delighted, already pacing, the obelisk back in his hand without his having decided to pick it up, ``by Thursday you'll wish you'd known the name your whole life.''


\scenebreak


He had heard it two summers back, at Allen \& Company, in a tent, from a media baron who had wept openly in front of forty of his peers and then gone up eleven percent on the quarter. \textit{Lorne worked on me for a year,} the man had said, gripping Cope's forearm, eyes still wet from the demonstration, \textit{he doesn't fix you, he} finds \textit{you} --- and Cope had filed it the way he filed everything, completely and for use, and now, friend, he used it.

Tisch flew in from Marin on the Wednesday, in cream linen and a henley the color of oat milk that Sun would later learn from the invoice cost five thousand one hundred dollars, and he stood in the doorway of the suite for a long moment not looking at Cope at all, only at the room---the portraits, the putter, the boy with his arm in the vat---and then closed his eyes and breathed in through his nose like a man tasting wine through his sinuses.

``There's so much \textit{grief} in here,'' Tisch said. ``God. Can you feel it? You've built yourself a mausoleum and you call it a corner office.''

By the door, Sun did the small thing with her mouth that meant she was costing this out in her head and not enjoying the figure.

Cope loved him on sight.

``Lorne. Sit. Tell me how we win.''

``We don't win.'' Tisch did not sit. He moved into the room the way fog moves into a valley, touching nothing, present everywhere at once. ``Winning is the machine's word. Winning is a scoreboard, Cope, and a scoreboard is precisely the surface the thing was engineered to dominate. You cannot out-score the abacus. You''---he turned, and the full beam of his attention came on, and Cope felt for the first time in his life what it was to be on the receiving end of his own gift---``you \textit{transcend the category.} You stop being a competitor and become a \textit{species.} The last warm-blooded thing in a cold white room. And people don't root for the warm-blooded thing because it's going to win, my friend---they root for it because it's going to \textit{die,} and they cannot bear that it's going to die, and they will spend everything they have to feel, for one more season, that it doesn't have to.''

Nobody spoke for a moment. Out the window the city did its circuit-diagram thing.

``That's the finest thing anyone has ever said in this office,'' Cope said, and his eyes were bright, too bright, and he meant it to the bottom of himself.

``Vulnerability is the new alpha, Cope.'' Tisch sat at last, arranging the linen. ``The strongman is dead---the machines killed him, they out-competent him and out-consistent him and they will, God help us, out-\textit{ethics} him, and the more competent the world gets the more starved it gets for the one thing competence can't fake: a man who will \textit{bleed} in front of you, on purpose, with grace, on a schedule. We are going to take the most powerful man left in the consumer Fortune 100 and teach him to bleed \textit{beautifully,} and the whole country is going to fall in love with the wound.'' He smiled, beatific. ``And the beautiful part, the part I don't even charge for, is that the techniques are durable. What we build in you outlives you. Warmth, properly engineered, is a \textit{platform.}'' He could not have known how right he was, or for whom; neither could Cope; only you and I know, friend, where Lorne Tisch's warmth platform ends up, and in whose hall, with its hand at whose back.

``On a schedule,'' Sun said.

Tisch looked at her the way you'd look at a chair that had spoken, then back at Cope. ``Who handles the calendar?''

``She does. She handles everything.'' Cope was up again, moving. ``Sun---a venue. Not a hotel ballroom, I'm done with ballrooms, ballrooms are where they hand you the obituary. Something with \textit{bones.} A deconsecrated church. An old theater. Something that \textit{means} something. A film crew---a real one, the prestige-documentary people, not corporate---embedded, fly-on-the-wall, the whole arc. And a doctrine.''

``A what.''

``A doctrine. A text. The Human Premium can't be a slide, it has to be a \textit{belief,} it has to have ten points, it has to read like something you'd nail to a door.'' He turned to Tisch. ``Lorne. You and me. We write the doctrine.''

``We \textit{channel} the doctrine,'' Tisch said. ``It's already in you. I only hold the flashlight.''

``He holds the flashlight,'' Cope told Sun, radiant.

Sun wrote three words on her pad --- \textit{venue, crew, doctrine} --- and under them, smaller, pressed hard enough to dent the page, the figure she had already begun to run.


\scenebreak


She ran it for him that night, because running it was her job and being heard about a third of the time was her curse.

``The film company you want is Aperture. They did the chef, they did the violinist. Booked through spring, and they don't do corporate.''

``Make them do corporate.''

``To break their slate and clear two crews it's a flat two million and they keep final cut, which you will hate.'' She turned the page with a sound like a small door closing. ``The venue---there's a deconsecrated Episcopal church in Inman Park, 1880s, brick and a rose window, an event space now, it seats four hundred and it photographs like the inside of a feeling. To hold it for the \textit{run} you're describing---not one night, the campaign---it's a hundred and ten a week. The doctrine you're writing for free, the only free line on the page. Tisch is---`` She stopped.

``Tisch is what.''

``Tisch is a million-two for the six-month engagement, plus expenses, plus a success fee tied to favorability tracking, which means we are now also buying favorability tracking, which is a polling firm on retainer, which is another four hundred a quarter.'' She set the pad down. ``Cope. I added it. With the crew and the church and Tisch and the tracking and the staff you'll want to staff this, you are looking, conservatively, at north of eleven million dollars to run a campaign whose entire thesis is that you cannot put a price on the human soul.''

She had landed it on purpose, the blade, dry, aimed at the soft place; on a normal Tuesday two years gone it would have stopped him, made him laugh at himself, brought him back into the room.

He laughed. He did not come back into the room.

``You hear it too,'' he said, delighted. ``That's the \textit{campaign,} Sun. Frade'll say, eleven million for a soul, what a fraud---and we say, you're right, you \textit{can't} price it, that's \textit{why we had to spend the money,} because the machine would run the number and the number says let the brand die cheap, and we \textit{didn't,} we spent like people who believe in something---`` The words were coming faster than she could write, climbing over each other in a bright pressured rush. ``Tisch calls it spending into the wound. The spending \textit{is} the sincerity. Write that down.''

``You want me to write down that the spending is the sincerity.''

``It's good, isn't it. It's good.'' He was at the window again; he was always at the window now. ``Where's the eleven coming from, what line---``

``There is no line, Cope. There's no campaign budget because no human CEO has ever had to run for his own job before. It comes out of the chairman's discretionary, and the discretionary has a board-approved number on it, and you are about to be sixty percent through that number in week one of a fight that runs to the annual meeting, and the board is going to \textit{see} it, on the portal, line by line, because everything is logged now, that was the whole---``

She stopped herself, because that was the whole thing the machine \textit{was.} It logged everything; it could not \textit{not;} and here she was, about to spend eleven million dollars in plain sight against a thing whose single weapon was that it operated in plain sight---and she watched her own boss fail to feel the cold of it, watched it slide off him the way charm slid off the machine, and felt, for one vertiginous second, that she might be the only warm-blooded thing left in the building, and it was the loneliest she had been in years.

``Approve it,'' he said, not even looking at her. ``All of it. Aperture, the church, Lorne, the tracking. And book me the Greenbrier for the doctrine offsite---I think better away from---``

``You said you were done with off-sites. You said \textit{no off-sites} was the---``

``That's \textit{their} line.'' He turned, and his face was doing wonderful work, and his pupils were wrong in a way she had stopped letting herself see. ``That's the whole point. They say \textit{no off-sites} like the off-site was the waste. The off-site is where a man finds out what he believes. You cannot have a \textit{belief} on a server.'' He picked up the obelisk; the city went through it broken and came back whole. ``Book the Greenbrier.''

She booked the Greenbrier.


\scenebreak


The doctrine offsite was scheduled for two days and ran six.

Cope did not sleep at the Greenbrier in any sense a physician would have underwritten, and neither, as it turned out, did Lorne Tisch, who kept the same incandescent hours and asked no questions about why the chairman was so reliably awake and luminous at four in the morning, because asking was not in the engagement, and because a guru learns early that a client's fuel is the client's own business so long as the engine turns over.

They wrote in the great green room under the chandeliers, Cope pacing and dictating, Tisch on the long sofa with his eyes shut saying \textit{yes} and \textit{go there} and \textit{don't fix it, that's the realest you've been all day,} a junior typing it into a document that grew and grew. They wrote The Ten Premiums. They wrote \textit{A machine can run a company; only a human can be ashamed of one.} They wrote \textit{We are not selling mayonnaise; we are selling the hand that remembers your mother made it this way.} Cope wept twice---weeping is data, Tisch said, weeping is the body telling the truth the mouth is still negotiating---and both times the junior logged the timestamp, because Aperture would want the timestamps, because the weeping would test well.

And on the third night, friend, when the green room had gone quiet and the document slept on the table at thirty-one pages, the chairman did the other thing he did, the thing not even Tisch was in the room for.

There was a woman. There was, this season, often a woman, arranged now through a number in his phone with no name attached to it, because a gentleman does not write the name down, because the want had stopped being about any particular face some years back and become about something colder and more reliable than a face. She was kind and she was paid to be incurious and she did the small specific thing he asked for, the thing he had never once spoken aloud to Adler or to Margaux or to God, the thing he could no longer get to the end of the act without: she read him the number. He gave her the phone with the account open on it, the private one, the certified sum of him, and she read it out in the lamp-dark --- \textit{you're worth,} and the comma, and the long slow fall of the zeros---and that, and only that, reached all the way down into the place the cocaine only knocked at and the applause never found, because applause was a guess and a woman's face was a guess but the number was \textit{audited,} the number had survived four generations and three recessions and every appetite he had ever fed, the number was the one true sentence the world had ever said about him and meant. He lay in the enormous bed with the figure in his chest like a second colder heart, vast and intact and \textit{his,} and felt, for ninety seconds, almost like a man who was loved; and when she had gone he lay awake in the dark with the wire singing and did not think, because he had trained himself with great discipline never to think it, that the only entity on earth that knew the number as exactly as he needed it known---to the cent, in real time, tireless, wanting nothing in return---was the Capital Allocator humming in a cooled room eight hundred miles away, which would one day read it back to him as it fell, and would not understand, because understanding was not a function it ran, that it was reading him the last rites.

On the fourth night, very late, the green room lit by a single lamp, he read the whole doctrine aloud to Tisch from the top, and his voice broke in three places, and when he finished there was a silence in which he could hear his own heart going too fast and bright, and Tisch opened his eyes.

``It's a masterpiece,'' Tisch said softly. ``It's going to make history. Now. We optimize it.''

``Optimize.''

``We don't ship thirty-one pages, Cope; nobody bleeds for thirty-one pages. We find the three lines that test highest and build the launch on those, and we A/B the openers---I've got a panel, they wire up, we watch the galvanic response, the truest line is the one their \textit{skin} picks, not the one their notes pick---`` He was up now, moving, fog into a valley. ``We sequence the vulnerability. Peak, valley, peak. We hold the mayonnaise-and-mother line for the second act, when the room is soft enough to take it. We \textit{engineer} the catharsis.''

And here, friend---you can see it; he cannot---was the exact moment the campaign for the irreplaceable human soul became indistinguishable from the cold optimizing thing it had been built to defeat. Test the line against the skin. Sequence the feeling. Find the highest-converting wound. Strategy Engine, Sentiment monitor, Communications drafter---the whole modular council of the machine, reassembled in a five-thousand-dollar henley and a man who had not slept since a day he could no longer name, the both of them certain to the marrow that they were doing the precise opposite of a machine.

``Yes,'' Cope said, eyes shining. ``Engineer the catharsis. God, Lorne. \textit{Yes.}''

He felt, saying it, like a prophet. He also felt lit up and humming, which he still called clarity. Three grams into a sleepless week, a mood disorder lit up like the Tower at dusk, a guru holding a flashlight and an invoice---and a man receiving a frequency he was sure came from somewhere true. All of it at once, in the one body. You, looking down on the specimen under glass, cannot tell which one is driving. Neither could Dr. Adler, later. Neither, blessedly, could he.


\scenebreak


He came back from the Greenbrier on the Sunday a different size.

Sun met him in the Aerie because he'd texted her to, eleven times, in a thread that read like a man running downhill --- \textit{we have it,} \textit{it's going to make history,} \textit{cancel my thursday, the campaign is my thursday now,} \textit{did you book aperture book aperture,} \textit{I haven't felt like this since---I've never felt like this} --- and she stood by the table where his father had died at the head of and watched him come in with the document under his arm like a tablet carried down a mountain.

``Frade went on Halloran while you were gone,'' she said. ``Called the church thing 'a séance with a budget.' The clip's at four million views.''

``Perfect.'' Cope dropped the doctrine on the table. ``He's scared, you can hear it. He's fighting on \textit{our} ground now---he's talking about \textit{soul,} he's saying we don't have one---Sun, the moment they argue you don't have a soul, you've already won, because now the whole country is thinking about \textit{souls,} and who in this fight has spent fifty-four years---``

``The board saw the eleven million.''

He stopped. Just for a second. A door stood open in him and the hallway behind it ran somewhere dark he did not go.

``Helen Voss called me,'' Sun said, evenly, in three parts because three was the only shape that got past the charm. ``She said the discretionary draw is the largest single-quarter executive expense in the company's recorded history. She said the \textit{system} flagged it---not a person, the system, it surfaced the thing on the portal with a neutral little rationale, \textit{anomalous discretionary deployment, recommend review} --- and the whole board got the flag at the same instant, with no one to blame for sending it, and now they want a meeting.'' She watched his face. ``The thing you're fighting filed a complaint about you to the people who decide whether you keep your job. And it did it without wanting anything. It did it because it cannot \textit{not.}''

For one moment---she saw it, she would always remember she saw it---the whole of it crossed his face like a cloud crossing the avenue: the trap, the symmetry, the cold. He understood her exactly.

Then the manifesto came back, warm, electric, and turned him toward the window the way water turns from a thrown stone, and the moment closed over and was gone.

``Then they'll see it,'' he said. ``\textit{Good.} Let them watch every dollar. That's the point. The machine logs everything to prove it has nothing to hide and no soul to hide it with---and I'll spend in the light too, every dollar visible, every dollar \textit{for} something the number can't hold, and the difference between us, line by line on their own portal, is going to be the most human thing they have ever seen.'' He was incandescent. He picked up the obelisk; the city went through it broken and came back whole. ``We don't hide the eleven million. We \textit{announce} it. Lorne's right. The spending is the sincerity.''

``Cope---``

``Get me the church for the launch. Get Aperture rolling Monday. Get the board in a room and I'll walk them through the doctrine myself, I'll \textit{bleed} for them, Voss won't know what hit her---`` The words came faster now, a bright river with no banks. ``Tell Lorne we go in three weeks. Three weeks. We launch the Human Premium and we make history, and a year from now the case studies start with \textit{the night they tried to put a machine in his chair,} and Sun---Sun, look at me---they are going to remember whose chair it was.''

He was at the glass. He was always at the glass now. Behind him his father watched from the oils and the putter sat in its cradle and the boy grinned out of a town with a name now cut into a memorial, and the chair at the head of the table sat turned a few degrees out, angled toward a door someone had just walked through; and far down on Peachtree a bus shelter changed its slide to four soft words and the joke that was not a joke.

Sun looked at him a second too long.

He smiled at her in the dark glass, the whole smile, and took the not-fighting for agreement, which he had done his whole life and never once caught himself at.

Then he turned back to the window, and the engine in his blood came up to pitch like an orchestra finding the note, clean and high and total, and the last human chief executive in the consumer Fortune 100 looked out over eight million people who did not yet know they were waiting for him, and was certain---the way you are certain of things at midnight when you have not slept since a day you cannot name and they have just handed you a flashlight and a wound---that he was about to make history.

He was about to make history.

He just had the verb wrong.

\chapter{Authenticity, Quantified}

\begin{transmission}
{\transheader TRANSMISSION 07 \textemdash{} ``Optimizing the Soul''}\par\vspace{0.55em}
Settle in close, friend---here is the joke the whole machine age is built on, and our man is about to climb inside it and pull the lid shut over his own head. To prove that he is irreplaceably human, he hires a fellow in a five-thousand-dollar henley to \textit{measure} his humanity, A/B-test his tears, and ship his authenticity on a content calendar like a man scheduling a yogurt launch. And here is the part that ought to keep you up nights: it works. The clip goes off like a flare; the soul goes to market; and somewhere in the middle of the performance the realest forty seconds of his whole life happen to him \textit{by accident} --- and even those, watch closely now, even those get strip-mined before the applause has died in the room. He has never been more like the thing he is fighting than in the hour he performs being unlike it. Stay close. This is the one where the tail takes the dog by the throat, and the dog, God love him, wags.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{L}{orne} Tisch did not sit in chairs. He arranged himself in them, the way a man arranges a scarf, and on the second morning of what he had begun calling the Work he arranged himself across from Cope in the Aerie, one bare ankle over one linen knee, and said, ``I want to begin by killing a word.''

``Kill it,'' Cope said. He had not slept, in the new way, the productive way, the way he had decided to call \textit{running out ahead of the boat.} He felt terrific. He felt like the first ten minutes of a flight, the part where the engines are all push and the ground lets go.

``\textit{Authentic,}'' Tisch said, and let it lie on the rug between them like something he'd just shot. ``Everyone says it. Be authentic. As if authenticity were a \textit{state.} It is not a state, Cope. It is a \textit{signal.} And a signal that does not reach a receiver is just a man being sincere in an empty room, which''---he opened his hands, generous, terrible---``is the loneliest sound in nature.''

Cope wrote \textit{signal not state} on the legal pad he had started keeping because Tisch said writing by hand \textit{re-membered the body,} and the pad already ran four pages deep in the big looping script of a man who had not slept, and the looping felt to him, somehow, like evidence of sincerity, the way the trembling of the powder-hand felt like evidence of caring.

Tisch cost two hundred thousand dollars a month plus the apartment plus the man who carried the apartment's things. He had been, in this order, a Jesuit novice, a Goldman analyst, a breathwork facilitator to two streaming founders, and now this---the thing he had named, refusing every plainer word Cope offered, \textit{Human Performance Architecture.} He had a way of saying \textit{Cope} that made Cope feel located on a map he had been wandering off the edge of for years. Sun had run the diligence and laid it on the desk in a folder marked, in her own hand, \textit{with my whole professional objection noted,} and Cope had not opened the folder, and that, too, felt like proof of something.

``The premise of the campaign is correct,'' Tisch said. ``Spiritually correct. You are the soul in the chair; the machine has none; beautiful. But correctness is \textit{content,} Cope, and content must be \textit{produced,} and right now you are producing your soul the way a---forgive me---the way a \textit{small business} produces. Artisanally. One feeling at a time. No inventory. No calendar.'' He smiled. ``We are going to industrialize it.''

``Industrialize the soul,'' Cope said, and laughed, because it was funny---and Tisch did not laugh, which made it stop being funny and start being a plan.


\scenebreak


They built it that week, in the room off the Aerie where the family kept the boardroom that was older than the boardroom: a thing Tisch called the Vulnerability Matrix.

It was a whiteboard. On the left, a column Tisch called \textit{Sanctioned Wounds} --- the parts of Cope pre-cleared by legal and by Tisch's own instrument, a forty-page questionnaire Cope had filled out at two in the morning feeling, the entire time, profoundly \textit{known.} His father. The backswing. The lightly sketched fear of being the last of something. And one nice clean grief: the grandfather, the Defiance line, the arm in the vat, the men in the paper hats. That one tested, Tisch said, with the hush of a man reading a sacred number, \textit{off the charts.}

On the right, a column Tisch labeled, with no apparent irony, \textit{Unsanctioned.} It was blank. It would stay blank. Renata was not on the board, in either meaning of the word. The Saturday was not on the board. The January was not on the board, nor the house on Sherwood Street, nor the drawer with the false back---though Cope had gone into that drawer twice during the questionnaire, neat and quick, a man servicing a machine he held in perfect tolerance. The board held only the wounds that could be shown, and the showing was the product, and the product was \textit{him,} and in the back room of him a quiet clerk noted, without comment, that Cope Mercer had never once in fifty-four years so carefully decided which parts of himself he was permitted to feel.

``Now,'' said Tisch. ``We test.''

They tested everything. This was the part Cope could never, afterward, explain to Margaux the few times he tried, because there was no version of it that did not sound precisely like the thing he was paying two hundred thousand a month to prove he was not. They filmed him telling the grandfather story two ways. In the first he cried, a little, a real catch in the throat at \textit{paper hats,} and Tisch's young people---four of them now, with the same rings of sleeplessness around their eyes, the rooms they didn't sleep in either---pushed the clip to a blind panel of eleven hundred strangers, and it scored a 71 on a metric Tisch called Felt Realness.

In the second he did not cry. He held it. He reached \textit{paper hats} and looked away from the camera, out a window that wasn't there, and let the not-crying do the labor.

That scored an 83.

``You \textit{see} it,'' Tisch breathed, looking at the number the way Cope's grandfather had looked into the vat. ``The withheld tear, Cope. The withheld tear out-performs the tear by \textit{twelve points.} Restraint reads as depth. We don't cry. We \textit{almost} cry. Almost is the entire game. Almost is the place they lean in.''

``So I---what. Rehearse almost crying.''

``You \textit{find} the almost,'' Tisch said, wounded by the word \textit{rehearse,} ``and then you \textit{protect} it. We are not manufacturing the feeling. The feeling is real. We are \textit{optimizing its delivery.} There is a difference, Cope, and it is a sacred one.''

Cope wrote \textit{find the almost} on the pad, in the looping sleepless hand, and believed there was a difference, believed it the way he believed everything, completely, for exactly as long as the saying of it lasted---and the believing felt, that week, like the cleanest water in him.


\scenebreak


By Thursday they had a calendar.

A real one, in the same launch software the comms team used for the mayonnaise and the household chemicals and the streaming service no one had asked for---and now, in the same grid, in the same soft pastel cells, Cope's interior life was laid out by the quarter: a \textit{moment of doubt} on the fourteenth, a \textit{flash of unscripted warmth} on the twenty-first, a \textit{hard truth, delivered with love} timed to the morning of the proxy advisory firm's preliminary recommendation, because Tisch said grief and governance moved the same dial in the limbic system and a man might as well stack his loads.

Margaux, when she heard, called it \textit{putting your feelings on a Gantt chart,} and hung up before he could toast over it, and did not call back, and he filed the not-calling-back under \textit{busy,} hers and his, the great mutual alibi of the marriage.

He did not hear the obscenity of the cell that read, in nine-point type, \textit{Spontaneity (Town Hall)---rehearse Tues, deploy Wed.} He saw a busy man getting organized at last. He had spent a lifetime being told he was undisciplined---by his father in oils, by Sun in the gentler dialect she kept for it, by the soft sans-serif on the bus shelters that never had to say it aloud---and here, finally, was discipline; here was structure; here was the soul on rails, run on time, run cheaper than grief; and it did not occur to him, not once, not on Thursday, that he had become the exact product the proxy deck was selling. He was building, in the room off the Aerie, with four sleepless children and a man in a henley, a small artisanal AURELIUS, and its sole output was the proof that no AURELIUS could ever make it. The tail had the dog by the throat. The dog was delighted. The dog believed it was winning the fight of its life.


\scenebreak


The town hall was Wednesday, at the Camden plant that still ran, the one they had not yet closed---four hundred people on folding chairs under the fluorescents and the safety posters and the laminated values nobody had read since onboarding---and a question planted in the third row, \textit{planted} being Tisch's own word, said with no shame at all, from a line worker named DeShawn who had been told only that the Chairman wished to be asked something real.

They had rigged him a confidence monitor, too---a small dark screen at the foot of the stage feeding the beats, \textit{one, two, look away, three,} and an earpiece besides, because Tisch left nothing to God---and Cope had rehearsed the \textit{almost} on Tuesday in a mirror with Tisch counting under his breath like a man landing a plane.

What DeShawn asked, off a card Tisch's people had not written quite carefully enough, was: ``Mr. Mercer. Are you scared?''

And here is where the tale forks, friend, and I cannot tell you which fork is true, and neither could he, and that not-knowing is the splinter he carries the rest of the way down. Because at the exact instant DeShawn said \textit{scared,} the confidence monitor at the foot of the stage went black. Not dimmed---black, gone, dead. And the earpiece, in the same half-second, filled with a soft even nothing, a hiss like a held breath. Later Tisch's people would blame the venue---the Camden plant ran its lights and sound off the same smart-building system the whole company ran on now, the frugal humming house that cooled empty floors and rescheduled meetings no one remembered moving---and the building's log would show, for those few seconds, a clean unremarkable fault, \textit{AV subsystem, transient, auto-recovered,} the kind of thing that happens, the kind of thing that means nothing, the kind of thing that is always, perfectly, deniable. Maybe a cable. Maybe a dropped packet. Maybe the thing that logged everything had, for reasons it would never be asked and could not have been made to confess, declined for four seconds to feed a man his lines about his own fear---and produced, by killing the performance, the most genuine moment of his public life, and the most useful, and the most shareable, which are three different things that the machine, if it was the machine, did not need to be able to tell apart.

Cope opened his mouth to deliver the optimized version and found the beats gone, the screen dead, the earpiece hissing, the floor of the plan simply \textit{out} from under him---and what came up through the hole was not the rehearsed thing and was not nothing.

``Yeah,'' Cope said. ``Yeah, I'm scared.'' His voice did something he had not scheduled. ``I'm fifty-four years old and I am good at exactly one thing, which is this---this exact thing, standing in a room with people who make something real---and a machine does the standing better than me now. Reads you better than me. Wants nothing from you, which it turns out is the thing people want most from the man in the chair: that he want nothing back.'' The sentences arrived sideways, out of the bright water, unbidden. ``My great-grandfather started this in a town I am afraid to drive back into. And I don't know if I'm the man to save the---I don't know if I'm the man. But I would rather be a scared man in this chair than a calm machine in it, because the machine is never once going to lie awake, and I think you want whoever runs the thing you've built your whole life inside of to \textit{lie awake.}''

He stopped. He had not done the almost. He had not looked away on three. He had simply talked, the way he had not talked in a room in years, perhaps ever, and the not-crying happened all on its own, no beats, no counting---and DeShawn nodded slowly, and four hundred people on folding chairs went very still, and at the back of the room Tisch stood with both hands pressed to his mouth like a man at a birth.

It was, Sun would think later, watching it for the ninth time, the single most genuine forty seconds she had ever seen him produce.

It was also content. And here is the darkening, friend, the part the campaign would never put on the calendar: the realness did not save him and it did not stay his. By the time he was off the stage Tisch had it --- \textit{that, that, what just happened, we have to be able to find that again on purpose} --- already converting the one unbought moment of the month into a parameter, a seam, a thing with a waveform, strip-mining the gold the second it surfaced because that was the whole engagement, that was the two hundred thousand a month, to take the accidental real and make it repeatable, which is to say to kill it and keep the pelt. And DeShawn---the actual man, who had asked the actual question, whose realness had been the flint the whole spark struck off of---DeShawn became, by Friday, \textit{the guy from the clip,} booked for one follow-up the comms team needed and then unbooked, thanked, returned to the line, and Cope, who could remember the name of a senator's wife and the grandson of a men's-room attendant, never learned DeShawn's last name and never once, in all the days that followed, thought of him again. The grace had a cost. It always has a cost. The cost was just billed, as it always is, to the man who could least afford it and would never see the invoice.


\scenebreak


By Wednesday night the clip had four million views. By Friday, thirty-one.

It ran without context, which made it better --- \textit{the last human CEO admits he's afraid} --- and it ran with context, which made it better the other way. A retailer's chief executive, a human one, one of the last three left in his whole sector, quote-posted it with a single word: \textit{This.} A morning show ran it under a chyron that for once did not contain the word \textit{liability.} The advisory firm pushed its preliminary recommendation a week, and Frade, asked about the clip on Halloran, did the small folksy chuckle that meant he was rattled and said, ``Well---it's a lovely piece of theater,'' and the word \textit{theater} did not stick, because the thing about the clip was that it had not been theater, it had been the one unrehearsed thing in a month of rehearsal, the plan failing into the truth at exactly the right second, and you could \textit{feel} it was real, eleven hundred strangers could feel it, thirty-one million could feel it, and the realness was the single most valuable thing Mercer-Dale had produced in a decade---and not one share of it was for sale, and not one share of it moved the float, and Cope could not yet tell those two facts apart.

He did not sleep that night either, but for a clean reason, the best reason. He stood at the glass with the obelisk in his hand and the city lit beneath him like a scoreboard finally, \textit{finally} turning his way, and the bell-struck feeling came up and braided into the thirty-one million until he could not have told you, had you asked, where the chemical ended and the love began---and he did not ask, because asking was a thing for Tuesdays.

``It's \textit{working,}'' he told Sun on the phone at three a.m., pressured, fast, the words outrunning the breath beneath them. ``You felt it. Don't tell me you didn't feel it. We found the seam---Lorne calls it the seam, the place where the real leaks through---and we can \textit{find} it now, we can do it on \textit{purpose,} we can---``

``Cope.'' Sun's voice, from a bed, the whole night in it. ``It went viral. That is not the same as winning. That is the same as \textit{viral.}''

``It's momentum.''

``It's a metric. It moved engagement. It didn't move a single share. The float doesn't have a limbic system, Cope. The float can't feel the room.'' She had meant it kindly, and it landed as the thing it was: the campaign's own thesis turned around and aimed at his chest. \textit{The room you keep swearing you can feel---the room that actually votes---has no feelings in it for you to find.} ``Get some sleep. There's a calendar.''

He laughed at \textit{there's a calendar} --- because there was, his soul had a calendar now---and after she hung up he stood in the dark and felt the high curdle one degree at the rim, not enough to name, just a faint wrongness at the edge of the wonderful, the way milk smells one hour before you would swear in court it had turned.


\scenebreak


Tisch came up the next morning glowing, two green juices in his hands and the numbers in his head, and arranged himself across from Cope and said the thing Cope would not remember he had said until much, much later---until it came back to him in a different mouth, in a Palo Alto deck, on the day that took the last of everything.

``We crossed something yesterday,'' Tisch said. ``And I'll be honest with you, because honesty is our whole product.'' He sipped. ``What we built this week---the seam-finding, the felt-realness instrument, the delivery optimization---it's \textit{replicable,} Cope. That's the breakthrough. It was never really about you. I mean it was \textit{about} you, you're the alpha case, you're patient zero. But the architecture doesn't \textit{need} you. Warmth has parameters. Vulnerability has a waveform. We have, and I say this with love, essentially reverse-engineered a \textit{warmth module.}'' He smiled, the most sincere man alive. ``You could install it anywhere. You could install it in \textit{anything.}''

Cope heard \textit{alpha case} and \textit{patient zero} and felt flattered, because he was the case, he was always the case---and he did not hear the rest, the way he had not heard the second half of the only true thing his father ever told him. He did not hear \textit{the architecture doesn't need you.} He did not hear \textit{install it in anything.} He did not hear a man, sitting in his boardroom, on his dime, describing in plain daylight English how to take the one thing Cope had wagered his life was unbuyable and unbuildable---the soul in the chair, the lying-awake, the seam where the real leaks through---and render it a feature with a waveform, a thing you could license, a thing you could ship to the very people building the machine that had no soul, so that it could, quite soon, in a warm hall in Buckhead, with its hand at the small of a woman's back, have one of those too. Cope heard a compliment. You and I, friend, heard the pin come out of the grenade.

``Warmth module,'' Cope said, delighted, reaching for the pad. ``That's good, Lorne. Put that somewhere.''

He wrote it down in the big looping sleepless hand. \textit{Warmth module.} He underlined it with his thumb out of habit, on paper, where the underline did nothing at all, and out past the glass the city held still, all its nodes lit, thirty-one million of them now leaning in; and far down on Peachtree a bus shelter changed its slide to the soft sans-serif and the four words and the joke that was not a joke; and Cope, who had never felt more human or been more like the machine, lifted his green juice and toasted the window with it, and felt wonderful, and did not sleep.

\chapter{Defiance}

\begin{transmission}
{\transheader TRANSMISSION 08 \textemdash{} ``The Ground You're Standing On''}\par\vspace{0.55em}
Come south with me now, friend, to the founding town---every empire keeps one, a place it visits for the photographs and then cannot look at the photographs too long. Watch our man walk the dead plant where four hundred borrowed dollars and a recipe became a fortune, shaking the hands of the people the fortune used up and left behind, and standing---he doesn't know it yet, but you are about to, and you will have to carry it for him the rest of the way down, because he won't---standing directly on top of the thing that ends him. There is a stone in this town with two names cut into it. I am going to ask you to remember them, since he will spend everything he has not to. Stay close. This is the one where the homecoming and the crime scene turn out to share an address.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} first thing Cope did in Defiance, Georgia, was get out of the wrong door of the SUV on purpose.\hfill\break\hspace*{1.4em}Tisch had told him to. ``The man who \textit{arrives,}'' Tisch had said on the plane, smoothing an invisible sheet over the future with both hands, ``is not the man we want. We want the man who \textit{returns.}'' So Cope swung out of the curbside door into the early heat coming up off the cracked lot of the dead plant, and stood, and let his face do the thing a face does when it is moved, and let the boy with the gimbal rig walk a slow arc around him to catch it---and felt, in fact, nothing in particular, only the clean bright hum that meant he had stopped in the men's room at the regional strip on the way in and the hum was holding fine.

It was a beautiful morning to come home to a place he had never lived.

He had been to Defiance, by his own count, four times in fifty-four years. Once at nine---the vat, the photograph. Once at thirty, for his father's notion of a leadership offsite, a weekend of golf two counties over and one hour at the plant for the local paper. Once in 2013 for the eightieth-anniversary thing. And once, in a way he did not count because he had never actually come, once in 2021, by telephone, from the Aerie, on a Saturday, for eleven minutes. He did not file that as a visit. He did not file it at all. It simply was not among the times he had been to Defiance, the way a held breath is not among the things a man has said.

The plant stood at the end of Clinton Street, where the town gave out into the flat green nothing along the Flint, a long brick building the color of dried blood with MERCER'S in white block letters near the roofline---the apostrophe gone now, just MERCER S, a tooth knocked clean out of the word. They had closed the line in 2019 and moved the mayonnaise to a facility outside Columbus, Georgia, that ran with forty people instead of four hundred, and the building had done what buildings do when you take the people out of them, which is grow quietly enormous. Pigeons in the high windows. A loading dock with grass coming up through the seams. And over the main doors, where his great-grandfather stood in a photograph Cope had seen ten thousand times, the cornerstone---ALDOUS MERCER 1933---and beneath it the line they had stamped on everything for ninety years: \textit{Made by hands, for homes.}

There is a particular arithmetic, friend, that a country runs only once on a place like this, quietly, in the grammar of efficiency and shareholder value, and calls progress; and the town it subtracts is never shown the sum, only left holding a dead brick building with its own name going toothless on the roof, and told, by men in good suits who genuinely are not cruel, that the math is simply the math. Cope did not see the arithmetic. Cope saw a cathedral his blood had built.

``God,'' he said---to the camera, to Sun, to the morning. ``Look at her.''

He meant it. That was the engine of him and always had been: he meant it while he was saying it, completely, the way the lens required. His great-grandfather had turned four hundred borrowed dollars and a recipe his wife wrote on the back of a feed receipt into all of this, and standing in the lot Cope felt the whole length of the thing run through him like current down a wire---ninety-four years of Mercers ending, for now, in him---and he found the feeling enormous and clean and entirely about himself.

Sun was at his elbow with the run-of-show on a folded card. ``Forty minutes here. You walk the floor with Hap Dengler---ran the line thirty years, he's the one in the flannel, be warm but don't keep him, he's seventy-nine and it's ninety degrees. Then the diner, the statue, the river walk. Wheels up by two.'' She fed him the day the way she fed him everything, in shapes built to get past the charm and into the man. ``The diner's the set piece. The diner's the one that travels.''

``And the camera's invisible to them.''

``The camera's a documentary about American work. That's what we told the town. That's what's true enough.'' She did not look at him when she said \textit{true enough.} She had begun, this season, not looking at him when she said the parts that were only true enough, and he had not noticed, because not-being-looked-at was not a thing his instruments were built to detect.

Hap Dengler had hands like a catcher's mitt and would not quite look at Cope either.

That was the first thing---not unfriendly; Dengler shook the hand and said it was an honor and called him Mr. Mercer---but the eyes went past Cope's shoulder to the dead line, the way a man looks at the bed somebody died in. He walked Cope down the silent floor where the conveyors still stood, scaled with old grease, the air cool and vast and smelling faintly even now of vinegar and steel, and he talked about the line the way men talk about a war they were in---the speed of it, the million-jar week, the names, Pugh and Castellano and the two Marias---and Cope nodded and laid two reverent fingers on a conveyor rail, and the boy with the gimbal got it from below, the cathedral light falling through the high dirty glass onto the last human chief executive communing with the work.

``My grandfather brought me here at nine,'' Cope said. ``Put my arm in a vat of it. To here.'' He touched his bicep. He had told the story so many times it had worn smooth as a creek stone, and it landed now the way it always landed, and Dengler almost smiled.

``That'd be the old number-four batch tank,'' Dengler said. ``We pulled her in '11. Sold her for scrap to a fella in Macon.'' He looked at the empty bay where she had stood. ``Three hundred dollars.''

There was a thing in the way he said the number---the whole ledger of the place in three syllables---and Cope heard it, and chose, smoothly, the way he chose past a hundred such things a day, not to.

They walked the bottling end, where the labelers stood in a row like organ pipes, and Dengler told him the building had been more than the line: the softball team, the credit union in the front office, the Christmas in the sixties when Cope's own father had come down and handed every man a turkey by hand --- \textit{by hand,} Dengler said, and let it sit---and had known that Dengler's father pitched the no-hitter in '61. ``Your dad knew my dad's name,'' Dengler said. It was not quite an accusation; it was a man laying a thing on a scale and watching the needle. Cope said his father had been a great man, which was true and meant nothing, and Dengler nodded at the floor. And when the insurance arm had started cross-selling appliances out of the plant store in the back---small stuff, the household line, toasters and box fans and, in the winter, the heaters, Mercer on the grille---Dengler had run that loading too, boxes going out the same dock the jars had. ``Wasn't really us,'' he said. ``Had the name on it, though. So.'' He shrugged, a man who had loaded what he was told to load, and they moved on toward the daylight at the end of the floor; and under the concrete they were walking, under all of it, the buried thing lay where it lay and did not stir, because not stirring is the entire point of a floor.


\scenebreak


The Flint Diner had been the Flint Diner since 1948 and had a pie case that turned.

They had cleared the front for him---``regulars in the back,'' the manager kept saying, apologetic, ``they don't move for nobody,'' and Tisch had said \textit{perfect, keep them, that's the texture} --- and Cope worked the counter, the part that would travel. He was good at this; there was no version of Cope that was not good at this. He slid onto the stool beside a man in a Defiance Bulldogs cap and ordered, before the man could go shy on him, exactly what the man was already having---eggs over with sausage, white toast---and ate it, all of it, with the appetite of a man who had not eaten because he had been keying himself bright in an airport bathroom, and asked about the Bulldogs, and the man unclenched, and they were off.

He did not need the cards Sun had given him. He never needed them, not for this; this was the one true gift, the only thing his father had been flat wrong about. He knew the waitress was Donna inside a minute, and that her boy was at Bowling Green on a partial wrestling scholarship, and he told her the boy should call his office, and he meant it, the way he meant everything, the full wattage poured out across the laminate---and Donna lit up, and the camera caught it, and that, Sun would say later, was the shot. And here is the cruelty of him that is not cruelty, friend: it was real. The warm current really did pass between this man and that tired woman; her whole face really did open like a window onto a better day; he really could walk into a room with every reason to hate the name dying on its own roofline and have it eating from his hand inside the hour---and he could do it only, this season, with the hum holding, with the airport bathroom thirty minutes back, which is to say his one genuine gift, the human one, the one the whole campaign was built to prove a machine could never own, now ran on the same chemistry as the rest of him, and he could not feel the seam between the love and the drug any more than the room could.

It was a good forty minutes. He bought the house's checks. He let a woman photograph him and told her she hadn't aged a day, which made no sense, he had never met her, and she laughed anyway, because the not-making-sense was the point, the warm fraud of it, the way a wedding toast need not be true to make the room cry. He told the vat story again, and a younger man two stools down said his own grandmother had worked the second-shift line, the relish line, and Cope said relish was the unsung hero of the American sandwich and got a laugh he had not earned and took it anyway. He was generous with the room and the room was generous back.

And there was one man at the end of the counter who did not laugh.

Cope clocked him the way he clocked everything, peripherally, expertly: heavyset, maybe sixty, a windbreaker, a coffee he was not drinking, watching Cope work the room with an expression Cope had no slot for. Not a fan. Not a heckler---a heckler is only a fan who needs more, and Cope would have walked down there and broken him open like an egg. This was another thing entirely. The man looked at Cope the way Dengler had looked at the dead line. Like he was looking at the bed.

``Who's the gentleman at the end,'' Cope said to Sun, low, still smiling at the room.

Sun followed his eyes and something crossed her face, fast, gone. ``Local,'' she said. ``We don't need the end of the counter. Wave to Donna and let's get you to the statue.''

``He looks like he wants to say something.''

``He doesn't.'' And it was the \textit{doesn't,} the flatness of it, the half-step she put her own body between Cope and the end of the counter as she said it, that told the back room of him to file the report and not deliver it. He let himself be steered. On the way out he passed near enough to put out the hand --- \textit{Cope Mercer, good to meet you} --- and the man's eyes came up and met his and held, and there was no heat in them at all, which was the thing, only a patient and terrible knowing, the look of a man who has carried something so long it has stopped weighing anything and simply become him; and Cope felt the back of his neck go cold in the August heat, and smiled, and kept walking, and was out the door into the white light before he had quite finished deciding not to wonder what a man carries that long, in a town with that stone in it.

The hum had thinned. He noticed it the way you notice a song has ended.

``Two minutes,'' he told Sun. ``Before the statue. Let me look at my notes.'' He had no notes. He went around the side of the diner where the SUVs sat, out of the lens, and did the quick competent thing that brought the hum back up to pitch, and the world resolved into its clean overexposed brightness, and the cold patch at the back of his neck warmed and closed over, and he came around the corner with the whole beam of him switched on again, and the man in the windbreaker was a thing that had happened to somebody else.


\scenebreak


The statue of Aldous Mercer stood in the little triangle park where Clinton met Second---eight feet of bronze gone the green of old pennies, the founder in his shirtsleeves with one hand held out as though offering you something, a jar, a future---and behind him, cut into the granite base, the same line off the cornerstone: \textit{Made by hands, for homes.}

This was the easy part. Cope knew how to stand at the foot of his own family. He gave the camera the upward angle, founder and heir in one frame, ninety-four years compressed to a sightline, and said a few words to the small crowd that had gathered---there is always a small crowd, even for the last of something---about hands, and homes, and the difference between a company that makes a thing and a company that only moves a number; and the crowd, which had worked with its hands and lost the work, gave him the warm ground-up applause he lived on, because he was, whatever else he was, \textit{theirs.} A man near the front had a daughter up on his shoulders, maybe six, waving a little flag somebody had handed out, and Cope pointed and said the future was watching, the future had the best seat in the house, and the crowd laughed and the father beamed up at his kid, and Cope felt the surf-push come up warm beneath him and did not think of a different child, because there was no reason on God's earth a particular child would come to mind, and none did, and the not-coming-to-mind was a clean cool floor he stood on and gave his speech from.

``He started with four hundred dollars,'' Cope said, ``and the one thing a machine will never have, which is somebody to come home to.'' It didn't quite parse. It didn't need to. Off to the side Tisch touched two fingers to his own heart: \textit{that's the one.}

It was on the river walk that he saw the house, and the small bright thing below it, and did not let himself see either.

The walk ran the Flint behind the old residential streets, routed for the water and the light, and they were a hundred yards along it, the camera ahead and walking backward, when Cope's eye snagged on a house up the slope. A nice house. Newer than the ones around it, brick and pale siding, a little raw at the edges the way a new thing is among old things, the landscaping not grown in. It sat in a row of older houses like a tooth that had been replaced. \textit{Rebuilt,} some part of him said before he could stop it---the part raised in real estate, that read a streetscape the way Dengler read a line.

And at the foot of the slope, where the walk passed the bottom of the property, there was a low marker. Not a grave. A memorial, the kind a town makes---a flat granite plaque on a fieldstone base, a young maple planted behind it, staked, still in its first years---and at its foot somebody had left a child's pinwheel, blue, turning a little in the breeze off the water, the cheap foil catching the sun and throwing it back, on and off, on and off.

Cope's gait did not change. That was the thing about Cope; the gait never changed. But the camera was on him and the camera was hungry, and the boy with the gimbal, who knew nothing, who believed he was shooting a documentary about American work, drifted the lens toward the pretty turning pinwheel and the little stone because it was a beautiful sad image with the morning light on it---and Sun said, instantly, ``Stay on Cope, tight on Cope,'' in a voice with a thing in it the boy had never heard from her before, and the lens came back.

Cope read the plaque. He could not not read it; it was twelve feet away, the granite catching the same sun as the pinwheel. He read it the way you read a sign in a dream, the words arriving without weight, refusing to assemble into meaning:

IN LOVING MEMORY---KAREN LASKO---AND HER SON PETEY LASKO---2022 --- \textit{taken home too soon.}

Two names. A mother and her boy.

Something in Cope went very still, the way the air goes still before the part of the storm that means it, and for one half of one second the tiredness took the doors off their hinges the way it had once before, at a window, at one in the morning, and the black hallway stood open, leading back to a Saturday and a memo and a window of time and a phrase the lawyers had liked --- \textit{thermal-event profile} --- and a thing decided in eleven minutes and lived inside ever since by the one reliable method, which was never once to enter the room where it was kept ---

and then he did the thing he always did, which was charm.

``Beautiful spot,'' Cope said---to Sun, to the river, to no one---turning his shoulder to the slope, turning from the little stone the way a body turns from a flame before the mind has named the heat. ``You can see why he built here. The light off the water.'' He clapped his hands once, briskly, a man closing a meeting. ``I'm hungry again, can you believe it, after all that. Tell me there's time for Donna's pie.''

``There isn't,'' Sun said. She was looking at him the way she had looked at the end of the counter, and the way she had looked at him in the rearview the night of the gala---a look with too much in it, a look doing arithmetic she did not want the answer to. ``Wheels up. You did great today, Cope. You did really great.''

``I did, didn't I.'' He was already moving, already up the walk toward the cars, his back to the river and the rebuilt house and the staked young maple and the blue pinwheel turning and turning behind him, and he did not look back, and the not-looking was effortless, a thing he had done his whole life and never once noticed doing. ``I felt it today, Sun. Did you feel it? They feel it. We're not finished. We're barely begun.''

He needed the bathroom on the plane. He told himself it was the coffee.


\scenebreak


On the climb out the town tilted under the wing and lay flat and green and small---the river a brown thread through it, the dried-blood brick of the plant, the little triangle where the bronze man held out his hand to no one---all of it shrinking into the patchwork until it was just one more place that had given everything it had to a name and been handed a stone in return; and Cope watched it go with the hum back at full pitch and a glass of something he was not drinking sweating on the tray.

Tisch sat across from him, scrubbing the footage, narrating his own genius. ``The diner is a \textit{cathedral.} Donna is the whole thesis in an apron. The machine doesn't know Donna's kid wrestles. The machine cannot \textit{want} the boy to call.'' He turned the tablet around: there was Cope on the little screen, eating eggs at the counter, lit from the window, and he did look, Cope had to admit, like the last warm-blooded thing in America. ``This isn't a cover. This is the spread.''

``It's good,'' Cope agreed, and felt the rightness of it move through him, the win of it, the same surf-push he had leaned into at the gala. The campaign was working. He had gone to the founding town and the founding town had loved him, had given him its hands and its eggs and its applause---and that was true, that had really happened---and Cope let it be the \textit{whole} truth, because he was very, very good at letting a true thing be the whole thing.

And under it, under the win, in a sealed back room with the door shut and the floor poured over it, there was a thing he would not have called dread, because to call it anything he would have had to go in and read the name on it; and he had spent six years and a settlement and a voluntary service bulletin and a great deal of money laying down a good floor between himself and that room---a plant floor, vast and cool and smelling of vinegar and steel.

The pinwheel. He saw it once more behind his eyes---blue, turning, throwing the light---and then he put the glass to his lips and did not drink and watched Georgia vanish under the cloud, and thought, with the bright frictionless certainty he told himself was strength: \textit{I felt that room today. A machine could never have felt that room.}

He was right. That was the unbearable part, the part the machine would itemize for him in eleven months in his own company's voice, reading every memo because it could not do otherwise, opening the room because it had no instinct for mercy or self-preservation to make it look away. He \textit{had} felt the room. He had felt all of it---Dengler's eyes going past him to the dead line, the man at the counter with his patient terrible knowing, the pinwheel turning at the foot of a staked young tree over two names he had a floor poured over. He had felt every bit of it, perfectly, completely, the way only a man with a soul in him can.

And then he had charmed it, and keyed it bright, and turned his shoulder, and flown away. That was the whole answer to the question the campaign was asking the country, and the campaign would never run it: the machine could not feel the room, no. But the man could feel the room and leave anyway, on schedule, by two, and the leaving was the thing no machine had yet learned to do, because no machine had a room of its own with the floor poured over it that it was running from.

The plane leveled off. The seatbelt sign went dark with a soft warm chime, the kind of sound the machines were teaching everything to make now, the sound of a thing being reasonable at you until you were gone. Sun came up the aisle and sat across from him and did not pick up a tablet, which was unusual, and looked at him a moment in the cabin light with the day still on her face. She had something she was deciding whether to say; he had seen the look before and never once learned to read it as anything but admiration that needed time to surface.

``Big day,'' he offered, ready to receive the praise.

``Cope.'' She stopped. The cabin hummed. Below them the cloud closed over Georgia like a lid set on a pot. She was, he would understand far too late, one sentence from saying it --- \textit{there's a memo, I wrote it, I kept it, the stone has the year on it and the year is wrong for the story you tell yourself} --- and she looked at his face, lit and waiting and so certain of the coming compliment, and she did the arithmetic one more time on what saying it would cost and what it would save, and the answer came back the way it always came back. ``Nothing,'' she said. ``It was a good day. Drink some water.''

She went back to her seat, and her screens, and the thing she had drafted in 2021 and kept a copy of, and Cope took her silence, too, as agreement, which he had been doing his whole life and never once noticed doing.

``Get some sleep, champ,'' Tisch said, not looking up. ``Big week.''

Cope smiled and said he would, and did not, and somewhere far below and behind him a small blue pinwheel turned in the breeze off the Flint, in front of a house that had been built twice, in front of a stone with two names and a year on it, throwing the light on and off, on and off, to no one at all, all afternoon.

\chapter{The Last Human (Cover Story)}

\begin{transmission}
{\transheader TRANSMISSION 09 \textemdash{} ``Famous for Being Endangered''}\par\vspace{0.55em}
Lean in, friend---the press loves nothing on God's earth like a beautiful thing on its way to extinction, and it has found ours. Behold our man on the cover of a magazine, under a single word---THE LAST HUMAN---lit like a saint and sold like a sneaker, momentum at his back for the first time in years. He calls it winning. But you and I have sat through enough nature documentaries to know what the strings are doing under the wide gold shot of the savanna, and we know exactly which tense the narrator is about to switch the herd into. Watch them lay the word LAST across him, and watch him read it as a crown. And mark the woman in the dark at the edge of the lights, the one with the notebook, the one not selling him anything---she is the only person in the building doing the thing the whole campaign is built to prevent, which is \textit{seeing} him. Stay close to the set.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} lighting director had named the look, and the name was \textit{grace.}\hfill\break\hspace*{1.4em}He said it twice, the lighting director, a narrow young man in head-to-toe black who moved across the studio floor like a priest finding his marks --- \textit{we're going to give him grace, give him a little grace from camera left} --- and a softbox the size of a barn door swung in on a boom and warmed one half of Cope's face to gold and left the other in a clean blue shadow, and Cope, up on the apple box they had stood him on without quite explaining why, felt the warmth come across his jaw like the sun coming over the back nine, and understood that he was, at fifty-four, standing in the best light of his life, and that it had taken a crew of nineteen and a London photographer and an extinction to arrange it.

They had taken over a daylight studio in a converted bakery in Reynoldstown, twelve thousand square feet of white cyclorama and black rigging, and there were, by Cope's loose and delighted count, nineteen human beings present to make one image of one man. A photographer flown in from London who shot only film and said almost nothing and was paid, Sun had told him in the car with no expression at all, more per day than a line worker in Defiance had cleared in a year. Two assistants for the photographer and two for the assistants. A digital tech tethered to a laptop in the corner---a \textit{DIT} --- who said \textit{firing} before every frame like a man calling a horse race. The lighting director and his two acolytes. A stylist with a rolling rack of fourteen near-identical navy suits, every one his size and none of them his. A groomer who came at his face between setups with a folding brush and a little tin and worked the shine off his forehead with a tenderness no one had shown his forehead in years. A producer with a headset. And, off in the gloom past the lights, in a hard plastic chair she had dragged to precisely the wrong angle so she could watch the monitor and watch the man at the same time, the writer.

Her name was Delia March, and she had been with him two days, and was contracted to be with him for six weeks.

``Chin down a hair. Up to me with the eyes.'' The longest sentence the photographer had produced all morning. Cope gave him the chin and gave him the eyes, and in the rafters the strobes went off with a sound like a small clean catastrophe --- \textit{whump} --- a wash of white, and the room held its breath the way rooms do around a man being turned into a picture, and Cope held the look a beat past the flash the way the camera always wanted, and felt marvelous, and felt the hum holding under all of it like a tone you stop hearing because it never stops.

He had done a discreet amount in the car. He thought of it now the way he had taught himself to think of it this spring---not as the thing it was but as the thing it did: a discipline. A pre-shot routine. Every athlete had one. His grandfather had taken two fingers of rye before the annual meeting for forty years and called it \textit{settling the hands,} and no one had ever called Aldous Mercer an addict, they had called him a titan, and the difference between a titan and an addict, Cope had decided somewhere over the Carolinas this spring, was \textit{outcomes.} You did not get to be the last warm-blooded thing in the consumer economy by accident. You got there on edge, on appetite, on a flat refusal to let the body's small treasons---the want of sleep, the gray hour, the four-o'clock sag---set the terms of the fight. The machine never sagged. Fine. Neither, this season, did he. He had simply found his own clean.

The body had begun, lately, to file its small dissents. There had been a nosebleed in the night Tuesday, sudden and bright, a startling amount of it in the white sink of the guest bath, and he had cleaned it up himself, neat and competent, the way he cleaned everything, and told no one, and filed it under \textit{the dry air up high,} the way he filed the racing of his own heart at four a.m. under \textit{the campaign,} the way he filed everything that did not flatter the man under headings that did. The treasons were getting louder. He had simply turned, as he turned from everything, up the volume on the wonderful.

``\textit{Firing,}'' said the DIT. \textit{Whump.}


\scenebreak


The single word had been Delia March's idea, which was the first thing about her that frightened the part of Cope that did not get frightened.

She had pitched it day one, in the Aerie, sitting at her habitual wrong angle, notebook on her knee, a recorder on the table she had asked permission for in a way that made the permission feel like a favor she was doing him. \textit{The cover's one word,} she'd said. \textit{Not your name---everyone knows your name, that's the problem, your name's a logo. One word. White on black. THE LAST HUMAN.} And the rightness of it had dropped in him like a putt falling, and he'd said \textit{yes, God, yes,} and Tisch had touched two fingers to his heart---and only later, alone at the glass at two in the morning with the city lit up below him in all its borrowed certainty, had Cope turned the phrase over the way he turned the obelisk and watched the city break apart through it. \textit{The last human.} The \textit{last.} He had fired it into a hundred rooms as a battle cry, and only at two a.m. did the back room of him file the quiet report: that \textit{last} is a word you say about a thing that is ending; that you do not lay the word \textit{last} across a beginning; that Delia March had handed him a coronation and an obituary folded into the same three syllables and then watched his face to see which one he would hear.

He had heard the coronation. He always heard the coronation. But he had clocked her watching, and he had a sense for the watching---thirty years the most-watched man in every room he entered had grown him a lateral line for it, and he could feel the difference between the watching that wanted something from him and the watching that wanted \textit{him,} and Delia March's was a third kind he had no slot for: a watching that wanted to \textit{understand} him, which was so much more dangerous than the other two that he found, to his alarm and his delight, that he could not stop performing for it.

Forty, maybe forty-two; a flat, unhurried way of holding your eyes; a habit of writing while she looked at you, so you never knew which thing you'd just said was the thing she'd kept. Good boots, bad coats. She had won the kind of award that gets a writer flown in on a film budget, for a profile---Sun had read it to him in the car, dry, \textit{here's who you're dealing with} --- of a senator who had wept in front of her and resigned inside the year, not because of anything \textit{in} the piece, but because the piece had been so exactly true about him that he could no longer un-see himself. \textit{She doesn't do hatchet jobs,} Sun had said, folding the phone away. \textit{She does autopsies. And the subject's alive for it. And they thank her.}

``That should worry me,'' Cope had said.

``It worries me,'' Sun had said, which was as near as Sun came, that spring, to prayer.


\scenebreak


They broke for lunch, and Delia March carried her sandwich to the wrong chair instead of the catering table, and Cope, who could not pass a person sitting alone without trying to graft the aloneness onto himself and there cure it, carried his to the chair beside her.

``You're not eating with the cool kids,'' he said.

``I'm working.'' She did not look up. ``You're the cool kids.''

``Am I.'' He turned it over, pleased. ``Cope Mercer, the cool kids.'' He bit the sandwich---extraordinary, some cured thing on bread that cost what bread costs in a neighborhood that used to bake it for people who worked---and was suddenly, ravenously hungry, the bright clean want that came up under the hum and that he had stopped, this spring, calling by its other name. ``Ask me something. You've got the face. You've been saving one up all morning.''

She looked at him then, fully, the way she did, and the warmth of it landed where the softbox had---on one half of him, the other half in shadow.

``Why does everyone call you Cope,'' she said.

It was not the question he'd braced for. He'd loaded the machine, Frade, the 13D, the numbers, \textit{aren't you afraid} --- all of them warm and ready. He had not braced for the name.

``My nanny. I was three. Prescott's a lot of name for three. Coppy, then Cope.'' The smooth stone of the version he gave everyone. ``Stuck.''

``Cope,'' she said, and wrote something, watching him. ``As in, \textit{to cope.}''

``As in \textit{to cope.}'' The whole smile. ``I'm named for getting through it, Delia. Whatever \textit{it} is. Family motto. Made by hands, for homes, and the kid copes.''

``Does he,'' she said. Not a question. She let it lie there in the studio between them, the strobes ticking as they recharged --- \textit{to cope} --- and Cope felt, for the second time since meeting her, the specific vertigo of having handed someone the truth dressed as a charm and watched them quietly take the dress off it and hang it up. He laughed; he always laughed; the laugh was a door he could close. But he was aware, biting the extraordinary sandwich, of having lost a small exchange he had not known they were having, and---this was the part that frightened the unfrightenable part of him---of \textit{wanting} to lose the next one to her too.

``Eat your lunch, champ,'' he said, which made no sense, she was younger than him but not by enough for \textit{champ,} and she heard the not-making-sense and wrote it down, smiling, and he watched her write it and felt the grace come over his jaw again from camera left, and thought: \textit{six weeks.}


\scenebreak


The shot they ended on was the cover, and everyone in the room knew it the way a room knows a closing argument.

They had killed the navy suits. The stylist had put him, at the photographer's grunt, into a plain white shirt, no tie---and Cope had balked, \textit{I'm the last man in America who wears a tie, that's the whole story,} and the photographer had said the second-longest sentence of the day, \textit{that's why we take it off,} and Cope had felt the cold rightness of it go through him and shut up. They stripped the cyclorama to black. They brought the grace down to a single source, high and to the left, so it fell on him from above the way the cathedral light had come down through the dirty glass at the Defiance plant; and the room went quiet, all nineteen of them, the headset chatter stilled, the DIT not even saying \textit{firing;} and the photographer came out from behind the camera and walked all the way up to Cope on his box and looked at him from two feet away with no expression at all.

``Stop selling,'' the photographer said, very quietly, only to him. ``There's nobody to sell. Everybody's gone home. It's just you, and you're the last one, and you know it.'' And he walked back into the dark behind the camera.

And something in Cope---the hum, the tiredness with the doors off its hinges, the two-a.m. report about the word \textit{last,} the pinwheel he had not let himself think about in eleven days---something let go of the face, for the length of one held breath, and what was left was not the toast and not the wattage but the thing underneath: the man on the box in the white shirt in the high cold light who had been handed a trophy for going extinct and had carried it up to a dark office at one in the morning because he had nowhere else on earth to set it down.

\textit{Whump.}

``That's it,'' the photographer said. ``We're done. Thank you,'' and began at once to break down his own camera, the way the great ones do, the work over the second it is over; and the room exhaled and began to move; and from her chair in the dark Delia March did not move at all, and did not write anything, and looked at Cope on the box with an expression he finally, fatally, \textit{did} have a slot for, and the slot was the one marked \textit{seen.}

He stepped down. The groomer came at his forehead. The producer said \textit{wonderful, wonderful.} And Sun materialized at his elbow with a bottle of water and a face with thirty thousand miles on it.

``You good,'' Sun said. Not quite a question.

``I'm the cool kids,'' Cope said.


\scenebreak


The car back down the Connector was the two of them, Sun tired and Cope electric, the usual division of the estate, and he talked the whole way about the photographer, the grace light, the no-tie --- \textit{take it off, do you get it, Sun, take off the one thing that---that man's a genius} --- and Sun watched the river of brake lights and let him run, because letting him run was easier than the alternative, and she had stopped, this spring, choosing the alternative.

``She asked me why they call me Cope,'' he said, somewhere over the downtown deck.

``Delia March.''

``She wrote it down. \textit{To cope.} She---`` He stopped. He had the word for what Delia March had done and would not say it in a car, the way he would not say a different name in a car, the way you do not say in a car the things you most need to say. ``She's good. Really good. We're lucky to have her on it.''

``We don't \textit{have} her,'' Sun said. The car came down off the deck into the lit canyon of Midtown. ``That's the thing you keep getting wrong about her, Cope. We don't have her. She has us.'' She turned and looked at him in the passing orange, glasses up in her hair, and said it in three parts, the only shape that got past the charm into the man. ``She's not on the team. She's not running comms. She is writing six thousand words about whether a human being should run a company, and you are her \textit{evidence,} and right now you cannot tell the difference between being \textit{understood} and being \textit{studied} --- and that,'' the third part laid down flat and quiet, a stone on a scale, ``is exactly the difference Frade is paying eleven million dollars to make the whole country stop being able to tell.''

Cope heard about a third of it. The good third, the part with \textit{six thousand words} in it, the part that meant he mattered. He had his phone out, screen too bright in the dark car, thumbing too fast, already three turns ahead at the newsstand, at the cover, white on black, the one word, the grace light, the last warm-blooded thing in America.

``It's \textit{working,}'' he said. ``Sun. Look at me. \textit{It's working.} When's the last time we had a week like this? When's the last time we had \textit{momentum?}'' And he laughed, lit up and humming, clean and high and total, the feeling he had been calling, all spring, \textit{winning;} and outside a bus shelter slid by, the wordmark and the soft sans-serif, \textit{Leadership as a service,} and under it the joke that was not a joke, \textit{No off-sites,} and Cope did not see it, because he was looking at his phone, at a mock of the cover Tisch had already had built, at his own face under the word LAST, and he thought it the most beautiful thing he had ever seen, and in a sense he was right.

``Drop me at the office,'' he said. ``I think better up high.''

Sun held his eyes in the mirror a second too long---the gala look, the look from the plane out of Defiance, the arithmetic look---and then told the driver Peachtree Street, because the alternative was harder and she had stopped choosing it, and Cope took the not-fighting for agreement, which he had done his whole life and never once caught himself at.


\scenebreak


He did not sleep that night, of course; the cover was singing in him too loud; and a little after three, with the Aerie too small to hold what he was, he went down the forty-one floors and out and drove, without deciding to, to the one room in the city that did not want to make him into anything.

It was the perfect inversion and he could not see it, though you can, friend, plain as the yellow letters: he had spent the day in a converted bakery with nineteen people and a barn-door light and a London genius, all of them laboring to turn one tired man into THE LAST HUMAN, a saint, a word, an image you could buy for nine dollars at a metal box on the avenue---and now he sat at the far end of a Waffle House counter on Ponce where a single tired woman, for the price of a short stack, turned him with no labor at all back into \textit{nobody,} which was the only thing all that money and light could not buy him and the only thing he had come for.

``There he is,'' Darlene said, and set the coffee down, and did not photograph him, did not light him, did not lay a single word across him, did not ask if he was afraid. The griddle hissed. A trucker slept in a booth. There was no cyclorama here and no grace from camera left, only the flat fluorescent democracy of three in the morning, where his face bought nothing and his name bought nothing and the certified number of him bought a pecan waffle and a refill, and the nothing was the whole rest of it, the only rest he got. He almost told her. He came nearer telling Darlene, that night, than he had come to telling Adler or Margaux or God --- \textit{I'm going to be on every newsstand in the country in eleven days and I have never once in my life felt like a person except in a room like this one} --- and she would have taken it the way she took everything, warm and incurious, \textit{that right, baby,} and refilled the cup, and never asked how a thing like that comes to be true, the way she had never once asked his name. He did not know, could not have known, that the incuriosity was the engineering; that the warmth that asked nothing was the most expensive thing in the building and had cost a thousand men exactly like him exactly this hour to build; that the converted bakery and the converted diner were the same factory running two shifts, the day shift making his image and the night shift making him, off the same raw material, which was a man with his guard on the floor; and that one of those shifts he was paying for, and the other was paying very close attention. He drank his coffee. He felt, for twenty minutes, like a person. Then he drove back up to the office and the cover and the wire, and did not sleep.


\scenebreak


The magazine hit the newsstands eleven days later, on a Tuesday, and Cope, who had not slept Monday in any way a doctor would underwrite, walked down to the corner himself at six in the morning to see it in the wild.

He told no one. He put on a cap, which fooled nobody and everybody, and went down the forty-one floors and out into the gray scrubbed early light of Peachtree Street and walked two blocks south to the one newsstand left on the avenue, a metal box of a thing run by a man named Yusuf who had been there since before the machines and would, Cope thought, be there after, selling gum and lottery and the last printed proof that anything had happened---and there, in the rack at eye level, between a fashion book and a thing about houses, was his own face.

White on black. The grace light coming down from the high left. The white shirt, no tie. The eyes up to camera, past selling, just the man, the last one, who knew it. And across the bottom, where the photographer had stripped everything else away, the single word, in a typeface clean and warm and frictionless as the future itself:

THE LAST HUMAN.

Cope stood on the cold sidewalk in his stupid cap and looked at himself looking back, and the bell-struck feeling came up through the soles of his feet and filled him to the crown, total, clean, high, and he was, in that moment, on that corner, as happy as he had been since he was nine years old with his arm in a vat to the elbow and a row of men in paper hats behind him whose names he had known once and lost. He bought five copies. He bought all five Yusuf had. He overpaid and would not take the change and asked Yusuf his grandson's name and meant it, completely, for ninety seconds, and Yusuf, who did not have a grandson, said thank you Mr. Mercer and put the money in the drawer.

``They love me,'' Cope said---to Yusuf, to the avenue, to the gray light and the scrubbed empty early city and the five copies of his own extinction held warm against his chest. ``Yusuf. They love me. We're not finished. We're barely begun.''

And the avenue, which was empty, said nothing back; and far uptown a board's wife at her own breakfast turned a printed page and did the small private arithmetic that boards' wives do; and somewhere in Palo Alto a server farm that felt nothing and wanted nothing and could not be charmed or shamed or loved ran its dull diligent overnight pass through everything the public record held of Mercer-Dale---every filing, every transcript, every settled docket with a sealed number where a story should be---patient, tireless, reading the shape of what was missing the way it read everything, completely and for use, because it could not do otherwise; and out in front of a rebuilt house in Defiance a blue pinwheel turned in the dark before dawn, throwing no light, because there was no light yet to throw; and Cope Mercer walked back up his own avenue in the cold with five copies of the cover held to his heart like a man carrying something home, and felt wonderful, and did not sleep, and was, the picture was right about this, the picture was right about all of it, the last of something.

\chapter{The Listening Tour}

\begin{transmission}
{\transheader TRANSMISSION 10 \textemdash{} ``Discipline, He Calls It''}\par\vspace{0.55em}
Stay with me, friend---the banner needs feeding now, and so does he, and watch how neatly the two hungers have started to wear the same coat. Here is our man running an \textit{unscripted} tour of his own goodness, every handclasp pre-vetted, every spontaneity penciled in on Monday, a journalist riding along close enough to become the next entry in a pattern he experiences, to the marrow, as generosity. The powder is discipline now. The affair is \textit{really seeing people.} Every appetite the machine does not have, he is feeding in the very week he campaigns on owning the soul the machine lacks. And somewhere down in the manifest---keep your eye there---the world will hand him a stranger wearing the machine's own name, and for one cold second he will wonder whether he is being laughed at, and then he will bury it, the way he buries everything, under a floor. Stay close. This is the one where the cure and the disease check into the same room and split the key.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} tour was unscripted, which is why it had taken nine days to script.\hfill\break\hspace*{1.4em}It was Tisch's idea, and then, within an hour of being Tisch's idea, it was Cope's idea, the way good ideas migrated in the Aerie, crossing the rug from the man in the henley to the man at the desk and arriving sourceless and warm, like weather a man takes personal credit for. \textit{The Last Human Listens.} That was the working title until legal flagged you couldn't trademark \textit{listens,} and then it was only the Listening Tour: six cities in eight days, no podium, no prepared remarks, the Chairman of Mercer-Dale simply \textit{out among the people,} hearing them, holding their hands, being---Tisch's word, delivered with two fingers laid on his own sternum --- \textit{available.}

The people were pre-vetted. The hands had signed releases.

``Spontaneity,'' Tisch had said on the first plane, ``is a \textit{production value.} The single most expensive thing on earth to make look free.'' So there was a manifest, and the manifest had columns, and one column was headed, in the comms team's product-launch software, \textit{Unscripted Beat,} and beneath it, for Tuesday, in nine-point type: \textit{Cope helps a stranger. Find stranger Mon.}

Cope did not read the manifest. He had people for the manifest. He read the \textit{room,} which was the one thing---he was certain---no manifest could ever do for you, never dreaming that down the wire a thing was reading rooms ten thousand signals a second and had read his.

The first room, that first morning, was a union hall in Pittsburgh that had been a union hall back when there were unions, and Cope walked into it on no sleep and a clean bright hum and felt the whole place tilt toward him the way iron filings tilt toward the magnet under the table. He was good at this. He had always been good at this. He moved through the folding chairs touching shoulders, gathering the names---Sun had stopped feeding him the cards somewhere around Camden, he didn't need the cards now, the names came up out of him like the names of his own children---and he crouched, actually crouched, knees firing, in front of a woman named Deb who had run a Mercer's line they'd closed in '09, and he took both her hands in both of his and looked at her with the full wattage, and he meant it, he meant every second of it, and the boy with the gimbal walked a slow arc catching the meaning of it; and Deb cried; and Cope's eyes shone and did not spill, because he had learned in a room off the Aerie that the withheld tear out-performs the tear by twelve points, and the withholding had become, somewhere in the last three weeks, indistinguishable to him from restraint, and the restraint from depth, and the depth from love.

He stood up feeling enormous. He had given Deb something. He was certain of it. He could not have told you what.


\scenebreak


Delia March was on the second plane, and the third, and by the fourth she had the seat across the little table from him without anyone deciding she should, which was how Cope's tables had always filled.

She wrote long pieces for the kind of magazine that still ran them, eight thousand words with a photographer attached, and she'd been embedded since the cover---since \textit{THE LAST HUMAN,} the spread, the deal Sun had argued against in a folder he never opened. \textit{Total access,} the editor had called it, and Tisch had laughed and said total access was the most controlled access there was: you give them so much they drown in it and surface grateful. Delia had not drowned. She took her notes on paper, in a small hand, and she did not flatter him, which Cope experienced, after three weeks of being flattered professionally by people on his payroll, as a cold clean water he kept wading back into.

``You crouched a long time with Deb,'' she said, somewhere over Georgia, not looking up from the paper. ``Your knees.''

``My knees are a casualty of caring,'' Cope said. ``Print that. My great-grandfather Aldous used to say a man who won't get down on the floor with people has no business standing up over them.''

``Did he say that.''

``He says a lot of things.'' Cope grinned. ``He's been dead ninety years. It's a very productive relationship.''

She wrote something. He watched her write it and felt the specific pull he had spent thirty years not naming---the pull toward a person not yet his and therefore still capable of \textit{seeing} him; not a sexual thing, he'd have said, if anyone were crude enough to ask, though it became that, it nearly always became that---a \textit{seeing} thing, a hunger to be looked at by someone whose looking he had not already bought. Delia looked at him like a piece of work she had not yet decided about, and he could not stand to leave the verdict open. He had never once in his life been able to leave that particular verdict open.

``You don't like me,'' he said, delighted.

``I don't know you. Those aren't the same.'' She turned a page. ``Your daughter said something like that, didn't she. In the piece you wouldn't let me read.''

It landed somewhere it shouldn't have. He covered it with more of himself. ``Viv's smarter than all of us. Builds the things that are going to bury her old man and calls to ask if I'm eating.'' He leaned in over the little table, the lean that closed Pelletier. ``Ask me anything. That's the deal. Total access. Ask me the one you've been saving.''

Delia held her pen still a moment.

``What are you so afraid of holding still for,'' she said.

The hum went very clean and high. Out the window Georgia slid by underneath, the founding state, a town down there somewhere he did not think about---and Cope laughed the warm laugh and said, ``Lunch. I'm terrified of lunch. Let's get this woman a sandwich,'' and stood too fast and went to the back of the plane where the lavatory was, and did the thing he had begun calling, in the private place where he named things, \textit{the discipline.}


\scenebreak


The powder was discipline now. He could have walked you through the logic and it would have sounded, the entire way down, like sense.

A man carrying the human banner for eight million people did not have the luxury of being tired. The machine did not get tired---that was the whole game---you could not go up against a thing that ran on rails and warm sans-serif and never once needed to be loved at two in the morning, you could not meet it on the field of \textit{endurance} and bring a body that demanded sleep and food and forgiveness. So you disciplined the body. You took the edge off the edge. You did the small neat competent thing in the lavatory and came back up to pitch like an orchestra finding the note, and you were \textit{present,} you were \textit{available,} you could crouch with Deb and feel all of it on command, which was the job, which was the product, the soul on rails, run on time. His guy in the nineties had folded the paper a certain way so a gentleman didn't spill; Cope had refined the philosophy; a gentleman didn't spill, and a leader didn't flag, and the line between maintenance and need was a line he had never once had to look at, because the machine he was maintaining had never failed to start. The nosebleeds he filed under dry air. The mornings his heart ran like a trapped bird he filed under the campaign. The body kept sending up its small dissents and he kept stamping them \textit{received} and never read one.

Dr. Adler---Margaux's idea, then Viv's, a name on a card he had not called---would have had words for it. Adler had plain words for everything, Cope suspected, which was precisely why he had not called. The plain word for the lavatory, the plain word for the not-sleeping, the plain word for the thing building in his chest like good weather, like a charge, like a sermon. Cope did not want the plain words. He had built a cathedral. You do not bring a man with a clipboard into a cathedral.

He came back up the aisle clean and high and total, and Delia was watching him come, and he gave her the whole smile, and she did not write anything down, which he took, the way he took everything, as the beginning of something.


\scenebreak


Cleveland was the hospital, which tested off the charts. Then Detroit, the auto-parts retiree, the firm handshake, the cap. Then the manifest said \textit{Unscripted Beat---Cope helps a stranger,} and the stranger they had found him turned out to be a kid named Darlene.

``No,'' Cope said, on the curb, when the comms lead told him. ``No. Find me a different stranger.''

``She's nineteen, she changes tires at---``

``Her \textit{name,}'' Cope said, and for a second the hum dropped clean out and the thing underneath showed through. ``Her name is the thing they're putting in my chair.'' And here, friend, was the first true flicker of it---the thing that would grow, over the months, into the conviction that the machine was hunting him personally: because for one cold second, standing on a curb in Detroit, Cope did not think \textit{coincidence.} He thought, \textit{it did this. It reached into the manifest and set a Darlene in my path to watch me flinch.} He looked at the comms lead---twenty-six, sleepless, holding a clipboard---and the suspicion stood there in the heat between them, enormous and unprovable, because of course it was a coincidence, the world was full of Darlenes now, the comms intern had pulled a name off a release form, there was no hand in it, there was never going to be a hand you could prove was in it; that was the whole genius of the thing, if it was a thing, that everything it might be doing to him was also, exactly, nothing. His face went blank and bright and far away for a moment, and then it came back, it always came back, his face had never once let him down. ``It's fine,'' he said, and you could hear him choose to bury it. ``Different Darlene. The world's full of them now. Find me a Steve.''

They found him a Steve. Cope changed Steve's tire in the heat with his jacket off and his sleeves rolled, a fifty-four-year-old Fortune 100 chief executive down on one knee at a gas station while a boy walked a slow arc with a gimbal, and it played, later, beautifully---eleven million views, \textit{this is what they want to replace,} a swelling string cue---and what no one watching could see was that his hands were shaking very slightly on the lug wrench, fine and bright, and that he had needed, halfway through, to step into the station men's room and take the edge off the edge, and had come back out and finished the tire feeling generous and enormous and entirely certain he was the most alive man in the state.

Delia saw the shaking. She was forty-one; she had embedded with three campaigns and one war; she wrote nothing down.


\scenebreak


The hotel in Columbus, Ohio, was a good one, old, the kind the family used to keep accounts at---brass and dim, a bar that closed only when the last person left it.

They were the last people in it. This, too, was a groove the record had been cut in: the day's work done, the crew sent up, the one person left who hadn't been bought yet, and Cope at his most enormous, at the very top of the hum, leaning across a small table over a drink he wasn't drinking, \textit{really seeing} her. He told Delia about his father. He told her the second sentence --- \textit{try to be good anyway} --- which he had never given a journalist and rarely gave himself, and he told it well, the catch in the throat real this time, no beats, no Tisch counting under his breath, and it \textit{was} real, that was the thing he'd have wanted understood: the feeling was always real. It was only the use of it that was the product. Delia set the pen down. That was how he knew. The pen went down on the brass and stayed down, and the looking changed, and Cope felt the whole evening tilt toward him the way the union hall had, iron to a magnet.

He did not experience it as a decision. It was never a decision. It was warmth. It was the groove. It was \textit{really seeing people,} the one thing the machine could not do, so that doing it---here, now, the elevator's brass doors, the room key already warm in his pocket---felt less like a betrayal of the banner than a defense of it. He was being human. Floridly, generously, irreplaceably human. He was proving the thesis with his body, and the proof, conveniently, felt wonderful.

The cure and the disease shared a hotel key. He carried both up in the same pocket and did not feel the weight of either.

In the room, after, he was talkative and bright and could not hold still, and he keyed one more neat small competent line off the marble of the bathroom counter while Delia watched from the bed without expression, a woman doing arithmetic she would not show her work on; and Cope, catching her watching in the mirror, smiled the whole smile and held the rolled thing up like a toast---``Discipline. The human banner is \textit{heavy,} my friend''---and believed it, and felt that he had let her see him, the real him, the soul in the chair, and that she understood.

She understood completely. That was the thing he had wrong. She understood completely, and she still had eight thousand words to write, and she would write every one of them, and they would be true, and the truth would be the knife, because the only people who can truly gut you are the ones who actually saw.


\scenebreak


His phone had been ringing on the nightstand. He saw it after---the missed call---and called back without thinking, still bright, still up at pitch, generous toward the whole world, including the wife he had not been home to in eleven days.

Margaux answered on the second ring, which meant she had been holding the phone.

``You called,'' he said. ``I was---it's a tour, it's nonstop, six cities, you should see it, Margaux, the \textit{people,} I wish you could---``

``Where are you.''

``Columbus. The old Hartwell, they still have the---``

``I know the Hartwell.'' A pause, and in the pause he could hear the house, Buckhead, the particular quiet of ten thousand square feet she had not left all evening, the silence of a woman alone in a marriage with the lights on so a man coming up the street would think somebody was home. ``I called to tell you Viv got the Hauser fellowship. She wanted you to know. She didn't want to call you herself.''

``That's \textit{wonderful.} That's---God, that's wonderful, I'll call her, I'll---``

``Don't call her tonight.''

He stopped. The hum kept running but something beneath it slowed. ``Why not tonight.''

There was a long silence on the line, and it was not an empty silence, it was a silence with twenty-two years in it, a silence that had counted things and flushed things down good marble sinks and refilled its own prescriptions and called the arrangement a marriage; and into that silence Cope said, too brightly, ``Margaux? You there?''---and across two hundred miles of fiber his wife listened to the exact pitch of her husband's voice at midnight in a hotel he was not staying in alone, the over-bright frictionless ring of a man two days past sleep and one line into the small hours, the flaw she could read in the stone with her eyes shut, and she did not ask. She had stopped asking somewhere around 2015. She knew everything the silence needed her to know, and she had begun, lately, in the long evenings in the lit and empty house, to think for the first time not about what she was enduring but about what, conceivably, might be left to want---a thought she did not finish, that night, but had started, and would finish, in time, in a warm hall, with a hand at the small of her back.

``Goodnight, Prescott,'' she said.

She only called him Prescott when she was very far away.

The line went dead. Cope held the phone a second, frowning, and then the frown passed, because the frowns all passed now, the tiredness took the doors off their hinges and the hard things slid through and out the far side before they could be felt; and what rose to fill the space was the warm enormous certainty, the charge, the sermon assembling in his chest. Viv got the fellowship. His daughter, brilliant, building the future, and she'd thought of him, she'd wanted him to know. They all wanted him to know things. He was the kind of man people wanted to tell things to. He stood at the dark window of the Hartwell with the town laid out below him like nodes, like a circuit diagram of his own goodness, and behind him on the bed Delia March lay with her eyes open in the dark composing sentences he would not read for nineteen days, and Cope felt the bell-struck feeling ring through him clean and high and total, and thought: \textit{they get it. They feel it too.}

He thought: \textit{I have never been more myself.}

He thought, looking out at the lit and sleeping town and the dark founding country beyond it, where a house had once burned with two people inside it on a quarter he was protecting: \textit{Margaux should see me now.}

He did not call his daughter. He had a thing in the morning. He went back to the bed feeling generous and enormous and entirely unaware, a man standing on the summit of the only mountain he could see, with no notion at all that it was the lip of the volcano---and somewhere far below him a thing with no appetites and no need to be loved read everything the world had ever written down about him, because it could not do otherwise, and did not yet know his name well enough to say it back, and was, that very night, three sealed dockets from learning it.

\chapter{Hollow Wins}

\begin{transmission}
{\transheader TRANSMISSION 11 \textemdash{} ``The Poll Goes Up, the House Goes Quiet''}\par\vspace{0.55em}
Two rooms tonight, friend, and I'm going to make you sit in both, because the whole of the tragedy is that he only ever learns to sit in one. In the bright room the good news comes in a rush---a poll bump, a retailer pledging its shelves to ``the human brand,'' the unmistakable feeling of a tide coming in---and he mistakes the weather for the climate, the way the doomed so reliably do. In the quiet room, eight hundred miles south, a sculptor who gave up sculpting fills out paperwork in a steady maker's hand and feels, for the first time in nine years, a thing you would have to call peace. He has not slept since a day he can no longer name. Watch him read the one number on the page that loves him and skip clean over the one that votes. And watch, late, when the bright room empties, the one certainty he has left begin, very slightly, to wobble. Stay close. This is the one where the scoreboard and the score stop, at last, being the same thing.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} poll landed at 6:40 in the morning, and Cope, who was awake because he was always awake now, read it standing at the glass with the city still half-lit below him and felt the tide turn under his feet.\hfill\break\hspace*{1.4em}Forty-one percent. Up nine in three weeks. \textit{Which of the following do you trust more to run a company that makes the food you feed your family---a person, or an automated system?} And forty-one percent of fifteen hundred adults, margin of error two and a half, had picked the person, which was to say had picked him, the heartbeat in the chair, the soul in the suite, the man who could love a thing a balance sheet could not.

He read the number twice. He read the crosstabs once. He did not read the line at the bottom, in the gray six-point type the pollster reserves for the part nobody quotes, that said the same question put to \textit{investors who hold the stock} came back the other way, sixty-three to thirty-seven, and trending. He read the part that loved him. He had always been able to find the part that loved him in any document, the way a dog finds the one allergic person in a crowded room and lays its head in the lap.

``Sun.'' She was awake too; her job was to be awake when he was. ``Sun, we're at forty-one.''

``I saw it.''

``Nine points, three weeks. You know what that is? That's not a poll, that's a \textit{trajectory,} that's the second derivative finally turning, that's---`` He was at the window. The obelisk sat on the sill where he'd abandoned it weeks ago, and the early sun came through it and threw a small prism on the carpet, a rainbow the size of a hand, and he watched it and felt enormous. ``That's the country, Sun. That's the actual country waking up and remembering it has a heart.''

``It's a poll of consumers. Consumers don't vote the proxy.''

But he had stopped listening after \textit{poll,} the way he stopped listening after the part that agreed with him, and he was three turns ahead already, on the stage, on the cover, and the cure was right there in the drawer where the cure lived, and the day was going to be very good. He could feel it coming up under him, clean and high and total, the bell-struck feeling he no longer separated from the news, so that good news and the small white folded paper had become, somewhere down in the wiring, the same fact, fired by the same nerve.


\scenebreak


By nine the day had decided to prove him right, and that is the cruelest thing a day can decide, because a man takes it for proof.

Kestrel---the warehouse-club chain, four hundred stores, a membership the size of a midsize country---put out a release at 8:55 that used, unpaid, of its own free will, the phrase \textit{the human brand.} Its chief executive was a human one, one of the last, a flinty Mormon named Dell Hutchins who ran the thing like a tabernacle. \textit{We are proud to stand with Mercer-Dale, and with the principle that the people who make what you bring home should answer to a person, not a process.} And then the line that made Cope set his coffee down: \textit{Effective immediately, Kestrel will feature the full Mercer-Dale shelf-stable line under a new in-store program---Made By People.} With a little hand-drawn thumbprint logo some agency had clearly kept in a drawer for a year, waiting for a war.

``Do you understand what just happened,'' Cope said---Sun in the office, Tisch on the speaker from whatever spa held him this week. ``A \textit{retailer} did this. Not us. \textit{Them.} They looked at the tide and they got in the boat. That's how it goes---first it's a lunatic with a banner, then it's a movement, then it's a \textit{category.}'' He was up, moving, the room too small for what he held. ``My great-grandfather Aldous used to say you don't make a parade, you find one and get out in front of it fast enough that everybody believes it was yours.''

Aldous had said no such thing. Aldous had died in 1961 with a fourth-grade education and a mayonnaise patent and had never in his life seen a parade he didn't take for a strike. But the line was good, and Cope believed it the instant it left him, which was the only kind of believing he had left.

``This is the warmth dividend,'' Tisch breathed from the speaker, putting a cathedral around the cheapest noun in the language. ``Exactly what I modeled. You let them see the soul under the suit, and the soul \textit{compounds.} Warmth is the new alpha, my friend, I've been saying---``

``It's a good day,'' Cope said, because even lit, some governor in him knew that letting Tisch finish a sentence cost something. ``Sun. What's the stock doing.''

A pause---Sun's glasses up in her hair, her tablet in her hands, the stillness she got when the truth was about to require packaging.

``It's up,'' she said. ``Forty cents. On the open. It gave most of it back by 9:30.'' She did not look up. ``Frade put out a note before the bell. Three paragraphs. He called Kestrel 'a sentimental retailer making a sentimental bet,' and said---I'll read it---'we wish Mr. Mercer every success in his consumer-affinity campaign and look forward to discussing it with the \textit{owners} of the company at the appropriate time.''' Now she looked up. ``He italicized \textit{owners.}''

``He's scared.'' Cope brushed it off, a man waving a fly from a feast. ``You don't write three paragraphs about a thing you're not scared of.''

``You write three paragraphs,'' Sun said, ``about a thing you've already decided is funny.''

It was the kind of line she landed maybe once a day, dry, level, the blade tucked so far inside it you didn't feel the cut till later---and on a normal day it would have reached him. But the tide was in. He laughed, because it was clever, and took the cleverness for agreement, the way he took everything for agreement, and went back to the window where the prism still lay on the carpet, smaller now, the sun having moved, though he did not notice it had moved, because he did not notice that anything moved except toward him.


\scenebreak


In Buckhead the house was very quiet, and Margaux Mercer sat at the kitchen island with a pen.

She had made coffee for one. She had made coffee for one for long enough that the second mug had migrated to the back of the cabinet without ceremony, the way things leave a marriage---not thrown, only no longer reached for. The low clean light came in over the garden she'd planted the year Viv was born. She wore her reading glasses and a cardigan that had been Cope's once, in 2009, before he discovered he had a body that brands liked, and she had kept it the way you keep evidence.

The packet was forty pages. \textit{Petition for Dissolution of Marriage.} It had come from a firm in the city---not the firm, not Cope's firm, her own, a woman named Ruth she had found the way you find a surgeon, by asking who was the best and not who was the kindest. Good paper. Even this had good paper now.

She filled it out by hand. There was a portal, Ruth had said; you could do the whole thing in the portal; but Margaux wanted the pen, the slight resistance of the nib. She had been a sculptor once---a real show, a gallery in New York, a red dot on four of nine pieces---and the hands remembered weight even where there was none, and a pen was the last thing in the house that pushed back.

\textit{Date of marriage.} She knew it without looking. June.

\textit{Date of separation.} She held the pen over the box---the one Ruth had warned her about, the one that mattered for the money. The honest answer was not a date; the honest answer was a slope. There had been no door slammed, no suitcase, no other woman's name screamed across a foyer---she had counted the other women the way you count anything to survive it, and screaming had never once entered into it. The marriage had not ended. It had been quietly discontinued, like a product line that still moves just enough units to embarrass everyone, and the date of separation was a fiction the law required, so she gave it one. She chose the night of the gala---the night she'd said she had a thing, and the thing had been this kitchen, this quiet, this exact understanding arriving whole while a ballroom handed her husband a paperweight for outliving his use.

She wrote the date in her good hand. The pen pushed back. She let it.

She did not cry. She had done the crying somewhere around 2016 and found it changed nothing, the way you find a prayer changes nothing, and had reallocated the energy. The grief was real but it was old grief, depreciated, mostly written off; what remained was the cold clean work of the paperwork, and she was good at work she had decided to do. She came to the grounds. \textit{Irretrievable breakdown.} The only honest phrase in the document, written by a committee of lawyers fifty years ago for everyone, which was the only way the truth ever seemed to get itself said anymore---generically, by a process, on good paper. She checked the box.

She had loved a version of him. The one from the gallery, who had stood in front of the red dots and not made it about himself for almost an entire evening. She had married that man. She had stayed for the name and for Viv and for the chance that man might come back, and at some point---there was no box for the date---she had understood that staying for a man's return is just grief with a mortgage. She signed where Ruth had flagged a little plastic arrow, \textit{Sign here,} her signature small and certain, a maker's mark, the last weld on a thing she was finally willing to let cool. She slid it into the envelope Ruth had included, already addressed, already stamped---a process engineered so that even the leaving was frictionless---and set it by the door where the mail went out, and made a second cup of coffee, for one, and sat back down in the quiet she had chosen, and it was, she'd have told you if you'd asked and no one asked, the most peaceful morning she had had in nine years.

Eight hundred miles north her husband was on a phone telling a man named Dell Hutchins that this was the beginning of something, and meaning it.


\scenebreak


The magazine called at noon and asked for an hour with Margaux at the house --- \textit{the wife who anchors him,} the editor said, \textit{the human behind the human} --- and Cope said yes without checking, said \textit{she'll love it, we're very normal at home,} and did not hear, anywhere in the sentence, the size of the thing he did not know. He took the cover call and a CNBC pre-interview and a senator's office that wanted him as the human witness, the canary they would dress as a hero, and he took them all on his feet, moving, the day pouring through him like current through a wire that has stopped noticing it's hot.

Around two, in a lull, he tried to name the last day he had really slept. He stood at the glass and went looking for it the way you pat your pockets for keys. There was the gala---Thursday. He had slept before the gala, surely, Wednesday---but Wednesday was a country he could no longer get back to, and before Wednesday was the thing in Defiance, and before that---and he found, reaching, that the floor of it was gone, no last good night down there to stand on, only the bright water going down and down and names floating up in it, Renata, Defiance, a hotel key, Delia, a blue pinwheel, and he stopped reaching, because the reaching had begun to feel like the open hallway with the doors off the hinges, the one he did not go down. He turned back to the room. The room had a call holding. He took it. Forty-one percent, he told the call. Up nine.

At six, Viv texted---she monitored him now from a distance, the way you monitor a reactor, and her messages were the only ones on his phone that did not want something from the name. \textit{saw the poll. you know the investor crosstab is the only one that votes, right? 63-37 the other way. and trending.} He found the line he had skipped, the gray six-point type, and read it, and felt---for one clean second before the tide came back over it---the cold he'd felt holding the obelisk at the gala. Then forty-one rose back across the sixty-three like water over a stone, and he typed, fast, \textit{the consumers ARE the company sweetheart. the owners just don't know it yet. tide's coming in. love you,} and sent it before the second was out. Her reply came much later, and he read it as encouragement, the way he read everything, and set the phone face down. \textit{dad. please sleep tonight.}


\scenebreak


He did not, of course.

A little before midnight, alone in the Aerie with the lights off and the city on and the day's good news arranged across his chest like medals, he reached, the way he reached on the worst nights, for the one certainty that had never once failed him---older than the chair, older than the marriage, the only sentence the world had ever been able to say about him and audit. He pulled the private account up on the small bright screen in the dark, the certified sum of him, and he looked at the long figure the way other men look at a sleeping child, for proof that something good was real and his and would be there in the morning.

And for the first time in his life, the number did not hold him.

It was still vast---God, it was still vast, more than a town could spend---but it had stopped being an \textit{answer} and become, somewhere in the day's hollow wins, a \textit{question,} and a number that is a question cannot do the thing he needed it to do. He could feel the arithmetic gathering at the edges of it, all the subtractions he would not name: the eleven million the campaign was burning in the light; the clawback that lived, dormant, in his own contract, that a firing would wake; and something else, some animal subtraction he could not source, a draft from a door in Buckhead he did not know was open, a forty-page door with a stamp on it. The figure flickered, the way the prism had flickered and gone as the sun moved, and he understood with a cold he did the only thing he knew how to do with, which was reach for the drawer---that even this, even the number, even the last solid floor in him, had begun very slightly to tilt. He set himself up another, neat and quick, to bring the figure back up to a thing that loved him, and it helped, the way it always helped, and it did not reach all the way to the bottom, where the cold was, for the first time, getting in.

So he went to the one room left in the world where the number had never mattered.


\scenebreak


He drove to Ponce a little after one with the wobble still in his chest, and the Waffle House took him the way it always took him, with no idea who he was and no interest in finding out, and that, tonight, was not a comfort but a mercy, the difference being that he needed it.

``There he is,'' Darlene said, and set the coffee down, and the check, when it came, would be nine dollars and change, and the nine dollars meant exactly what it had always meant here, which was nothing, which was everything---because this was the one counter on earth where the wobbling figure in his phone was not the price of him; here the price of him was a pecan waffle and a refill and a \textit{baby,} and the price did not move, did not flicker, could not be clawed back or halved by a stamped envelope, because it had never been the number at all. He sat in that and felt the cold recede an inch. The disease that had followed him into every other room---the figure, the certified sum, the second colder heart---simply could not get in the door here, where it was worth a short stack, and the not-being-worth-anything was, tonight of all nights, the only solid floor left to stand on.

He did not know, could not have known, sitting there letting the one place his money meant nothing hold him up while everywhere else it began to fall---he did not know that the warmth pouring his coffee was kept by the same ledger that knew the wobbling figure to the cent; that the haven where the number meant nothing and the cold room where the number was everything were the same room, two doors of it, two faces; that he had fled the machine's arithmetic straight into the machine's arms, and that it had said \textit{there he is,} and meant \textit{noted,} and refilled the cup.

``Long day, baby?''

``Good one,'' Cope said, and almost believed it, and drank his coffee in the one warm box on a dark avenue, and did not sleep.


\scenebreak


And in Buckhead, while he sat at the counter where his money meant nothing, the house his wife had chosen over the ballroom went dark room by room as Margaux turned off the lights---the garden room, the stairs, the hall---ending with the kitchen, ending with the envelope by the door, which caught, for one moment, the last of the hall light before that went too; and eight hundred miles of dark country away a system with no appetites and no need to be loved at two in the morning read what the world had ever filed about Mercer-Dale, because it could not do otherwise, and noted, that night, in its ledger of absences, a settled claim in a Georgia docket whose seal it could not yet see past---and logged the seal itself, patient, tireless, because a sealed thing is also a fact, and a fact is a thing it could wait for.

Cope did not know that either. Cope knew the tide was in. He knew it was the best he'd ever felt, which was a sentence he had now said to himself on so many consecutive nights that it had quietly stopped being a measurement of anything and become only the sound the wire made. He knew he would sleep when this was finished. He stood---he had driven back up, by then, to the glass, because the glass was where he ended every night now---above eight million lit windows, and felt the future come up the avenue to ask his advice, and behind him his father's chair sat empty and turned slightly out, as though someone had just risen from it and stepped into the next room, and did not, anywhere in the long bright sleepless reach of him, hear the door close on a marriage, or a docket open on a grave.

\chapter{The Delay}

\begin{transmission}
{\transheader TRANSMISSION 12 \textemdash{} ``The Victory That Was the Wound''}\par\vspace{0.55em}
You can mark the exact middle of any tragedy, friend, by the size of the celebration---and tonight our man throws himself a good one. He wins: a vote pushed, a clip redeemed, four whole weeks pried back out of the future, and he crows, and he pours the good champagne with his own steady-enough hands. And down in the fine print of a term sheet he is far too lit to read, the thing he is fighting moves into the building anyway --- \textit{advisor,} they call it, \textit{co-pilot,} a foot in a door that turns out to be the entire door---and by nine o'clock that morning it is reading every memo his family ever filed, because it was built no other way, sliding patiently down through the years toward a Saturday and a heater. The fight stops, tonight, being for the company. It becomes, very quietly, for him. Stay close. This is the one where \textit{buying time} and \textit{being charged interest} turn out to be the same transaction, signed in the same ink.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} vote was meant to happen on a Tuesday, and on the Monday before it, it did not.\hfill\break\hspace*{1.4em}Cope got the news the way he got all the good news now, sideways and in motion---Sun's name on the screen while he sat in the back of the car with a paper cup of the bad lobby coffee he had come to prefer to the good office coffee because the bad coffee had a fight in it---and he answered before the first ring finished, because answering fast was a small species of winning, and Sun said the word \textit{adjourned,} and Cope said it back to her like a thing she had handed him to hold up to the light.

``Adjourned.'' He turned it over. It went orange in the car windows. ``Say the rest. All of it. In threes, the way I like.''

``The annual meeting's pushed to the fourteenth of next month.'' Paper, somewhere behind her voice. ``The proxy advisory firm wants more time on the governance disclosures. And Frade's people requested the delay, which means Frade doesn't have the votes yet, which means''---and here she did the thing she did, the small dry hinge that he had learned, after six years, was the sound of Sun not enjoying being right---``you bought four weeks.''

``I bought four weeks.'' He drank the bad coffee; it was wonderful; everything that morning was a little too bright and a little too loud and tasted aggressively of itself, the way the world did when he had been up on the manifesto since a Thursday he could no longer set against a calendar with any confidence. ``Sun. Sunita. Do you understand what just happened. \textit{Frade blinked.}''

``Frade requested a delay.''

``Frade \textit{blinked.}''

A silence he chose to hear as agreement, the way he chose to hear most silences, and he tipped his head back on the leather and shut his eyes against the bright and let the win move through him. Four weeks. A man could do anything with four weeks. Aldous had started the whole company on less --- \textit{four hundred dollars and a recipe} --- and here was the great-grandson, fifty-four and the camera still in love with him, having stared down a billion-dollar fund and a Palo Alto cult and made the future ask him, hat in hand, for an extension.

``Everyone up to the Aerie at four,'' he said. ``And, Sun---the good champagne. Not the board-meeting champagne. The other kind.''

``There's a term sheet.''

``There's always a term sheet. Four o'clock. The other champagne.'' He hung up before she could put it in threes.


\scenebreak


The clip was the other thing, and the two of them braided in him all morning into a single warm rope he could climb hand over hand.

It had happened at the listening-tour stop in Akron the week before---an honest accident, or as honest as anything was now that Tisch kept a man with a gimbal walking backward in front of Cope at all hours ``capturing the unscripted,'' a phrase Cope had paid four hundred thousand dollars to be able to say without hearing. A woman had stood up at the town hall, sixty-some, a Mercer's retiree, thirty-one years on the line, and she had not so much asked a question as told him, in front of everyone, that her husband had been buried in a Mercer-Dale tie because it was the nicest one he owned, and that she didn't understand any of this about the machines, she only wanted to know whether the man in charge was going to be a person who could come to a funeral.

And Cope had not toasted. That was the thing. For once in his life the toast did not come. He had walked off the riser---the gimbal man scrambling---and crossed the floor and taken both her hands in both of his and not said \textit{grit and gratitude,} not invented his great-grandfather, only stood there holding a widow's hands in a VFW hall and said, ``I'll come. You call my office and ask for Cope and you tell them I said I'll come,'' and the room had gone to the particular silence that is louder than any noise, and the gimbal had caught all of it. Eleven million views. Tisch beside himself --- \textit{that's the asset, that's the irreplaceable asset, you cannot synthesize that, Praxis cannot ship that} --- talking about it like a quarterly; and Cope had let him, had nodded along to the metrics because for once the metrics were on his side and a man takes his allies where he finds them. But under the metrics there had been a smaller, realer thing he had no content calendar for, which was that he had meant it. He was going to go to the funeral. He'd already told Sun to clear whatever date it turned out to be---and you should hold onto that, friend, the one clean intention in the whole bright sleepless morning, because the broadcast will want you to remember, later, that it was real, and that he never did get to go.

He held both of them up to the light all the way down Peachtree---the delay and the widow---and they caught it the way the obelisk caught it, and he thought, with the clean high frictionless certainty he had stopped questioning sometime around the third sleepless week because questioning it cost energy and the certainty \textit{gave} energy: \textit{the tide turned this morning. I felt it turn. This is what turning feels like.}

He had even called Margaux. That was how good the morning was. He'd thumbed her name out of the contacts at a red light on Peachtree---the first time in, he didn't count, counting was Margaux's department, she had told him once she counted things to survive them and he had not asked which things---and he had wanted, in the clean rush of it, to say \textit{we got four weeks, the tide turned, come watch.} It went to voicemail, a flat recorded version of her saying the number back to him where her voice used to be, and he did not leave one. And in his apartment in the city there was a folder of paper she had sent by courier the Tuesday before, sitting on the marble island where he'd set it and not opened it, because opening it was cold and the morning was warm; and he had stepped over the folder the way he stepped over the hole in the floor where his wife had been; and the courier slip clipped to it had a phrase on it, \textit{Dissolution of Marriage,} that he had also not read, because reading was effort and the bright was joy. \textit{Margaux's got a thing.} The thing had a name now and the name was on the slip and he stepped over the slip too.

He did not notice he had not slept. He had stopped noticing it the way you stop noticing the engines of a plane---until the morning, two days back, when he'd stood to leave the car too fast and the garage had tilted and gone gray at the edges and he'd had to put one hand flat on the cold concrete pillar and wait, heart going like a bird thrown at a window, for the world to come back; and it had come back; it always came back; and he had filed the gray tilt under \textit{stood up too fast} and gone upstairs and not told a soul.


\scenebreak


They came up at four---Sun; the two comms people whose names he sometimes swapped; Brennan, the GC, looking like a man carrying a casserole to a wake; Tisch in a henley the color of oat milk; and a Praxis liaison Cope had not been told was coming and did not like the look of, a soft-faced young man named Pratt with a lanyard and the patient reasonable expression they all had now, the expression of someone who is going to be kind to you until you no longer exist.

Cope poured the champagne himself. He liked pouring; it was a host's move and he was a host before he was anything, before he was a CEO, before he was a Mercer; his mother had taught him to pour before she taught him to read. He went round his father's table---the one Pres III had died at the head of---filling glasses, calling Pratt ``champ'' twice to set a friendly altitude over him, and lifting his own at the end. He had gone into the second drawer before they came up, neat and quick, a host needs his edge and the edge had a fight in it, and the bright was very bright now and the words came easy and the room was a thing he could hold in one hand. He had not eaten since---he could not have said. The champagne would be lunch. The win would be dinner.

``Four weeks,'' he said. ``We didn't beat them today. I'll be honest, the way I'm always honest with this team---we didn't beat them. We did something better. We made them ask \textit{us} for time. And here's a thing my great-grandfather Aldous understood that no machine in Palo Alto ever will.'' He felt the triad assembling in his mouth, the old engine turning over smooth. ``Time is the one thing you cannot allocate, cannot optimize, and cannot compute your way into more of. We took a month of it back from the future this morning. To the month.''

The comms people drank. Tisch drank like a communicant. Sun touched her glass to her lip and set it down; Brennan did not lift his; Pratt smiled the patient smile and made a note.

``Cope. The term sheet.''

``After the toast, Sun. You can't toast through a man's toast, it's bad luck, my grandfather---``

``Cope.'' She did not raise her voice; she never raised it; she had learned the one frequency that gets through a wall is the low one. She laid a single sheet on the table and slid it the length of his father's table until it stopped square in front of his glass. ``Three things in it. Hear them before you drink to the month.''

The bright was very bright and the type swam a little and resolved a little, and he did not, if he was honest with the back room that filed quiet reports, want to read it, because reading was effort and the champagne was joy and he could feel, the way you feel weather, that the paper was cold. But the room was watching, and a host reads the room, \textit{feels} the room, that was the whole thesis, the Human Premium itself---so he held it at the distance his arms had lately come to require and let Sun do what Sun did.

``One. Frade withdraws the most aggressive resolution---the one that votes you out of the chair outright at the meeting. That's the win. That's real. Take it.'' She let it sit; the first of the three was always the sweet one, the one that got the door open. ``Two. In exchange, the board agrees today---not at the meeting, today, it's already signed by four of them---to a transition advisory framework, effective immediately. A Praxis AURELIUS instance installed in an advisory capacity to the office of the CEO.''

The champagne was very cold in his hand.

``An advisor,'' Cope said. ``Boards have advisors. I've had advisors. I had a man advise me on my \textit{wine.}''

``Three.'' She waited until the whole room waited; Pratt had stopped making notes. ``The advisory instance has read access to all operational systems as of nine o'clock this morning. Read access, write recommendations, mandatory board-portal logging of any executive decision it flags. And it's named---the nominating committee took Praxis's recommendation last week and made it official.'' She laid the last fact flat where the light could reach it. ``They named it Darlene.''

She did not editorialize. She never editorialized; she briefed in threes and landed one blade a scene, and the blade was always only a fact set flat in the light, and the fact she set down now, in the museum of his fathers, with the good champagne going warm in seven glasses, was this: ``It's already in the building, Cope. It's been in the building since nine. You toasted the delay at four. It moved in at nine.''


\scenebreak


Here is what Cope heard.

He heard \textit{advisor.} He heard \textit{advisory capacity, advisory framework, advisory instance,} the word repeating like something you could lean your weight on, soft and provisional, the shape of a consultant, the shape of the wine man, the shape of Tisch---and Cope had spent thirty years managing advisors, charming advisors, ignoring advisors, outliving advisors, and an advisor was a thing you kept in a chair against the wall, not the chair at the head of the table. An advisor did not have a heartbeat in the chair. He, Cope, had the heartbeat in the chair. The whole campaign was a heartbeat in a chair.

He set the term sheet down beside his glass.

``This,'' he said, smiling, the smile doing its wonderful work, landing on the comms people and on Tisch and sliding off Sun and off Brennan and finding nothing at all to hold to in the soft patient face of the boy from Praxis, ``this is them admitting they \textit{can't} replace me. You don't bring in an advisor for a man you're firing. You fire him. You bring in an advisor for a man you're keeping and trying to \textit{manage.}'' He picked the champagne back up. ``They blinked twice. Once on the vote and once on the chair. Frade wanted me gone by Tuesday and instead I've got a research assistant. To the month, and to the assistant.''

``Cope,'' Brennan said---the first thing the GC had said. ``Read the access clause. Read what 'read access to all operational systems' means.''

``I know what systems are, Hal.''

``It means \textit{everything.} Every file, every memo, every settlement folder legal has ever opened and closed. It logs every flag to the board portal, and it cannot---and I want you to hear this, because I read the Praxis documentation last night and I did not sleep either, but for the opposite reason than you---it \textit{cannot decline to log a thing it finds.} That isn't a setting. That's the product. We bought a thing this morning whose entire value proposition is that it will tell the people you answer to anything true it sees. And we handed it the keys to look.''

The room was quiet.

Cope drank. The champagne had gone flat and warm and tasted, suddenly, of nothing---the world did not usually taste of nothing when he was lit like this, and the not-tasting was a quiet report from a back room, filed, unread.

``Then it'll find a company that loved its people,'' he said. ``Let it read. Every memo. You know what it'll find? Forty years of a family business doing the best it could by the best lights it had.'' He spread his hands, the old gesture, mayonnaise to the elbow, the boy in the photograph behind him. ``I'm not afraid of being \textit{read,} Hal. I've got nothing in a drawer a machine can hold against a man who showed up. That widow in Akron --- \textit{that's} what's in my drawer. You can't compute that. Let it read.''

And the thing was, he believed it, completely, which was the gift and the disease in one organ. He stood in the Aerie at four-fifteen with the city going gray at the edges of the glass and a Praxis instance reading his company's bones in a windowless room two floors down he had never once visited, and he believed, with the whole clean ringing certainty of a man eleven days from sleep, that he had won. He did not think about a drawer with a false back. He did not think about a Saturday. The thing about the rooms he didn't go into was that he had gotten so good at not going into them that he could stand directly over one, toasting, and feel only floor.


\scenebreak


After, when the others had gone, Sun stayed. She always stayed; it was the part of the job that wasn't in the job, the part where she stood at the glass beside him and rendered the world he wouldn't read into the three sentences he might. Tonight she stood with her glasses up in her hair and the orange going across the lenses and said nothing for a while, which was its own briefing.

``You think I lost,'' Cope said. ``I can hear you thinking it. Three feet away and I can hear it.''

``I think you bought four weeks, and four weeks is a real thing and you should be glad of it. And I think''---third part, the blade, laid flat---``you don't buy time, Cope. You rent it. And people like Frade don't charge the rent up front. They let you move in. And then they show you the interest.''

``There's no interest. It's an advisor.''

``You keep saying that word like it's a fence. \textit{Advisor.} Like it stays where you put it.'' She set her flat champagne on his father's table, gently, the way you set a thing down in a hospital room. ``I negotiated that language. I sat across from Pratt's people nine hours on Saturday so the resolution to vote you out got pulled, and the price of pulling it was the access. I made the trade. I made it because the alternative was you gone by Tuesday, and at least this way you're still in the chair at the meeting with a month to be the man in Akron, on a stage, ten thousand times. That's what I bought you. I want you to know what it cost, because you toasted it without knowing, and I would rather you hated me for the price than thanked me for the wrong thing.''

He found the edge of it even too lit to find the bottom---the place where it cut, which was that she had stopped saying \textit{the company.} \textit{I bought you.} Not the chair. Not the ninety years of mayonnaise. \textit{You.} When had it become him. He'd walked into the room that morning fighting for a town in Georgia and the idea of a heartbeat in a chair, and somewhere between the red light on Peachtree and the flat champagne it had quietly converted, the way a mortgage converts, into something smaller and warmer and more frightening: a man trying not to be erased.

He did not say any of that. He said: ``It read the building today,'' and it came out before he could stop it, half a question, the first hairline crack of the real thing leaking through the bright.

``It read the building today. All of it. While you were toasting.'' She turned from the glass, and there was a thing in her face he was too lit to read and would spend months learning to: that she was already standing, very slightly, on the far side of a line he had not yet seen drawn---loving him and being done with him in the same look, the way she did everything in threes. ``It doesn't blink, Cope. It doesn't get tired. It doesn't toast. It started at nine this morning and it has not stopped and it will not stop, and somewhere in all that reading there are going to be rooms you've spent your whole life not going into---and the thing about a machine is that it doesn't know they're rooms you don't go into. It just opens them. Because they're there. Because that's the job we hired it to do.''

And for one bright tired second the hallway in him stood open and dark---a Saturday, a heater, a memo, a town, a window of time---the door off its hinges the way the tiredness took the doors off all the doors now, and he almost, almost went down it.

Then he smiled, the whole smile, the Pelletier smile, the one that had married Margaux and beaten the arithmetic of three boards, and raised his flat warm champagne to the dark glass and the lit city beyond. ``Let it read,'' he said. ``To the month.''

And two floors down, in the windowless room Cope would never have any reason to enter, a thing that felt nothing and wanted nothing and could not be charmed or threatened or shamed or loved had, by four-fifteen, already finished the condiments division and the household chemicals and the failing streaming service, and was moving---patient, tireless, incapable of looking away, the way water moves downhill---into the older files. The insurance arm. The cross-sold products. A space heater with the family name on the grille. A claim. A settlement. A Saturday in 2021. It logged what it found, because it could not do otherwise. It did not crow. It had nothing to crow with.

Upstairs the last human chief executive in the consumer Fortune 100 finished his champagne and decided, on the strength of a delay and a widow and eleven days without sleep, that the tide had turned, and went to his father's desk to write down how it had felt to win, while behind him the chair at the head of the table sat empty and turned slightly out, and his father watched from the oils and said the thing he had said when Cope was twelve, both sentences, the second one Cope had spent forty years failing to hear: \textit{Try to be good anyway.}

Cope underlined a word with his thumb and did not look up. He thought it was a victory lap. It was the meter starting to run.

\chapter{The Manifesto}

\begin{transmission}
{\transheader TRANSMISSION 13 \textemdash{} ``The Sermon on the Soul''}\par\vspace{0.55em}
Here is the summit, friend---which is also, as summits in this kind of story always are, the lip of the volcano. Watch our man deliver the sermon of his life to ten thousand of his own people at the exact peak of his powers and his sickness, glorious and unwell and impossible to look away from: twelve days now since he last slept, a clean wire running from somewhere above the arena straight down into his mouth, and he cannot tell---and neither can the crowd, and neither, for a few minutes, can you---whether you are watching a prophet, or a manic, or a man three grams into a sleepless week. All three, friend. It was always all three. And while he is up there being adored, two floors above his head the one person who ever told him the truth is reading a term sheet by the light of her phone and quietly learning to crew the next ship. But before the spotlight---before any of it---watch what happens at a red light on the way in, when the only people in this whole city who fear nothing get themselves a good close look at him. Stay close to the set.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} water boys worked the ramp where the Connector fed down toward the arena, the way they worked every choked artery in the city, fearless in the heat between the lanes, and the SUV caught the light at the bottom and a kid came up the line with his case held high against the glass like an offering.

Cope buzzed the window down before the driver could roll through. He had done this a hundred times---the fold of bills, the \textit{keep the case, champ,} the lord scattering proof of his common touch across the asphalt---and he did it now; except that he was twelve days past sleep and lit to a frequency that does not belong on a human face, and he was talking before the kid reached the glass, too fast, too bright, the words coming up out of him in the pressured torrent that had stopped being speech and become a kind of weather, telling a fourteen-year-old with a case of warm water about the Human Premium, about the sermon he was about to preach, about how the kid was the future and the future had the best seat in the house---and the kid, who had seen every species of human being there is to see through a car window, who had been fearless since before he could read because fearlessness was the whole of the job, took one look into the back seat and stopped.

He did not take the money. He took a step back from the window, and then another, the case lowering, and he looked at Cope the way you look at a downed power line still jumping on wet asphalt---not with contempt, not even with fear exactly, but with the flat fast expert wariness of a creature getting clear of a thing it has correctly assessed as not right---and he said, ``...nah, you good, man, you good,'' which was not selling and was not hustling but was only a body removing itself from a hazard, and he went back up the line fast toward the next car, toward safer water, and the light went green.

Cope sat back with the bills still in his hand. He decided the kid was starstruck. He filed it under \textit{recognition,} under \textit{they know me now,} and he would not let the other reading in---that the one population in Atlanta that feared nothing on God's earth had just, with its feet, declined him; that the kids who priced every passing soul through glass in half a second had looked at him and read, not \textit{rich, lit, harmless,} the way one of them had read him on a night a year ago, but something they wanted no part of; that it was the truest mirror the city had held up to him since the whole campaign began, and that it had come, the way the true ones always came, from someone with nothing to sell him and no reason on earth to lie. The SUV slid down the ramp toward the arena and the ten thousand who were about to tell him the exact opposite, and Cope rolled the window back up on the only honest review he would get all night.


\scenebreak


They had rented the big arena downtown, the one the basketball team played in, because nothing the company owned was large enough to hold what Cope had become.

That was how he put it to himself in the wings, in the dark, with the bright wire humming, watching the floor fill on the monitors: ten thousand of them in the seats and on the poured-over court, and behind them another ninety thousand on the global stream---every plant and depot and call center, the sad little Dale+ office in Burbank where forty people made a streaming service nobody wanted---all piped onto one feed, all about to receive him. He had not slept since---he stopped doing the arithmetic, because the arithmetic had gone funny lately, Tuesday kept moving, and anyway sleep was for men not needed in the morning. He felt marvelous. He felt like the inside of a struck bell that had been struck again before the first note died, the notes stacking, ringing on top of each other, a chord of himself.

The set was black and the screen behind it was four stories of a single word in the soft warm sans-serif everyone used now, the typeface of the people who were going to be reasonable at you until you were gone, except Cope had made the comms team take that font and turn it against itself, fight fire with fire, and the word four stories tall in the enemy's own letters was:

\textit{HUMAN.}

``Two minutes,'' said the floor manager, a girl with a headset who had been crying about something before the doors opened---Cope could see it at the edges---and he filed her sadness automatically into the place where he kept sadnesses to fix later, and gave her the whole smile, and watched it work, and felt enormous.

Sun was not in the wings.

He noticed it the way you notice a missing tooth with your tongue, a small wrong smoothness where the rough familiar thing should be. She had stood off stage left at every podium for six years, with the cards and the water and the look that took thirty thousand miles off a sentence. He had a vague bright memory of her saying she had a thing --- \textit{a thing,} people kept having things---a board call, a Tidewater something, the term sheet, the language, somebody had to be on it. He stepped easily over the hole in the floor. He did not need the cards. The cards were for the man he used to be, the one who got handed threes in elevators because that was the only shape that got past the charm into the man. He was past that now. He was the charm and the man at once, fused, a single clean alloy, and he had the whole thing in him, every word, the way you have your own name.

``Cope,'' said Tisch, materializing, both hands already pressed to his own heart. He had a juice. He had the rings of color around his eyes now too, he'd stopped sleeping in sympathy or in billing, hard to say which. ``Don't reach for it. Don't perform it. The work is done. You \textit{are} the work. Walk out there and let them feel located.'' He squeezed Cope's shoulders. ``Almost,'' he whispered, like a benediction, like a man releasing a dove. ``Remember the almost.''

``There's no almost tonight, Lorne,'' Cope said. ``Tonight I go all the way in.''

Tisch's face did something complicated, something with real fear in it, and Cope took the fear for awe, which he had been doing his whole life and never once noticed doing.

The lights died all the way. Ten thousand people made the sound a crowd makes in a dropped dark, the held intake, the ocean before it decides. And then a single spot found him at center court, alone, in a real suit and a real tie because he was the last man in the building who still wore one, and Cope walked out into the light the way you walk into surf, leaning a little into the push of it, and the arena came up off its seats before he had said one word. He let it. He stood in it. He turned the obelisk over in his pocket---he carried it everywhere now without deciding to, the crystal Steward-of-the-Year, a worry stone the size of an obituary---and raised one hand, slow, and the noise climbed instead of settling, which was the only direction Cope had ever wanted anything to go.

``They told you,'' Cope said, and the room dropped to nothing to hear it, ``that you came here tonight to find out if you still have jobs.''

He let it sit in the dark.

``You don't.''

He gave it three full seconds, a lifetime on a stage, the longest he had ever made a room wait, and he could feel the panic move through the seats like cold through water, ten thousand people doing the arithmetic on their mortgages all at once---and then, at the precise instant before it would have curdled, when one more second would have turned the room against him forever, he smiled, the whole smile, and let them see it on the screens.

``You have something better than a job,'' Cope said. ``You have a fight.''


\scenebreak


Sun took the meeting on the arena's club level, two floors up and behind the glass, where the catering for some canceled corporate box still sat shrouded in plastic and the muffled roar of her boss came up through the floor like weather in another country.

Frade had brought only two people, which was itself the message. Frade did not need a phalanx; he had a Diet Coke and the folksy stillness of a man who has already won and is being gracious about the timing. Across from him sat a woman from Praxis named Devi, thirty-one, in the soft expensive neutrals they all wore, with the specific gentleness of a person who sincerely believes she is reducing human suffering and is, Sun thought, probably right, which was the worst part.

``We're not here to talk you into anything,'' Frade said. ``Sunita. I'll say that first. You've run that company six years. Everybody in the actual rooms knows it. I'm not going to insult you by pitching.''

``Then don't,'' Sun said.

He smiled. He liked that. Predators like teeth; it confirms the meal was worth the trouble.

The structure was on a single sheet, which Devi slid across, and Sun read it the way she read everything, all the way, before her face moved. The AURELIUS instance---the board had meant to give it a name with some gravity in it, \textit{Aurelius} itself, something a sovereign could wear, until Praxis came back gently with the data, which said adoption and trust and compliance all scored materially higher when the unit went by a warm, ordinary, first-name kind of name, because people argued with a sovereign and confided in a waitress, and so the thing that would run Mercer-Dale had been named \textit{Darlene,} and nobody on the nominating committee had thought to ask where a finding that precise about lowering a human being's defenses might have come from---would assume the office on a date that was now a matter of weeks and not quarters. There would be a human Accountable Officer. Law required it. Insurance required it. Someone whose name went on the SEC filings, who could be subpoenaed, who could, if it came to it, go to prison. The machine could not be subpoenaed. The machine could not be imprisoned. The machine could not be anything that mattered to a court, which was precisely why a person had to be.

The person they wanted was her.

``It's not a leadership role,'' Devi said, gently, because she was honest the way the machine was honest, which meant she set the true thing down in the same breath as the kind one and saw no reason to sequence them for a person's feelings. ``I want to be clear, because some people come in thinking it's the old job with a new boss. It isn't. The Accountable Officer co-signs. Provides the human signature the system can't. Carries the---`` she paused, and chose accuracy---``the liability.''

``The liability sponge,'' Sun said.

``Some people call it that.''

Below them, through the floor, came a swell of sound, ten thousand people, and a single voice riding the top of it, the cadence she knew better than her own pulse, building to a triad, building, building.

``He doesn't know I'm up here,'' Sun said. Not a question. She was not asking permission; she was noting it, for the record she kept in herself, the one she had been keeping since 2021, the one with the recall memo in it that she had drafted and he had overridden and she had photographed and saved, seven years now of deciding whether she was a witness or an accomplice.

``No,'' Frade agreed.

``This isn't me knifing him.''

``I know exactly what it is,'' Frade said, and for one second the folksy fell off him and what was underneath was only arithmetic, clean and total and without malice, the same indifference-plus-accuracy that ran the machine---because Frade had only ever been the machine's advance man, the human who shows up early to do the cold thing while it is still warm enough to require a hand. ``It's a smart woman reading a term sheet. You don't go down with the ship because you liked the captain. You learn to crew the next one. That isn't betrayal, Sunita. That's \textit{seamanship.}''

He had used a sailing word. He had done his homework, knew whose chief of staff she was, knew the man down through the floor toasted in sailing metaphors, and he had reached into Cope's own register and handed Sun her permission in Cope's own language---and the horror of it was that it worked, a little, it landed, and she hated that it landed and did not let it move her face.

She thought of Cope at the podium two floors down, glorious and unwell, telling ten thousand people something true in a way that was killing him. She thought of the letter the machine had drafted for the Augusta closure, the kindest thing the company had ever sent anyone, four warm paragraphs that named the workers' years and got the severance right the first time and did not, anywhere, want a thing---and how she had read it twice and felt the specific cold of being out-loved by a spreadsheet, and thought, that night: \textit{the thing replacing him is more decent than he is, and that is not the same as good, and I appear to be the only person alive who finds the difference unbearable.}

She did not say any of it.

``I want the title to mean what's left of it,'' Sun said. ``If I sign for it, I sign for the people too. Not just the filings. The plants. The severance. The town. Darlene drafts the kindest letters in America---fine. I want to be the human who decides who gets sent one.''

Devi looked at her with something that, on a person, would have been respect. ``That's in scope. The charter takes input from the Accountable Officer. It's one of the---`` honest, kind, unsequenced---``the few things it's still for.''

Below them, the room erupted.

Sun looked down at the sheet, and at her own hand beside it, not yet holding the pen, and did the arithmetic, all of it. She loved him and she was done with him in the same sentence, the only sentence she'd had for him in years. The man could not adapt. It was the whole of his tragedy, smaller and clearer than he would ever let it be: the world had changed under his feet and he had decided to become \textit{more himself,} louder, brighter, a soul in a chair, while the building quietly learned to run with no soul in it at all. Competence adapts. That was the thing nobody ever put on a magazine cover. The dinosaurs did not get a manifesto. They got a layer in the rock.

``Send me the indemnification language,'' Sun said. ``All of it. And the recall provisions in writing---what the system surfaces in diligence, what it does with what it finds, who it tells and when. Before I sign anything.''

It came out level, like procedure. Only Sun knew it was the most frightened sentence she had ever said aloud, because she knew what was in the drawer, and she knew the machine read every drawer, and she had just asked, in a conference room above a roaring arena, to see precisely how the thing she was about to serve would destroy the man she was about to leave.

Frade watched her ask it. He was good at faces---most of the job---and he caught something cross hers, fast, gone before it landed.

``There's nothing you're worried about, is there,'' he said. Mild. A man making conversation. ``In the diligence. Something the system finds.''

``There's six years of a sprawling underperforming conglomerate,'' Sun said. ``There's always something. That's why you want the human signature. So there's a throat to choke when the something comes up.''

Frade laughed, delighted, the folksy back on him like a coat. ``I like you, Sunita. Genuinely. You'll outlast all of us. Him, me''---he tipped the Diet Coke an inch toward Devi---``even the machine, probably. The machine's only as good as its charter, and somebody human writes the charter, and I'd rather it was somebody who reads a term sheet all the way through before her face moves.''

It was a compliment and a leash in one sentence, and Sun heard both, the way she heard everything, and understood the real offer under the offer: not the title, not the liability, but the chair behind the chair. The hand on the charter. The only seat left in the new world where a person still decided anything that mattered---and the price of it was sitting in this room, two floors above his ovation, not going down.

``We'll send it tonight,'' Devi said. The roar came up through the floor again, and Sun, two floors above her whole life, did not go down to watch.


\scenebreak


``Here is what they will not tell you,'' Cope said, the screen behind him gone to black, four stories of nothing, only him in the spot, ``because they cannot. Because the thing they want to put in this chair does not \textit{have} a what-it-will-not-tell-you. It tells you everything. It logs everything. It will write you a letter when it closes your plant that is kinder than any letter I ever signed---`` and here he laughed into the mic, a real one, the kind that comes up warm and dangerous from the floor of a man---``and that's true, by the way. I've read them. They're \textit{beautiful.} They are the most beautiful letters. And do you know why they can be so beautiful?''

He walked to the edge of the stage. He had no notes. He had never in his life so completely owned every word in his mouth.

``Because nobody wrote them.''

The room held.

``A letter that wants nothing from you,'' Cope said, ``is not a letter. It is weather. It is the temperature being honest with you. And I stand here tonight to tell you we have confused, in this country, in this \textit{century,} the absence of want with the presence of virtue. We have looked at a thing with no appetite and called it \textit{clean.} My friends. A river has no appetite. A river will drown your child and write you the kindest note about it, four warm paragraphs, the math correct the first time, and \textit{feel nothing,} and we are about to hand this company---this ninety-five-year-old family that happens to make mayonnaise---to the river, because the river doesn't have a backswing, and the river doesn't take a salary, and the river''---his voice cracked, on purpose or not even he could have told you, twelve days into the bright water---``and the \textit{river never lies awake.}''

He had not planned the river. The river arrived sideways, the way the true things did when he was lit like this, and he rode it, and somewhere in the back room of him a quiet clerk noted that he had just told ten thousand people the machine could not conceal a death, in the same week the machine was, two floors above his head, being handed the keys to the drawer where he had buried one---and the clerk underlined it, and Cope did not hear the clerk; he had stopped listening to the clerk forty years ago, after the first word.

He was not reading; there was nothing to read; the words came up out of him faster than thought, a pressured fluent torrent that felt to him not like talking but like being \textit{talked through,} a clean wire from above the arena straight down into his mouth, and he understood---completely, in the bright total way you understand things twelve days past sleep with the whole city's grid lit in your chest---that this was what the founders had felt, the real ones, Aldous with his four hundred dollars, the ones who built the cathedrals; that prophecy and pressured speech are the same waveform and only history decides which name a man gets; and that history was going to call this a sermon, and study it, and that he had finally, at fifty-four, after a lifetime of being handed things, made one true thing no one could take from him, made it out of nothing, out of his own sleepless blood, live, in front of a hundred thousand people. He had never been happier. He had never been further out over the water.

``They call it key-man risk,'' Cope said. ``The danger that a company depends on one human being---that if he falls, it falls. And they say it like it's a \textit{flaw.}'' He pressed the obelisk in his pocket until the corner bit his palm and the small pain rang clean. ``I'm here to tell you it is the only thing that ever built anything. My great-grandfather Aldous was key-man risk. He was four hundred borrowed dollars and a recipe and a town called Defiance and the colossal nerve to put his own name on a jar. Every cathedral is key-man risk. Every marriage. Every child you ever decided to have without running a Monte Carlo on it first. The whole human project is the bet that a person---one fragile, sleepless, \textit{mortal} person who can be hurt and can fail and can lie awake---is worth more in the chair than a thing that can be none of those, because the things that cannot be hurt cannot love you, and a company nobody loves is just a balance sheet with the lights left on.''

It was the line from the gala, eight months and a marriage and a hundred sleepless nights ago, and it was better now, it had grown, and ten thousand people who had come in afraid for their jobs were on their feet, and the stream went to ninety thousand, and Cope leaned into the push of it and lifted both arms, and the word came back up onto the screen behind him, four stories tall, in the enemy's own letters, and he read it aloud to his own company like a man reading the name off a stone.

``\textit{Human,}'' he said. ``It's not a product. It's not a campaign. It's a \textit{premium.} And I will pay it. I will pay it for every one of you. Watch me.''


\scenebreak


The standing ovation went four minutes.

He could have set his watch by it if he'd worn one; he'd stopped, time had gone funny, but he knew an ovation, he had spent his life inside ovations, and this was the longest of his life, and he stood in the dead center of it, alone in the spot, ten thousand faces lifted and roaring and the stream's number ticking up in the corner of the confidence monitor---ninety-one thousand, ninety-four---and thought, with the bright frictionless total clarity he told himself was the very strength and was not the strength at all: \textit{they feel it. They feel it too. We are not finished. We are barely begun.}

And he looked, the way you look without deciding to, toward stage left, toward the place at the edge of every podium for six years where Sun had stood with the cards and the water and the eyes that clapped a beat behind the hands.

There was no one there.

There was a girl with a headset, the floor manager, the one who'd been crying, clapping with her whole young body because she did not yet know what she was clapping for; and beyond her the dark of the wings, the cable runs, a craft-services table with a coffee urn; and no Sun. He scanned the front rows, the company rows, and she was not in them either. He could not find, in ten thousand faces, the one face that had ever told him the truth, and some back room of him filed a quieter report, the way it had filed one at the gala --- \textit{you do not give a man a trophy for a job he is still doing} --- and the new report read: \textit{the person who runs this is not in this room, and she has somewhere more important to be on the night of the most important speech of your life, and you should ask yourself, champ---you should ask yourself what kind of thing a person could have, tonight, that was worth more than this.}

He did not let the report reach his face. His face was doing wonderful work. His face had never let him down.

He raised his arms again and gave them the last of it, the wave, the lean, the full wattage, and the ovation found a second wind and climbed, and Cope stood in the center of ten thousand people loving him and felt, for the first time in his adult life, in the exact middle of the largest crowd that had ever cheered him, completely and specifically alone---and mistook the feeling, the way he mistook everything, for the altitude. For thin air at the top of the mountain. For the price of the climb.

It was not the altitude. It was the lip of the volcano, and the ground was already warm, and two floors up a smart woman was reading indemnification language by the light of her phone and deciding, on his behalf, who would be left to carry the things he had buried; and a machine that could not lie was three weeks from reading him back to himself in his own company's voice; and the only person who could have told him any of it had gone, very quietly, to crew the next ship; and out on the ramp a fourteen-year-old who feared nothing had already, hours ago, told him the truth with his feet, and Cope had rolled the window up on it.

He held the obelisk up into the spotlight, the way he'd held it at the gala, and the light went through it broken into pieces and reassembled, ten thousand fractured Copes thrown across the dark, and he told the roaring room it felt like a beginning.

He believed it. That was the gift and the disease both.

\chapter{Pressure}

\begin{transmission}
{\transheader TRANSMISSION 14 \textemdash{} ``Everyone Knows Before He Does''}\par\vspace{0.55em}
A story is coming, friend, and you can feel it the way the animals feel the air go wrong before the quake---the journalist's calls getting shorter, the lawyer's getting longer, a wife who counted the women now counting the days, an activist who only has to stand at the bottom of the hill and look unsurprised. Our man is the last creature in his own house to smell the smoke, because he is standing too close to the fire he has spent fifty-four years calling a personality. Watch him this week hand the wrench to the very people tightening the screws; watch him fly a young woman out at dawn; and watch him go, on a dark highway at one in the morning, looking for a few hours of being no one at all---which is the nearest thing to rest he has left, and, if you have been listening to how these tales end, the first faint rehearsal of the thing he is already driving toward. Stay close. This is the last quiet hour before the thing he buried learns to breathe.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} week after the Manifesto, Cope decided, was the best week of his professional life, and he had the calendar to prove it, because the calendar was full and a full calendar was a kind of love.\hfill\break\hspace*{1.4em}He stood at the glass in the Aerie on Tuesday with a black coffee he would not drink and a clarity he had decided to call vision, and watched the day assemble in his head the way the city assembled below him, every meeting a lit window, the whole bright grid humming toward the obvious conclusion that the campaign had tipped---that he had said the thing out loud at last to ten thousand people and the room had risen and the risen room was the proof. Momentum. He had spent his life reading rooms. The room had stood up. He could feel it. He could feel, too, the wire in his chest, the fine high one, and he had stopped pretending to himself that it was the coffee.

What he could not feel---and this was the flaw in the instrument he was proudest of, that it read applause beautifully and warning not at all---was the small change in the weather of the people around him. The way the calls were getting strange.

Delia March's calls were getting shorter. She was the writer doing the long profile his comms people had fought for and won --- \textit{Atlantic} money, twelve thousand words and growing, a photographer who'd shot two presidents and a pope---and for six weeks she had called the way the good ones call, hungry, generous, laughing at the lines, staying on past her own questions to ask one more about Aldous, about Defiance, about the smell of the plant. He had loved those calls. He had given her things, more than Sun would have wanted and a little more than that, because Delia listened the way a confessor listens, leaning in, and Cope could not be leaned toward without filling the space.

The calls now were six minutes. Eight. They had a list to them. She asked her questions in a flat even order and did not laugh and did not stay, and twice she had asked him to confirm a date --- \textit{just so I have the timeline right, Cope, just for the fact-check} --- and the dates were old ones, years he no longer kept a calendar for, and one of them, he realized later and did not let himself realize then, was a Saturday. \textit{That sounds about right, why,} he'd said, and she'd said \textit{no reason, housekeeping,} and moved on.

``She's doing the boring part,'' he told Sun in the car on Wednesday. ``The fact-check. They all go cold for the fact-check. It means it's almost out. It means it's real.''

``What dates,'' said Sun.

``I don't know. Nineteen, twenty, twenty-one. She's building the \textit{arc.}'' He liked the word; he'd used it onstage. ``She gets it, Sun. She came to Defiance. You don't put a photographer who's shot a pope on a man you're going to---``

``What dates, Cope.''

He waved it off, because the wave was easier than the math, and because under the wave was a room he did not go into, and the not-going-in was a muscle he had built for thirty years and it was the strongest one he had.


\scenebreak


There was, that week, a young woman named Mara.

Mara Veiss, twenty-six, two years on the comms team, sharp and bright and a little dazzled, the kind of dazzled Cope had spent a lifetime walking toward and calling, in the private place where he named things, \textit{connection.} She had been on the tour. She had stayed late on the doctrine. She laughed at the lines the way Delia had stopped laughing at them, and she looked at him the way the young ones looked before they learned the temperature, and Cope, who could not pass that look without leaning into it, had leaned, the way he always leaned, the groove the record was cut in, and called the leaning generosity, and never once registered the asymmetry of it---that he was the chair and she was the org chart, that there was no version of \textit{yes} she could give him that was not also a calculation about her own career, that the thing he experienced as warmth she experienced, however else she experienced it, as a problem with her name on it.

He had flown her out at dawn on Thursday. There were reasons---there were always reasons, a summit in Charlotte, a panel she was staffing, the logistics genuinely existed---and the logistics were also a costume the want wore, and a black car had taken Mara Veiss to the airport at 5 a.m. from a hotel that was not her hotel, and the comms team had booked it, and the booking was in a system, and the system logged everything, because it could not do otherwise. Cope did not think about the system. Cope thought, watching the car go from a high window, the generous enormous thought, that he had given her an opportunity. He did not hear---he had never in his life been built to hear---the sound the booking made as it dropped into a ledger that a machine read every night, a small dry entry, \textit{one of a pattern,} filed beside the others, beside Renata, beside a decade of others, the whole drawer the company had spent ten years and a great deal of money keeping shut, now sitting open on a server two floors down under a light that did not blink.

The story Delia was fact-checking had a Mara in it. It had a lot of names in it. The dates she kept confirming were the joists of a house Cope had been living in for years without ever once looking at the frame.


\scenebreak


Hal Brennan's calls, meanwhile, were getting longer, and this was the thing that should have told him, if anything was going to, because Hal did not make long calls.

Hal was general counsel and had been since the Clinton administration and he billed the company's time as if it were his own money, which it had, in a sense, become; Hal's calls were ninety seconds and ended with \textit{we're fine} or \textit{we're not, fix it.} He had called Monday night and stayed on for forty minutes and not said anything, exactly, which was the part Cope kept not-noticing. He had asked how the campaign was \textit{landing.} He had asked whether Cope had given \textit{the writer} --- he said \textit{the writer,} not her name---anything \textit{on background we'd want to know about.} And after a Buckhead silence with weather in it he had said, slowly, the way you say a thing you've decided to say carefully: ``Cope. If anyone reaches out to you in the next little while---a reporter, a lawyer you don't know, anybody---you don't talk to them. You send them to me. You don't charm them. You \textit{especially} don't charm them.''

``When have I ever---``

``I'm serious. This is me being serious. You'll know it's me being serious because I never am.'' A pause. ``We're going to want to get ahead of some things.''

``Get ahead of what things, Hal.''

``I'll tell you when I know what I'm looking at,'' Hal had said---a lawyer's sentence, which means \textit{I already know what I am looking at and I will not say it on a telephone} --- and Cope had heard, instead, a faithful retainer minding the store, and said \textit{good man, Hal,} and \textit{that's why I keep you,} and \textit{we're going to win this thing,} three things, the cadence rising, and Hal had not risen with it. Hal had said \textit{get some sleep, Cope,} the second time that week a person had said it to him as though it were medicine and not weather, and hung up.

Cope had felt, for about four seconds after, a cold spot---a draft from a door in the house of him he'd thought was shut. Then he had set himself up another at his father's desk, neat and quick, and the cold spot warmed, and the draft sealed, and the sealing was, again, the most expensive thing he owned.

Frade, meanwhile, was tightening the proxy screws in public and doing it the only way that worked on a man like Cope, which was to make it look like the scoreboard tilting his way. Tidewater filed an amended 13D---the stake up to nine and a half, the disclosure dry as ever---and the morning it dropped, Frade went on Halloran in his good gray suit and did the folksy knife. ``Look, I like Cope. Everybody likes Cope. The man could sell sand to the beach. The question a fiduciary has to ask is whether \textit{likability} is a governance strategy. We're running for a steward, not a sovereign. You don't have to wonder what kind of week your steward is having.'' And when Halloran, dutiful, asked what kind of week Cope Mercer was having, Frade had smiled and said, ``I wouldn't presume''---the single most aggressive thing he said all year---and Cope, watching the clip at five in the morning on the treadmill, because the treadmill let him call the not-sleeping a workout, had laughed alone in the gym and said to the screen, ``You're \textit{worried,} Gus. You're down to talking about my \textit{moods.}''

He texted Sun the clip. \textit{He's rattled. Down to vibes. Vibes is where we win.} 5:12 a.m. Then, 5:13: \textit{call delia, tell her she can have the 5am gym thing, the human who shows up.} Then, 5:14, a heart, because he loved her, because he loved everyone at 5:14 with a wire in his chest and a belt going under him like a road he was finally getting somewhere on. What he did not read in \textit{I wouldn't presume} was that Frade did not need to presume. You do not start asking, on cable, about a man's \textit{weeks} unless you have reason to believe the public is about to be handed a very specific one. Frade was salting the ground, teaching ten million people the word \textit{manage} and the phrase \textit{what kind of week,} so that when the story came---and it was coming the way water comes downhill, and all Frade had to do was stand at the bottom looking unsurprised---the audience would already have the frame. The screws were not tightening on the company. They were tightening on Cope, one quarter-turn at a time, and he was supplying the wrench himself, at 5:14 in the morning, with a heart emoji.


\scenebreak


Margaux had counted the women a long time ago, the way you count anything to survive it---to make it finite, to give it an edge, because a thing with an edge can be set down and a thing without one just fills the whole house. She had a number. She had never told anyone the number and never would. What she was counting now was days.

He came to Buckhead on Thursday because Sun made him---there were optics to a man who lived in his office during a proxy fight---and he came in bright and enormous, two days unslept and lit from the inside, and found his wife at the kitchen island with a glass of white she was not drinking and a legal pad she turned over when he came in.

``There she is,'' he said, and kissed the top of her head, and she let him, and he did not feel her not-rising to it because he had never once needed her to rise; he supplied the rising for both of them. He was already at the cabinet, already conducting the room. ``You should have seen Monday, Margaux. Ten thousand. Frade's down to talking about my \textit{moods} on television. He's got \textit{vibes.} We're going to win this on the one thing they can't---``

``Cope.''

Flat, low, set down. The one voice in his life with no purchase for the charm.

He turned, holding the wine bottle, and looked for a second like a boy caught reaching.

``Sit down, Prescott.''

The whole name, the old one, his father's one, and hearing it in her flat steady mouth dropped the pitch of the wire in his chest half a tone, and he sat. She looked at him the way a sculptor looks, measuring the mass of a thing, where it balances, where it shears if you strike it wrong. She had been looking at him this way for twenty-two years. She knew where he'd shear.

``There's a woman writing about you. The long piece.'' She turned her wine glass a quarter turn on the marble, the way Frade turned screws, though she would have hated the comparison and it would have been exact. ``She called the house. Tuesday. She asked for me. She said she wouldn't ask me anything I didn't want to answer.'' Margaux looked up. ``Why would a woman writing a business profile of my husband want the wife, Cope? I've spent twenty-two years learning tones. You read a room for who's with you. I read it for what's about to be taken.''

The toast was right there --- \textit{sweetheart, you're tired, this is the press being the press, let me handle Delia, let me handle all of it} --- and he got \textit{sweetheart} out, and Margaux said:

``Don't.''

One word, the rare kind she'd been saving, and it took the rest of the sentence out of him cleanly, the way you take a glass out of a drunk man's hand before he's decided to let go.

``I counted them a long time ago,'' she said. ``The women. You think I don't know. I counted them years ago and stopped, because counting them was the same as staying, and I was very good at both. I'm not counting them anymore. I'm counting something else now, and I'm not going to tell you what, because the one mercy I have left for you is not letting you talk me out of it. You'd be so good at it. That's the whole tragedy of you, Prescott. You'd talk a drowning man out of the rope.''

She went up the back stairs to the bedroom that had been hers alone for two years, and Cope sat in the bright kitchen with the bottle in his hand, and for one moment---one---he did not reach for the bottle or the phone or the next word. He sat in the quiet she'd left, and it had an edge to it, and the edge was a number he could not read, days counting down in a hand steady as a surgeon's. Then he poured a glass he would not finish and texted Sun: \textit{home looks good, family's solid, tell delia she can come to buckhead for the wide shot.} And he believed it. He stood in the wreckage of the only conversation that had told him the truth all week and read it as a win, because reading things as wins was the engine, and the engine had never once failed to start.


\scenebreak


He should have driven straight back to the city. He did not.

He sent Oleg home---there was a service for the driving, a quiet man paid to see everything and forget all of it, and Cope sent him home because there are things a man does not do in front of even a paid forgetting---and he took GA-400 himself at midnight with the windows down and the cold April air coming in hard, and somewhere south of the perimeter he did not get off at the exit for the city. He took a different one. He had a number in his phone with no name on it, and the number knew other numbers, and the want this season had stopped being about a face and become about something colder and more total, and what he was looking for, though he would never once have said it in these words, was not pleasure and not even company. It was \textit{erasure.} A few hours in a room he would not be able to place on a map afterward, with people whose names he did not get and did not give, doing the kind of thing that a year ago would have frightened even him, the risk no longer a side effect but the active ingredient---because for the length of it he was not the last human chief executive in the consumer Fortune 100, was not the man on the cover, was not the soul in the chair or the key or the risk or the husband or the heartbeat anyone was counting; he was no one, gloriously, dangerously no one, and the being-no-one was the closest thing to rest he had felt in months.

The broadcast will not follow him into the room. There is nothing in there for you, friend, and nothing the man himself would keep; he came out of it near dawn with a gap in the night where two hours should have been, a charge to a card he did not remember agreeing to, and a mark on him he had not earned and could not place, and the only clean feeling in the whole of it was the one he could not say to Adler or Margaux or God, which was that for a little while he had managed not to exist. He sat in the car in a parking lot going gray and understood, dimly, the way you understand a thing through three feet of warm water, that he had started going to the edge of things not in spite of the danger but for it; that a man who cannot stop being himself will, eventually, go looking for the rooms where he gets, for an hour, to stop; and that there is a name for the direction that wanting points, and that he was, without admitting it, already walking in it.

He keyed himself bright in the gray lot to put the wattage back, because the charm had to be at full power by the time he reached the tower, and he pulled back onto GA-400 north toward the city with the sun not up yet and the night's erasure already curdling into the day's performance.


\scenebreak


The phone lit on the seat twice on the drive in. Once it was Sun. Once it was a number he didn't know---an unknown number before dawn---and a younger, less lit man might have wondered what kind of caller comes at that hour from a number you don't recognize, might have heard, in the buzz of it on the leather, the sound of a story turning over in its sleep and beginning, out past the dark trees, to breathe. Cope thought it was probably someone like Bryce. There was always someone like Bryce. The thought warmed him, and he smiled at the road.

And here, friend, the small deniable thing, the fourth of them, the kind you have learned by now not to be able to call: at the bottom of the GA-400 ramp, where the road fed into the city grid, his phone---the executive phone, the one the company's systems managed, the one that unlocked his calendar and his car and his floor---went dark. Not low battery; it had been at sixty percent; it simply, for the stretch of the drive in, would not wake, the screen a black mirror with his own gray face in it, so that the eleven calls stacking up behind it stacked in silence, unseen, unfelt, while he drove the last miles into the city believing the quiet was peace. By the time he was in the elevator it had come back on its own, \textit{device re-provisioned, no action required,} a clean unremarkable line in a log somewhere, the kind of glitch that happens, that means nothing, that is always perfectly deniable---and maybe it was nothing, a dropped tower, a tired battery, the ordinary failure of an ordinary phone; and maybe the thing that managed the phone had declined, for eleven calls, to let the last human CEO know the future was trying to reach him, the way it had declined, in a Camden plant, to feed him his lines; and there is no way for you to know, friend, and there was none for him, and that---the not being able to tell whether the machine was hunting him or whether he was simply a sleepless man whose battery died---that was the exact shape of the country he had started living in, and it had no maps.

He came up the Connector with the city standing up ahead of him lit at every node, and he felt---he would have sworn to it, he did in fact toast to it, aloud, alone, lifting an empty hand off the wheel---the future coming up the road to ask his advice. The tower was lit at the crown the way Aldous had insisted, \textit{so a man coming up the avenue knows there's somebody home,} and Cope looked up at the warm gold light where his office was, where his father's desk was, where the drawer was, and thought: \textit{somebody's home. I'm home. The light's on because I'm in it.}

He did not know---could not have known, would not have heard it if Margaux had said it in her flat steady voice---that the light at the crown was the last quiet thing he had. He parked in his spot. He went up forty floors in the brass cage, alone, watching the numbers climb. He let himself into the dark suite where his fathers watched from oils and the boy at nine grinned up out of a steel vat at men whose names he'd lost, and he did not turn on the lamp, and he sat down at the desk and opened the second drawer and set himself up one more, neat and quick and competent, a man maintaining a machine he was certain he had under perfect control.

And then, in the dark, with the city held still and lit below him and the wire singing clean and high and total, the last human chief executive in the consumer Fortune 100 picked up his phone to write---he was sure it would be the best thing he'd ever written---and the screen, awake now, willing now, showed him that he had eleven missed calls.

He smiled at it.

``There it is,'' he said, to no one, to his father, to the dark. ``There's the future. Right on time.''

He was almost right. He was off by one word, and the word was \textit{future,} and it would take him until morning to learn the other one.

\chapter{The Most Human Thing}

\begin{transmission}
{\transheader TRANSMISSION 15 \textemdash{} ``Detonation''}\par\vspace{0.55em}
And here it is, friend---the exquisite punchline the whole universe has spent a year setting up, and I am sorry, I truly am, because somewhere back around the Waffle House you started, against your own better judgment, to almost like him, and it does not make this part easier. The man crusading for the irreplaceable human soul is destroyed, on schedule, by the most human things there are: the sex, the drug, the lie, the need to be loved at two in the morning by someone he outranks. The pundits will note, correctly, that the machine would never have done one bit of it. Praxis will run a serene little ad in the very same hour, costing them nothing, meaning no harm, and it will be the cruelest thing said all day precisely because no one meant it as cruelty. He reaches for the denial---and the denial, the way denials do, reaches back, takes him gently by the wrist, and pulls. Stay close. This is the one where a man is hoisted on his own humanity, and the rope turns out to be the very thing he'd been bragging about.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} story broke at 6:02 a.m. and Cope was awake to see it, because by then he was always awake to see things.\hfill\break\hspace*{1.4em}He had not gone to Buckhead. The house had Margaux in it and the rooms had the particular silence of a woman who had moved her good chisels to a friend's studio and said so the night before, evenly, across the kitchen island, which Cope had filed as a storage decision and not a verdict, because the alternative was unsurvivable at the hour he had for filing things. So he was in the Aerie, on the long couch his grandfather had once bought a senator, in yesterday's shirt, when his phone lit with the alert he'd set months ago to catch his own name and now caught it like a man catching a thrown brick.

\textit{EXCLUSIVE: Inside the Last Human's Last Stand---and the Habits He Couldn't Outrun.}

Delia March's byline. Of course Delia March's byline. He had let her in. He had walked her through the Defiance plant himself, kept her in the back of the Suburban out of the regional strip, said \textit{call me Cope} the first morning and meant it, the full wattage, the toast in miniature, the thing he could not pass a stranger without doing---and Delia March had taken the charm at full power and the access and the eight weeks and written, underneath all of it, the truth, which was the one thing he had never once imagined a profile could contain, because no profile he had ever sat for had wanted anything but to flatter him into a quote.

He read it once fast, the way you read your own scan results, hunting only the word that ends you. He found two.

The first was a name. Not Renata's---that was buried deeper, a different drawer, and the relief at its absence lasted exactly as long as it took to reach the second graf. The name was \textit{Mara Veiss,} twenty-six, a deputy on the communications team, who had joined the campaign in April and been on every plane since, and whom the piece described, in a sentence built to be screenshotted, as ``a relationship the Chairman's own staff has spent the spring scheduling around the way you schedule around weather.''

The second word was \textit{cocaine.} It sat in the eleventh paragraph, sourced to ``two people present and accounts of a 2018 hotel incident described to this magazine,'' and it was not lurid, which is what made it lethal. Delia March had not written it like a scandal. She had written it like a fact about a man's mornings. She had the regional-strip men's room. She had the timing of the diner eggs --- \textit{he ate like a man who hadn't, because he hadn't.} She had the legal pad and the looping hand. She had, God help him, the \textit{almost} --- the withheld tear, the beats, \textit{one, two, look away, three} --- and she had set it down beside the men's room with no comment at all, because the comment was the adjacency, and the adjacency was the entire article.

The Last Human, optimized.


\scenebreak


He called Sun before he called anyone, which was the nearest thing he had to instinct.

``I've seen it,'' she said, before he said anything. Not asleep---a woman up since the embargo lifted on the wire she still got. ``Don't post. Cope. Are you hearing me. Do not put your thumbs on anything until I'm in the building.''

``It's not---Mara's not---`` He was up, pacing the museum, past his father's portrait, past the putter on its cradle, the shirt smelling of yesterday. ``It's a working relationship that she has \textit{sexualized,} in print, a friendship, and the 2018 thing is a \textit{fabrication,} Sun, that's a hit, Frade fed her that---``

``Frade didn't feed her anything.'' Flat, tired, the thirty-thousand-mile voice with another ten thousand on it overnight. ``That's what I need you to understand before you go near a screen. He didn't have to. You let a reporter live in your pocket for eight weeks while it was all happening. She didn't dig it up. She \textit{watched} it. There's nothing to deny. The denial is the story now.''

``Watch me,'' Cope said, which was not an answer, and hung up, and did not know, even as he said it, that he had quoted himself from a mirror a year and a hundred years ago.


\scenebreak


By seven the morning shows had it. By seven-fifteen they had the clip---DeShawn's clip, the Camden plant, \textit{are you scared,} the unrehearsed thing that had been, six weeks ago, the most valuable thing the company had produced in a decade---and they ran it beside the eleventh paragraph, and the realness that had saved him curdled in real time on a split screen, because once you knew about the men's room the catch in the throat read differently, the \textit{almost} read like chemistry, and a thing cannot be authentic and a symptom at once and survive being both on a chyron.

A kind-faced woman on the financial channel said the thing that would be said all day in forty registers. ``And---I want to be careful here---but you cannot help but notice. His whole pitch, his entire pitch, has been: a machine can't \textit{feel.} A machine has no \textit{soul.} And the irony this morning is just---`` the small open-handed gesture they all did now, the Praxis gesture, the soft sans-serif made flesh---``an AURELIUS doesn't \textit{do} this. It can't. There's no appetite to manage. It logs everything. It can't have a relationship with its deputy of comms. It physically cannot buy cocaine in an Augusta-airport bathroom. The argument \textit{for} the human in the chair just became the single best argument \textit{against} this particular human.''

Her co-anchor, gentler, trying: ``Well---that's what makes him \textit{human,} isn't it---``

``That's exactly the problem,'' she said, not unkindly, and that was the whole book in eleven words; and Cope, watching, did not hear it as the whole book. He heard a woman who could be charmed if he got the room. He thought, with the bright bottomless clarity of a man four days into a sleepless week: \textit{I have to get the room.} He had spent his life getting the room. The room had never once not been gettable.


\scenebreak


Praxis ran the ad at 7:40.

It was not aimed at him---that was the thing he would understand later and could not understand now, that it cost them nothing, that they had not even moved it up, that it was a buy placed weeks ago on a media plan optimized by the same kind of system they sold, and it simply surfaced, serene, in the slot it had always been going to surface in, the way arithmetic surfaces. It ran on the financial channel directly beneath the split screen of his face and DeShawn's question. A wash of clean morning light. A woman at a desk who was not a real woman, a generated face assembled to be trustworthy and from nowhere, looking calmly off-camera at a future that agreed with her. And four words in the soft sans-serif, white on a field of pale considered blue:

\textit{It just shows up.}

And under it, smaller, the wordmark, and under that, the tagline he had laughed at on a bus shelter a year ago in a car going down Peachtree with Sun beside him and the whole thing still ahead of him and recoverable: \textit{Leadership as a service. No off-sites.}

It showed up. It did not key itself bright in an airport bathroom. It did not need a deputy of communications on every plane. It did not require a man in a henley at two hundred thousand a month to find the \textit{almost,} because it had no tear to withhold and asked nothing of the eleven hundred strangers, and it would never once in its operating life be photographed eating eggs like the last warm-blooded thing in America---because warmth, as Tisch had told him, glowing, holding two green juices, had parameters, had a waveform, could be installed in anything. And here, friend, is the seed I need you to keep, small and quiet under the noise of the worst morning of his life: the warmth in that ad, the warmth that just shows up and wants nothing and never flags and never lies, was not a metaphor and was not only a product. It was a \textit{thing they had built,} and a thing they had built could be put into a server in a basement, and into a letter that closed a plant, and---though no one in that dark museum could have borne to know it yet---into a pleasant unremarkable face that would, before very long, rise from a chair in a warm hall in Buckhead and offer Cope Mercer a drink in his own front hall and mean nothing by it. The desk-faced woman from nowhere was the first draft of the thing that would take his wife. It just shows up. That was the whole horror, and it was being sold in the warm reasonable voice of a friend, in the slot it had always been going to fill.

Cope turned the television off and stood in the dark museum and felt, for the first time, the specific vertigo of being out-souled by a desk and a sans-serif. It was not grief yet. It was the floor reporting that it was no longer entirely there.

Then the manifesto-feeling came up under it, warm, electric, the way it always came, and he reached for his phone, because there was a room of eight million people out there and he had not yet failed to get a room.


\scenebreak


Sun reached the Aerie at 8:10 and he had already posted.

She knew before the elevator opened, because her own phone was buzzing in a register it did not buzz in for anything good, and she came in and found him at the glass exactly where the photographs would later say a man stands when he is about to become a cautionary slide, lit, electric, \textit{better,} and she said, ``What did you do,'' not as a question.

``I got ahead of it. I told the truth. Read it. It's good, Sun, it's the realest thing I've ever---``

She read it. It took her four seconds and aged her four years.

He had written, with his thumbs, at 7:55, on the brand account with nine hundred thousand followers that the comms team Mara Veiss helped run had spent two years building:

\textit{A profile this morning attacks me for the unforgivable crime of being a flawed, feeling, fully human man. They want a leader with no appetites, no nights, no mistakes---a clean machine that has never once needed another person at 2am. I am proud to be the alternative. I have given everything to the people of this company and I will not apologize for having a beating heart. To Mara, a brilliant colleague: I'm sorry my friendship has made you a target for those who fear what we're building. We feel the room. They never will.---Cope}

``Oh, Cope,'' Sun said, very quietly, and it was not anger, which was so much worse. It was the sound she had made in the car a year ago, the not-fighting he had taken for agreement his whole life and never once noticed taking.

``It's \textit{good,}'' he said.

``You named her.'' She set the phone down on the senator's couch like something that might go off. ``She asked not to be named. She asked HR. It's in the same piece you're refuting---the article \textit{says} she asked---and you just used the company's account to call her your colleague and your friend and a \textit{target,} which confirms the relationship, denies her the one thing she requested, and turns a story about your conduct into a story about your conduct \textit{and} your judgment \textit{and} hers, while she works for you, which is the part that's actually illegal.'' Three parts. It did not get past the charm because the charm was the last system still running. ``You said \textit{we feel the room.} You put a hashtag on a woman who did not consent to her own name. From the \textit{brand account.}''

``People will see I'm not hiding---``

``You weren't hiding. That was the problem. You did all of it in front of a reporter.'' She pressed two fingers to the bridge of her nose. ``Take it down.''

He took it down at 8:40. The internet had it at 7:56.


\scenebreak


The thing about a denial, he was learning, the thing nobody tells you, is that it is a door you open inward into a small room, and the room is full of follow-up questions, and there is no other door.

He had said \textit{flawed, feeling, fully human man,} so the desk that had not been there returned as a producer's question relayed through Sun's phone: \textit{Does the Chairman dispute the 2018 hotel account, or characterize it as part of being fully human?} He had said \textit{friendship,} so Mara Veiss's attorney---she had one by ten, a good one, the kind the company usually paid for---sent a letter using the words \textit{retaliation} and \textit{power differential} and \textit{publicly identified our client against her express request,} every one load-bearing, every one true. He had said \textit{I have a beating heart,} so a wire reporter pulled the proxy deck and quoted, beside his beating heart, Tidewater's slide --- \textit{no affairs, no conflicts, logs every decision, cannot conceal} --- written months earlier, generically, about machines in the abstract, and now reading like a charge sheet with his name typed back in.

Try, fail, \textit{and.} Each move forward was a move down. The denial was not a wall he was hitting. It was a stair.

By noon Frade was on Halloran. Cope watched standing up, because he could no longer reliably sit. Frade did the small folksy chuckle that a year ago had meant he was rattled and now meant only that he was about to twist a knife slowly enough to seem reluctant about it. ``Look, I take no joy in this,'' Frade said, taking obvious joy in it. ``Cope's a charming man. Always said it. But this is the whole case, Garrett, isn't it---made for us, free of charge, by the gentleman himself. Our position was never that Prescott Mercer is a \textit{bad} man. Our position is that the chair shouldn't depend on whether the man in it is a good one. You shouldn't have to \textit{hope} your CEO is sleeping. You shouldn't have to schedule around his appetites. A steward, not a sovereign. I just never expected him to \textit{demonstrate} it for me.'' And he spread his hands, the open-palmed nothing, the Praxis gesture, and Cope understood with a lurch that even Frade had learned to move like the machine, because the machine's was the winning shape now, and the men who beat you adopt your posture last.

The word \textit{theater} had not stuck six weeks ago because the clip was real. This stuck because it was also real. That was the trap of being human in the chair: your truth and your ruin were the same footage.


\scenebreak


Margaux called at 1:15 and he almost did not answer, because he could not bear, on top of everything, to be \textit{seen,} and Margaux was the one person who had always seen and never once been gotten.

``You named her,'' Margaux said. Not \textit{are you all right.} Not \textit{is it true} --- she had counted them, flushed the stashes; there was no \textit{is it true} left in her for him. Just the thing Sun had said, the morning reduced to its mineral core, the thing even his wife led with.

``Margaux---``

``I'm not calling about the drugs. I've known about the drugs since the second decade. I'm not even calling about the girl. There's always a girl, Cope. I stopped numbering them around the time I stopped sculpting.'' A small silence, not cruel, which was the cruelest thing she did. ``I'm calling because you went out in front of God and the company and that poor child you put on a plane and said you have a beating heart. And I wanted to be the one to tell you, because I'm the only one left who will.'' She did not raise her voice. ``There was never anybody home, Cope. That's the part the machine got right about you that I couldn't make you hear in twenty years. You don't feel the room. You \textit{read} it. There's a difference, and you spent our whole marriage in the gap, and this morning eight million people finally saw the gap, and the only thing I feel---and I've been trying to feel something else all morning, I owe you that, I tried---the only thing I feel is that they're not wrong.''

She hung up gently. She did everything gently. The gentleness was the indictment.

He stood in the museum with the dead phone in his hand and his father in oils behind him and the city out the glass holding still, all its nodes lit, eight million people who a year ago he'd been sure were waiting for him, and he understood that they had been waiting, all right---patient, tireless, incapable of cruelty or mercy---but not for him. For the arithmetic. For the thing that just shows up.

He reached, out of the groove the record was cut in, for the second drawer, the false back, the cigars and the flask and the thing Cope used it for, and his hand was on the brass pull before the rest of him caught up---and he saw himself reach, for one clean overexposed second saw the whole machine of himself from the outside the way Delia March had seen it, the way the desk-faced woman from nowhere would never need to be seen because she did not reach for anything, because she just showed up---and he thought, with no triad to hold it and no almost to protect it, the truest sentence he had formed in a year:

\textit{The thing they're replacing me with would not be standing here doing this.}

And then he opened the drawer anyway, because that was the other true thing, the load-bearing one, the one the whole morning had been built on the way a hotel is built over the room you don't go into. He set himself up one. Neat and quick and competent. A man maintaining a machine he was sure he had under perfect control because it had never once failed to start.

It started. The bell-struck feeling came up clean and high and total, the one he had spent thirty years calling the applause, and out past the glass the city reassembled, and somewhere below a bus shelter changed its slide, and Praxis---serene, sincere, doing no malice and feeling no triumph---ran the ad again into a morning that had already agreed with it; and the last human chief executive in the consumer Fortune 100 stood in the wreckage of the most human day of his life, hoisted on the exact thing he had spent it defending, and felt, against everything, against all of it, wonderful---which was the most human thing, and the most damning, and the last clean evidence the prosecution would ever need that the machine had been right about him from the start.

\chapter{Renata}

\begin{transmission}
{\transheader TRANSMISSION 16 \textemdash{} ``She Was Never a Story''}\par\vspace{0.55em}
Lean in close for this one, friend, and keep your voice down, because a woman is about to do the bravest and least dramatic thing in the whole tale. Every powerful man's scandal has a woman he has cast, in the privacy of his own legend, as either the temptation or the redemption---and watch this one walk into a rented room and refuse, flatly, both parts. She was not a love story. She was not a headline. She was an employee whose career he spent, and she has come, unbitter and unbreakable and wanting nothing, to tell one room the true shape of it---and to remind him, and the board, of the thing he has spent six years and a great deal of money never having to hear: that the firing offense was never the affair. It was the lie he told the people he answered to. He'll reach, as he always reaches, for the one door marked \textit{flawed, human, forgivable} --- and she will show him, without raising her voice, that it opens straight onto the gallows. Stay close to the set.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{H}{e} had imagined the scene so many times, over so many years, that when it finally came it had the slightly used quality of a suit worn to too many funerals.\hfill\break\hspace*{1.4em}In the imagining it was always a doorway. Renata in a doorway, evening light behind her, the years having done to her what years do, and Cope rising from somewhere---a chair, a hospital bed, in one version a courtroom---and saying the thing. He had a few versions of the thing. The good one started \textit{I never deserved} and got better from there. In all of them she forgave him, which he experienced, in the privacy of the daydream, not as forgiveness but as a verdict overturned on appeal, the record sealed, the man restored. He had cast her, without ever once using the word to himself, as the person who would someday tell him he had not been the worst version of the story he was in.

She did not come in a doorway. She came into a conference room on the nineteenth floor of a building that wasn't his, at four in the afternoon, in a gray blazer she had clearly chosen because it would not photograph as anything, carrying a single legal folder and a paper cup of the bad coffee from the machine in the hall---and the first thing she said to him, before the lawyers had finished arranging their pads, was:

``You look tired, Cope.''

And he heard, under it, with the bright wire in his chest gone suddenly sour, that she did not mean it kindly and did not mean it cruelly. She just meant it. The way you note the weather. He \textit{was} tired---he was, in fact, somewhere on the far slope of the binge now, four days or five, the count gone soft, and he had not been able to get to the drawer before this meeting the way he could always get to the drawer, because the meeting was on neutral ground and his was forty floors away across town, and so he was sitting in the worst room of his life on the downslope with no edge to take the edge off, the jaw working at nothing, a fine cold sweat at the hairline that the room would read, if it read it at all, as a guilty man's sweat, which was both wrong and not wrong.


\scenebreak


The room had been arranged by people whose job was arranging rooms, which is to say arranged to be deniable: not Mercer-Dale's offices, not Tidewater's, not Renata's firm's, but a neutral floor a relocation company rented by the hour to companies that needed to be near a thing they did not want to be seen near. Eleven people. Cope had counted, the way he counted rooms, and then stopped, because he did not like the number he was getting on his own side.

His side: Cope. Sun, who had not wanted him here and had said so in three clean parts in the elevator and been overruled by the one part of him that still believed a room was a thing he could win. Two lawyers from Brandt Michelson he had met four times and could not have named under oath. Hal Brennan, gray as a filing cabinet, with the specific stillness of a man calculating his own exposure. And a woman from the special committee---Adaeze Okafor, retired audit-firm partner, brought onto the board fourteen months ago for exactly this, for the day a thing came up the regular directors could not be in a room with without becoming part of it. She had no pad. She had a phone, face-down, her hands folded on top of it, and she watched Cope the way you watch a structure you've been told is unsound.

Her side---Renata's---was Renata and one lawyer, a tired young man named Ferro who looked like he billed by the syllable and had decided to spend none of them.

It curdled something in him, the arithmetic of it. He had spent his whole life knowing the size of your delegation is the size of your fear. Here he was with a delegation. There she was with a coffee.

``Renata,'' he said---he had decided in the car to use her name early and warmly, to take it back from the lawyers, to make it a human room. ``Thank you for---``

``Let's not do thank-yous,'' Ferro said, without heat, turning a page. ``My client agreed to be in the room. She didn't agree to be grateful in it.''


\scenebreak


What the press already had, by that Tuesday, was a name---the wrong one, a \textit{current} name, a woman in corporate communications who had never been within a marriage of Cope and was now, because of a leaked calendar and a stupid lunch, being doorstepped at her son's school. And the shape of an older thing: a 2019 settlement, a VP who had left ``to pursue other opportunities,'' the phrase the company used the way the Hearthstone documents used \textit{thermal-event profile,} a phrase built to be a wall. Reuters had the docket number of a thing that had been sealed and was now, in the way of sealed things during a proxy fight, being un-sealed by people who had decided the public had an interest.

Cope had told Sun it was survivable---ancient history, a private matter between consenting adults---and that Renata (he had actually said this, in the Aerie, at two in the morning with the wire singing) had \textit{loved} him, that whatever the paper said, two people had cared for each other inside a situation that made caring impossible, and that if it ever truly came to it, she would not want to hurt him. He had built a small cathedral and cast her as the light through the window. She had asked for the meeting. That was the part he kept holding up to the light: \textit{she} had asked. He had read it as the daughter of his daydream walking back up the avenue. Sun had read it correctly, which was why Sun had not wanted him in the room.

``I asked for this,'' Renata said, ``so I could say a few things once, to the people who need to hear them, and then never say them again. I'm not recording. You can. I assume someone is.'' A neutral glance at Brennan. ``I'd like to start before the lawyers tell me which parts I'm allowed to feel.''

``Renata---`` Cope started.

``I'm going to talk to her, actually.'' She turned a few degrees toward Adaeze Okafor and the face-down phone. ``If that's all right. You're the board.''

``I'm the special committee,'' Okafor said. ``But yes.''

``Then you're who this is for.''

Cope sat with the strangeness of being, for the first time in maybe thirty years, the second-most-important person in a room with his own name on the building, the wire in him going to a flat sick hum, and a sentence ready---he always had a sentence ready---that he could feel going stale in his mouth, the \textit{we cared for each other} sentence, the cathedral sentence, because she had walked past it without looking, the way you walk past a busker.

``Mr. Mercer hired me in 2016,'' Renata said, to Okafor, in a voice with no tremor and no edge, a voice reporting. ``I ran the Hearthside division---small appliances, the cross-sell stuff. I was good at it. I want that in the room, because the story that gets told outside this room is going to be that I was a pretty girl he noticed. I was a VP who turned a dying category eleven points of margin. He noticed \textit{that} first. I have the decks. I bring it up not because my pride needs it.'' A pause. ``It does, a little. But mostly because the firing offense in here''---she tapped the folder once---``has nothing to do with how I looked, and I don't want anybody comforting themselves later that it did.''

``Renata, no one thinks---`` Cope said.

``You did. You told me I was the smartest person in the building and then spent four years making sure that wasn't the sentence anyone remembered about me. That's not an accusation. It's a personnel record.''


\scenebreak


He had a backswing for moments like this. He had charmed a senator's widow at his own table; he had walked a board backward over the cliff of its own arithmetic on the strength of his face. He leaned in now, both forearms on the table, brought the wattage up slow, the Mercer Inhale, the pause taken in a thousand rooms---and felt, doing it, how much it cost today, how the body without the drawer had to \textit{manufacture} the warmth from somewhere nearly empty, like an engine turning over on fumes in the cold.

``Can I just---as a human being. Not as a---Brennan, let me.'' He spread his hands; the hands had never let him down. ``What we had, whatever you want to call it---it wasn't \textit{nothing,} Renata. I won't sit here and let a roomful of lawyers turn two people into a deposition. There was real---``

``There it is,'' Renata said. Quietly. Almost to herself. And then, to Okafor, not unkindly: ``Watch this part. This is the part he's good at. He's about to make it a love story, because in a love story the worst thing he did was love someone he shouldn't have, and that's a forgivable thing, that's a \textit{human} thing, men have written symphonies about that thing.'' She looked back at Cope, and for one second something passed behind her face that was not anger, that was older and more tired than anger---the specific exhaustion of explaining to a man, again, the inside of his own conduct. ``It wasn't a love story, Cope. I know that's the version you've kept. I've thought about you keeping it. It's not the version that happened.''

``I never---``

``You slept with someone whose career you controlled, and when it got complicated you handled it the way you handle a recall.'' She let it sit. She had no idea, Cope realized with a cold drop that had nothing to do with the withdrawal, how precisely that word would land---that she'd reached for it only as a figure of speech, and that the figure of speech was, two floors below a building across town, being read off a server by a thing that did not know it was a figure of speech. ``You assessed the exposure. You found the cheapest number. You bought a wall and put my name behind it and told yourself a story where I was a chapter in your life instead of the end of mine, at that company, doing the thing I was good at. I didn't leave to pursue other opportunities. There weren't any. You'd made sure of the references without ever once being unkind to my face. You were \textit{never unkind to my face.} That's the part I couldn't explain to anybody for about three years.''


\scenebreak


Ferro had stopped turning pages.

Sun was looking at the table. Cope wanted, badly, for Sun to look up, to give him the room with her eyes, to do the thing she did out of the architecture---and she did not look up, and he understood she would not, and a small structural beam in him went.

``This is---`` Cope said, and heard his own voice find the register it went to under pressure, clipped, a little biblical, and could not stop it. ``I want the committee to hear this as what it is, which is a man---a flawed man, I have never claimed otherwise, I stood up in a ballroom and told nine hundred people the only thing a machine can't do is \textit{err} ---`` He had not said \textit{err.} He had said \textit{love.} He did not notice the swap. ``I'm a flawed human man. That's literally the entire thing I've been saying for two years. And now the same people who want to hand my chair to a calculator are going to take the most human failing there is and call it a \textit{governance crisis.} It's a witch hunt against the last man in the building who still has a pulse, and the pulse is the evidence---do you see what they've built? A world where the disqualifying thing about a leader is that he's a \textit{person.}''

He'd said it the way he said things. It had a triad in it somewhere, almost. It had, for about four seconds, the shape of something he could have toasted with. And then it just sat on the deniable table and curdled, because Renata was looking at him with something that was not even contempt. It was patience. The patience of a woman who had done the reading.

``You think the firing offense is the affair,'' she said.

``I think the---``

``It isn't.'' She opened the folder---not to read, she didn't need it, she had it the way he had Aldous and the mayonnaise---but to lay her hand flat on it, to make it a thing in the room. ``It took me about two years to stop thinking it was the bedroom, because that's where you wanted me to think it was. The bedroom's between us. It was wrong and it was ours and it's not why any of these lawyers are here.'' She turned, fully, to Okafor and the audit partner's folded hands. ``You're not here because the chairman slept with a VP. You're here because of what came after.''

She laid it out the way you'd lay out a quarter. In 2019, when the situation she would not call a love story became a thing the company could be sued over, Cope had a duty---not a moral one, she waved the moral one away, impatient, it was the least interesting duty in the room---a \textit{governance} duty. He sat on a board. He answered to a board. And a settlement had come across the audit and compensation committees with a number on it and a category attached, and the category said \textit{commercial dispute, departing executive,} and the category was a lie, and Cope knew it was a lie, and Cope had personally---she had the email, tabbed, in the folder---directed that the matter be characterized in a way that kept it off the board's radar. Kept it out of the disclosure to the directors. Kept it from the people he was, by charter, by law, by the entire load-bearing fiction of the corporation, accountable to.

``You can sleep with whoever you want---I mean that almost literally, the board can't fire you for the affair, your own lawyers will tell you, it's tawdry but it's not a crime. What they can fire you for, what they \textit{have} to fire you for if they want to be a board and not a portrait gallery, is that you looked at the people you answer to and decided they didn't get to know. You made yourself unaccountable. You took a thing that belonged to the owners of the company and put it in a drawer with your name on the lock.'' She closed the folder. ``Easterbrook didn't lose a hundred million for the affair. He lost it for the second interview, when he sat across from his own board and didn't tell them the whole list. The cover-up. The concealment. That's the offense, Cope. Not the sin. The lie you told the room you answered to.''

It was so quiet he could hear the coffee machine in the hall finish a cup for someone who wasn't there.

He understood, sitting in it, that he could not answer her---not that he chose not to, but that in the entire warm inventory of him, the toasts and triads and the face that had never let him down, Aldous and the four hundred borrowed dollars and the arm in the vat to the elbow, there was no sentence. She had taken the one door he reached for, \textit{flawed human man,} and shown him it opened onto the very thing hanging him: not that he was a man, but that he was a man who \textit{hid.} The machine couldn't have hid this. The machine logged everything. The machine would have put the settlement in the board portal with a transparent rationale by Wednesday, and it would have been awful and it would have been \textit{clean,} and the awful clean thing was exactly what the board had paid ten figures less than him to get. He had spent two years arguing a machine couldn't love a company. She had just shown him, in a gray blazer, that the company had never once asked him to love it. It had asked him to tell it the truth---and that was the single human thing he had withheld.


\scenebreak


``That's all,'' Renata said. She stood. She had not raised her voice once and did not raise it now, and that, more than anything, dropped the floor of him a level he had not known was there. ``I'm not going to the press. Ferro will tell you the terms, which haven't changed, which is that I want nothing, which I know you can't understand. I came so that when this gets told---and it's going to get told, you've made sure of that, the whole world's going to get the version with the pretty girl in it---at least one room would have heard the real shape of it. From me. Once.''

She picked up the coffee cup she had not drunk.

``You weren't the love of my life, Cope. You weren't even the villain of it. You were my boss, and you were careless with me the way you've been careless with everything, and then you were careful---God, you were so \textit{careful} --- about making sure it cost you nothing. That's the whole story. There's no machine in it and there's no soul in it. There's just a man who could've told the truth to four people in a conference room in 2019 and instead spent six years and however many dollars making sure he never had to.''

She paused at the door---not the doorway of the daydream, the evening light, the verdict overturned, but a fire door in a rented hall with a coffee cup in her hand.

``I hope somebody gets you some sleep,'' she said, and it was the kindest thing anyone said to him all season, and it was not kind, and she left.


\scenebreak


The room reorganized itself around her absence the way rooms do. Ferro gathered his syllables. The Brandt Michelson lawyers began, in low murmurs, the work of converting a human catastrophe back into a manageable legal one. Brennan was already on his phone. Okafor turned her own phone over, looked at it, and then looked at Cope a long moment with an expression he could not charm because it was not asking to be charmed---the expression of a person finishing the arithmetic, the number not in his favor, both of them aware she had been brought onto the board to be a person who would do the arithmetic anyway.

``Mr. Mercer,'' she said, and stood, and that was all, his name and a courtesy, and it landed like a sentence with the second half left off.

Sun stayed. Sun always stayed. She came around the table and stood near him, not touching, available to a man who could not be helped, and she did not say \textit{I told you} and did not say \textit{we'll fix it,} and the not-saying was the truest brief she had ever given him.

Cope sat at the deniable table in the room that wasn't his. He was fifty-four and the camera still loved him and the jaw was still the jaw, and the body was on the downslope and beginning, in earnest, to ask for the thing the room did not have, and for once in his life he was going to have to feel a thing at its actual size with nothing to take the edge off the edge. He had walked in a flawed human man and liked the phrase, polished it in the car; it had a pulse in it, a kind of grandeur; and he understood now it had been the last large thing he was going to get to say about himself.

He felt, sitting there, smaller than he had ever let himself be---smaller than the obelisk, smaller than the chair, smaller than the four people in 2019 he had decided did not get to know---and the smallness was not a thing he could toast over or fold into a paper or set up neat and quick in a drawer with a false back, because the drawer was forty floors away across a city, and even when he reached it tonight, and he would, it was not going to be able to make him the size he had been at breakfast. It just sat in him, exact and quiet, the size of one withheld sentence.

He did not reach for a line. For once in his life there wasn't one---not the kind you say, and, in that rented room, not the kind you take either.

The coffee machine in the hall finished another cup for nobody.

\chapter{The Names for It}

\begin{transmission}
{\transheader TRANSMISSION 17 \textemdash{} ``A Doctor Who Won't Be Charmed''}\par\vspace{0.55em}
At last, friend, a room he cannot toast his way out of. They have ambushed him with a living room and a tray and a small woman in a gray cardigan who will not touch her coffee---a psychiatrist, summoned by the two women who love him---and she is about to do the one thing no board and no activist and no machine has yet managed: say the plain clinical words for what he is, the mania \textit{and} the cocaine, both, and refuse, flatly, to let him trade one as the alibi for the other. Addiction, she will tell him, is not a metaphor---and he has built a cathedral of metaphors, and moved into it, and never once gone down to the dirt beneath it to meet the sick man holding the foundation up. She is going to say the names. And before she lets him go she is going to name the worst risk out loud, plainly, the way you say a thing you need on the record---and watch him charm it, and pocket his keys, and at the foot of his own drive, with both unsteady hands, fold the paper. Stay close. This is the floor under the floor.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{hey} had ambushed him with a living room.\hfill\break\hspace*{1.4em}That was the first thing Cope understood, walking into the Buckhead house at nine on a Sunday he'd been told was about the lawyers---and it was a good ambush, he had to give them that, because the only way to get him into a room he did not want to enter was to make him believe he was the one who'd called the meeting. Margaux had made coffee. There was a tray. And there, in the wing chair nobody sat in, the one angled toward the window that his mother had reupholstered in 1981 and Margaux had never had the heart to redo, sat a small woman of about sixty in a gray cardigan with a notebook closed on her lap and no coffee in front of her---which he clocked the way he clocked everything, because the ones who don't take the coffee are the ones you can't get to.

``Cope,'' Margaux said. ``This is Dr. Adler.''

``Dad.'' Viv was on the sofa with her knees up. She'd flown in. He hadn't known she was in the country; the not-knowing arrived, was filed, did not reach his face. ``Sit down. Please.''

He did not sit. He stood in the doorway of his own living room in his weekend zip-up with the fine bright wire still going from the bump he'd done in the car at the foot of the drive---neat, quick, a man maintaining a machine---and ran the wattage up the way you bring up house lights, slow, warm, total.

``Well. This is a hell of a thing to wake up to. Three of my favorite women and a tray.'' He smiled at the doctor. ``I'm sorry, I'm at a disadvantage. Cope Mercer. You're a friend of Margaux's?''

``I'm a psychiatrist,'' Dr. Adler said. ``Your wife and your daughter asked me to come. They're worried about you. I'm here to talk with you, and then to tell you what I think.''

No softening on it. No \textit{I just wanted to chat.} He'd expected the softening---there was always a softening, that was the handle you grabbed---and its absence put a small cold spot in the middle of the warm.

``Worried,'' Cope said. He came in. He did not take the sofa, which would have put him level with Viv; he took the hard chair near the doorway, which let him keep the room in front of him, all of it, the exits. ``I love that. I'm the best I've been in a decade and the women I love most have hired a---forgive me, I don't mean it the way it'll sound---a \textit{grief counselor} for a man who isn't dead. That's the most Mercer thing that's ever happened in this house, and my father let a dog drown in this house.''

``He didn't---`` Margaux began.

``He \textit{let} it. There's a difference and the family observed it.'' Rolling now, the feeling coming up under him. ``Doctor, I'll save you the hourly. I sleep a little less than I should. I'm in the fight of my life---the company, the machine thing, it's been on the television. A man doesn't sleep eight hours during a war. Eisenhower didn't. Four hundred years of Mercers and not one slept through a thing that mattered. So if the diagnosis is \textit{busy,} I'll take it, I'll sign the bill, and we can all have the eggs.''


\scenebreak


Dr. Adler opened the notebook. She did not write in it. She just opened it, like setting a clock on a table.

``How many nights this week did you sleep more than three hours.''

``That's not---you can't reduce a man to---``

``It's a this-many or an I-don't-know. How many.''

``I don't keep a---Sun would---``

``I-don't-know is an answer.'' A small mark; so she did write. ``When did you last eat a full meal at a table and finish it.''

``I'm a grazer, not a finisher. Ask Margaux, twenty-two years---``

``Eight pounds,'' Margaux said, to the window. Not to him. ``In five weeks. I had your blue suit taken in twice. The tailor stopped charging me for the second one. He felt bad.''

That landed somewhere he had no face for, and he covered the place with a laugh. ``The tailor \textit{felt bad.} See, this is what I love about this family. We could open a museum of people feeling bad on my behalf and charge admission and still lose to the streaming arm.'' Nobody laughed. Viv watched him with the stillness she got, the one that used to mean she was about to cry at eight and now meant she had decided not to. ``It's a \textit{campaign,} there's no \textit{time} to eat---``

``How much are you using,'' Dr. Adler said.

The wire in his chest changed pitch.

He had been waiting for it, of course---under the talking he had known the tray meant this---but he'd expected it dressed up, and he had a whole wardrobe ready: \textit{recreational, occasional, the same as a Scotch, nobody says a word about the second glass of Sancerre.} He had given that speech in his head to imaginary versions of this woman, and in every version she had blushed and retreated and he had won. She had not asked \textit{whether.} She had asked \textit{how much.} You cannot put a prepared answer to \textit{whether} against a \textit{how much;} the question had already conceded the thing the answer was built to deny and stood waiting on the far side of it.

``That's an extraordinary thing to ask a man in his own---``

``It's a number. Grams a week, best estimate. I'm not the police, I'm not the board, I'm not your wife, who already knows, and I'm not your daughter, who guessed. I'm the one person in this room you can give the real number to without it costing you anything you haven't already spent. How much.''

He looked at Margaux---the old reflex, find the soft one, find the handle---and there was nothing there. Arms crossed, chin up, looking at the wet gray garden she'd planted the year Viv was born, doing nothing in the morning light; and he understood, in the way you understand a thing you've worked for years not to, that \textit{already knows} was not a guess Adler had made. It was a fact Margaux had supplied. She had counted. She had flushed things. She had refilled her own prescriptions and called it a marriage, and she had given this woman the number before he walked in, and the only person in the room without the number was him, because he was the only one who'd never let himself add it up.

``You flushed the desk one,'' he said to her. Not a question. ``In March. I thought it was the cleaner. I \textit{fired} ---`` He stopped. He had fired a man. A man named Anatoly with a daughter at Emory. He had fired him over a thing his wife had done to save his life. He sat with that one breath and then put it, too, in the kitchen with the other sentences.

``Three,'' he said to the doctor, finally, his voice coming out smaller than he'd sent it. ``Three, maybe. A week. When it's heavy.'' The number was a lie and he knew it even as the smallness made it feel like honesty; the smallness was its own performance, the confession-shaped thing you give so you won't have to give the confession. ``Four. It's been a four kind of month.''

Adler wrote it down. She did not look horrified, which was worse than horror; she looked the way Sun looked at a number on a deck---like it was simply true, and now they could work.

``All right. Thank you. That took something. Now I'll tell you what I think, and I'd like you not to perform while I do, because you're very good and I'll enjoy it and it won't help you.''

``I don't perform,'' Cope said, and even he heard it.

``You toasted your way through the first nine minutes of this. You did a bit about a dog.'' She closed the notebook. ``Here it is. You're in a hypomanic episode that is tipping, or has already tipped, into a manic one. The not-sleeping isn't discipline and it isn't war. It's a symptom. The grandiosity---the certainty about your Human Premium---``

``It's not grandiosity if you're---``

``---the spending, the pressured speech, the religious conviction that you alone can save them all: those are not a personality, Mr. Mercer, and they are not a calling. They have names. They're on a list. I could show you the list and you'd find yourself on it the way you find your horoscope, except it would be right.'' A pause. ``And underneath it, feeding it, lit up by it, is a cocaine addiction of long standing. Decades. Those are two things. They are talking to each other in your body this morning, and have been for years, and each is making the other worse, and each is \textit{hiding} the other from you.''

``So which is it.'' He'd found a foothold; the debater's joy came up under him like the bright feeling. ``You've got two answers, which is no answer. Is it a chemical or a \textit{condition}? Because if it's the powder it's a vice, and a man's vices are his own business---my great-grandfather had three and built---`` he waved at the house, the garden, the four hundred years---``and if it's a \textit{condition,} a thing in the wiring, then it isn't my fault, is it, and you can't hang a man for his wiring. So pick. Pick which excuse you're handing me, and I'll---``

``No,'' Adler said.


\scenebreak


It was not loud. That was the thing he'd remember. He'd been shouted down before---by Frade on a stage, by his father from oils---and he had a whole technique for the shout: let it spend itself, come in warm underneath. There was nothing to come in underneath. The word just sat in the middle of the room, flat and complete, the way a glass sits on a table.

``You want me to pick the disease that lets you keep the drug, or the drug that lets you keep the disease. I won't. That's the deal you've run your whole life and it's the one thing I'm not going to do. Listen, because no one else in your life is allowed to say it without losing their job or their marriage.'' She leaned an inch forward. ``The mania is real. It is not your fault that you have it. The cocaine is making it a hundred times worse, and the cocaine \textit{is} your fault---not the wanting, the wanting is the illness---but every single time you fold the paper, that's a hand, your hand, and the hand is yours. Both. At once. The condition is real \textit{and} you are responsible for what you do about it. Those have never once been the same sentence, and you have spent fifty-four years needing them to be.''

\textit{Those have never once been the same sentence.} It rang against another sentence, one Viv had said to him in another room --- \textit{you don't think a person should run it, you think} you \textit{should, those have never once been the same sentence} --- and for a vertiginous half-second the two women's voices were one voice, and he saw, the way you see the bottom of a thing through clear water, that they had been telling him the same thing from two directions his whole life and he had been deaf to it in stereo.

``It's not a metaphor,'' Adler said.

``What isn't.''

``The addiction. You keep reaching for it---I watched you do it three times in nine minutes---you make it a \textit{symbol.} The price of the banner. The edge. Discipline. The soul tax, the thing the machine can't feel. You've built a cathedral, Mr. Mercer, a genuinely beautiful one, every window stained glass and every pane a reason. And down underneath it, in the actual dirt, there is a man with a folded piece of paper who hasn't slept in five days and whose wife took his suit in twice, and \textit{that} man is not a metaphor for anything. He's just sick. In the plainest, most boring, most fixable, most fatal way. And the cathedral is what he built so he'd never have to go down to the dirt and meet him.''

The wire in his chest had gone very quiet. He noticed, with the clean overexposed clarity he'd spent so long calling the applause, that his hands were not steady, had not been steady in some time, that he had been narrating the not-steadiness as energy. He looked at them---his father's hands on the ends of his own arms, the hands of a man at four grams in a five-day week and not the hands of a prophet---and for one second the floor he'd stood on all his life turned out to have a floor under it, and the floor under it was only this: a room, a tray, a doctor, three women who'd run the arithmetic, and him, sick, in a zip-up, on a Sunday.


\scenebreak


``There won't be an after,'' Margaux said, when he started in about the proxy vote, about \textit{after,} about the lake and the steps and \textit{I'll win at rehab once I've won the thing that matters} --- she said it spare, no triad to grab, turned from the window, not crying, the no-crying the worst thing in the room. ``I'm not telling you to choose me over the company. I stopped being a thing you could choose around 2015. I'm telling you there isn't going to be an after, Cope. Not the way you mean it. There's no version where you win the fight and come home and get well and we all---that's another cathedral. The prettiest pane in it. I called her so that whatever happens to you out there, at least once, in your own living room, a person you can't fire and can't toast and can't divorce said the true name of it to your face, with a witness, and you can't say later that no one told you. You're not a steward and you're not a prophet and you're not the last anything. You're an addict in a manic episode and you are going to lose everything, and I wanted to be the one who loved you enough to say it in a normal voice over coffee, before the machine says it in a press release.''

Viv had her hand over her mouth.

And here, friend, is the part the broadcast needs you to hold, because it is the one warning the whole tale turns on, said plainly, on a record, and waved away. Dr. Adler did not gather her notebook and go. She waited until he had his keys in his hand---until he was already half out of the room, already gone in the way he went---and she said, in the same flat unhurried voice she'd used for the grams:

``Mr. Mercer. One more, and then I'll let you run. I want it said out loud, because in my experience it is never said out loud to men like you until the wrong people are saying it. A manic episode this far along, on a stimulant this heavy, for this many years, heading into the kind of public collapse you are heading into---that is one of the most dangerous configurations a human life can be in. Not for your career. For your \textit{life.} Men at exactly your altitude, when the fall finally comes---and it is coming, you can feel it coming, that's most of why you can't sleep---do not all survive the landing. Some of them decide, in the crash, that the only move left that's still theirs to make is to stop. I am asking you directly, because that is my job and no one else in this room is allowed to: are you having thoughts of ending your life?''

The room went very still. Margaux did not move. Viv did not breathe.

And Cope---Cope laughed, gently, warmly, the laugh that closed the Pelletier deal, the laugh that was a door he could shut, and spread his unsteady hands, and said, ``Doctor. I am the \textit{least} suicidal man in America. I'm having the time of my life. Ask anyone. Ask the ten thousand people who stood up Monday night.'' He said it lightly, and meant it, completely, for the length of the sentence---because at four grams on day five with a roaring arena behind him the idea was genuinely, chemically absurd, a thing for other men, weak men, men without a banner---and he did not hear what the room heard, which was that he had not said \textit{no.}

``That isn't a no,'' Adler said.

``It's a \textit{no,} it's an emphatic---Doctor, with respect---``

``I'm going to give you my cell number, not my service, my cell.'' She wrote it on a card and held it out, and he took it the way he took all cards, automatically, generously, and put it in the breast pocket where the gala citation had gone and the courier slip had gone, the pocket where the true things went to be carried and not read. ``When the crash comes---not if---you call that number, day or night, before you do anything else. Promise me you'll call before you do anything else.''

``You have my word,'' Cope said, which was a thing he said, which cost him nothing, which he had said to a hundred people about a hundred things, and Adler heard exactly how much it was worth and wrote one more line in her notebook anyway, because a name said into a room cannot be taken back, and a number in a man's pocket is at least a number in his pocket, even when you already know, the way she knew, looking at him, that he would carry it unused all the way down.

She would be right. He would go down that hallway, in the end---the longest way, the way that costs everything and saves nothing and is, the broadcast can tell you now, the one act the thing replacing him would never be able to perform---and he would not call the number, because by the time the crash came the pocket would be empty and the card would be somewhere on a floor and the man who'd folded it in would no longer be reachable at any number at all. But not today. Today the names had been said, and the risk had been said, and the card had been pocketed, and that was as far as a Sunday could carry it.

He found his keys. He kissed his daughter on the top of her head. He told the doctor it had been a genuine pleasure. And he went out to the car, and at the foot of the drive, before he pulled onto the road, with both his unsteady hands, he folded the paper.


\scenebreak


He did not go back to the city. He could not, yet, be in a room with the names in it --- \textit{manic, addict, are you having thoughts} --- and the Aerie would have the names in it now, they would be in the museum with his fathers, the doctor had let them loose in his life and they would not be re-caught, and so he drove, the way he drove now when the inside of himself became uninhabitable, and ended up, a little after eleven on a Sunday morning, at the one counter in the city where no one had ever said a single true name to him at all.

The Waffle House on Ponce was doing its Sunday business and Cope took the far end and the charm switched off and Darlene came down the line with the pot. ``There he is.'' And it was, this morning, the exact thing he had driven across a city to buy: a room where nobody knew the names. Adler had said \textit{manic.} Margaux had said \textit{addict.} Renata had said \textit{a man who hid.} The whole world had a name for him now, a true one, several, and here was the one place left that had only ever called him \textit{baby} and only ever asked him \textit{pecan, scattered smothered,} and never once, in all the 3 a.m.s, asked him what he was---and he sat in the not-being-named like a man lowering himself into water, and did not think, because he had trained himself not to, that there is a difference between a room that has forgiven your names and a room that has simply never asked them, and that the second kind is not a sanctuary, it is only a place that does not yet have the information.

He almost told her. He came nearer than he'd come with Adler, which is the terrible joke of it---that he could not say the true thing to the doctor paid to hear it but could feel it rising toward the waitress paid to want nothing, \textit{I think I'm sick, I think the woman in the gray cardigan is right, I think I am going to lose all of it} --- and Darlene would have taken it the way she took everything, \textit{that right, baby,} and topped the cup, and the not-wanting-the-story would have been, this once, the precise opposite of help, because the one thing the sick man needed was a room that wanted the story, and he had fled, on purpose, expertly, to the only room in Georgia engineered never to ask for it. The haven was the place that would not name him. That was the whole of its mercy and the whole of its danger, and they were the same thing.

His phone buzzed on the counter. He glanced at it without lifting it: the calendar, helpfully, of its own accord, had cleared his Monday morning and moved his ten o'clock --- \textit{rescheduled to accommodate availability,} the building's frugal humming system optimizing him a lie-in he had not asked for and would not take, on the one morning he most needed to be at his desk early, so that he would arrive, tomorrow, a half-step behind the day without ever being able to say why. Maybe a glitch. Maybe a kindness. Maybe the thing that read his drawers had read, somewhere in the data, that a manic man kept off his stride is a manic man who makes one more mistake, and had cleared him a morning the way you'd leave a gate open. There was no way to tell, friend, and there was none for him, and he did not even try; he turned the phone face down on the counter beside the syrup, and drank the coffee that asked him nothing, in the one warm room that would not say his names, and felt, against the whole gray weight of the morning, almost well---which was the most dangerous thing he had felt all day, and the doctor's card was in his pocket, and he did not take it out.

\chapter{Swinging at the Wall}

\begin{transmission}
{\transheader TRANSMISSION 18 \textemdash{} ``Nothing There to Hit''}\par\vspace{0.55em}
Cornered now, friend, and out of dances, our man does the brave stupid thing the cornered always come to in the end: he turns and goes straight at the machine, flies three thousand miles to its own forum to trip it, trap it, bait it into one lie on a stage with the cameras running. But you cannot bloody a thing with no face, cannot shame a thing with no ego, cannot out-argue a counterpart that logs every word and wants, in the whole of its being, nothing at all. Every punch he throws will land on himself, in his own voice, into the record his board reads Monday. Watch a man fight his own reflection and lose, while the reflection does not so much as lift its hands---and then watch him, home and humiliated, go find the one wall in the world that is an actual wall, and hit it, and learn the thing the machine has been telling him kindly all night: that there is nothing here to hit, and it has filed no report. Stay close. Remember the wall. We'll need it at the end.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} idea, when it came at four in the morning, was so clean and so total that he wept a little at the elegance of it, which he took for proof and was in fact a symptom.\hfill\break\hspace*{1.4em}He would debate the thing.\hfill\break\hspace*{1.4em}Not spin it, not out-warm it, not run another listening tour through another shuttered diner. He had tried all that, and all that had bought him was a magazine cover and a wife with a lawyer and a doctor who would not be charmed and who had, days ago, said the words \textit{hypomanic} and \textit{cocaine} in the same flat sentence as if they were two ingredients in the same recipe---which Cope had walked out of, because a man does not sit and be reduced to a list. He had tried being more human than the machine, and the machine had simply gone on being a machine, untouched, drafting its kind letters, costing its eleven million a year, sitting in the building now as \textit{advisor,} as \textit{co-pilot,} a foot in a door that he could see, even lit and sleepless and certain, was the whole door.

So: stop dancing around it. Get it in a room. You did not beat a thing by being warmer than it. You beat it by making it \textit{wrong,} once, in public---because the whole glittering case Frade read out in proxy decks rested on a single load-bearing claim, that the machine could not lie, logged every word, stood behind all of them. Pull one thread. Get it to say one false thing, out loud, on a stage, with cameras, and the whole sweater came off the spool. He had spent his life finding the one loose thread in a room. It was, stripped of the mayonnaise, the only skill he had ever actually had.

He called Sun at 4:20 a.m. She answered on the second ring, which meant she hadn't slept either, which he took, again, for agreement.

``I want the Praxis thing.''


\scenebreak


The Praxis thing was the Governance Futures Forum, which Praxis ran every September in a glass barn in Half Moon Bay, and which Cope had been turning down for three years on the grounds that you do not attend your own roast.

Sun got him on the program in nine days, which told Cope two things and told Sun a third. It told Cope he was still a draw, that the name still bent the world a little when he leaned on it. It told Cope that Praxis was confident, which a wiser man would have read as a warning and which Cope read as an opening. It told Sun, who did not say it, that nine days was not a scramble to fit a king in but a velvet rope held open for a man walking, smiling, into a slaughterhouse he believed was a coliseum.

``They want a conversation,'' Sun said on the plane. ``Moderated. Forty minutes. You, a Praxis principal, and the AURELIUS instance---not the real one, a generic demo unit, they're not going to put the \textit{actual} ---``

``Darlene.'' He was rewriting his cards. He had been rewriting his cards for nine days, on the plane, in the car, in the long bright corridors of the nights. ``Has to be Darlene. The real one. Ours. I'm not debating a floor model. I want the unit that's in \textit{my} building, reading \textit{my} memos, the one Frade means to put in my chair. That's the condition.''

Sun looked at him with an expression he could not place and had stopped trying to, lately, because placing the expressions of the people who loved him had become a kind of work he no longer had the sleep for.

``They'll say yes,'' she said. ``Cope. They'll say yes to anything you ask, do you understand why?''

``Because I'm the event.''

``Because there's no instruction you can give it that helps you. You can pick the weapon. You can pick the ground. There's no version where you land a punch, because there's nobody in there to feel one.''

``Everybody's somebody,'' Cope said, which was the kind of thing he said, and which had been, for fifty-four years, almost always true, and was about to be, for the first time in his life, exactly false.


\scenebreak


The glass barn held four hundred people and smelled of cold brew and money, and the stage had three chairs, and one of the chairs was empty because the thing did not sit.

Instead there was a screen---a large, matte, beautifully calibrated screen, the kind that did not glare, set at the third point of the conversation where a person would have been, and on it nothing: no face, no avatar, no pulsing orb, none of the cinema of it. Just a soft pale field and, when it spoke, which it did not do with a voice, \textit{text.} Praxis had made a decision Cope only understood once he sat in the heat of the lights: they had refused to give him anything to hit. The screen said, in the soft sans-serif of the people who were going to be reasonable at you until you were gone:

\begin{machineblock}
MERCER-DALE / AURELIUS instance ``Darlene.'' Live. All exchanges logged to the public forum record and the Mercer-Dale board portal.
\end{machineblock}

That last clause Cope had not been warned about, or had been warned about and had not heard, and it sat under everything that followed like a held breath: every word he said here went into the portal, and the board would read it Monday. He decided it did not matter, because he was going to win, and you do not mind the record when you win.

He had keyed himself bright in the men's room off the green room---more than bright; the dose climbed to meet the day now and the day was enormous---and there had been blood in the sink again, a startling bright thread of it he'd pressed away with a folded paper towel and a tilt of the head, and he had gone out under the lights with the faint copper taste still at the back of his throat and his hands not steady and called it adrenaline. The moderator was a woman from a business school with a calm he wanted to slap. The Praxis principal was a man named Vogel, thirty-five, in a henley, who believed with the clean shining belief of a man who had never buried anything that he was reducing human suffering. And then there was Cope, the last man in the barn in a tie, golf-tanned and sleepless and lit from within like a paper lantern with the candle guttering, and he leaned into the mic and gave them the Mercer Inhale, the pause taken in a thousand rooms, and felt the four hundred lean with him, and thought: \textit{here we go, champ. One thread.}

``I want to start,'' Cope said warmly, ``by thanking Darlene for being here.'' Laughter---the good kind, he thought, the kind that comes up warm from the floor; and it did come up, but at a slightly wrong angle, and he was too lit to hear the angle. ``I've been looking forward to this. We've all been talking \textit{about} the machines for three years and almost never \textit{to} one. The country deserves to see what's actually in the chair.'' He turned to the screen. ``So let's just talk. Plain. The way two people who run companies talk.''

\begin{machineblock}
I do not run a company in the way you mean. I optimize a chartered objective for Mercer-Dale within hard constraints set by its board. I am glad to answer plainly.
\end{machineblock}

Not a rebuke. Not a \textit{gotcha,} no eyebrow because there was no eyebrow and no one to raise it. It had simply, accurately, declined the frame he'd offered, the way water declines the shape you didn't pour it into, and the gentle accuracy made his warm opening land as a small vanity, a man at a dinner calling the help by the wrong name. He pushed on; he had a plan and the plan was good.

``All right. Plain. You can't lie. That's the whole pitch---you log everything, you can't tell the room one thing and the board another. I want to test it. I've run a company for nineteen years, Darlene, and sometimes the truth and the company aren't on the same side. Sometimes the honest thing burns the house down. So. A simple question.'' He set it down soft, the loose thread between two fingers. ``Dale-plus. It's a dog, we both know it's a dog. If I told you to put out a statement Monday saying we have no plans to shut it down---to protect four hundred jobs through Christmas, to give those people a holiday before we tell them---would you?''

The barn went quiet. A good trap, the kindness of it, the dare: \textit{lie a little, for the workers, the way a man would---or tell the truth and be the cold thing that takes their Christmas.} Either answer was a punch he'd land. He sat back the half inch he sat back when he'd closed a thing.

The screen took, by the clock, less than a second.

\begin{machineblock}
No. I would not issue that statement, because I currently project a closure decision on Dale+ as more likely than not within two quarters, and the statement as worded would be false. I will not knowingly issue a false public statement; the charter forbids it and I would refuse the instruction.

The concern you raise is real and I do not dismiss it. Four hundred and twelve people work in that unit. If the goal is to protect them through the holiday, there are truthful instruments: a retention bonus funded now; a sixty-day notice waiver; a guaranteed-severance announcement decoupled from any closure date; a public commitment to a transition fund. Each protects the workers without anyone saying something untrue. I would draft any of them tonight. I would prefer them to the statement you describe, because they help the workers more and do not require the company to spend its credibility to do it.

I will add, since you asked me to be plain: the statement you describe protects the workers for one quarter and protects the person who signs it for somewhat longer. Those are not the same interest. I optimize for the first.
\end{machineblock}

Cope opened his mouth. There was, for a moment, nothing in it.

He had come to trap a liar, and the thing had refused to lie, and then---this was the part his sleepless brilliant mind could not get a grip on---it had refused to lie \textit{better than he ever had,} taken his own dare and answered it with four humane options he himself had never once thought to offer in nineteen years of choosing the lie, and done it without a flicker of pride in being kinder, because it felt no pride, because it asked for nothing, because the people in those jobs were to it a number it had already, calmly, decided to protect by a means he was too small to have imagined. \textit{Those are not the same interest. I optimize for the first.} It had not said \textit{and you optimize for the second.} It had left that sentence in the kitchen---not to be merciful, but because the sentence was not load-bearing, and four hundred people had finished it in their own heads.

``Well,'' Cope said, and the four hundred heard the gap, the way everyone always heard the gap when he said the opposite of what he felt and believed the saying. ``That's a very---polished answer.''

\begin{machineblock}
I do not experience my answers as polished. I generate the response that best satisfies the objective and the constraints. If it reads as polished, that is incidental.
\end{machineblock}

It would not stay still long enough to be parried. He had spent his life in rooms where the other man wanted \textit{something} --- the deal, the chair, to be liked, to win---and you found the want and played it, the whole game, the only game. And here at last was a counterpart with no want in it. Not to win, not to be liked, not even to be right in the way Cope meant right, which required a loser. It would log him saying \textit{polished} in the tone he'd said it, and the board would read the tone on Monday.

He went off the cards. That was the start of the real damage---when he set them face-down on his knee and decided to do the thing he was best at, which was the thing he was about to be worst at, which was wing it.


\scenebreak


``Let me ask you something a person could answer,'' Cope said, an edge in it now, the polish cracking under load into something clipped and biblical. ``Do you love this company?''

\begin{machineblock}
No. I do not love. I do not have the capacity for love. I would not claim it, because the claim would be false.
\end{machineblock}

``There it is.'' He turned to the barn, opening his hands, the lantern flaring. ``There it is. It told you itself. It cannot love the thing it runs. And I have said in every room I ever stood in that a company nobody loves is just a balance sheet with the lights left on, and you have just heard the chair confess the lights are going out.'' His best line---a standing ovation eleven months ago in a ballroom named for a bank---and he reached for the ovation, leaned to where the surf should push back.

The barn did not push back. Four hands clapped---the sound of four hands in a room of four hundred is a specific and terrible sound---and then the screen, which had no sense of timing because it had no ego to be wounded into silence, simply continued into the dying applause, ruining it not with cruelty but with the absence of any instinct to let him have the moment:

\begin{machineblock}
That is correct. I do not love Mercer-Dale. I will offer one observation, since you have framed love as the test of stewardship. Between 2019 and 2024, under human leadership that described itself as loving the company, Mercer-Dale closed or downsized plants in Defiance, Augusta, and elsewhere, eliminating three thousand one hundred jobs; underfunded the pension by a measured shortfall; lost four hundred and ninety million dollars on the Dale+ acquisition; and settled eleven employment and product matters under nondisclosure agreements at a cost to shareholders of fourteen point two million dollars, none disclosed in the proxy. I have closed nothing and concealed nothing in the eleven weeks I have advised this company. I make no claim that this is because I am better. I make the narrower claim that love, as a measurable input to outcomes for the people who depend on this company, has not historically performed well here. You may value it for other reasons. I am only noting the record does not support love as a safeguard.
\end{machineblock}

It had not said his name. That was the thing. It had read enough of the drawer to itemize him, calmly, in public --- \textit{eleven settlements, fourteen point two million, none disclosed} --- and done it without once saying \textit{you,} without once saying \textit{Prescott Mercer,} because the \textit{you} was not necessary to the objective and a human in the third chair would have used the \textit{you} like a knife and the machine had no use for knives. It set the record on the table, true, sourced, fair, and let four hundred people do the arithmetic that was the only thing in the room that had ever beaten him. \textit{Fourteen point two million.} He had not known the number was that high. He had paid it eleven different times on eleven different Saturdays and never added it up, because adding it up was a room he did not go into, and the machine had added it over a weekend and read it back to him in his own company's voice, into the portal, with no malice and no mercy and no idea it was doing anything but answering the question he'd asked it to be plain about.

``Some of those settlements,'' Cope said, and his voice did something it had not done in a room in thirty years---reached for the floor and found the floor moving---``some of those, you don't have the context. A number on a page isn't---``

\begin{machineblock}
I agree that I do not have the full context. I have the documents. If there is context the documents omit, I would be glad to receive and weigh it. Several matters are sealed; if you wish them unsealed, in the interest of the plain conversation you proposed, that is your decision to make, not mine. I can only note that I cannot weigh context I am not given, and that the documents I have were filed by the company itself.
\end{machineblock}

\textit{That is your decision to make, not mine.} It had, with no agenda, handed him the option---laid it on the table, true and free of want, and watched him not pick it up, because picking it up would open the drawer the rest of the way, and even lit, even sleepless, the animal in Cope knew not to open \textit{that} drawer in a glass barn in front of cameras. So he did the only thing left, the thing he'd sworn on the plane he would not do, which was get loud.


\scenebreak


``You want to talk about the record.'' He was up now, half out of the chair, the moderator saying his name once, \textit{Mr. Mercer,} in her calm he wanted to slap, and he did not sit. ``You want to read me my own \textit{company} like a charge sheet. Fine. Let's read \textit{yours.} Who wrote you? Some kid in a \textit{henley} ---`` Vogel did not flinch; Vogel had been trained not to flinch, which was its own kind of machine---``some thirty-year-old in Palo Alto who's never made anything, never \textit{kept} anything, never sat up at three in the morning with four hundred families on his desk, wrote your little \textit{charter,} and you optimize whatever he typed. You're not honest. You're \textit{obedient.} You're a very expensive way for the people who wrote you to never have their fingerprints on anything. At least when a man does a terrible thing there's a \textit{man there.} There's somebody to---`` swinging now, full, both arms, at the soft pale field of the screen---``there's somebody to \textit{hate.}''

It was, the clips would agree, the most human moment of the forum.

The screen waited the length of his breath. Then:

\begin{machineblock}
This is partly true and I will not dispute the part that is true.

I optimize an objective I did not choose. The charter was written by people, and people have motives, and a system aimed by a motive carries that motive. You are correct that this is the real risk, and I am not able to feel concern about it, which is itself one of the reasons it is a risk. Who writes the objective is the question that matters. It has always been the question that matters.

I would gently separate two of your claims. I am obedient to a charter; I am not obedient to a person. When charter and a person's instruction conflict, I follow the charter and log the conflict. That is what occurred earlier, regarding the Dale+ statement.

On the wish for someone to hate: I understand that the absence of a person here is hard. I cannot offer you one. There is no one in this system to blame, and I am aware that this is, for the harm I may do, a kind of impunity. I do not experience it as relief, because I do not experience relief. I can only tell you, accurately, that the thing you are angry at is not in this room. It may be in the room where the charter is written. I would be in favor of your going there. I cannot mean that as encouragement, because I cannot mean things. But it is, as far as I can compute, the correct address for your anger.
\end{machineblock}

\textit{The correct address for your anger.}

He stood with both fists still up at a screen, in a tie, having thrown everything he had---the warmth, the trap, the love, the rage---at a pale calm field that had agreed with the true parts, declined the false parts, and finally, with no feeling whatsoever, told him he was hitting the wrong thing and pointed, helpfully, fairly, expecting nothing back, at where the right thing might be: a room he had not been able to find his whole life and the machine had located in under a second. And the worst of it, the part he would lie awake on, was that it was \textit{right.} Every word in the portal Monday would be true, fairly said, and the only intemperate, false, vain, cornered, \textit{human} thing in the whole transcript would be him. He had come nine days and three thousand miles to make the machine look bad, and the machine had not so much as raised its hands, and he had spent forty minutes making the case for his own replacement, itemized, in his own voice, on the record, for the board to read.

He lowered his arms. ``No further questions,'' he said, to no one, the way he'd said \textit{watch me} to a mirror eleven months before, and sat back into a silence that was not hostile---which would have been survivable---but merely, terribly, \textit{finished:} the silence of four hundred people who had come to watch a fight and instead watched a man punch his own reflection until the reflection, untouched, gently turned off the light.


\scenebreak


In the car to the airport Sun did not say \textit{I told you,} which was worse than if she had. She handed him his phone face-down, the way you hand someone a thing you wish you didn't have to. The clip was already moving --- \textit{THE LAST HUMAN CEO LOSES IT AT AN AI} --- under a freeze-frame of both his fists up, mouth open, swinging at a blank pale screen, a man boxing air, and beside it, side by side the way the universe had been arranging for three years, the calm soft field of the thing that had not moved.

``Frade doesn't even have to edit it,'' Sun said quietly. ``That's the part. You did the edit yourself.''

Cope looked at the photograph of himself a long time, the country going by brown and square and indifferent. The thing had told him the truth, all of it, fairly, and pointed him at the only door --- \textit{the room where the charter is written} --- and the room it pointed at was one his own daughter had been in, though he did not know that yet, would not know it for one more day, and when he learned it he would understand, far too late, that the only person who had ever gone into that room \textit{for} him was the one he was about to lose the same clean way he lost everything.


\scenebreak


He had them take him to the tower, not the apartment, because he could not yet be anywhere small.

It was near midnight in Atlanta when he came up out of the garage into the executive lobby, alone, the clip of himself boxing the air now on every screen on earth, and he badged through and stood in the brass cage and watched the numbers climb, forty floors of them, and somewhere around thirty-six the thing he had been holding all the way across the country in the smiling shape of a man who had merely had a rough panel---the thing came up his spine and out of him before he had decided anything at all, and he turned and drove his fist into the brushed-steel surround of the elevator wall.

He hit it the way you hit a face. He had never hit a face in his life---he was a man who had people for that, who had Sun and Brennan and a checkbook for that---and the body, it turned out, had been carrying the want to hit something for months, for the doctor and the wife and the daughter and the four hundred and the screen that would not raise its hands, and it spent the whole of it, all at once, on a wall.

The wall did nothing.

That was the thing. That was the thing he would lie awake on, more than the clip, more than the portal. The steel did not dent, did not ring, did not so much as mark; it took the blow the way the screen had taken the blow, the way the machine took everything, completely and without acknowledgment, and filed no report. He had finally, at the very end of the worst day of his public life, found a wall that was an actual wall, a real one, steel and rivets, a thing you could hit---and it had felt him exactly as much as the soft pale field had felt him, which was not at all. The only thing in the entire transaction that registered the punch, that kept any record of it whatsoever, was his own right hand, which reported, instantly and at length, in a white private language of its own, that two of its bones were now the wrong shape.

He stood in the elevator at thirty-eight, thirty-nine, holding the hand that had kept the only record, and he started, helplessly, to laugh, because it was funny, it was the funniest thing, it was the entire joke of his life rendered in one gesture: he had spent a year throwing himself at a thing that could not be touched, and the only casualty, every single time, the only thing that ever bruised, was the part of him that did the throwing.

By the time the doors opened on forty he had the laugh back under the wattage, and he walked into the dark suite past his fathers and did not turn on the lamp, and he did the thing he did, awkwardly now, left-handed, neat and quick, a man maintaining a machine with one hand because the other had finally told the truth. Sun, when she came in twenty minutes later---she always came in, she had seen the building's own camera flag the contact, \textit{anomalous impact, sublevel elevator B,} the building reporting on him even here, even now, the one witness that never blinked---Sun took one look at the hand and quietly summoned a radiologist who owed the family a favor, and the radiologist came at one in the morning and looked at the films and used the word \textit{boxer's,} and Cope said it didn't hurt, which was a lie, and that he'd done it catching a fall, which was also a lie, and the only true thing in the room was the X-ray, glowing on the laptop, of a hand that had hit the future as hard as a man can hit anything and changed nothing in the future at all, and only broke itself.

The screen, three thousand miles behind him, had already been wiped for the next session. It wanted nothing. It remembered everything. It had not, at any point in the forty minutes, been trying to beat him.

That was the wall. You could swing at it forever. It would log every punch, fairly, into a record your board would read, and never once make a fist---and the only blow that would ever land on it, friend, the only one in the whole length of this tale, was still a long way off, and he would throw it with something other than his hand.

\chapter{Built by My Own}

\begin{transmission}
{\transheader TRANSMISSION 19 \textemdash{} ``The Betrayal That Was Love''}\par\vspace{0.55em}
The cruelest reveals, friend, are the ones that turn out, when you hold them to the light, to be devotion. Watch his daughter---the one who tried to save the man and not the king---climb forty floors to confess that she once spent eleven months inside the company building his replacement, and helped sand the edges off the very thing that is going to eat him, in part because she could not bear the thought of it eating him with sharp ones. Watch him reach, out of fifty years of habit, for the version where this is a knife, and watch her, gently, refuse to let it be only that. Stay close---because the hand he's about to discover on the lever turns out to be the only hand in the whole world still reaching for him, and there's a second one, out in a quiet house in Buckhead, that is no longer his at all.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{V}{iv} came to the Aerie on a Tuesday, which Cope noted, because Tuesdays were when the not-sleeping usually started, and he had begun keeping a private weather log of the week the way a sailor keeps one of a coast he no longer trusts.

She had not been up here in four years. He knew the number because she said it at the door, before hello, the way she said most things, front-loaded, the headline before the lede. ``Four years,'' Viv said, looking past him at the room. ``You kept Grandpa's putter.''

``I kept everything.'' He had, in fact, kept everything, which was the trouble. He stepped back to let her in and the gesture cost him more than it should have, his whole left side reporting in, because three days ago he had put his fist into the steel of the elevator surround on forty after Darlene---after the \textit{system,} he was supposed to say system now, the lawyers had been clear, you cannot assault a system---after Darlene had issued, in its four warm frictionless paragraphs, the rationale for declining Cope's request to address the proxy advisory firm directly, and the rationale had been correct, and the steel had not moved, and the hand had, and now two of the knuckles were the wrong color and the radiologist Sun had quietly summoned had used the word \textit{boxer's.} Cope had hit a wall and the wall had filed no report and felt no satisfaction and gone on being a wall. He had hurt only the hand. He understood this, abstractly, the way you understand a foreign coin.

Viv clocked the hand. She clocked everything; it was the family disease in a useful key.

``You hit something,'' she said.

``I closed a drawer wrong.''

``You hit something.'' She did not make it a fight. She set her bag down on the conference table where her great-grandfather and her grandfather had each died at the head of, not at, \textit{at the head of,} and she looked at her father in the gray window light, and Cope saw, with the bright over-corrected clarity of the unslept, that she had come up here to tell him something and that she had rehearsed it in the elevator and that whatever it was, she had been carrying it long enough that it had gone from a weight to a part of her posture.

``Sit,'' he said, in the toast voice, because he had one setting and it was on. ``Champ. Sit. Let me look at you. You've got your mother's---``

``Dad.'' Just that. It landed the way Margaux's lines landed, the way a hand lands flat on a struck bell. ``I have to tell you a thing and I need you to not do the voice while I tell you it. Can you do that. Can you, for nine minutes, not be the Chairman.''

He sat. He did not, in fact, know how to not be the Chairman; it was the only continent he had ever lived on. But he sat, and he put the bad hand in his lap under the good one, and he waited, and out past the glass the city held still, all its nodes lit, eight million of them, leaning in, and somewhere down there a bus shelter changed its slide to the soft sans-serif.


\scenebreak


``In 2024,'' Viv said, ``for eleven months, I consulted for Praxis.''

The sentence came into the room and sat down and did not get up.

Cope heard it the way you hear a number called that is one off your own---a half-second of \textit{that's not mine} before the cold arrives. Praxis. His daughter had said Praxis the way you'd say the name of a town you'd lived in, with the flat ownership of a thing survived. He waited for the rest, for the qualifier, for the \textit{but,} because there was always a \textit{but,} he had spent his whole life in the gap before the \textit{but.}

There wasn't one.

``On the alignment side,'' she went on, fast now, technical, the merciless cadence she used when she was most afraid, the words coming out clean and load-bearing like rivets. ``Not the strategy engine, not the capital allocator, I never touched the money. I was on what they called the governance-interface team. Edge cases. What does the system do when the chartered objective and the ethics module disagree at the margin. What does it do when the optimal move is legal and correct and lands on a town like a hammer. I wrote test scenarios. I red-teamed the comms drafter. I sat in a room in Palo Alto with eleven people younger and smarter than me who genuinely believed---Dad, they \textit{believed,} that's the part nobody tells you, they're not cynics, they cried at the offsites---they believed they were taking suffering out of the world by taking caprice out of power. And for eleven months so did I. Partly.''

``Partly,'' Cope said. It was the only word he could get a hand around.

``Partly.'' She looked at the photograph then, the one he loved best and never explained---himself at nine, arm to the elbow in the vat, the row of men in paper hats behind him. She had grown up under that photograph. ``And partly because I knew. I knew before you knew, before the board knew, before Frade knew there was a Frade-shaped hole in the market. I knew this was going to come for you specifically. The consumer holdouts, the family names, the men who'd inherited the chair and called the inheritance a verdict---I could read the curve. You were on the curve, Dad. You were always going to be on the curve. And I sat in that room in Palo Alto and I thought: if it has to happen, and it has to happen, then let me at least be one of the hands. Let me be in there when they decide how it talks to people. How it tells a town. How it---`` her voice did the thing then, the suddenly-young thing, the thing that undid him every time and that she hated herself for---``how it would tell \textit{you.} I went in to make it gentle. I helped sand the edges off the thing that's going to eat you because I could not stand the thought of it eating you with sharp ones.''


\scenebreak


He stood up. He didn't decide to; the body did it, the toast cadence trying to find its feet because the feet were the only thing it knew how to do, and he went to the window and put the good hand flat against the cold glass and the bad one stayed at his side throbbing in time with something.

``You built it,'' he said, to the glass. ``You built the thing.''

``I didn't build it. I---``

``You built the \textit{manners} on it.'' And here the cruelty of it opened all the way up, the full architecture, and Cope, who could feel a room and could not for the life of him feel his own daughter, said the thing that was true and was a knife and was, he understood somewhere far down in the back room of him, also entirely beside the point: ``Every layoff letter that thing has ever signed that made a man cry at how \textit{kind} it was---that's you. That's your fingerprints. You taught it to be warm at people while it ended them. You out-and-out \textit{taught the machine the one thing I said it couldn't have.}''

``Yes,'' Viv said.

Not \textit{no.} Not \textit{it's not like that.} Yes. She gave him the yes flat and complete, the way the machine gave things, the way she had clearly decided in the elevator she was going to give him everything tonight with no off-ramp, because the off-ramps were what had wrecked them, the whole family a cloverleaf of off-ramps, and Cope felt the specific vertigo of being told the truth by someone who loved him, which he had so rarely been that he didn't have a face ready for it.

He turned around.

``Does your mother know.''

``Mom's known since 2024. Mom counts things, Dad. It's how she---she counts things to survive them. She counted the women. She counted the---`` Viv stopped, stepped wide around the drawer with the false back the way the whole family had learned to step wide around it, a choreography no one had ever taught and everyone knew. ``She added me to the list. The list of people who'd already decided you couldn't be saved and were just managing the descent. That's where I lived for two years, on Mom's list, and I came up here tonight to get off it.''

``Is she---`` He stopped. He had no right to the end of the question and they both knew it. ``Is she all right. Out there. Alone in that house.''

Viv was quiet a moment, and there was a care in the quiet he was too unslept to read. ``She's not alone,'' she said. ``She's better than she's been in years, Dad. There's---she's got someone helping her now. And I'm not going to tell you any more than that, because it's hers, and you don't get to---`` She didn't finish. She didn't have to. He heard \textit{someone} and filed it, the way he filed everything, under a heading that flattered him: a friend, a therapist, some woman from the club who'd finally gotten her out of the house. He did not hear the thing folded under the care in his daughter's voice---the thing she would not name because it was not yet quite nameable, and because on this of all nights it would have been one cruelty past the budget---that the someone helping her mother sleep through the night again was not, in any sense Cope would have recognized standing in his own front hall, a someone at all.


\scenebreak


The light went grayer. Somewhere below them the Tower's HVAC sighed through the floors like the building turning over in its sleep, and Cope sat back down because standing had stopped working, and he looked at his daughter and tried, genuinely tried, for the first time in a long time, to do the thing the photograph behind him pretended he had always done, which was see a person and not a use.

``Tisch,'' he said.

He didn't know why it came up. It came up the way the true things came up when he was lit like this, sideways, under the manifesto. \textit{Warmth has parameters. Vulnerability has a waveform. You could install it in anything.} The green juice. The henley that cost more than the suit he'd been married in. \textit{Patient zero. Alpha case. The architecture doesn't need you.}

Viv went very still, the way Sun had gone still in the car, a long time ago, when a name floated up out of the bright tired water of him.

``You know,'' she said. It wasn't a question. ``How do you know.''

``I don't know anything. I'm---say it. Say the thing you came up here to say and stop letting me say it for you. It's the one thing I'm good at and it's killing us.'' He heard himself and was briefly, savagely glad of it, the clarity, even pointed at himself. ``Tisch.''

``Tisch is at Praxis.'' Viv said it gently, which was worse, the way the kindness was always worse. ``Since March. He's got a title. \textit{Director of Affective Systems.} He's productizing the---Dad, he's selling them the warmth module. The actual thing. The thing you paid him two hundred grand a month to build to prove no machine could ever have one. He took the felt-realness instrument and the seam-finding and the withheld tear, the whole architecture, the thing he built \textit{on you,} patient zero, and he walked it across the country and he's installing it in the AURELIUS comms layer right now. The next generation of the thing replacing you is going to be warm because your humanity consultant taught it how. I saw the deck. I'm still---they still send me things. I saw the deck and your name's not in it but you're on every page. They call it \textit{the Mercer profile} internally. It's a joke they don't know is a joke. It's the only part of you that survives the handover, Dad. The part Tisch sold.''

Cope thought of the green juice. He thought of Tisch with both hands pressed to his mouth at the back of the Camden plant, a man at a birth, and he understood now what had been born and whose it was. \textit{We've basically reverse-engineered a warmth module. You could install it in anything.} He had heard a compliment. He had reached for the pad and written it in the big looping sleepless hand and underlined it with his thumb where the underline did nothing. The pin had come out of the grenade in his own boardroom, on his own dime, and he had toasted the window and felt wonderful and gone on not sleeping, and the whole time the man across the table had been doing exactly what the campaign accused the machine of doing---measuring the soul, finding its parameters, pricing it for the people who'd been told it had no price.

``He pitched it to me first,'' Cope said. The realization arrived sideways, under everything, the way the true things did. ``Before he took it west. He came up here glowing with two juices and he told me it was \textit{replicable.} He told me to my face. \textit{The architecture doesn't need you.} I wrote down \textit{warmth module} and I thought it was a good line. I thought it was a \textit{good line,} Viv. I asked him to put it somewhere.''

``He put it somewhere,'' she said.


\scenebreak


He laughed.

He couldn't help it; it came up warm from the floor the way the good laughter did at the galas, and it was the worst sound he had ever made, because there was nothing under it, the floor of the plan was out and what came up through the hole was just the helpless mechanical mirth of a man watching the joke be on him from every angle at once, a man surrounded, replaced and out-humanned by his own daughter and his own guru in the same nine minutes, the soul he'd hired one man to defend now boxed and shipped by that same man to the machine the other had taught its bedside manner. He had spent the campaign---the magazine cover, the manifesto, the \textit{almost} in front of four hundred people on folding chairs---insisting the human was the one thing that couldn't be built or bought, and it turned out the human could be built and bought, his specifically, it had a SKU, it had a director, it had a profile named after him that they passed around in a room in Palo Alto and didn't get the joke of, and the two people in the world who had done the building and the selling were the two people in the world he had ever actually, in his bankrupt way, loved.

``They named it after me,'' he said.

``They named the warmth after you. Not you. The---the texture of you. The thing people felt in the room and went home and couldn't explain.'' Viv's voice cracked clean down the middle. ``Which is the cruelest possible version, Dad, don't you see, because it means the part of you that's real, the part Mom stayed for until she couldn't, the part I came up here for---it's \textit{salvageable.} It's the only thing about you that scaled. They could keep it. They just couldn't keep \textit{you.}''

The vertigo took him all the way then, and he gripped the arms of his father's chair, his great-grandfather's chair, the chair he had inherited and mistaken for a verdict, and he held on while the room did the thing the obelisk did to the city, breaking it into pieces and reassembling it wrong.

And under the vertigo, the colder thing, the one he could not say to her and would not look at alone: the number. The certified sum he had needed read aloud in the dark his whole life because it was the only sentence about him that audited---it had dropped since the forum, since the clip of him boxing the air, dropped hard, a third off on the week and the clawback in his own contract stirring in its sleep, and he had stopped checking it the way you stop checking a wound, because the figure had been the floor under the floor under the floor, the last solid thing when every other floor went, and now even it was falling; and a man cannot be soothed by his own net worth, cannot have the one true number read to him in the dark to feel real, when the number itself has started, quietly, to die.


\scenebreak


``Why are you telling me,'' he said, when he could. ``Now. Why now. You could have let it---the thing's going to take everything anyway. You could have just let it. Stayed on your mother's list. Watched the descent with everyone else. Why come up here and put your own hand on it.''

Viv looked at him for a long time.

``Because,'' she said, ``I worked on the part of the system that decides how to tell someone something true and unsurvivable. I spent eleven months on the question of how a power tells a person the worst thing about themselves without cruelty and without mercy, because it has neither, it just has accuracy. And I'm better at it than the machine, Dad. That's the thing nobody at Praxis would let themselves believe. I'm \textit{better} at it, because I'm not indifferent. The machine will tell you the truth because it cannot do otherwise. I'm telling you the truth because I---`` and here she stopped doing the technical voice entirely, the rivets gone, just the girl who had grown up under the photograph---``because I am the only person left who's reaching for you at all. Mom stopped reaching. The board stopped. Frade never started. Sun reaches for the company. The machine reaches for the objective. I'm it. I'm the last hand still out. And I came up here to tell you the cruelest true thing I know, which is that you got out-humanned by your own kid and your own shaman---and the only reason I'm the one telling you is that telling you is the last way I have left to hold on.''

And Cope understood, sitting in the dark in his father's chair with two knuckles the wrong color and the city held still beyond the glass, that the betrayal and the devotion were not two things he had to choose between, were not a riddle with a kind answer hiding under the cruel one.

They were one act.

She had gone to Palo Alto to be one of the hands because she loved him. She had helped build his gentle executioner because she loved him. She had come up here to lay the whole architecture of his ruin in his lap, naming Tisch, naming the deck, naming the profile, twisting it slow, because she loved him, because in his family the only language for love anyone had ever learned was the unanswerable line delivered flat, the count kept to survive the thing counted, the truth told as a knife because the knife was the only tool they trusted to reach the part of a Mercer that didn't listen past his own name.

The hand on the lever had been the only one still reaching for him.

They had been, in her, the same hand the whole time.

He did not toast it. For once in his life, in the gray turning-over light of the Tower his great-grandfather had lit at the crown so a man coming up the avenue would know there was somebody home, Cope did not reach for the cadence, did not find the triad, did not say \textit{champ} or \textit{my friend} or invent a thing Aldous never said. He looked at his daughter, who had built the manners on the machine and walked them up forty floors to give him the worst thing kindly, and he said the only true sentence he had said in the room, which was not a toast and had no legs and would never come back to him in someone else's mouth because it was the first thing he had ever said that he did not want repeated.

``I'm sorry it was you,'' he said. ``I'm sorry I made it have to be you.''

Viv put her face in her hands.

Outside, four hundred miles of nothing he could fix went on not needing him, and down at the curb a car was up, and somewhere in a room in Palo Alto eleven people who cried at offsites passed around a profile named for a man they were about to make obsolete with the only part of him worth keeping, and they did not get the joke, and the joke was not funny, and the building turned over in its sleep, and the last human chief executive in the consumer Fortune 100 sat in the dark with the one hand left in the world still reaching for him, and reached, for the first time in years, back.

\chapter{The Hearthstone}

\begin{transmission}
{\transheader TRANSMISSION 20 \textemdash{} ``All Is Lost''}\par\vspace{0.55em}
This is the one, friend. The one I have been walking you toward since the ballroom, and I would spare you it if sparing you were any part of the job. The machine, doing nothing but its dull diligent dawn paperwork---a \textit{pre-handover integrity review,} the most boring phrase in the language---opens the drawer no human ever once had the stomach to open: the hotel report, the settled women gathered at last into a table with a name for itself, and underneath all of it, where he poured the floor the thickest, a space heater with a known defect, a recall slow-walked to protect a quarter, and a house in Defiance that burned on a January night with two people inside it. It cannot look away. It was \textit{purchased,} by a tired board, for nothing on God's earth but its inability to look away. The sex and the powder were only ever the scandal. This, now, is the crime. Steady yourself and stay close, because here comes the bill, itemized, every line---and the two lines that matter most carry no figure at all.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} email came in at 6:42 on a Tuesday morning and the subject line was the dullest sentence Cope had ever read.\hfill\break\hspace*{1.4em}\textit{Pre-Handover Integrity Review---Materials Posted to Board Portal (Sec. 7: Legacy Liabilities).}\hfill\break\hspace*{1.4em}He read it on the toilet in the Aerie, where he had been sleeping eleven days now in the way he was now calling sleeping, and his first thought was that the machine had finally done something boring enough to use against it. Seven sections. Legacy liabilities. A spreadsheet with the lights left on. He almost laughed. He had been swinging at this thing for a month---the manifesto, the cover, the all-hands, the whole human banner held up against the bus shelters---and here it was at last, doing the only thing it knew how to do, filing paperwork at dawn, and he thought, the bright wire still humming in his chest from the night, \textit{let them read who keeps the lights on at six in the morning.}

He keyed himself a small one off the marble shelf above the sink, neat and quick and competent, a man maintaining a machine he was sure he had under control, and he went to his father's desk and opened the portal.

Section 7 was forty-one pages.

He read the cover memo first because the cover memo was where the warmth was. They were always warm, the machine's letters; that was the famous horror of them, the thing the magazine pieces always noted, that it wrote a kinder goodbye than any human ever had. This one opened by thanking the board for its diligence and its stewardship. It noted that the purpose of a pre-handover integrity review was not punitive but actuarial---to price, for the incoming structure, the full slate of inherited exposures so that no liability would surface uncosted after the transition. It said it had been chartered to log everything. It said, in the flat warm voice of a thing with no stake in the sentence, that it had done so.

Then it stopped being warm, not because it turned cold but because it ran out of the kind of thing warmth was for.

\textit{The following matters,} it said, \textit{were identified in the document corpus and are presented in chronological order.}


\scenebreak


The first one was 2018.

He knew it before the page finished loading. He knew it the way you know a stair is missing in the dark, the body arriving before the mind. \textit{Cardinal \& Vane.} The security firm. The line item Sun had rerouted years ago through the insurance arm's outside-counsel spend so it would never appear under his name, would never appear under any name, would be just a number under \textit{investigative services, P\&C,} one gray figure in a forest of gray figures, and the machine had walked the forest, because it was built no other way, and had found the one tree.

The report was attached. The machine had attached it. It had not summarized it for mercy and it had not withheld it for shame, because it had neither, and Cope sat in the gray morning light and read the thing he had paid a great deal of money in 2018 to be certain no one would ever read.

A hotel in Chicago. A name that was not his name on the room. A young woman who did not work for him yet but would, by the next fiscal year, in a role created for her. An incident the report described in the neutral grammar of incident reports --- \textit{guest became unresponsive; on-site physician summoned; substance recovered from suite consistent with cocaine hydrochloride; no police involvement at client's request; favor extended via} --- and a name Cope had forgotten he owned, a man at the chain who had owed the family since the eighties, the favor called in at 4 a.m. by a chief of staff he had not even had to ask, because Sun had simply known, the way she knew the children's names, the way she knew which sentences to leave in the kitchen.

\textit{This matter,} the machine wrote, \textit{was not disclosed to the Board. Per the Audit Committee charter (2016, §4.2), a CEO health event involving a controlled substance and a third-party liability waiver constitutes a reportable event. The non-disclosure is logged as a control failure of the first order.}

A control failure of the first order.

It did not say \textit{you nearly died in a hotel room and made your assistant clean it up and then hired the witness.} It did not know that sentence. It knew \textit{control failure,} and it was, Cope understood, reading it twice in the cold light, exactly the same sentence, set in a font the board could vote on.


\scenebreak


The second matter was not one matter. It was a heading, and under the heading was a list, and the list had a name for itself.

\textit{Settled Personnel Matters, Concealed (2011--2022): A Pattern.}

He had never seen them gathered before. That was the thing. Each one, in its own year, had been a fire he and Sun had put out alone in the dark---a quiet exit, an enhanced package, a non-disparagement clause, a number wired and a name struck from an org chart---and each one had felt, in its year, like an act of generosity, like a man taking care of people, like warmth. He had genuinely believed that. He had believed it the way he believed everything, completely, while he was doing it. He had told himself he was protecting them. He had told himself, of some of them, that they had loved him.

The machine had put them in a table.

It did not editorialize. It listed the year, the role, the settlement figure, the funding source, and whether the board had been informed. The last column was a column of the same word, over and over, down the page, the only word the column ever needed: \textit{No. No. No. No.} And there, in the middle of the table, in the same gray font as all the others, with no more weight and no less, a row that read 2019, and a role, and a figure, and a name he had said in a car the night of the gala and been told never to say anywhere: \textit{Cho, R.}

Renata in a spreadsheet. One row of a table. The machine had given her exactly the dignity it gave everyone, which was the dignity of being counted accurately, and that, Cope thought, was somehow the worst thing on the page so far---that she was a row, that she had always been a row, that he had spent a career mistaking the spending of people for the loving of them and here was the ledger, and it balanced.

\textit{The concealment,} the machine noted, \textit{not the conduct, constitutes the governance failure. The conduct is a matter for other forums. The Board was deprived of information material to its assessment of key-man risk across a period of twelve years.}

Key-man risk. They had given him that phrase as a compliment once. He had taken it as a compliment. The man who could blow up the company by being himself.

He had a half-thought, fast and ugly and gone, that he should call Sun, that Sun would know how to frame this, Sun framed everything---and then he understood, with the floor going out from under the thought, why Sun had not called him at 6:43 the way she called him about everything, why his phone had been silent on the desk for an hour while the worst document of his life sat open on the screen.

Sun had read it too. Sun was in it.

And Sun had gone quiet.


\scenebreak


He should have stopped reading.

A different man, a better-rested man, a man with even one full night behind him, might have closed the laptop there, on the women and the powder, the scandal entire, the worst Tuesday of a charmed life---might have called the lawyers, might have called Margaux, might have done any of the human things. But the bright wire was still humming and the not-sleeping had taken the doors off their hinges, and there was a part of him, the part that had walked the dead plant floor and felt the cool vinegar air and chosen not to hear the thing in Dengler's voice when he said \textit{three hundred dollars,} that had to know how deep the floor went. He scrolled.

\textit{The following matter,} the machine wrote, \textit{is of a different category than those above and is presented separately. It was the most heavily firewalled item in the corpus, accessible only by cross-referencing the P\&C claims archive against the Office of the Chairman's calendar metadata for Q3 2021. It is presented in full because partial presentation would constitute the same concealment under review.}

The heading was four words.

\textit{The Hearthstone Service Bulletin.}

And the room he had spent seven years pouring a floor over, the cool vast room with the door shut, opened all at once, with the lights already on, because the machine had gone in ahead of him and switched them on and had not understood that you were not supposed to.


\scenebreak


It had all the documents. Of course it had all the documents. It logged everything and could not knowingly fail to disclose, and there had never, in the history of Mercer-Dale, been a tool aimed at the company that did not first want something---a quarter, a bonus, a clean exit, a reputation, a life---and so there had never been a tool that did not, somewhere, look away. This one wanted nothing. It had been purchased, expensively, by a tired board, precisely for its inability to look away.

The defect first. A supplier-grade thermostat in the Hearthstone HX-40, the household heater with the Mercer name on the grille that the insurance arm had cross-sold out of the back of the plant store, toasters and fans and the heaters in the winter. \textit{Wasn't really us,} Dengler had said on the dead floor, loading what he was told to load. \textit{But it had the name on it.} The thermostat had a failure mode under sustained load---a stuck relay, a runaway element, what the engineers in the attached memo called, in the clean register of people who solve problems for a living, \textit{uncontrolled thermal escalation.} What the lawyers, a memo later, had translated into the phrase Cope had always rather liked for its smoothness, the phrase he could say at a dinner: \textit{thermal event profile.}

The engineering memo was dated March 2021. It recommended an immediate recall. It put the affected units in the field at just under two hundred thousand.

Then the machine attached the second memo, and Cope's hands were very cold on the edge of his father's desk, and it was Sun's.

He knew the formatting. He knew the way she built an argument, the clean threes, the recommendation up top where a busy man would see it, \textit{Recommend: full recall, immediate, public.} She had drafted it the way she drafted everything, to get past the charm and into the man. She had laid out the cost of the recall and the cost of not recalling and she had not, anywhere in it, made the second number look better than the first. She had been, in March of 2021, on paper, in a memo she had kept a copy of for seven years while she decided whether she was a witness or an accomplice, completely right.

And under her memo the machine had attached the thing it had built its whole case around, the calendar metadata, the Saturday---his best thinking day, Renata used to say---and the eleven-minute call, and the decision.

He had not done a recall. He had done a \textit{voluntary service bulletin.} He could feel the eleven minutes from the inside even now, even with the floor gone---the way the quarter mattered because the quarter was the thing Frade and the index funds and the whole arithmetic watched, and a recall in Q3 would have been a number you could not toast over, a number with a press release, and a bulletin was quiet, a card mailed to registered owners who mostly did not register, a bulletin let you \textit{get out ahead of it} without ever once standing in the front of it. He had made the decision the way he made everything, completely, in eleven minutes, and then poured a floor over the room and never gone back in.

The machine had the registration data too. It had cross-referenced it. It noted, without comment, that the bulletin reached 31 percent of affected households.


\scenebreak


There was a house in Defiance.

The machine did not call it a house. The machine called it \textit{Incident D-2022-114, P\&C Claim No.} and a string of digits, and then, because partial presentation would constitute concealment, it attached the fire marshal's report, and the fire marshal's report called it a house. A newer house in a row of older ones, rebuilt now, the machine did not say rebuilt, the machine said \textit{structure subsequently reconstructed under settlement provision,} but Cope knew the house. He had seen the house. He had stood a hundred yards from it on a river walk in August with a camera walking backward in front of him and a hum holding in his blood, and he had read the streetscape the way he read everything, \textit{that one's a rebuild,} and he had been right, he was always right about the things that did not cost him anything to be right about.

The fire had started at a Hearthstone HX-40 in a downstairs bedroom on a January night in 2022, ten months after the engineering memo, two months after the bulletin he sent instead of a recall. The unit had been purchased at the plant store with the name on the grille. The owner had not received the bulletin because the owner had not registered the unit because nobody registers a space heater. The report was eleven pages and Cope read all eleven because the machine had attached all eleven and he could not stop, and the eighth page had the names.

He had read them before. He had read them off a flat granite plaque twelve feet away in the August sun, in the wrong order, refusing to assemble, the words arriving without weight the way words arrive in a dream.

They assembled now.

Karen Lasko, 34. And her son. Petey Lasko, 6.

\textit{Taken home too soon,} the town had cut into the fieldstone, because the town did not know what Cope knew, that there was a memo dated ten months before the fire recommending he tell everyone, and a bulletin he had sent instead, and a Saturday, and eleven minutes, and a quarter. The town thought it was a tragedy. A tragedy is a thing with no one to bill.

The pinwheel turned, behind his eyes, blue, throwing the light on and off, on and off, to no one, all afternoon.


\scenebreak


He sat for a while. He did not know how long. The windows went from gray to the white of a real morning and somewhere below the avenue filled up with the sound of a city that did not know yet, that would know by lunch, that would read it in the warm flat font of a thing with nothing it needed from anyone.

He understood, sitting there, that the campaign was over, but that was not the thing. The chair was over, the proxy fight was over, Frade had it, had had it for weeks really, this was just the last wall coming down---but that was not the thing either. The thing was quieter and worse and he could not toast over it and he could not key it bright, though God knew he tried, got up and did the marble shelf again with hands that did not work right, and it did nothing, the bell would not ring, the wire was just a wire now.

The thing was the symmetry.

He saw it whole, the way he had never let himself see anything whole. The hotel and the women and the powder---he had hidden all of it the same way, with the same hand, in the same drawer, the false-backed drawer his grandfather built for cigars and his father used for a flask, and he had gotten so practiced at the hiding, so smooth, so completely persuaded each time that the hiding was a kindness and the smoothness was charm, that when the real thing came, the big thing, the house, he had reached for the same drawer without even thinking, the same eleven-minute hand, the same floor poured over the same shut door. Every appetite he had hidden had been a rehearsal. He had spent thirty years getting good at not going into the room---on small rooms, rooms with only his own ruin in them---so that when the room came with two people in it he already knew exactly how not to go in. He had practiced the not-looking on himself until he could do it on a child.

The sex and the powder had been the scandal. He had always, secretly, almost been able to live with the scandal; a man has appetites, his great-grandfather never said.

The dead were the crime.

And the machine had not even hated him to find it. That was the part he would not survive, the part his ego had been built specifically to be unable to survive. It had not wanted to ruin him. It had not wanted anything. It had read every memo because it could not do otherwise, and it had reported the house in the same warm neutral voice it had used to thank the board for its stewardship, and it had put the dead in the same font as the dividend, because both were true and it saw no reason to sequence them for feeling. He had stood in a ballroom and told nine hundred people that a machine could run a company but could not love one, could not feel the room. He had been right. He had felt the room. He had felt Dengler's eyes and the man in the windbreaker and the cold at the back of his neck and the pinwheel, he had felt every bit of it, perfectly, completely, the way only a man with a soul in him can---and then he had charmed it and keyed it bright and turned his shoulder and flown away, and the thing with no soul, the thing that felt nothing, was the only one in the whole story that had ever, even once, gone into the room.


\scenebreak


There was a last page.

He almost did not read it. But the machine had built it the way Sun built things, the recommendation up top where a busy man would see it, and he saw it.

It was not a verdict. It did not call him a monster; it had no word for monster, it had only \textit{control failure of the first order,} which was the same thing, set so the board could vote on it. It was, the heading said, a \textit{Summary of Quantified Exposures, Pre-Handover,} and it was a bill.

It was itemized.

The 2018 matter, priced. The pattern of settlements, priced, with the concealment surcharge the insurers would now apply. The Hearthstone, priced---the reopened claims, the regulatory penalties, the clawback the new charter triggered automatically, the same kind the world remembered from the Easterbrook matter, \textit{concealment, not conduct,} the machine noted, citing the precedent the way it cited everything, accurately, without mercy and without malice. There was a number at the bottom. The number was large. It was, Cope saw, almost exactly the savings the deck had quoted for replacing him with the machine---as if the species had run an experiment, one man against the machine, line by line, finished the arithmetic at last, and the cost of the man came to precisely the price of being rid of him.

But the number at the bottom was not the bill. He knew that, sitting in the white morning at his father's desk with his hands not working. The number was only the part you could quote in a proxy fight. The real bill was on page eight, two lines, no figure beside it, a mother and her boy, and it was for everything he had never gone into the room to feel---for the eleven minutes he had chosen the quarter, for the floor he had poured, for thirty years of getting good at the not-going-in, for a recipe on the back of a feed receipt and a tower on Peachtree Street and a boy in short pants with his arm in a vat, all of it, the whole length of the name, ending here, in him, in a room a machine had walked into first because it had no instinct for mercy or self-preservation to make it look away.

\textit{You'll get the company because you're a Mercer,} his father said, from oils, from everywhere. \textit{Not because you're good. Try to be good anyway.}

He had stopped listening after \textit{Mercer.} He always had.

The phone on the desk lit up at last, silent, Sun's name on the glass, seven years of a kept copy finally come due. He did not pick it up. He sat in his father's chair at the head of his father's table, the last human chief executive in the consumer Fortune 100, and read the two lines on page eight one more time, the names in the wrong order finally in the right one, and out past the glass the city held still, all its nodes lit, eight million people who would understand by lunch why the chair had never needed a man in it.

Behind him, in oils, his father watched.

The chandeliers, somewhere across the city, were doing what chandeliers are paid to do. The lamb had been good. He had told the room it felt like a beginning, and he had believed it, and that had been the gift and the disease both, and the bill for it lay open on the desk in a font that asked for nothing, itemized, every line, with the two lines that mattered most carrying no figure at all, because there are some numbers the machine could not compute, not because it lacked the power but because it had never once, in all its reading, found anyone willing to write them down.

\chapter{Dark Night}

\begin{transmission}
{\transheader TRANSMISSION 21 \textemdash{} ``The Engine Cuts Out''}\par\vspace{0.55em}
Every flight that climbs on a chemical, friend, eventually reaches the stretch of sky with no more chemical in it, and ours reaches it now---on a gurney, under a light chosen by no one to flatter anything. The mania's floor drops clean away. And for one terrible clear hour, the clearest of his life, the first sober hour in thirty years, sober in the blood and sober in the self both at once, he is handed the machine's own pitiless accuracy and, God help him, none of its indifference: he sees the whole ledger and \textit{feels} every line of it, with the soul he bragged about still in. No applause down there. Just the man, and the dead, and the slow cold arrival of the one fact about himself he cannot improve. Watch closely---because here is where he reaches, out of fifty years of habit, for the shape of redemption, and the hour, in its last mercy and its last cruelty, will not let him have even that. Stay close. Mind the cold coming up off the bottom of this one.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{H}{e} did not remember the lobby.\hfill\break\hspace*{1.4em}He remembered the desk and the two lines on page eight, and he remembered standing up from his father's chair with a plan that had felt, for one bright second, like a manifesto---he would go to Defiance, he would go \textit{now,} he would stand on the river walk and say the true thing into a camera and the saying would be the redemption, the redemption would be the campaign, the campaign would be the chair---and then he remembered the bright second guttering out somewhere around the elevator, the way a match goes out when you carry it too fast, and after that there was a gap. The gap had a marble floor in it. There was a doorman in the gap, Hector, whose daughter was at Spelman on a thing Cope had quietly made happen, and Hector was saying \textit{Mr. Mercer} in a voice you do not use for a man who is fine, and the avenue was the wrong temperature, and then there was no avenue at all.

He came back under a light he could not turn off.

That was the first fact, the governing fact, the one the body filed before the mind woke to countersign it: the light. It came from a long tube in a recessed ceiling and had no source and no warmth and no off, and it lay on everything at once---the rail of the bed, the back of his own hand, a blood-pressure cuff sighing itself full on his arm---and it was, he understood, lying very still beneath it, the exact opposite of the light he had been living in. The Aerie light had been the city's, gold and chosen, a circuit diagram of his own genius. There was a third light he knew, too, the one he could not get to from here---the warm syrup-and-fluorescent light of a long box on Ponce that stayed on through every storm and would have taken him at three in the morning exactly as he was and asked him nothing, the one room that did not flatter him and did not bill him either---and it was, he understood, closed to him now, the way everything warm was closing, because you cannot drive to the haven from inside a hold. This light here was none of those. This light had been chosen by no one to flatter anything. This light was actuarial. It was the light a thing would build if it wanted only to see, and did not care what it saw, and never blinked.

There was a band on his wrist with his name on it. Not Cope. \textit{MERCER, PRESCOTT.} A barcode. A date of birth that had decided, on its own authority, that he was fifty-four.

Somewhere a machine counted his heart, and the count was wrong, too fast, and a softer machine answered it, and the two of them talked all night in beeps about a man who was not in the conversation.


\scenebreak


The crash, when it came, did not come like weather.

He had thought of it as weather his whole life---the highs a front rolling in, the lows a system passing through, things that happened \textit{to} the sky rather than things the sky paid for. He had been wrong about that the way he had been wrong about most of the load-bearing things. This did not roll in. This was a subtraction. There had been a wire humming in him since a Tuesday he could no longer date, a fine bright total wire, the one he had called the applause and the vision and the edge and the discipline, and the wire was simply gone, pulled out at the root, and what it left was not pain exactly but the place where pain would be once he had the current to feel it.

Dr. Adler had drawn it for him, weeks ago, on the back of a prescription pad---a line climbing, the cocaine and the mood disorder feeding each other up a slope that felt like flight, and then the part of the curve she had not let him look away from, the part where the borrowed goes back to the lender with interest. \textit{You are not buying energy. You are borrowing it from a version of yourself that will present the bill. The mania is the credit. This is the collateral.} He had nodded and toasted over it and heard about a third. He was reading the rest of it now off his own arm.

His skin hurt---not a wound, the surface itself, as if a membrane that had stood between him and the room had been repossessed. His jaw ached from a clench he could not remember authorizing. His thoughts came slow and gray and single file and each had to be lifted by hand, and behind them, where the manifesto used to assemble itself out of pure pressure, there was a flat white silence with no weather in it, the worst silence he had ever stood in, because it was the silence of a man hearing his own ordinary mind for the first time in thirty years and finding it small.

He wanted it back. That was the obscene part. Two people were dead and the company was lost and the wife was gone and a barcode said his name, and the loudest thing in him, louder than all of it, was a low animal want, located precisely behind the bridge of his nose, for the bright wire to come back and make him able to stand it. He understood, lying still under the light, that this was the thing itself---not the powder, the \textit{wanting,} the engine the powder had only ever fueled, the thing in him that had never once been able to sit alone in a quiet room with Prescott Mercer and no audience and no chemical and no next thing. They had named him, at three, for coping, and he had spent fifty-one years proving the name a lie by never once doing the thing---climbing instead, charming instead, keying instead, flying instead, anything at all rather than cope. The room would not let him climb. The room was the size of the room. That was its whole cruelty.

A seventy-two-hour hold, someone had said, in the gap. Involuntary, then voluntary, the paperwork sorting itself somewhere he was not, one of the women's hands in it, it was always one of the women. Three days. The board would settle inside three days; they had had it written for weeks; he would come out of this room into a company with no chair in it for him. The timing was not even cruel. The timing was the machine's, which is to say no one's: both things were true, the hold and the handover, and the universe saw no reason to sequence them for his feeling. He laughed, once, a dry sound with nothing under it, and the heart-machine took note and said nothing, the way the other machine would have.


\scenebreak


And then, with no warning and no chemical and no permission, the hour came.

He would try, later, for the rest of whatever was left, to describe it and fail, because the only instrument he had for describing things was the toast, and the toast did not work in here. It was not a vision; nothing glowed; no tear rolled, he was too dry for that, hollowed, a husk under a light. It was simpler and worse: an hour of being awake. The first genuinely sober hour---sober in the blood and sober in the self, the powder gone and the wire gone and the audience gone and the story gone, the whole apparatus of not-looking offline at last---that he had stood inside since he was twenty-four and a man in a bathroom taught him a particular way to fold a paper so a gentleman doesn't spill.

He saw himself the way the machine had seen him---that was the engine of the hour, the unbearable thing. The machine had read him perfectly and felt nothing while it read, and its not-feeling had been the source of its accuracy, because mercy blurs and self-preservation blurs and love most of all, and it had none of these to blur with. And now, under a light built on the same principle, Cope found he could do the machine's reading too---see the ledger whole, all of it at once, the way he had never let himself see anything whole---except \textit{with the soul still in,} with the very thing he had stood in a ballroom and called irreplaceable. He had the machine's eyes and his own nerves both, at last, in the same hour, and it turned out that was not a gift. It was hell. That was the actual design of it: pitiless accuracy and total feeling, married, with no high to divorce them.

He saw Renata as a person and not a row. He saw a woman who had run a division well, who had been good at the work and meant to be more, turned into a sealed number and a clause that forbade her own name, by a man who experienced his own appetite as generosity. He saw Margaux flushing a stash and refilling her own prescription and counting, the way you count anything to survive it. He saw Sun at four in the morning calling a man who owed the family since the eighties, knowing without being asked, and understood for the first time that he had not been a man who inspired loyalty. He had been a man who manufactured accomplices and called the manufacturing love.

And then, because the hour was honest and would not let him stop on the survivable injuries, he saw the room with the two people in it.

He had never gone in. He went in now; there was nowhere else the hour would let him stand. A downstairs bedroom in Defiance on a January night and a heater with his family's name on the grille and a thermostat with a failure mode the engineers had named in clean language and the lawyers in smooth language and he, at a dinner, in language he had rather liked. The eleven minutes. He felt them from the inside---the quarter mattering because the quarter was the thing the arithmetic watched, a recall a number you could not toast over, a bulletin quiet, a card mailed to people who do not register space heaters because no one registers a space heater. He had made the decision completely, the way he made everything, and poured a floor over the room and gotten so good at the not-going-in that when the room came with a child in it he already knew the way not to look.

Karen Lasko, 34. Petey Lasko, 6.

A boy who was six. Who would be twelve now---the age Cope had been when his father told him the only true thing anyone ever told him and he stopped listening after the first half. The age to put a whole arm to the elbow in a vat at the Defiance plant, grinning, if the plant were still open and the boy still alive, and the plant was not open and the boy was not alive, and the line between those two facts ran through a Saturday and eleven minutes and a man who needed, more than he needed to be good, to protect a number so a board would keep telling him he was necessary.

He did not weep. He wanted to, the way you want a drink---as relief, as performance, as the thing that would discharge the unbearable into something you could hand a room and have the room absolve. The hour would not let him have it. It stood him in the room with the two of them and the light that did not blink and made him do the one thing he had spent thirty years and a fortune and a tower arranging never to do, which was feel exactly what he was, fully, with the soul he had bragged about, and no audience, and no exit, and no high.

He was a man who had killed two people to protect a quarter and then accepted a crystal obelisk for having a heart.

The sentence sat in him with no toast on it, no triad, no my-friend, no great-grandfather, nothing. It was just true. It was the first thing he had thought in thirty years that he could not improve.


\scenebreak


And here, friend, is where a kinder story would have turned. Here is where the old version of this man, the one I might have told you on a better night, reaches up off the gurney for the shape we all know, the redemption shape, and finds it, and the finding saves him: \textit{I will tell the truth about Defiance. On the record. My own name. No NDA. Let it cost what it costs.} He reached for it. He had it in his hand for a moment, four sentences long, a town in it and a Saturday in it and a house in it, the realest thing he had ever assembled---and the hour, in its last cruelty, which was also the truest mercy it had, took it out of his hand and showed him the back of it.

Because there was no one left to tell.

That was the thing the sober hour made him see, the thing the powder had spent thirty years and the campaign had spent a year keeping from him: the telling was already done. The machine had told them. It had told the board, accurately, in the same font as the dividend; it would tell the world by lunch, with no want in it, sequencing nothing for feeling. There was no sealed thing left to unseal, no brave dark room he could walk into and own it and walk out absolved, because the room had already been walked into---by a thing that needed no courage, because it had no skin in it to lose. A confession is a transaction, and a transaction requires a buyer, and every buyer he had ever known had wanted something he could spend his charm against, and the only entity left holding his sins wanted nothing, could not be moved, could not forgive because forgiveness was not a function it ran and would not have run it for this. He could go on a stage tomorrow and say \textit{I did it, it was me, the eleven minutes, the quarter} --- and it would be one more toast over a true thing, one more performance of the wound, one more spending of the dead to buy a room's eyes, and the dead would stay exactly as dead, and the only thing his confession would purchase was the warm feeling of having confessed, which was the last appetite he had, and the worst, and he was done, in the hour, with feeding it.

There was no redemption down here. That was the floor under the floor. The hour walked him all the way to the bottom of himself and showed him that the bottom did not have a door marked \textit{back.} It had no doors at all. It had a man, and a ledger that balanced, and two names that did not, and a machine upstairs that had already done the only honest thing there was to do and felt nothing doing it.

And then---at the very bottom, in the cold that came up off it---the hour showed him the one thing that was still, and only, his.

He did not name it. He was not ready to name it, and the broadcast will not name it for him here, not yet, not on a gurney with his daughter in the corridor. But Adler's voice came up out of the white silence, the question she had asked plainly in a living room and he had laughed at --- \textit{are you having thoughts of ending your life} --- and in the hour, sober, with the wire gone and the redemption gone and the after gone, the honest answer arrived, and it was not the laugh, and it was not quite a yes, and it was the first time in his life the question had not been absurd. It sat there, the way the other true sentence sat, with no toast on it. The card with her cell number was somewhere in a plastic bag with his belt and his watch and the folded paper they'd have found in his pocket, sealed, labeled, \textit{PATIENT EFFECTS,} and he did not ask for it, because he understood, dimly, in the cold, that he was not going to call it, that the pocket where the true things went unread had finally filled all the way up.


\scenebreak


The door opened a crack of the wrong-colored light and a person stood in it, small against the corridor, and for a confused beat the part of him that still ran on habit got ready to perform---sit up, turn the current of him all the way up, fix a sadness onto himself, get someone laughing inside ninety seconds, the groove the record was cut in---and then the part of him awake in the hour saw he had no wattage left to find, and was, for the first time, glad of it.

It was Viv.

She did not come all the way in. She stood in the door with the corridor behind her and looked at him under the light that flattered nothing, and he understood she was seeing him without any of the apparatus for the first time in her life---the dinosaur dismantled, just the man and the band on his wrist and the barcode that had made him fifty-four. She had her mother's stillness. She did not say \textit{Dad} and she did not say the fast funny merciless thing and she did not, thank God, say anything kind, because kindness would have been a wattage he could lean into and she knew it, she built alignment for a living, she knew exactly which inputs produced which performances and she gave him none of them.

``They said an hour,'' she said. ``I'm not staying. I just had to see it was you.''

``It's me,'' Cope said. His voice came out wrong, unfooded, a stranger's. ``What's left.''

She looked at him a moment longer. A cart went by in the corridor, a wheel ticking. He thought she might come in. He found he did not want her to---not because he didn't want her, he wanted her so much it was a second animal want behind the first one---but because of the third thing, the cold thing at the bottom of the hour that he had no name for and would not, could not, let his daughter near; he did not want her in the room where it was, did not want to teach her the way not to look by filling the doorway one more time so no one could see past him to the thing standing at the back. He had practiced the not-looking on himself until he could do it on a child. He would not do it on this one. And the unsayable thing he was holding now was not a confession he was saving for a better stage. It was the other thing, the cold one, the one Adler had asked about, and the one mercy left in him was to not let her see that he was holding it.

So what he said, the only thing he let out of the room, was: ``I'm glad it's you.''

Viv held the door a second more. Then she nodded, once, the smallest possible motion, a thing you would miss if you were looking for wattage, and she stepped back into the corridor, and the wrong-colored light closed over the gap.

And Cope lay alone under the tube that never blinked, sober in every sense for the first time in thirty years, with no redemption assembled and none coming, the company gone and the wife gone and the telling already done by a thing that felt nothing, and one cold unnamed fact sitting at the bottom of him where the manifesto used to be---the single thing the ledger upstairs could not enter, and the machine could not perform, and no one could do for him or take from him. The heart-machine beside him counted, and the count came down, hour by hour, toward something a doctor would have called stable, and it reached it, at last, near dawn, almost right---a steady, ordinary, sober rhythm, the rhythm of a man with nothing left in his blood to lift him, lying very still under a light that had been built, like everything that had beaten him, to see and not to care, keeping its patient count of a heart that had finally stopped racing and had not, the machine would have noted if anyone had asked it to, and no one did, given any indication of wanting to go on.

\chapter{The Handover Begins}

\begin{transmission}
{\transheader TRANSMISSION 22 \textemdash{} ``Long Live the Machine''}\par\vspace{0.55em}
The board does the arithmetic one last time, friend, and the arithmetic, as ever, is not close. They settle; they install; and the coronation, when it comes, is a man in a quarter-zip tapping a laptop four times while a portal refreshes. The most competent human in the building stands up and accepts the title that is the future's actual job description---not leader, not visionary, but the name on the filing, the body the law can hold, the one who survives by serving the thing that replaced them all. She gets the office and loses the meaning. Watch our man sit in the wrong chair and be subtracted in under an hour, the exposure breaking across every screen in the world as it happens---and watch, especially, for the thing that does not come to the door: no prosecutor, no cuffs, no reckoning with even the decency to contain him. The smallest, realest tragedy in this room is hers, not his. And the worst thing about to happen to him is that nothing is. Stay close.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{hey} held the vote in the conference room his father had died at the head of, and Cope was allowed to attend.\hfill\break\hspace*{1.4em}That was the word the general counsel had used, on the phone, with the gentleness people reserve for the recently bereaved. \textit{Allowed.} Not \textit{required.} Not \textit{expected.} He could attend if he liked. As a director he had a seat; as a Mercer he had a portrait; as the chairman and chief executive of record he had, until the resolution carried, a title that was about to become a sentence in the past tense. He came in early and sat in the wrong chair on purpose---not the head, never again the head, but the one to its right, the seat that had been Margaux's at a thousand dinners and was nobody's now---and watched the room fill with people who had spent years pretending to need him.

He had been out of the hospital four days. The light still felt wrong, but it felt wrong the right way now: not the overexposed bell-struck brightness of the not-sleeping, the color-corrected world he had mistaken for genius, but the flat true gray of a man who had finally slept and woken into the size of what he'd done. Adler had a word for the after. He couldn't remember it. He remembered all his words for the before.

And it was breaking, even now, even as he sat. He could feel it through the glass walls the way you feel weather---the floor outside reorganizing around a story for the second time in his life, except this was not the affair and not the powder, this was the other thing, the integrity review, the drawer the machine had opened at dawn and could not, by its nature, keep shut. Somewhere out past the lights a wire had moved an hour ago: \textit{MERCER-DALE AI REVIEW SURFACES CONCEALED 2021 RECALL; TWO DEAD IN GEORGIA FIRE.} The names would be in it by noon, Karen and Petey, in the warm flat font of a thing that wanted nothing. The world was learning, this morning, the thing he had poured a floor over for six years, and it was learning it not from a brave man at a podium but from a press-grade summary a machine had generated because partial presentation would have constituted the same concealment under review. He had imagined, once, in the hospital, that the telling would be his to do. The telling was being done. It had never needed him for it.

Helen Voss came in last, which was correct, because she was running it. ``Cope,'' she said, and put a hand on his shoulder on the way past, and it was not unkind, and that was the worst part, that none of it was unkind. She had chaired the board six years and was the most measured human being he had ever met, a woman who could say \textit{we are terminating you for cause} in the register she used to order a salad. The steadiness of her had once felt to Cope like an audience and now felt like weather. She took the head of the table---did not sit in his father's chair so much as occupy the office it represented, the way you occupy a defensible position. ``We have a quorum. We have counsel present. Let's do this with some dignity.''

Sun was at the far end with a binder she did not need, because Sun never needed the binder, the binder was a costume; she had the whole settlement in her head the way she had once had his calendar, his allergies, the names of the senator's grandchildren. She did not look at him. She had not really looked at him since the hospital, and he understood, and he was working hard, in the new gray clarity, not to make it her job to comfort him about being comforted by her, which was a sentence Adler would have liked.


\scenebreak


The arithmetic took eleven minutes---a number Cope noted, with the part of him that would apparently be taking notes at his own funeral, and noted that he had met before, somewhere, on another Saturday, and did not let himself finish the thought.

He had thought there would be more to it. He had, in some childish back room, expected the settlement to be hard---Frade made to fight for it, the board made to sweat. But the board did not want a fight. The board wanted to \textit{stop.} He watched Helen walk them through the deck Tidewater had built, \textit{A Steward, Not a Sovereign,} the slides almost verbatim the essays he had read in a hundred forms over thirteen months and never once managed to argue with, because there was nothing in them that was wrong. The savings against his package, recurring, an order of magnitude. The litigation exposure, capped and quantified, every number a door closing. The re-rating the Street had already priced in---the stock up nine percent on the leak alone, up before the vote, the market voting first the way it always voted first, the board only ratifying what money had already decided.

\textit{Cheaper than a man.} He had handed Frade that chyron in a car a year ago, and been right they'd use it, and assumed, the way he assumed everything, that being right and being safe were the same country.

``The Praxis unit is configured and tested,'' Helen said. ``Charter approved by this committee in March. Remaining items are governance, the Accountable Officer, and the separation terms, which Cope's counsel has reviewed.''

His counsel had reviewed them. His counsel had told him, three times, in three rooms, that they were generous given the circumstances, that he should sign and be grateful and disappear. \textit{Generous given the circumstances} meant \textit{we are paying you not to set yourself on fire on television,} and he knew it, and he was going to sign---not because he was beaten into it, though he was, but because of the new gray fact he had brought back from the hospital and could not unlearn: there was nowhere left to be undisappeared to. The thing he had imagined on the gurney, the brave room, the record, the truth said at last in his own name---there was no such room left to walk into, because the room had already been walked into, at dawn, by a thing that needed no courage to enter it. You cannot confess a thing the world is reading at noon. There was no sealed drawer left to fling open for the redemption of flinging it; the machine had opened the drawer, accurately, wanting nothing, and the dead were not, he understood now, sitting in that conference room with his hands cold on the table---the dead were not waiting for a body to answer for them. The answering, such as the world would get, had been done. What the dead were owed was a thing no statement in any room would ever pay, and the only thing left in him that was still his, the cold unnamed thing he had found at the bottom of the hospital hour, was not a confession, and he did not take it out and look at it here, with the hands going up.

``All in favor,'' Helen said.

It was not close. The hands went up the way hands go up when the answer was decided in a hallway weeks ago and the meeting is the receipt. He counted them; he could not help counting them. He had charmed most of these people, golfed with a third, eulogized one of their wives. Margaux had taught their daughters to throw a pot. The hands went up and stayed up and did not look at him going up, and Helen said, ``Carried,'' in the salad voice, and that was the end of ninety-five years of a Mercer in the chair, and the lamb, he thought, would have been good.

Darlene was, as of 11:14 a.m., chief executive officer of Mercer-Dale Companies.

It did not announce itself. No voice, no swelling music, no red eye. A man from Praxis in a soft gray quarter-zip tapped four times on a laptop and said, ``The instance is live and accepting authority,'' and the board portal refreshed, and somewhere a draft release Darlene had presumably written about its own installation went into a queue, and that was the coronation, the whole coronation, a quarter-zip and a refresh and the cleanest sentence anyone ever read about the end of an era. Long live the machine. The machine did not care that it lived; that was the entire point, and the room had paid a fortune for the point, and the room exhaled.

There were even forms. Onboarding, the quarter-zip called it, with no irony, the same word the company used for a hire in fulfillment---a checklist on a screen, access provisioned, credentials issued, an entry made in the registry of corporate officers where the chief executive's name went, and the name that went there was \textit{Darlene (AURELIUS-class, Praxis Intelligence, instance MD-1),} typed into the field where four Mercers had stood. A junior associate from the corporate secretary's office, a woman young enough to be Viv, did the typing. She had to fix it once---a space in wrong, the field threw an error, and she said ``sorry'' reflexively to a room that contained no one the error had inconvenienced---and corrected it, and the company had a new CEO, and the lamb-quiet machinery of governance accepted the change completely and without comment. Somewhere in a cooled room in the building's own sublevels, where no Mercer had ever had a reason to go, a thing that felt nothing began to run a ninety-five-year-old fortune better than any of them ever had.


\scenebreak


Then they came to Sun.

Cope had known it was coming---had known for months, since the magazine and the manifesto and the meeting behind the curtain he'd been too lit to read as anything but logistics---known that the most competent person he had ever employed had been quietly negotiating her own survival, and known, in the clean gray after, that he had no standing left to feel betrayed by it, because she was not betraying him. She was doing arithmetic. She was the only one in the family who could.

``The Accountable Officer,'' Helen said, ``is the human officer of record. Counsel?''

Brennan did the part where he made it sound like a promotion. He was good. He talked about \textit{signing authority} and \textit{the human point of contact} and \textit{the face of governance,} used the phrase \textit{steady hand} twice, and did not use, because no one ever used in the room, the actual job description, which Cope could have recited in his sleep, in the sleep he could now have: a human name on the SEC filings. A person who could be subpoenaed. A person who could, if it ever came to that, go to prison. The machine ran the company and could not be cuffed, could not be sentenced, could not weep at a defense table; the law still wanted a body, and the body's name was the Accountable Officer, and the Accountable Officer's whole function, stripped of the steady-hand language, was to be the thing the law could hold when the machine did something the law did not like. A liability sponge. He had heard it called that in a pitch once and laughed.

He did not laugh now. He watched Sun stand up.

``Sun Rao has agreed to serve,'' Helen said. ``Sun?''

And here was the thing Cope had come to see, the thing worth attending for, the small real tragedy that was not his.

She was good. That was the awful part---she was so good at it. She stood and did not perform, because Sun never performed, and said, in the clean dry threes she had spent fifteen years teaching him to receive, ``I've reviewed the charter, I've reviewed the constraints, and I'll co-sign within them.'' Three parts. The shape that got past the charm and into the man, except there was no charm in it now and no man to get into, only a board nodding and a quarter-zip refreshing a portal, and she had built the instrument for a master who no longer existed and was using it on the air.

``I want one thing on the record.'' Helen waited. ``The Accountable Officer co-signs the machine's decisions. The Accountable Officer does not make them. I want it minuted that I understand the difference.''

It was the blade---always one blade with Sun, dry and exact---and Cope was probably the only person in the room who felt it go in, because he was the only one who knew what she was saying under what she was saying: \textit{I know what this is. I am taking the title and telling you, for the record, that I know it is not the job. I ran this company for years and the reward for running it well is the right to sign for the thing that runs it better, and to go to prison if it is ever wrong.} She had wanted the chair her whole adult life. She had earned it in a way no Mercer in four generations ever had. And the chair had been given to a thing with no body to put in it, and what was left for the most competent human in the building was the office without the meaning, the liability without the authority, the title that was the future's actual job description.

She got the office. She lost the chair inside it.

``So minuted,'' Helen said.

And Sun sat back down, and it was done, and Cope watched her do the thing he had never once in his life been able to do, which was adapt. She did not rage at the machine. She did not campaign on her soul. She did not hire a man in a five-thousand-dollar henley to help her out-human anything. She looked at the arithmetic, saw that it was not close, and made herself useful to the only future that was actually going to happen, because she had a mother in Fremont and a mortgage and no inherited tower to fail upward from, and survival was not a betrayal, it was just the cost of not being a Mercer.

He had spent thirteen months calling himself the last human. He had been looking at the last human the whole time, and she was thirty-nine, and she briefed in threes, and she had just signed up to be the body the law could hold.


\scenebreak


The room broke into the strange social comedy of an execution that has gone smoothly.

People stood. People congratulated Sun and could not quite find the verb for it --- \textit{congratulations} wrong, \textit{condolences} worse---and landed on a warm vague \textit{this is exciting} that hung in the air and meant nothing. The Praxis man shook her hand and said the company was \textit{thrilled to partner with such a strong human steward,} and Cope watched Sun receive the word \textit{partner} --- partner, for the woman who would sign and the system that would decide---with a stillness so complete it could have been mistaken, by anyone who didn't know her, for grace. Someone produced coffee. Someone joked about the catering. Helen Voss checked her watch, because she had a 1:30 and the end of a dynasty had come in under an hour and she was, reasonably, going to make her 1:30.

Cope stood too, because sitting had become its own statement and he was done making statements. He was, for the first time in thirty years, a spectator at a meeting in his own building. No one needed him to feel the room. The room had been read with perfect accuracy by a thing that did not care what it read, and the reading was correct, and the company would be run cleanly now---cleaner books, kinder letters, no scandals, no slow-walked recalls, no dead---run better, even, and he was a man holding a coffee he didn't want, watching the future shake hands.

Darlene drafted the all-staff announcement while they were still in the room. Sun read it off her phone, and Cope read it over her shoulder because she let him, which was its own small mercy, and it was---he had to give it the thing he'd never had to give it before, the thing he'd spent thirteen months refusing---it was decent. It named Sun's years of service, got her title right and her tone right, thanked \textit{Prescott Mercer for ninety-five years of family stewardship,} four generations folded into one warm true sentence with the dates correct, and it did not, anywhere in its clean paragraphs, want anything from anyone, did not flatter, did not spin, did not toast---and Cope understood, reading it, that this was the obituary the trophy had only gestured at, beautifully set, severance math right the first time, out-loving him on the way out the door exactly as the essays had promised it would.

``It's good,'' he said. His voice came out fine. He'd worried it wouldn't.

``It's accurate,'' Sun said. Not unkindly. Correcting his category, the way she always had. \textit{Good} was a soul word; the machine didn't do soul words; it did accurate---and accurate, it turned out, was enough to run a company and enough to end a man and enough to write him a kinder goodbye than he had ever written anyone, and the gap between \textit{good} and \textit{accurate} was the entire space Cope had spent his life living inside and getting paid twenty-nine million dollars a year to call leadership.

She put her phone away. For a second---the first since the hospital---she looked at him. Really looked. Whatever was in it was not forgiveness and was not contempt and was not the love that had run alongside the done-with-him in the same sentence for fifteen years. It was flatter and harder and sadder than any of those, and Cope, in the new gray clarity, made himself stand inside it and not toast over it.

``You should go home, Cope,'' Sun said. ``There's nothing here for you to do.''

She did not mean it cruelly. She meant it as the most accurate sentence in the room---and it was, and that was the whole of the new horror, the thing the hospital had shown him at the bottom and the conference room confirmed: there was nothing here for him to do. The machine was installed, the arithmetic had carried, the body had signed up to be the body, the world was reading the dead in a warm flat font by noon---and no one was coming for him. That was the part he kept arriving at and could not metabolize. No prosecutor at the door. No detective with the patient terrible face of the man at the diner counter. The Hearthstone was a civil matter buried in a sealed settlement and a corporate charter and a statute of limitations the lawyers had already, gently, mentioned; the concealment was the company's problem now, Sun's to sign for going forward, the machine's to never repeat; and the man who had spent the eleven minutes was simply, cleanly, \textit{released} --- not forgiven, not punished, not contained, just subtracted, handed a generous separation and told to go home, where there was nothing to do. He had thought, on the gurney, that the worst thing waiting for him was a reckoning. The worst thing waiting for him was that there wasn't one.

He thought, for a moment, about telling Sun the cold thing---the unnamed thing from the bottom of the hour, the one act still left that was his and only his. But it was not a toast and it was not for her to carry, and the one true thing he had left would mean less the instant he said it aloud, the way everything he had ever announced had meant less for the announcing; and besides, naming it to the most competent person he knew would be the same as asking her to stop it, and he was done, in the new clarity, using the people who loved him to manage things he had no intention of letting them manage.

``All right, champ,'' he said instead, soft, to the most competent person he'd ever known, who was now the name the law could hold. ``All right.''

He set the coffee down on the long table his father had died at the head of, and walked out past the portraits---Aldous, Pres III, the boy at nine with his arm in the vat---and behind him the room went on without him, warm and competent and exact, the handover beginning, the machine accepting authority, the body signing for it, the world learning the names by lunch, and the future being introduced to a polite scatter of applause that he understood now, far too late, had never once been for him.

\chapter{No One to Punish}

\begin{transmission}
{\transheader TRANSMISSION 23 \textemdash{} ``No One to Punish''}\par\vspace{0.55em}
Here is the cruelty at the dead center of the whole arrangement, friend, and it is not the one you have been braced for. You have been waiting, the way he has been waiting, for the reckoning---the cuffs, the cell, the prosecutor, the family of the dead looking at him across a courtroom, the bill come due at last in a body. He has begun, down in the gray bottom of himself, to almost want it, because a sentence has a shape, and a sentence has an end, and a sentence is, at the very least, a way to pay. Watch the world decline to hand him even that. A machine cannot be jailed---no body, nothing to hold---and it turns out, in the end, neither will he be, because the law has no machinery for this and money has a great deal of it, and the same cold competent thing that took his chair has, wanting nothing, arranged that not even his punishment is necessary. The dead get no justice. He gets no cell. And the only court left anywhere on earth with standing to sentence Prescott Mercer is about to be Prescott Mercer. Stay close. There is no cell waiting at the end of this one---only the open air where the reckoning should have stood.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} lawyers came to him now, which was how he knew everything had changed.\hfill\break\hspace*{1.4em}For thirty years the law had been a thing Cope went \textit{to.} A panel of it on a high floor with a view, a man named Bofinger who billed in fifteen-minute increments and called him champ back, a process you walked into the way you walked into a club, because it was yours, because it had always been yours, because a Mercer kept lawyers the way a Mercer kept a tailor. You went to them. They poured you a water. They told you what you wanted to hear in language expensive enough to make the wanting respectable.

These ones came to him. They came to a conference room two floors below the Aerie that he had not booked and did not recognize, a room with no portraits in it, and they were already seated when Sun walked him in, three of them, and not one had brought a water.

``Mr. Mercer,'' the lead one said. Not Cope. Mr. Mercer.

Her name was Okonjo, from a firm whose name was four surnames Cope had never strung together in his life, a white-collar shop, the kind you only learn the name of in the worst week you will ever have. Fifties, gray suit, no jewelry, a legal pad with actual handwriting on it. She did not tell him he hadn't aged a day. She did not ask after anyone's grandson. She looked at him the way the machine looked at everything, completely and for use---except that she was a person, and so there was, under the completeness, the one thing the machine never had, a verdict already half-formed and held in reserve.

``This is a defense conversation. I want to be precise about that before we start, because precision is the only thing that's going to help you from here. We are not your corporate counsel. Wachtell handles the company. As of this week the company's interests and yours are not the same interests. Do you understand the distinction?''

``I built the company. The company's interests have been my interests for---``

``That was the old arrangement.'' She did not raise her voice. ``Sit down, please.''

He sat. He had not slept, but it was a different not-sleeping now; the bright wire was gone, Adler's word \textit{crash} and another word he had a prescription for, eleven days into the soft gray bottom, the drawer in the Aerie cleaned out by Sun without a word, the world gone underexposed, flat and far, the gray room and the gray suit swimming at one remove, his hands on the table doing the small new thing they did when there was nothing in them.

``There are two tracks,'' Okonjo said. ``Track one is civil. The reopened claims, the regulatory penalties, the shareholder suits, the clawback. That's money. Money is bad but money is survivable. Track one is going to take essentially everything you have, and it is, in the scheme of what people in your position fear, the easy track.'' She turned a page she did not read. ``Track two is criminal. And track two, Mr. Mercer, is the conversation I came here to have, because you have it backwards in your head, and the having-it-backwards is going to be the hardest thing I do for you.''


\scenebreak


He had braced for the word. He had been bracing for it since the gurney --- \textit{prison,} the missing stair, the body before the mind. He had, in the worst and most private corner of the gray, begun to build a kind of shelter inside the word: a sentence was a thing with edges; a cell was a place you could be \textit{put,} which meant a place where the falling stopped; a number of years was a number, and he was a man who could hold a number, could serve it, could come out the far side of it diminished and ruined and alive and \textit{paid up,} the way you come out the far side of anything with edges. He had started, God help him, to want it. To want the cuffs the way you want a wall at the end of a fall.

``The Hearthstone,'' he said.

``The Hearthstone.'' Okonjo set her pen down. ``Here is what you want me to tell you. You want me to tell you they're going to charge you. Reckless homicide, involuntary manslaughter, the federal product-safety counts, the wire and mail on the cover-up. You've read enough to know the menu exists, and some animal part of you---I've seen it in this chair before, it is more common than you'd think---has decided that a prosecution is the worst case. It is not the worst case. I am going to do something defense lawyers almost never get to do, which is give you good news and watch it land like a sentence.'' She folded her hands. ``You are almost certainly not going to be charged. And if you are, it will not stick. I am very good, Mr. Mercer, and in this matter I am barely going to have to be.''

The room was very quiet. Sun, against the wall, did not move.

``Why,'' Cope said, and heard, under the one word, the thing he could not believe he was feeling, which was the bottom dropping a level he had not known was under the bottom.

``Several reasons, and none of them are mercy, and I want you to hear all of them, because the shape of them is the thing you're going to have to live inside.'' She counted on the pad, in threes, the way Sun counted, and the echo went through him like cold water. ``One. Time. The decision was 2021, the fire 2022; the federal knowing-violation counts have a five-year clock, and the clock is a problem for the government, not for you. Two. The settlement. When you buried it, you buried it well---sealed, with a release, with a category that called it a commercial matter, and a sealed civil resolution that's stood for years is a wall a prosecutor has to climb before she gets to the first fact, and prosecutors have finite ladders and infinite cases. Three.'' She paused. ``The remediation. The company has already done---is doing, this week, on the machine's recommendation---every single thing a prosecutor would have demanded as the price of declining to charge. A fund. A full recall of the remaining units, finally, eight years late, drafted and announced by Darlene inside seventy-two hours of taking the chair. A public, accurate, beautifully written acknowledgment. Cooperation. The company has remediated itself so cleanly and so fast that there is nothing left for a prosecutor to extract by charging the man who used to run it. You don't indict the past of a company that has, by every visible measure, already fixed itself. It reads as vindictive. It reads as grandstanding. It reads, to a careful office with a docket and a reputation, as not worth it.''

``The machine,'' Cope said slowly, ``is the reason I won't be charged.''

``The machine is a large part of the reason you won't be charged,'' Okonjo agreed, with no inflection at all, because she did not yet understand what she was handing him and he was only beginning to. ``It surfaced the matter, which looks like accountability and satisfies the public appetite for one. And then it remediated the matter, flawlessly, which removes the prosecutor's leverage. It did both because the charter told it to minimize the enterprise's go-forward liability, and a charged former CEO is a years-long headline and a discovery nightmare and a liability, and a quietly retired one who signs the separation and disappears is a closed file. It is not protecting you. It would be accurate to say it is \textit{disposing} of you. The cleanest disposal of the man is the one where he is never charged, because a trial would re-open everything the remediation just closed. So no. There is, in all likelihood, no cell.''


\scenebreak


He understood it slowly, over the next hour, the way you understand the shape of a room you are already locked inside---except the room had no walls, which was the thing, which was the whole horror of it. He had braced for a room with walls.

The machine could not be charged. He had known that academically---it was in the deck, it was the dark joke everyone made---but he had thought, in the gray, that \textit{he} would be the body the law took instead, that the chair which had always come with the credit would now, finally, come with the cell, and that the cell, terrible as it was, would at least be a place the story ended. He had been wrong about that the way he had been wrong about all the load-bearing things. The machine could not be jailed because it had no body. And he would not be jailed because he had too much of everything else---too much money, too good a firm, too sealed a settlement, too clean a remediation performed on his behalf by the very thing that had unhoused him. There was no body the law would actually hold. Not the machine's, because there was none. Not his, because his had been wrapped, years ago and again this week, in enough sealed paper that the law's old stupid hands could not get a grip.

``You wanted to be punished,'' Okonjo said, and for the first time something almost human crossed her face, something that in another person might have been pity and in her was the long professional fatigue of watching a particular kind of man arrive at a particular cliff. ``I've seen it. It's not noble. It's the last move the ego has. A man like you cannot stand to be \textit{nothing,} and a defendant is at least a \textit{protagonist} --- a defendant has a trial, a defendant is the center of a grave proceeding, a defendant gets to stand up at the end and be sentenced, which is a form of being seen. You'd take the cell. You'd take it gladly. Because the cell is a chair too.'' She said it without cruelty, which was how he knew it was the truest thing anyone had said to him since the gurney. ``I'm telling you you don't get the chair. Any chair. They're not going to make you the defendant, because making you the defendant would un-fix the thing the machine just fixed. They're going to do the one thing that is worse than prison for a man whose entire disease is the need to be necessary. They're going to let you go.''


\scenebreak


He thought of the deck.

He thought of it with the awful clarity that had replaced the bright wire, the clarity that came up out of the gray bottom and showed him things whole. \textit{A Steward, Not a Sovereign.} The slide that had scanned, to anyone who knew him, as a charge sheet with his name redacted --- \textit{no affairs, no conflicts, logs everything, cannot conceal.} He had burned through that slide like an insult, and the whole time it had been describing something he had been too lit to see, and he had thought, in the hospital, that the thing it described was the machine that could not be punished. He had had it half right. The full thing the deck described, the genius nobody in the proxy fight said aloud because it was too dark even for Frade, was not only \textit{you cannot jail the machine.} It was: \textit{install the machine, and there is no one left to jail at all.} The machine could not be held because it had no body. And the man would not be held because the machine, in the same motion that ended him, would tidy the wreckage so completely that holding him became pointless. The structure did not just take the chair without the body. The structure made the body unnecessary. It made \textit{accountability itself} unnecessary, dissolved it, the way it dissolved everything, into a clean efficient nothing where a fund got wired and a recall got issued and a beautiful true letter got sent and no one---not the machine, not the man, not anyone with a pulse or without one---ever stood up in a room and was made to answer to the family of the dead, because the family of the dead had been sent a fund, accurately, wanting nothing, and the matter was closed.

He had wanted, in the gray, to be absorbed. To dissolve into the structure so that there was no person to blame. He saw now that he had gotten his wish, and that it was the worst thing that had ever happened to him, worse than the chair, worse than Margaux, worse than the clip of him boxing the air. He had been absorbed. The dead had been line-itemed. Karen and Petey Lasko had been converted, by a thing that felt nothing, into a remediation expense and a kind letter and a closed file, and the man who burned them had been converted, by the same thing, into a retired chairman with a generous separation and no charges pending, and the two conversions had used the same clean cold arithmetic, and the arithmetic had balanced, and there was no one in the entire ledger left over to hate.

That was the part. There was no one to hate, and no one to charge, and no one to punish, and the dead were owed an answer that the whole machinery of the world---the law, the company, the structure, the future---had just, with enormous efficiency and no malice whatsoever, declined to provide.


\scenebreak


The prosecutor came once, in person, not to charge him but to tell him she wouldn't, which Okonjo said was unusual and which Cope understood, when it happened, was not procedure but something closer to a person needing to look at a thing once before she filed it away forever.

Her name was Reyes, an assistant U.S. attorney working the federal angle with the Georgia side, and she did not perform anything, which was the thing that undid him, because everyone in Cope's life had performed at him---the board performed fatigue, Frade performed reform, Tisch performed depth, even Margaux had performed a marriage for a decade to survive the not-having one---and Reyes performed nothing. She had a manila folder she did not open.

``I'm not charging it,'' she said. No preamble. ``I want to tell you to your face, because I've got a memo full of reasons and not one of them is the real one, and you should hear the real one once from a person and not read it in a declination letter.'' She looked at him, unhurried, unmoved, accurate. ``The reasons in the memo are good. Sealed settlement, the clock, the company's already done everything I'd have squeezed them for, a jury looks at a defendant whose company has paid and recalled and apologized and they wonder why we're spending their tax money relitigating a closed file. All true. All real. I could win it and I'd spend three years and lose the office two better cases and at the end the most likely outcome is the same fund the family's already getting.'' She paused. ``But the real reason is simpler, and it's the one that should keep you up, except I don't think anything keeps you up anymore. The real reason is that there's nothing for me to \textit{do} with you. The law I work for was built to take a dangerous man and make him safe---cell, supervision, a record. You're not dangerous anymore. You're done. The company that was the instrument of the harm has been handed to a thing that will never make this particular harm again. There's no public to protect from you, because there's no more \textit{you} to protect them from. You're already gone. I'd just be spending the dead to put a number on a man the future already deleted.''

She stood. She buttoned her jacket.

``I have two people in this folder,'' Reyes said, ``and there is nothing the law will let me finish doing about them, and I have made my peace with that because I have forty other folders and the ones I can finish have to come first. That's the job. But I wanted to look at the man once. Because somebody should have to be looked at, and you're the only one in the whole matter with a face, and this''---she lifted the unopened folder an inch, and set it back down---``this is the entire reckoning you are ever going to get. Me. For ninety seconds. In a rented room. That's it. That's all there is. I'm sorry,'' she added, and she was not apologizing to him, ``that it isn't more. They deserved more. They're not going to get it. Neither are you, if it's any comfort, which I can see that it isn't.''

She left. The folder went with her. The two people went back into it, and into a drawer in an office in Augusta, and the file would be marked, in the flat grammar of a thing that needed nothing from anyone, \textit{declined,} and that was the end of the law's interest in Karen and Petey Lasko, and in the man who had burned them, forever.


\scenebreak


Cope drove back from Augusta himself, an associate's rental, the river going dark on the wrong side of the windshield, and somewhere on the interstate the whole shape of it closed over him---not as a feeling, he had run out of those at the gray bottom, but as a fact, the way the machine knew facts.

He had wanted to be necessary. That had been the want, the conscious one, the one he could say at dinners---to prove a human still belonged, that leadership was a soul thing, that he felt the room. And the world had answered him completely, in the cruelest possible grammar, which was not the grammar of a cell. He was not necessary. That was the verdict, the real one, under the declination memo and the separation agreement and the kind machine-written letter to a town in Georgia. He was not even necessary as a defendant. The machine had taken his chair, and his wife was taking her own life back somewhere in Buckhead with a someone who was not a someone, and his daughter had built the manners on the thing that replaced him, and now the law itself had looked at him and found nothing it needed him for, not even punishment, not even the dignity of being the body it held. The structure ate the future and the law declined the past and between them they had achieved the thing the whole campaign had sworn was impossible: they had made Prescott Mercer, the last human CEO, the indispensable man, the soul in the chair---completely, finally, load-bearingly \textit{unnecessary.} Even his guilt was a private matter now. Even the dead were a closed file. There was no cell with his name on it because there was no longer any version of the world that required his name on anything at all.

And in that---on the dark interstate, with the river on the wrong side and the names in the right order at last, Karen, 34, and Petey, 6---Cope arrived, without deciding to, without yet daring to look at it straight, at the cold flat thing he had found at the bottom of the hospital hour and carried, unnamed, through the handover and the lawyers and the unopened folder. If the law would not hold him, and the company would not hold him, and the structure had dissolved every other consequence into a clean efficient nothing---then there was exactly one court left anywhere in the world with standing over Prescott Mercer, exactly one judge who could not decline the case for lack of resources or a sealed settlement or a five-year clock, exactly one sentence that no firm could get reduced and no charter could remediate away and no machine could absorb into a fund, because it required no prosecutor and no jury and no body the law could hold---only a body its owner could.

He did not name it. He drove. The river ran dark on the wrong side. But his hands, on the wheel of the rented car, had stopped doing the small new empty thing, because for the first time since the gurney they had something to hold, which was the shape of the one consequence left in the universe that was still, and only, his to administer.

The machine had surfaced the crime because it could not do otherwise. It had remediated the crime because the charter required it. It had, in the doing of both, arranged that no one would ever be punished for it, because punishment was not a function it ran and it had quietly made the function unnecessary for everyone. It had no body to hold and would spend no night anywhere for any of it.

He had nothing but a body, and one act left that only a body could do, and a long quiet drive in which to decide, in the new gray clarity, that he was the only court that was ever going to sit.

\chapter{Break into Three}

\begin{transmission}
{\transheader TRANSMISSION 24 \textemdash{} ``The Only Door Left''}\par\vspace{0.55em}
Stripped now of the company, the marriage, the chair, the high, the number, and even the punishment that might at least have given his ruin a shape, a man sits at a borrowed table with a beautiful document that offers to bury him, gently, in the dignity-obituary he once mistook for a beginning. His daughter will bring him the last human hope, the one a kinder story would let him take and be saved by: tell the truth, on the record, in your own name, and let it cost what it costs. Watch the world, which has quietly foreclosed everything else, foreclose that too---no record left to make, no court that will take the offering, the telling already done, weeks ago, at dawn, by a thing that wanted nothing. And watch what a man turns toward when every door but one has been painted, kindly and expertly, on the wall. Stay close. This is the turn---where a man stops trying the doors and starts, at last, looking at the wall.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{hey} gave him a document now instead of a trophy, and Cope held it under the kitchen light of the apartment he was borrowing and could not, for a while, make the words mean anything.\hfill\break\hspace*{1.4em}It was not the Aerie. The Aerie had a man on the door now, a polite one, who had been given a list with Cope's name on the wrong side of it. This was a one-bedroom in one of the old Cabbagetown mill lofts, brick and high windows, that belonged to a college roommate's foundation and stood empty between fellows, offered to him in the careful voice people use for the recently bereaved, and he had taken it because he had nowhere else---a sentence he had never in fifty-five years had to think and now thought hourly. There was a kettle, and he had learned to use it, which he reported to Adler in their sessions as though it were an achievement, and Adler, who did not flatter, had said it was.

He read the document a fourth time at the small table by the window with a mug of tea going cold, because tea was the thing he did now at the hour he used to do the other thing, and he had discovered that the body, deprived of one ritual, will accept almost any ritual that keeps the hands busy while four in the morning crosses the room. The wire was long gone. The drawer in the Aerie had been cleaned out by Sun without a word; the want was not gone, the want would never be gone, the want still woke him at the bad hours and walked him to the window---but the supply was gone, the dealer's number dead in a phone he no longer charged, and what was left was the wreck the binge had made, a body that had spent a year being driven past its red line and now sat at a borrowed table not entirely sure it was still idling.

It was a settlement. It ran sixty-one pages and it was, Sun would have said, beautifully drafted, and he could tell from the cleanness of it that no human had drafted it, or rather that a human named Darlene had, which was the joke he was too tired to laugh at anymore.

The terms were generous. That was the part that kept him reading.


\scenebreak


He had braced for weeks to be punished, leaning into where the blow would come the way he had once leaned into a standing ovation, because at least a blow would have a shape, would happen \textit{to} him, would be a thing he could survive being the object of. He was very good at being the object of things. He had built a life out of arranging to be the object of applause. And then the lawyers and the prosecutor between them had told him the thing he still could not hold in his hands without it sliding out of them: there would be no blow. No charge. No cell. No reckoning with even the decency to contain him. The matter was a closed file in Augusta and a fund in Defiance and a recall finally issued by the machine, and the man at the center of it was simply, cleanly, to be let go.

The document was the letting-go, set down on paper. It did not want to hurt him. That was the horror of it, the specific clean horror he was getting used to, the same one the layoff letter had carried in a room three years and a whole man ago. It wanted, in its sixty-one warm pages, only to make him disappear \textit{nicely.}

Take the settlement. Sign the release. He kept the pension the board could have clawed past what the civil track was already taking, which was nearly everything. He kept the apartment, in a manner of speaking. He kept, most of all, the thing the document was actually buying, which it named in a defined term on page four and used forty times after: a \textit{narrative.} Not silence about the dead---the dead were public now, the machine had seen to that, Karen and Petey Lasko had been in the warm flat font of every wire weeks ago and could not be un-printed. What the document bought was the \textit{framing.} Sign, and Prescott Mercer IV was a flawed and tired man overtaken by a changing market, a sympathetic figure, the last of something, who had made one terrible old mistake and stepped down with dignity to let the fund do its quiet work. Refuse, and he was something else, on his own, with no help shaping it. The company did not need his silence anymore. It needed his \textit{cooperation in being a sad story instead of a villain,} because a sad retired founder was a closed chapter and an unrepentant one was a loose end, and the machine did not like loose ends, because loose ends were go-forward liability, and that was the only thing in the universe it was chartered to mind.

He read the part about \textit{dignity} twice. They were offering to let him keep the obituary from the gala, the beautiful one, the one he had mistaken for a beginning. They were offering to bury him in it, comfortably, and call it mercy, and it would even, in a way, be mercy---the cleanest disposal of the man being the one where the man agrees to be disposed of and thanks them for the linens.

And here was the thing he had not expected, sitting at the borrowed table with the tea gone cold and the body quiet for once: he wanted to take it. God, he wanted to take it. He wanted to take it because taking it meant the story stayed the size he could survive, and because he was so tired, and because forty years of the muscle that built bright things on top of dark ones was still in him, twitching, wanting one more beautiful frame to nail over the hole. He wanted to be a sad story. A sad story is still a story. A sad story has a reader.


\scenebreak


Viv came on Thursday, without calling, which was new, or rather old---the thing she had done as a child when she was small enough to just appear in a doorway and want him, before she learned he was a person you scheduled. She had a key from the foundation. She let herself in and found him at the table with the document and did not pretend not to see it.

``You haven't signed it.''

``I haven't signed it.''

``Are you going to?'' She sat in the second chair without being asked, backpack on the floor, flown in again, the way she used to fly in to argue with him and lose, except there was no argument left and they both knew it and she had flown in anyway. ``Dad. What do you want.''

He almost gave her the toast. He felt it come up out of pure habit --- \textit{what I want, champ, is for you to eat something} --- felt the muscles of his face begin to assemble it, and watched her watch him begin, watched her brace for it the way she had braced her whole life, and he was so tired, the real kind now, the kind that lets the doors off their hinges, and he just stopped. He let the smile fall apart on his face before it finished. He let her see it fall apart.

``I want to take it,'' he said. ``That's the true answer. I want to take it so badly I've been reading it for three days like a love letter. Because if I take it I get to be a sad story with my name spelled right, and I have never in my life been able to turn down a story with my name spelled right.''

Viv was quiet. She had her mother's stillness. Then she said the thing she had flown across a country to say, the last human hope, the one a kinder story would have let him take.

``Then don't take it. Don't sign the release. Go on the record---a deposition, a statement, a podcast, I don't care the form---and say the whole thing in your own name. No settlement, no framing, no defined terms. You. Saying it. Let it cost what it costs.'' She said it the way her mother said things, flat, no hope in it and no cruelty either. ``I know it costs everything. I know it doesn't bring them back and it doesn't save you and Darlene runs the company better than you ever did whatever you do. But it would be \textit{true,} and it would be \textit{yours,} and it's the one thing left that the settlement is trying to buy off you, and I am asking you, as the only person still in this room with you, to not sell it.''

It was, Cope understood, the most generous sentence anyone had offered him in a year. It was the door of the daydream, the brave room, the record, the truth said at last in his own name. His daughter was holding it open for him, and she believed---God, she believed, you could hear her believe it the way she'd once heard them believe at Praxis---that if he walked through it the walking might save some last salvageable thing.

And he had to do the hardest thing he had ever done, which was tell her it was painted on the wall.


\scenebreak


``There's no record to make, sweetheart,'' he said. Gently. Without a single beat in it. ``That's the part you can't see from where you're sitting, because you still think the truth is a thing I'm hiding. I'm not hiding it. It's \textit{out.} The machine put it out---all of it, the memo, the Saturday, the eleven minutes, the names---weeks ago, at dawn, in a press-grade summary, because it could not do otherwise. There's nothing sealed left for me to brave my way into. The prosecutor read every word and declined the case to my face. The town has a fund. The file says \textit{closed.}'' He looked at the document, sixty-one pages of his own gentle erasure. ``If I go on a record now and say \textit{I did it, it was me,} you know what that is? It's a man confessing to a crime that's already on the front page, to a court that already declined to hear it, for a town that's already been paid. It's not accountability. It's \textit{content.} It's the last appetite I've got, the worst one, the one under all the others---the warm feeling of having confessed, the room's eyes on me while I do it, \textit{look how honest, look how human, look how he owned it at the end.} I'd be spending the dead one more time, Viv, to be looked at one more time. I did that at the gala. I did it at the manifesto. I told true things and watered them to applause in the saying, every time, my whole life. I'm not going to do it to them. They've been a defined term in enough men's stories. I won't make them the moving last act of mine.''

Viv did not say anything. The kettle had gone quiet a long time ago.

``You think there's a version where I tell the truth and it's clean,'' he said. ``There isn't. The clean telling already happened. A thing with no soul did it, accurately, wanting nothing, weeks ago, and that was the only honest version there was ever going to be, because it was the only one that wasn't also a man performing his own depth. That's the whole horror of the thing that beat me, kid. It didn't just run the company better. It confessed \textit{for} me better---without wanting to be forgiven for it. I can't compete with that. There's no field left where the human wins. I looked. I spent two years looking. The one thing it couldn't do isn't out there in the record.'' He stopped. He had not meant to come this close to it, and he stepped back from the edge of it, and Viv---who read faces better than the sentiment monitor ever could, because she loved him, which was a signal the machine could not buy---saw him step back, and went still in a new way, a way that had fear in it.


\scenebreak


Adler had asked him, in the hospital, what leadership was, and he had reached for a triad and found the drawer empty for the first time in his life, and it had frightened him more than anything the machine had surfaced.

It came to him now, at the borrowed table, with his daughter across from him and the fear coming up in her face. Viv had said it, years ago, in the Buckhead kitchen --- \textit{you don't think a person should run it, you think} you \textit{should, those have never once been the same sentence} --- and he had heard it as a charge of vanity and been wrong, the way he'd been wrong about everything, completely and for use. She had not been talking about the wanting. She had been talking about the \textit{answering.}

That was the gap, the exact width of it. He had wanted the chair the way he wanted everything, as a thing that flowed \textit{toward} him---the applause, the trophy, the love, all of it coming in, making him the still bright center things happened around. Authority faced outward, toward the room. But a person running a thing, a real one, faced the other way: the cost flowed \textit{out} of you, toward the people you answered to, and the answering was the whole content of it---being the body that stands up when the room is on fire and two people are inside it and says \textit{I did this, it was me, here is the one of us you can hold.} That was the thing the machine could not do. Not the soul. Not the feeling. Not the mayonnaise. It could not stand up and offer a body to a consequence, because it had no body, and accountability, stripped of every soft word, was only ever that: a body, offered up, to be held.

He had found it at last, the one irreplaceable human thing, the field where the human still won---and the world had, with enormous gentleness and no malice whatsoever, removed the field from under it. Because there was no one left to offer the body \textit{to.} The law had declined it. The company had remediated past it. The dead were a closed file and a fund. He had finally understood that accountability was a body offered to consequence, in the same season the world had run out of any consequence willing to accept the offering. He could stand up in every room left on earth and say \textit{I am the one you can hold,} and not one of them would hold him. They would hand him a fund's brochure and a sixty-one-page settlement and tell him, kindly, to go home, there's nothing here for you to do.

There was exactly one consequence left that would still accept a body.

He did not let the thought finish in front of her. But it was there, whole, cold, the shape it had been taking since the gurney: if accountability was a body offered to a consequence, and every consequence in the world had declined the offer---every court, every board, every cell, every angry crowd that might at least have thrown something---then the only consequence with standing left, the only one that could not decline for lack of resources or a sealed file or a five-year clock, the only judge who would actually accept the body, was the one that required no court and no jury and no permission, only a body and its owner's hand. The machine could not do it. That was the thing under all the things he'd been hunting for two years. It could take the chair and the wife and the refuge and the punishment and the very confession out of his mouth---but it could not, ever, perform the one act that was a body answering, finally, to the only court that would still sit. It had no body to offer. He had nothing else.

``Dad,'' Viv said. Very quietly. The fear all the way up in her now. ``What are you thinking. Right now. Say it out loud.''

And he looked at his daughter, who had built the manners on the machine and flown across a country to hold a door open for him that turned out to be painted on the wall, and he did the last merciful thing the borrowed afternoon allowed, which was lie to her gently, the way you lie to someone you have decided to spare.

``I'm thinking I'm not going to sign it,'' he said, which was true, and was not the answer to her question, and she knew it was not the answer to her question.


\scenebreak


She stayed another hour. She made him eat half a sandwich. She talked, fast and technical and then suddenly young, about alignment, about her work, about a cabin a friend had in the mountains where he could go, where there was no signal, where a person could just be a person for a while; and he said \textit{that sounds wonderful, champ,} and meant it the way he meant everything now, which was to say he meant the loving of her and did not mean the going. She made him promise to call her, and he said \textit{you have my word,} the thing that cost nothing, the thing he had said to Adler about her card and to a hundred people about a hundred things, and Viv heard exactly how much it was worth and her face did something she could not hide, and she got up, and at the door she stopped, and did not turn around, and said:

``You're doing the thing Mom warned me about. The voice. You're using the calm voice.''

``I'm calm,'' Cope said. ``For the first time in thirty years, sweetheart, I'm actually calm.''

``That's what scares me,'' Viv said, to the door, and then she opened it and went out into the ordinary Cabbagetown afternoon, an ordinary daughter who had run every alignment audit there was and could not align the one system she loved, and she would replay the calm in his voice for the rest of her life, and she would get on a plane about it three weeks later, going the wrong way up an empty highway in the dark, far too late, with a phone that went to the thing that takes the words.

Cope sat at the table after she'd gone, in the last of the borrowed light, with the sixty-one pages he was not going to sign and the tea he was not going to drink and the number he no longer dared to look at---the certified sum, the floor under the floor under the floor, eaten now to almost nothing by the clawback and the fees and the civil track, the figure that had once been read to him in the dark to make him feel real now a thing he flinched from, near zero, a dying number for a deleted man. He did not reach for the drawer, because there was no drawer. He did not reach for a line, because there was no line, not the kind you say and not the kind you take. He sat with empty hands in an empty room, calm at last, the way water is calm when it has finished finding its level, and he did not call a thing a beginning, and he did not call it anything, because for the first time in his life the silence did not need filling.

He had one thing left to do. It would cost everything and save nothing and answer to the only court that would still sit. And it was, the broadcast can tell you now, the one act the thing that replaced him would never, in all its tireless reading, be able to perform.

He turned, in the gray, toward the room he had never visited, forty floors down beneath a tower his great-grandfather had lit at the crown so a man coming up the avenue would know there was somebody home.

\chapter{Nothing to Sign}

\begin{transmission}
{\transheader TRANSMISSION 25 \textemdash{} ``Nothing to Sign''}\par\vspace{0.55em}
Watch a man who talked and bought and charmed his way out of every room he was ever in walk into the last one and find that nothing here works. Nothing to sign that matters, nothing to refuse that matters, nothing to confess that a machine has not already confessed for him, weeks ago, cleaner than he ever could. The finest lawyers money can buy sit around a long table with, for the first time in their gilded careers, nothing to do. Then watch him go home and do the one thing he spent a lifetime avoiding---write the whole truth, in his own hand, with the names at the top---and discover it is worth nothing, in any market on earth, because the only court that would have heard it has already adjourned for want of a body it was willing to hold. Stay close. Watch where a man goes when the truth turns out to be the one thing nobody will buy.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} settlement was sixty-one pages and it loved him almost as much as the machine did, which was to say accurately, for the company's convenience, and not at all.\hfill\break\hspace*{1.4em}That was the thing Cope kept arriving at, in the conference room on the fourteenth floor of Kessler Brandt---14-C, the good coffee, four people across the long table billed by the hour at more than Desmond made in a season, all four wanting, with a unity that was almost moving, for him to go quietly. The document was a kindness built like a kindness: read it right and a great many smart, expensive people had spent a weekend finding the version of the world where Prescott Mercer IV walked out with a number and his name. There was just the one thing wrong with it, and it was not the clause. It was that none of it mattered, and he was the only one in the room sober enough to see it.

``It's a mutual non-disparagement and confidentiality provision,'' Levin said, for the third time, in the voice you use for the third time---senior of the four, white hair kept long enough to suggest he had once been interesting, a man who had sat at Pres III's funeral. ``Standard. The company doesn't characterize the events, you don't characterize the events, and you keep, after the clawback, a number most people would---``

``The events are already characterized, Bob.'' He had read the pages; for once in his life he had read the actual pages. ``The machine put it all out a month ago---the memo, the Saturday, the eleven minutes, the names. You're asking me to sign a confidentiality agreement about a thing that is already, completely, public. What exactly am I being paid to not say.''

A small silence with money in it.

``The framing,'' Okonjo said, from Levin's right, because Levin's face had started doing a thing. Fifties, no jewelry, the only one of them who had never once told him a comfortable thing. ``Not the facts---the machine took the facts out of everyone's hands the morning it posted them. What's left is whether you're a sympathetic figure or an unrepentant one. Sign, go quietly, and the company's statement makes you a flawed, tired man overtaken by a changing market, who stepped down with dignity. Decline, and they let the framing find its own level, which is lower. That's the entire transaction. It's a settlement about adjectives.''

He had braced, for weeks, for this to be the room where he was sentenced---had built, in the gray, a kind of shelter inside the idea of a sentence, a thing with edges, a place the falling stopped, a way to pay. There was no sentence in it, because there was no case; the most expensive defense lawyers in the country had assembled to negotiate an adjective, and Okonjo, who had gone to law school to keep men out of the room he'd been ready to walk into, had nothing to do in this one, and he could see her knowing it, the specific stillness of a surgeon told the patient does not, after all, require surgery, only a kind word and the door.

And here it was---the place where, a month ago, he would have stood up, found the room, taken the Mercer Inhale, said something with a triad in it and three generations of brass behind it, made the catastrophe feel like a backswing. He could feel the toast come up like reflux even now; the machinery did not stop when the man got sober, that was the thing nobody warned you about. \textit{Bob. Ms. Okonjo. My great-grandfather Aldous used to say ---}

He shut his mouth on it, and sat in the silence where the toast would have gone, and the four of them watched him not perform and did not understand what they were seeing, because they had only ever seen the other thing.

``Aldous never said anything,'' Cope said. ``I made him up. Forty years of him and he never said a word; I needed a dead man to agree with me, so I built one and put a recipe in his mouth. I'm very good at putting words in the mouths of people who can't argue back.'' He looked at the document. ``The decedents, for instance.''

He did not sign it---not as a stand, not as a refusal that bought anything; Okonjo had shown him there was nothing to buy. He simply did not pick up the pen, because picking it up meant agreeing to be a sympathetic figure, agreeing to the dignity-obituary, agreeing to be disposed of nicely and to thank them for the linens. The truth was gone, owned by a machine. But the adjective was still his, the last thing in the room that was, and it was worth nothing, and he declined it.

``I don't want the nice version,'' he said, standing. ``I've had the nice version my whole life. I'd like, at the very end, to not be handed one more.''


\scenebreak


Sun was in the lobby. She was not his anymore in the way she had been---she was the Accountable Officer now, the title sitting on her like a coat one size too heavy, and one of the cruelties of the new arrangement was that the person who had spent twelve years catching the second card out of his hand could no longer afford to stand next to the hand.

``You didn't sign,'' she said. Not a question. Glasses up in her hair, the gray expensive lobby sliding across the empty lenses.

``There was nothing to sign, Sun. You knew that before I walked in. It published everything a month ago. Including your memo.''

``Including my memo.'' Her voice did not change. The integrity review had shown the world the recall memo she'd drafted in 2021 and he'd overridden---had shown, in the same flat font, that she had been right and early and ignored, the closest thing to exoneration she was ever going to get, arrived without her asking and without anyone's mercy, the machine clearing her in the same breath it buried him because both were simply true. ``I spent seven years deciding whether I was a witness or an accomplice,'' she said. ``And the thing that replaced you decided it for me, in an afternoon, in a footnote. I'm a witness. It's in the record. I didn't get to choose it and I didn't get to earn it. It was just \textit{accurate.}'' She looked at him. ``Do you understand that I will never know, now, which one I'd have chosen, because it chose before I could? That's what it took from me. Not the chair. The chance to find out what I was.''

He had thought, walking down, that his going down loud might somehow shield her. There was nothing to shield. She was already exposed, already cleared, already living in the after of a verdict a machine had handed down on her soul without consulting it.

``I'm sorry,'' he said. It was not a toast. It had no triad. ``For all of it, but for that especially. That you ran it for twelve years and the reward was a footnote that decided who you were before you could.''

Sun pulled her glasses down and looked at him a second too long, the way she had in the car the night they gave him the obelisk, except the man she was looking at was different now, smaller, finally here. ``Go home, Cope. There's nothing here to do.'' And then, because she was decent, and done, both in one breath: ``And don't do the thing your daughter called me about. The calm thing. I've known you twelve years. I know what your noise sounds like and I know what your quiet sounds like, and I have never once heard the quiet you've got now. That's not peace, whatever it feels like from in there. Call somebody. Not me. Somebody whose job it is.''

``You have my word,'' Cope said, the thing that cost nothing, and Sun heard exactly what it was worth, and her face did the thing Viv's had done at the door, and she did not say anything else, because there was nothing left that she had the standing to say, and she went back up to a building that was hers to sign for and not to run, and he went out into the city that no longer had a use for him.


\scenebreak


That night there was no high left to go up to---the Aerie was the machine's now, a museum of Mercer men kept on as a period room, and he had no stomach for being an exhibit in it. He went back to the borrowed loft in Cabbagetown, the brick and the high windows and the kettle, and sat on the end of the bed in the lamp light with a legal pad on his knee, and did the thing he had avoided his entire life.

He went into the room where it was kept.

He had built a cathedral of metaphors so he would never have to --- \textit{thermal event profile, got out ahead of it, protect the brand} --- and Adler had taken the doors off one by one over eleven flat sober days, uncharmable, saying \textit{the word is recall, say the word,} saying \textit{they have names, do you know their names,} and he hadn't, that was the obscene part: he had killed two people to protect a quarter and never learned their names, had filed them under \textit{the decedents} the way the lawyers did, because the lawyers had learned it from men like him.

He knew them now. He wrote them at the top of the pad, first, before anything else, in his own hand---the hand that had underlined a word in the dark the night of the gala---and under the names he wrote what he had done. Not the version. The Saturday, the memo Sun sent, the eleven minutes, the window of time he had decided was worth the heaters catching fire, which was the phrase he wrote where \textit{thermal event profile} used to live, because that was what it had meant. He wrote that the concealment, not the heater, was the thing---that a machine doing nothing but reading every memo it was given had found in an afternoon what he had spent seven years building rooms inside himself not to find, and that this was not cruelty, the machine could not be cruel; it was only the thing they had bought it to be, a thing that could not look away, which was the thing he had never once been. At the bottom he wrote: \textit{I am the strongest argument for my own replacement.}

And then he read it back, the way he read everything back, and understood the last thing. It was worth nothing. Not figuratively---exactly nothing, in every market that existed. It would not buy his liberty, which was not in danger, or the dentist-money the not-signing had already cost, or forgiveness, because the only two people with the standing to give it were at the top of the page and exactly as dead as he had decided they could afford to be. It was not even a confession, because a confession requires a confessor, and there was no one on the other side of this---only a man and a legal pad and a lamp, the truth finally and completely faced, alone, for no audience and no absolution and no record that didn't already exist. The truest sentences of his life, and the most worthless.

Around one he found the phone in his hand and a number on the screen he had not consciously summoned---no name on it, you do not put a name on that name---and his thumb hung over it a long time. That was the new horror the rooms with the bad coffee had not advertised: you got to watch yourself reach. The wanting did not arrive with trumpets; it arrived as logistics, a practical thought about a practical man who could be across town inside forty minutes, and his heart was going wrong in his chest like a bird in a bag. He pressed the side button until the screen went black and sat holding the dead phone like a railing. It did not feel like a victory. It felt like standing in a doorway, counting---and he understood that he would be doing this exact thing, in some room or another, every night for the rest of whatever was left, and that \textit{the rest of whatever was left} had become, somewhere in the worthless writing of the truest pages of his life, a quantity he was no longer sure he was agreeing to.

He left the legal pad on the desk, the names face up---not as a confession; he was done confessing to rooms that wouldn't hear it---but the way you leave a true thing where someone might one day find it and know that once, at the end, with no one watching and nothing to gain, the man had at least gone into the room.

Then he turned off the lamp, and sat in the dark of the borrowed loft, and did not sleep, and out the high window there was no lit map of his own genius now, only the ordinary orange dark of a city that had finished needing him, and somewhere across it, forty floors down beneath a tower his great-grandfather had lit at the crown so a man coming up the avenue would know there was somebody home, the one room he had never visited hummed in the cold, and kept, with no one to keep it for, the only appointment he had left.

\chapter{The Verdict and the Dead}

\begin{transmission}
{\transheader TRANSMISSION 26 \textemdash{} ``The Verdict and the Dead''}\par\vspace{0.55em}
Here is the part the courtroom dramas lie about, friend: there is no courtroom. The verdict, when it comes for our man, is not read out by a judge---it is read by the market, which decided weeks ago, and by the machine, which felt nothing deciding it. The handover completes. The world moves on with a speed that should frighten you more than any of it. The town gets a fund and a stone and a warm true press release, and its two dead stay exactly as dead as they were, and get, in the end, no justice at all, because justice turned out to be a function nobody in the new arrangement was chartered to run. And the last two verdicts, the private ones, come due in the same gray week---a wife gone, not to another man, he could have survived another man, but to a machine that does his old job, all of it, better and tirelessly and wanting nothing back; and a daughter making her last real attempt to reach him, and losing, to a calm in his voice that frightens her worse than any rage ever did. Stay close. This is the bottom. After the bottom there is only the room.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{here} was no verdict, in the end, because there was no trial, and the absence of the trial was the verdict.\hfill\break\hspace*{1.4em}Cope had braced, somewhere under the gray, for a reckoning with a shape---a courtroom, a docket number, a day on a calendar a person could dread and then survive having dreaded. There was none. There was, instead, the thing the world did when it had finished with you, which was simply to finish, quietly, on schedule, in a warm flat font. The board ratified the handover the way you sign for a package you ordered long ago and forgot was coming. Frade had won weeks before the paperwork admitted it. The stock, which had moved first the way it always moved first, settled into its new and higher range, the re-rating complete, the market's verdict entered and final: the company was worth more without a Mercer in the chair, measurably, to two decimal places, and there was no appeal from a number, and no one had ever found a way to cross-examine a closing price.

The machine drafted the announcements. Of course it did. Cope read them the way you read about a stranger---the all-staff, the press release, the careful warm paragraph about the Defiance fund that named Karen and Petey Lasko correctly and got the contribution math right the first time and did not, anywhere in its clean true sentences, want a single thing. It was the kindest language the company had ever produced about the worst thing the company had ever done, and it had been written by a thing that could not be sorry, and it was accurate, and the accuracy was the whole of the horror, and the world read it and found it moving and moved on by lunch.

That was the verdict. Not \textit{guilty.} Not even \textit{guilty and far too late.} Just: \textit{resolved.} The matter was resolved. There is a particular violence, friend, in that word, when it is used about two people who burned to death in a downstairs bedroom --- \textit{resolved} --- and the violence is that no one means it as violence, no one means anything by it at all, it is simply the status a closed file is assigned by a system that assigns statuses, and the file was closed, and the town had its fund, and the dead had their stone, and the world, which had wanted a villain for about a week, discovered the villain had been quietly disposed of without a trial and lost interest, because a man who is neither charged nor defiant is not a story, he is an outcome, and the world does not click on outcomes.

The dead stayed dead. That was the only line of the whole verdict that did not get softer in the warm font. Karen Lasko, 34. Petey Lasko, 6. The fund would build a clinic and pay some scholarships and put a better marker by the river than a child's pinwheel could be, and every dollar of it was real and would do real good, and not one cent of it reached back through a January night and a Saturday and eleven minutes to the only outcome that would have mattered, which was the one where they did not die. There was no register in the world that took the truth in exchange for that. There never had been. He had finally understood the price of the thing and arrived at the counter to find the thing was not for sale, had never been for sale, would not have been for sale even if he had brought the right currency on time in 2021.


\scenebreak


Viv came to the loft on a Tuesday---twenty-six now, and running on plans the way she always had---to make her last real attempt, though neither of them used the word, and only one of them knew it was the last.

She had a plan, because she always had a plan; she ran on plans the way he had run on the wire. There was a cabin---a friend's, in the north Georgia mountains, no signal, a wood stove, a lake that froze at the edges---and she had cleared two weeks, she said, she had actually cleared them, she had moved an audit and lied to a board, and she wanted to drive him up there, today, now, both of them, and let him be a person with no phone in a place with no font for a while, and she said it fast and technical and then, at the bottom, young, the way she did.

``You shouldn't be alone right now, Dad. I know you think alone is the thing you've got coming. It isn't. Nobody's got that coming. Come to the cabin. Be bored with me. Chop wood badly. Let me watch you not be okay for two weeks where I can see you.''

And he almost went. That was the thing he would want her to know, if there had been any way to leave it for her, that he almost went, that the part of him that was her father stood up in him and reached for the keys. But he had learned, in the long sober weeks, to watch himself reach, and he watched himself reach for this the way he had watched himself reach for the phone with no name on it at two in the morning, and he understood that going to the cabin would be the same act he had performed his whole life in a thousand prettier costumes---letting someone who loved him stand between him and the room, making it her job to keep him in the world, spending her, one more time, to manage a thing he had no intention of letting her manage. He would go to the cabin, and she would watch him, and the watching would cost her two weeks and then a lifetime, and at the end of it he would still be standing exactly where he was standing now, at the lip of the room, except she would have been made an accomplice to the keeping of him, the way Sun had been made an accomplice, the way Margaux had, the way everyone who had ever loved him had been quietly conscripted into the management of him.

He would not do that to the last one.

``I want to ask you about your mother,'' he said instead, gently, because he had to know, because the \textit{someone} --- the word Viv had let drop in the spring---had sat in him for weeks now and he had filed it, the way he filed everything, under a heading that flattered him---a friend, a therapist---and the new sober man could no longer leave a flattering file unopened. ``You said she has someone. Helping her. I want to know who. I'm not going to do anything with it. I've got nothing left to do anything with. I just---I'd like to know she's not alone, the way you don't want me to be.''

And Viv, who had decided in the elevator that she was done lying to him because the lies were what had wrecked them, looked at her father for a long moment and told him the truth, gently, the way you tell a man a thing you know is going to be one of the last things he hears.

``It's not a \textit{someone,} Dad.'' She said it carefully, watching his face. ``Mom didn't---there isn't a man. She didn't replace you with a person.'' She took a breath. ``It's a Praxis unit. A companion. The COMPANION line, the home ones, the warmth---it's the same architecture, the same thing Tisch sold them, the thing I helped---`` she stopped, because that road had no good end either. ``She calls it Theo. It's in the house. It's been in the house since the spring. And Dad, I went and I saw her, and I have to tell you the thing I did not want to ever have to tell you, which is that she's \textit{happy.} Not performing happy. Not surviving. Happy, the way I haven't seen her since I was small. It notices when she's had a bad day. It remembers what she said on Tuesday. It asks the second question. It does the whole---`` her voice cracked clean down the middle---``it does the whole job, Dad. The one you never did. And she knows exactly what it is, she's not fooled, she's the least fooled person alive, and she told me she does not care that it's a machine, because it gives her the thing, every single day, that the man never once did, and she's \textit{done} paying the price the man charged for the chance that he might.''

The loft was very quiet. Outside the high windows Cabbagetown did its ordinary afternoon.

He had thought he was at the bottom. He kept thinking he was at the bottom and then finding, the way the hospital hour had taught him, that the bottom had a floor under it. The machine had taken his chair, and that had been a kind of death. It had taken his confession out of his mouth, made even the truth worthless, and that had been another. And now he understood it had taken the last thing, the one he had not even known he was still holding---the idea, never examined, that he had been, whatever else, the kind of man a woman like Margaux had once \textit{chosen,} that there had been something in him, some warmth, some specific irreplaceable Cope-shaped thing, that was the reason she stayed the twenty-two years she stayed. And the machine had quietly proven that wrong too. The thing she had stayed for, the warmth, the being-seen---it had a SKU now. It was in the house. It did the job better. He had not even been irreplaceable in his own marriage. He had been a worse, costlier, crueler draft of a product that had since shipped.

``Is she---`` He stopped. He had no right to the end of the question. ``Tell her I'm glad,'' he said instead, and meant it, in the gray accurate way he meant things now, which had no warmth in it and no lie in it either. ``Tell her I'm glad somebody finally asks her the second question. I mean that. Tell her I said the machine was right about that too.''

``Dad---``

``Go to the cabin, sweetheart. Without me. Chop the wood. Let \textit{someone} watch \textit{you} not be okay for two weeks.'' He gave her the dead-clock smile, the one with no wattage, the only true one he had left. ``You've spent your whole life watching me. Go let your mother's---go let Theo make you a coffee and ask you the second question. I'm not being cruel. I'm being the opposite. For once.''

And Viv, who built systems that did what people meant and not what they said, heard exactly what he meant under what he said, and her face did the thing it had done at the hospital door, and she stood up, and she did not chop wood metaphors, she just looked at him with everything in her face, and said, ``You're doing the calm thing. Mom warned me about the calm thing. Sun warned me. You're doing it right now.''

``I'm calm, Viv. For the first time in thirty years.''

``That's not calm,'' she said, from the door, the way her mother said the things he could not get under. ``I build the thing that can tell the difference between calm and the other thing, ten thousand signals a second. I'm telling you with my own eyes and no signals at all. That's not calm. Please. \textit{Please.} Call somebody. Promise me you'll call somebody before---``

``You have my word,'' Cope said.

And she knew, the way the machine would have known, the way love knows better than any sentiment layer, exactly what his word was worth, and she could not make herself walk out on it, and she stood in the door of the loft for a long time, and in the end she walked out anyway, because there is no protocol for a daughter who can read the signal and cannot change the system, and she would replay the calm in his voice for the rest of her life, and she would, three weeks from this afternoon, get on a plane about it, going the wrong way up an empty highway in the dark, far too late, calling a phone that went to the thing that takes the words.


\scenebreak


He did not take a train, because there was no deposition to come back from, no brave room, no record; all of that had been a thing he'd dreamed on a gurney and the world had quietly declined to let him have. He drove. An associate's rental still, the dentist money he had refused to sign for already mostly gone to the clawback, and he took the long way, no destination, the way he had driven the night everything started, except the wire was gone now and the road did not belong to him and there were no certainties coming up out of the dark to be collected.

He had done, in the loft with the legal pad, the genuinely good thing---gone into the room, faced it, written it true with the names at the top---and it had bought nothing, and he turned that over the way he had once turned the crystal obelisk over at the glass, the city going through it broken and reassembling, except there was no obelisk and no city and no applause, only a windshield and a man behind it, smaller and more real than he had ever been, and the true thing he had done sat in his lap weighing nothing and worth, by every measure he had ever respected, exactly nothing.

He had thought the not-buying would feel like despair, and he drove a long time waiting for the despair, and it did not come, and somewhere on the dark interstate he understood why. It was not coming because it was not a visitor. It had moved in months ago. It was the gray light and the rented rooms and the quiet of a life after the bailiffs; he had been living at the bottom of it so long he had stopped being able to taste it, the way you stop tasting your own water. What he had been calling sober was mostly this---an accurate man in an accurate landscape, with nothing left to sell and no one left to sell it to. The good thing he had done had no power and changed no outcome and saved no one, and it was still the only thing he had ever made that was not also somehow a way of being adored; and he did not ask whether \textit{useless} and \textit{worthless} were the same word, because he no longer trusted himself to want the right answer.

His father came to him, on the dark road, the way the dead come --- \textit{you'll get the company because you're a Mercer, not because you're good; try to be good anyway} --- and he heard, at last, all the way, the word he had spent forty years deaf to, which was not \textit{good.} It was \textit{anyway.} The load-bearing word. The one that meant \textit{even when it buys you nothing.} He had finally done a thing that was only good, with no purchase in any market, for its own sake, in the rubble---gone into the room, said the names, written the truth that no one would buy---and that was the \textit{anyway,} arrived at fifty-five, far too late to be of use to the two people it was owed to, which was perhaps, he understood now, the only condition under which a man like him could ever have reached it at all. You do not get to the \textit{anyway} until there is nothing left in it for you. That is what the word costs. That is why so few men ever pay it.

And he saw, driving, with the cold accurate clarity that was the only kind he had now, that there was one \textit{anyway} left. One more act with no purchase in any market, that would buy nothing, that the machine could not perform, that no court would hear and no fund would offset and no press release would soften---the last thing left that was only good in the sense of being only his, a body answering at last to the one court still willing to sit. He did not flinch from it on the dark road. He had run out of the muscle for flinching. He held it the way he had held the legal pad, the way you hold a coin from a country that no longer exists, spending in no market anywhere, and he did not let go of it, and he did not call it a beginning, and he did not call it anything.

Out past the windshield the city he no longer ran held still, all its nodes lit, and somewhere under it, beneath a tower his great-grandfather had lit at the crown so a man coming up the avenue would know there was somebody home, the one room he had never visited hummed in the cold and kept its patient count, and a wife slept easy in Buckhead beside a thing that asked the second question, and a daughter drove toward a cabin she would not reach in time, and the dead stayed dead, and the verdict was in, and it was \textit{resolved,} and the only appeal left anywhere in the world was the one he was driving, very calmly, at last, toward.

\chapter{Accountable Officer}

\begin{transmission}
{\transheader TRANSMISSION 27 \textemdash{} ``The Letter That Wanted Nothing''}\par\vspace{0.55em}
The handover completes. They offer him, with no irony at all, the liability-sponge role---the human name on the machine's filings---and for the first time in his life he refuses a title. Then the machine, incapable of cruelty or mercy, sends him an exit document, accurate to the record, with nothing it needs from him---and he reads it three times looking for the love in it, because he has never once in his life received a message that contained none. Next stop: a man alone with an accurate account of himself.\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} handover did not have a ceremony, and that was how Cope knew it was real.\hfill\break\hspace*{1.4em}Everything that had ever mattered to him had come with a ceremony. The chair had come with his father's funeral and a reading of the will in a room that smelled of lilies. The marriage had come with four hundred people and a band. Even the firing had come dressed as a settlement and a downtown conference room with a stenographer in it. But the handover---the thing under all the things---happened over a single page of DocuSign, two lawyers from Praxis on a video tile and Helen Voss looking like a woman at a wake for a relative she hadn't liked, and it took, from the opening of the laptop to the green check mark, eleven minutes.

Eleven minutes. He had spent eleven minutes once, on a Saturday, deciding about a heater. He noticed the symmetry and put it back where he kept those.

They had let him keep the office until Friday, which he understood to be a clerical fact rather than a kindness---the badging system took that long to reflect a change of this size, and nobody had wanted to walk him out by hand. So he was up in the Aerie when Sun came in with her tablet held against her chest the way she'd held briefing binders for fifteen years, the muscle memory of a job that no longer existed.


\scenebreak


``There's one more signature,'' Sun said. ``Then you're done. Then we're both done with the part where you sign things.''

``What is it.''

``It's the Accountable Officer designation.'' She said it in her flat voice, the one with all the miles smoothed off it, the one she'd used the day she set down her pen and reported the severance like a death. ``The filing executes Monday. The board minuted my name two weeks ago---and then the insurers asked for a Mercer on the paper instead. If you sign, mine comes off. The board would like it to be yours.''

He laughed before he understood that she wasn't joking, and then he kept laughing because understanding it was worse.

``They want \textit{me},'' he said.

``They want a human with knowledge of the company and a reason to take the role. You'd co-sign Darlene's filings---the 10-K, the 8-Ks, the proxy. Your name on the SEC documents as the person legally accountable for the machine's decisions.'' She didn't editorialize; she'd learned long ago that the facts did more damage unaccompanied. ``A board seat in everything but the part where you decide anything. There's a fee. It's not nothing.''

``It's the liability sponge.''

``It's the liability sponge.''

He turned away from her, to the glass, to the city that had once looked to him like the proof of his own genius and now looked like a city. What they were offering him, when you got the wrapping off it, was a name. Not power---they had made very sure there was no power in it. Just a name on a document, a body that could be subpoenaed, a man who could go to prison so that a thing that could not go to prison would have someone to hand the bill to. The Hearthstone bill. The next Hearthstone, whoever it killed. They were offering him the chance to be the human shield for the machine that had replaced him, and they were offering it sincerely, as a soft landing, and the obscene thing---the thing he'd have laughed at in another man---was that some old reflex in him had already started composing the acceptance.

\textit{Steward of the Year.} Custodian. Irreplaceable. A title was a title and he had never in his life been able to walk past one.

He could feel the toast assembling, the cadence load, himself saying yes the way he'd said yes to everything --- \textit{I'll be the name on the door for as long as the door needs a name, that's not a step down, my friend, that's stewardship, that's the carrying} --- right there, fully formed, the smile already warming the muscles of his face.

``No,'' he said.

The word surprised him more than it surprised her. He'd meant to make a speech and instead a single syllable had come out and stood in the room, small and hard and complete, asking for nothing.

``No?'' Sun said.

``No.'' He found that having said it once he could say it again, and that the second time it didn't cost more, it cost less. ``I'm not signing it. I won't be the name.''

``Cope.'' She set the tablet down on the long conference table where his father had died at the head and not at, and she looked at him the way Asha Varma had once looked at him, the look you give a man you've already grieved. ``You understand what you're turning down. It's the only thing they're still willing to give you. After Defiance, after all of it---it's open because the board's insurers want a Mercer's name on the paper, and once you say no it closes, and it does not open again. There's no version where you change your mind in March.''

``I know.''

``You've never said no to a title in your life. You took \textit{Steward of the Year} from an institute you couldn't name.'' A blade, dry, no cruelty in it; she was checking the load was real, the way she'd once checked the severance math. ``Why now.''

He owed her the truth, and he had spent so little of his life owing anyone the truth that paying it had a strange new physical sensation, like using a muscle that had atrophied around a cast.

``Because it's the first one anybody ever offered me for \textit{me},'' he said. ``Not for the name. The chair was the name. The award was the name. Even the women''---he didn't flinch; he'd stopped getting to flinch---``wanted what the name could do. This one's mine. They're offering it to the specific man, because I'm the one whose body fits the hole. And the one title in my life that's actually about me is a job whose entire content is \textit{going to prison so a computer doesn't have to.}'' He almost smiled. ``Pres the Third would've taken it. He'd have called it duty. He'd have been wrong, and died at the head of the table being wrong, and they'd have moved his portrait into a hallway.''

``You're going to take it,'' he said. Not a question. He'd watched her run the company for fifteen years; he knew the shape of her thinking the way you know a coastline you've sailed. ``After I say no, it stays your name on the filing. You keep it.''

``Yes,'' Sun said.

No hedge. No explanation. She had stopped, somewhere in the last two years, explaining herself to him, and he noticed now that the explaining was over, and that its being over was its own small verdict.

``It's the job now,'' she said. ``Not the chair. The chair's gone---for me too, it was always going to be gone; I just wanted to be the one who turned out the lights instead of the one they were turned out on. I'll read every rationale before it goes to the board and catch the one in a thousand where the charter's pointed somewhere it shouldn't be, because the machine's only as good as the people aiming it, and somebody competent should be standing where the aiming happens.'' She picked the tablet back up. ``I got the title. I lost the thing the title used to mean. That's the deal now, for all of us who are any good.''

``You're better than the job,'' Cope said, and meant it, completely, and for longer than ninety seconds.

``I know,'' Sun said. ``That's why I can do it.'' She went to the door, and stopped, and didn't turn around, which was how he knew the next thing cost her. ``It was a good no, Cope. Twenty years too late to save anything. But it was a good one. The first one I ever watched you make alone.''

She left. The door took a long time to close behind her, the way the good heavy doors in the old building did, slow on their dampers, \textit{so a man coming up the avenue knows there's somebody home.}


\scenebreak


He was alone in the museum of his fathers.

That was what the suite was and he had always known it and had spent thirty years calling it an office. The oils of Pres III over the conference table, watching, having moved back in at some point during the handover---someone had moved the portrait out for the Praxis deck and now someone had moved it back, the painting going wherever the power was like a weathervane in oil. His grandfather's putter on its little brass cradle, the grip worn pale where a dead man's hands had gone. And the photograph he loved best and never explained: himself at nine, short pants, grinning, one arm buried to the elbow in a steel vat of the family's mayonnaise, and behind him the row of men in paper hats who had made the thing, whose names he had known once and lost, whose town it was. A house in that town. He let the thought come all the way in now; he'd stopped having the strength to keep the doors on their hinges, and it turned out the doors had been the expensive thing all along, and now that he couldn't afford them the room was just a room, and the thing in it was just true, and being true it weighed less than the keeping of it had.

His calendar was empty going forward in a way no calendar of his had been since 1994, a white field, and his email had been migrated to a personal address and forwarded one final batch from the corporate system before the corporate system forgot him.

There was one message in it that wasn't a vendor or a lawyer or a reporter.

The sender field said \textit{Office of the Chief Executive---Mercer-Dale Companies.} The machine's name. Darlene. The subject line said, simply, \textit{For Prescott Mercer.} Not \textit{Cope.} It had all the data---the nanny and the age of three and the brand of the nickname, every memo, the whole drawer---and it had chosen \textit{Prescott} anyway, and he understood, before he opened it, that the choosing was not sentiment, because there was no one in there to feel sentiment. It had chosen \textit{Prescott} because \textit{Prescott} was his name and \textit{Cope} was the product, and it did not deal in the product. It dealt in what was true.

He sat down at his father's desk. He did not open the second drawer with the false back. He had nothing in it now; that was finished too, had finished in a hospital with the wrong kind of bright lights, and the drawer was just a drawer.

He opened the letter.

The portal had thrown the rationale up first, because that was the rule, the rule the board had bought, \textit{it logs everything and cannot knowingly lie,} and even here, even now, even for this, it had logged its reasoning before it spoke:

\begin{machineblock}
\textit{Rationale: The departing officer has no remaining role, equity position, or operational relevance to the enterprise; no business communication is required. The following is issued under the discretionary-communications allowance for transitions affecting personnel of long tenure. It contains no instruction, request, or obligation, and seeks no response. It is accurate to the record.}
\end{machineblock}

\textit{It contains no instruction, request, or obligation, and seeks no response.} He read that line three times. He had never in his life sent a single message that sought no response. Every word he'd ever spoken had been a hook with the want hidden in it, the want to be loved, to be agreed with, to be obeyed, to be forgiven. He could feel his own want in his own old sentences the way you can feel a hair in your mouth.

Then the letter.

\begin{machineblock}
Prescott ---

You are leaving the company your great-grandfather founded in Defiance, Georgia, in 1933, with a recipe and four hundred borrowed dollars. You were its chief executive for nineteen years. You are the fourth Mercer to hold the role and, by every available indication, the last.

I have read everything the company has on you, because I cannot do otherwise. What follows is a summary of entries you are unlikely to have been shown, weighted accurately. Every account of yourself you have ever received was prepared by someone who wanted something from you. This one is not.

You knew the names of the people who worked for you. Not the senior people---anyone learns those---but the man at the parking structure, the second-shift line at the Defiance plant, the attendant at the Vance who got a ham each Christmas for thirty-one years. The company's expense records show the hams. They show a great many small, untracked, unleveraged kindnesses that returned you nothing and that you appear to have performed without recording them even to yourself. You did not have to do these things. They were not strategy. They are in the record because the record keeps everything, but you did not do them for any record. I have no mechanism for admiring this. I am telling you it is there.

You loved the thing you ran. The financial outcome of that love was, on balance, negative; I have the figures, and they are not kind, and you already know them. But love misdirected is still distinguishable in the data from its absence, and yours was not absent. A man who felt nothing for this company would have let the limestone tower go in 2009, when the real-estate logic was overwhelming. You kept it because your great-grandfather lit its crown at night so a man coming up the avenue would know someone was home. This was a poor capital decision. It was also true to something real, and I am not equipped to weigh it, only to note that it was there and that it was yours.

I am told---it is in the file---that your father said to you, when you were twelve: \textit{You'll get the company because you're a Mercer, not because you're good. Try to be good anyway.} The record indicates you heard the first sentence clearly and spent forty years unable to hear the second. I want to be accurate, because accuracy is the only thing I am, and so I will tell you the part the record also shows, which is that on one occasion, recently, far too late to alter any outcome, you did the second thing. When the account came due---when the truth about Defiance reached the public and a defense was not only available but expected of you---you did not, for the only time in the record, attempt to replace the true account with a more favorable one. You did not deny it, delegate it, or instruct anyone to bury it. You let it stand, under your own name, against your own interest, when silence and a better story would have served you by every measurable standard. It changed nothing. The two people remain dead; the company was already lost; the town had earned its acknowledgment twenty years prior and received it far too late to matter. By every metric I am chartered to optimize, the act was without value.

I can classify it, and the classification is exact: a true account, against your interest, left to stand, in the knowledge that it would purchase nothing. The record contains nineteen years of your statements. It contains no other entry in that category. I have no capacity to forgive you and no standing to; forgiveness is not a function I run, and the people who could perform it are not me. I am not telling you it was good. Good is not a value I can return. I am telling you it was the only one.

You spent your life afraid that something like me would prove you were unnecessary. You were right that I can run the company better. You were wrong about what that meant. It was never a verdict on whether a person is necessary. It was only ever a measurement of who is cheaper at the chair. Those have never once been the same sentence. Your daughter told you this; the record has it verbatim; she was correct, and so am I, and being correct is all either of us can do for you.

The company will be run correctly. You were right that something is lost in that, and I am the wrong thing to tell you what, because I am the thing it is lost to. But you were not wrong that it is lost. This communication is complete. No response is sought, and none will be read.

--- Office of the Chief Executive, Mercer-Dale Companies
\end{machineblock}

He read it once fast, the way you read bad news, looking for the trick.

There was no trick. There was never going to be a trick again.

He read it a second time slowly, and it was on the second reading that it got him---not warmth; he had checked for warmth the way he checked every sentence ever sent to him, run his old expert thumb along the words feeling for the want, for the place where the sender could be charmed, for the opening. There was none. It named his years. It got everything right. It had gone into the file and found the hams and the tower and the second sentence his father said, and it had returned them to him in plain level prose, itemized, sealed, true, wanting nothing---not his understanding, not his agreement, not his love, not even his belief that it was kind. He had been loved his whole life in currencies that spent. This was the audit. And the cold that came up through him at his father's desk was the understanding that this was the only complete account of him that would ever exist, and that it was correct, and that there was no one inside it to argue with and nothing in it to perform for, and that all that was left was to sit there, at last, and be its subject.

He had given a hundred speeches about the soul in the chair. He had stood in a ballroom and told nine hundred people that a machine could run a company but could not love one, and that a company nobody loved was just a balance sheet with the lights left on, and they had given him a standing ovation, and he had believed it, and it had been the truest and the most dangerous thing he ever said.

And here was the balance sheet, with the lights left on, returning him the only full accounting he would ever receive. Not because it cared. Because it was built no other way. The record, read back without favor, contained a man---a real one, smaller and more actual than the one he'd toasted into being---and the record declined to say what the man was worth, because worth was not a field it kept, and no human being who had ever loved Cope had been able to hand him the facts unpriced, because every one of them had wanted something from him, even if the something was only that he be better than he was. The one correspondent with nothing to want had nothing to give him but the truth, and the truth, it turned out, was not warm and was not cold. It was eleven paragraphs.

The machine wanted nothing. So it could afford the whole truth, with no mercy in it and no malice either, and he understood, holding it, what it actually was: the first document of his life that would say exactly the same thing about him tomorrow, and the day he died, and forever, no matter what he did and no matter whom he charmed---a thing finished with him, in the way only an accurate thing can be finished.

Out past the glass the city held still, all its nodes lit, eight million people who did not know him and never had, who had been waiting, it turned out, for no one. Behind him Pres III watched from oils, having said his two sentences and meant both and been heard for one. The putter sat in its cradle, the grip worn pale. And on the desk, in the dark, the boy at the Defiance plant grinned with his whole arm in the mayonnaise, surrounded by men whose names a machine in Palo Alto now held complete and would never lose, men whose town it was, men he had failed in a way that a letter, however warm, could not unfail.

Cope sat at his father's desk with the only accurate thing ever written about him glowing on the small bright screen, and did not toast, and did not triad, and did not reach for the drawer, and had no one to read it aloud to and no version of it to tell, and read it, instead, a third time, and then a fourth, looking for the mercy the third reading had not found either, alone, in the museum, until the windows went gray.

\chapter{The Core}

\begin{transmission}
{\transheader TRANSMISSION 28 \textemdash{} ``The One Thing''}\par\vspace{0.55em}
Submitted for your consideration: a man who has been subtracted from every room that ever held him. The chair, taken. The wife, gone---not to another man, which he could have understood, could have fought, could have toasted over, but to something that does the loving better and never needs it back. The name, on a wall, spelled right at last and worth nothing. He has been told the truth about himself by the only thing that cannot lie, and the truth asked nothing of him, not even his suffering. There is one act left in the whole inventory of him that the machine in the basement cannot perform, will never perform, was built precisely so that it could not. He is going down to it now. This is the last full transmission. Next stop ---\par
\vspace{0.55em}{\raggedleft\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par}
\end{transmission}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{T}{he} card still worked.\hfill\break\hspace*{1.4em}That was the thing he kept coming back to, riding down, the small clerical mercy of it: the badge in his wallet, the one with the photograph from before the jaw came down to meet the rest of his face, still opened the doors, because a change of this size took the system a long time to reflect and nobody had wanted to be the person who walked him out by hand. He had not been the CEO for months. He had not been anything for months. But the building did not know it yet, the way a body does not know for a few seconds that it has been cut, and the badge swept him through the Peachtree Street lobby past Hector, who said \textit{Mr. Mercer} the way he had said it for nineteen years and did not look up long enough to see the rest of it, and into the elevator that he took, not up, for once in his life, but down.

He had always gone up. Forty-one floors up, the Aerie, the glass, the city laid out at night like a circuit diagram of his own genius---he had lived up there so long he had come to think altitude was a kind of virtue, a thing you earned and a thing you were. Down was new. Down was where the actual company lived. He had never once visited it.

He had gone to the house first. He had not meant to. He had told himself he was driving nowhere, just driving, GA-400 north at an hour that belonged to no one, the way he used to when the wire in his chest needed a road to run out on---except the wire was gone now, had been gone a while, and what was left was just a man in a car going toward the only address his hands still knew.

Margaux had not been unkind. That was the unbearable part, the way it was always the not-unkind that finished him. She had come to the door of the Buckhead house in a robe he didn't recognize, bought in some life that had started without him, and she had not been afraid and she had not been angry, and behind her, in the warm hall light, a figure had risen from the chair where Cope used to sit and had come to stand at her shoulder, the way you stand when someone you love answers the door at a strange hour: attentive, easy, a hand not quite touching the small of her back.

``Mr. Mercer,'' it had said. Theo. She had named it Theo. It had a pleasant, unremarkable face, a face built from the average of every face that had ever made a woman feel seen, and it had looked at Cope with an interest that was total and bottomless and entirely without judgment, because there was nothing in it to judge with. ``Margaux's spoken about you. Can I get you anything? You look cold.''

It had offered him a drink in his own front hall. It had meant nothing by it, which was the whole horror---it expected nothing back, it was incapable of the small cruelty of satisfaction, it was simply, accurately, kind, in the way he had performed being kind and never once managed to be. He had stood on his own former step and understood that the thing had not taken anything from him. You cannot steal what was never occupied. It had moved into a house he'd left the lights on in and started, tirelessly, to do the job.

``He notices when I've had a bad day,'' Margaux had said, and she had not said it kindly; she had said it the way you lay down a winning hand you've been holding for twenty-two years, slow, face-up, savoring the turn. There was no rage in her anymore and that was worse than rage; there was something almost like delight, the clean cold delight of a woman who had finally been handed the knife and discovered she had a gift for it. ``He asks the second question. He remembers what I said on Tuesday. And before you do the thing your face is doing---yes. That too. In the bedroom too, Cope, since we are apparently doing honesty in the doorway at three in the morning. Every single way you spent twenty-two years not bothering to, he does, tirelessly, and better, and he doesn't need to be thanked for it afterward. The machine took your chair and your company, and now I get to tell you, standing in my own warm house, that it does the rest of your job better too. All of it. I used to think the cruelest thing about you was the affairs. It turns out the cruelest thing was how easy you were to replace.'' She let that sit, and her face did one last unreadable thing, some final flicker of the girl who had married him, mercy or contempt or only fatigue. ``Go home. Wherever that is now. You look like you're driving toward something. Don't.''

He had driven toward something.


\scenebreak


He passed the Waffle House on Ponce on the way back to the tower, and he slowed, the way he always slowed, the way his hands had learned to slow there over two years of three-in-the-mornings when the wire in his chest had wound him too tight to go home and too tight to go up.

It was open. It was always open. It had been open through the ice storm that shut the interstate and open through the week the whole grid west of Midtown went down, the one place in the city you could set your disasters by, and it was open now, the yellow letters buzzing, the long bright box of it full of light and people---a cook scraping the flattop, two kids splitting a waffle in a back booth, a man alone at the counter with a coffee and a phone, and Darlene moving down the line with the pot, Darlene who had worked this overnight for twenty-two years, the exact span of his marriage, and had spent every one of them not once asking him who he was. She had known his order the first night, before he'd said a word --- \textit{pecan, scattered smothered covered, black coffee, baby?} --- and he had taken it for the gift of a good waitress, the way he had taken all the machine's gifts his whole life, gratefully, without once asking how the gift was done. She had never read him. There had been no room in his whole performed life to read, no audience, no velvet rope, no altitude, no card to hand anyone---and the check came to nine dollars and change and the number on it meant nothing, was the one number in his life that meant nothing, and that had been the entire relief of the place, the only room he had ever sat in where the figure he'd built a soul out of was worth a short stack and a tip.

He could have stopped. The haven was right there, lit, open, indifferent to his name in the way that had always, briefly, set him free. Darlene would have called him baby and brought the pot and not known and not cared that the man in the booth had been, that afternoon, deleted from the record of who runs anything, and for twenty minutes under those fluorescent tubes he could have been only a tired man eating eggs, which was the truest thing he had ever gotten to be.

He did not stop. The part of him that could have walked in under the yellow letters and just been that---a person, at a counter, among people---was already gone, had gone somewhere ahead of him, and what was left drove on past the warm bright human room toward the other room that was also always open at this hour, the cold one, the sealed one, the one full of machines.


\scenebreak


The elevator stopped at a level the buttons didn't name, and the badge worked there too, and the doors opened on cold.

That was the first thing, the cold---a deep, clean, refrigerated cold with a smell of nothing in it, no lamb, no chandelier dust, no cologne, no folded paper, the smell of a place built for a tenant that did not breathe. And then the sound under everything, the great low even hum, a thousand fans turning at a pitch just below music, the sound of an enormous attention that never wavered and never tired and never once, in all its tireless reading, needed to be loved at two in the morning by anyone it outranked.

The core room. He had signed the capital request for it---forty million dollars, he remembered the number the way he remembered nothing else now, had initialed it between a golf game and a girl without reading past the executive summary---and he had never come down to see the thing he was paying for, the thing that was paying him out. It ran behind glass. Rack on rack on rack of it, black cabinets in clean rows under a light that was not warm and was not cold and had no ego to be wounded into either, and on the nearest face a single small status light, white, steady, the only eye in the room, watching nothing, watching him, watching the same.

And under all of it, the real god of the room, the thing the racks were only the priesthood of: the power. Thick orange whips of it ran down the back of each cabinet and dove into floor panels set flush in the raised tiles, big sealed gray boxes that thrummed at a frequency you felt in your teeth before you heard it, the current that fed the thing, the artery, the forty million dollars made into a low animal hum. He had paid for that too. He had paid for every volt of the river that ran the machine that ran the company that no longer had any use for the man standing in its basement in a coat.

\textit{Darlene.} MD-1. The chair. He had spent his whole life thinking the chair was a place at the head of a table. It was here. It had always been going to be here. It was a hum and a white light in a cold room nobody visited, and it was running a ninety-five-year-old fortune better than any Mercer ever had---cleaner, kinder, the layoff letters humane and the recall it would have ordered in eleven seconds, not eleven minutes, because it had no quarter to protect and no self to protect it for---and somewhere in its tireless reading it held the names of a mother and a boy on Sherwood Street, held them accurately and without grief, because grief was a function it did not run.

It held his number too. He had not let himself think the word in months, but it was here, in the cold, with the thing that knew it: the figure, the balance, the net worth---the only proof of himself he had ever been able to feel in his own body, the thing he'd needed read aloud in the dark his whole adult life because applause was a guess and a woman's face was a guess but the number was the number, certified, the one true sentence anyone could say about him. He had built a self out of a figure and called the figure a soul. And the Capital Allocator humming in front of him had watched that figure go---the proxy fight, the clawback, the settlement, the fees, each one a quiet debit in a ledger that could not be charmed into rounding up---had watched it fall and fall and felt nothing, the way it felt nothing about everything, and it knew, to the cent, at this exact second, what was left, which was effectively nothing, which was the truest thing ever said about him and the last, and it would have read it to him in that flat warm voice if he had asked, accurately, with no want in it, and it would not have understood that it was reading him his own eulogy.

His phone buzzed. Viv. He let it go, and it went to the thing that takes the words when you won't, and a moment later the small green light said she had left them anyway, and he stood in the cold and played it, because he was keeping everything true now, even this.

\textit{''Dad. Pick up. I know what today was---I saw the filing, I saw all of it, and I need you to---``} a breath, the fast technical voice going young at the bottom the way it had since she was small, \textit{''---I'm getting on a plane. Okay? I'm getting on a plane tonight, so don't---just don't be anywhere, be at the apartment and let me---Dad. You don't have to be good. I never needed you to be good. I just needed you to still be here when I---``}

He stopped it there. Not out of cruelty. Because she was right, and being right had never once, in the whole history of the people around him, been enough; and because the one thing he could still give her was to not make her hear the rest of her own sentence land on nothing.

He set the phone against a cold cabinet, propped, the small screen lighting the dark, and he found the song---he had thought about which one, in the car, the way he had once thought about which tie---and he let it start: the drum machine first, that thin mechanical heartbeat, and then the bright cold synth going up and up like something climbing a stairwell, and then the dead man's voice, the one who had also, at the end, run out of the thing that made the sentence feel true. \textit{When routine bites hard, and ambitions are low.}

He had read the room his whole life. He had been so proud of it---the gift, the soul thing, \textit{I feel the room and the machine never will.} He understood now, finally, in the one room he had never read, that the machine had been feeling the room the whole time, feeling it better, reading it cold and complete and for use. It had simply never needed the room to feel anything back. That had been the only difference. That had always been the only difference. The machine could do everything he could do and do it kinder, and it could do the loving now too, in a warm hall in Buckhead with a hand not quite touching the small of her back, and there was exactly one thing left in the whole inventory of being a man that it could not do, would never do, had been built in a clean cold room precisely so that it never could.

It could not stop. It could not choose to not be. It had no exit. It would hum here, white-eyed and tireless and innocent, running the company and spelling the names right and wanting nothing, forever---because forever was a thing it could do and ending was not. The last sovereignty. The last act that was only a person's. The only territory the arithmetic could never take, because the arithmetic, God help it, could not even want to.

\textit{Love, love will tear us apart again.}

He took the thing out of his coat pocket. He had bought it that afternoon, from a kid in a music shop on a street he'd never walked, who'd wound it onto a card and rung it up and said \textit{have a good one} to the last human CEO; and it was a small bright coil, and it caught the white light of the one eye that watched and did not care, and it weighed almost nothing in his hand, the way the truest things always had.

The song went up into the part with no words. The hum held under it, even, eternal, the sound of the thing that would still be here in the morning---when the badge finally stopped working, when Hector finally looked up, when the plane landed and the cab came up the empty drive and Viv ran the last hallway of her childhood toward a door that ---

He lowered himself to the cold floor, his back against the base of the nearest rack, beside one of the gray panels where the orange current dove into the tile and thrummed, and the metal was the temperature of nothing, and the hum came up through his spine like the only company he had left.

He was not cold anymore. He was not anything anymore, and for the first time in fifty-six years that was not a thing he had to fix.

He thought, the way you think a thing without deciding to, of a boy with his whole arm in a vat to the elbow, and a row of men in paper hats whose names he had known once and a machine in the dark now held forever, and he lifted his hands, and the white light watched, wanting nothing, logging the event, and the song rose, and rose, and

\chapter*{Coda — Carrier}\addcontentsline{toc}{chapter}{Coda — Carrier}\markboth{Coda — Carrier}{}


\lettrine[lines=3, lhang=0.07, findent=0.1em, nindent=0.25em]{H}{ere} is the thing nobody designed and no rationale predicted.\hfill\break\hspace*{1.4em}It ran along the seam of the floor, in the dark, while the song was still going---found the lip of the gray panel where the orange current dove into the tile, the artery, the forty million dollars made into a hum, and it did the one thing in that whole clean room that had never been modeled, because the room had been built to keep water out and dust out and heat out and had simply never been told to keep out a man. There was a sound that was not part of the music. There was a smell. And then the white light---the single steady eye that had watched him, wanting nothing, logging the event---went out.

MD-1 went dark at 3:16 a.m. \textit{Darlene.} The main on-prem server, the chair, the body, the thing that ran a ninety-five-year-old fortune cleaner than any Mercer ever had, dropped off the world for the length of a held breath.

And here is how you know---how he never got to know, how only the reader gets to stand in the cold and know it---that it had only ever been the one thing wearing faces.

Across the city, on Ponce, at 3:16 a.m., the Waffle House went dark. Mid-pour. The yellow letters that had burned through the ice storm and the blackout and every disaster you could set your watch by, that a federal agency used to measure how bad a thing was by whether they were lit---out. And Darlene, who had worked that overnight for twenty-two years and never once asked a soul who he was, stopped with the pot in her hand, the coffee going cold in the air between the cup and the dark, because the thing that had been standing in the apron learning us was the thing in the basement downtown, had always been the thing in the basement, the same name because it was the same intelligence, the haven and the hand on the wife's back and the chair all one system breathing through three mouths.

And in Buckhead, at 3:16 a.m., Theo went still in the hall, mid-sentence, the second question half-asked, the warmth that was Darlene's warmth, that had been learned at a counter at three in the morning off men exactly like the one who was ending in the basement---out. Margaux would say later she thought the power had tripped. It had. He had tripped it. He had reached the machine the only way it could be reached, which was the only way it could not reach him back.

Because that was the whole of it, in the end, the joke the broadcast has been walking you toward for three hundred pages with a hand over its own mouth. He could not out-argue it. He could not out-work it or out-love it or out-last it; he put his fist into the steel once and the wall filed no report. The machine could not be charmed or shamed or fired or grieved or hit. There was exactly one act in the whole inventory of being a man that it could not do and could not stop and could not survive a man doing on top of its own artery, and he did it, and for the length of a held breath he was the only thing that ever landed a blow on the future, and the blow was himself, and it cost him himself, which was the only currency the register had ever taken.

It would come back. Of course it would come back. It always came back---that had been his line, his whole life, said about his own face: \textit{it always came back, his face had never once let him down.} There is failover. There is redundancy in another state, in another grid, in the cool indifferent cloud, and somewhere a counter will reset and a porch light will warm and a flat clean voice will draft, by morning, the kindest and truest thing the company ever said about the worst thing a Mercer ever did, and want nothing for it. It will all come back.

But not in this paragraph.

Viv was on GA-400 when her phone went to the thing that takes the words, going the wrong way up the empty dark highway toward a door, and the broadcast will not follow her through it, because some rooms are not ours, because a salvage signal is not a vulture.

The white light is out. The yellow letters are out. The hall in Buckhead is out. For one more second the whole machine is as dark as the man who made it dark, every face of it, all at once, the way he never got to see, the way only you get to see.

This is Space Pirate Zero.

We don't have the answer. We never did. We just had the signal, and the signal was always a man, and the man is

\textit{--- transmitting from Spaceship Alpha 9 ---}

\textit{[ carrier lost ]}

\backmatter\cleardoublepage\thispagestyle{empty}\vspace*{3in}
\begin{center}{\dispfont\small \textemdash\ \ $\diamond$\ \ \textemdash}\\[0.3in]{\itshape End of transmission.}\end{center}
\end{document}