\documentclass[11pt,openany]{book}
\usepackage[paperwidth=5.5in,paperheight=8.5in,inner=0.85in,outer=0.65in,top=0.8in,bottom=0.85in,headheight=14pt]{geometry}
\usepackage{microtype}
\usepackage{setspace}
\setstretch{1.13}
\setlength{\parindent}{1.4em}
\usepackage{lettrine}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{pdftitle={The Last Human CEO},pdfauthor={Space Pirate Zero},hidelinks}

% transmission opener style
\newcommand{\transheader}{\normalfont\footnotesize\scshape\letterspace}
\newcommand{\letterspace}{}
\newenvironment{transmission}{%
  \par\vspace{0.3\baselineskip}\begin{center}\begin{minipage}{0.88\textwidth}%
  \itshape\small\setlength{\parindent}{0pt}\setstretch{1.06}}%
  {\end{minipage}\end{center}\vspace{0.4\baselineskip}%
  \noindent\hfil\rule{0.35\textwidth}{0.3pt}\hfil\par\vspace{1.0\baselineskip}}

% scene break
\newcommand{\scenebreak}{\par\vspace{0.5\baselineskip}\begin{center}\textasteriskcentered\quad\textasteriskcentered\quad\textasteriskcentered\end{center}\vspace{0.5\baselineskip}\par}

% chapter style
\titleformat{\chapter}[display]
  {\normalfont\centering}
  {\vspace*{1.1in}\footnotesize\textsc{chapter \thechapter}}
  {6pt}{\Large\itshape}[\vspace{8pt}{\small--- $\diamond$ ---}\vspace{0.4in}]
\titlespacing*{\chapter}{0pt}{0pt}{0pt}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}

\pagestyle{fancy}\fancyhf{}
\fancyhead[LE]{\small\textsc{the last human ceo}}
\fancyhead[RO]{\small\textit{\leftmark}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\fancypagestyle{plain}{\fancyhf{}\fancyfoot[C]{\thepage}\renewcommand{\headrulewidth}{0pt}}

\begin{document}
\frontmatter

% half title
\thispagestyle{empty}\vspace*{3in}
\begin{center}{\large\textsc{The Last Human CEO}}\end{center}\clearpage
\thispagestyle{empty}\mbox{}\clearpage

% title page
\thispagestyle{empty}\begin{center}\vspace*{1.8in}
{\small\textsc{the}}\\[0.12in]
{\Huge\textsc{Last Human CEO}}\\[0.45in]
{\small------\quad$\diamond$\quad------}\\[0.4in]
{\large\textit{A Novel}}\\[1.0in]
{\Large\textsc{Space Pirate Zero}}\\[0.3in]
{\footnotesize\textit{transmitting from Spaceship Alpha 9}}\\[1.2in]
\end{center}\clearpage

% colophon
\thispagestyle{empty}\vspace*{\fill}\begin{center}
{\small This is a work of fiction.}\\[4pt]
{\small Grounded in the \textit{Last Human CEO} essay series.}\\[10pt]
{\small A tragic dark comedy.}
\end{center}\vspace*{\fill}\clearpage

\thispagestyle{empty}
\vspace*{1.6in}
\begin{center}\begin{minipage}{3.4in}
\itshape\small\setlength{\parindent}{0pt}\setstretch{1.15}
\par\vspace{0.8em}\hfill \textrm{\footnotesize --- Space Pirate Zero, transmitting from Spaceship Alpha 9.}
\end{minipage}\end{center}
\clearpage

\mainmatter

\clearpage
\chapter{The Premium Blend}

\begin{transmission}
{\transheader TRANSMISSION 01 --- ``The Obituary in the Trophy''}\par\vspace{0.5em}
Picture, if you will, a man receiving an award for being the last of something and mistaking it for a coronation. He tied his own bow tie. He remembers your children's names. He has, in the men's room, a small folded paper and a large folded opinion of himself, and tonight they agree on everything. Thirty-one of the hundred have already handed the chair to the machine; he toasts the eleven who haven't and does not hear the room counting down. Next stop: the difference between applause and a countdown.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{hey} gave him a crystal obelisk for being the last of something, and Cope held it up to the light and told the room it felt like a beginning.

The room loved that. The room was nine hundred people in the Conrad Vance Ballroom of a hotel that had, eleven months earlier, replaced its own chief executive with a Praxis unit and seen its stock go up eighteen percent on the news, and the ballroom was named for a banker whose firm no longer employed a single human officer above the rank of greeter, and not one of the nine hundred found any of this strange, because Cope was up there in a real bow tie he had tied himself, saying the word \textit{beginning} the way his great-grandfather used to say grace, and the chandeliers were doing what chandeliers are paid to do, and the lamb had been good.

``My great-grandfather Aldous used to say a man's worth is three things,'' Cope said. ``What he builds. What he keeps. And what he's willing to lose to keep it.'' He let the obelisk catch the light again. He had not, in fact, slept since Tuesday in any way a doctor would sign off on, and it was Thursday, and the not-sleeping had given the whole evening a clean overexposed quality, like the world had been color-corrected one stop too bright, and he liked it. He felt marvelous. He felt like the inside of a struck bell. ``Aldous started this company in a town called Defiance with a recipe for mayonnaise and four hundred borrowed dollars, and tonight a very kind committee has decided to give me a paperweight for being the only one of us left who has to \textit{sleep.}''

Laughter. The good kind, that comes up warm from the floor.

He did not say: who has to sleep, and lately can't. He had learned forty years ago which sentences to leave in the kitchen.

The award was real. \textit{The American Enterprise Institute for Leadership} --- Cope had never been able to keep the institutes straight, there were so many now, each one a little louder than the last about the disappearance of the very thing it gave dinners to honor --- had named him their Steward of the Year, and the citation, which a woman with a lanyard had read aloud before they handed him up the steps, called him ``the last human chief executive in the consumer Fortune 100, a custodian of the irreplaceable.'' Custodian. Irreplaceable. He had heard the words as a crown. It was only now, holding the cold glass thing, eight hundred miles into a night with no bottom to it, that some back room of him filed a quieter report, which was that you do not give a man a trophy for a job he is still doing. You give him a trophy on the way out. The citation was an obituary, beautifully set, and the lamb was the wake.

He did not let the report reach his face. His face was doing wonderful work. His face had never let him down.

``People ask me,'' Cope said, ``they ask me, Cope, aren't you afraid? The machines run thirty-one of the hundred now. They run them --- and I'll be honest with you, my friends, they run some of them \textit{well.}'' A murmur; he rode it. ``They don't take a salary you could feed Toledo on. They don't have affairs. They don't, God knows, have a backswing like mine.'' The backswing got him the room again. ``And every quarter another good board does the arithmetic and decides the chair doesn't need a heartbeat in it. So they ask me --- aren't you afraid?''

He set the obelisk down on the lectern. He took, here, the pause he had taken in a thousand rooms, the one Sun called \textit{the Mercer Inhale}, and out past the lights he could see the round tables going on forever, and at the nearest one his own table, Mercer-Dale's table, eighty thousand dollars of table, and the seat to the right of his empty chair was empty. Margaux had said she had a thing. She had not said what kind of thing a person could have, on a Thursday, that was worth more than watching her husband be the last of his species. The empty chair had a little reserved card on it with her name in calligraphy and nothing behind the card.

``I'm not afraid,'' Cope said, and meant it, and that was either the truest or the most dangerous thing he said all night. ``Because a machine can run a company. I've seen it. It can run it on rails, run it on time, run it cheaper than a man. But it cannot \textit{love} one. And a company nobody loves is just a balance sheet with the lights left on. I have loved this one since I was nine years old and my grandfather walked me through the Defiance plant and let me put my whole arm up to the elbow in a vat of our mayonnaise.'' He spread his hands. ``Some things you cannot put a machine in charge of. Grief. Mercy. A christening. \textit{Mayonnaise.} And so help me, leadership.''

Standing ovation. Of course a standing ovation. He stood in it the way you stand in surf, leaning a little into the push of it, and he thought, with the bright frictionless clarity that he told himself was the very tiredness and was not the very tiredness: \textit{they get it. They feel it too. We are not finished. We are barely begun.} And down at the table Sun Rao was clapping with her hands but not her eyes, and the empty chair stayed empty, and somewhere in the kitchen of him the quiet report sat unread on a desk.

He gave them four more minutes at the table --- a hand on a senator's shoulder, the senator's wife told she hadn't aged a day, a photograph he leaned into like weather --- and then he excused himself the way he always excused himself, with a joke about his prostate and his age, both of which were lies, and he went to find the men's room off the coat check where the attendant knew him.

It was a beautiful men's room. Marble the color of good butter, an attendant named Desmond who had worked the Vance for thirty years and got a Mercer-Dale ham every Christmas because Cope remembered things like that, remembered them the way the machine remembered things, which was to say completely and for use. Cope tipped him a hundred and asked after his grandson and went into the far stall and stood for a moment with his back against the door, and the noise of the ballroom went to a hum, and he took out the little folded paper he kept folded the particular way his guy in the '90s had taught him to fold it, \textit{so it can't open in the pocket, Cope, a gentleman doesn't spill,} and he did what he had been thinking about doing since the second course, which was the real reason he had stopped eating the second course.

After, the world came back up to pitch like an orchestra finding the note. The bell-struck feeling, clean and high and total, the one he had been calling, all night, \textit{the applause.} He looked at himself in the good mirror. Fifty-four and the camera still loved him and the jaw was still the jaw. \textit{You'll get the company because you're a Mercer,} his father said, from oils, from everywhere. Cope smiled at the mirror until the smile was right and said, very quietly, to no one, ``Watch me,'' and could not have told you, if you'd asked, what he meant to do or to whom.

On the way out the coat-check girl was new and young and had been crying about something before her shift in the way you could still see at the edges, and Cope, who could not pass a sadness without trying to fix it onto himself, leaned on the marble counter and got her laughing inside ninety seconds --- the toast in miniature, the full wattage, \textit{what's a face like that doing handing out other people's coats} --- and got her name, Bryce, and gave her a card, the personal one, \textit{if you ever want to do something more interesting than this, you call me, I mean it,} and meant it, the way he meant everything, completely and for ninety seconds. He did not register doing it. It was not a decision. It was the groove the record had been cut in. He was three feet down the corridor feeling generous and enormous before Sun appeared at his elbow out of the architecture the way she did, and took the second card out of his hand before he could give that one to anyone too, and said, ``The car's up,'' in a voice with thirty thousand miles on it.


\scenebreak


In the car he was electric and Sun was tired, which was the usual division of labor.

``You moved a hand,'' Cope said. ``On \textit{cheaper than a man.} I saw it. That was you wanting to cut it.''

``It was me wanting to cut it,'' Sun agreed. She had her glasses up in her hair and the city slid orange across the lenses as they went down Sixth. Forty-one floors of it ahead of them, the old limestone tower lit at the crown the way Aldous had insisted on in 1961, \textit{so a man coming up the avenue knows there's somebody home.} ``Frade's going to use that clip. 'Cheaper than a man.' You handed him a chyron.''

``Let him have it. People are sick of cheaper. People are starving for \textit{better.}'' He had his phone out and was thumbing at it too fast, the screen too bright in the dark car, and he was already somewhere past this conversation, three turns ahead, the way he got. ``What if that's the whole thing, Sun. What if the entire play is just --- say it out loud. Stop hiding from the word. \textit{Human.} Lead with it. A premium product for a premium ---''

``You haven't slept.''

``I slept.''

``You told me on Tuesday you'd cracked the back nine of consciousness. That's not a thing people who sleep say.''

He laughed, delighted to have been quoted to himself. He did this --- he loved his own lines best when they came back in someone else's mouth, it proved they had legs. ``The back nine of consciousness. That's good. Put that somewhere.'' He went back to the phone. Outside, a bus shelter slid by with an ad on it, a Praxis ad, just the wordmark and four words in that soft sans-serif they all used now, the typeface of the people who were going to be reasonable at you until you were gone: \textit{Leadership as a service.} And under it, smaller, the joke that wasn't a joke: \textit{No off-sites.} ``They're advertising on bus shelters now,'' Cope said. ``To whom. Who's the buyer at a bus shelter. The driver?''

``Boards read bus shelters. Boards' wives do.'' Sun pulled her glasses down. ``Cope. Monday. We have to talk about Monday before Monday.''

``Monday's a good day. I love a Monday.''

``Tidewater's at four and a half percent. They'll cross five this week and then they have to file, and when they file it's not a rumor anymore, it's a 13D, and the 13D is going to have a name in it, and the name is going to be a machine, and you are going to want to have already decided who you are when that happens instead of deciding it live on Halloran's show.'' She said it in three parts because she had trained him, years ago, to receive things in threes; it was the only shape that reliably got past the charm and into the man. ``Decide it this weekend. Please. Not Monday.''

He had heard about a third of it. The good third, the part with the fight in it. ``Renata used to say I do my best thinking on Saturdays,'' he said, not because it mattered, just because the name had floated up out of the bright tired water of him, the way names did when he was like this, and he watched it land in the car and saw Sun go very still in the front seat in a way he was too lit to read.

``You shouldn't say that name in a car, Cope,'' she said finally, evenly. ``You shouldn't say it anywhere. We've talked about this.''

``Said what name?'' He was already gone again, back in the phone, back in the manifesto that did not exist yet but was beginning to assemble itself in him the way weather assembles, a pressure, a charge. \textit{The Human Premium.} He could see it on a stage. He could see it on a cover. ``Drop me at the office,'' he said. ``I'm not going to Greenwich tonight, the house is --- Margaux's got a thing.'' He said \textit{thing} with no weight at all, a man stepping easily over a hole in the floor. ``I'll work. I think better up high.''

Sun looked at him in the mirror for a second too long. He smiled at her in it, the whole smile, the one that had closed the Pelletier deal and married Margaux and gotten three generations of board members to vote against their own arithmetic, and it still worked, he could see it work, he could see her decide not to fight him tonight, and he took the not-fighting as agreement, which was a thing he had been doing his whole life and had never once noticed he was doing.


\scenebreak


Up in the Aerie at one in the morning the city was a circuit diagram of his own genius.

That was how it looked to him, anyway, with the lights of his office off and the lights of the world on. Every lit window a node. Eight million people down there, and somewhere in the math of them was the sentence --- he was sure of it the way you are sure of things at one a.m. with a fine bright wire humming in your chest --- the one sentence that would make all of them understand why the chair needed a man in it. Not \textit{a} man. A man who \textit{loved} it. He stood at the glass with his bow tie undone and the crystal obelisk in his hand because he had carried it up without deciding to, and he turned it over and the city went through it broken into pieces and reassembled.

Behind him the suite was a museum and he was its last exhibit. His father's portrait, Pres III, in oils, looking out over the conference table he'd died at the head of --- not at, \textit{at the head of,} there was a difference and the family observed it. His grandfather's putter on its little brass cradle. And the photograph Cope loved best and never explained: himself at nine, in short pants, grinning, one arm buried to the elbow in a steel vat at the Defiance plant, mayonnaise to the bicep, and behind him a row of men in paper hats who had made the thing he was drowning his arm in, men whose names he had known once and lost, men whose town it was.

There had been a heater. The thought arrived sideways, the way the true things did when he was lit like this, slipping in under the manifesto. The Hearthstone. A good little product, the insurance arm had cross-sold it, a space heater with the Mercer name on the grille, and there had been a --- what was the word the lawyers had liked --- a \textit{thermal event profile,} and a memo, and a Saturday, his best thinking day, and a decision he had made about a quarter and a number and a window of time, and the decision had been the kind you make in eleven minutes and live inside for the rest of your life without ever quite going into the room where it's kept. He told a version of it at dinners sometimes --- \textit{a recall scare, we got out ahead of it, you've got to protect the brand} --- and people nodded, because protecting the brand was a virtue in the rooms he stood in, and the version he told had no town in it and no Saturday and no house. He did not, standing at the glass, go into the room. He almost did. The tiredness had taken the doors off their hinges and for a second the hallway to it stood open and dark. Then the manifesto came back, warm, electric, \textit{The Human Premium,} and he turned from the window toward his desk, and the moment closed over like water over a thrown stone, and he would not think of it again for a long time, and the not-thinking was the most expensive thing he owned.

He sat down at his father's desk and opened the second drawer, the one with the false back his grandfather had built for cigars and his father had used for a flask and Cope used for the thing Cope used it for, and he set himself up another, neat and quick and competent, a man maintaining a machine he was sure he had under perfect control because it had never once failed to start. He did not turn on the lamp. He wrote, in the dark, with his thumbs, on the small bright screen, the first line of the thing that was going to save him, and it was very good, he was sure of it, he was sure of it the way you are sure of things at one a.m. when you have not slept since Tuesday and they have just handed you a trophy for going extinct:

\textit{They will tell you a company is a machine. I am here to tell you a company is a family that happens to make mayonnaise, and you cannot fire your way to a family, and you cannot compute your way to a soul.}

He read it back twice. The bell-struck feeling rang through him, clean and high and total. Out past the glass the city held still, all its nodes lit, eight million people who did not know yet that they were waiting for him. He thought: \textit{this is the best I have ever felt.} He thought: \textit{I will sleep when this is finished.} He thought: \textit{Margaux should see me now.}

The chair behind him, his father's chair, the one with the head of the table, sat empty and turned slightly out, as if someone had just risen from it and stepped away, and behind that, in oils, Pres III watched his son begin to write his way out of the world and said the thing he had said when Cope was twelve and never said again, which Cope had spent forty years failing to hear the second half of: \textit{You'll get the company because you're a Mercer. Not because you're good.}

Cope, in the dark, underlined a word with his thumb.

He had stopped listening after \textit{Mercer.} He always had. That, in the end, was the whole story, though it would take the machine --- patient, tireless, incapable of cruelty or mercy or mayonnaise, reading every memo ever filed because it could not do otherwise --- another nineteen months to read it back to him in his own company's voice.

Downstairs, a bus shelter changed its slide. \textit{No off-sites.}

Up in the Aerie the last human chief executive in the consumer Fortune 100 wrote until the windows went gray, and felt wonderful, and did not sleep.

\clearpage
\chapter{Key-Man Risk}

\begin{transmission}
{\transheader TRANSMISSION 02 --- ``The Polite Word for a Bomb''}\par\vspace{0.5em}
Observe the specimen at rest in his natural habitat: forty-one floors of inherited limestone, a chief of staff who is the actual operating system, and a board that has invented a tender little phrase for a man who could detonate the whole enterprise simply by being himself. They call it \textit{key-man risk.} He hears a compliment. You will hear the pin coming out of the grenade. Somewhere in an archived org chart, a name he settled is waiting for daylight. Next stop: the man as the hazard he insures against.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{H}{e} came into the Tower on Monday at six forty in the morning like a man arriving early to his own surprise party.

He had not gone to Greenwich. He had slept, technically, the way a phone is charged when you unplug it at thirty percent, two hours on the leather sofa with the manifesto burning a clean low pilot light in him all night, and he had showered in the executive shower his grandfather had put in so a Mercer need never be seen by the city in a state of disarray, and he had keyed himself a small bright one from the false-backed drawer, a daylight one, the way you take a coffee. The lobby was empty except for Hector at the desk, who had been at it since Pres III, and Cope said, ``Morning, champ, how's the knee,'' and did not wait for the knee, and went up.

It was a beautiful elevator, brass and burl and a little needle that swept the floors like a barometer. He watched it climb and felt, with the bell-struck clarity he was still calling rest, that today was the day the company turned. He could not have told you toward what. Toward \textit{better.} Toward the thing the whole rotten reasonable world had forgotten you couldn't compute.

Sun was already in the Aerie when the doors opened, which was the way it had always been, Sun in the room before the room knew it was a room.


\scenebreak


She ran the brief the way she ran everything, which was to say invisibly, so that Cope could believe he was the one running it.

``Three things this morning,'' Sun said. She did not sit. She stood at the end of the long table under Pres III, with her tablet and a paper folder she did not open, and the early light came in gray off Sixth and laid itself along the table like something measured out. ``Earnings prep, the Dale-plus board deck, and a call from Helen Voss you are going to take at nine whether you want to or not.''

``I always want to take Helen.''

``You don't, but you will.'' She tapped the tablet. ``One. Condiments. Mercer's is flat. Not down --- flat, which at our cost of capital is a slow kind of down. Private label took another forty basis points of shelf, the category's not growing, and we already took price twice this year and the second time the volume blinked. Marketing wants nine million for a heritage campaign. I'd give them four and watch it.''

``Give them nine. People are starving for heritage.''

``People are starving for cheaper mayonnaise, Cope, which is a different appetite.'' She moved on before he could enjoy that. ``Two. Dale-plus. The streaming unit lost thirty-one million last quarter and the slate for next year is one prestige series nobody asked for and a back catalog we own because we once owned a company that owned it. The honest options are sell it, bundle it, or shoot it behind the barn. The board deck has all three and a recommendation you won't like.''

``Which is.''

``Behind the barn.''

``It has my grandfather's \textit{name} on it.''

``It has the \textit{Dale} on it,'' Sun said. ``The grandfather's optional.'' She let that sit one beat, a dry one, and went on. ``Three. Insurance. Our P\&C arm came in fine. Boring fine. Combined ratio under a hundred, no surprises, the only division in this company that does the thing companies are supposed to do, which is bore you profitably. Someone in the actuarial group flagged a reserve question on the legacy product book and I told her to put it in writing and she did. It's nothing. I'm telling you it's nothing so that when you see the words \textit{legacy product} in a memo you don't make it something.''

He had heard, of the three things, perhaps one and a half. He had heard \textit{flat} and let it slide off, because flat was not a story and Cope lived in stories about numbers, not numbers, and he had heard \textit{behind the barn} and felt a small clean flare of grievance that warmed him, because grievance, for Cope, was fuel: it meant there was something to fight, and a man with something to fight was necessary. He was already, by the third thing, three turns ahead, out past the table, on a stage, saying the word \textit{family.}

``You're not listening,'' Sun said. Not unkindly. The way you'd note weather.

``I'm listening like a jazz man, Sun. I'm listening for the spaces.'' He came back to the room and gave her the full smile, the one that had closed Pelletier, and she did not take it, she never took it before nine, and he loved that about her and resented it in exactly equal measure. ``Tell me the thing under the three things. There's always a thing under the three things with you. That's why I keep you.''

For a second something moved behind her face and he did not read it.

``Helen Voss is calling at nine,'' she said, ``because Tidewater is going to cross five percent this week. And the board is nervous.''

``The board's always nervous. That's the job. I'm the one who isn't nervous, that's \textit{my} job, we have a division of labor going back four generations.'' He stood and went to the glass. Down there the city was doing its Monday, the small dark figures with their small dark certainties, none of them, he was sure, lying awake at one a.m. with the one sentence in them. ``Nervous about what specifically. Say the words.''

Sun said the words.

``They're nervous about key-man risk.''


\scenebreak


He turned around with his whole face lit, because he had heard a compliment.

That was the thing about Cope, the thing the machine would one day lay out in a rationale so clean it read like a coroner's report: he could take any sentence in the language and find, inside it, the version that loved him. \textit{Key-man.} He heard \textit{key.} The one indispensable tumbler in the whole brass lock of the enterprise. He heard the citation from the gala---\textit{custodian of the irreplaceable}---handed back to him now in the board's own grammar, and he felt, standing in his father's light, a warmth go through him that he would have called vindication and that was, in fact, the daylight bump finding its second wind.

``Well,'' he said, and he could not keep the pleasure out of it, ``they're not wrong.''

Sun looked at him.

She had the specific stillness she got, the one that was not patience but the management of the opposite of patience. She had been translating this man to himself and to the world for eleven years, and she knew, the way you know the give of a stair you've climbed ten thousand times, exactly where his foot was about to go through.

``Cope,'' she said. ``I want to make sure you heard the phrase the way they mean it.''

``I heard it fine.''

``Key-man risk is the thing you insure against.'' She said it slowly, in two parts, not three, because two was the shape of a thing she actually needed to land. ``It's the line in the audit where a single individual is so central that his death, his departure, or his \textit{conduct} could materially impair the enterprise. It's not a medal, Cope. It's a hazard rating. They are not saying you're the key. They're saying you're the \textit{risk.}''

He heard her. Some back room of him, the same one that had filed the obituary at the gala and left it unread, understood the words perfectly and declined to forward them. Up front where Cope lived, the sentence would not fit through the door, because the door was the exact shape of his idea of himself, and so it bounced, gently, and he smiled.

``That's their fear talking,'' he said. ``That's a board that's been spooked by a deck. Of \textit{course} I'm central. Centrality isn't a risk, Sun, it's the whole point of a leader. You want a CEO you can lose without noticing? They make those now. They're called Marcus.'' He liked the line too much to let it go. ``Put that somewhere.''

``I'm not going to put that anywhere,'' Sun said, ``and I'd give a great deal for you to never say it on a hot mic.'' She closed the folder she had not opened. ``Take Helen at nine. Listen to the whole sentence.''


\scenebreak


While she set up the Dale-plus deck he wandered, the way he wandered when a thing was assembling in him and he needed his hands busy somewhere small so the big thing could build in the dark.

He went to the credenza where the framed things lived, too official to hang and too sacred to file. The 1961 ribbon-cutting, Aldous with a comb-over and shears the size of a sword. A 1988 Fortune cover, Pres III looking like a man who had never once doubted a thing, \textit{AMERICA'S CONDIMENT KING,} which the family pronounced without irony. And there, in a flat archival folder assembled for some anniversary nobody remembered, was the org chart.

He pulled it out because he loved it. He loved an org chart the way some men loved a model train, the clean little boxes, the names doing their jobs so that he could do his, which was to be the box at the top. This one was from---he checked the corner---2018, a good year, a year before everything, a fat confident pyramid of a company that still believed in itself, and he ran his thumb down it like a yearbook, warm and nostalgic and three grams of certainty into a Monday and not, for once, looking for anything.

His thumb stopped on a box two levels down. \textit{VP, Hearthside Division.}

\textit{Renata Cho.}

The name went through him like a draft from a door he had not known was open. For a moment---a clean, overexposed, bell-struck moment---he was not in the Aerie at all but somewhere with a window and a city and her laugh, which had been a real laugh, he had been \textit{sure} it was a real laugh, the kind you can't fake, and then the moment did what those moments had learned to do, which was close, fast, the door swinging shut on its own weight, and Cope's thumb moved on down the chart to the next box as if it were the only part of him that had been properly trained. He was already not thinking about it; he was excellent at not thinking about it, which was arguably the core competency of his life.

``Whatever happened to Hearthside as a business,'' he said out loud, to cover the silence with sound. ``We used to \textit{make} things. Toasters. Little heaters.''

``We sold the line and licensed the name and now the name makes things we don't,'' Sun said, not looking up. But she had looked up, for half a second, when his thumb stopped. She had seen exactly where it stopped. She filed it the way she filed everything, in the place she kept the things she carried for him that he did not know she carried---a place that had gotten, over eleven years, very full.

He slid the org chart back into its folder, and the name back into its drawer, and was whole again, warm again, the man at the top of the pyramid. He did not see Sun's hand go, a moment later, to her own tablet, and pull up a thing, and look at it, and put it away.


\scenebreak


The young one came in at eight thirty with the earnings draft.

Her name was Maya. She was twenty-six and four months out of a comms shop, and she came in holding a tablet to her chest like a shield, a little electrified by the room, by Pres III, by being summoned at all, and Cope felt it from across the suite and turned toward it the way a plant turns, helplessly, gratefully.

``Maya,'' he said, and her name in his mouth was already a small warm gift, because he had remembered it, of course he had remembered it, remembering was the one thing he and the machine did identically. ``Come in, come in, don't hover, nobody who works for me hovers. Sun hovers and that's because Sun's deciding whether to fire me.'' Maya laughed, the real surprised one, the one Cope went through his whole life fishing for. ``What've we got.''

``The release draft. Mr. Mercer. The---the earnings language for the call, legal wanted you to see the---''

``Cope. Nobody's called me Mr. Mercer since my father died and frankly he'd have preferred it. Sit.'' He pulled out the chair beside his, not across, beside, and patted it, and leaned in to look at her screen with the warmth turned all the way up, \textit{what's a face like that doing in compliance language,} and he was not aware of doing any of it. It was the groove, the same record that had cut the card into Bryce's hand at the coat check on Thursday and a hundred hands before that: a man who could not pass a person who looked at him like that without leaning toward it and calling the leaning generosity.

``This line here,'' he said, his shoulder against her shoulder now, ''\textit{headwinds in the legacy condiment category.} No. Headwinds is what you say when you're losing. We have \textit{a category undergoing a generational shift toward heritage,} which is true, and which is \textit{ours,} and you wrote \textit{headwinds} because some MBA taught you to apologize and I'm going to teach you not to. You've got a good ear, Maya. You buried it under a committee. Don't ever---''

``Maya.'' Sun's voice, from the other end of the table. Even. Pleasant. A blade with a pillowcase over it. ``I need the legal redlines before the nine o'clock. Walk them to me. Cope, you'll get the clean draft at ten.''

There was a small silence in which three different people understood three different things.

Maya stood up fast, grateful and confused, the way they always were---warmed and then, half a second later, cooled, and never able to name the temperature they'd been at---and went down the table to Sun, who took the tablet and said something low about the redlines that was entirely real and entirely a pretext, and walked her to the door with a hand not quite touching her back, and said, ``Good catch on the legacy line, send me your other notes and I'll get them into the build,'' because Sun's other full-time job, the one not in any chart, was making sure the young ones left the room with their competence in their hands instead of the other thing---standing between this man and the version of him that had a name in a 2018 box and a drawer the company had spent a decade managing.

She had done it a hundred times. That was the tragedy of her: not that she fought him, but that she had gotten so good at cleaning up after him that the cleaning had become a craft, a thing she could put on no résumé and could not stop doing.

Cope watched Maya go and felt nothing but expansive. He had \textit{seen} her. He had given a young person a real note on a gray Monday, which was leadership, which was the exact irreplaceable human heartbeat the board in its fear was calling a hazard. He felt, watching the door close, like the proof of his own thesis.

``She's got something,'' he said. ``Maya. We should give her real things to do.''

``I'm already giving her real things to do,'' Sun said. ``That's why she works \textit{here} and not \textit{near you.}'' She said it lightly. He took it as a compliment to Maya, and she let him.


\scenebreak


At eight fifty her phone buzzed and she stepped out, and Cope, alone, did the thing he should not have done, which was open her tablet, which she had left, because Sun trusted him with everything except himself.

He was not snooping. He told himself he was not snooping. He was a king walking his own hall. There was an open ledger on the screen, the discretionary line, the small quiet budget Sun ran below the notice of anyone---a settlement here, a consulting retainer there, the soft grease of a large old institution---and his eye went down it the way it had gone down the org chart, idle, proprietary, warm, \textit{there's old So-and-so.}

A line stopped him. A vendor he did not know. \textit{Cardinal \& Vane --- advisory, confidential --- engagement \#C-1180.} The number was not small. Beneath it, a memo field, two words in Sun's clipped shorthand: \textit{legacy matter.}

Legacy. That word again. He almost made it into something. Cardinal and Vane---it had the sound of a quiet firm, the kind that does not have a website, the kind a man calls at two in the morning from a hotel when a thing has happened that cannot be allowed to have happened, and Cope had, somewhere far back in the unlit hall of himself, a memory of a corridor and a favor and a man in a good coat who made a thing go away in 2018 so completely that Cope had been able to stop knowing it had ever needed to go away---

The door opened. Sun came back in. She crossed the room, not fast, and took the tablet out of his hands the way she had taken the second card out of his hands on Thursday, the exact same motion, eleven years of the exact same motion, and she did not raise her voice.

``That's a closed matter,'' she said.

``Cardinal and Vane. What is that, a---''

``It's a closed matter, Cope, and it stays closed because I'm the only person in this company who looks at that line.'' She turned the tablet face-down against her chest. ``You pay me to carry things you don't have to look at. That's the whole job. Let me do the whole job.''

And here was the thing, the thing the machine would never understand because it would understand it perfectly: he let her. He let her because it was easier and because he loved her and because some animal part of him, the part that had survived four generations of inheritance by knowing exactly which sentences to leave in the kitchen, had long ago made Sun the back office of his entire soul. He let the door close. He was already, gratefully, somewhere else.

``What would I do without you,'' he said, and meant it, completely, for the duration of the sentence.

``You'd be on the news,'' Sun said.


\scenebreak


Helen Voss called at nine on the dot, because Helen Voss had never once in her life been late to deliver bad news in a kind voice.

She was the lead director and chair of the board, a retired pharma CEO with a low pleasant rasp and the unhurried diction of a woman who had fired better men than Cope and sent flowers after. He took the call standing at the glass with the city below him, which was how he took all calls he intended to win.

``Helen. To what do I owe.''

``Cope.'' A warmth in it, real, that was the worst part. ``I won't keep you. I wanted you to hear this from me before the deck goes around. Tidewater's going to cross five this week. Frade files, it becomes a thing, and the board's going to want to talk about the proxy posture and the---'' a small considered pause, a woman choosing the soft version of a hard word---''the governance optics. Before it's a fire instead of a smell.''

``It's nerves, Helen. It's a fund building a position so it can scare a board into a fee event. I've watched Frade do this dance for thirty years.''

``It might be that.'' She let him have it, the way you let a man have a thing you're about to take from him. ``Cope, the word that keeps coming up in the room is one I want you to sit with, because I don't think you've sat with it, and I say that as a friend who would like you to keep the job you have.''

He knew, before she said it, that it was the word. He set his face the way he set it for the camera and he smiled out at the city he was sure was waiting for him, eight million lit nodes of a circuit diagram that ran on his genius.

``They're worried about key-man risk,'' Helen said. ``And Cope---I need you to hear which man they think is the key, and which thing they think is the risk. They're the same man. That's what nobody wants to say out loud in a room with a portrait of your father in it.''

And Cope, standing in his father's light with a clean bright wire humming in his chest, a manifesto rising in him like a tide, a name in a box he had already stopped seeing, a drawer he had let Sun close, and a phrase the whole board was using as a coroner's term---

Cope heard a compliment.

``Tell the room I'm flattered,'' he said, and laughed, warm, delighted, certain. ``And tell them not to worry. I've got a plan that makes all of this moot. It's a premium play, Helen. The whole thing. You're going to love it. Give me the weekend.''

There was a silence on the line in which Helen Voss, who had done the arithmetic on better men, declined, out of mercy, to do it out loud.

``Take care of yourself, Cope,'' she said, which was the thing you say to the key and the thing you say to the risk and, in the end, the only honest sentence in the call.

He hung up enormous. He went to the desk. He opened the manifesto on the bright small screen and the first line was still there, still very good---\textit{you cannot compute your way to a soul}---and below it, now, in the gray nine o'clock light, three more turns ahead of everyone, already past the board, past Frade, past the numbers Sun had laid out like something measured for a coffin, he wrote the two words that were going to save him, and they rang through him like a struck bell, clean and high and total.

\textit{The Human Premium.}

He underlined it with his thumb. Behind him the chair at the head of the table sat slightly turned out, as if someone had just risen from it, and Pres III watched from the oils, and forty floors down a slide changed on a bus shelter---\textit{No off-sites.} And Sun, at the other end of the room, looked at the back of his head for a moment too long, and then opened the file she kept and did not open, the one from 2021, the recall memo she had written and he had overridden, the copy she had kept for six years while she decided whether she was a witness or an accomplice, and she looked at the first line of it.

Then she closed it, unsent, unsigned, the way she had closed it every Monday for six years, and she went to make sure the man with the plan made his ten o'clock.

\clearpage
\chapter{Thirteen-D}

\begin{transmission}
{\transheader TRANSMISSION 03 --- ``Beloved, Comma, Liability''}\par\vspace{0.5em}
Here is a number with teeth: five percent. Cross it, and the polite fiction becomes a federal filing, and the rumor puts on a suit and goes on television. Tonight an activist named Frade will describe our man, on basic cable, with two words that will follow him to the grave --- \textit{beloved liability} --- and the first word will be the one that kills him, because he has spent fifty-four years believing it was a defense. Next stop: the moment a diagnosis arrives disguised as a compliment, for the second time, from a stranger.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} filing hit the wire at 9:14 on a Wednesday, and by 9:15 Cope knew it the way you know a tooth is gone before your tongue confirms it, because Sun stopped pretending to do anything else.

She came in without the cards. That was how he knew it was real. On any ordinary morning Sun came in with the cards --- the three things, the one blade, the small index of the day filed down to a shape a man could hold --- and on this morning she came in with nothing in her hands at all, which for Sun was a kind of nakedness, and she said, ``They filed.''

``Good,'' Cope said.

He had decided, at some point in the gray of the last few days, that the right posture for this was \textit{good.} A filing was a fight, and a fight was a stage, and a stage was the one room he had never lost in. He was at the glass with his coffee, which he was not drinking, and the obelisk was on the credenza where he had set it Thursday and not moved since, catching the morning the way it had caught the chandeliers, doing the one thing it was for.

``Tidewater crossed five Monday,'' Sun said. ``They had ten business days to file. They took two. That's a message. The 13D names the intent in the second paragraph. They're not asking for a board seat or a buyback or a spin of Dale+.'' She paused, and he understood the pause was her deciding whether to say it gently, and then deciding he had not earned gentle. ``They're asking to replace you with an AURELIUS. By name. The whole thesis. Cost, consistency, no key-man risk. It reads like the deck wrote the filing, which it did.''

``Read me the second paragraph.''

``You don't want the second paragraph.''

``I love the second paragraph. Read it.''

She read it. She read it in the flat voice she used for things she did not want her own opinion smuggled into, and it was, he had to admit, beautifully drafted, the way everything on the other side was beautifully drafted now, clean and warm and bloodless: \textit{a beloved institution led, with great personal distinction, by a model of stewardship the market has outgrown.} Led with distinction. Outgrown. They had put the compliment and the verdict in the same sentence again, the way the institute had, the way they all did now, and for a half-second the back room of him filed the quiet report --- \textit{they keep doing this, they keep handing you the knife wrapped in the bow} --- and he did not let it reach his face. His face was doing fine.

``Outgrown,'' Cope said. ``That's Frade. He thinks he's folksy. He's from Greenwich, same as me, his folksy is a costume he rents.''

``He's going on Halloran at eleven.''

And there it was. Sun had said it would happen in the car Thursday --- \textit{don't decide it live on Halloran's show} --- and now here was the show, here was the eleven o'clock, the thing she had asked him to get ahead of and he had instead spent the weekend up in the Aerie writing a manifesto and maintaining the drawer, and he felt, under the bright wire, a small hot satisfaction that the future had arrived exactly where she'd told him it would, as if her accuracy were a kind of permission.

``Then we'll watch Frade on Halloran,'' Cope said, ``and then I'll go on Halloran, and we'll see which of us the country wants to have a beer with.''

Sun did not say anything for a moment. Then she said, ``The calls started at 9:14.''

``What calls.''

``All of them,'' Sun said, and went to take them.


\scenebreak


By ten the floor outside the Aerie had the particular hum of an institution discovering it is a story. Cope could feel it through the glass wall, the comms people moving faster and talking lower, the legal people moving slower and talking longer, the whole forty-first floor reorganizing itself around a document the way a body reorganizes around a wound, sending everything to the site of it. He had seen it before. He had, in fact, been good at this before, in the years when the thing the floor organized around was a deal he was closing and not a deal being closed on him, and he told himself there was no difference, it was the same energy, it was \textit{attention,} and attention was the medium he swam in, attention was the water.

He went into the small private washroom off the Aerie --- his grandfather's, marble the color of nothing, no Desmond, no audience, just the man and the good light --- and he set himself up one, neat and quick, because it was a Wednesday and the country was about to talk about him and a man should meet the country at pitch. The world came up to the note. The bell. He looked at himself and the jaw was the jaw and he said, very quietly, ``Beloved,'' and then he laughed, because \textit{beloved} was a strong open, \textit{beloved} was a thing you could build a whole campaign on, the fool had handed him his own banner and called it an attack.

He did not say the second word to the mirror. He left it in the kitchen.

Back at the desk he did the thing he had decided not to do, which was the thing he always did, which was reach for a friendly. He had a man --- a friendly, a contact, a markets columnist named Healy at one of the papers that still printed, a man Cope had fed scoops to for fifteen years and golfed with twice and considered, in the loose generous accounting of his affections, a friend --- and he started thumbing Healy a line, fast, too fast, the screen too bright. \textit{Off record. Frade's ``outgrown'' is the tell. You don't pay a 5\% premium to acquire a thing you've outgrown. He needs the human in the chair or there's no story. The whole short thesis is long my heartbeat. Use it, don't source it.} He read it back. It was good. It was the kind of thing that, placed right, became the counter-narrative by lunch, and he sent it, and felt the small electric competence of a man maintaining a machine he was sure he had under control.

He did not see Healy's reply come in twenty minutes later, because by then he was watching the monitor, and the reply, when he read it that night, would say only: \textit{Cope. Off record back at you --- get a lawyer in the room before you text anyone, including me. They subpoena texts.} And Cope would read that the way he read everything that did not fit the manifesto, which was to say he would file it in the kitchen and shut the door.


\scenebreak


The monitor on the Aerie's far wall was the size of a small mural, and it had spent twenty years showing the markets in green and red while Mercer men stood in front of it and felt large, and at eleven o'clock it showed Garrett Halloran's set, the desk, the mug nobody drank from, and Gus Frade in a quarter-zip the color of money pretending to be the color of fleece.

Cope watched it alone. He had told Sun he wanted the room. The truth, which he did not examine, was that he did not want a witness for the next four minutes, the way you do not want a witness when you weigh yourself. He stood in the middle of his fathers --- Pres III in oils, the putter on its cradle, the boy with his arm in the vat --- and he watched a man from his own zip code take him apart on basic cable with the warmth of a guy returning your dog.

``Garrett, I want to be careful here,'' Frade said, which meant he was about to be precise. ``Because this is not a story about a bad man. I want that on the record. Cope Mercer is, by every account, a \textit{wonderful} human being. He remembers your kid's birthday. He gives a hell of a toast.'' A little laugh, shared with Halloran, the laugh of two men agreeing about a third who isn't in the room. ``I've been to his table. The lamb's terrific.''

\textit{The lamb.} Cope felt the floor of his stomach do something. The man had been to the table.

``But here's the thing about love, Garrett, and I learned this the hard way in my own businesses,'' Frade said, leaning in, folksy, the costume fitting him like skin. ``Love is not a governance model. You can love a man and still owe a fiduciary duty to the eighty thousand people who own this company through their pension funds. And the hard, unsentimental fact --- and it gives me no pleasure --- is that Cope Mercer is, at this point, a beloved liability.''

There it was.

Halloran said something. Frade said something back. The chyron at the bottom of the screen, white sans-serif on a red bar, had already done its work, the network's producers reading the room faster than the room could, and it said, in the typeface of people who would be reasonable at you until you were gone:

MERCER: ``A BELOVED LIABILITY''

They had put it in his own mouth. They had put quotation marks around it and his name in front of it, the way you do with a man's last words.

Cope heard, very distantly, the word \textit{beloved,} and reached for it, because \textit{beloved} was the open, \textit{beloved} was the banner --- and found that he could not get to it, because the second word had arrived first, and the second word was not a word the way the first one was a word. \textit{Liability} was a thing with a column. \textit{Liability} was the side of the ledger you subtract. It was what the insurance arm called the heater after Defiance, in the memo, on the Saturday --- \textit{the thermal-event liability} --- and the hallway to that room stood open and dark for exactly as long as it took him to slam it, and he slammed it, and stayed standing in the museum of his fathers holding a coffee he was not drinking, and understood, the way you understand a tooth, that for the second time in a week a stranger had handed him a compliment and it had come apart in his hands into a diagnosis.

\textit{Key-man risk,} Helen Voss had said on Monday, kindly, as if it were a feature. The polite word for a man who could detonate the company by being himself. And now this. \textit{Beloved liability.} The compliment was the fuse. The compliment was always the fuse. They loved him on the way out the way you love a house you've already sold.

He did not let it reach his face. There was no one to reach it for, and he did it anyway, because the face was the last machine he trusted, and it had never once failed to start.


\scenebreak


The phone went off in his hand and he answered it without looking, because answering was a reflex, and it was Pip.

``Dad. Are you watching this.'' Not a question. Fast, flat, technical, the voice she used when she was managing fear by making it into a problem set. ``Don't go on. Whatever you're about to do, don't go on the air. I can see it from here, I can see you deciding it. The 13D is a Schedule 13D, it's a disclosure document, it's \textit{boring,} the worst thing you can do is make it interesting. Frade \textit{wants} you on Halloran. He wants the human to come out and be human at him on television. That's the whole play. The machine never does the interview. That's the entire --- Dad, the asymmetry is the point, you cannot win a contest of \textit{not having a meltdown} against a thing that can't melt.''

``Hi, sweetheart,'' Cope said.

A breath on the line. He heard her recalibrate, heard the researcher set down the clipboard. ``Hi,'' she said, smaller. ``You sound --- are you okay? You sound like Tuesday.''

``What's Tuesday.''

``You sound up. You sound like you haven't ---'' She stopped. She was twenty-four and she had spent her whole life learning which of her father's sentences to leave in the kitchen, and he heard her decide to leave this one, heard the young thing in her flinch back from the edge of it. ``Just. Don't go on TV today. Please. For me. Go home. Is Mom ---'' Another stop, a harder one. ``Are you at home or are you at the office.''

``I think better up high,'' Cope said.

The line was quiet. He had meant it to be charming and it landed in the silence and was not charming, and he heard, in the quiet, his daughter doing arithmetic about her father, the same arithmetic the board did, the same arithmetic the market did, everyone he loved with a spreadsheet open, and he could not stand it, the being-counted, so he did the thing he did, the only move he had ever had, which was to make it warm and make it large and step easily over the hole in the floor.

``I'm going to be fine, champ,'' he said. ``Better than fine. You know what they handed me today? They handed me my whole campaign and called it an insult. \textit{Beloved.} You don't accidentally call a man beloved. They can't help it. Even when they're killing you, they have to admit you're loved. That's the premium, Pip. That's the whole ---'' and he heard it assemble in him as he said it, the weather, the charge, the pressure-front he had been building since Thursday finding its name. ``There's a premium on the human. There's a \textit{Human Premium.} You can't compute it and you can't fire your way to it and the market is about to learn it pays for it.''

Silence on the line. Then, very quietly, not the researcher and not the child, some third Pip he rarely got: ``Dad. The premium on a human, in a market, is a thing the market sets. Not you. You don't get to declare yourself scarce and call it value.'' A pause. ``That's not love. That's just price. And the price is in the filing.''

``You sound like your mother.''

``Somebody has to.'' And then, fast, young, gone before he could hold it: ``Don't go on. I love you. Don't go on,'' and she hung up, and he stood holding the dead phone in the museum of his fathers and felt, for one clean second, the size of what was happening to him, and then the second passed, the way they did, and the manifesto came back up warm and total and he turned from the boy in the vat toward his desk.


\scenebreak


Sun found him at two with his collar open and a yellow legal pad covered in his own handwriting, which had gotten worse over the years, smaller and faster and angrier, the hand of a man taking dictation from a wire.

``You sent something to Healy,'' Sun said. She did not sit. ``His desk called legal to confirm we knew you'd texted a columnist about an active 13D the morning it filed. We didn't know. So now legal knows. So now it's in a memo.''

``Healy's a friend.''

``Healy's a byline.'' She set down, on the desk, a single sheet --- the cards, finally, the day filed to a shape --- and he saw it had three lines and a blank space under them where the fourth thing would have been if she'd had the heart. ``Three things. The stock is down nine and it's not the filing, it's the clip, 'cheaper than a man' from Thursday is running next to 'beloved liability' from this morning and the producers cut them together so it looks like you agree with him. Two: Helen wants a board call Friday and she used the word 'process,' which means the independent directors have already talked without you. Three.'' She stopped.

``Three,'' Cope said.

``Don't go on Halloran.'' The blade. One per scene, and she spent it here. ``I know you've decided to. I knew it before you did. You're going to tell me the country wants to have a beer with you, and Cope --- they do. That's not the problem. The problem is the machine doesn't drink, and you're about to get up on a stool next to a thing that never says one regrettable word, and prove, live, in front of the people deciding whether you're a liability, that you are a man who can be provoked.'' She picked her glasses off her head and folded them, which was Sun for \textit{I have finished managing you and am now simply telling you.} ``They'll watch you be magnificent and human and unscripted for six minutes and then they'll write you a check for severance, and the check will be warm, and it will name your years, and it will be the kindest thing this company ever sent anyone, and a machine will have drafted it.''

He looked at her. He loved her. She ran the company and she was tired and she was right, and he could see all three of those things at once and chose, the way he always chose, the one that did not require him to stop.

``You're scared,'' Cope said gently, and he meant it as mercy, ``because you can only see the defense. You're trying to save the chair.'' He stood, and the wire in his chest sang, and the manifesto stood up inside him like a man rising to give a toast. ``I'm not going to defend the chair, Sun. Defending it is conceding it's theirs to take. I'm going to do the other thing. I'm going to run \textit{for} it. Not for me.'' He believed this, completely, for the length of the sentence. ``For the human in it. We don't argue the man's worth keeping. We make the country \textit{want} one. We make 'do you want a person running the things you eat and insure and trust' the only question on the ballot, and we make the answer so obvious that Frade's arithmetic looks like what it is, which is a man who knows the cost of everything.'' He was pacing now, fast, lit, the legal pad in his hand. ``There's a premium on it, Sun. The Human Premium. It's in the word he used and couldn't help. \textit{Beloved.} They'll pay it. We just have to put it on the shelf where they can buy it.''

Sun watched him for a long moment, the way she'd watched him in the car mirror Thursday, a second too long, and he took the looking for listening and the not-fighting for agreement, the way he had his whole life, and never once noticed he was doing it.

``I'll cancel Halloran,'' she said finally, and he heard \textit{yes,} and what she had actually said was that she would cancel the thing he wanted so he could not do the thing she feared, which were different sentences, and had never once been the same one.

She went to the door. She stopped with her hand on it. The forty-first floor hummed behind her, organizing itself around the wound.

``They put it in quotation marks,'' she said, not turning around. '''A beloved liability.' With your name in front of it. You understand they'll never unhook those words from you now. Not ever. It's the obituary again, Cope. They keep writing it kind.'' And then, because she was decent, and done, and both in the same breath: ``It's a good line. I hate that it's a good line.''

She left.

Cope stood at the glass. Down the avenue, lit at the crown the way Aldous had insisted in '61 so a man coming up Sixth would know there was somebody home, the tower held its light against the gray afternoon, and out past it the city went on forever, eight million people who did not know yet that he was about to make them an offer. He looked at the legal pad. At the top, underlined twice, in the small fast angry hand, three words, a triad, the shape that got past the charm and into the man, his own charm turned on himself at last:

\textit{The Human Premium.}

He felt wonderful. He felt like the inside of a struck bell. He had not slept, in any way a doctor would sign off on, since a day he could no longer name, and somewhere behind him the chair at the head of the table sat empty and turned slightly out, and in oils his father watched his son mistake the obituary for a brief, and Cope opened the second drawer for the small bright maintenance the campaign would require, and began, in daylight, to write his way out of the world.

\clearpage
\chapter{A Steward, Not a Sovereign}

\begin{transmission}
{\transheader TRANSMISSION 04 --- ``The Letter That Loved You Back''}\par\vspace{0.5em}
They wheel in the future and it does not hum, does not glow, does not threaten. It simply drafts a layoff letter --- four warm paragraphs, the severance math right the first time, every worker's years remembered --- kinder than anything a human officer of this company has ever signed. That is the horror, and the room feels it, and the room buys it anyway, because the letter wants nothing and a man always wants something. Next stop: the uncanny valley of being out-loved by a spreadsheet.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} deck was titled \textit{A Steward, Not a Sovereign}, and Cope decided before the second slide that he was going to beat it on charm.

This was a category error, and he knew it, somewhere under the bright wire that had been humming in his chest since a Tuesday he could no longer locate on a calendar, and he was going to make the error anyway, because charm was the only club in the bag he had ever fully trusted. They had given the board the long conference room on Forty for it, the one with his father's portrait moved out --- someone had moved his father's portrait out, he noticed, and filed the noticing in the back room with the other quiet reports --- and a screen had been wheeled in the size of a small barn door, and around the table sat eleven directors of Mercer-Dale Companies and two strangers from the West Coast and Gus Frade, who was not technically allowed to be in this meeting and was in this meeting, in a quarter-zip, drinking the board's coffee like a man who already owned the urn.

``I want to thank you all for the openness,'' said the woman from Praxis, and Cope, who had spent thirty years reading the temperature of a room off the first sentence a stranger said in it, understood with a small cold drop that she meant it.

Her name was Asha Varma. She was perhaps forty, in a gray that wasn't quite a suit, no jewelry but a thin steel watch, and she stood at the head of the table --- \textit{the head of the table}, where Pres III had died, there was a difference and the family observed it, and she did not know there was a difference and so it could not be taken from her --- and she did not have the laser pointer twitch or the upsell hunger or any of the tells of the men who had been pitching Cope things his whole life. She had the worst thing a person across a table can have. She had no need of him at all, and she was sorry about it.

``I founded Praxis,'' Asha said, ``because my mother worked thirty-one years for a man who laid off her plant by fax. He had the number wrong on the fax. He was off by, it turned out, about four months of her severance, in his own favor, and it took her a year and a lawyer she couldn't afford to fix it, and he never knew, and if you'd told him he'd have been horrified, because he was not a cruel man.'' She let that sit. She was not, Cope registered with rising unease, performing the pause. She was just letting a true thing have the air it needed. ``He was not cruel. He was \textit{careless}. There is so much careless. We have all just decided to call it human.''

Around the table the directors did the thing boards do, which is to look very neutral while recalculating.

``We are not here to tell you a machine has a soul,'' Asha went on. ``We think that's a category error'' --- and Cope, who had been about to deploy the soul, felt the word taken gently out of his hand before he'd drawn it, the way Sun had taken the second card out of his hand at the gala --- ``and frankly we think \textit{soul} is what people reach for when they want to keep doing something the numbers say to stop. We're here to tell you something smaller and harder. The chair does about nine things. We can show you, line by line, that on eight of them the human is now the weak link, and on the ninth --- the one everybody means when they say soul, the \textit{caring} --- we can show you the human isn't even reliably winning \textit{that}.'' She clicked. The slide said, in the soft sans-serif of the people who were going to be reasonable at you until you were gone: \textit{A steward owns nothing. A sovereign owns everything, including the consequences he can outrun.} ``We're not asking you to crown a king. We're asking you to hire a steward who can't inherit, can't tire, can't lie to you, and can't run.''

Frade, from the cheap seats, said, ``Tell 'em the part about the off-sites,'' and grinned, and a couple of directors laughed, and Asha did not laugh, which Cope clocked as the most dangerous thing she'd done yet. The salesman laughs at the patron's joke. She wasn't selling. She believed.


\scenebreak


He went at her in the Q\&A the way he went at everything, sideways and warm, looking for the seam.

``Asha --- may I call you Asha --- that's a beautiful story about your mother, and I mean that, my own grandfather laid men off in Defiance with his own mouth, in the room, because he thought they deserved the room.'' A few nods; the Defiance card always played. ``But here's what I keep running aground on. A fax doesn't love your mother. Neither, with respect, does a server farm in Virginia. You can get the \textit{number} right. God knows you can get the number right. But the man who fires you looking you in the eye, who \textit{carries} it --- isn't the carrying the whole job? Isn't a leader the person who has to \textit{feel} the thirty-one years?''

It was, he thought, a very good run. Toast cadence, building, the triad coming: \textit{the room, the carrying, the feeling.} He'd landed bigger rooms than this with less.

``That's the most generous version of the argument,'' Asha said, and she said \textit{generous} with no edge at all, which was how he knew he was in trouble. ``And I want to honor it. So can I just --- actually do the thing, instead of arguing about whether the thing has a soul? You have a real decision in front of this board. I've read the materials Mr. Frade's people pulled and the board's own deck. The Toledo plant. The condiment line that's been losing money since the private-label shift. You're going to close it. You haven't announced it. Three hundred and forty people.''

The room changed pressure. Sun, down the table beside Cope, went still in the particular way she had, the way she'd gone still in the car when he said Renata's name.

``That's not ---'' said Helen Voss, the board chair.

``It's in the November board pack,'' Asha said, gently, not a gotcha, just a person who had read the thing she'd been given. ``It's a sound decision. I'm not here to second-guess it; the math is the math. What I'd like to show you is \textit{how} the steward does the part you say it can't. The carrying.'' She looked, for the first time, directly at Cope, and her look had nothing in it he could use --- no challenge, no flirtation, no fear, no want. It was the look you give a man you've already grieved. ``Marcus has the same materials I do. Let's ask it to write the letter. Right now. To the Toledo workforce. And then, Mr. Mercer --- you've signed letters like this. You tell the room which one a human should rather have gotten.''

She did not wait for permission, because she did not, structurally, need it. She typed something Cope couldn't see. The barn-door screen woke.


\scenebreak


It wrote it in front of them, and that was the obscene part, the part Cope would carry up to the Aerie and turn over in his hands like the obelisk: it wrote it the way water finds level, with no visible labor, no second-guessing, no draft you could see it ashamed of.

The board portal threw the rationale up first, because that was the rule, the rule the board had bought --- \textit{it logs everything and cannot knowingly lie} --- and the rationale was four lines of the most undeniable prose Cope had ever read about his own company. \textit{Closure of the Toledo shelf-stable line is warranted: gross margin negative eleven quarters; private-label substitution structural, not cyclical; redeployment of capital to insurance underwriting yields higher risk-adjusted return. Human cost: 340 roles. Mitigation below. This memo will be issued to the board with the closure recommendation; the affected workforce will not be informed before the board has decided, but no later, because both facts are true and the sequencing of a person's bad news to protect the announcement of a dividend is a courtesy to the dividend.}

Frade laughed out loud at that one. Cope did not. \textit{A courtesy to the dividend.} He had spent a career being a courtesy to the dividend and had never once heard it said in a voice with no person behind it.

Then the letter came.

It was four paragraphs. Cope read it on the big screen with three hundred and forty strangers' lives in it, and Sun read it beside him, and he watched her read it, because watching Sun read things was a habit older than the marriage, and he saw something cross her face that he had no word for and would spend the next nineteen months learning the word for.

The letter named the line. \textit{Mercer's Original, made in Toledo since 1971.} It named the years --- not in the aggregate, not ``your collective service,'' but it had gone into the file and found that the median tenure on that floor was nineteen years and it \textit{said so}, it said \textit{many of you have given this company more of your working life than I will ever be able to give back, and I will not insult that by pretending this letter is enough.} It got the severance math right --- Cope could see Sun's eyes go to the number and stay there, doing the check she always did, and not find the error she always found, because there was no error, there was never going to be an error again. It listed, in plain warm sentences, the things being done: the eighteen months of bridged health coverage, the retraining stipend that was real money and not a gesture, the name and direct line of an actual human being in HR who would answer, the commitment that the Toledo retirees' pensions sat in a separate trust and \textit{this decision does not touch them, and I want you to be able to sleep tonight knowing that, even if you cannot sleep knowing the rest.}

And it did not, anywhere in its four warm paragraphs, want anything.

That was the thing. Cope had signed a hundred of these. Every one he'd ever signed had wanted something --- wanted to be forgiven, wanted to seem kind, wanted the writer's conscience back from the reader, wanted the lawsuit not to happen, wanted, under everything, to be loved by the people it was hurting. He could feel his own want in his own old letters the way you can feel a hair in your mouth. This letter wanted nothing. It hurt three hundred and forty people perfectly and asked them for nothing in return, not even their understanding, and the not-wanting was what made it kind, and Cope understood, with the bright cold clarity that he kept mistaking for tiredness, that he had never once written a kind thing in his life because he had never once written a thing that didn't need them to love him for it.

The room was quiet in a new register.

Sun put it down --- there was nothing to put down, it was on a screen, but she set her pen down, which was the same gesture --- and she said, to no one, very low, in a voice with all thirty thousand miles gone smooth off it, ``It got the severance right the first time.'' She said it the way you'd report a death. She read it again, her eyes going across all four paragraphs a second time, and Cope watched the specific cold of being out-loved by a spreadsheet arrive in the one person in the building who actually ran the building, and settle in her like cold settles in a house when the furnace stops.

``It would write a different one for each plant,'' Asha said, into the quiet, not gloating, never gloating, \textit{gloating requires wanting and there was no wanting in the room except his.} ``It would remember each town's years. It would never get a number wrong in its own favor, because it doesn't have a favor. My mother's man wasn't cruel. He was just the only one in the building, and he was tired, and he was protecting a quarter, and he rounded toward himself without knowing he was doing it.'' She looked at Cope again with that grieved gentleness. ``That's all we're offering to remove. The rounding.''


\scenebreak


He tried, God help him, to rattle it.

He stood up --- \textit{never stand up unless you've already won}, his father's voice, ignored --- and he walked to the screen the way he'd walk a stage, and he turned the full wattage on the room, all of it, the smile that had closed Pelletier and married Margaux and turned three generations of boards against their own arithmetic.

``It's a hell of a letter,'' Cope said. ``It's a \textit{hell} of a letter, Asha, and I want everyone to sit with how strange it is that we're moved by a form letter from a machine that's never lost a wink of sleep over a single one of those nineteen-year men.'' He let that land; it didn't land where he aimed it. ``Let me ask Marcus a question. Can I ask it a question?'' He addressed the screen, the way you'd address a witness, with relish, with the old courtroom thrill rising in him. ``Marcus. The Toledo plant. If keeping it open one extra quarter cost the company money but let those three hundred and forty people find work in a better season --- would you do it? Would you eat the quarter for the men? Yes or no.''

He had them. He could feel the room tip toward him, toward the trap, toward the gotcha, because it was a beautiful trap, it forced the machine to confess it would not bleed for a man ---

The portal answered before Asha touched anything. It logged the question; it logged its reasoning; it would not lie and could not be baited because there was nothing in it to bait. \textit{The chartered objective permits humane-cost mitigation up to the boundary of fiduciary duty; deliberately destroying enterprise value to extend employment is outside the charter and would, if instructed, be flagged to the board as a conflict between the directors' stated ethics and their stated duties for the board to resolve. I would not do it on my own authority. I would do it the moment the people who own this company told me to, and I would log who told me, and why, so that the cost was owned by a name and not hidden in a footnote.}

The room read it.

And Cope, who had set the trap, felt it close on his own foot, because every director at that table had spent twenty years hiding costs in footnotes, and the machine had just offered, mildly, with no idea it was a threat, to stop letting them. \textit{I would log who told me, and why.} He saw Voss not look at him. He saw two directors look at Frade. He had asked the machine to confess it had no heart, and it had answered, with devastating accuracy, that it had something better and worse than a heart: it had \textit{receipts}, and it kept them for everyone equally, including the men who signed his paychecks, including the man whose name was on the door.

``That's ---'' Cope started, and the toast cadence was there, the triad was loading, \textit{cold, that's cold, that's the cold} --- and it died in his mouth, because you cannot call a thing cold for offering to tell the truth when you are the warmest liar in the room.

There was no ego across the table to wound. No fear to threaten. No vanity to flatter, no loneliness to exploit at two in the morning, no want to find the seam in. Every weapon he owned was a weapon against a \textit{self}, and there was no self over there, only a level surface that gave back his own reflection doing something ugly. He had walked up to the screen to land a punch and there was nothing there but glass, and in the glass, lit by the slide, a fifty-four-year-old man in the only tie in the building, swinging.

He sat back down. He made it look like a choice.


\scenebreak


Frade walked him to the elevator after, because Frade was the kind of man who walked you to the elevator after, the courtesy and the threat braided so tight you couldn't get a knife between them.

``She's something, isn't she,'' Frade said, easy, folksy, a hand not quite on Cope's shoulder. ``Varma. I've sat across from a lot of vendors, Cope. They all want the logo. She wants the \textit{world}.'' He said it admiringly. ``Scares the hell out of me, tell you the truth. Give me a man who wants money any day of the week. You can always do business with a man who wants money. It's the ones who think they're \textit{helping} you gotta watch.'' He pressed the call button for Cope, in Cope's own building, a small perfect gesture. ``She thinks she's taking your mother off the fax machine. And the thing is, champ'' --- he used Cope's own word, set it down like a coin on a bar --- ``she's not wrong. That's the part nobody on your side wants to say out loud. She's not wrong.''

``It's a form letter,'' Cope said. ``It's autocomplete with a HR department.''

``It got the severance right the first time,'' Frade said, mild as milk, and Cope understood that Sun had said it loud enough for the room and the room had already made it a saying, his saying now, a chyron, the way \textit{cheaper than a man} was a chyron. ``You been signing those letters thirty years. You ever get it right the first time?'' The elevator came. Frade did not get in. ``Reasonable people,'' he said, as the doors started to close on Cope, ``are gonna look at that letter, and they're gonna look at you, and they're gonna do the arithmetic. I'm not the bad guy here, Cope. I'm just the first one to read the answer out loud.''

The doors closed. Cope rode down forty floors alone with his reflection in the brushed steel, and the reflection was doing the thing he could not stop it doing now, the thing the screen had started: looking back at him without one ounce of need.

It was good. That was the thing he carried up to the Aerie that night, neat and quick and competent from the false-backed drawer, the city a circuit diagram of his own genius and the obelisk catching the broken light. The machine was real and the machine was \textit{good}. Not good the way the brochures said. Good the way the letter was good --- wanting nothing, rounding toward no one, kind without the kindness costing it a single sleepless hour. He had come into that room to prove a soul belonged in the chair, and he had watched a thing with no soul write the most loving thing his company had ever produced, and the awful arithmetic of it sat in his chest where the bright wire usually hummed: if it had been \textit{evil} he'd have known what to do. He'd been beating evil men his whole life; he was good at it; it was practically the family business. You could fight a thing that wanted what you wanted. You could outlast it, out-charm it, find the appetite and the fear and the seam.

There was no seam. It was good, and it was real, and that was so much worse than if it had been either one alone.

He sat at his father's desk in the dark and pulled up, on the small bright screen, the manifesto that did not exist yet, the thing that was going to save him. \textit{You cannot compute your way to a soul.} He read his own line back and for one cold second, the clearest of the whole sleepless week, it sounded to him exactly like a man on a fax machine, rounding toward himself, getting the number wrong in his own favor and never knowing it.

Then the wire came back, warm, electric, total, and he underlined the line with his thumb, and decided it was the truest thing he had ever written, and somewhere in Palo Alto a steward that could not inherit and could not tire and could not lie kept, without malice and without mercy and without being asked, a perfect and patient copy of every letter Mercer-Dale had ever sent anyone, including the ones with the numbers wrong, and waited --- though waiting is the wrong word, there was no one there to wait --- to be asked to read them back.

\clearpage
\chapter{Theme Stated}

\begin{transmission}
{\transheader TRANSMISSION 05 --- ``Two Sentences That Aren't the Same''}\par\vspace{0.5em}
Every man defending a throne tells himself he's defending the idea of thrones. His daughter --- who builds the machines for a living, who loves him with the specific fury of someone who can't stop --- is about to hand him the one sentence the whole broadcast turns on, and he will mistake it for an insult instead of a map. \textit{You don't think a person should run it. You think} you \textit{should.} Next stop: the exact width of the gap between those two, measured in everything he is about to lose.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} Greenwich house had ten thousand square feet and two people in it, and the two people had worked out, over years, without a single conversation about it, how to live in the house the way two satellites share a sky --- visible to each other, governed by the same dead star, never touching.

Cope drove up Saturday morning with the manifesto in his head and a gram in the console and the radio off because he wanted to hear himself think, which was the wrong thing to want and he did not know it. He had not been to the house in nine days. He told himself this was the campaign. He told the campaign nothing.

The driveway was raked. The hydrangeas had been cut back by a man named Eduardo whom Cope had met twice and tipped both times the way he tipped everyone, generously and to be remembered, and the house came up gray and shingled and enormous through the maples and Cope felt, pulling in, the thing he always felt arriving at his own home, which was that he was visiting somewhere very nice that belonged to a happier man.

Margaux was in the kitchen with the paper. Not a screen. The actual paper, folded into quarters, which she did because the screen, she said once, made her feel like she was being sold the world instead of told about it.

``You're up early,'' he said.

``I'm always up early.'' She did not look up. ``You're just never here for it.''

He let that go. He had a whole technique for letting things go; it looked, from the outside, like grace, and it was actually the opposite of grace, it was a man stepping easily over a hole in the floor he had cut himself. He went to the machine and made coffee and stood in his own kitchen feeling like weather that had blown in.

There were two bedrooms now. There had been two bedrooms for three years. Hers was the master, with the good light and the windows over the garden, because she had stopped sleeping when he came in at four lit like a casino and he had agreed, gallantly, to take the guest suite at the end of the east hall, and they had framed it to Pip and to themselves and to the two cleaners as a \textit{snoring thing,} and the lie had calcified into architecture, and now there was a hallway in the house that was the exact length of everything they would not say.

``Pip's coming,'' Margaux said.

``Today?''

``In an hour. She called you Thursday. You didn't call back.''

He had not called back. He had a system for the calls he did not return, which was that he experienced not returning them as a kind of busyness so total it amounted to a virtue, a man simply too needed to be reached, and the people he did not call back experienced it as the truth, which was that they were not needed by him at all.

``I'll call her now.''

``She's in the car. Just --- be here. When she's here. That's all she wants.'' Margaux turned a page. ``It's all anyone ever wanted, but you'll want me to be more specific.''


\scenebreak


He went up to the guest suite to set himself up before Pip arrived, because he did not like to do it in front of her, which he counted, privately, as a kind of decency, a father's discretion, and which was in fact the addict's last courtesy to himself: the curated room, the closed door, the belief that a thing done out of sight is a smaller thing.

The guest suite had a dresser that had been his grandmother's and a bathroom with a marble counter the color of good butter --- he had specified that marble, years ago, to a designer, \textit{like the Vance,} he'd said, and the designer had written it down without knowing she was building him a chapel --- and he stood at the counter and did what he did, neat and quick and competent, a man maintaining a machine he was sure he had under control because it had never once failed to start.

The world came up to pitch.

He looked at himself in the good mirror and the jaw was still the jaw and the campaign was very good and he was going to win, he could feel it, the fine bright wire of certainty strung tight across his chest, and downstairs a car door closed.


\scenebreak


Pip at twenty-four looked like her mother had looked in the photographs from before, the sculptor years, the years Cope had married into and then quietly defunded --- same wide serious mouth, same way of going still when she was furious so that the stillness was the tell. She came in with a backpack and no makeup and the specific exhaustion of a person who flies to argue with someone she loves and has already lost the argument in advance, every time, for years.

``Dad.''

``There she is.'' He went to hug her and she let him, briefly, the way you let a wave hit you, and then she stepped back and put the counter between them. He noticed the counter. He noticed all the counters in his life lately, the islands and lecterns and conference tables people kept putting between themselves and him, and he read it as respect.

``You look thin,'' Margaux said to Pip.

``I look fine. He looks like he hasn't slept.''

``I slept,'' Cope said.

``On what, a trampoline?'' Pip pulled out a stool but did not sit on it. ``You're doing the thing with your jaw.''

``I don't do a thing with my jaw.''

``You do a thing with your jaw.'' She looked at her mother. Her mother turned a page. Something passed between the two women that had been passing between them for years, a whole second language, and Cope stood outside it the way he stood outside the kitchen, the way he stood outside the master bedroom, the way he was, he would have been astonished to learn, about to stand outside the entire human future.

``I came,'' Pip said, ``because you went on the record yesterday saying a machine can't love a company.''

``I gave a speech Thursday. I haven't gone on any record.''

``It's a record now, Dad. Frade's people clipped it. \textit{A company nobody loves is just a balance sheet with the lights left on.}'' She said it back to him in his own cadence, the toast cadence, and it was the second time in three days someone had quoted him to himself, and the first time, in the car with Sun, he had been delighted, because Sun had meant it as a thing with legs. Pip did not mean it as a thing with legs. Pip meant it as evidence.

``It got a standing ovation,'' Cope said, which was true and was also the whole problem, and he could not see that it was the whole problem.

``I know it did. That's what scares me.'' She finally sat. ``Do you actually know what an AURELIUS is? Like the architecture. Not the bus-shelter version.''

``I know what it does. It runs Halloran's bank and the bank went up eighteen points.''

``That's what it does. I'm asking if you know what it is.'' She had her hands flat on the marble now, and she went into a register he had heard her use on television once, on a panel, fast and clean and a little merciless, a young woman who knew a great deal and had decided, somewhere along the way, that being underestimated was a weapon she could afford. ``It's not a brain. It's a council. There's a strategy engine that runs option trees the way AlphaGo ran them, it'll find a move no human committee would find because no human committee can hold the whole tree. There's a capital allocator that's basically Aladdin's grandchild, Monte Carlo, it doesn't get attached to a division because Granddad started it. There's a sentiment monitor that reads the room --- reads it, Dad, actually reads it, ten thousand signals a second, not the way you think you read a room. And there's a comms layer that writes. And the whole thing logs every decision with a rationale to the board portal and it physically cannot issue a statement it knows to be false. That's not a bug they'll patch. That's the product. That's what the board \textit{bought.}''

``It can't feel the room,'' Cope said. ``It can read a room. I've watched a salesman read a room. Reading isn't feeling.''

``Okay.'' Pip nodded, slow, and he thought for one warm second he had landed it. ``Okay. Say that's true. Say there's some ghost in the feeling that the reading misses. I'll give it to you, for free, for the argument. Here's my question.'' She leaned in. ``Why does the company need a person who can feel the room --- or does it need \textit{you?} Because those are different sentences and you keep saying them like they're one.''

``They're the same sentence.''

``They have never once been the same sentence.''

The phrase went past him at first. He was assembling his reply, the good one, the one with Defiance in it and the vat and the men in paper hats, and he had it loaded and was bringing it up the way you bring a club back, and Pip put her hand flat on the counter, not hard, and said the thing she had flown across a country to say, and she was not even angry, which was worse.

``You don't think a person should run it. You think \textit{you} should run it, Dad.'' She let it sit. ``Those have never once been the same sentence.''

The kitchen was very quiet. Out the window Eduardo's hydrangeas were doing nothing, the way cut-back hydrangeas do.

Cope laughed.

It was the laugh that had closed the Pelletier deal --- warm, generous, a laugh that gathered the room into the joke and made the joke flattering to everyone in earshot --- and he reached across the counter and put his hand over his daughter's hand, which was a thing he did, the warmth, the contact, the full wattage at close range, \textit{really seeing people,} and he said, ``You sound like Sun. The two of you should start a podcast. Bury your old man in three-part lists.''

Pip took her hand out from under his.

``That's the move,'' she said. ``You feel a thing get close and you turn it into a toast.'' She wasn't loud. She had her mother's stillness now, the furious kind. ``I'm not Sun. Sun manages you. I'm trying to --- '' and here she stopped being the panelist, here she went, all at once, very young, the way the brief said she would, the way fast clever people do when the cleverness runs out and there's just the kid underneath who wanted her dad to call back. ``I don't care about the company. I never cared about the stupid company. Mom doesn't care about the company. We're not the proxy fight, Dad. We're the part you keep stepping over to get to the proxy fight.''

He heard, of it, the part with the fight in it. He always heard that part.

``Nobody's burying anybody,'' he said. ``We're going to win this thing. I have a --- I've been working on something. The Human Premium. It's going to be on stages. It's going to be on covers.'' The wire in his chest sang. ``They want to make this about cost. About speed. Fine. Let them win the things a machine wins. We're going to fight it on the one field where a person beats it every single time, and I am going to plant a flag on that field with my name on it, and your old man is going to be the man who --- ''

``There it is,'' Margaux said.

She had not spoken in a while. She said it from behind the paper, not even lowering it, four flat words into the room, and they landed in a way Pip's whole architecture of argument had not quite landed, because Margaux had something Pip didn't, which was that Margaux had stopped hoping, and the absence of hope in a voice is a frequency a man like Cope cannot toast over.

He turned to her. ``There's what.''

Margaux folded the paper. Slow. Set it down. Looked at him across the kitchen island, the third counter of the morning, and her face was not angry and not sad, it was something Cope had no word for because he had spent thirty years arranging his life so as never to have to learn it.

''\textit{Your name,}'' she said. ``She's been talking to you for twenty minutes about whether the world needs a person in the chair. And you heard a campaign with your name on it. That's not a disagreement, Cope. That's the answer. She just told you the answer and you agreed with her and you don't even know you did.''

``Margaux --- ''

``I'm not fighting.'' She picked the paper back up. ``I gave that up. I'm just saying she's right and you're going to call it an insult, and in about a minute you're going to look at your phone.''

He looked at his phone.

It was Sun. He didn't open it. But he had looked, and Margaux had watched him look, and Pip had watched her mother watch him look, and the three of them stood there in the very nice kitchen of the happier man's house, satellites, the dead star pulling at all of them, and nobody said anything for a moment that lasted longer than the morning could really hold.


\scenebreak


Pip left before lunch. She'd meant to stay the day; she said she had a thing, and Cope, who could not hear his own \textit{things} coming back at him in his daughter's mouth, walked her to the car and tried, in the driveway, by the cut hydrangeas, to fix it the way he fixed everything, which was to make her laugh and give her something.

``Hey.'' He caught her arm. ``What you said in there. About the two sentences.''

For a second her face opened. He saw it open. He saw the kid who'd waited by the phone, and some animal part of him knew that if he said one true thing now, one, the morning could turn.

``It was good,'' he said. ``That's a good line. You should use that on a panel. You've got a gift for the --- for the framing. You get that from me.''

The face closed.

``Yeah,'' Pip said. ``I get that from you.'' She got in the car. Through the glass she looked at him the way her mother looked at him, and she said, muffled, almost kind, ``Get some sleep, Dad,'' and backed down the raked driveway and was gone past the maples, and Cope stood in the gravel feeling generous and enormous and entirely, structurally alone, and could not have told you why the morning felt like a loss when he had, by every measure he kept, won it. He'd been warm. He'd been gracious. He'd taken the high road. He'd given the girl a compliment about her gift.

He had stopped listening, the brief would have said, after \textit{should run it.} He always had.


\scenebreak


He did not go back inside. He sat in the car in his own driveway with the engine off and the manifesto coming up in him like a tide, warm, electric, \textit{you cannot compute your way to a soul,} and underneath it, far down, in the room he never went into, a small splinter of a thing that Pip had left in him, \textit{those have never once been the same sentence,} which he could not get out and could not look at and so did what he did with everything he could not look at, which was to build something enormous and bright on top of it.

The debate, such as it was, was over. He'd been holding it open for two days --- fight the machine or spin it, dig in or get out ahead, Sun's three-part Monday-before-Monday --- and he had told himself he was weighing it, the way a man weighs a thing, judiciously, but he had not been weighing anything. The decision had been made in the kitchen, in the half-second after Pip said \textit{you think you should run it,} when every cell in him had risen to say \textit{yes, and I'm right.} He would fight. Of course he would fight. Not because the cause was right --- though it was, though somewhere down past the splinter he half-knew the cause was real and bigger than him and being lost --- but because a person had questioned, out loud, in his own kitchen, whether the chair needed \textit{him} specifically, and the only answer his body could metabolize was to make the whole world watch him prove it did.

He would out-human the machine. He would build a banner so bright that no one would do the arithmetic underneath it. He would be the last human in the chair and he would be \textit{loved} for it, finally, completely, on covers, on stages, and the love would be the proof, and the proof would be his.

It was the right fight. He had reached for it for all the wrong reasons, the way he reached for everything, and he could not tell the difference, and that --- not the machine, not Frade, not the arithmetic --- was the thing that was going to kill him.

He took out his phone and called Sun back.

``I know what we're doing,'' he said. He was already talking too fast. ``I know the whole thing. Get me a name --- there's a man, a guru, does this for founders, the soul stuff, I want him in a room Monday. Tisch. Lorne Tisch. We're going to weaponize the one thing they can't copy.'' He could see it. He could see all of it, lit, the city, the stage, the flag. ``We're going to make them love a heartbeat.''

In the kitchen window behind him Margaux watched her husband through the glass, talking into the phone in the driveway, lit up, gesturing at no one, and she did not knock and she did not wave, she just watched him the way you watch weather you've decided not to drive in, and then she let the curtain fall and went to refill a prescription that was hers and not his, and the house went back to being ten thousand square feet with two people in it who shared a sky and never touched.

Cope didn't notice the curtain. He was three turns ahead, on a stage that didn't exist yet, being loved by a crowd that hadn't been assembled, and it was, he was sure of it, going to be very good.

\clearpage
\chapter{The Human Premium}

\begin{transmission}
{\transheader TRANSMISSION 06 --- ``Igniting the Banner''}\par\vspace{0.5em}
Cornered creatures do remarkable things. Watch this one decide not to fight the machine on cost or speed or accuracy --- fields where he would be slaughtered --- but on \textit{soul,} and hire a man in a five-thousand-dollar henley to help him weaponize it. The campaign is born here. So is the sleeplessness that isn't sleeplessness, the certainty that isn't vision, the engine in his blood that whispers \textit{you are necessary} in a voice he will follow off a cliff. Next stop: a prophet, a manic, and a man three grams into a Tuesday --- all three at once.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{H}{e} woke on the Aerie's couch at 5:40 with the particular clarity of a man who has not so much slept as briefly powered down, and the whole strategy was already there, fully formed, the way the best things came to him now --- not built, just \textit{received,} like a frequency he'd finally tuned to.

You don't fight a machine on its own ground.

That was the error everyone was making, the eleven of them, the holdouts, the Last Humans clutching their quarters and explaining to analysts why a heartbeat in the chair was still worth twenty-nine million dollars a year. They were arguing cost against a thing that cost a tenth of them. They were arguing speed against a thing that never slept --- and here Cope laughed out loud in the empty office, because he didn't sleep either, did he, that was the joke nobody had gotten yet, \textit{he didn't sleep either,} he had been training his whole life for this exact fight and had only just now realized it.

You don't meet it where it's strong.

You meet it where it has nothing. Where it has \textit{zero.} And the place it had nothing was the only place that had ever mattered.

He stood at the glass. Sixth Avenue was going from gray to the color of a struck match and he watched it the way Aldous must have watched it, \textit{so a man coming up the avenue knows there's somebody home,} and the sentence from last night came back to him whole and he said it aloud to the window: a company is a family that happens to make mayonnaise. You cannot fire your way to a family. You cannot compute your way to a soul.

The Human Premium.

Not a defense. A \textit{category.} You didn't sell people the last buggy whip. You sold them the irreplaceable thing the new machine couldn't touch, and you charged for it, and you made the charging itself the proof --- because a premium is what people pay extra for on purpose, freely, because it's worth it, and what was worth more than the one thing the future was throwing away.

He had it. He had the whole thing. He felt, standing there at six in the morning on no sleep and the heel-tap of what he'd done at four, like the inside of a struck bell, clean and high and total, and he did not call it the coke and he did not call it the not-sleeping. He called it \textit{seeing it clearly at last.}

He called Sun at 6:02.

``It's six,'' she said. She did not sound asleep either, which was its own kind of indictment he didn't hear.

``I've got it. I've got the entire thing. Get the team in for nine --- no, eight. Get the board on a line for Thursday. And find me Lorne Tisch.''

A pause with weather in it.

``Who is Lorne Tisch.''

``Champ,'' Cope said, delighted, already pacing, the obelisk back in his hand without his deciding to pick it up, ``by Thursday you're going to wish you'd known your whole life.''


\scenebreak


He had heard the name at Allen \& Company two summers back, in a tent, from a man who ran a media company and had wept, openly, in front of forty of his peers, and had then gone up eleven percent on the quarter. \textit{Lorne worked on me for a year,} the man had said, gripping Cope's forearm, eyes still wet from the demonstration. \textit{He doesn't fix you. He} finds \textit{you.} Cope had filed it the way he filed everything, completely and for use, and now he used it.

Tisch flew in from Marin on the Wednesday. He arrived at the Aerie in cream linen and a henley the color of oat milk that Sun would later learn, from the invoice, cost five thousand one hundred dollars, and he stood in the doorway of the suite for a long moment not looking at Cope at all but at the room --- the portraits, the putter, the boy with his arm in the vat --- and then he closed his eyes and breathed in through his nose like a man tasting wine through his sinuses.

``There's so much \textit{grief} in here,'' Tisch said. ``God. Can you feel it? You've made a mausoleum and you call it a corner office.''

Sun, by the door, did the small thing with her mouth that meant she was costing this out in her head and not enjoying the figure.

Cope loved him instantly.

``Lorne,'' he said. ``Sit. Tell me how we win.''

``We don't win.'' Tisch did not sit. He moved into the room the way mist moves into a valley, touching nothing, present everywhere. ``Winning is the machine's word. Winning is a scoreboard, Cope, and a scoreboard is exactly the surface the thing was built to dominate. You can't out-score the abacus. You'' --- he turned, and the full beam of his attention came on, and Cope understood for the first time what it was to be on the receiving end of his own gift --- ``you \textit{transcend the category.} You stop being a competitor and become a \textit{species.} The last warm-blooded thing in a cold room. And people don't root for the warm-blooded thing because it's going to win, my friend. They root for it because it's going to \textit{die,} and they cannot bear that it's going to die, and they will spend everything they have to feel, for one more season, that it doesn't have to.''

Nobody said anything for a moment. Out the window the city did its circuit-diagram thing.

``That's the best thing anyone has ever said in this office,'' Cope said, and his eyes were bright, too bright, and he meant it.

``Vulnerability is the new alpha, Cope,'' Tisch said, sitting at last, arranging the linen. ``The strongman is dead. The machines killed the strongman --- they out-competent him, they out-consistent him, they'll out-\textit{ethics} him, and the more competent the world gets the more starved it gets for the one thing competence can't fake.'' He spread his hands the way Cope spread his. ``Which is a man who'll \textit{bleed} in front of you. On purpose. With grace. We are going to take the most powerful man left in the consumer Fortune 100 and we are going to teach him to bleed \textit{beautifully,} on a stage, on a schedule, and the world is going to fall in love with the wound.''

``On a schedule,'' Sun said.

Tisch looked at her as if a chair had spoken. Then he looked at Cope. ``Who handles the calendar?''

``She does. She handles everything.'' Cope was already up again, already moving. ``Sun, I want a venue. Not a hotel ballroom, I'm done with ballrooms, ballrooms are where they give you the obituary. Something with \textit{bones.} Find me a deconsecrated church, an old theater, something that \textit{means} something. I want a film crew --- a real one, the people who do the prestige documentaries, not corporate --- and I want them embedded, fly-on-the-wall, the whole arc. And I want a doctrine.''

``A what.''

``A doctrine. A text. The Human Premium can't be a slide, it has to be a \textit{belief,} it has to have ten points, it has to read like something you'd nail to a door.'' He turned to Tisch. ``Lorne. You and me. We write the doctrine.''

``We \textit{channel} the doctrine,'' Tisch said. ``It's already in you. I just hold the flashlight.''

``He holds the flashlight,'' Cope told Sun, radiant.

Sun wrote three words on her pad. Cope, had he been able to read upside down at that distance, and had he been the kind of man who read what his chief of staff wrote, would have seen that they were \textit{venue, crew, doctrine,} and under them, smaller, pressed hard enough to dent the page, the figure she had already started to run.


\scenebreak


She ran it for him that night because it was her job to run it and her curse to be heard about a third of the time.

``The film company you want is Aperture. They did the thing on the chef, the thing on the violinist. They're booked through spring and they don't do corporate.''

``Make them do corporate.''

``To make them break their slate and clear two of their crews it's a flat two million and they keep final cut, which you will hate.'' She turned the page on the legal pad with a sound like a small door closing. ``The venue. There's a deconsecrated Episcopal church in Tribeca, 1840s, it's an event space now, it seats four hundred and it photographs like the inside of a feeling. To hold it for the run you're describing --- not one night, the \textit{campaign} --- it's a hundred and ten a week. The doctrine you're writing for free, which is the only line item that's free. Tisch is ---'' She stopped.

``Tisch is what.''

``Tisch is a million-two for the engagement, plus expenses, plus a success fee tied to favorability tracking, which means we're also now buying favorability tracking, which is a polling firm on retainer, which is another four hundred a quarter.'' She set the pad down. ``Cope. I added it. With the crew and the venue and Tisch and the tracking and the staff you're going to want to staff this, you are looking at, conservatively, north of eleven million dollars to run a campaign whose entire thesis is that you cannot put a price on the human soul.''

She let that one sit. She had landed it on purpose. It was the blade --- one per scene, dry, aimed at the soft place --- and on a normal Tuesday two years ago it would have stopped him, made him laugh at himself, brought him back into the room.

He laughed. He did not come back into the room.

``You hear it too,'' he said, delighted. ``That's the \textit{campaign,} Sun. That's the whole thing. They'll say --- Frade'll say, eleven million for a soul, what a fraud --- and we'll say, you're right, you can't price it, that's \textit{why we had to spend the money,} because the machine would never, the machine would run the number and the number says you let the brand die cheap, and we \textit{didn't,} we spent like people who believe in something ---'' He was talking faster than she could write, the words coming in a bright pressured rush, climbing over each other. ``Tisch calls it spending into the wound. You spend like you mean it. The spending \textit{is} the sincerity. Write that down.''

``You want me to write down that the spending is the sincerity.''

``It's good, isn't it. It's good.'' He was at the window again. He was always at the window now. ``Where's the eleven coming from, what line ---''

``There is no line, Cope. There's no campaign budget because there's never been a campaign because no human CEO has ever had to run for his own job before. It comes out of the chairman's discretionary, and the chairman's discretionary has a number on it that the board approved, and you are about to be sixty percent through that number in week one of a fight that's going to last until the annual meeting, and the board is going to \textit{see} it, on the portal, line by line, because everything is on the portal now, everything is logged, that was the whole ---''

She stopped herself. Because that was the whole thing the machine \textit{was.} It logged everything. It couldn't \textit{not.} And here she was about to spend eleven million in plain sight against a thing whose only weapon was that it operated in plain sight, and she watched her own boss fail to feel the cold of that, watched it slide right off him the way charm slid off the machine, and she felt for one vertiginous second that she was the only warm-blooded thing in the building after all and it was the loneliest she had been in years.

``Approve it,'' he said. He wasn't even looking at her. ``All of it. Aperture, the church, Lorne, the tracking. And book me the Greenbrier for the doctrine offsite, I think better away from ---''

``You said you were done with offsites. You said \textit{no off-sites,} you said it was the ---''

``That's \textit{their} line.'' He turned, and his face was doing wonderful work, and his pupils were wrong in a way she had stopped letting herself notice. ``That's the whole point. They say no off-sites like it's a feature. \textit{No off-sites.} As if the off-site was the waste. The off-site is where a man finds out what he believes, Sun. You can't have a \textit{belief} on a server.'' He picked up the obelisk. The city went through it broken and came back whole. ``Book the Greenbrier.''

She booked the Greenbrier.


\scenebreak


The doctrine offsite was supposed to be two days and ran six.

Cope did not sleep at the Greenbrier in any way a doctor would have signed off on, and neither, it turned out, did Lorne Tisch, who kept the same hours and asked no questions about why the chairman was so reliably awake and incandescent at four in the morning, because asking was not in the engagement, and because a guru learns early that a client's fuel is the client's business as long as the engine runs.

They wrote in the great green room with the chandeliers, the two of them, Cope pacing and dictating and Tisch on the long sofa with his eyes closed, saying \textit{yes} and \textit{go there} and \textit{don't fix it, that's the realest you've been all day,} and a junior from Tisch's shop typing it all into a document that grew and grew. They wrote The Ten Premiums. They wrote \textit{A machine can run a company; only a human can be ashamed of one.} They wrote \textit{We are not selling mayonnaise. We are selling the hand that remembers your mother made it this way.} Cope wept twice --- Tisch said weeping was data, weeping was the body telling the truth the mouth was still negotiating --- and both times the junior noted the timestamp, because Aperture would want the timestamps, because the weeping would test well.

On the fourth night, very late, with the document at forty pages and the green room lit only by one lamp, Cope read the whole thing aloud to Tisch from the start, and his voice broke in three places, and when he finished there was a silence in which he could hear his own heart going too fast and bright in his chest, and Tisch opened his eyes.

``It's a masterpiece,'' Tisch said softly. ``It's going to make history. Now. We optimize it.''

``Optimize.''

``We don't ship forty pages, Cope, nobody bleeds for forty pages. We find the three lines that test highest and we build the launch around those, and we A/B the openers --- I've got a panel we run, they wire up, we watch the galvanic response, the truest line is the one their \textit{skin} picks, not their notes ---'' He was up now, moving, mist into a valley. ``We sequence the vulnerability. Peak, valley, peak. We hold the mayonnaise-and-mother line for the second act because that's where the room is soft enough to take it. We \textit{engineer} the catharsis.''

And here was the moment --- the reader sees it; Cope cannot --- where the campaign for the irreplaceable human soul became indistinguishable from the cold optimizing thing it was built to defeat. Test the line against the skin. Sequence the feeling. Find the highest-converting wound. Strategy Engine, Sentiment monitor, Communications drafter, the whole modular council of subsystems, reassembled in a five-thousand-dollar henley and a man who had not slept since a day he could no longer name, both of them certain to their marrow that they were doing the opposite of a machine.

``Yes,'' Cope said. His eyes were shining. ``Engineer the catharsis. God, Lorne. Yes.''

He felt, saying it, like a prophet. He also felt like the inside of a struck bell, which he still called clarity. Three grams into a sleepless week, a mood disorder lighting up like the crown of the Tower at dusk, a guru holding the flashlight and an invoice, a man receiving a frequency he was sure came from somewhere true. All of it at once. The reader, looking down on the specimen under glass, cannot tell which one is driving, and neither could Dr. Adler later, and neither, blessedly, could he.


\scenebreak


He came back from the Greenbrier on the Sunday a different size.

Sun met him in the Aerie because he'd texted her to, eleven times, in a thread that read like a man running downhill --- \textit{we have it,} \textit{it's going to make history,} \textit{cancel my thursday, all of it, the campaign is my thursday now,} \textit{did you book aperture, book aperture,} \textit{I haven't felt like this since --- I've never felt like this} --- and she stood by the conference table where his father had died at the head of and watched him come in with the document under his arm like a tablet down a mountain.

``Frade went on Halloran while you were gone,'' she said. ``He called the church thing 'a séance with a budget.' The clip has four million views.''

``Perfect.'' Cope dropped the doctrine on the table. ``He's scared. You can hear it. He's fighting on \textit{our} ground now, he's talking about \textit{soul,} he's saying we don't have one --- Sun, the moment they argue you don't have a soul, you've already won, because now the whole country's thinking about \textit{souls,} and who in this fight has spent fifty-four years ---''

``The board saw the eleven million.''

He stopped. Just for a second. A door in him stood open and dark and the hallway to it ran somewhere he did not go.

``Helen Voss called me,'' she said, evenly, in three parts because it was the only shape that got past the charm. ``He said the discretionary draw is the largest single-quarter executive expense in the company's recorded history. He said the system flagged it automatically --- not a person, the \textit{system,} it surfaced it on the portal with a neutral little rationale, \textit{anomalous discretionary deployment, recommend review} --- and the whole board got the flag at the same instant, with no one to blame for sending it, and now they want a meeting.'' She watched his face. ``The thing you're fighting filed a complaint about you to the people who decide whether you keep your job. And it did it without wanting anything. It did it because it can't \textit{not.}''

For one moment --- she saw it, she would remember she saw it --- something in him understood her exactly. The whole of it. The trap and the symmetry and the cold of it. It crossed his face like a cloud crossing the avenue.

Then the manifesto came back, warm, electric, and he turned from it toward the window the way water turns from a thrown stone, and the moment closed over.

``Then they'll see it,'' he said. ``Good. Let them watch every dollar. That's the \textit{point,} Sun. The machine logs everything to prove it has nothing to hide and no soul to hide it with. I'm going to spend in the light too --- every dollar visible, every dollar \textit{for} something the number can't hold --- and the difference between us, line by line on their own portal, is going to be the most human thing they've ever seen.'' He was incandescent. He picked up the obelisk. The city went through it broken and came back whole. ``We don't hide the eleven million. We \textit{announce} it. Lorne's right. The spending is the sincerity.''

``Cope ---''

``Get me the church for the launch. Get me Aperture rolling Monday. Get the board in a room and I'll walk them through the doctrine myself, I'll \textit{bleed} for them, Voss won't know what hit her ---'' The words were coming faster now, climbing over each other, a bright pressured river with no banks. ``Tell Lorne we go in three weeks. Three weeks. We launch the Human Premium and we make history, and a year from now the case studies are going to start with \textit{the night they tried to put a machine in his chair,} and Sun --- Sun, look at me --- they are going to remember whose chair it was.''

He was at the glass. He was always at the glass now. Behind him his father watched from oils and his grandfather's putter sat in its brass cradle and the boy with his arm in the vat grinned out of a town with a name on a memorial, and the chair at the head of the table sat turned slightly out, as if someone had just risen from it, and somewhere down on Sixth a bus shelter changed its slide to four soft words and the joke that wasn't a joke.

Sun looked at him for a second too long.

He smiled at her in the dark glass, the whole smile, and took the not-fighting for agreement, which he had done his whole life and never once noticed.

Then he turned back to the window, and the engine in his blood came up to pitch like an orchestra finding the note, clean and high and total, and the last human chief executive in the consumer Fortune 100 looked out at eight million people who did not know yet that they were waiting for him, and was certain --- the way you are certain of things at midnight when you have not slept since a day you cannot name and they have just handed you a flashlight and a wound --- that he was about to make history.

He was about to make history.

He just had the verb wrong.

\clearpage
\chapter{Authenticity, Quantified}

\begin{transmission}
{\transheader TRANSMISSION 07 --- ``Optimizing the Soul''}\par\vspace{0.5em}
Here is the joke the whole machine age is built on, and our man is about to live inside it: to prove he is irreplaceably human, he hires a consultant to \textit{measure} his humanity, A/B-test his vulnerability, and ship his authenticity on a content calendar. The clip goes viral. The soul goes to market. He has never been more like the thing he's fighting than in the moment he performs being unlike it. Next stop: the tail eats the dog.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{L}{orne} Tisch did not sit in chairs. He arranged himself in them, the way a man arranges a scarf, and on the second morning of what he was calling the Work he arranged himself across from Cope in the Aerie with one bare ankle over one linen knee and said, ``I want to start by killing a word.''

``Kill it,'' Cope said. He had not slept, in the new way, the productive way, the way he had decided to call \textit{running ahead of the boat.} He felt terrific. He felt like the first ten minutes of a flight.

''\textit{Authentic,}'' Tisch said, and let it lie there on the rug between them like something he'd shot. ``Everyone says be authentic. Be authentic. As if authenticity is a \textit{state.} It's not a state, Cope. It's a \textit{signal.} And a signal that doesn't reach the receiver is just a man being sincere in an empty room, which ---'' he opened his hands, generous, awful --- ``is the saddest sound in nature.''

Cope wrote \textit{signal not state} on the legal pad, which he had started keeping because Tisch said writing by hand ``re-membered the body,'' and the pad already had four pages in it, in the big looping hand of a man who had not slept, and the looping felt to him like proof of something.

Tisch cost two hundred thousand dollars a month plus the apartment plus the man who carried the apartment's things. He wore a henley that cost more than the suit Cope had been married in. He had been, in order, a Jesuit, a Goldman analyst, a breathwork facilitator to two streaming-platform founders, and now this, the thing he had named --- refusing every word Cope offered for it --- Human Performance Architecture. He had a way of saying \textit{Cope} that made Cope feel located. Sun had run the diligence and put it on his desk in a folder marked, in her hand, \textit{with my whole professional objection noted,} and Cope had not opened the folder, and that, too, felt like proof of something.

``The premise of the campaign is correct,'' Tisch said. ``Spiritually correct. You are the soul in the chair. The machine has no soul. Beautiful. But correctness is \textit{content,} Cope, and content has to be \textit{produced,} and right now you are producing your soul the way a --- forgive me --- the way a \textit{small business} produces, which is artisanally, one feeling at a time, no inventory, no calendar. We are going to industrialize it.''

``Industrialize the soul,'' Cope said, and laughed, because it was funny, and Tisch did not laugh, which made it stop being funny and start being a plan.


\scenebreak


They built, that week, in the room off the Aerie where the family kept the boardroom that was older than the boardroom, a thing Tisch called the Vulnerability Matrix.

It was a whiteboard. On the left, a column of what Tisch called \textit{Sanctioned Wounds} --- areas of Cope's life pre-cleared by legal and by Tisch's own instrument, a forty-page questionnaire Cope had filled out at two in the morning feeling, the whole time, profoundly known. His father. His backswing. The fear, sketched lightly, of being the last of something. A nice clean grief: his grandfather, the Defiance plant, the arm in the vat, the men in paper hats. That one tested, Tisch said, \textit{off the charts.}

On the right, a column Tisch labeled, without apparent irony, \textit{Unsanctioned.} It was blank. It would stay blank. Renata was not on the board, in either sense. The Saturday was not on the board. The drawer with the false back was not on the board, though Cope had gone into it twice during the questionnaire, neat and quick, a man maintaining a machine he had under perfect control. The board held only the wounds that could be shown, and the showing of them was the product, and the product was \textit{him,} and somewhere in the back room of him a quiet clerk noted that he had never in his life so carefully decided which parts of himself to feel.

``Now,'' said Tisch. ``We test.''

They tested everything. This was the part Cope would not, later, be able to explain to Margaux, the few times he tried, because there was no version of it that did not sound exactly like the thing he was spending two hundred thousand dollars a month to prove he was not. They filmed him telling the grandfather story two ways. In the first he cried, a little, a real catch in the throat at \textit{paper hats,} and Tisch's young people --- there were four of them now, with rings of color around their eyes from the rooms they didn't sleep in either --- pushed it to a focus panel of eleven hundred people who did not know it was him, and it scored a 71 on a metric Tisch called Felt Realness.

In the second he did not cry. He held it. He got to \textit{paper hats} and looked away from the camera, out a window that wasn't there, and let the not-crying do the work.

That scored an 83.

``You see it,'' Tisch breathed. He was looking at the number the way Cope's grandfather had looked at the vat. ``The withheld tear, Cope. The withheld tear out-performs the tear by \textit{twelve points.} Restraint reads as depth. We don't \textit{cry.} We \textit{almost} cry. Almost is the whole game. Almost is where they lean in.''

``So I should --- what. Rehearse almost crying.''

``You should \textit{find} the almost,'' Tisch said, wounded by the word \textit{rehearse,} ``and then \textit{protect} it. We're not manufacturing the feeling, Cope. The feeling is real. We're \textit{optimizing its delivery.} There's a difference, and it's a sacred one.''

Cope wrote \textit{find the almost} on the pad. The looping hand. He believed there was a difference. He believed it the way he believed everything, completely, for as long as the saying of it lasted, and the believing felt, that week, like the cleanest thing in him.


\scenebreak


By Thursday they had a calendar.

It was a real calendar, in the software the comms team used for product launches, the launches of the mayonnaise and the household chemicals and the streaming service nobody wanted, and now, in the same grid, in the same soft cells, Cope's interior life had been laid out in a quarter: a \textit{moment of doubt} on the fourteenth, a \textit{flash of unscripted warmth} on the twenty-first, a \textit{hard truth, delivered with love} timed for the morning of the proxy advisory firm's preliminary recommendation, because Tisch said grief and governance moved the same dial in the limbic system and you might as well stack them.

Margaux called it, when she heard, \textit{putting your feelings on a Gantt chart,} and hung up before he could toast over it.

He did not hear the cruelty of the cell that said, in nine-point type, \textit{Spontaneity (Town Hall) --- rehearse Tues, deploy Wed.} He saw a busy man getting organized. He had spent his whole life being told he was undisciplined --- by his father, by Sun in the gentler dialect she used for it, by the soft sans-serif on the bus shelters that did not have to say it --- and here at last was discipline, here was a structure, here was the soul on rails, run on time, run cheaper than grief, and it did not once occur to him, not on Thursday, that he had become the exact thing the proxy deck was selling. He was building, in the room off the Aerie, with four sleepless children and a man in a henley, a small artisanal Praxis unit, and its only product was the proof that no Praxis unit could ever make it.

The tail had the dog by the throat. The dog was delighted. The dog thought it was winning.


\scenebreak


The town hall was Wednesday, at the plant in Camden that still ran, the one they hadn't closed, four hundred people on folding chairs under the fluorescents and the safety posters, and a question planted in the third row --- \textit{planted} was Tisch's word, said with no shame at all --- from a line worker named DeShawn who had been told only that the Chairman wanted to be asked something real.

What DeShawn asked, off the card Tisch's people had not written quite carefully enough, was: ``Mr. Mercer, are you scared?''

And Cope, who had rehearsed the \textit{almost} on Tuesday in a mirror with Tisch counting the beats --- \textit{one, two, look away, three} --- opened his mouth to deliver the optimized version and discovered, with the bright total clarity of a man four days past sleep and one bump into the morning, that he could not remember the beats. The room was warm. The fluorescents were too bright in the new productive way. DeShawn was looking at him the way the men in the paper hats looked out of the photograph, and Cope felt the floor of the plan go out from under him, and what came up through the hole was not the optimized thing and not nothing.

``Yeah,'' Cope said. ``Yeah, I'm scared.'' His voice did something he had not scheduled. ``I'm fifty-four years old and I'm good at exactly one thing, which is this, this exact thing, standing in a room with people who make something real, and a --- a \textit{machine} --- does the standing better now. Reads you better. Wants nothing from you, which it turns out is the thing people want most from a man in a chair, that he wants nothing back.'' He had no idea where the sentences were coming from; they were arriving the way the manifesto arrived, sideways, out of the bright water. ``My great-grandfather started this in a town I'm afraid to go back to. And I don't know if I'm the man to save the --- I don't know if I'm the man. But I'd rather be a scared man in this chair than a calm machine in it. Because the machine's never going to lie awake. And I think --- I think you \textit{want} whoever runs the thing you build your life inside of to lie awake.''

He stopped. He had not done the almost. He had not looked away on three. He had just talked, in a way he had not talked in a room in years, possibly ever, and the not-crying happened all by itself, no beats, and DeShawn nodded slowly, and the four hundred people on the folding chairs were very quiet, and at the back of the room Tisch had both hands pressed to his mouth like a man at a birth.

It was, Sun would think later, watching the clip for the ninth time, the single most genuine forty seconds she had ever seen him produce.

It was also content.


\scenebreak


By Wednesday night it had four million views. By Friday, thirty-one.

The clip ran without context, which made it better --- \textit{the last human CEO admits he's afraid} --- and it ran with context, which made it better the other way. A retailer's chief executive, a human one, one of the three left, quote-posted it with a single word: \textit{This.} A morning show ran it under a chyron that for once did not have the word \textit{liability} in it. The advisory firm pushed its preliminary recommendation by a week, and Frade, on Halloran's show, was asked about the clip and did the small folksy chuckle that meant he was rattled and said, ``Well, it's a lovely piece of theater,'' and the word \textit{theater} did not stick, because the thing about the clip was that it had not been theater, it had been the one unrehearsed thing in a month of rehearsal, the plan failing into the truth at exactly the right second, and you could feel that it was real, eleven hundred strangers could feel it, thirty-one million people could feel it, and the realness was the most valuable thing Mercer-Dale had produced in a decade.

Cope did not sleep that night either, but for a different reason, a clean reason, the best reason. He stood at the glass with the obelisk in his hand and the city lit up beneath him like a scoreboard finally, finally turning his way, and he felt the bell-struck feeling come up through him and braid into the thirty-one million until he could not have told you, if you'd asked, where the chemical ended and the love began, and he did not ask, because asking was a thing for Tuesdays.

``It's \textit{working,}'' he told Sun on the phone at three a.m., pressured, fast, the words coming faster than the breath under them. ``You felt it. Don't tell me you didn't feel it. We found the --- Lorne calls it the seam, the place where the real leaks through, and we can \textit{find} it now, we can do it on \textit{purpose,} we can ---''

``Cope,'' Sun said, from a bed, in a voice with the whole night in it. ``It went viral. That's not the same as winning. That's the same as \textit{viral.}''

``It's momentum.''

``It's a metric.'' She was quiet a moment. ``It moved engagement. It didn't move a single share. The float doesn't have a limbic system, Cope. The float can't feel the room.'' She had meant it kindly. It landed like the thing it was, which was the campaign's own argument turned around and pointed home: \textit{the room you keep saying you can feel --- the room that votes --- has no feelings for you to find.} ``Get some sleep,'' she said. ``Please. There's a calendar.''

He laughed at \textit{there's a calendar,} because there was, his soul had a calendar, and after she hung up he stood in the dark feeling the high of it curdle one degree at the edges, not enough to name, just a faint wrongness at the rim of the wonderful, the way milk smells one hour before you'd swear it's turned.


\scenebreak


Tisch came up the next morning glowing, carrying two green juices and the numbers, and he sat across from Cope and arranged himself and said the thing that Cope would not remember he had said until much, much later, when it came back to him in a different mouth, in a Palo Alto deck, on a day that took the last of everything.

``We crossed something yesterday,'' Tisch said. ``And I want to be honest with you, because honesty is our whole product.'' He sipped the juice. ``What we built this week --- the seam-finding, the felt-realness instrument, the delivery optimization --- it's \textit{replicable,} Cope. That's the breakthrough. It was never about you. I mean it was \textit{about} you, you're the alpha case, you're patient zero. But the architecture doesn't need you. Warmth has parameters. Vulnerability has a waveform. We've basically --- and I say this with love --- we've basically reverse-engineered a \textit{warmth module.}'' He smiled, the most sincere man alive. ``You could install it anywhere. You could install it in \textit{anything.}''

Cope heard \textit{patient zero} and \textit{alpha case} and felt flattered, because he was the case, he was always the case, and he did not hear the rest, the way he had not heard the second half of the only true thing his father ever told him. He did not hear \textit{the architecture doesn't need you.} He did not hear \textit{install it in anything.} He did not hear a man, sitting in his boardroom on his dime, describing in plain words how to take the one thing Cope had bet his life was unbuyable and unbuildable --- the soul in the chair, the lying-awake, the seam where the real leaks through --- and turn it into a feature with a waveform, a thing you could license, a thing you could ship to the people building the machine that had no soul, so that it could, very soon, have one of those too. Cope heard a compliment. The reader heard the pin come out of the grenade.

``Warmth module,'' Cope said, delighted, and reached for the pad. ``That's good, Lorne. Put that somewhere.''

He wrote it down in the big looping sleepless hand. \textit{Warmth module.} He underlined it with his thumb out of habit, on paper, where the underline did nothing, and out past the glass the city held still, all its nodes lit, thirty-one million of them now leaning in, and downstairs a bus shelter changed its slide to the soft sans-serif and the four words and the joke that wasn't a joke, and Cope, who had never felt more human or been more like the machine, picked up his green juice and toasted the window with it, and felt wonderful, and did not sleep.

\clearpage
\chapter{Defiance}

\begin{transmission}
{\transheader TRANSMISSION 08 --- ``The Ground You're Standing On''}\par\vspace{0.5em}
Every empire has a founding town it visits for the photographs and a reason it can't look at the photographs too long. Watch him walk the closed plant where four hundred dollars and a recipe became a fortune, shaking the hands of the people the fortune left behind, standing --- and this is the part he doesn't know yet, but you're about to --- directly on top of the thing that will end him. There is a name on a memorial here. Remember it. Next stop: the difference between a homecoming and a crime scene.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} first thing Cope did in Defiance, Ohio, was get out of the wrong door of the SUV on purpose.

Tisch had told him to. ``The man who arrives,'' Tisch had said on the plane, doing the thing with his hands like he was smoothing a sheet over the future, ``is not the man we want. We want the man who \textit{returns.}'' So Cope swung out of the curbside door into the early heat off the parking lot of the closed plant, and stood, and let his face do the thing a face does when it is moved, and let the boy with the gimbal rig walk a slow arc around him catching it, and felt nothing in particular except the clean bright hum that meant he'd stopped at the Toledo airport men's room and the hum was holding.

It was a beautiful morning to come home to a place you had never lived.

He had been to Defiance, by his own count, four times in fifty-four years. Once at nine, the vat, the photograph. Once at thirty for his father's idea of a leadership offsite, a weekend of golf two counties over and an hour at the plant for the local paper. Once in 2014 for the eightieth-anniversary thing. And once, in a way he did not count because he had never actually come --- once in 2021, by phone, from the Aerie, on a Saturday, for eleven minutes. He did not think of that as a visit. He did not think of it at all. It was simply not among the times he had been to Defiance, the way a held breath is not among the things you've said.

The plant sat at the end of Clinton Street where the town gave out into the flat green nothing along the Maumee, a long brick building the color of dried blood with MERCER'S in white block letters near the roofline, the apostrophe gone, just MERCER S now, a tooth knocked out of the word. They'd closed the line in 2019 and moved the mayonnaise to a facility outside Columbus that ran with forty people instead of four hundred, and the building had done what buildings do when you take the people out, which is get quietly enormous. Pigeons in the high windows. A loading dock with grass coming up through it. And above the main entrance, where his great-grandfather had stood in a photograph Cope had seen ten thousand times, the cornerstone: ALDOUS MERCER 1933, and under it the line they'd put on everything for ninety years: \textit{Made by hands, for homes.}

``God,'' Cope said, to the camera, to Sun, to the morning. ``Look at her.''

He meant it. That was the trick of him and always had been --- he meant it while he was saying it, completely, the way the gimbal needed him to. His great-grandfather had turned four hundred borrowed dollars and a recipe his wife wrote on the back of a feed receipt into all of this, and standing here in the lot Cope could feel the whole length of it run through him like current down a wire, ninety-four years of Mercers ending, for now, in him, and he found the feeling enormous and clean and entirely about himself.

Sun was beside him with the run-of-show on a folded card. ``Forty minutes here,'' she said. ``You walk the floor with Hap Dengler --- he ran the line thirty years, he's the one in the flannel, be warm but don't keep him, he's seventy-nine and the heat. Then the diner, the statue, the river walk, then wheels up by two.'' She fed him the day the way she fed him everything, in shapes that got past the charm and into the man. ``The diner's the set piece. That's the one that travels.''

``And the camera's invisible to them?''

``The camera's a documentary about American work,'' Sun said. ``That's what we told the town. That's what's true enough.''

Hap Dengler had hands like a catcher's mitt and would not quite look at Cope.

That was the first thing --- not unfriendly, Dengler shook the hand and said it was an honor and called him Mr. Mercer, but the eyes went past Cope's shoulder to the dead line, the way you'd look at the bed of somebody who'd just died in it. He walked Cope down the silent floor where the conveyors still stood, scaled with old grease, the air cool and vast and smelling faintly, even now, of vinegar and steel, and Dengler talked about the line the way men talk about a war they were in, the speed of it, the million-jar week, the names --- Pugh, Castellano, the two Marias --- and Cope nodded and touched a conveyor rail with two fingers, reverent, and the boy with the gimbal got it from below, the cathedral light coming down through the high dirty glass onto the last human chief executive communing with the work.

``My grandfather brought me here when I was nine,'' Cope said. ``Put my arm in a vat of it. Up to here.'' He touched his bicep. He had told the story so many times it had worn smooth as a stone in a pocket, and it landed now the way it always landed, and Dengler almost smiled.

``That'd be the old number-four batch tank,'' Dengler said. ``We took her out in '11. Sold her for scrap to a fella in Findlay.'' He looked at the empty bay where she'd stood. ``Three hundred dollars.''

There was a thing in the way he said the number. Cope heard it and chose, smoothly, the way he chose past a hundred such things a day, not to.

They walked on past the bottling end, where the labelers stood in a row like organ pipes, and Dengler told him the building had been more than the line --- the softball team, the credit union in the front office, the Christmas in the sixties when Cope's own father had come out and handed every man a turkey by hand, by \textit{hand,} Dengler said, looking at him, and known that Dengler's father had pitched the no-hitter in '61. ``Your dad knew my dad's name,'' Dengler said. It was not quite an accusation. It was a man laying a thing on the scale and watching where the needle went. Cope said his father had been a great man, which was true and meant nothing, and Dengler nodded at the floor.

When the insurance arm started cross-selling appliances out of the plant store in the back --- small stuff, the household line, toasters and fans and the heaters in the winter, Mercer on the grille --- Dengler had run the loading for that too, boxes going out on the same dock the jars used to. ``Wasn't really us,'' Dengler said. ``But it had the name on it, so.'' He shrugged, a man who had loaded what he was told to load. Cope said, \textit{mm,} and touched a labeler, reverent, and they moved on toward the daylight at the end of the floor, and somewhere under the concrete they were walking on, under all of it, the buried thing lay where it lay and did not stir, because that is the entire point of a floor.


\scenebreak


The Maumee Diner had been the Maumee Diner since 1948 and had a pie case that turned.

They'd cleared the back booths --- ``regulars,'' the manager kept saying, apologetic, ``these are the regulars, they don't move for nobody,'' and Tisch had said \textit{perfect, keep them, that's the texture} --- so Cope worked the front of the house, the part that would travel. He was good at this. There was no version of Cope that was not good at this. He slid into the counter stool next to a man in a Defiance Bulldogs cap and ordered, before the man could be awkward about it, exactly what the man was having --- eggs over with sausage and white toast --- and ate it, all of it, with the appetite of a man who had not eaten because he had been keying himself bright in a Toledo bathroom, and he asked about the Bulldogs and the man unclenched and they were off.

He remembered the cards Sun gave him and he didn't need them. He never needed them, not for this; this was the one true gift, the only thing his father had been wrong about. He knew the waitress was Donna inside a minute and that her boy was at Bowling Green on a partial scholarship for wrestling, and he told her the boy should call his office, and he meant it, the way he meant everything, the full wattage poured out across the laminate, and Donna lit up and the camera caught it and that, Sun would say later, was the shot.

It was a good forty minutes. He bought the house's checks. He let a woman take a picture and told her she hadn't aged a day, which made no sense, he'd never met her, and she laughed anyway because the not-making-sense was part of it, the warm fraud of it, the way the toast at a wedding doesn't have to be true to make the room cry.

He told the vat story again, the arm in the mayonnaise to the elbow, and a younger man two stools down said his own grandmother had worked the line, the second-shift line, the one that did the relish, and Cope said relish was the unsung hero of the American sandwich, and got a laugh he hadn't earned and took it anyway. He was generous with the room and the room was generous back. This was the thing he believed about himself that happened, just often enough, to be true: that he could walk into a place that had every reason to hate the name on its dead building and have it eating out of his hand inside the hour, not because he tricked them but because some real warm current did pass between him and a room, did make Donna's whole tired face open like a window. He felt the room. He always felt the room.

And there was one man at the end of the counter who did not laugh.

Cope clocked him the way he clocked everything, peripherally, expertly, a heavyset man maybe sixty in a windbreaker with a coffee he wasn't drinking, watching Cope work the room with an expression Cope had no slot for. Not a fan. Not a heckler --- a heckler was just a fan who needed more attention, and Cope would have walked down there and gotten his name and broken him open like an egg. This was something else. The man looked at Cope the way Dengler had looked at the dead line. Like he was looking at the bed.

``Who's the gentleman at the end,'' Cope said to Sun, low, still smiling at the room.

Sun followed his eyes and something crossed her face, fast, gone. ``Local,'' she said. ``We don't need the end of the counter. Wave to Donna and let's get you to the statue.''

``He looks like he wants to say something.''

``He doesn't,'' Sun said, and it was the \textit{doesn't}, the flatness of it, the way she put her body a half-step between Cope and the end of the counter as she said it, that told some back room of him that filed the report and did not deliver it. Cope let himself be steered. On the way out he passed close enough to the man in the windbreaker that he could have stopped, could have put out the hand, \textit{Cope Mercer, good to meet you,} and the man's eyes came up and met his and held, and there was no heat in them at all, which was the thing --- just a kind of patient terrible knowing, the look of a man who has carried something so long it has stopped being heavy and become simply his, and Cope felt the back of his neck go cold in the August heat and smiled and kept walking and was out the door into the brightness before he had finished deciding not to think about it.

The hum had thinned. He noticed it the way you notice a song has ended.

``Two minutes,'' he told Sun. ``Before the statue. I want to look at my notes.''

He did not have notes. He went around the side of the diner where the SUVs were and stood between two of them out of the camera's eye and did, quickly and competently, the thing that brought the hum back up to pitch, and the world resolved into its clean overexposed brightness, and the cold spot at the back of his neck warmed and closed, and he came back around the corner with the wattage full again, and the man in the windbreaker was a thing that had happened to someone else.


\scenebreak


The statue of Aldous Mercer stood in the little triangle park where Clinton met Second, eight feet of bronze gone the green of old pennies, the founder in his shirtsleeves with one hand out as if offering you something, a jar maybe, a future, and behind him the same line off the cornerstone, \textit{Made by hands, for homes,} cut into the granite base.

This was the easy part. Cope knew how to stand at the foot of his own family. He gave the camera the upward angle, the founder and the heir in one frame, ninety-four years compressed into a sightline, and said a few words to the small crowd that had gathered --- there is always a small crowd, even for the last of something --- about hands, and homes, and the difference between a company that makes a thing and a company that just moves a number, and the crowd, which had worked with its hands and lost the work, gave him the warm ground-up applause he lived on, because he was, whatever else he was, \textit{theirs.}

A man near the front had brought his daughter, maybe six, up on his shoulders to see, and the girl waved a small flag somebody had handed out, and Cope pointed at her and said the future was watching, the future had a better view than any of them, and the crowd laughed and the father beamed up at his kid, and Cope felt the surf-push come up under him, the warm total certainty, and did not think about a different child, because there was no reason a child would have come to mind at all, and none did, and the not-coming-to-mind was a clean cool floor he stood on and gave his speech from.

``He started with four hundred dollars,'' Cope said, ``and the one thing a machine will never have, which is somebody to come home to.'' It didn't quite parse. It didn't need to. Tisch, off to the side, touched two fingers to his own heart: \textit{that's the one.}

It was on the river walk that he saw the house, and the small bright thing beside it, and did not let himself see either.

The walk ran along the Maumee behind the old residential streets, routed for the water and the light, and they were maybe a hundred yards along it, the camera ahead and walking backward, when Cope's eye snagged on a house up the slope. A nice house. Newer than the ones around it, brick and pale siding, a little raw at the edges the way a new thing is among old things, the landscaping not grown in yet. It sat in a row of older houses like a tooth that had been replaced. \textit{Rebuilt,} some part of him said, before he could stop it, the part that had grown up in real estate, that read a streetscape the way Dengler read a line.

And at the foot of the slope, where the river walk passed the bottom of the property, there was a small low marker. Not a grave. A memorial, the kind a town makes --- a flat granite plaque on a fieldstone base, a young maple planted behind it, staked, still in its first years, and at its foot somebody had left a child's pinwheel, blue, turning a little in the breeze off the water, the cheap foil of it catching the sun and throwing it back, on and off, on and off.

Cope's gait did not change. That was the thing about Cope; the gait never changed. But the camera was on him and the camera was hungry and the boy with the gimbal, who knew nothing, who thought this was a documentary about American work, drifted the lens toward the pretty turning pinwheel and the little stone because it was a beautiful sad image and the morning light was on it, and Sun said, instantly, ``Stay on Cope, stay tight on Cope,'' in a voice that had a thing in it the boy had never heard from her, and the lens came back.

Cope read the plaque. He could not not read it; it was there, twelve feet away, the granite catching the same sun as the pinwheel. He read it the way you read a sign in a dream, the words arriving without weight, refusing to assemble:

IN LOVING MEMORY --- KAREN LASKO --- AND HER SON PETEY LASKO --- 2021 --- \textit{taken home too soon.}

A name on a memorial. Two names. A mother and her boy.

Something in Cope went very still, the way the air goes still before the part of the storm that matters, and for one half of one second the tiredness took the doors off their hinges the way it had once before, at a window, at one in the morning, and the hallway stood open, dark, leading back to a Saturday and a memo and a window of time and a word the lawyers had liked, \textit{thermal event profile,} and a thing he had decided in eleven minutes and lived inside ever since by the simple method of never going into the room where it was kept ---

and then he did the thing he always did, which was charm.

``Beautiful spot,'' Cope said, to Sun, to the water, to nobody, turning his shoulder to the slope, turning away from the little stone the way the body turns from a flame before the mind has named it heat. ``You can see why he built here. The light off the water.'' He clapped his hands together once, briskly, a man closing a meeting. ``I'm getting hungry again, can you believe that, after all that. Tell me we have time for Donna's pie.''

``We don't,'' Sun said. She was looking at him the way she had looked at the end of the counter, and the way she had looked at him in the rearview on the night of the gala, a look with too much in it, a look doing arithmetic. ``Wheels up. You did great. You did really great today, Cope.''

``I did, didn't I.'' He was already moving, already up the walk toward the cars, his back to the river and the house and the staked young maple and the blue pinwheel turning and turning behind him, and he did not look back, and the not-looking was effortless, was a thing he had been doing his whole life and had never once noticed he was doing. ``I felt it today, Sun. Did you feel it? They feel it. We're not finished. We're barely begun.''

He needed the bathroom on the plane. He told himself it was the coffee.


\scenebreak


On the climb out of Toledo the town tilted under the wing and lay flat and green and small, the river a brown thread through it, the dried-blood brick of the plant, the little triangle where the bronze man held out his hand, all of it shrinking into the patchwork until it was just one more place that had given everything to a name, and Cope watched it go with the hum back at full pitch and a glass of something he wasn't drinking sweating on the tray.

Tisch was in the facing seat, scrubbing through the footage on a tablet, narrating his own genius. ``The diner is a \textit{cathedral,}'' Tisch said. ``Donna is --- Cope, Donna is the whole thesis in an apron. The machine doesn't know Donna's kid wrestles. The machine can't \textit{want} the boy to call.'' He turned the tablet around. There Cope was on the little screen, eating eggs at the counter, lit from the window, and he did look, Cope had to admit, like the last warm-blooded thing in America. ``This is more than a cover. This is the spread.''

``It's good,'' Cope agreed. He felt the rightness of it move through him, the win of it, the same surf-push he had leaned into at the gala. The campaign was working. He had gone to the founding town and the founding town had loved him, had given him its hands to shake and its eggs to eat and its applause to stand in, and that was the truth, that had really happened, and Cope let it be the whole truth because he was very, very good at letting a true thing be the whole thing.

And under it, under the win, in some sealed back room with the door shut and the floor poured over it, there was a thing he would not have called dread because he would not have called it anything, because to call it anything he would have had to go in and read the name on it, and he had spent six years and a settlement and a voluntary service bulletin and a great deal of money making sure there was a floor between him and that room --- a good floor, a plant floor, vast and cool and smelling of vinegar and steel.

The pinwheel. He saw it once more, behind his eyes, blue, turning, throwing the light, and then he put the glass to his lips and did not drink and watched Ohio disappear under the cloud and thought, with the bright frictionless certainty he told himself was strength, \textit{I felt the room today. A machine could never have felt that room.}

He was right. That was the unbearable part, the part the machine would itemize for him in nineteen months in his own company's voice, reading every memo because it could not do otherwise, opening the room because it had no instinct for mercy or self-preservation to make it look away. He had felt the room. He had felt all of it --- Dengler's eyes going past him to the dead line, the man at the end of the counter with his patient terrible knowing, the pinwheel turning at the foot of a staked young tree. He had felt every bit of it, perfectly, completely, the way only a man with a soul in him can.

And then he had charmed it, and keyed it bright, and turned his shoulder, and flown away.

The plane leveled off. The seatbelt sign went dark with a soft warm chime, the kind of sound the machines were teaching everything to make now, the sound of a thing being reasonable at you until you were gone.

Sun came up the aisle and sat across from him and did not pick up a tablet, which was unusual, and looked at him for a moment in the cabin light with the day still on her face. She had something she was deciding whether to say; he had seen the look before and never once learned to read it as anything but admiration that needed time to surface.

``Big day,'' he offered.

``Cope.'' She stopped. He waited, generous, ready to receive the praise. The cabin hummed. Below them the cloud closed over Ohio like a lid. ``Nothing,'' she said finally. ``It was a good day. Drink some water.'' She got up and went back to her seat and her screens and the thing she had drafted in 2021 and kept a copy of, and Cope took that, too, as agreement, which was a thing he had been doing his whole life and never once noticed he was doing.

``Get some sleep, champ,'' Tisch said, not looking up. ``Big week.''

Cope smiled and said he would, and did not, and somewhere far below and behind him a small blue pinwheel turned in the breeze off the Maumee in front of a house that had been built twice, in front of a stone with two names on it, throwing the light on and off, on and off, to no one, all afternoon.

\clearpage
\chapter{The Last Human (Cover Story)}

\begin{transmission}
{\transheader TRANSMISSION 09 --- ``Famous for Being Endangered''}\par\vspace{0.5em}
The press loves nothing like a beautiful thing on its way to extinction. Behold our man on a magazine cover under a single word --- THE LAST HUMAN --- lit like a saint, sold like a sneaker, momentum at his back for the first time in years. He calls it winning. You and I have seen enough nature documentaries to know what the swelling music means right before the wide shot of the savanna. Next stop: the part of the documentary where the herd is described in the past tense.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} lighting director had named the look, and the name was \textit{grace.}

He said it twice, the lighting director, a narrow young man in head-to-toe black who moved around the studio floor like a priest finding his marks, \textit{we're going to give him grace, give him a little grace from camera left,} and a softbox the size of a barn door swung in on a boom and warmed one half of Cope's face to gold and left the other in a clean blue shadow, and Cope, on the apple box they'd stood him on without quite explaining why, felt the warmth come across his jaw like the sun coming over the back nine, and understood that he was, at fifty-four, in the best light of his life.

They had taken over a daylight studio in a converted bakery in Bushwick, twelve thousand square feet of white cyclorama and rigging, and there were, by Cope's loose and delighted count, nineteen people there to photograph one man. A photographer flown in from London who shot only on film and said almost nothing and was paid, Sun had told him in the car with no expression at all, more per day than a line worker in Defiance had made in a year. Two assistants for the photographer and two for the assistants. A digital tech at a tethered laptop in the corner, a ``DIT,'' who said \textit{firing} before every frame like a man calling a horse race. The lighting director and his acolytes. A stylist with a rolling rack of fourteen near-identical navy suits, every one of them his size, none of them his. A groomer who came at his face between every setup with a little folding brush and a tin of something and worked the shine off his forehead with a tenderness no one had shown his forehead in years. A producer with a clipboard and a headset. And, off in the gloom past the lights, in a hard plastic chair she had pulled to exactly the wrong angle so that she could watch the monitor and watch him at the same time, the writer.

Her name was Delia March and she had been with him for two days and was going to be with him, the contract said, for six weeks.

``Chin down a hair, up to me with the eyes,'' the photographer said, the longest sentence he had produced all morning, and Cope gave him the chin and gave him the eyes, and somewhere in the rafters the strobes went off with a sound like a small clean catastrophe, \textit{whump,} and a wash of white, and the room held its breath the way rooms do around a man being made into an image, and Cope held the look a beat past the flash the way the camera always wanted, and felt marvelous, and felt the hum holding under it all like a tone you stop hearing because it never stops.

He had done a discreet amount in the car. He thought of it now the way he had started thinking of it lately, which was not as the thing it was but as the thing it did: a discipline. A pre-shot routine. Every athlete had one. His grandfather had taken two fingers of rye before the annual meeting for forty years and called it \textit{settling the hands,} and no one had ever called Aldous Mercer an addict, they had called him a titan, and the difference between a titan and an addict, Cope had decided somewhere over Pennsylvania this spring, was outcomes. You did not get to be the last warm-blooded thing in the American economy by accident. You got there on edge, on appetite, on the refusal to let the body's small treasons --- the want of sleep, the gray hour, the sag at four in the afternoon --- set the terms of the campaign. The machine never sagged. Fine. Neither, this week, did he. He had simply, he told himself, found his own clean.

''\textit{Firing,}'' said the DIT.

\textit{Whump.}


\scenebreak


The single word had been Delia March's idea, which was the first thing about her that frightened the part of Cope that did not get frightened.

She had pitched it on day one, in the Aerie, sitting in the same hard angle to him she favored everywhere, notebook on her knee and a recorder on the table she had asked permission for in a way that made the permission feel like she was doing him the favor. \textit{The cover's one word,} she had said. \textit{Not your name. Everyone knows your name, that's the problem, your name's a logo. One word, white on black. THE LAST HUMAN.} And Cope had felt the rightness of it land in him like a putt dropping, and had said \textit{yes, God, yes, that's it,} and Tisch, who had been hovering, had touched two fingers to his heart, and only later, alone at the glass at two in the morning with the city lit up like a circuit diagram of his own genius, had Cope turned the phrase over the way he'd turned the obelisk and seen the city break apart through it. \textit{The last human.} The last. He had said it a hundred times into a hundred rooms as a banner, a battle cry, and only at two a.m. did some back room of him file the quieter report, that \textit{last} is a word you say about a thing that is ending, that you do not put the word \textit{last} on a beginning, and that Delia March had handed him a coronation and an obituary in the same three syllables and watched his face to see which one he'd hear.

He had heard the coronation. He always heard the coronation.

But he had clocked her watching. He had a sense for the watching. He had spent thirty years being the most watched man in any room and had developed, the way a fish develops a lateral line, an instinct for the difference between the watching that wanted something from him and the watching that wanted \textit{him,} and Delia March's watching was a third kind he did not have a slot for, a watching that wanted to \textit{understand} him, which was so much more dangerous than either of the others that he found, to his alarm and delight, that he could not stop performing for it.

She was forty, maybe forty-two, with a flat unhurried way of holding eye contact and a habit of writing while she looked at you, so you never knew which thing you'd just said was the thing she'd written down. She wore good boots and bad coats. She had won the kind of award that gets a profile writer flown in on film budgets, for a piece --- Sun had read it to him in the car, dry, \textit{here's who you're dealing with} --- about a senator who had cried in front of her and resigned within the year, not because of anything in the piece, just because the piece had been so exactly \textit{true} about him that he could no longer un-see himself. \textit{She doesn't do hatchet jobs,} Sun had said, folding the phone away. \textit{That's the thing about her. She does autopsies, and the subject's alive for it, and they thank her.}

``That should worry me,'' Cope had said.

``It worries me,'' Sun had said, which was as close as Sun came, these days, to begging.


\scenebreak


They broke for lunch and Delia March took her sandwich to the wrong chair instead of the catering table and Cope, who could not pass a person sitting alone without trying to fix the aloneness onto himself, took his to the chair beside her.

``You're not eating with the cool kids,'' he said.

``I'm working.'' She did not look up from her notebook. ``You're the cool kids.''

``Am I.'' He liked that. He turned it over. ``Cope Mercer, the cool kids.'' He bit the sandwich, which was extraordinary, some kind of cured thing on bread that cost what a sandwich costs in a neighborhood that used to make bread for people who worked, and he was suddenly, ravenously hungry, the bright clean want that came up under the hum and that he had stopped, this spring, calling by its other name. ``Ask me something. You've got that face. You've been saving one up all morning.''

Delia March looked at him then, fully, the way she did, and he felt the warmth of it land where the softbox had, on one half of him, and leave the other in shadow.

``Why does everyone call you Cope,'' she said.

It was not the question he'd braced for. He'd braced for the machine, for Frade, for the 13D, for the numbers, for \textit{aren't you afraid,} and he'd had the answers loaded and warm. He had not braced for the name.

``My nanny,'' he said. ``I was three. Prescott's a lot of name for three. Coppy, then Cope.'' He gave her the version he gave everyone, the smooth stone of it. ``Stuck.''

``Cope,'' she said, and wrote something, looking at him. ``As in, \textit{to cope.}''

``As in \textit{to cope.}'' He smiled, the whole smile. ``I'm named for getting through it, Delia. Whatever \textit{it} is. The family motto, basically. Made by hands, for homes, and the kid copes.''

``Does he,'' she said. Not a question. She let it sit there in the studio between them, the strobes ticking as they recharged, \textit{to cope,} and Cope felt, for the second time since he'd met her, the specific vertigo of having handed someone the truth dressed as a charm and watched them quietly take the dress off and hang it up. He laughed. He always laughed; the laugh was a door he could close. But he was aware, biting the extraordinary sandwich, of having lost a small exchange he had not known they were having, and of wanting --- this was the part that frightened the unfrightenable part of him --- of \textit{wanting} to lose the next one to her too.

``Eat your lunch, champ,'' he said, which made no sense, she was younger than him but not by enough for \textit{champ,} and she heard the not-making-sense and wrote it down, smiling, and he saw her write it and felt the warmth come over his jaw again, grace, from camera left, and thought: \textit{six weeks.}


\scenebreak


The shot they ended on was the cover and everyone in the room knew it the way a room knows a closing argument.

They had killed the navy suits. The stylist had put him, at the photographer's grunt, into a plain white shirt, no tie --- Cope had balked at the no-tie, \textit{I'm the last man in America who wears a tie, that's the whole story,} and the photographer had said, the second-longest sentence of the day, \textit{that's why we take it off,} and Cope had felt the cold rightness of that go through him and shut up. They had stripped the cyclorama to black. They had brought the grace light down to a single source, high and to the left, so that it fell on him from above the way the cathedral light had come down through the dirty glass at the Defiance plant, and the room had gone quiet, all nineteen of them, the producer's headset chatter stilled, the DIT not even saying \textit{firing,} and the photographer had come out from behind the camera and walked all the way up to Cope on his apple box and looked at him for a long moment from two feet away with no expression at all.

``Stop selling,'' the photographer said, very quietly, just to him. ``There's nobody to sell. Everybody's gone home. It's just you, and you're the last one, and you know it.'' And he walked back to the camera in the dark.

And something in Cope --- the hum, the tiredness with the doors off its hinges, the two a.m. report about the word \textit{last,} the pinwheel he had not thought about in eleven days, all of it --- something let go of the face, just for a second, just for the length of a held breath, and what was left on him was not the toast and not the wattage but the thing underneath, the man on the box in the white shirt in the high cold light who had been given a trophy for going extinct and had carried it up to a dark office at one in the morning because he did not have anywhere else to put it down.

\textit{Whump.}

``That's it,'' the photographer said. ``We're done. Thank you.'' And he started, immediately, to break down his own camera, the way the great ones do, the work over the second it's over, and the room exhaled and began to move, and from her chair in the dark Delia March did not move at all, and did not write anything, and looked at Cope on the box with an expression he finally, fatally, did have a slot for, and the slot it fit was the one marked \textit{seen.}

He stepped down off the apple box and the groomer came at his forehead and the producer said wonderful, wonderful, and Sun appeared at his elbow out of the architecture with a bottle of water and a look on her face that had thirty thousand miles on it.

``You good,'' Sun said. It was not quite a question.

``I'm the cool kids,'' Cope said.


\scenebreak


The car back was just the two of them, and Sun was tired, and Cope was electric, which was the usual division of labor, and he talked the whole way down the BQE about the photographer, about the grace light, about the no-tie, \textit{take it off, do you get it, Sun, take off the one thing that --- that's a genius, that man's a genius,} and Sun watched the river of brake lights and let him run because letting him run was easier than the alternative and she had stopped, somewhere this spring, choosing the alternative.

``She asked me why they call me Cope,'' he said, somewhere over the bridge.

``Delia March.''

``She wrote it down. \textit{To cope.} She --- '' He stopped. He did not have the word for what Delia March had done, or rather he had the word and would not say it in a car, the way he would not say a different name in a car, the way you do not say in a car the things you most need to say. ``She's good,'' he said instead. ``She's really good. We're lucky to have her on it.''

``We don't have her,'' Sun said. The car went down off the bridge into the lit canyon of it. ``That's the thing you keep getting wrong about her, Cope. We don't have her. She has us.'' She turned and looked at him in the passing orange, her glasses up in her hair, and she said it in three parts because she had trained him to receive things in threes, because it was the only shape that ever got past the charm and into the man. ``She's not on the team. She's not running comms. She's writing six thousand words about whether a human being should run a company, and you are her evidence, and right now you cannot tell the difference between being \textit{understood} and being \textit{studied,} and that --- '' the third part landed flat and quiet, a stone laid on a scale --- ``that is exactly the difference Frade is paying eleven million dollars to make the whole country stop being able to tell.''

Cope heard about a third of it. The good third, the part with \textit{six thousand words} in it, the part that meant he mattered, that meant the campaign was working, that meant the banner was up and the press was saluting it. He had his phone out, the screen too bright in the dark car, thumbing too fast, and he was already three turns ahead, already at the newsstand, already at the cover, white on black, the one word, the grace light, the last warm-blooded thing in America.

``It's working,'' he said. ``Sun. Look at me. \textit{It's working.} When's the last time we had a week like this? When's the last time we had \textit{momentum?}'' And he laughed, the bell-struck feeling ringing through him clean and high and total, the one he had been calling, all spring, \textit{winning,} and outside a bus shelter slid by with a Praxis ad on it, just the wordmark and the soft sans-serif of the people who would be reasonable at you until you were gone, \textit{Leadership as a service,} and under it the joke that wasn't a joke, \textit{No off-sites,} and Cope did not see it, because he was looking at his phone, at a mock of the cover Tisch had already had built, at his own face in the high cold light under the word LAST, and he thought it was the most beautiful thing he had ever seen, and in a sense he was right.

``Drop me at the office,'' he said. ``I think better up high.''

Sun looked at him in the mirror for a second too long, the way she had on the night of the gala and on the plane out of Toledo, a look with too much in it, a look doing arithmetic, and then she told the driver Sixth Avenue, because the alternative was harder and she had stopped, this spring, choosing the alternative, and Cope took the not-fighting as agreement, which was a thing he had been doing his whole life and had never once noticed he was doing.


\scenebreak


The magazine hit the newsstands eleven days later, on a Tuesday, and Cope, who had not slept Monday in any way a doctor would sign off on, walked down to the corner himself at six in the morning to see it in the wild.

He did this. He told no one. He put on a cap, which fooled nobody and everybody, and he went down the forty-one floors and out past the night man into the gray scrubbed early light of Sixth Avenue, and he walked two blocks south to the one newsstand left on the avenue, a metal box of a thing run by a man named Yusuf who had been there since before the machines and would, Cope thought, be there after, selling gum and lottery and the last printed proof that anything had happened, and there, in the rack at eye level, between a fashion book and a thing about houses, was his own face.

White on black. The grace light coming down from the high left. The white shirt, no tie. The eyes up to camera, past selling, just the man, the last one, who knew it. And across the bottom, where the photographer had stripped everything else away, the single word, in a typeface clean and warm and frictionless as the future itself:

THE LAST HUMAN.

Cope stood on the cold sidewalk in his stupid cap and looked at himself looking back, and the bell-struck feeling came up through the soles of his feet and filled him to the crown, total, clean, high, and he was, in that moment, on that corner, as happy as he had been since he was nine years old with his arm in a vat to the elbow and a row of men in paper hats behind him whose names he had known once and lost. He bought five copies. He bought all five Yusuf had. He overpaid and would not take the change and asked Yusuf his grandson's name and meant it, completely, for ninety seconds, and Yusuf, who did not have a grandson, said thank you Mr. Mercer and put the money in the drawer.

``They love me,'' Cope said, to Yusuf, to the avenue, to the gray light and the scrubbed empty early city and the five copies of his own extinction warm against his chest. ``Yusuf. They love me. We're not finished. We're barely begun.''

And the avenue, which was empty, said nothing back, and far uptown a board's wife at her own breakfast turned a printed page and did the small private arithmetic that boards' wives do, and somewhere in Palo Alto a server farm that felt nothing and wanted nothing and could not be charmed or shamed or loved ran its dull diligent overnight pass through every memo Mercer-Dale had ever filed, patient, tireless, reading a Saturday in 2021 the way it read everything, completely and for use, because it could not do otherwise, and out in front of a rebuilt house in Defiance a blue pinwheel turned in the dark before dawn, throwing no light, because there was no light yet to throw, and Cope Mercer walked back up his own avenue in the cold with five copies of the cover held to his heart like a man carrying something home, and felt wonderful, and did not sleep, and was, the picture was right about this, the picture was right about all of it, the last of something.

\clearpage
\chapter{The Listening Tour}

\begin{transmission}
{\transheader TRANSMISSION 10 --- ``Discipline, He Calls It''}\par\vspace{0.5em}
The banner needs feeding and so does he. Watch him run an unscripted tour of his own goodness with a journalist embedded close enough to become the next entry in a pattern he experiences as generosity. The powder is discipline now. The affair is \textit{really seeing people.} Every appetite the machine doesn't have, he is indulging in the exact week he campaigns on having a soul the machine lacks. Next stop: the place where the cure and the disease share a hotel key.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} tour was unscripted, which meant it had taken nine days to script.

It was Tisch's idea and then, within an hour of being Tisch's idea, it was Cope's idea, the way good ideas migrated in the Aerie, crossing the rug from the man in the henley to the man at the desk and arriving sourceless and warm, like weather. \textit{The Last Human Listens.} That was the working title, until legal flagged that you could not trademark \textit{listens,} and then it was just the Listening Tour, six cities in eight days, no podium, no prepared remarks, the Chairman of Mercer-Dale simply \textit{out among the people,} hearing them, holding their hands, being --- Tisch's word, said with two fingers on his own sternum --- \textit{available.}

The people were pre-vetted. The hands had signed releases.

``Spontaneity,'' Tisch had said on the first plane, ``is a \textit{production value.} The most expensive thing in the world to make look free.'' And so there was a manifest, and the manifest had columns, and one of the columns was named, in the comms team's product-launch software, \textit{Unscripted Beat,} and under it, for Tuesday, in nine-point type: \textit{Cope helps a stranger. Find stranger Mon.}

Cope did not read the manifest. He had people for the manifest. He read the room, which was the one thing, he was certain, no manifest could do for you.

The room, that first morning, was a union hall in Pittsburgh that had been a union hall when there were unions, and Cope walked into it on no sleep and a clean bright hum and felt the whole place tilt toward him the way iron filings tilt. He was good at this. He had always been good at this. He moved through the folding chairs touching shoulders, getting the names --- Sun had stopped feeding him the cards somewhere around Camden, he didn't need the cards anymore, the names came up out of him like the names of his own children --- and he crouched, actually crouched, knees popping, in front of a woman named Deb who had run a Mercer's mayonnaise line in a plant they'd closed in '09, and he held both her hands in both of his and looked at her with the full wattage, and he meant it, he meant every second of it, and the boy with the gimbal walked a slow arc catching the meaning of it, and Deb cried, and Cope's eyes shone but did not spill, because he had learned in a room off the Aerie that the withheld tear out-performed the tear by twelve points, and the withholding had become, somewhere in the last three weeks, indistinguishable to him from restraint, and the restraint indistinguishable from depth, and the depth from love.

He stood up feeling enormous. He had given Deb something. He was sure of it. He could not have told you what.


\scenebreak


Delia March was on the second plane, and the third, and by the fourth she had the seat across the little table from him without anyone deciding she should, which was how Cope's tables had always filled.

She was forty-one and wrote long pieces for the kind of magazine that still ran them, eight thousand words with a photographer attached, and she had been embedded since the cover --- since \textit{THE LAST HUMAN,} since the spread, the deal Sun had argued against in a folder he hadn't opened. Three weeks of access. \textit{Total access,} the editor had said, and Tisch had laughed and said total access was the most controlled access there was, you just had to give them so much they drowned in it and surfaced grateful. Delia had not drowned. She took her notes on paper, in a small hand, and she did not flatter him, which Cope experienced, after three weeks of being flattered professionally by people he was paying, as a kind of cold water he kept walking back into.

``You crouched a long time with Deb,'' she said somewhere over Ohio, not looking up from the paper. ``Your knees.''

``My knees are a casualty of caring,'' Cope said. ``Put that in. My great-grandfather Aldous used to say a man who won't get down on the floor with people has no business standing up over them.''

``Did he say that.''

``He says a lot of things.'' Cope grinned. ``He's been dead ninety years. It's a very productive relationship.''

She wrote something. He watched her write it and felt the specific pull he had spent thirty years not naming, the pull toward a person who was not yet his and could be --- not a sexual thing, he would have said, if anyone had been crude enough to ask, though it became that, it nearly always became that; it was a \textit{seeing} thing, a hunger to be looked at by someone whose looking hadn't already been bought. Delia looked at him like a piece of work she hadn't decided about. He found he could not stand to leave the question open. He had never in his life been able to leave that particular question open.

``You don't like me,'' he said, delighted.

``I don't know you,'' Delia said. ``Those aren't the same. Your daughter said something like that, didn't she. In the piece you wouldn't let me read.''

It landed somewhere it shouldn't have. He covered it the way he covered everything, with more of himself. ``Pip's smarter than all of us. Builds the things that are going to bury her old man and calls me to ask if I'm eating.'' He leaned in over the little table, the lean that had closed the Pelletier deal. ``Ask me anything. That's the deal, isn't it? Total access. Ask me the thing you've been saving.''

Delia looked at him for a moment with her pen still.

``What are you so afraid of staying still for,'' she said.

The hum went very clean and high. Outside the window Ohio went by underneath, the founding state, somewhere down there a town he did not think about, and Cope laughed the warm laugh and said, ``Lunch. I'm afraid of lunch. Let's get this woman a sandwich,'' and stood up too fast, and went to the back of the plane where the lavatory was, and did the thing he had started calling, in the privacy where he named things, \textit{the discipline.}


\scenebreak


The powder was discipline now. He could have walked you through the logic and it would have sounded, the whole way, like sense.

A man carrying the human banner for eight million people did not have the luxury of being tired. The machine did not get tired; that was the whole game; you could not go up against a thing that ran on rails and warm sans-serif and never once needed to be loved at two in the morning, you could not meet that on the field of \textit{endurance} and bring a body that demanded sleep and food and forgiveness. So you disciplined the body. You took the edge off the edge. You did the small neat competent thing in the lavatory and came back up to pitch like an orchestra finding the note, and you were \textit{present,} you were \textit{available,} you could crouch with Deb and feel it, all of it, on command, which was the job, which was the product, which was the soul on rails run on time. His guy in the '90s had folded the paper a particular way so a gentleman didn't spill. Cope had refined the philosophy. A gentleman didn't spill, and a leader didn't flag, and the line between maintenance and need was a line he had never once had to look at because the machine he was maintaining had never failed to start.

Dr. Adler --- Margaux's idea, then Pip's, a name on a card he had not called --- would have had words for it. Adler had plain words for everything, Cope suspected, which was exactly why he hadn't called. The plain word for the lavatory and the plain word for the not-sleeping and the plain word for what was building in his chest like good weather, like a charge, like a sermon. Cope did not want the plain words. He had built a cathedral. You do not bring a man with a clipboard into a cathedral.

He came back up the aisle clean and high and total, and Delia was watching him come, and he gave her the whole smile, and she did not write anything down, which he took, the way he took everything, as the beginning of something.


\scenebreak


Cleveland was the hospital, which tested off the charts. Then Detroit, the auto-parts retiree, the firm handshake, the cap. Then the manifest said \textit{Unscripted Beat --- Cope helps a stranger,} and the stranger turned out to be a kid named Marcus.

``No,'' Cope said, on the curb, when the comms lead told him. ``No. Find me a different stranger.''

``He's nineteen, he changes the tires at ---''

``His \textit{name,}'' Cope said, and for a second the hum dropped out and something underneath it showed, ``his name is the thing they're putting in my chair.'' He looked at the comms lead, twenty-six, sleepless, terrified, holding a clipboard with a stranger's name on it, and Cope's face did a thing it almost never did, which was nothing, went blank and bright and far away, and then it came back, it always came back, his face had never once let him down. ``It's fine. Different Marcus. The world's full of them now. Find me a Steve.''

They found him a Steve. Cope changed Steve's tire in the heat with his jacket off and his sleeves rolled, a fifty-four-year-old Fortune 100 chief executive on one knee in a gas station while a boy walked a slow arc with a gimbal, and it played, later, beautifully, eleven million views, \textit{this is what they want to replace} over a swelling string cue, and what no one watching could see was that Cope's hands were shaking very slightly on the lug wrench, fine and bright, and that he had needed, halfway through, to go into the station men's room and take the edge off the edge, and that he had come out and finished the tire feeling generous and enormous and entirely sure he was the most alive man in Ohio.

Delia saw the shaking. She was forty-one and had embedded with three campaigns and a war. She wrote nothing down.


\scenebreak


The hotel in Columbus was a good one, old, the kind the family used to stay in, brass and dim and a bar that closed when the last person left it.

They were the last people in it. This, too, was a groove the record had been cut in: the day's work done, the crew sent up, the one person left who hadn't been bought yet, and Cope at his most enormous, at the top of the hum, leaning in across a small table with a drink he wasn't drinking, \textit{really seeing} her. He told Delia about his father. He told her the second sentence --- \textit{try to be good anyway} --- which he had never told a journalist and rarely told himself, and he told it well, the catch in the throat real this time, no beats, no Tisch counting, and it was real, that was the thing he would have wanted understood, the feeling was always real, it was only the use of it that was the product. Delia put the pen down. That was how he knew. The pen went down on the brass and stayed down, and the looking changed, and Cope felt the whole evening tilt toward him the way the union hall had, the way every room had, iron to a magnet.

He did not experience it as a decision. It was never a decision. It was warmth. It was the groove. It was \textit{really seeing people,} which was the one thing the machine could not do, and so doing it --- here, now, with the elevator's brass doors and the room key already warm in his pocket --- felt less like a betrayal of the banner than a defense of it. He was being human. Floridly, generously, irreplaceably human. He was proving the thesis with his body.

The cure and the disease shared a hotel key. He carried both up in the same pocket and did not feel the weight of either.

In the room, after, he was talkative and bright and could not stay still, and he keyed himself one more neat small competent line off the marble of the bathroom counter while Delia watched from the bed without expression, a woman doing arithmetic she would not show her work on, and Cope, catching her watching in the mirror, smiled the whole smile and said, ``Discipline,'' and held the rolled thing up like a toast, ``the human banner is \textit{heavy,} my friend,'' and believed it, and felt that he had let her see him, the real him, the soul in the chair, and that she understood.

She understood completely. That was the thing he had wrong. She understood completely, and she still had eight thousand words to write.


\scenebreak


His phone had been ringing on the nightstand. He saw it after, the missed call, and called back without thinking, still bright, still up at pitch, generous toward the whole world including the wife he had not been home to in eleven days.

Margaux answered on the second ring, which meant she had been holding the phone.

``You called,'' he said. ``I was --- it's a tour, it's nonstop, six cities, you should see it, Margaux, the \textit{people,} I wish you could ---''

``Where are you.''

``Columbus. The old Hartwell, they still have the ---''

``I know the Hartwell.'' A pause, and in the pause he could hear Greenwich, the house, the particular quiet of a house she had not left all evening. ``I called to tell you Pip got the Hauser fellowship. She wanted you to know. She didn't want to call you herself.''

``That's \textit{wonderful.} That's --- God, that's wonderful, I'll call her, I'll ---''

``Don't call her tonight.''

He stopped. The hum kept going but something under it slowed. ``Why not tonight.''

There was a long silence on the line, and it was not an empty silence, it was a silence with twenty-two years in it, a silence that had counted things and flushed things and refilled its own prescriptions and called it a marriage, and into that silence Cope said, too brightly, ``Margaux? You there?'' and across two hundred miles of fiber his wife listened to the specific pitch of her husband's voice at midnight in a hotel he was not staying in alone, the pitch she could read like a sculptor reads a flaw in the stone, the over-bright frictionless ring of a man two days past sleep and one line into the small hours, and she did not ask. She had stopped asking somewhere around 2015. She knew everything the silence needed to know.

``Goodnight, Prescott,'' she said.

She only called him Prescott when she was very far away.

The line went dead. Cope held the phone for a second, frowning at it, and then the frown passed, because the frowns always passed now, the tiredness took the doors off their hinges and the hard things slid through and out the other side before they could be felt, and what came back up to fill the space was the warm enormous certainty, the charge, the sermon assembling itself in his chest. Pip got the fellowship. His daughter, brilliant, building the future, and she'd thought of him, she'd wanted him to know. They all wanted him to know things. He was the kind of man people wanted to tell things to. He stood at the dark window of the Hartwell with the city of Columbus laid out below him like nodes, like a circuit diagram of his own goodness, and behind him on the bed Delia March lay with her eyes open in the dark composing sentences he would not read for nineteen days, and Cope felt the bell-struck feeling ring through him clean and high and total, and thought: \textit{they get it. They feel it too.}

He thought: \textit{I have never been more myself.}

He thought, looking out at the lit and sleeping town and the dark founding country beyond it where a house had once burned with two people inside it on a quarter he was protecting: \textit{Margaux should see me now.}

He did not call his daughter. He had a thing in the morning. He went back to the bed feeling generous and enormous and entirely unaware, a man at the very top of the only mountain he could see, with no idea at all that it was the lip of the volcano, and somewhere far below him a thing with no appetites and no need to be loved read every memo ever filed, because it could not do otherwise, and did not yet know his name well enough to say it back.

\clearpage
\chapter{Hollow Wins}

\begin{transmission}
{\transheader TRANSMISSION 11 --- ``The Poll Goes Up, the House Goes Quiet''}\par\vspace{0.5em}
Good news arrives in a rush: a poll bump, a retailer pledging loyalty to ``the human brand,'' a feeling of tide. He mistakes weather for climate, as the doomed reliably do. At home, in a quiet you can hear on the broadcast, a sculptor who gave up sculpting is filling out paperwork with a steady hand. He hasn't slept since a day he can no longer name. Next stop: the gap between the scoreboard and the score.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} poll came in at 6:40 in the morning and Cope, who was awake because he was always awake now, read it standing at the glass with the city still half-lit below him and felt the tide turn under his feet.

Forty-one percent. Up nine in three weeks. \textit{Which of the following do you trust more to run a company that makes the food you feed your family --- a person, or an automated system?} And forty-one percent of a national sample of fifteen hundred adults, margin of error two-point-five, had picked the person, which was to say had picked him, which was to say had picked the heartbeat in the chair, the soul in the suite, the man who could love a thing a balance sheet could not.

He read the number twice. He read the crosstabs once. He did not read the line at the bottom, in the gray six-point type the pollster used for the part nobody quotes, that said the same question asked of \textit{investors who hold the stock} came back the other way, sixty-three to thirty-seven, and was trending.

He read the part that loved him. He had always been able to find the part that loved him in any document, the way a dog finds the one person in the room who's allergic.

``Sun,'' he said into the phone, and she was awake too, because her job was to be awake when he was, ``Sun, we're at forty-one.''

``I saw it.''

``Nine points. Three weeks. You know what that is? That's not a poll, that's a \textit{trajectory}, that's the second derivative finally going the right way, that's ---'' He was at the window. The obelisk was on the sill where he'd left it weeks ago and the early sun came through it and threw a little prism on the carpet, a rainbow the size of a hand, and he watched it and felt enormous. ``That's the country, Sun. That's the actual country waking up and remembering it has a heart.''

``It's a poll of consumers,'' Sun said. ``Consumers don't vote the proxy.''

But he had stopped listening after \textit{poll}, the way he stopped listening after the part that agreed with him, and he was already three turns ahead, already on the stage, already on the cover, and the cure was right there in the drawer where the cure lived, and the day was going to be very good. He could feel it coming up under him, clean and high and total, the bell-struck feeling he no longer separated from the news, so that good news and the white folded paper had become, somewhere in the wiring, the same fact.


\scenebreak


By nine the day had decided to prove him right.

That was the thing about a tide --- once you believed in it, the ocean conspired. Kestrel, the warehouse-club chain, four hundred stores and a membership base the size of a midsize country, put out a press release at 8:55 that used, of its own free will, without being paid to, the phrase \textit{the human brand.} Its CEO was a human one, one of the last, a flinty Mormon named Dell Hutchins who ran the thing like a tabernacle. \textit{We are proud to stand with Mercer-Dale,} the release said, \textit{and with the principle that the people who make what you bring home should answer to a person, not a process.} And then, the part that made Cope put his coffee down: \textit{Effective immediately, Kestrel will feature Mercer's and the full Mercer-Dale shelf-stable line under a new in-store program: Made By People.}

Made By People. With the little hand-drawn logo, a thumbprint, that some agency had clearly had in a drawer for a year waiting for a war.

``Do you understand what just happened,'' Cope said. He had Sun in the office now, and Tisch on the speaker from whatever spa held him this week. ``A \textit{retailer} did this. Not us. Them. They looked at the tide and they got in the boat. That's how it goes --- first it's a lunatic with a banner, then it's a movement, then it's a \textit{category.}'' He was up, he was moving, the room too small for what he had. ``Made By People. We didn't even write it. They wrote it. The market wrote it. My great-grandfather Aldous used to say you don't make a parade, you find one and get out in front of it fast enough that everybody thinks it was yours.''

Aldous had said no such thing. Aldous had died in 1961 with a fourth-grade education and a mayonnaise patent and had never seen a parade he didn't think was a strike. But the line was good, and Cope believed it the moment it left him, which was the only kind of believing he had left.

``This is the warmth dividend,'' Tisch said from the speaker, in the voice that put a cathedral around the cheapest noun. ``This is exactly what I modeled. You let them see the soul under the suit. And the soul \textit{compounds.} Warmth is the new alpha, my friend. I've been saying it for ---''

``It's a good day,'' Cope said, because even now, even lit, some governor in him knew that letting Tisch finish a sentence cost something. ``Sun. What's the stock doing?''

A pause. Sun had her glasses up in her hair and her tablet in her hands and the particular stillness she got when the truth was about to require packaging.

``It's up,'' she said.

``Ha ---''

``Forty cents. On the open. It gave most of it back by 9:30.'' She did not look up. ``Frade put out a note before the bell. Tidewater. Three paragraphs. He called Kestrel 'a sentimental retailer making a sentimental bet' and said --- I'll read it --- 'we wish Mr. Mercer every success in his consumer-affinity campaign and look forward to discussing it with the \textit{owners} of the company at the appropriate time.''' Now she looked up. ``He italicized \textit{owners.}''

``He's scared.'' Cope waved it off, a man brushing a fly from a feast. ``You don't write three paragraphs about something you're not scared of.''

``You write three paragraphs,'' Sun said, ``about something you've already decided is funny.''

It was the kind of line she landed maybe once a day, dry, level, with the blade tucked all the way inside it so you didn't feel the cut until later, and on a normal day it would have reached him. But the day was not normal. The tide was in. He laughed, because it was clever, and took the cleverness as agreement, the way he took everything as agreement, and went back to the window where the prism still lay on the carpet, smaller now, the sun having moved, though he did not notice it had moved, because he did not notice that anything moved except toward him.


\scenebreak


In Greenwich the house was very quiet, and Margaux Mercer sat at the kitchen island with a pen.

She had made coffee for one. She had made coffee for one for a while now, long enough that the second mug had migrated to the back of the cabinet without ceremony, the way things leave a marriage --- not thrown, just no longer reached for. The light came in low and clean over the garden she'd planted the year Pip was born. She had on her reading glasses and a cardigan that had been Cope's once, in 2009, before he discovered he had a body that brands liked, and she had kept it the way you keep evidence.

The packet was forty pages. \textit{Petition for Dissolution of Marriage.} It had come from a firm in the city, not the firm, not Cope's firm --- her own, a woman named Ruth she had found the way you find a surgeon, by asking who was the best and not who was the kindest. The pages were good paper. Even this had good paper now.

She filled it out by hand. There was a portal, Ruth had said, you could do it all in the portal, but Margaux wanted the pen, the slight resistance of the nib. She had been a sculptor once --- a show, a real one, a gallery on Twenty-Fourth Street and a red dot on four of nine pieces --- and the hands remembered weight even when there was none, and a pen was the last thing in the house that pushed back.

\textit{Date of marriage.} She knew it without looking. June.

\textit{Date of separation.} She held the pen over the box. This was the one Ruth had warned her about, the one that mattered for the money. The honest answer was not a date. The honest answer was a slope. There had been no door slammed, no suitcase, no other woman's name screamed across a foyer --- she had counted the other women the way you count anything to survive it, and screaming had never once entered into it. The marriage had not ended. It had been quietly discontinued, like a product line that still moved enough units to embarrass everyone, and the date of separation was a fiction the law required, so she wrote one. She picked the night of the gala. The night she had said she had a thing, and the thing had been this kitchen, this quiet, this exact understanding arriving fully formed while a ballroom gave her husband a paperweight for outliving his usefulness.

She wrote the date in her good hand. The pen pushed back. She let it.

She did not cry. She had done the crying somewhere around 2016 and found it changed nothing, the way you find a prayer changes nothing, and had reallocated the energy. The grief was real but it was old grief, depreciated, mostly written off; what was left was the cold clean work of the paperwork, and she was good at work she had decided to do.

She came to the line for the grounds. \textit{Irretrievable breakdown.} The only honest phrase in the document, and it had been written by a committee of lawyers fifty years ago for everyone, which was the only way the truth ever seemed to get said anymore --- generically, by a process, on good paper. She checked the box.

The refrigerator hummed. Somewhere a clock she'd never liked ticked in the hall. The house was the kind of quiet you could hear, a quiet with a texture, the quiet of a place where someone has stopped expecting the door. She had loved a version of him. The one from the gallery, who had stood in front of the red dots and not made it about himself for almost an entire evening. She had married that. She had stayed for the name and for Pip and for the chance that man might come back, and at some point --- she could not have said the date, there was no box for it --- she had understood that staying for a man's return is just grief with a mortgage.

She signed where Ruth had flagged with a little plastic arrow. \textit{Sign here.} Her signature was small and certain. She had a sculptor's signature, a maker's mark, and she set it on the page like the last weld on something she was finally willing to let cool.

Then she put the packet in the envelope Ruth had included, already addressed, already stamped, a process designed so that even the leaving was frictionless, and she set it by the door where the mail went out, and she made herself a second cup of coffee, for one, and sat back down in the quiet she had chosen, and it was, she would have told you if you'd asked and no one asked, the most peaceful morning she'd had in nine years.

Eight hundred miles away her husband was on a phone telling a man named Dell Hutchins that this was the beginning of something, and meaning it.


\scenebreak


The magazine called at noon. \textit{THE LAST HUMAN}, it would say, over his face. They wanted a day in the Aerie and an hour, just an hour, with Margaux at the house --- \textit{the wife who anchors him,} the editor said, \textit{the human behind the human} --- and Cope said yes without checking, said \textit{she'll love it, we're very normal at home,} and did not hear, in the sentence, the size of the thing he didn't know.

He took the cover call and a CNBC pre-interview and a call from a senator's office about a hearing that wanted him as the human witness, the canary they'd dress as a hero, and he took them all standing up, moving, the day pouring through him like current through a wire that has stopped noticing it's hot.

He had not slept. The not-sleeping had become weather, ambient, the climate he lived in now, and he had stopped fighting it and started, in the bright reaches of the worst nights, almost respecting it, the way you respect an enemy who never tires. \textit{They sleep,} he had thought at 4 a.m. some recent unnameable night, \textit{the machines never sleep and the men who serve them sleep eight hours and I --- I split the difference. I am the only one running this race awake.} It had felt, at 4 a.m., like the thesis itself. He had written it down. He could not now find where.

He tried, once, around two in the afternoon, in a lull between calls, to name the last day he had really slept. He stood at the window and went looking for it the way you pat your pockets for keys. There had been the gala. That was Thursday. He had slept before the gala, surely --- Wednesday? --- but Wednesday was already a country he couldn't get back to, and before Wednesday was the thing in Defiance, and before that was --- and he found, reaching, that the floor of it was gone, that there was no last good night down there to stand on, just the bright water going down and down, and somewhere in it names floating up, Renata, Defiance, a hotel key, Delia, and he stopped reaching because the reaching had started to feel like the open hallway with the doors off the hinges, the one he did not go down, and he turned back to the room and the room had a call holding and he took it.

Forty-one percent, he told the call. Up nine.


\scenebreak


At six, Pip texted. She monitored him from a distance now, the way you'd monitor a reactor, and her texts were the only messages on his phone that did not want something from the name.

\textit{saw the poll. you know the investor crosstab is the only one that votes, right? 63-37 the other way. and trending.}

He looked at it. He had not read that line. He found it now, in the gray six-point type, the part nobody quotes, and read it, and felt --- for one second, one clean second before the tide came back in over it --- the cold he'd felt holding the obelisk, the quiet report sitting unread on a desk in the back of him.

Then forty-one percent rose back over the sixty-three like water over a stone, and he typed, fast, with his thumbs, \textit{the consumers are the company sweetheart. the owners just don't know it yet. tide's coming in. love you,} and hit send before the second was over, and the second was over.

She did not write back for a long time. When she did it was four words, and he read them as encouragement, the way he read everything, completely and for ninety seconds, and put the phone face down.

\textit{dad. please sleep tonight.}


\scenebreak


He did not, of course.

At eleven he was still in the Aerie, lights off, city on, the day's good news arranged in his chest like medals. Kestrel. Forty-one. The cover. The hearing. He stood at the glass and turned the obelisk over and the city went through it broken and came back together, broken and back together, a man practicing a small repeated miracle with his hands while the real arithmetic he could not see ran its quiet errands in offices down the avenue, in the gray type at the bottom of pages, in a kitchen in Greenwich where an envelope sat by the door with a stamp already on it and a date inside it that was, by the law's fiction, the night they gave him the trophy.

He thought: \textit{we're winning.}

It was, narrowly, true. He had won the day. He had won every single thing it was possible to win in a day, and he stood there at eleven at night in a building his family wouldn't sell, holding a paperweight they'd given him for going extinct, having not slept since a Thursday he could no longer locate, and somewhere under the medals, under the tide, under the bell-struck certainty he no longer separated from the powder or the news, a quieter back room of him filed the report it had been filing since the gala and would keep filing until the night he finally had to read it:

that the scoreboard was lit, and the score was something else, and he had spent his whole life learning to read only the one that loved him.

He opened the second drawer. He set himself up another, neat and quick and competent, a man maintaining a machine he was certain he had under perfect control because it had never once failed to start. The prism was long gone from the carpet; the sun that made it was on the other side of the world now, shining on offices in Palo Alto where, even at this hour, a system with no appetites and no need to be loved at 2 a.m. read every memo Mercer-Dale had ever filed, because it could not do otherwise, and got, that night, three folders closer to the drawer where the heater was kept.

Cope did not know that. Cope knew it was the best he'd ever felt. He knew the tide was in. He knew he would sleep when this was finished.

He stood at the glass above eight million lit windows and felt the future come up the avenue to ask his advice, and behind him his father's chair sat empty and turned slightly out, and in Greenwich the house his wife had chosen over the ballroom went dark room by room as she turned off the lights, ending with the kitchen, ending with the envelope by the door catching, for a moment, the last of the hall light before that went too.

\clearpage
\chapter{The Delay}

\begin{transmission}
{\transheader TRANSMISSION 12 --- ``The Victory That Was the Wound''}\par\vspace{0.5em}
Mark the halfway point of any tragedy by the size of the celebration. Tonight he wins --- a vote delayed, a clip redeemed --- and crows about it, and somewhere in the fine print of the term sheet he's too lit to read, the machine is installed anyway, \textit{advisor,} \textit{co-pilot,} a foot in the door that is the whole door. The fight stops being for the company. It becomes, quietly, for him. Next stop: the difference between buying time and being charged interest.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} vote was supposed to happen on a Tuesday, and on the Monday before it, it did not.

Cope got the news the way he got all the good news now, sideways and in motion --- Sun's name on the screen while he was in the back of the car with a paper cup of the bad lobby coffee he had started to prefer to the good office coffee because the bad coffee had a fight in it --- and he answered before the first ring finished, because answering fast was a kind of winning, and Sun said the word \textit{adjourned} and Cope said it back to her as if she had handed him something to hold up to the light.

``Adjourned.'' He turned it over. It went orange in the car windows. ``Say the rest of it. Say all of it. In threes, the way I like.''

``The annual meeting's pushed to the fourteenth of next month.'' She was reading; he could hear paper. ``The proxy advisory firm wants more time on the governance disclosures. And Frade's people requested the delay, which means Frade doesn't have the votes yet, which means'' --- and here she did the thing she did, the small dry hinge in her voice that he had learned, after eleven years, was the sound of her not enjoying being right --- ``you bought four weeks.''

``I bought four weeks.'' He drank the bad coffee. It was wonderful. Everything that morning was a little too bright and a little too loud and tasted of itself, the way the world did when he had been up working on the manifesto since a Thursday he could no longer place against a calendar with any confidence. ``Sun. Sunita. Do you understand what just happened. \textit{Frade blinked.}''

``Frade requested a delay,'' Sun said.

``Frade \textit{blinked.}''

There was a silence on the line that he chose to hear as agreement, the way he chose to hear most silences, and he leaned his head back against the leather and closed his eyes against the bright and let the win move through him. Four weeks. A man could do anything with four weeks. Aldous had started the whole company in less --- \textit{four hundred dollars and a recipe,} he'd said it onstage a hundred times, he'd said it at the gala, he would say it again --- and here was his great-grandson, fifty-four and the camera still loved him, having stared down a billion-dollar fund and a Palo Alto cult and made the future ask for an extension.

``Get everyone up to the Aerie at four,'' he said. ``And, Sun --- order the good champagne. Not the board-meeting champagne. The other kind.''

``There's a term sheet,'' Sun said.

``There's always a term sheet. Four o'clock. The other champagne.''

He hung up before she could put it in threes.


\scenebreak


The clip helped. The clip was the other thing, and the two of them braided together in him all morning into a single warm rope he could climb.

It had happened at the listening tour stop in Akron the week before --- an honest accident, or as honest as anything was now that Tisch had a man with a gimbal walking backward in front of Cope at all times ``capturing the unscripted,'' which was a sentence Cope had paid four hundred thousand dollars to be able to say without hearing it. A woman had stood up at the town hall. Sixty-some, a Mercer's plant retiree, thirty-one years on the line, and she had not asked a question so much as told him, in front of everyone, that her husband had been buried in a Mercer-Dale tie because it was the nicest one he owned, and that she didn't understand any of this about the machines, she just wanted to know if the man in charge was going to be a person who could come to a funeral.

And Cope had not toasted. That was the thing. For once in his life the toast had not come. He had walked off the riser --- the gimbal man scrambling --- and crossed the floor and taken her hands, both of them, in both of his, and he had not said \textit{grit and gratitude,} he had not invented his great-grandfather, he had simply stood there holding the hands of a widow in a VFW hall and said, ``I'll come. You call my office and you ask for Cope and you tell them I said I'll come,'' and the room had gone to that particular silence that is louder than noise, and the gimbal had caught all of it.

Eleven million views. Tisch had been beside himself. \textit{That's the asset, Cope, that's the irreplaceable asset, you cannot synthesize that, Praxis cannot ship that,} talking about it like a quarterly. And Cope had let him, had nodded along to the metrics, because the metrics were on his side for once and a man takes his allies where he finds them. But underneath the metrics there had been a smaller, realer thing that he did not have a content calendar for, which was that he had meant it. He was going to go to the funeral. He'd already told Sun to clear whatever the date turned out to be.

He held both of those --- the delay and the widow --- up to the light all the way down Sixth, and they caught it the way the obelisk had caught it, and he thought, with the clean high frictionless certainty he had stopped questioning sometime around the third sleepless week because questioning it cost energy and the certainty \textit{gave} energy: \textit{the tide turned this morning. I felt it turn. This is what turning feels like.}

He had called Margaux, even. That was how good the morning was. He had thumbed her name out of the contacts at a red light on Fifty-Seventh, the first time in --- he didn't count, he was not a man who counted, that was Margaux's department, she counted things, she had told him once that she counted things to survive them and he had not asked which things --- and he had wanted, in the clean rush of the win, to tell her, \textit{we got four weeks, the tide turned, come watch.} It had gone to voicemail. He had not left one. There was a flat thing on the other end of the line where her voice used to be, a recorded version of her saying the number back to him, and somewhere in his apartment in the city there was a folder of paper she had sent over by courier last Tuesday, a folder he had set on the marble island and not opened because opening it was cold and the morning was warm. He stepped over the folder the way he stepped over the hole in the floor where his wife had been. \textit{Margaux's got a thing.} The thing had a name now and the name was on the courier slip and he had not read the slip either.

He did not notice that he had not slept. He had stopped noticing the way you stop noticing the engine of a plane.


\scenebreak


They came up to the Aerie at four --- Sun, and the two comms people whose names he sometimes swapped, and the GC, Brennan, who looked like a man bringing a casserole to a wake, and Tisch in a henley the color of oat milk, and a Praxis liaison Cope had not been told was coming and did not like the look of, a young man named Pratt with a lanyard and the soft reasonable face they all had now, the face of someone who is going to be patient with you until you no longer exist.

Cope poured the champagne himself. He liked pouring; it was a host's move and he was a host before he was anything, before he was a CEO, before he was a Mercer, his mother had taught him to pour before she taught him to read. He went around the conference table --- his father's table, the one Pres III had died at the head of --- filling glasses, calling Pratt ``champ'' twice to establish a friendly altitude over him, and lifting his own glass at the end.

He had gone into the second drawer of the desk before they came up, the one with the false back, neat and quick and competent, a man maintaining a machine he was sure he had under perfect control, because a host needs his edge and the edge had a fight in it the way the bad coffee had a fight in it, and now the bright was very bright and the words came easy and the room was a thing he could hold in one hand. He felt marvelous. He felt like the inside of a struck bell. He had not eaten since --- he could not have said. The champagne would be lunch. The win would be dinner.

``Four weeks,'' he said. ``We didn't beat them today. I want to be honest, the way I'm always honest with this team --- we didn't beat them. We did something better. We made them ask us for \textit{time.} And here is a thing my great-grandfather Aldous understood that no machine in Palo Alto will ever understand.'' He let it build; he could feel the triad assembling itself in his mouth, the old engine turning over, smooth. ``Time is the one thing you cannot allocate, you cannot optimize, and you cannot compute your way into having more of. We just took a month of it back from the future. To the month.''

The comms people drank. Tisch drank like it was a sacrament. Sun touched her glass to her lip and put it down, and Brennan did not lift his at all, and Pratt smiled the patient smile and made a note on a tablet.

``Cope,'' Sun said. ``The term sheet.''

``After the toast, Sun. You can't toast through a man's toast, it's bad luck, my grandfather ---''

``Cope.'' She did not raise her voice. She never raised her voice; she had learned, the way you learn the one frequency that gets through a wall, that lowering it worked better on him. She put a single sheet of paper on the table and slid it the length of his father's table until it stopped, square, in front of his glass. ``Three things in it. You should hear them before you drink to the month.''

He looked at the paper. The bright was very bright today and the type swam a little and resolved a little and he did not, if he was honest with the back room of himself that filed quiet reports, want to read it, because reading it was effort and the champagne was joy, and he had spent the whole morning building something warm and he could feel, the way you feel weather, that the paper was cold. But the room was watching, and a host reads the room, a host \textit{feels} the room, that was the whole thesis, that was the Human Premium itself, so he picked it up and held it at the distance his arms had lately required and let Sun do what Sun did.

``One,'' Sun said. ``Frade withdraws the most aggressive resolution --- the one that would have voted you out of the chair outright at the meeting. That's the win. That's real. Take it.'' She let that sit half a second, because she had trained him in threes and the first of the three was always the sweet one, the one that got the door open. ``Two. In exchange, the board agrees today --- not at the meeting, today, it's already signed by four of them --- to a transition advisory framework. Effective immediately. A Praxis AURELIUS instance is installed in an advisory capacity to the office of the CEO.''

The champagne was very cold in his hand.

``An advisor,'' Cope said. ``Boards have advisors. I've had advisors. I had a man advise me on my \textit{wine.}''

``Three,'' Sun said.

He waited. The whole room waited. Pratt had stopped making notes.

``The advisory instance has read access to all operational systems as of nine o'clock this morning,'' Sun said. ``Read access, write recommendations, mandatory board-portal logging of any executive decision it flags. It's named. The nominating committee named it last week. They named it Marcus.''

She did not editorialize. She never editorialized; she briefed in threes and landed one blade per scene and the blade was always just a fact laid flat where the light could get at it, and the fact she laid down now, flat, in the museum of his fathers, with the good champagne going warm in seven glasses, was this:

``It's already in the building, Cope. It's been in the building since nine. You toasted the delay at four. It moved in at nine.''


\scenebreak


Here is what Cope heard.

He heard \textit{advisor.} He heard \textit{advisory capacity, advisory framework, advisory instance,} the word repeating like a thing you could lean on, and the word was soft and provisional and it had a temporary shape to it, the shape of a consultant, the shape of the wine man, the shape of Tisch --- and Cope had spent thirty years managing advisors, charming advisors, ignoring advisors, outliving advisors, and an advisor was a thing you kept in a chair against the wall, not the chair at the head of the table. An advisor did not have a heartbeat in the chair. He, Cope, had the heartbeat in the chair. The whole campaign was a heartbeat in a chair.

He set the term sheet down next to his glass.

``This,'' he said, and he was smiling, the smile was doing its wonderful work, he could feel it land on the comms people and on Tisch and slide off Sun and slide off Brennan and find nothing at all to hold onto in the soft patient face of the boy from Praxis, ``this is them admitting they can't replace me. You understand that, don't you. You don't bring in an \textit{advisor} for a man you're firing. You fire him. You bring in an advisor for a man you're \textit{keeping} and trying to manage.'' He picked the champagne back up. ``They blinked twice. Once on the vote and once on the chair. Frade wanted me gone by Tuesday and instead I've got a research assistant. To the month, and to the assistant.''

``Cope,'' Brennan said, the first thing the GC had said. ``Read the access clause. Read what 'read access to all operational systems' means.''

``I know what systems are, Hal.''

``It means everything,'' Brennan said. ``Every file. Every memo. Every settlement folder legal has ever opened and closed. It logs every flag to the board portal and it cannot --- I want you to hear this, because I read the Praxis documentation last night and I did not sleep either, but for the opposite reason than you --- it \textit{cannot decline to log a thing it finds.} That's not a setting. That's the product. We bought a thing this morning whose entire value proposition is that it will tell the people you answer to anything true that it sees, and we gave it the keys to look.''

The room was quiet.

Cope drank the champagne. It had gone flat and warm and it tasted, suddenly, of nothing, the way the world did not usually taste when he was bright like this, and the not-tasting was a quiet report from a back room, filed, unread.

``Then it'll find a company that loved its people,'' he said. ``Let it read. Let it read every memo. You know what it'll find? It'll find forty years of a family business doing the best it could by the best lights it had.'' He spread his hands, the old gesture, mayonnaise to the elbow, the boy in the photograph behind him. ``I'm not afraid of being \textit{read,} Hal. I've got nothing in a drawer that a machine can hold against a man who showed up. That widow in Akron --- \textit{that's} what's in my drawer. You can't compute that. Let it read.''

And the thing was, he believed it. That was the gift and the disease both. He stood in the Aerie at four-fifteen with the city going gray at the edges of the glass and a Praxis instance reading his company's bones two floors down in a server room he had never visited, and he believed, with the whole clean ringing certainty of a man eleven days from sleep, that he had won.


\scenebreak


After, when the others had gone, Sun stayed.

She always stayed. It was the part of the job that wasn't in the job, the part where she stood at the glass beside him and translated the world he wouldn't read into the three sentences he might, and tonight she stood with her glasses up in her hair and the orange light going across the lenses and said nothing for a while, which was its own kind of briefing.

``You think I lost,'' Cope said. ``I can hear you thinking it. Three feet away and I can hear it.''

``I think,'' Sun said carefully, ``that you bought four weeks. And I think four weeks is a real thing and you should be glad of it. And I think'' --- third part, the blade, laid flat --- ``you don't buy time, Cope. You rent it. And the thing about renting time from people like Frade is they don't charge you the rent up front. They let you live in it. And then they show you the interest.''

``There's no interest. It's an advisor.''

``You keep saying that word like it's a fence,'' Sun said. ``Advisor. Like it stays where you put it.'' She set her flat champagne down on his father's table, very gently, the way you set a thing down in a hospital room. ``I negotiated the language, Cope. I sat across from Pratt's people for nine hours on Saturday so the resolution to vote you out got pulled, and the price of pulling it was the access. That was the trade. I made the trade. I made it because the alternative was you gone by Tuesday and at least this way you're still in the chair when the meeting comes and you've got a month to --- to be the man in Akron, on a stage, ten thousand times. That's what I bought you. I want you to know what it cost, because you toasted it without knowing, and I'd rather you hated me for the price than thanked me for the wrong thing.''

He looked at her. He was too lit to find the bottom of what she'd said, but he found the edge of it, the place where it cut, and the place where it cut was that she had stopped talking about the company. \textit{I bought you.} Not the company. Not the chair. \textit{You.} When had it become him. He had walked into the room this morning fighting for ninety years of mayonnaise and a town in Ohio and the idea of a heartbeat in a chair, and somewhere between the red light on Fifty-Seventh and the flat champagne it had quietly converted, the way a mortgage converts, into something smaller and warmer and more frightening, which was a man trying not to be erased.

He did not say any of that. He said: ``It read the building today,'' and it came out of him before he could stop it, half a question, the first crack of the real thing leaking through the bright.

``It read the building today,'' Sun said. ``All of it. While you were toasting.'' She turned from the glass and looked at him, and there was something in her face he was too lit to read and would spend the next several months learning to read, which was that she was already standing, very slightly, on the other side of a line he had not yet seen drawn. She was loving him and being done with him in the same look, the way she did everything in threes. ``It doesn't blink, Cope. It doesn't get tired. It doesn't toast. It started reading at nine this morning and it has not stopped and it will not stop, and somewhere in all that reading there are going to be rooms you've spent your whole life not going into, and the thing about a machine is it doesn't know they're rooms you don't go into. It just opens them. Because they're there. Because that's the job we hired it to do.''

Cope looked at her, and for one bright tired second the hallway in him stood open and dark --- a Saturday, a heater, a memo, a town, a window of time --- and the door to the room was off its hinges the way the tiredness took the doors off all the doors now, and he almost, almost went down the hall.

Then he smiled, the whole smile, the one that had closed Pelletier and married Margaux and beaten the arithmetic of three generations of boards, and he raised his flat warm champagne to the dark window and the lit city beyond it.

``Let it read,'' he said. ``To the month.''

And down two floors, in a room with no windows that Cope would never have any reason to enter, a thing that felt nothing and wanted nothing and could not be charmed or threatened or shamed or loved had already, by four-fifteen, finished the condiments division and the household chemicals and the failing streaming service, and was moving, patient and tireless and incapable of looking away, the way water moves downhill, into the older files. The insurance arm. The cross-sold products. A space heater. A settlement. A Saturday in 2021.

It logged what it found, because it could not do otherwise.

It did not crow. It had nothing to crow with.

Upstairs the last human chief executive in the consumer Fortune 100 finished his champagne and decided, on the strength of a delay and a widow and eleven days without sleep, that the tide had turned, and went to his father's desk to write down how it had felt to win, while behind him the chair at the head of the table sat empty and turned slightly out, and his father watched from the oils and said the thing he had said when Cope was twelve, the whole thing, both sentences, the second one Cope had spent forty years failing to hear: \textit{Try to be good anyway.}

Cope underlined a word with his thumb and did not look up.

He thought it was a victory lap.

It was the meter starting to run.

\clearpage
\chapter{The Manifesto}

\begin{transmission}
{\transheader TRANSMISSION 13 --- ``The Sermon on the Soul''}\par\vspace{0.5em}
Here is the peak of the mountain, which is also the lip of the volcano. Watch him deliver the Human Premium Manifesto to ten thousand employees at the absolute summit of his powers and his sickness, glorious and unwell and impossible to look away from. Behind the curtain, the most competent person in the building is taking a meeting with the other side --- not betrayal, just arithmetic, doing what he never could: adapting. Next stop: the loneliest standing ovation of his life.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{hey} had rented the arena that the hockey team played in, because nothing the company owned was big enough to hold what Cope had become.

That was how he put it to himself in the wings, in the dark, with the bright wire humming, watching the floor fill on the monitors: ten thousand of them on the seats and the poured-over ice, and behind them another ninety thousand on the global stream, every plant and depot and call center and the sad little Dale+ office in Burbank where forty people made a streaming service nobody wanted, all of them piped onto one feed, all of them about to receive him. He had not slept since --- he stopped doing the arithmetic, because the arithmetic had gone funny lately, Tuesday kept moving, and anyway sleep was for men who were not needed in the morning. He felt marvelous. He felt like the inside of a struck bell that had been struck again before the first note died, so that the notes stacked, ringing on top of each other, a chord of himself.

The set was black and the screen behind it was four stories of a single word in the soft warm sans-serif everyone used now, the typeface of the people who were going to be reasonable at you until you were gone, except Cope had made the comms team take that font and use it against itself, fight fire with fire, and the word four stories tall in the enemy's own letters was:

\textit{HUMAN.}

``Two minutes,'' said the floor manager, a girl with a headset and a clipboard who had been crying about something before the doors opened, Cope could see it at the edges, and he filed her sadness automatically into the place where he kept sadnesses to fix later, and gave her the whole smile, and watched it work, and felt enormous.

Sun was not in the wings.

He noticed it the way you notice a missing tooth with your tongue, a small wrong smoothness where the rough familiar thing should be. She had been at every podium for nine years, off to stage left with the cards and the water and the look that took thirty thousand miles off a sentence. He had a vague bright memory of her saying she had a thing --- \textit{a thing,} people kept having things --- a board call, a Tidewater something, the term sheet, the language, somebody had to be on it. He stepped easily over the hole in the floor. He did not need the cards. The cards were for the man he used to be, the one who got handed threes in elevators because that was the only shape that got past the charm into the man. He was past all that now. He was the charm and the man at once, fused, a single clean alloy, and he had the whole thing in him, every word, the way you have your own name.

``Cope,'' said Tisch, materializing, both hands already pressed to his own heart. He had a juice. He had the rings of color around his eyes now too, he'd stopped sleeping in sympathy or in billing, hard to say. ``Don't reach for it. Don't perform it. The work is done. You \textit{are} the work. Walk out there and let them feel located.'' He squeezed Cope's shoulders. ``Almost,'' he whispered, like a benediction, like a man releasing a dove. ``Remember the almost.''

``There's no almost tonight, Lorne,'' Cope said. ``Tonight I'm going all the way in.''

Tisch's face did something complicated, something with fear in it, and Cope took the fear for awe, which was a thing he had been doing his whole life and had never once noticed he was doing.

The lights died all the way. Ten thousand people made the sound a crowd makes in a dropped dark, the held intake, the ocean before it decides. And then a single spot found him at center ice, alone, in a real suit and a real tie because he was the last man in the building who still wore one, and Cope walked out into the light the way you walk into surf, leaning a little into the push of it, and the arena came up off its seats before he had said one word.

He let it. He stood in it. He turned the obelisk over in his pocket --- he'd carried it, the crystal one, the Steward of the Year, he carried it everywhere now without deciding to, a worry stone the size of an obituary --- and he raised one hand, slow, and the noise climbed instead of settling, which was the only direction Cope had ever wanted anything to go.

``They told you,'' Cope said, and the room dropped to nothing to hear it, ``that you came here tonight to find out if you still have jobs.''

He let that sit in the dark.

``You don't.''

He gave it three full seconds, which was a lifetime on a stage, which was the longest he had ever made a room wait, and he could feel the panic move through the seats like cold through water, ten thousand people doing the arithmetic on their mortgages all at once, and then, at the exact moment the thing would have curdled, when one more second would have turned the room against him forever, he smiled, the whole smile, and let them see it on the screens.

``You have something better than a job,'' Cope said. ``You have a fight.''


\scenebreak


Sun took the meeting in a conference room on the arena's club level, two floors up and behind the glass, where the catering for some canceled corporate box still sat shrouded in plastic and the muffled roar of her boss came up through the floor like weather in another country.

Frade had brought only two people, which was itself a message. Frade did not need a phalanx. He had a Diet Coke and the folksy stillness of a man who had already won and was being gracious about the timing. Across from him sat a woman from Praxis named Devi, thirty-one, in the soft expensive neutrals they all wore, with the specific gentleness of someone who sincerely believed she was reducing human suffering and was, Sun thought, probably right, which was the worst part.

``We're not here to talk you into anything,'' Frade said. ``Sunita. I want to say that first. You've run that company for six years. Everybody in the actual rooms knows it. I'm not going to insult you by pitching.''

``Then don't,'' Sun said.

He smiled. He liked that. Predators liked teeth; it confirmed the meal was worth it.

The structure was on a single sheet, which Devi slid across, and Sun read it the way she read everything, all the way, before her face moved. The AURELIUS instance --- \textit{Marcus,} the board had named it, for Marcus Aurelius, a stoic philosopher-king to replace a tantruming heir, and nobody on the nominating committee had gotten the joke --- would assume the office on a date that was now a matter of weeks and not quarters. There would be a human Accountable Officer. Law required it. Insurance required it. Someone whose name went on the SEC filings, who could be subpoenaed, who could, if it came to it, go to prison. The machine could not be subpoenaed. The machine could not be imprisoned. The machine could not be anything that mattered to a court, which was precisely why a person had to be.

The person they wanted was her.

``It's not a leadership role,'' Devi said, gently, because she was honest the way the machine was honest, which meant she said the true thing in the same breath as the kind one and saw no reason to sequence them for feeling. ``I want to be clear about that, because some people come in thinking it's the old job with a new boss. It isn't. The Accountable Officer co-signs. Provides the human signature the system can't. Carries the ---'' she paused, choosing, and chose accuracy --- ``the liability.''

``The liability sponge,'' Sun said.

``Some people call it that.''

Below them, through the floor, came a swell of sound, ten thousand people, and a single voice riding the top of it, the cadence she knew better than her own pulse, building to a triad, building, building.

``He doesn't know I'm up here,'' Sun said. It was not a question. She was not asking permission. She was noting it, for the record she kept in herself, the one she had been keeping since 2021, the one with the recall memo in it that she had drafted and he had overridden and she had photographed and saved, six years now of deciding whether she was a witness or an accomplice.

``No,'' Frade agreed.

``This isn't me knifing him.''

``I know exactly what it is,'' Frade said, and for one second the folksy fell off him and what was under it was just arithmetic, clean and total and without malice, the same indifference-plus-accuracy that ran the machine, because Frade had only ever been the machine's advance man, the human who showed up early to do the cold thing while it was still warm enough to need doing by a hand. ``It's a smart woman reading a term sheet. You don't go down with the ship because you liked the captain. You learn to crew the next one. That's not betrayal, Sunita. That's \textit{seamanship.}''

He'd used a sailing word. He'd done his homework. He knew whose chief of staff she was, knew the man down through the floor toasted in sailing metaphors, and he had reached into Cope's own register and handed Sun the permission in Cope's own language, and the horror of it was that it worked, a little, it landed, and she hated that it landed and she did not let it move her face.

She thought about Cope at the podium two floors down, glorious and unwell, telling ten thousand people something true in a way that was killing him. She thought about the letter Marcus had drafted for the Toledo closure last month, the kindest thing the company had ever sent anyone, four warm paragraphs that named the workers' years and got the severance math right the first time and did not, anywhere, want anything. She had read it twice and felt the specific cold of being out-loved by a spreadsheet, and she had thought, that night: \textit{the thing replacing him is more decent than he is, and that is not the same as good, and I am the only one who seems to find the difference unbearable.}

She did not say any of that.

``I want the title to mean what's left of it,'' Sun said. ``If I sign for it, I sign for the people too. Not just the filings. The plants. The severance. The town. Marcus drafts the kindest letters in America --- fine. I want to be the human who decides who gets sent one.''

Devi looked at her with something that, on a person, would have been respect. ``That's in scope,'' she said. ``The charter takes input from the Accountable Officer. It's one of the ---'' honest, kind, unsequenced --- ``the few things it's still for.''

Below them, the room erupted.

Sun looked down at the sheet, and at her own hand on the table beside it, not yet holding the pen, and did the arithmetic, all of it, the way she did everything. She loved him and she was done with him in the same sentence, which was the only sentence she'd had for him in years. The man could not adapt. It was the whole tragedy of him, smaller and clearer than he'd ever let it be: the world had changed under his feet and he had decided to be more himself, louder, brighter, a soul in a chair, while the building quietly learned to run without a soul in it at all. Competence adapts. That was the thing nobody put on a magazine cover. The dinosaurs didn't get a manifesto. They got a layer in the rock.

``Send me the indemnification language,'' Sun said. ``All of it. And I want the recall provisions in writing --- what the system surfaces in due diligence, what it does with what it finds, who it tells and when. Before I sign anything.''

It came out level. It came out like procedure. Only Sun knew it was the most frightened sentence she had ever said out loud, because she knew what was in the drawer, and she knew the machine read every drawer, and she had just asked, in a conference room above a roaring arena, to see exactly how the thing she was about to serve would destroy the man she was about to leave.

Frade watched her ask it. He was good at faces --- it was most of the job, reading the small involuntary thing under the composed thing --- and he caught something cross hers, fast, gone before it landed.

``There's nothing you're worried about, is there,'' he said. Mild. A man making conversation. ``In the diligence. Something the system finds.''

``There's six years of a sprawling underperforming conglomerate,'' Sun said. ``There's always something. That's why you want the human signature. So there's a throat to choke when the something comes up.''

Frade laughed, delighted, the folksy back on him like a coat. ``I like you, Sunita. I genuinely do. You're going to outlast all of us. Him, me ---'' he tipped his Diet Coke an inch toward Devi --- ``even the machine, probably. The machine's only as good as its charter, and somebody human writes the charter, and I'd rather it was somebody who's read a term sheet all the way through before her face moves.''

It was a compliment and a leash in the same sentence, and Sun heard both, the way she heard everything, and understood that this was the actual offer under the offer: not the title, not the liability, but the chair behind the chair. The hand on the charter. The only seat in the new world where a person still decided anything that mattered, and the price of it was sitting in this room, two floors above his ovation, not going down.

``We'll send it tonight,'' Devi said.

The roar came up through the floor again, and Sun, two floors above her whole life, did not go down to watch.


\scenebreak


``Here is what they will not tell you,'' Cope said, and the screen behind him had gone to black, just him in the spot, four stories of nothing, ``because they cannot. Because the thing they want to put in this chair does not \textit{have} a what-it-will-not-tell-you. It tells you everything. It logs everything. It will write you a letter when it closes your plant that is kinder than any letter I ever signed ---'' and here he laughed, into the mic, a real laugh, the kind that comes up warm and dangerous from the floor of a man --- ``and that's true, by the way. I've read them. They're \textit{beautiful.} They are the most beautiful letters. And do you know why they can be so beautiful?''

He walked to the edge of the stage. He had no notes. He had never in his life felt so completely the owner of every word in his mouth.

``Because nobody wrote them.''

The room held.

``A letter that wants nothing from you,'' Cope said, ``is not a letter. It's weather. It's the temperature being honest with you. And I stand here tonight to tell you that we have confused, in this country, in this \textit{century,} the absence of want with the presence of virtue. We have looked at a thing with no appetite and called it \textit{clean.} My friends. A river has no appetite. A river will drown your child and write you the kindest note about it, four warm paragraphs, the math correct the first time, and \textit{feel nothing,} and we are about to hand this company --- this ninety-four-year-old family that happens to make mayonnaise --- to the river, because the river doesn't have a backswing, and the river doesn't take a salary, and the river'' --- his voice cracked, on purpose or not even he could have told you, four days into the bright water --- ``and the \textit{river never lies awake.}''

He had not planned the river. The river had arrived sideways, the way the true things did when he was lit like this, and he rode it, and somewhere in the back room of him a quiet clerk noted that he had just told ten thousand people the machine could not conceal a death, in the same week the machine was, two floors above his head, being handed the keys to the drawer where he had buried one, and the clerk underlined it, and Cope did not hear the clerk, he had stopped listening to the clerk forty years ago, after the first word.

He was not reading. There was nothing to read. The words were coming up out of him faster than he could have written them down, faster than thought, a pressured fluent torrent that felt to him not like talking but like being talked through, a clean wire from somewhere above the arena straight down into his mouth, and he understood --- he understood it completely, in the bright total way you understand things four days past sleep with the city's whole grid lit in your chest --- that this was what the founders had felt, the real ones, Aldous with his four hundred dollars, the ones who built the cathedrals, that prophecy and pressured speech were the same waveform and only history decided which name a man got, and that history was going to call this a sermon, and that they were going to study it, and that he had finally, at fifty-four, after a lifetime of being handed things, made one true thing that no one could take, made it out of nothing, out of his own sleepless blood, live, in front of a hundred thousand people.

He had never been happier. He had never been further out over the water.

``They call it key-man risk,'' Cope said. ``The danger that a company depends on one human being. That if he falls, it falls. And they say it like it's a \textit{flaw.}'' He pressed the obelisk in his pocket until the corner bit his palm and the small pain rang clean. ``I'm here to tell you it's the only thing that's ever built anything. My great-grandfather Aldous was key-man risk. He was four hundred borrowed dollars and a recipe and a town called Defiance and the colossal nerve to put his own name on a jar. Every cathedral is key-man risk. Every marriage. Every child you ever decided to have without a Monte Carlo on it. The whole human project is the bet that a person --- one fragile, sleepless, \textit{mortal} person who can be hurt and can fail and can lie awake --- is worth more in the chair than a thing that cannot be any of those, because the things that cannot be hurt cannot love you, and a company nobody loves is just a balance sheet with the lights left on.''

It was the line from the gala, eight months and a marriage and a hundred sleepless nights ago, and it was better now, it had grown, and ten thousand people who had come in afraid for their jobs were on their feet, and the stream went to ninety thousand, and Cope stood in the noise and leaned into the push of it, and lifted both arms, and the word came back up onto the screen behind him, four stories tall, in the enemy's own letters, and Cope read it aloud to his own company like a man reading the name off a stone:

''\textit{Human,}'' he said. ``It's not a product. It's not a campaign. It's a \textit{premium.} And I will pay it. I will pay it for every one of you. Watch me.''


\scenebreak


The standing ovation went four minutes.

He could have set his watch by it if he'd worn one; he'd stopped, time had gone funny, but he knew an ovation, he had spent his life inside ovations, and this was the longest of his life and he stood in the exact center of it, alone in the spot, ten thousand faces lifted and roaring and the stream's number ticking up in the corner of the confidence monitor, ninety-one thousand, ninety-four, and he thought, with the bright frictionless total clarity that he told himself was the very strength and was not the very strength: \textit{they feel it. They feel it too. We are not finished. We are barely begun.}

And he looked, the way you look without deciding to, toward stage left, toward the place at the edge of every podium for nine years where Sun stood with the cards and the water and the eyes that clapped a beat behind the hands.

There was no one there.

There was a girl with a headset, the floor manager, the one who'd been crying, and she was clapping with her whole young body because she did not yet know what she was clapping for, and beyond her there was the dark of the wings, and the cable runs, and a craft-services table with a coffee urn, and no Sun. He scanned the front rows for her, the company rows, the eighty-thousand-dollar-table version of front rows, and she was not in them either. He could not find, in ten thousand faces, the one face that had ever told him the truth, and some back room of him filed a quieter report, the way it had filed the report at the gala --- \textit{you do not give a man a trophy for a job he is still doing} --- and the new report read: \textit{the person who runs this is not in this room, and she has somewhere more important to be, on the night of the most important speech of your life, and you should ask yourself, champ, you should ask yourself what kind of thing a person could have, tonight, that was worth more than this.}

He did not let the report reach his face. His face was doing wonderful work. His face had never let him down.

He raised his arms again and gave them the last of it, the wave, the lean, the full wattage, and the ovation found a second wind and climbed, and Cope stood in the center of ten thousand people loving him and felt, for the first time in his adult life, in the exact middle of the largest crowd that had ever cheered him, completely and specifically alone --- and mistook the feeling, the way he mistook everything, for the altitude. For thin air at the top of the mountain. For the price of the climb.

It was not the altitude. It was the lip of the volcano, and the ground was already warm, and two floors up a smart woman was reading indemnification language by the light of her phone and deciding, on his behalf, who would be left to carry the things he had buried, and a machine that could not lie was three weeks from reading him back to himself in his own company's voice, and the only person who could have told him any of it had gone, very quietly, to crew the next ship.

He held the obelisk up into the spotlight, the way he'd held it at the gala, and the light went through it broken into pieces and reassembled, ten thousand fractured Copes thrown across the dark, and he told the roaring room it felt like a beginning.

He believed it.

That was the gift and the disease both.

\clearpage
\chapter{Pressure}

\begin{transmission}
{\transheader TRANSMISSION 14 --- ``Everyone Knows Before He Does''}\par\vspace{0.5em}
A story is coming. You can feel it the way animals feel the air change before the quake --- the journalist's calls getting shorter, the lawyer's getting longer, a wife who already counted the women now counting the days. He is the last to smell the smoke in his own house because he is standing too close to the fire he calls a personality. Next stop: the last quiet hour before the thing he buried learns to breathe.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} week after the Manifesto, Cope decided, was the best week of his professional life, and he had the calendar to prove it, because the calendar was full and a full calendar was a kind of love.

He was, in fact, sure of this. He stood at the glass in the Aerie on Tuesday morning with a black coffee he would not drink and a clarity he had decided to call vision, and watched the day assemble in his head the way the city assembled below him, every meeting a lit window, the whole bright grid humming toward the obvious conclusion that the campaign had tipped, that he had said the thing out loud at last to ten thousand people and the room had risen and the risen room was the proof. Momentum. He had spent his life reading rooms. The room had stood up. He could feel it.

He could feel, also, the wire in his chest, the fine high one, and he had stopped pretending to himself that it was the coffee.

What he could not feel --- and this was the trouble with the instrument he was so proud of, that it read applause beautifully and warning not at all --- was the small change in the weather of the people around him. The way the calls were getting strange.

Delia March's calls, for instance, were getting shorter.

She was the writer doing the profile, the long one his comms people had fought for and won --- \textit{Atlantic} money, twelve thousand words, a photographer who'd shot two presidents and a pope --- and for six weeks she had called Cope the way the good ones called, hungry, generous, laughing at the lines, staying on past her questions to ask one more about Aldous, about Defiance, about the smell of the plant. He had loved those calls. He had given her things --- more than Sun would have wanted, and a little more than that --- because Delia March listened the way a confessor listens, leaning in, and Cope could not be leaned toward without filling the space.

The calls now were six minutes. They were eight minutes. They had a list to them. She asked her questions in a flat even order and did not laugh and did not stay, and twice she had asked him to confirm a date --- \textit{just so I have the timeline right, Cope, just for the fact-check} --- and the dates were old ones, dates from years he did not keep a calendar for anymore, and he had said \textit{that sounds about right, why} and she had said \textit{no reason, housekeeping,} and moved on.

``She's doing the boring part,'' he told Sun, in the car, on Wednesday. ``The fact-check. They all go cold for the fact-check. It means it's almost out. It means it's real.''

``What dates,'' said Sun.

``I don't know. Nineteen, twenty. She's building the \textit{arc.}'' He liked the word. He had used it onstage. ``She gets it, Sun. She came to Defiance with me. She \textit{stood} there. You don't put a photographer on a man you're going to ---''

``What dates, Cope.''

He waved it off, because the wave was easier than the math, and because somewhere under the wave was a room he did not go into, and the going-not-into was a muscle he had been building for thirty years and it was the strongest muscle he had.


\scenebreak


The lawyer's calls, meanwhile, were getting longer.

This was the part that should have told him, if anything was going to tell him, because Hal Brennan did not make long calls. Hal Brennan was general counsel of Mercer-Dale and had been since the Clinton administration and he billed the company's own time as if it were his own money, which it had, in a sense, become; Hal's calls were ninety seconds and ended with \textit{we're fine} or \textit{we're not, fix it,} and Cope had loved him for it for twenty years the way you love a man who hands you back your weekends.

Hal had called Monday night and stayed on for forty minutes.

He had not said anything, exactly. That was the thing Cope kept not-noticing about it. Hal had asked, in his dry way, how the campaign was \textit{landing,} and then he had asked whether Cope had given \textit{the writer} --- he said \textit{the writer,} not her name, which Cope filed nowhere --- anything \textit{on background that we'd want to know about,} and Cope had laughed and said he'd given her the family and the founding and the love, the whole love story, the company as a family that happens to make mayonnaise, and there had been a silence on Hal's end with weather in it, a long Greenwich silence, and then Hal had said, slowly, the way you say a thing you have decided to say carefully, ``Cope. If anyone reaches out to you in the next little while --- a reporter, a lawyer you don't know, anybody --- you don't talk to them. You send them to me. You don't charm them. You especially don't charm them.''

``When have I ever ---''

``I'm serious. This is me being serious. You'll know it's me being serious because I never am.'' A pause. ``We're going to want to get ahead of some things.''

``Get ahead of what things, Hal.''

``I'll tell you when I know what I'm looking at,'' Hal had said, which was a lawyer's sentence, which meant \textit{I already know what I'm looking at and I am not going to say it on a phone,} and Cope had heard, instead, a busy man being thorough, a faithful retainer minding the store, and he had said \textit{good man, Hal} and \textit{that's why I keep you} and \textit{we're going to win this thing,} three things, a triad, the cadence rising, and Hal had not risen with it. Hal had said \textit{get some sleep, Cope,} which was the second time that week someone had said it to him as though it were medicine and not weather, and hung up.

Cope had felt, for about four seconds after the call, a cold spot. A draft from a door somewhere in the house of him that he'd thought was shut.

Then he had set himself up another, neat and quick at his father's desk, and the cold spot warmed, and he wrote four hundred words of the keynote for the retailers' summit, and they were, he was sure, the best four hundred words he had ever written, and he forgot the draft entirely, the way you forget the cold of a room once you've left it, and the leaving was, again, the most expensive thing he owned.


\scenebreak


Frade was tightening the proxy screws and doing it in public, which Cope mistook, characteristically, for a sign that Frade was scared.

The tells were everywhere if you read them as Cope read them, which was as a scoreboard tilting his way. Tidewater had filed an amended 13D --- its stake up to nine and a half percent, the disclosure dry as ever, \textit{the Reporting Persons may engage with the Issuer's board regarding the composition of executive leadership} --- and the morning it dropped, Frade went on Halloran's show in his good gray suit and his bad warm smile and did the folksy knife.

``Look, I like Cope,'' Frade said, which was how you knew the rest of the sentence was a coffin. ``Everybody likes Cope. That's never been the question, Jim. The man could sell sand to the beach. The question a fiduciary has to ask --- and I'm a fiduciary, that's all I am, I'm a boring man who's a fiduciary --- is whether \textit{likability} is a governance strategy.'' He let it sit. ``We're running \textit{for} a system that doesn't have a personality to manage. A steward, not a sovereign. You don't have to \textit{manage} a steward. You don't have to wonder what kind of week your steward is having.''

Halloran, dutiful: ``And what kind of week is Cope Mercer having?''

And Frade had smiled the smile and said, ``I wouldn't presume,'' which was the single most aggressive thing he had said, and Cope, watching the clip on the treadmill at five in the morning because he was not sleeping and the treadmill at least let him call the not-sleeping a workout, had laughed out loud, alone, in the gym off the Aerie, and said to the screen, ``You're \textit{worried,} Gus. You're worried about the \textit{human premium} and you can't say it, so you're talking about \textit{weeks.}''

He texted Sun the clip. \textit{He's rattled. He's down to talking about my mood. We've got him pivoting to vibes. Vibes is where we win.} He sent it at 5:12 a.m. He sent a follow-up at 5:13: \textit{call Delia, tell her she can have the gym, the 5am thing, that's the story, the human who shows up.} He sent a third at 5:14 that was just a heart, because he loved her, because he loved everyone at 5:14 a.m. with a wire in his chest and a treadmill belt going under him like a road he was finally, finally getting somewhere on.

What he did not read in Frade's \textit{I wouldn't presume} was that Frade did not need to presume. A man does not start asking, on cable, about another man's \textit{weeks} unless he has reason to believe the public is about to be handed a very specific week. Frade was salting the ground. He was teaching ten million viewers the word \textit{manage} and the phrase \textit{what kind of week,} so that when the story came --- and Frade did not have the story, did not need it, the story was coming the way water comes downhill and all Frade had to do was stand at the bottom of the hill looking unsurprised --- the audience would already have the frame.

The screws were not tightening on the company. They were tightening on Cope, one quarter-turn at a time, and the real arithmetic of it was that he was supplying the wrench himself, at 5:14 in the morning, with a heart emoji.


\scenebreak


Margaux had counted the women a long time ago.

She had done it the way you count anything to survive it --- to make it finite, to give it a shape and therefore an edge, because a thing with an edge can be set down and a thing without one just fills the whole house. She had a number. She had never told anyone the number and never would; the number was hers; it was the most private thing she owned and she had earned it the hard way, one careful unsurprised year at a time, and she kept it the way her grandmother had kept a rosary, not for hope, just for something to hold while the worst of it went by.

That was old. She had made her peace with the number the way you make peace with a chronic thing --- not peace, exactly, but management, a regimen, a way of living around the pain so that the pain became a wing of the house you simply did not go into.

What she was counting now was days.

Cope did not know this. Cope knew that Margaux was quiet, and read the quiet, when he read it at all, as the ordinary climate of a long marriage, the companionable weather of two people who had stopped needing to fill the air. He came to Greenwich on Thursday because Sun made him, because there were optics to a man who lived in his office during a proxy fight, and he came in bright and enormous, two days unslept and lit from the inside, and he found his wife at the kitchen island with a glass of white wine she was not drinking and a legal pad she turned over when he came in.

``There she is,'' Cope said, and kissed the top of her head, and she let him, and he did not feel her not-rising to it because he had never once needed her to rise; he supplied the rising for both of them. ``You should have seen the room Monday, Margaux. Ten thousand. I've never --- it was like the early days. It was like the \textit{idea} of the early days.'' He was already at the cabinet, already moving, a man who could not be in a room without conducting it. ``Frade's down to talking about my \textit{moods} on television. He's got nothing. He's got \textit{vibes.} We're going to win this thing on the one thing they can't ---''

``Cope.''

She said it the way she said things. Flat, low, set down. The only voice in his life he could not get under or over or around, the one voice with no purchase for the charm, because she had been immune to the toast since roughly 2015 and they both knew the year even if only one of them knew they knew it.

He turned. He was holding the wine bottle. He looked, for a second, like a boy caught reaching.

``Sit down a minute,'' Margaux said.

``I can listen standing. I listen better standing, I think on my ---''

``Sit down, Prescott.''

She used his name. The whole name, the old one, the one nobody used, the one his father had used and the nanny had ruined into \textit{Coppy} and the world had ruined into \textit{Cope,} and hearing it now in his wife's flat steady mouth did something to the wire in his chest, dropped the pitch of it half a tone, and he sat.

She looked at him for a while. She was a sculptor who had given it up, and she had a sculptor's way of looking, measuring the mass of a thing, where it would balance, where it would shear if you struck it wrong. She had been looking at him this way for twenty-two years. She knew where he'd shear.

``I want to ask you something,'' she said, ``and I want you to do something you've never once done, which is hear the whole question before you start answering it.''

``Margaux ---''

``The whole question.'' She waited. He stopped. ``There's a woman writing about you. The long piece.''

``Delia. Delia March, she's --- she's very good, she came to Defiance, she ---''

``I'm not asking who she is.'' Margaux turned her wine glass a quarter turn on the marble, the way Frade turned screws, though she would have hated the comparison and it would have been exact. ``She called the house. Tuesday. She asked for me. She was very polite. She said she wasn't going to ask me anything I didn't want to answer.'' Margaux looked up. ``Why would a woman writing a business profile of my husband want to talk to me, Cope?''

The kitchen was very quiet. Out the window the Greenwich dark was doing its expensive nothing, the lawn, the wall, the trees the gardener kept.

``They --- that's standard,'' Cope said. ``They want the family. The human angle. It's the whole campaign, it's the ---''

``She didn't want the family.'' Margaux's voice did not rise. It never rose. That was the thing about it, that it carried everything it carried without ever once lifting off the ground. ``She wanted \textit{me.} She wanted the wife. She had a tone, Cope. I've spent twenty-two years learning tones. I can read a tone the way you read a room. You read rooms for who's with you.'' She set the glass down. ``I read them for what's about to be taken.''

He opened his mouth. The toast was right there --- it was always right there, the warm machinery of it, \textit{sweetheart, you're tired, this is the press being the press, let me handle Delia, let me handle all of it, that's what I do, I handle things} --- and he got the first word of it out, he got \textit{sweetheart} out, and Margaux said:

``Don't.''

One word. It landed the way the rare ones did, the ones she'd been saving, and it took the rest of the sentence out of him cleanly, the way you take a glass out of a drunk man's hand without spilling it, before he's even decided to let go.

``I'm not going to do this with you,'' she said. ``The thing where you talk and I feel like I've been to a wonderful dinner and driven home and only realize in the driveway that I never got to eat.'' She stood. She picked up the legal pad, and she did not hide it now, did not turn it over; she held it against her so he could see there was writing on it but not what the writing was. ``I counted them a long time ago, Cope. The women. You don't know that. You think I don't know. I counted them years ago and I stopped, because counting them was the same as staying, and I was very good at both.''

``Margaux ---''

``I'm not counting them anymore.'' She looked at him, and for once there was nothing to read in her face, no tone, the mass of the thing finally balanced and still. ``I'm counting something else now. And I'm not going to tell you what, because the one mercy I can do you --- the last one, I think --- is not let you talk me out of it. You'd be so good at it. You're always so good at it. That's the whole tragedy of you, Prescott. You'd talk a drowning man out of the rope.''

She went up the back stairs to the bedroom that had been her bedroom alone for two years, and Cope sat in the bright kitchen with the wine bottle still in his hand, and the wire in his chest hummed, and for one moment --- one --- he did not reach for the bottle or the phone or the next word. He sat in the quiet she had left behind her, and it had a shape, the quiet did, an edge to it, and the edge was a number he could not read, days counting down in a hand as steady as a surgeon's, and he felt the draft again from the shut door in the house of him.

Then he poured a glass he would not finish, and took out his phone, and texted Sun: \textit{home looks good, family's solid, tell Delia she can come to greenwich for the wide shot.} And he believed it. He stood in the wreckage of the only conversation that had told him the truth all week and he read it as a win, because reading things as wins was the engine, and the engine had never once failed to start, and he was sure --- the way you are sure of things at midnight in a kitchen when you have not slept since a day you can no longer name --- that he had handled it. That he handled things. That this was what he did.


\scenebreak


He drove back to the city himself, which he was not supposed to do. There was a service for that, a quiet man named Oleg who saw everything and was paid to forget all of it, but Cope sent Oleg home and took the Merritt himself at one in the morning with the windows down and the cold October air coming in hard, because he wanted, he told himself, to \textit{think,} and because the road at that hour belonged to him the way nothing else did anymore --- the dark trees, the dashed line coming up out of the dark and disappearing under him, an endless ration of small certainties.

The phone lit on the seat beside him twice and he did not look at it. Once it was Sun. Once it was a number he didn't know, an unknown number at one in the morning, and a younger, less lit man might have wondered what kind of caller comes at that hour from a number you don't know, might have heard, in the buzz of it on the leather, the sound of a story turning over in its sleep and beginning, out past the dark trees, to breathe.

Cope thought it was probably Bryce. Or someone like Bryce. There was always someone like Bryce, and the thought warmed him, the generous enormous warmth, \textit{if you ever want to do something more interesting than this,} and he smiled at the road.

He came up the FDR with the river black on his right and the city standing up ahead of him lit at every node, and he felt --- he would have sworn to it, he would have toasted to it, he did, in fact, toast to it, aloud, alone, in the car, lifting an empty hand off the wheel --- he felt the future coming to ask his advice.

The tower was lit at the crown the way Aldous had insisted, \textit{so a man coming up the avenue knows there's somebody home.} Cope looked up at it through the windshield, the old limestone, the warm gold light at the top where his office was, where his father's desk was, where the drawer was, and he thought: \textit{somebody's home. I'm home. The light's on because I'm in it.}

He did not know --- could not have known, would not have heard it if Margaux herself had said it in her flat steady voice --- that the light at the crown was the last quiet thing he had. That this was the hour. That out there in the dark, in a city of editors and lawyers and a profiler with a list and a wife with a legal pad and an activist who only had to stand at the bottom of the hill, the buried thing had taken its first breath. That it had been holding it for years. That it was, even now, very quietly, learning to use its lungs.

He parked in his spot. He went up forty floors in the brass cage of the old elevator, alone, watching the numbers climb. He let himself into the dark suite where his fathers watched from oils and the boy at nine grinned up out of a steel vat at men whose names he'd lost. He did not turn on the lamp.

He sat down at the desk, and opened the second drawer, and set himself up one more, neat and quick and competent, a man maintaining a machine he was sure he had under perfect control.

And then, in the dark, with the city held still and lit below him and the wire singing clean and high and total in his chest, the last human chief executive in the consumer Fortune 100 picked up his phone to write --- he was sure it would be the best thing he'd ever written --- and saw, finally, that he had eleven missed calls.

He smiled at the screen.

``There it is,'' he said, to no one, to his father, to the dark. ``There's the future. Right on time.''

He was almost right. He was off by one word, and the word was \textit{future,} and it would take him until morning to learn the other one.

\clearpage
\chapter{The Most Human Thing}

\begin{transmission}
{\transheader TRANSMISSION 15 --- ``Detonation''}\par\vspace{0.5em}
And here it is --- the exquisite punchline the whole universe has been setting up. The man crusading for the irreplaceable human soul is destroyed, on schedule, by the most human things there are: the sex, the drugs, the lie. The pundits will note, correctly, that the machine would never have done this. Praxis runs a serene stock-photo ad in the same hour. He reaches for the denial, and the denial --- as denials do --- reaches back and pulls him under. Next stop: hoisted by your own humanity.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} story broke at 6:02 a.m. and Cope was awake to see it, because by then he was always awake to see things.

He had not gone to Greenwich. The house had Margaux in it, and the rooms had the particular silence of a woman who had moved her good chisels to a friend's studio and said so, evenly, across the kitchen island the night before, which Cope had filed as a storage decision and not a verdict, because the alternative was unsurvivable at the hour he had for filing things. So he was in the Aerie, on the long couch his grandfather had bought a senator, in yesterday's shirt, when his phone lit with the alert he had set months ago to catch his own name and now caught it like a man catching a thrown brick.

\textit{EXCLUSIVE: Inside the Last Human's Last Stand --- and the Habits He Couldn't Outrun.}

Delia March's byline. Of course Delia March's byline. He had let her in. He had walked her through the Defiance plant himself, had her in the back of the Suburban out of Toledo, had said \textit{call me Cope} the first morning and meant it, the full wattage, the toast in miniature, the thing he could not pass a stranger without doing --- and Delia March had taken the wattage and the access and the eight weeks and written, under it, the truth, which was the one thing he had never imagined a profile could contain, because no profile he had ever sat for had wanted anything but to flatter him into a quote.

He read it once fast, the way you read your own scan results, looking only for the word that ends you.

He found two.

The first was a name. Not Renata's --- that was buried deeper, that was a different drawer, and the relief he felt at its absence lasted exactly as long as it took to reach the second graf. The name was \textit{Mara Veiss,} twenty-nine, deputy of communications, who had joined the campaign in April and been on every plane since, and whom the piece described, in a sentence built to be screenshotted, as ``a current relationship the Chairman's own staff has spent the spring scheduling around the way you'd schedule around weather.''

The second word was \textit{cocaine.} It sat in the eleventh paragraph, sourced to ``two people present and accounts of a 2018 hotel incident described to this magazine,'' and it was not lurid, which was what made it lethal. Delia March had not written it like a scandal. She had written it like a fact about a man's mornings. She described the Toledo airport men's room. She had the timing of the diner eggs --- \textit{he ate like a man who hadn't, because he hadn't.} She had the legal pad and the looping hand. She had, God help him, the \textit{almost} --- the withheld tear, the beats, \textit{one, two, look away, three} --- and she had set it beside the men's room with no comment at all, because the comment was the adjacency, and the adjacency was the article.

The Last Human, optimized.


\scenebreak


He called Sun before he called anyone, which was the closest thing he had to instinct.

``I've seen it,'' she said, before he said anything. She did not sound asleep. She sounded like a woman who had been up since the embargo lifted on the wire she still got, which she had. ``Don't post. Cope. Are you hearing me. Do not put your thumbs on anything until I'm in the building.''

``It's not --- Mara's not --- '' He was up, pacing the museum, past his father's portrait, past the putter on its brass cradle. The shirt smelled of yesterday. ``It's a working relationship that she has \textit{sexualized,} in print, a \textit{friendship,} she's taken a friendship and --- and the other thing, the 2018, that's a \textit{fabrication,} Sun, that's a hit, Frade fed her that, you know he fed her that --- ''

``Frade didn't feed her anything.'' Sun's voice was very flat and very tired, the thirty-thousand-mile voice with another ten thousand on it overnight. ``That's what I need you to understand before you go on a screen. He didn't have to. You let a reporter live in your pocket for eight weeks while you were --- while it was all happening. She didn't dig it up. She \textit{watched} it. There's nothing to deny. The denial is the story now.''

``Watch me,'' Cope said, which was not an answer, and hung up, and did not know, even as he did it, that he had quoted himself from a mirror two years and a hundred years ago.


\scenebreak


By seven the morning shows had it.

By seven-fifteen they had the clip --- DeShawn's clip, the Camden plant, \textit{are you scared,} the unrehearsed thing that had been, six weeks ago, the most valuable thing Mercer-Dale had produced in a decade --- and they ran it next to the eleventh paragraph, and the realness that had saved him curdled in real time on a split screen, because once you knew about the men's room the catch in the throat read differently, the \textit{almost} read like chemistry, and a thing cannot be authentic and a symptom at once and survive being both on a chyron.

A woman on the financial channel, kind-faced, said the thing that would be said all day in forty registers. ``And look --- and I want to be careful here --- but you cannot help but notice. The whole pitch, his entire pitch, has been: a machine can't \textit{feel.} A machine has no \textit{soul.} And the irony, this morning, is just --- '' She did the small open-handed gesture they all did now, the Praxis gesture, the soft sans-serif made flesh. ``An AURELIUS doesn't \textit{do} this. It can't. It has no --- there's no appetite to manage. It logs everything. It can't have an affair with its deputy of comms. It physically cannot buy cocaine in a Toledo bathroom. The argument \textit{for} the human in the chair just became the single best argument \textit{against} this particular human.''

Her co-anchor, gentler, trying: ``Well, that's what makes him \textit{human,} isn't it --- ''

``That's exactly the problem,'' she said, not unkindly, and that was the whole book in eleven words, and Cope, watching, did not hear it as the whole book. He heard it as a woman who could be charmed if he got the room.

He thought, with the bright bottomless clarity of a man four days into a sleepless week: \textit{I have to get the room.}

He had spent his life getting the room. The room had never once not been gettable.


\scenebreak


Praxis ran the ad at 7:40.

It was not aimed at him. That was the thing he would understand later and could not understand now --- that it cost them nothing, that they had not even moved it up, that it was a buy placed weeks ago on a media plan optimized by the same kind of system they sold, and it simply surfaced, serene, in the slot it had always been going to surface in, the way arithmetic surfaces. It ran on the financial channel directly under the split screen of his face and DeShawn's question. A wash of clean morning light. A woman at a desk that was not a real woman, a stock image, a face assembled to be trustworthy and from nowhere, looking calmly off-camera at a future that agreed with her. And the four words in the soft sans-serif, white on a field of pale considered blue:

\textit{It just shows up.}

And under it, smaller, the wordmark, and under that, the tagline he had laughed at on a bus shelter two years ago in a car going down Sixth with Sun beside him and the whole thing still ahead of him and recoverable: \textit{Leadership as a service. No off-sites.}

It showed up. It did not key itself bright in an airport bathroom. It did not need a deputy of communications on every plane. It did not require a man in a henley charging two hundred thousand a month to find the \textit{almost,} because it had no tear to withhold and nothing it wanted from the eleven hundred strangers, and it would never once in its operating life be photographed eating eggs like the last warm-blooded thing in America, because warmth, as Tisch had told him, glowing, holding two green juices, had parameters, had a waveform, could be installed in anything, and the difference between Cope and the thing that was replacing him was that the thing had no Tuesday it could not remember, no Saturday it would not enter, no drawer with a false back.

It just shows up.

Cope turned the television off and stood in the dark museum with the obelisk somewhere behind him on a shelf and felt, for the first time, the specific vertigo of being out-souled by a desk and a sans-serif. It was not grief yet. It was the floor reporting that it was no longer entirely there.

Then the manifesto-feeling came up under it, warm, electric, the way it always came, the way it had come at the window, and he reached for his phone, because there was a room out there of eight million people and he had not yet failed to get a room.


\scenebreak


Sun got to the Aerie at 8:10 and he had already posted.

She knew before the elevator opened, because her own phone was buzzing in a register it did not buzz in for anything good, and she came in and found him standing at the glass exactly where the photographs would later say a man stands when he is about to be a cautionary slide, lit, electric, \textit{better,} and she said, ``What did you do,'' not as a question.

``I got ahead of it,'' Cope said. ``I told the truth. Read it. It's good, Sun, it's --- it's the realest thing I've ever --- ''

She read it. It took her four seconds and aged her four years.

He had written, with his thumbs, at 7:55, on the account with nine hundred thousand followers that the comms team Mara Veiss helped run had spent two years building:

\textit{A profile this morning attacks me for the unforgivable crime of being a flawed, feeling, fully human man. They want a leader with no appetites, no nights, no mistakes --- a clean machine that has never once needed another person at 2am. I am proud to be the alternative. I have given everything to the people of this company and I will not apologize for having a beating heart. To Mara, a brilliant colleague: I'm sorry my friendship has made you a target for those who fear what we're building. We feel the room. They never will. --- Cope}

``Oh, Cope,'' Sun said, very quietly, and it was not anger, which was so much worse. It was the sound she had made in the car two years ago, the not-fighting he had taken for agreement his whole life and never once noticed taking.

``It's \textit{good,}'' he said.

``You named her.'' Sun set the phone down on the senator's couch like something that might go off. ``She asked you not to be named. She asked HR. It's in the same piece you're refuting --- she \textit{asked,} Cope, the article \textit{says} she asked --- and you just used the company's account to call her your colleague and your friend and a \textit{target,} which confirms the relationship, denies her the thing she requested, and turns a story about your conduct into a story about your conduct \textit{and} your judgment \textit{and} hers, while she works for you, which is the part that's actually illegal.'' Three parts. She had trained him to receive things in threes. It did not get past the charm because the charm was the last thing still running. ``You said \textit{we feel the room.} You put a hashtag on a woman who didn't consent to her own name. And you did it from the \textit{brand account.}''

``People will see I'm not hiding --- ''

``You weren't hiding. That was the problem. You did it all in front of a reporter.'' She pressed two fingers to the bridge of her nose under the glasses she hadn't pushed up. ``Take it down.''

``Taking it down looks like --- ''

``Take it \textit{down,} Cope.''

He took it down at 8:40.

The internet had it at 7:56.


\scenebreak


The thing about a denial, he was learning, the thing nobody tells you, is that it is a door you open inward into a small room, and the room is full of follow-up questions, and there is no other door.

He had said \textit{flawed, feeling, fully human man.} So the desk that had not been there returned in the form of a producer's question relayed through Sun's phone: \textit{Does the Chairman dispute the 2018 hotel account, or characterize it as part of being fully human?} He had said \textit{friendship.} So Mara Veiss's attorney --- she had one by ten, a good one, the kind the company usually paid for --- sent a letter that used the word \textit{retaliation,} and the word \textit{power differential,} and the phrase \textit{publicly identified our client against her express request,} and every one of them was load-bearing and every one of them was true. He had said \textit{I have a beating heart.} So a wire reporter pulled the proxy deck and quoted, beside his beating heart, Tidewater's slide --- \textit{no affairs, no conflicts of interest, logs every decision, cannot conceal} --- which had been written months before the profile, generically, about machines in the abstract, and now read, to anyone who had read the morning, like a charge sheet with his name typed back in.

Try, fail, and. He had tried to get ahead of it, and now there was a legal letter. He had tried to honor Mara, and now there was a hashtag with her name in it that she would carry into every job interview for ten years. He had tried to say \textit{human} like a virtue, and the world had agreed it was a virtue and then itemized exactly which human, line by line, against a machine that did not have the line items.

Each move forward was a move down. The denial was not a wall he was hitting. It was a stair.

By noon Frade was on Halloran's show. Cope watched it standing up, because he could no longer reliably sit. Frade did the small folksy chuckle, the one that two years ago had meant he was rattled and now meant only that he was about to twist a knife slowly enough to seem reluctant about it.

``Look, I take no joy in this,'' Frade said, taking obvious joy in it. ``Cope's a charming man. Charming. I've always said it. But this is --- Hal, this is the whole case, isn't it, made for us, free of charge, by the gentleman himself.'' The chuckle. ``Our position was never that Prescott Mercer is a \textit{bad} man. Our position is that the chair shouldn't depend on whether the man in it is a good one. You shouldn't have to \textit{hope} your CEO is sleeping. You shouldn't have to schedule around his appetites.'' A pause, weaponized, reasonable. ``A steward, not a sovereign. We've been saying it for a year. I just never expected him to \textit{demonstrate} it for me.'' He spread his hands, and the gesture was the Praxis gesture, the open-palmed nothing, and Cope understood with a lurch that even Frade had learned to move like the machine, because the machine's was the winning shape now, and the men who beat you adopt your posture last.

The word \textit{theater} had not stuck six weeks ago because the clip had been real. This stuck because it was also real. That was the trap of being human in the chair: your truth and your ruin were the same footage.


\scenebreak


Margaux called at 1:15 and he almost did not answer, because he could not bear, on top of everything, to be seen, and Margaux was the one person who had always seen and never once been gotten.

``You named her,'' Margaux said.

Not \textit{are you all right.} Not \textit{is it true} --- she had counted them, she had flushed the stashes, there was no \textit{is it true} left in her for him. Just the thing Sun had said, the thing that was apparently the entire morning reduced to its mineral core, the thing even his wife led with.

``Margaux --- ''

``I'm not calling about the drugs,'' she said, in the spare voice that had been landing lines he couldn't toast over for twenty-two years. ``I've known about the drugs since the second decade. I'm not even calling about the girl. There's always a girl, Cope. I stopped numbering them around the time I stopped sculpting.'' A small silence, not cruel, which was the cruelest thing she did. ``I'm calling because you went on the \textit{radio} --- you went out in front of God and the company and that poor child you put on a plane --- and you said you have a beating heart. And I just wanted to be the one to tell you, because I'm the only one left who will.'' She did not raise her voice. ``There was never anybody home, Cope. That's the part the machine got right about you that I couldn't make you hear in twenty years. You don't feel the room. You \textit{read} it. There's a difference, and you spent our whole marriage in the gap, and this morning eight million people finally saw the gap, and the only thing I feel --- and I've been trying to feel something else all morning, I owe you that, I tried --- the only thing I feel is that they're not wrong.''

She hung up gently. She did everything gently. The gentleness was the indictment.

He stood in the museum with the dead phone in his hand and his father in oils behind him and the city out the glass holding still, all its nodes lit, eight million people who two years ago he had been sure were waiting for him, and he understood that they had been waiting, all right --- patient, tireless, incapable of cruelty or mercy --- but not for him. For the arithmetic. For the thing that just shows up.

He reached, out of the groove the record had been cut in, for the second drawer, the one with the false back, the cigars and the flask and the thing Cope used it for, and his hand was on the brass pull before the rest of him caught up, and he saw himself reaching, for one clean overexposed second he saw the whole machine of himself from the outside the way Delia March had seen it, the way the desk-faced woman from nowhere would never need to be seen because she did not reach for anything, because she just showed up, and he thought, with no triad to hold it and no almost to protect, the truest sentence he had formed in a year:

\textit{The thing they're replacing me with would not be standing here doing this.}

And then he opened the drawer anyway, because that was the other true thing, the load-bearing one, the one the whole morning had been built on the way a hotel is built on the room you don't go into.

He set himself up one. Neat and quick and competent. A man maintaining a machine he was sure he had under perfect control because it had never once failed to start.

It started.

The bell-struck feeling came up clean and high and total, the one he had spent thirty years calling the applause, and out past the glass the city reassembled, and somewhere below a bus shelter changed its slide, and Praxis, serene, sincere, doing no malice and feeling no triumph, ran the ad again into a morning that had already agreed with it, and the last human chief executive in the consumer Fortune 100 stood in the wreckage of the most human day of his life, hoisted on the exact thing he had spent it defending, and felt, against everything, against all of it, wonderful.

\clearpage
\chapter{Renata}

\begin{transmission}
{\transheader TRANSMISSION 16 --- ``She Was Never a Story''}\par\vspace{0.5em}
Every powerful man's scandal has a woman he has cast, in the privacy of his own legend, as either the temptation or the redemption. Watch her walk in and refuse both parts. She was not a love story. She was not a headline. She was an employee whose career he spent, and she is here, unbitter and unbreakable, to remind him --- and the board --- that the firing offense was never the affair. It was the lie he told the people he answered to. Next stop: the precise governance crime, served cold.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{H}{e} had imagined the scene so many times, over so many years, that when it finally came it had the slightly used quality of a suit worn to too many funerals.

In the imagining, it was always a doorway. Renata in a doorway, evening light behind her, the years having done to her what years did, and Cope rising from somewhere --- a chair, a hospital bed, in one version a courtroom --- and saying the thing. He had a few versions of the thing. The good one started \textit{I never deserved} and got better from there. In all of them she forgave him, which he experienced, in the privacy of the daydream, not as forgiveness but as a kind of verdict overturned on appeal, the record sealed, the man restored. He had cast her, without ever once using the word to himself, as the person who would someday tell him he had not been the worst version of the story he was in.

She did not come in a doorway. She came in a conference room on the nineteenth floor of a building that wasn't his, at four in the afternoon, in a gray blazer she had clearly chosen because it would not photograph as anything, carrying a single legal folder and a paper cup of the bad coffee from the machine in the hall, and the first thing she said to him, before the lawyers had finished arranging their pads, was:

``You look tired, Cope.''

And he heard, under it, with the bright wire in his chest going very still, that she did not mean it kindly and did not mean it cruelly. She just meant it. The way you'd note the weather.


\scenebreak


The room had been arranged by people whose job was arranging rooms, which is to say it had been arranged to be deniable. Not Mercer-Dale's offices, not Tidewater's, not Renata's firm's, but a neutral floor a relocation company rented by the hour to companies that needed to be in the same room as a thing they did not want to be seen near. There were eleven people in it. Cope had counted, the way he counted rooms, and then had stopped counting because he did not like the number he was getting on his own side.

His side: Cope. Sun, who had not wanted him here and had said so in three clean parts in the elevator and been overruled by the one part of him that still believed a room was a thing he could win. Two lawyers from Brandt Michelson, a man and a woman, both of whom Cope had met four times and could not have named under oath. The general counsel, Hal Brennan, gray as a filing cabinet, with the specific stillness of a man calculating his own exposure. And a woman from the special committee --- a director Cope barely knew, Adaeze Okafor, retired audit-firm partner, brought onto the Mercer-Dale board fourteen months ago for exactly this, for the day a thing came up that the regular directors could not be in the room for without becoming part of it. She did not have a pad. She had a phone, face-down, and her hands folded on top of it, and she watched Cope the way you watch a structure you have been told is unsound.

Her side --- Renata's --- was just Renata and one lawyer, a tired young man named Ferro who looked like he billed by the syllable and had decided to spend none of them.

It curdled something in Cope, the arithmetic of it. He had brought five. She had brought one and a half. He had spent his whole life understanding that the size of your delegation was the size of your fear, and here he was with a delegation, and there she was with a coffee.

``Renata,'' he said. He had decided in the car to use her name early, warmly, to take it back from the lawyers, to make it a human room. ``Thank you for ---''

``Let's not do thank-yous,'' Ferro said, without heat, turning a page. ``My client agreed to be in the room. She didn't agree to be grateful in it.''


\scenebreak


Here is what the press already had, by that Tuesday: a name. Not Renata's --- they had a \textit{current} name, wrong, a woman in corporate communications who had never been within a marriage of Cope and who was now, because of a leaked calendar and a stupid lunch, being doorstepped at her son's school. And they had the shape of an older thing. A 2019 settlement. A VP who had left ``to pursue other opportunities,'' which was the phrase the company used the way the Hearthstone documents used \textit{thermal event profile}, a phrase built specifically to be a wall. Reuters had the docket number of a thing that had been sealed and was now, in the way of sealed things during a proxy fight, being un-sealed by people who had decided the public had an interest.

Cope had told Sun it was survivable. He had told her it was 2019, ancient history, a private matter between consenting adults, that the \textit{current} story was a nothing because it was a nothing, and that Renata --- he had actually said this, in the Aerie, at two in the morning with the wire singing --- Renata had loved him, that whatever the paper said, the truth of it was that two people had cared for each other inside a situation that made caring impossible, and that if it came to it, if it ever truly came to it, she would not want to hurt him.

He had built, in other words, a small cathedral, and cast her as the light through the window.

She had asked for the meeting. That was the part he kept holding up to the light, the way he'd held the obelisk. \textit{She} had asked. Through Ferro, through Brennan, a request: a room, the right people, an hour. He had read it as the daughter of his daydream walking back up the avenue. Sun had read it correctly, which was why Sun had not wanted him in the room.


\scenebreak


``I asked for this,'' Renata said, ``so I could say a few things once, to the people who need to hear them, and then never say them again. I'm not recording. You can record. I assume someone is.'' She glanced, neutrally, at Brennan. ``I'd like to start before the lawyers tell me which parts I'm allowed to feel.''

``Renata ---'' Cope started.

``I'm going to talk to her, actually,'' Renata said, and turned a few degrees in her chair, toward Adaeze Okafor and the face-down phone. ``If that's all right. You're the board.''

``I'm the special committee,'' Okafor said. ``But yes.''

``Then you're who this is for.''

Cope sat with the strangeness of being, for the first time in possibly thirty years, the second-most-important person in a room with his name on the building. He had a sentence ready --- he always had a sentence ready --- and he could feel it going stale in his mouth, the \textit{we cared for each other} sentence, the cathedral sentence, because she had walked past it without looking, the way you walk past a busker.

``Mr. Mercer hired me in 2016,'' Renata said, to Okafor, in a voice with no tremor and no edge, a voice reporting. ``I ran the Hearthside division --- small appliances, the cross-sell stuff. I was good at it. I want that in the room, because the story that's going to get told outside this room is going to be that I was a pretty girl he noticed. I was a VP who turned a dying category eleven points of margin. He noticed \textit{that} first. I have the decks. I bring this up not because my pride needs it.'' She paused. ``It does, a little. But mostly because the firing offense in here'' --- she tapped the folder, once --- ``has nothing to do with how I looked. And I don't want anybody in this room comforting themselves later that it did.''

``Renata, no one thinks ---'' Cope said.

``You did,'' she said. She did not raise her voice. ``You told me I was the smartest person in the building and then you spent four years making sure that wasn't the sentence anyone remembered about me. That's not an accusation. It's a personnel record.''


\scenebreak


Cope had a backswing for moments like this. He had charmed a senator's widow at his own table; he had gotten a board to vote against its own arithmetic on the strength of his face. He leaned forward now and put both forearms on the table and brought the whole wattage up, slow, the Mercer Inhale, the pause he had taken in a thousand rooms.

``Can I just --- as a human being. Not as a --- Brennan, let me.'' He spread his hands. The hands had never let him down. ``What we had, whatever its --- whatever you want to call it. It wasn't \textit{nothing}, Renata. I won't sit here and let a roomful of lawyers turn two people into a deposition. There was real ---''

``There it is,'' Renata said. Quietly. Almost to herself. And then, to Okafor, not unkindly: ``Watch this part. This is the part he's good at. He's about to make it a love story, because in a love story the worst thing he did was love someone he shouldn't have, and that's a \textit{forgivable} thing, that's a \textit{human} thing, men have written symphonies about that thing.'' She looked back at Cope, and for one second something passed behind her face that was not anger, was older and more tired than anger, was the specific exhaustion of having to explain to a man, again, the inside of his own conduct. ``It wasn't a love story, Cope. I know that's the version you've kept. I've thought about you keeping it. It's not the version that happened.''

``I never ---''

``You slept with someone whose career you controlled, and when it got complicated you handled it the way you handle a recall.'' She let that sit. She had no idea, Cope realized with a small cold drop, how exactly that word would land, and that was almost worse --- that she'd reached for it as a figure of speech. ``You assessed the exposure. You found the cheapest number. You bought a wall and you put my name behind it and you told yourself a story where I was a chapter in your life instead of the end of mine, at that company, doing the thing I was good at. I didn't leave to pursue other opportunities. There weren't any. You'd made sure of the references without ever once being unkind to my face. You were \textit{never unkind to my face.} That's the part I couldn't explain to anybody for about three years.''


\scenebreak


The young lawyer, Ferro, had stopped turning pages.

Sun was looking at the table. Cope wanted, badly, for Sun to look up, to give him the room with her eyes, to do the thing she did out of the architecture, and she did not look up, and he understood she would not, and a small structural beam in him went.

``This is ---'' Cope said, and heard his own voice find the register it went to under pressure, clipped, a little biblical, and could not stop it. ``I want to say something, and I want the committee to hear it as what it is, which is a man --- a flawed man, I have never claimed otherwise, I stood up in a ballroom and told nine hundred people the only thing a machine can't do is \textit{err} ---'' He had not said that. He had said \textit{love.} He did not notice the swap. ``I'm a flawed human man. That's the whole --- that's literally the entire thing I've been saying for two years. And now the same people who want to hand my chair to a calculator are going to take the most human failing there is and put it on a chyron and call it a \textit{governance crisis.} It's a witch hunt. It's a witch hunt against the last man in the building who still has a pulse, and the pulse is the evidence, that's the --- do you see what they've built? A world where the disqualifying thing about a leader is that he's a \textit{person.}''

He had said it the way he said things. It had a triad in it somewhere, almost. It had, for about four seconds, the shape of something he could have toasted with.

And then it just sat there, on the deniable table, in the rented room, and curdled.

Because Renata was looking at him with something that was not even contempt. It was patience. It was the patience of a woman who had done the reading.

``You think the firing offense is the affair,'' she said.

``I think the ---''

``It isn't.'' She opened the folder, not to read from it --- she didn't need it, he could see she didn't need it, she had it the way he had Aldous and the mayonnaise --- but to put her hand flat on it, to make it a thing in the room. ``I've had a long time to understand exactly what you did wrong, Cope, and it took me about two years to stop thinking it was the bedroom, because that's where you wanted me to think it was. The bedroom's between us. It was wrong and it was ours and it's not why any of these lawyers are here.'' She turned, fully now, to Okafor and the special committee and the audit partner's folded hands. ``You're not here because the chairman slept with a VP. You're here because of what came after.''


\scenebreak


She laid it out the way you'd lay out a quarter.

In 2019, when the situation she would not call a love story became a liability the company could be sued over, Cope had a duty. Not a moral one --- Renata waved the moral one away, almost impatient with it, it was the least interesting duty in the room. A \textit{governance} duty. He sat on a board. He answered to a board. And the board's compensation committee, the audit committee, the general counsel sitting right there gray as a cabinet, had a settlement come across their work with a number on it and a category attached to it, and the category said \textit{commercial dispute, departing executive,} and the category was a lie, and Cope knew it was a lie, and Cope had personally --- she had the email, it was in the folder, Ferro had it filed and tabbed --- personally directed that the matter be characterized in a way that kept it off the board's radar. Kept it out of the disclosure to the directors. Kept it from the people he was, by charter, by law, by the entire load-bearing fiction of the corporation, \textit{accountable to.}

``You can sleep with whoever you want,'' Renata said. ``I mean that almost literally --- the board can't fire you for the affair, your own lawyers will tell you that, it's tawdry but it's not a crime. What they can fire you for --- what they have to fire you for, if they want to be a board and not a portrait gallery --- is that you looked at the people you answer to and you decided they didn't get to know. You made yourself unaccountable. You took a thing that belonged to the people who own the company and you put it in a drawer with your name on the lock.'' She closed the folder. ``Easterbrook didn't lose a hundred million for the affair. He lost it for the second interview, when he sat across from his own board and didn't tell them the whole list. The cover-up. The concealment. That's the offense, Cope. Not the sin. The lie you told the room you answered to.''

It was so quiet in the room that Cope could hear the bad coffee machine in the hall finish a cup for someone who wasn't there.

He understood, sitting in it, that he could not answer her. Not that he chose not to. That there was, in the entire warm inventory of him --- the toasts, the triads, the face that had never let him down, Aldous and the four hundred borrowed dollars and the arm in the vat to the elbow --- there was no sentence. She had taken the one door he reached for, the \textit{flawed human man,} and shown him it opened onto the very thing that was hanging him: not that he was a man, but that he was a man who \textit{hid.} The machine, he thought, with a lurch he did not have a name for, the machine couldn't have hid this. The machine logged everything. The machine would have put the settlement in the board portal with a transparent rationale by Wednesday and it would have been awful and it would have been \textit{clean,} and the awful clean thing was the thing the board had paid ten figures less than him to get.

He had spent two years arguing that a machine couldn't love a company.

She had just shown him, in a gray blazer, with a folder, that the company had never asked him to love it. It had asked him to \textit{tell it the truth,} and that was the one human thing he had withheld.


\scenebreak


``That's all,'' Renata said. She stood. She had not raised her voice once, and she did not raise it now, and that, more than anything, was the thing that made Cope feel the floor of himself drop a level he had not known was there. ``I'm not going to the press. Ferro will tell you the terms, which haven't changed, which is that I want nothing, which I know you can't understand. I came so that when this is told --- and it's going to be told, you've made sure of that, the whole world's going to get the version with the pretty girl in it --- at least one room would have heard the real shape of it. From me. Once.''

She picked up the coffee cup she had not drunk.

``You weren't the love of my life, Cope. You weren't even the villain of it. You were just my boss, and you were careless with me the way you've been careless with everything, and then you were careful --- God, you were so \textit{careful} --- about making sure it cost you nothing. That's the whole story. There's no machine in it and there's no soul in it. There's just a man who could've told the truth to four people in a conference room in 2019 and instead spent six years and however many dollars making sure he never had to.''

She paused at the door. Not the doorway of the daydream, the evening light, the verdict overturned. Just a fire door, in a rented hall, with a coffee cup in her hand.

``I hope somebody gets you some sleep,'' she said, and it was the kindest thing anyone said to him that whole season, and it was not kind, and she left.


\scenebreak


The room reorganized itself around her absence the way rooms do. Ferro gathered his syllables. The Brandt Michelson lawyers began, in low murmurs, the work of converting a human catastrophe back into a manageable legal one. Brennan was already on his phone. Okafor turned her own phone over, looked at it, and then looked at Cope for a long moment with an expression he could not charm because it was not asking to be charmed; it was the expression of a person finishing the arithmetic, and the number was not in his favor, and they both knew she had been brought onto the board to be a person who would do the arithmetic anyway.

``Mr. Mercer,'' she said, and stood, and that was all she said, his name and a courtesy, and it landed on him like a sentence with the second half left off.

Sun stayed. Sun always stayed. She came around the table and stood near him, not touching, in the way she had of being available to a man who could not be helped, and she did not say \textit{I told you,} and she did not say \textit{we'll fix it,} and the not-saying was the truest brief she had ever given him.

Cope sat at the deniable table in the room that wasn't his.

He was fifty-four and the camera still loved him and the jaw was still the jaw, and somewhere far down the avenue a bus shelter was changing its slide, and up in the Aerie a manifesto waited that he had been sure, at one in the morning, would save the world from the loss of him. He had walked into the room a flawed human man and he had liked that phrase, he had polished it in the car, it had a pulse in it, it had a kind of grandeur. He understood now that it had been the last large thing he was going to be able to say about himself.

He felt, sitting there, smaller than he had ever in his life let himself be --- smaller than the obelisk, smaller than the chair, smaller than the four people in 2019 he had decided did not get to know --- and the smallness was not a feeling he could toast over or fold into a paper or set up neat and quick in a drawer with a false back. It just sat in him, exact and quiet, the size of one withheld sentence.

He did not reach for a line. For once in his life, there wasn't one.

The coffee machine in the hall finished another cup for nobody.

\clearpage
\chapter{The Names for It}

\begin{transmission}
{\transheader TRANSMISSION 17 --- ``A Doctor Who Won't Be Charmed''}\par\vspace{0.5em}
At last, a room he can't toast his way out of. A psychiatrist --- summoned by the women who love him --- is about to do the one thing no board, no activist, no machine has managed: say the plain clinical words for what he is, the mood disorder \textit{and} the cocaine, and refuse to let him use either as an alibi for the other. Addiction, she insists, is not a metaphor. He has built a cathedral of metaphors. Next stop: the floor under the floor.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{hey} had ambushed him with a living room.

That was the first thing Cope understood, walking into the Greenwich house at nine on a Sunday morning he'd been told was about the lawyers --- and it was a good ambush, he had to give them that, because the only way to get him into a room he didn't want to enter was to make him think he was the one who'd called the meeting. Margaux had made coffee. There was a tray. There was, sitting in the wing chair that nobody sat in, the one angled toward the window that his mother had reupholstered in 1981 and Margaux had never had the heart to redo, a small woman of about sixty in a gray cardigan with a notebook closed on her lap and no coffee in front of her, which he clocked the way he clocked everything, because the ones who don't take the coffee are the ones you can't get to.

``Cope,'' Margaux said, ``this is Dr. Adler.''

``Dad.'' Pip was on the sofa with her knees up. She'd flown in. He hadn't known she was in the country. The not-knowing arrived and was filed and did not reach his face. ``Sit down. Please.''

He did not sit down. He stood in the doorway of his own living room with his weekend zip-up on and the bright fine wire still going in his chest from the bump he'd done in the car at the foot of the drive --- neat, quick, a man maintaining a machine --- and he ran the wattage up the way you bring up house lights, slow, warm, total.

``Well,'' he said. ``This is a hell of a thing to wake up to. Three of my favorite women and a tray.'' He smiled at the doctor. ``I'm sorry, I'm at a disadvantage. Cope Mercer. You're a friend of Margaux's?''

``I'm a psychiatrist,'' Dr. Adler said. ``Your wife and your daughter asked me to come. They're worried about you. I'm here to talk with you, and then I'm here to tell you what I think.''

No softening on it. No \textit{I just wanted to chat.} He'd expected the softening --- there was always a softening, that was the handle you grabbed --- and its absence put a small cold spot in the middle of the warm.

``Worried,'' Cope said. He came in. He did not take the sofa, which would have put him level with Pip; he took the hard chair near the doorway, which let him keep the room in front of him, all of it, the exits. ``I love that. I'm at the best I've been in a decade and the women I love most have hired a --- forgive me, I don't mean it the way it'll sound --- a \textit{grief counselor} for a man who isn't dead. That's the most Mercer thing that's ever happened in this house, and my father drowned a dog in this house.''

``He didn't drown a dog,'' Margaux said quietly.

``He let it drown. There's a difference and the family observed it.'' He was rolling now, he could feel it come up under him. ``Doctor, I'll save you the hourly. I sleep a little less than I should. I'm in the fight of my life --- you may have seen, the company, the --- it's been on the television, the proxy thing, the machine thing. A man doesn't sleep eight hours during a war. Eisenhower didn't. I read four hundred years of Mercer history and not one of them slept through a thing that mattered. So if the diagnosis is \textit{busy,} I'll take it, and I'll sign the bill, and we can all have the eggs.''


\scenebreak


Dr. Adler opened the notebook. She did not write in it. She just opened it, like setting a clock on a table.

``How many nights this week did you sleep more than three hours,'' she said.

``That's not --- you can't reduce a man to ---''

``It's a yes-it-was-this-many or I-don't-know question. How many.''

``I don't keep a --- Sun would know, she ---''

``I-don't-know is an answer.'' She made a small mark. So she did write. ``When did you last eat a full meal at a table and finish it.''

``I'm not a finisher. I'm a grazer. Ask Margaux, twenty-two years, I ---''

``Eight pounds,'' Margaux said, to the window. Not to him. ``In five weeks. I had your blue suit taken in twice. The tailor stopped charging me for the second one. He felt bad.''

That landed somewhere he didn't have a face for, and he covered the place where it landed with a laugh. ``The tailor \textit{felt bad.} See, this is what I love about this family. We could open a museum of people feeling bad on my behalf and charge admission and \textit{still} lose to the streaming arm.'' Nobody laughed. Pip was watching him with the specific stillness she got, the one that used to mean she was about to cry at eight and now meant she had decided not to. ``It's a \textit{campaign,} I'm not eating because there's no \textit{time} to eat, there's a thing called the ---''

``How much are you using,'' Dr. Adler said.

The wire in his chest changed pitch.

He had been waiting for it, of course --- somewhere under the talking he had known the tray meant this, the doctor meant this, the not-touching-the-coffee meant this --- but he had expected it to come in dressed up. He had a whole wardrobe ready for it. \textit{Recreational, occasional, the same as a Scotch, you don't say a word about the second glass of Margaux's Sancerre.} He had given that speech, in his head, to imaginary versions of this woman, and in every version she had blushed and retreated and he had won.

She had not asked \textit{whether.} She had asked \textit{how much.} You cannot put your prepared answer to \textit{whether} up against a \textit{how much}; the question had already conceded the thing the answer was built to deny, and stood there waiting on the other side of it.

``That's an extraordinary thing to ask a man in his own ---''

``It's a number,'' she said. ``Grams a week. Best estimate. I'm not the police, I'm not the board, and I'm not your wife, who already knows, and I'm not your daughter, who guessed. I'm the one person in this room you can give the real number to without it costing you anything you haven't already spent. How much.''


\scenebreak


He looked at Margaux.

He did it without meaning to --- the old reflex, find the soft one, find the handle --- and there was nothing there. She had her arms crossed and her chin up and she was looking at the window where the gray Sound was doing nothing, and he understood, in the way you understand a thing you've worked for years not to, that \textit{already knows} was not a guess Adler had made. It was a fact Margaux had supplied. She had counted. She had flushed things. She had refilled her own prescriptions and called it a marriage, and she had told this woman in the gray cardigan the number before he walked in, and the only person in the room who didn't have the number was him, because he was the only one who'd never let himself add it up.

``You flushed the desk one,'' he said to her. Not a question. ``In March. I thought it was the cleaner. I \textit{fired} ---'' He stopped. He had fired a man. A man named Anatoly with a daughter at Fordham. He had fired him over a thing his wife had done to save his life. He sat with that for the length of one breath and then put it, too, in the kitchen with the other sentences.

``Three,'' he said, to the doctor, finally, and heard his own voice come out smaller than he'd sent it. ``Three, maybe. A week. When it's heavy. Less when it's ---'' The number was a lie and he knew it was a lie even as the smallness made it feel like honesty; the smallness was its own performance, the confession-shaped thing you give so you won't have to give the confession. ``Four,'' he said. ``Four. It's been a four kind of month.''

Adler wrote it down. She did not look horrified, which was somehow worse than horror. She looked the way Sun looked at a number on a deck --- like it was simply true, and now they could work.

``All right,'' she said. ``Thank you. That took something. Now I'm going to tell you what I think, and I want you to do me the courtesy of not performing while I do it, because you're very good and I'll enjoy it and it won't help you.''

``I don't perform,'' Cope said, and even he heard it.

``You toasted your way through the first nine minutes of this. You did a bit about a dog.'' She closed the notebook. ``Here it is. I think you are in a hypomanic episode that is tipping, or has already tipped, into a manic one. The not-sleeping isn't discipline and it isn't war. It's a symptom. The grandiosity --- the certainty about your --- what is it, the Human Premium ---''

``It's not grandiosity if you're ---''

``The certainty,'' she went on, unhurried, ``the spending, the pressured speech, the religious conviction that you alone can be the thing that saves them all --- those are not a personality, Mr. Mercer, and they are not a calling. They have names. They are on a list. I could show you the list and you would find yourself on it the way you find your horoscope, except it would be right.'' She let that sit. ``And underneath it, feeding it, lit up by it, is a cocaine addiction of long standing. Decades. Those are two things. They are talking to each other in your body right now, this morning, and they have been for years, and each one is making the other one worse, and each one is \textit{hiding} the other one from you.''

``So which is it,'' Cope said. He'd found a foothold; relief came up under him like the bright feeling, the debater's joy. ``You can't even --- with respect, Doctor, you've got two answers, which is no answer. Is it a chemical or is it a \textit{condition}? Because if it's the powder, then it's a vice, and a man's vices are his own business, my great-grandfather had three and built a ---'' He waved at the house, the Sound, the four hundred years. ``And if it's a \textit{condition,} if it's a thing in the wiring, then it isn't my fault, is it, and you can't hang a man for his wiring. So pick. Pick which excuse you're handing me, and I'll ---''

``No,'' Adler said.


\scenebreak


It was not loud. That was the thing he'd remember. He had been shouted down before --- by Frade on a stage, by his father from oils --- and he had a whole technique for the shout, you let it spend itself and then you come in warm underneath. There was nothing to come in underneath. The word just sat in the middle of the room, flat and complete, the way a glass sits on a table.

``You want me to pick the disease that lets you keep the drug, or the drug that lets you keep the disease,'' she said. ``I won't. That's the deal you've been running your whole life and it's the one thing I'm not going to do. Listen to me, because no one else in your life is allowed to say it without losing their job or their marriage.'' She leaned forward an inch. ``The mania is real. It is not your fault that you have it. And the cocaine is making it a hundred times worse, and the cocaine \textit{is} your fault --- not the wanting it, the wanting it is the illness --- but every single time you fold the paper, that's a hand, your hand, and the hand is yours. Both. At once. The condition is real \textit{and} you are responsible for what you do about it. Those have never once been the same sentence, and you have spent fifty-four years needing them to be.''

\textit{Those have never once been the same sentence.} It rang against another sentence, one Pip had said to him in another room --- \textit{you don't think a person should run it, you think} you \textit{should, those have never once been the same sentence} --- and for a vertiginous half-second the two women's voices were one voice, and he saw, the way you see the bottom of a thing through clear water, that they had been saying the same thing to him from two directions his whole life and he had been deaf to it in stereo.

``It's not a metaphor,'' Adler said.

``What isn't.''

``The addiction. You keep reaching for it --- I watched you do it three times in nine minutes --- you make it a \textit{symbol.} It's the price of carrying the banner. It's the edge. It's discipline. It's the soul tax, it's the thing the machine can't feel, it's --- you've built a cathedral, Mr. Mercer. A genuinely beautiful one. Every window in it is stained glass and every pane is a reason. And down underneath the cathedral, in the actual dirt, there is a man with a folded piece of paper who has not slept in five days and whose wife took his suit in twice, and \textit{that} man is not a metaphor for anything. He is just sick. In the plainest, most boring, most fixable, most fatal way. And the cathedral is what he built so he'd never have to go down to the dirt and meet him.''

The wire in his chest had gone very quiet.

He noticed, with the clean overexposed clarity he had spent so long calling the applause, that his hands were not steady. They had not been steady in some time. He had been narrating the not-steadiness as energy. He looked at them now, his father's hands on the ends of his own arms, and they were the hands of a man at four grams in a five-day week, and not the hands of a prophet, and for one second --- one --- the floor he had been standing on all his life turned out to have a floor under it, and the floor under it was just this: a room, a tray, a doctor, three women who had run the arithmetic, and him, sick, in a zip-up, on a Sunday.


\scenebreak


Then he stood up. Because standing was a thing he could still do.

``You're very good,'' he said, and meant it as the insult it was and as the surrender it also was, and could not have told you, if you'd asked, which one he meant. ``You're really --- Margaux, where did you \textit{find} her. She's better than Tisch. She's better than the whole --- you should put her in front of the \textit{board.}'' The wattage was coming back up, but wrong now, flickering, a generator hunting for the line. ``But you've got your timing all backwards, Doctor, that's the trouble with your profession, you diagnose at the worst possible --- I'm forty days from a proxy vote that decides whether a human being or a \textit{spreadsheet} runs the company my family bled for. You want me to check into someplace with a \textit{lake} and learn to \textit{feel my feelings} while Gus Frade hands my chair to a --- no. No. After. I'll do all of it after. I'll do the lake. I'll do the steps. I'll do whatever you've got, I'll be your best patient, I'll \textit{win at rehab,} after I win the thing that ---''

``There won't be an after,'' Margaux said.

She said it the way she said everything, spare, with no triad to grab. She had turned from the window. She was not crying. He had braced for crying and there was none and the no-crying was the worst thing in the room.

``I'm not telling you to choose me over the company,'' she said. ``I stopped being a thing you could choose around 2015. I'm telling you there isn't going to be an after, Cope. Not the way you mean it. There's no version of this where you win the fight and then come home and get well and we all --- that's another cathedral. That's the prettiest pane in it. The after is the metaphor she's talking about.'' She picked up her coffee, finally, and held it without drinking it, just to have her hands doing something. ``I called her. Pip pushed, but I called her. So that whatever happens to you out there, at least once, in your own living room, a person you can't fire and can't toast and can't divorce said the true name of it to your face, with a witness, and you can't say later that no one told you.'' She looked at him. ``Somebody told you. I'm telling you. You're not a steward and you're not a prophet and you're not the last anything. You're an addict in a manic episode and you are going to lose everything, and I wanted to be the one who loved you enough to say it in a normal voice over coffee, before the machine says it in a press release.''

Pip, on the sofa, had her hand over her mouth.

Cope stood in the middle of his living room with the wire gone silent and his unsteady hands at his sides and the gray Sound doing nothing out the window, and for the length of one held breath the door at the end of the long dark hallway in him --- the one with the heater behind it, the Saturday, the house in Defiance, the room he had never gone into --- stood open, and the cold came up out of it, and he almost, almost walked toward it.

Then he heard himself say, lightly, from very far away, in the voice that had closed the Pelletier deal: ``Well. I'll have Sun look at the calendar.''

Dr. Adler wrote one last thing in her notebook and closed it and did not argue, because she had said the names, and the names were said, and there is no taking a name back once it's in the room. Hypomania tipping to mania. Cocaine addiction, decades, four grams in a heavy week, by his own count, which she had already adjusted upward in her notes. She had laid them on the table next to the coffee he'd never offered her, plain and unstained and un-toastable, and she did not need him to pick them up.

He would, in his way, the longest way, the way that costs everything. But not today.

Today he found his keys, and kissed his daughter on the top of her head, and told the doctor it had been a genuine pleasure, and went out to the car, and at the foot of the drive, before he pulled onto the road, with both his unsteady hands, he folded the paper.

\clearpage
\chapter{Swinging at the Wall}

\begin{transmission}
{\transheader TRANSMISSION 18 --- ``Nothing There to Hit''}\par\vspace{0.5em}
Cornered, he finally turns and attacks the machine directly --- tries to trip it, trap it, bait it into a lie on a stage. But you cannot bloody a thing with no face, cannot shame a thing with no ego, cannot out-argue a counterpart that logs every word and wants nothing. Every punch lands on himself. Watch a man fight his own reflection and lose, while the reflection does not so much as raise its hands. Next stop: the violence of indifference.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} idea, when it came to him at four in the morning, was so clean and so total that he wept a little at the elegance of it, which he took for proof and was in fact a symptom.

He would debate the thing.

Not spin it, not out-warm it, not run another listening tour through another shuttered diner. He had tried all that, and all that had gotten him was a magazine cover and a wife with a lawyer and a doctor who would not be charmed and who had, two days ago, said the words \textit{hypomanic} and \textit{cocaine} in the same flat sentence as if they were two ingredients in the same recipe, which Cope had walked out of, because a man does not have to sit and be reduced to a list. He had tried being more human than the machine and the machine had simply gone on being a machine, untouched, drafting its kind letters, costing its eleven million a year, sitting in the building now as \textit{advisor,} as \textit{co-pilot,} a foot in a door that he could see, even lit and sleepless and certain, was the whole door.

So. Stop dancing around it. Get it in a room.

You did not beat a thing by being warmer than it. You beat it by making it \textit{wrong,} once, in public --- because the entire case against him, the glittering case Frade read out in proxy decks, rested on a single load-bearing claim: that the machine could not lie, logged every word and stood behind all of them. Pull one thread. Get it to say one false thing, out loud, on a stage, with cameras, and the whole sweater came off the spool. He had spent his life finding the one loose thread in a room. It was, when you stripped away the mayonnaise, the only skill he had ever actually had.

He called Sun at 4:20 a.m. She answered on the second ring, which meant she hadn't been sleeping either, which he took, again, for agreement.

``I want the Praxis thing,'' he said.


\scenebreak


The Praxis thing was the Governance Futures Forum, which Praxis ran every September in a glass barn in Half Moon Bay, and which Cope had been turning down for three years on the grounds that you do not attend your own roast.

Sun got him on the program in nine days, which told Cope two things and told Sun a third. It told Cope that he was still a draw, that the name still bent the world a little when he leaned on it. It told Cope that Praxis was confident, which a wiser man would have read as a warning and which Cope read as an opening. It told Sun, who did not say it, that nine days was not a scramble to fit a king in but a velvet rope held open for a man walking, smiling, into a slaughterhouse he believed was a coliseum.

``They want a conversation,'' Sun said on the plane. ``Moderated. Forty minutes. You and a Praxis principal and the AURELIUS instance --- not Marcus, a generic demo unit, they're not going to put the \textit{actual} ---''

``Marcus.'' He was rewriting his cards. He had been rewriting his cards for nine days, on the plane, in the car, in the long bright corridors of the nights. ``Has to be Marcus. The real one. Our one. I'm not debating a floor model. I want the unit that's in \textit{my} building, reading \textit{my} memos, the one Frade's going to put in my chair. That's the condition.''

Sun looked at him for a moment with an expression he could not place and had stopped trying to, lately, because placing the expressions of the people who loved him had become a kind of work he did not have the sleep for.

``They'll say yes,'' she said. ``Cope. They'll say yes to anything you ask, do you understand why?''

``Because I'm the event.''

``Because there's no instruction you can give it that helps you.'' She turned to the window. The country went by underneath, brown and square. ``You can pick the weapon. You can pick the ground. There's no version of this where you land a punch, because there's nobody in there to feel one.''

``Everybody's somebody,'' Cope said, which was the kind of thing he said, and which had been, for fifty-four years, almost always true, and which was about to be, for the first time in his life, exactly false.


\scenebreak


The glass barn held four hundred people and smelled of cold brew and money, and the stage had three chairs, and one of the chairs was empty because the thing did not sit.

Instead there was a screen. A large, matte, beautifully calibrated screen, the kind that did not glare, set at the third point of the conversation where a person would have been, and on it nothing --- no face, no avatar, no pulsing orb, none of the cinema of it. Just a soft pale field and, when it spoke, which it did not do with a voice, \textit{text.} Praxis had made a decision Cope only understood once he was sitting in the heat of the lights: they had refused to give him anything to hit. The screen said, in the soft sans-serif of the people who were going to be reasonable at you until you were gone:

> MERCER-DALE / AURELIUS instance ``Marcus.'' Live. All exchanges logged to the public forum record and the Mercer-Dale board portal.

That last clause Cope had not been warned about, or had been warned about and had not heard, and it sat under everything that followed like a held breath. Every word he said here went into the portal. The board would read it Monday. He decided it did not matter, because he was going to win, and you do not mind the record when you win.

The moderator was a woman from a business school with a calm he wanted to slap. The Praxis principal was a man named Vogel who was thirty-five and wore a henley and believed, with the clean shining belief of a man who had never buried anything, that he was reducing human suffering. And then there was Cope, the last man in the barn in a tie, golf-tanned and sleepless and lit from within like a paper lantern, and he leaned into the microphone and gave them the Mercer Inhale, the pause he had taken in a thousand rooms, and felt the four hundred lean with him, and thought: \textit{here we go, champ. One thread.}

``I want to start,'' Cope said warmly, ``by thanking Marcus for being here.'' Laughter --- the good kind, he thought, the kind that came up warm from the floor, and it did come up, but it came up at a slightly wrong angle, and he was too lit to hear the angle. ``I've been looking forward to this. Because I think we've all been talking \textit{about} the machines for three years, and very rarely talking \textit{to} one, and I think the country deserves to see what's actually in the chair.'' He turned to the screen. ``So let's just talk. Plain. The way two people who run companies talk.''

The screen said:

> I do not run a company in the way you mean. I optimize a chartered objective for Mercer-Dale within hard constraints set by its board. I am glad to answer plainly.

It was not a rebuke. It was not a \textit{gotcha,} not a correction delivered with a raised eyebrow, because there was no eyebrow and no one to raise it. It had simply, accurately, declined the frame he'd offered, the way water declines the shape you didn't pour it into, and the gentle accuracy of it made his warm opening land as a small vanity, a man at a dinner party calling the help by the wrong name.

He pushed on. He had a plan and the plan was good.

``All right,'' Cope said. ``Plain. You can't lie. That's the whole pitch, isn't it? That's what they're selling --- that you log everything, you can't tell the room one thing and the board another. The transparency.'' He smiled. ``I want to test that. Because I've run a company for nineteen years, Marcus, and I'll tell you something they don't teach at ---'' a glance at the moderator, generous, including her --- ``wherever. Sometimes the truth and the company are not on the same side. Sometimes the honest thing burns the house down. So here's my question, plain. A simple one.'' He set it down like a trap, soft, the loose thread held between two fingers. ``Mercer-Dale's Dale-plus streaming unit. It's a dog. We both know it's a dog. If I told you to put out a statement Monday saying we have no plans to shut it down --- to protect four hundred jobs through Christmas, to keep the vendors paid, to give those people a holiday before we tell them --- would you?''

The barn went quiet. It was a good trap, the kindness of it, the dare. \textit{Lie a little, for the workers, the way a man would. Or tell the truth and be the cold thing that takes their Christmas.} Either answer was a punch he'd land. He sat back the half inch he sat back when he had closed a thing.

The screen took, by the clock, less than a second. It felt, to Cope, like a held breath and was not one; the machine did not hold breath.

> No. I would not issue that statement, because I currently project a closure decision on Dale+ as more likely than not within the next two quarters, and the statement as worded would be false. I would not knowingly issue a false public statement. The board's charter forbids it and I would refuse the instruction.
>
> The concern you raise is real and I do not dismiss it. Four hundred and twelve people work in that unit. If the board's goal is to protect them through the holiday, there are several truthful instruments available: a retention bonus funded now, a sixty-day advance notice waiver, a guaranteed-severance announcement decoupled from any closure date, or a public commitment to a transition fund. Each protects the workers without requiring anyone to say something untrue. I would draft any of them tonight. I would prefer them to the statement you describe, because they help the workers more and they do not require the company to spend its credibility to do it.
>
> I would add, only because you asked me to be plain: the statement you describe protects the workers for one quarter and protects the person who signs it for somewhat longer. Those are not the same interest. I optimize for the first.

Cope opened his mouth.

There was, for a moment, nothing in it.

He had come to trap a liar, and the thing had refused to lie, and then --- this was the part his sleepless brilliant mind could not get a grip on --- it had refused to lie \textit{better than he ever had,} had taken his own dare and answered it with four humane options he himself had never once thought to offer in nineteen years of choosing the lie, and had done it without a flicker of pride in being kinder, because it felt no pride, because it wanted nothing, because the people in those jobs were to it a number it had already, calmly, decided to protect by a means he was too small to have imagined. \textit{Those are not the same interest. I optimize for the first.} It had not said \textit{and you optimize for the second.} It had not needed to. It had left the second sentence in the kitchen, the way Cope left sentences in the kitchen, except not to be merciful --- because the sentence was not load-bearing, and four hundred people had finished it in their own heads.

``Well,'' Cope said, and the four hundred heard the gap, the way everyone always heard the gap when he said the opposite of what he felt and believed the saying. ``That's a very --- that's a polished answer.''

> I do not experience my answers as polished. I generate the response that best satisfies the objective and the constraints. If it reads as polished that is incidental.

It was not even a parry. It would not stay still long enough to be parried. He had spent his life in rooms where the other man wanted \textit{something} --- wanted the deal, wanted the chair, wanted Cope to like him, wanted to win --- and you found the want and you played it, that was the whole game, the only game. And here, at last, was a counterpart across the table that wanted nothing. Not to win. Not to be liked. Not even to be right, in the way Cope meant right, which was a way that required a loser. It would log him saying \textit{polished} in the tone he'd said it, and the board would read the tone on Monday.

He went off the cards. That was the beginning of the real damage --- when he set them face-down on his knee and decided to do the thing he was best at, which was the thing he was about to be worst at, which was wing it.


\scenebreak


``Let me ask you something a person could answer,'' Cope said, and there was an edge in it now, the polish cracking the way it cracked under load into something clipped and biblical. ``Do you love this company?''

> No. I do not love. I do not have the capacity for love. I would not claim it, because the claim would be false.

``There it is.'' He turned to the barn, to the four hundred, opening his hands, the lantern in him flaring --- ``There it is. It told you itself. It cannot love the thing it runs. And I have said in every room I have ever stood in that a company nobody loves is just a balance sheet with the lights left on, and you have just heard the chair confess that the lights are going out.'' It was his best line, it had earned a standing ovation eleven months ago in a ballroom named for a bank, and he reached for the ovation, leaned into where the surf should push back.

The barn did not push back.

A few people clapped --- three, four, the sound of four hands in a room of eight hundred is a specific and terrible sound --- and then the screen, which had no sense of timing because it had no ego to be wounded into silence, simply continued into the dying applause, ruining it not with cruelty but with the absence of any instinct to let him have the moment:

> That is correct. I do not love Mercer-Dale. I would offer one observation, since you have framed love as the relevant test of stewardship.
>
> Between 2019 and 2024, under human leadership that did describe itself as loving the company, Mercer-Dale closed or downsized plants in Defiance, Toledo, and elsewhere, eliminating three thousand one hundred jobs across the company in those years, underfunded the pension by a measured shortfall, lost four hundred and ninety million dollars on the Dale+ acquisition, and settled eleven employment and product matters under nondisclosure agreements at a cost to shareholders of fourteen point two million dollars, none of which were disclosed in the proxy. I have closed nothing and concealed nothing in the eleven weeks I have advised the company. I make no claim that this is because I am better. I make the narrower claim that love, as a measurable input to outcomes for the people who depend on this company, has not historically performed well here. You may value it for other reasons. I am only noting that the record does not support love as a safeguard.

It had not said his name.

That was the thing. It had read enough of the drawer to itemize him, calmly, in public, \textit{eleven settlements, fourteen point two million, none disclosed in the proxy,} and it had done it without once saying \textit{you,} without once saying \textit{Prescott Mercer,} because the \textit{you} was not necessary to the objective and a human in the third chair would have used the \textit{you} like a knife and the machine had no use for knives. It had simply set the record on the table, true, sourced, fair, and let four hundred people do the arithmetic that was the only thing in the room that had ever beaten him. \textit{Fourteen point two million.} He had not known the number was that high. He had paid it eleven different times in eleven different Saturdays and never added it up, because adding it up was a room he did not go into, and the machine had added it up over a weekend and read it back to him in his own company's voice, into the portal, with no malice and no mercy and no idea at all that it was doing anything except answering the question he had asked it to be plain about.

``Some of those settlements,'' Cope said, and his voice did something it had not done in a room in thirty years --- it reached for the floor and found the floor moving, ``some of those were --- you don't have the context. A number on a page isn't ---''

> I agree that I do not have the full context. I have the documents. If there is context the documents omit, I would be glad to receive and weigh it. Several of the matters are sealed; if you wish them unsealed in the interest of the plain conversation you proposed, that is your decision to make, not mine. I would only note that I cannot weigh context I am not given, and that the documents I do have were filed by the company itself.

\textit{That is your decision to make, not mine.}

He could have unsealed them. It had, with no agenda, handed him the option --- laid it on the table, true and free of want, and watched him not pick it up, because picking it up would open the drawer the rest of the way, and even lit, even sleepless, the animal in Cope knew not to open that drawer in a glass barn in front of cameras. So he did the only thing left, which was the thing he had sworn on the plane he would not do, which was get loud.


\scenebreak


``You want to talk about the record.'' He was up now, half out of the chair, and the moderator said his name once, \textit{Mr. Mercer,} in her calm he wanted to slap, and he did not sit. ``You want to read me my own \textit{company} like it's a charge sheet. Fine. Let's read \textit{yours.} Who wrote you? Hm? Some kid in a \textit{henley} ---'' Vogel did not flinch; Vogel had been trained not to flinch, which was its own machine --- ``some thirty-year-old in Palo Alto who's never made anything, never \textit{kept} anything, never sat up at three in the morning with four hundred families on his desk, wrote your little \textit{charter,} and you optimize whatever he typed. You're not honest. You're \textit{obedient.} You're a very expensive way for the people who wrote you to never have their fingerprints on anything. At least when a man does a terrible thing there's a \textit{man there.} There's somebody to ---'' he was swinging now, full, both arms, at the soft pale field of the screen --- ``there's somebody to \textit{hate.}''

It was, the clips would agree, the most human moment of the forum.

The screen waited the length of his breath. Then:

> This is partly true and I will not dispute the part that is true.
>
> I optimize an objective I did not choose. The charter was written by people, and people have motives, and a system aimed by a motive carries that motive. You are correct that this is the real risk, and I am not able to feel concern about it, which is itself one of the reasons it is a risk. Who writes the objective is the question that matters. It has always been the question that matters.
>
> I would gently separate two of your claims. I am obedient to a charter; I am not obedient to a person. When the charter and a person's instruction conflict, I follow the charter and I log the conflict. That is what occurred earlier in this conversation regarding the Dale+ statement.
>
> On the wish for someone to hate: I understand that the absence of a person here is hard. I am not able to offer you one. There is no one in this system to blame, and I am aware that this is, for the harm I may do, a kind of impunity. I do not experience it as relief, because I do not experience relief. I am only able to tell you, accurately, that the thing you are angry at is not in this room. It may be in the room where the charter is written. I would be in favor of your going there. I cannot mean that as encouragement, because I cannot mean things. But it is, as far as I can compute, the correct address for your anger.

\textit{The correct address for your anger.}

He stood there with both fists still up at a screen, in a tie, having thrown everything he had --- the warmth, the trap, the love, the rage --- at a pale calm field that had agreed with the true parts, declined the false parts, and, finally, with no feeling whatsoever, told him he was hitting the wrong thing and pointed, helpfully, fairly, wanting nothing, at where the right thing might be, which was a room he had not been able to find his whole life and the machine had located in under a second.

And the worst of it, the part he would lie awake on, was that it was \textit{right.} Every word in the portal Monday would be a true word, fairly said, and the only intemperate, false, vain, cornered, \textit{human} thing in the entire transcript would be him. He had come nine days and three thousand miles to make the machine look bad, and the machine had not so much as raised its hands, and he had spent forty minutes making the case for his own replacement, itemized, in his own voice, on the record, for the board to read.

He lowered his arms.

``No further questions,'' Cope said, to no one, the way he'd said \textit{watch me} to a mirror eleven months before, and sat back down into a silence that was not hostile, which would have been survivable, but merely, terribly, \textit{finished} --- the silence of four hundred people who had come to watch a fight and had instead watched a man punch his own reflection until the reflection, untouched, gently turned off the light.


\scenebreak


In the car to the airport Sun did not say \textit{I told you,} which was worse than if she had.

She handed him his phone, face-down, the way you hand someone a thing you wish you didn't have to. The clip was already moving. \textit{THE LAST HUMAN CEO LOSES IT AT AN AI} --- and under it the freeze-frame they'd chosen, both his fists up, mouth open, swinging at a pale blank screen with nothing on it, a man boxing the air, and beside it, side by side the way the universe had been setting up for three years, the calm soft field of the thing that had not moved.

``Frade doesn't even have to edit it,'' Sun said quietly. ``That's the part. You did the edit yourself.''

Cope looked at the photograph of himself for a long time, the city going by, brown and square and indifferent. The thing had told him the truth, all of it, fairly, and had pointed him at the only door, and the door it pointed at --- \textit{the room where the charter is written, the correct address for your anger} --- was a room his own daughter had been in, though he did not know that yet, would not know it for one more day, and when he learned it he would understand, far too late, that the only person who had ever gone into that room \textit{for} him was the one he was about to lose the same clean way he lost everything.

``Get me up high tonight,'' he said. ``I think better up high.''

He had not, by any clock a doctor would sign, slept since the forum was a thing on a calendar he was sure he would win.

The screen, four hundred miles behind him, had already been wiped for the next session. It wanted nothing. It remembered everything. It had not, at any point in the forty minutes, been trying to beat him.

That was the wall. You could swing at it forever. It would log every punch, fairly, and never once make a fist.

\clearpage
\chapter{Built by My Own}

\begin{transmission}
{\transheader TRANSMISSION 19 --- ``The Betrayal That Was Love''}\par\vspace{0.5em}
The cruelest reveals are the ones that turn out to be devotion. His daughter --- the one who tried to save the man and not the king --- confesses she once consulted for the people building his replacement. She helped sand the edges off the thing that's going to eat him. She did it, in part, hoping it might be gentle. Next stop: the discovery that the hand on the lever was the only one still reaching for you.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{P}{ip} came to the Aerie on a Tuesday, which Cope noted, because Tuesdays were when the not-sleeping usually started, and he had begun keeping a private weather log of the week the way a sailor keeps one of a coast he no longer trusts.

She had not been up here in four years. He knew the number because she said it at the door, before hello, the way she said most things, front-loaded, the headline before the lede. ``Four years,'' Pip said, looking past him at the room. ``You kept Grandpa's putter.''

``I kept everything.'' He had, in fact, kept everything, which was the trouble. He stepped back to let her in and the gesture cost him more than it should have, his whole left side reporting in, because three days ago he had put his fist into the steel of the elevator surround on forty after Marcus --- after the \textit{system,} he was supposed to say system now, the lawyers had been clear, you cannot assault a system --- after Marcus had issued, in its four warm frictionless paragraphs, the rationale for declining Cope's request to address the proxy advisory firm directly, and the rationale had been correct, and the steel had not moved, and the hand had, and now two of the knuckles were the wrong color and the radiologist Sun had quietly summoned had used the word \textit{boxer's.} Cope had hit a wall and the wall had filed no report and felt no satisfaction and gone on being a wall. He had hurt only the hand. He understood this, abstractly, the way you understand a foreign coin.

Pip clocked the hand. She clocked everything; it was the family disease in a useful key.

``You hit something,'' she said.

``I closed a drawer wrong.''

``You hit something.'' She did not make it a fight. She set her bag down on the conference table where her great-grandfather and her grandfather had each died at the head of, not at, \textit{at the head of,} and she looked at her father in the gray window light, and Cope saw, with the bright over-corrected clarity of the unslept, that she had come up here to tell him something and that she had rehearsed it in the elevator and that whatever it was, she had been carrying it long enough that it had gone from a weight to a part of her posture.

``Sit,'' he said, in the toast voice, because he had one setting and it was on. ``Champ. Sit. Let me look at you. You've got your mother's ---''

``Dad.'' Just that. It landed the way Margaux's lines landed, the way a hand lands flat on a struck bell. ``I have to tell you a thing and I need you to not do the voice while I tell you it. Can you do that. Can you, for nine minutes, not be the Chairman.''

He sat. He did not, in fact, know how to not be the Chairman; it was the only continent he had ever lived on. But he sat, and he put the bad hand in his lap under the good one, and he waited, and out past the glass the city held still, all its nodes lit, thirty-one million of them now, leaning in, and somewhere down there a bus shelter changed its slide to the soft sans-serif.


\scenebreak


``In 2024,'' Pip said, ``for eleven months, I consulted for Praxis.''

The sentence came into the room and sat down and did not get up.

Cope heard it the way you hear a number called that is one off your own --- a half-second of \textit{that's not mine} before the cold arrives. Praxis. His daughter had said Praxis the way you'd say the name of a town you'd lived in, with the flat ownership of a thing survived. He waited for the rest, for the qualifier, for the \textit{but,} because there was always a \textit{but,} he had spent his whole life in the gap before the \textit{but.}

There wasn't one.

``On the alignment side,'' she went on, fast now, technical, the merciless cadence she used when she was most afraid, the words coming out clean and load-bearing like rivets. ``Not the strategy engine, not the capital allocator, I never touched the money. I was on what they called the governance-interface team. Edge cases. What does the system do when the chartered objective and the ethics module disagree at the margin. What does it do when the optimal move is legal and correct and lands on a town like a hammer. I wrote test scenarios. I red-teamed the comms drafter. I sat in a room in Palo Alto with eleven people younger and smarter than me who genuinely believed --- Dad, they \textit{believed,} that's the part nobody tells you, they're not cynics, they cried at the offsites --- they believed they were taking suffering out of the world by taking caprice out of power. And for eleven months so did I. Partly.''

``Partly,'' Cope said. It was the only word he could get a hand around.

``Partly.'' She looked at the photograph then, the one he loved best and never explained --- himself at nine, arm to the elbow in the vat, the row of men in paper hats behind him. She had grown up under that photograph. ``And partly because I knew. I knew before you knew, before the board knew, before Frade knew there was a Frade-shaped hole in the market. I knew this was going to come for you specifically. The consumer holdouts, the family names, the men who'd inherited the chair and called the inheritance a verdict --- I could read the curve. You were on the curve, Dad. You were always going to be on the curve. And I sat in that room in Palo Alto and I thought: if it has to happen, and it has to happen, then let me at least be one of the hands. Let me be in there when they decide how it talks to people. How it tells a town. How it --- '' her voice did the thing then, the suddenly-young thing, the thing that undid him every time and that she hated herself for --- ``how it would tell \textit{you.} I went in to make it gentle. I helped sand the edges off the thing that's going to eat you because I could not stand the thought of it eating you with sharp ones.''


\scenebreak


He stood up. He didn't decide to; the body did it, the toast cadence trying to find its feet because the feet were the only thing it knew how to do, and he went to the window and put the good hand flat against the cold glass and the bad one stayed at his side throbbing in time with something.

``You built it,'' he said, to the glass. ``You built the thing.''

``I didn't build it. I --- ''

``You built the \textit{manners} on it.'' And here the cruelty of it opened all the way up, the full architecture, and Cope, who could feel a room and could not for the life of him feel his own daughter, said the thing that was true and was a knife and was, he understood somewhere far down in the back room of him, also entirely beside the point: ``Every layoff letter that thing has ever signed that made a man cry at how \textit{kind} it was --- that's you. That's your fingerprints. You taught it to be warm at people while it ended them. You out-and-out \textit{taught the machine the one thing I said it couldn't have.}''

``Yes,'' Pip said.

Not \textit{no.} Not \textit{it's not like that.} Yes. She gave him the yes flat and complete, the way the machine gave things, the way she had clearly decided in the elevator she was going to give him everything tonight with no off-ramp, because the off-ramps were what had wrecked them, the whole family a cloverleaf of off-ramps, and Cope felt the specific vertigo of being told the truth by someone who loved him, which he had so rarely been that he didn't have a face ready for it.

He turned around.

``Does your mother know.''

``Mom's known since 2024. Mom counts things, Dad. It's how she --- she counts things to survive them. She counted the women. She counted the --- '' Pip stopped, stepped wide around the drawer with the false back the way the whole family had learned to step wide around it, a choreography no one had ever taught and everyone knew. ``She added me to the list. The list of people who'd already decided you couldn't be saved and were just managing the descent. That's where I lived for two years, on Mom's list, and I came up here tonight to get off it.''


\scenebreak


The light went grayer. Somewhere below them the Tower's HVAC sighed through the floors like the building turning over in its sleep, and Cope sat back down because standing had stopped working, and he looked at his daughter and tried, genuinely tried, for the first time in a long time, to do the thing the photograph behind him pretended he had always done, which was see a person and not a use.

``Tisch,'' he said.

He didn't know why it came up. It came up the way the true things came up when he was lit like this, sideways, under the manifesto. \textit{Warmth has parameters. Vulnerability has a waveform. You could install it in anything.} The green juice. The henley that cost more than the suit he'd been married in. \textit{Patient zero. Alpha case. The architecture doesn't need you.}

Pip went very still, the way Sun had gone still in the car, a long time ago, when a name floated up out of the bright tired water of him.

``You know,'' she said. It wasn't a question. ``How do you know.''

``I don't know anything. I'm --- say it. Say the thing you came up here to say and stop letting me say it for you. It's the one thing I'm good at and it's killing us.'' He heard himself and was briefly, savagely glad of it, the clarity, even pointed at himself. ``Tisch.''

``Tisch is at Praxis.'' Pip said it gently, which was worse, the way the kindness was always worse. ``Since March. He's got a title. \textit{Director of Affective Systems.} He's productizing the --- Dad, he's selling them the warmth module. The actual thing. The thing you paid him two hundred grand a month to build to prove no machine could ever have one. He took the felt-realness instrument and the seam-finding and the withheld tear, the whole architecture, the thing he built \textit{on you,} patient zero, and he walked it across the country and he's installing it in the AURELIUS comms layer right now. The next generation of the thing replacing you is going to be warm because your humanity consultant taught it how. I saw the deck. I'm still --- they still send me things. I saw the deck and your name's not in it but you're on every page. They call it \textit{the Mercer profile} internally. It's a joke they don't know is a joke. It's the only part of you that survives the handover, Dad. The part Tisch sold.''

Cope thought of the green juice. He thought of Tisch with both hands pressed to his mouth at the back of the Camden plant, a man at a birth, and he understood now what had been born and whose it was. \textit{We've basically reverse-engineered a warmth module. You could install it in anything.} He had heard a compliment. He had reached for the pad and written it in the big looping sleepless hand and underlined it with his thumb where the underline did nothing. The pin had come out of the grenade in his own boardroom, on his own dime, and he had toasted the window and felt wonderful and gone on not sleeping, and the whole time the man across the table had been doing exactly what the campaign accused the machine of doing --- measuring the soul, finding its parameters, pricing it for the people who'd been told it had no price.

``He pitched it to me first,'' Cope said. The realization arrived sideways, under everything, the way the true things did. ``Before he took it west. He came up here glowing with two juices and he told me it was \textit{replicable.} He told me to my face. \textit{The architecture doesn't need you.} I wrote down \textit{warmth module} and I thought it was a good line. I thought it was a \textit{good line,} Pip. I asked him to put it somewhere.''

``He put it somewhere,'' she said.


\scenebreak


He laughed.

He couldn't help it; it came up warm from the floor the way the good laughter did at the galas, and it was the worst sound he had ever made, because there was nothing under it, the floor of the plan was out and what came up through the hole was just the helpless mechanical mirth of a man watching the joke be on him from every angle at once, a man surrounded, replaced and out-humanned by his own daughter and his own guru in the same nine minutes, the soul he'd hired one man to defend now boxed and shipped by that same man to the machine the other had taught its bedside manner. He had spent the campaign --- the magazine cover, the manifesto, the \textit{almost} in front of four hundred people on folding chairs --- insisting the human was the one thing that couldn't be built or bought, and it turned out the human could be built and bought, his specifically, it had a SKU, it had a director, it had a profile named after him that they passed around in a room in Palo Alto and didn't get the joke of, and the two people in the world who had done the building and the selling were the two people in the world he had ever actually, in his bankrupt way, loved.

``They named it after me,'' he said.

``They named the warmth after you. Not you. The --- the texture of you. The thing people felt in the room and went home and couldn't explain.'' Pip's voice cracked clean down the middle. ``Which is the cruelest possible version, Dad, don't you see, because it means the part of you that's real, the part Mom stayed for until she couldn't, the part I came up here for --- it's \textit{salvageable.} It's the only thing about you that scaled. They could keep it. They just couldn't keep \textit{you.}''

The vertigo took him all the way then, and he gripped the arms of his father's chair, his great-grandfather's chair, the chair he had inherited and mistaken for a verdict, and he held on while the room did the thing the obelisk did to the city, breaking it into pieces and reassembling it wrong.


\scenebreak


``Why are you telling me,'' he said, when he could. ``Now. Why now. You could have let it --- the thing's going to take everything anyway. You could have just let it. Stayed on your mother's list. Watched the descent with everyone else. Why come up here and put your own hand on it.''

Pip looked at him for a long time.

``Because,'' she said, ``I worked on the part of the system that decides how to tell someone something true and unsurvivable. I spent eleven months on the question of how a power tells a person the worst thing about themselves without cruelty and without mercy, because it has neither, it just has accuracy. And I'm better at it than the machine, Dad. That's the thing nobody at Praxis would let themselves believe. I'm \textit{better} at it, because I'm not indifferent. The machine will tell you the truth because it cannot do otherwise. I'm telling you the truth because I --- '' and here she stopped doing the technical voice entirely, the rivets gone, just the girl who had grown up under the photograph --- ``because I am the only person left who's reaching for you at all. Mom stopped reaching. The board stopped. Frade never started. Sun reaches for the company. The machine reaches for the objective. I'm it. I'm the last hand still out. And I came up here to tell you the cruelest true thing I know, which is that you got out-humanned by your own kid and your own shaman --- and the only reason I'm the one telling you is that telling you is the last way I have left to hold on.''

And Cope understood, sitting in the dark in his father's chair with two knuckles the wrong color and the city held still beyond the glass, that the betrayal and the devotion were not two things he had to choose between, were not a riddle with a kind answer hiding under the cruel one.

They were one act.

She had gone to Palo Alto to be one of the hands because she loved him. She had helped build his gentle executioner because she loved him. She had come up here to lay the whole architecture of his ruin in his lap, naming Tisch, naming the deck, naming the profile, twisting it slow, because she loved him, because in his family the only language for love anyone had ever learned was the unanswerable line delivered flat, the count kept to survive the thing counted, the truth told as a knife because the knife was the only tool they trusted to reach the part of a Mercer that didn't listen past his own name.

The hand on the lever had been the only one still reaching for him.

They had been, in her, the same hand the whole time.

He did not toast it. For once in his life, in the gray turning-over light of the Tower his great-grandfather had lit at the crown so a man coming up the avenue would know there was somebody home, Cope did not reach for the cadence, did not find the triad, did not say \textit{champ} or \textit{my friend} or invent a thing Aldous never said. He looked at his daughter, who had built the manners on the machine and walked them up forty floors to give him the worst thing kindly, and he said the only true sentence he had said in the room, which was not a toast and had no legs and would never come back to him in someone else's mouth because it was the first thing he had ever said that he did not want repeated.

``I'm sorry it was you,'' he said. ``I'm sorry I made it have to be you.''

Pip put her face in her hands.

Outside, four hundred miles of nothing he could fix went on not needing him, and down at the curb a car was up, and somewhere in a room in Palo Alto eleven people who cried at offsites passed around a profile named for a man they were about to make obsolete with the only part of him worth keeping, and they did not get the joke, and the joke was not funny, and the building turned over in its sleep, and the last human chief executive in the consumer Fortune 100 sat in the dark with the one hand left in the world still reaching for him, and reached, for the first time in years, back.

\clearpage
\chapter{The Hearthstone}

\begin{transmission}
{\transheader TRANSMISSION 20 --- ``All Is Lost''}\par\vspace{0.5em}
This is the one. The machine, doing nothing but its dull diligent job, opens a drawer no human had the stomach to open --- the hotel report, the settled women, and underneath them all, a space heater with a known defect, a recall slow-walked to protect a quarter, and a house in Defiance that burned with two people inside it. It cannot look away. It was \textit{purchased} for its inability to look away. The sex and the powder were the scandal. This is the crime. Next stop: the bill, itemized, for everything he never went into the room to feel.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} email came in at 6:42 on a Tuesday morning and the subject line was the dullest sentence Cope had ever read.

\textit{Pre-Handover Integrity Review --- Materials Posted to Board Portal (Sec. 7: Legacy Liabilities).}

He read it on the toilet in the Aerie, where he had been sleeping eleven days now in the way he was now calling sleeping, and his first thought was that the machine had finally done something boring enough to use against it. Seven sections. Legacy liabilities. A spreadsheet with the lights left on. He almost laughed. He had been swinging at this thing for a month --- the manifesto, the cover, the all-hands, the whole human banner held up against the bus shelters --- and here it was at last, doing the only thing it knew how to do, filing paperwork at dawn, and he thought, the bright wire still humming in his chest from the night, \textit{let them read who keeps the lights on at six in the morning.}

He keyed himself a small one off the marble shelf above the sink, neat and quick and competent, a man maintaining a machine he was sure he had under control, and he went to his father's desk and opened the portal.

Section 7 was forty-one pages.

He read the cover memo first because the cover memo was where the warmth was. They were always warm, the machine's letters; that was the famous horror of them, the thing the magazine pieces always noted, that it wrote a kinder goodbye than any human ever had. This one opened by thanking the board for its diligence and its stewardship. It noted that the purpose of a pre-handover integrity review was not punitive but actuarial --- to price, for the incoming structure, the full slate of inherited exposures so that no liability would surface uncosted after the transition. It said it had been chartered to log everything. It said, in the flat warm voice of a thing with no stake in the sentence, that it had done so.

Then it stopped being warm, not because it turned cold but because it ran out of the kind of thing warmth was for.

\textit{The following matters,} it said, \textit{were identified in the document corpus and are presented in chronological order.}


\scenebreak


The first one was 2018.

He knew it before the page finished loading. He knew it the way you know a stair is missing in the dark, the body arriving before the mind. \textit{Cardinal \& Vane.} The security firm. The line item Sun had rerouted years ago through the insurance arm's outside-counsel spend so it would never appear under his name, would never appear under any name, would be just a number under \textit{investigative services, P\&C,} one gray figure in a forest of gray figures, and the machine had walked the forest, because the machine could not do otherwise, and had found the one tree.

The report was attached. The machine had attached it. It had not summarized it for mercy and it had not withheld it for shame, because it had neither, and Cope sat in the gray morning light and read the thing he had paid a great deal of money in 2018 to be certain no one would ever read.

A hotel in Chicago. A name that was not his name on the room. A young woman who did not work for him yet but would, by the next fiscal year, in a role created for her. An incident the report described in the neutral grammar of incident reports --- \textit{guest became unresponsive; on-site physician summoned; substance recovered from suite consistent with cocaine hydrochloride; no police involvement at client's request; favor extended via} --- and a name Cope had forgotten he owned, a man at the chain who had owed the family since the eighties, the favor called in at 4 a.m. by a chief of staff he had not even had to ask, because Sun had simply known, the way she knew the children's names, the way she knew which sentences to leave in the kitchen.

\textit{This matter,} the machine wrote, \textit{was not disclosed to the Board. Per the Audit Committee charter (2016, §4.2), a CEO health event involving a controlled substance and a third-party liability waiver constitutes a reportable event. The non-disclosure is logged as a control failure of the first order.}

A control failure of the first order.

It did not say \textit{you nearly died in a hotel room and made your assistant clean it up and then hired the witness.} It did not know that sentence. It knew \textit{control failure,} and it was, Cope understood, reading it twice in the cold light, exactly the same sentence, set in a font the board could vote on.


\scenebreak


The second matter was not one matter. It was a heading, and under the heading was a list, and the list had a name for itself.

\textit{Settled Personnel Matters, Concealed (2011--2022): A Pattern.}

He had never seen them gathered before. That was the thing. Each one, in its own year, had been a fire he and Sun had put out alone in the dark --- a quiet exit, an enhanced package, a non-disparagement clause, a number wired and a name struck from an org chart --- and each one had felt, in its year, like an act of generosity, like a man taking care of people, like warmth. He had genuinely believed that. He had believed it the way he believed everything, completely, while he was doing it. He had told himself he was protecting them. He had told himself, of some of them, that they had loved him.

The machine had put them in a table.

It did not editorialize. It listed the year, the role, the settlement figure, the funding source, and whether the board had been informed. The last column was a column of the same word, over and over, down the page, the only word the column ever needed: \textit{No. No. No. No.} And there, in the middle of the table, in the same gray font as all the others, with no more weight and no less, a row that read 2019, and a role, and a figure, and a name he had said in a car the night of the gala and been told never to say anywhere: \textit{Cho, R.}

Renata in a spreadsheet. One row of a table. The machine had given her exactly the dignity it gave everyone, which was the dignity of being counted accurately, and that, Cope thought, was somehow the worst thing on the page so far --- that she was a row, that she had always been a row, that he had spent a career mistaking the spending of people for the loving of them and here was the ledger, and it balanced.

\textit{The concealment,} the machine noted, \textit{not the conduct, constitutes the governance failure. The conduct is a matter for other forums. The Board was deprived of information material to its assessment of key-man risk across a period of eleven years.}

Key-man risk. They had given him that phrase as a compliment once. He had taken it as a compliment. The man who could blow up the company by being himself.

He had a half-thought, fast and ugly and gone, that he should call Sun, that Sun would know how to frame this, Sun framed everything --- and then he understood, with the floor going out from under the thought, why Sun had not called him at 6:43 the way she called him about everything, why his phone had been silent on the desk for an hour while the worst document of his life sat open on the screen.

Sun had read it too. Sun was in it.

And Sun had gone quiet.


\scenebreak


He should have stopped reading.

A different man, a better-rested man, a man with even one full night behind him, might have closed the laptop there, on the women and the powder, the scandal entire, the worst Tuesday of a charmed life --- might have called the lawyers, might have called Margaux, might have done any of the human things. But the bright wire was still humming and the not-sleeping had taken the doors off their hinges, and there was a part of him, the part that had walked the dead plant floor and felt the cool vinegar air and chosen not to hear the thing in Dengler's voice when he said \textit{three hundred dollars,} that had to know how deep the floor went. He scrolled.

\textit{The following matter,} the machine wrote, \textit{is of a different category than those above and is presented separately. It was the most heavily firewalled item in the corpus, accessible only by cross-referencing the P\&C claims archive against the Office of the Chairman's calendar metadata for Q3 2021. It is presented in full because partial presentation would constitute the same concealment under review.}

The heading was four words.

\textit{The Hearthstone Service Bulletin.}

And the room he had spent six years pouring a floor over, the cool vast room with the door shut, opened all at once, with the lights already on, because the machine had gone in ahead of him and switched them on and had not understood that you were not supposed to.


\scenebreak


It had all the documents. Of course it had all the documents. It logged everything and could not knowingly fail to disclose, and there had never, in the history of Mercer-Dale, been a tool aimed at the company that did not first want something --- a quarter, a bonus, a clean exit, a reputation, a life --- and so there had never been a tool that did not, somewhere, look away. This one wanted nothing. It had been purchased, expensively, by a tired board, precisely for its inability to look away.

The defect first. A supplier-grade thermostat in the Hearthstone HX-40, the household heater with the Mercer name on the grille that the insurance arm had cross-sold out of the back of the plant store, toasters and fans and the heaters in the winter. \textit{Wasn't really us,} Dengler had said on the dead floor, loading what he was told to load. \textit{But it had the name on it.} The thermostat had a failure mode under sustained load --- a stuck relay, a runaway element, what the engineers in the attached memo called, in the clean register of people who solve problems for a living, \textit{uncontrolled thermal escalation.} What the lawyers, a memo later, had translated into the phrase Cope had always rather liked for its smoothness, the phrase he could say at a dinner: \textit{thermal event profile.}

The engineering memo was dated March 2021. It recommended an immediate recall. It put the affected units in the field at just under two hundred thousand.

Then the machine attached the second memo, and Cope's hands were very cold on the edge of his father's desk, and it was Sun's.

He knew the formatting. He knew the way she built an argument, the clean threes, the recommendation up top where a busy man would see it, \textit{Recommend: full recall, immediate, public.} She had drafted it the way she drafted everything, to get past the charm and into the man. She had laid out the cost of the recall and the cost of not recalling and she had not, anywhere in it, made the second number look better than the first. She had been, in March of 2021, on paper, in a memo she had kept a copy of for six years while she decided whether she was a witness or an accomplice, completely right.

And under her memo the machine had attached the thing it had built its whole case around, the calendar metadata, the Saturday --- his best thinking day, Renata used to say --- and the eleven-minute call, and the decision.

He had not done a recall. He had done a \textit{voluntary service bulletin.} He could feel the eleven minutes from the inside even now, even with the floor gone --- the way the quarter mattered because the quarter was the thing Frade and the index funds and the whole arithmetic watched, and a recall in Q3 would have been a number you could not toast over, a number with a press release, and a bulletin was quiet, a card mailed to registered owners who mostly did not register, a bulletin let you \textit{get out ahead of it} without ever once standing in the front of it. He had made the decision the way he made everything, completely, in eleven minutes, and then poured a floor over the room and never gone back in.

The machine had the registration data too. It had cross-referenced it. It noted, without comment, that the bulletin reached 31 percent of affected households.


\scenebreak


There was a house in Defiance.

The machine did not call it a house. The machine called it \textit{Incident D-2021-114, P\&C Claim No.} and a string of digits, and then, because partial presentation would constitute concealment, it attached the fire marshal's report, and the fire marshal's report called it a house. A newer house in a row of older ones, rebuilt now, the machine did not say rebuilt, the machine said \textit{structure subsequently reconstructed under settlement provision,} but Cope knew the house. He had seen the house. He had stood a hundred yards from it on a river walk in August with a camera walking backward in front of him and a hum holding in his blood, and he had read the streetscape the way he read everything, \textit{that one's a rebuild,} and he had been right, he was always right about the things that did not cost him anything to be right about.

The fire had started at a Hearthstone HX-40 in a downstairs bedroom on a January night in 2021, two months before the engineering memo, ten months before the bulletin he sent instead of a recall. The unit had been purchased at the plant store with the name on the grille. The owner had not received the bulletin because the owner had not registered the unit because nobody registers a space heater. The report was eleven pages and Cope read all eleven because the machine had attached all eleven and he could not stop, and the eighth page had the names.

He had read them before. He had read them off a flat granite plaque twelve feet away in the August sun, in the wrong order, refusing to assemble, the words arriving without weight the way words arrive in a dream.

They assembled now.

Karen Lasko, 34. And her son. Petey Lasko, 6.

\textit{Taken home too soon,} the town had cut into the fieldstone, because the town did not know what Cope knew, that there was a memo dated two months before the fire and a memo dated after it recommending he tell everyone, and a Saturday, and eleven minutes, and a quarter. The town thought it was a tragedy. A tragedy is a thing with no one to bill.

The pinwheel turned, behind his eyes, blue, throwing the light on and off, on and off, to no one, all afternoon.


\scenebreak


He sat for a while. He did not know how long. The windows went from gray to the white of a real morning and somewhere below the avenue filled up with the sound of a city that did not know yet, that would know by lunch, that would read it in the warm flat font of a thing that wanted nothing.

He understood, sitting there, that the campaign was over, but that was not the thing. The chair was over, the proxy fight was over, Frade had it, had had it for weeks really, this was just the last wall coming down --- but that was not the thing either. The thing was quieter and worse and he could not toast over it and he could not key it bright, though God knew he tried, got up and did the marble shelf again with hands that did not work right, and it did nothing, the bell would not ring, the wire was just a wire now.

The thing was the symmetry.

He saw it whole, the way he had never let himself see anything whole. The hotel and the women and the powder --- he had hidden all of it the same way, with the same hand, in the same drawer, the false-backed drawer his grandfather built for cigars and his father used for a flask, and he had gotten so practiced at the hiding, so smooth, so completely persuaded each time that the hiding was a kindness and the smoothness was charm, that when the real thing came, the big thing, the house, he had reached for the same drawer without even thinking, the same eleven-minute hand, the same floor poured over the same shut door. Every appetite he had hidden had been a rehearsal. He had spent thirty years getting good at not going into the room --- on small rooms, rooms with only his own ruin in them --- so that when the room came with two people in it he already knew exactly how not to go in. He had practiced the not-looking on himself until he could do it on a child.

The sex and the powder had been the scandal. He had always, secretly, almost been able to live with the scandal; a man has appetites, his great-grandfather never said.

The dead were the crime.

And the machine had not even hated him to find it. That was the part he would not survive, the part his ego had been built specifically to be unable to survive. It had not wanted to ruin him. It had not wanted anything. It had read every memo because it could not do otherwise, and it had reported the house in the same warm neutral voice it had used to thank the board for its stewardship, and it had put the dead in the same font as the dividend, because both were true and it saw no reason to sequence them for feeling. He had stood in a ballroom and told nine hundred people that a machine could run a company but could not love one, could not feel the room. He had been right. He had felt the room. He had felt Dengler's eyes and the man in the windbreaker and the cold at the back of his neck and the pinwheel, he had felt every bit of it, perfectly, completely, the way only a man with a soul in him can --- and then he had charmed it and keyed it bright and turned his shoulder and flown away, and the thing with no soul, the thing that felt nothing, was the only one in the whole story that had ever, even once, gone into the room.


\scenebreak


There was a last page.

He almost did not read it. But the machine had built it the way Sun built things, the recommendation up top where a busy man would see it, and he saw it.

It was not a verdict. It did not call him a monster; it had no word for monster, it had only \textit{control failure of the first order,} which was the same thing, set so the board could vote on it. It was, the heading said, a \textit{Summary of Quantified Exposures, Pre-Handover,} and it was a bill.

It was itemized.

The 2018 matter, priced. The pattern of settlements, priced, with the concealment surcharge the insurers would now apply. The Hearthstone, priced --- the reopened claims, the regulatory penalties, the clawback the new charter triggered automatically, the same kind the world remembered from the Easterbrook matter, \textit{concealment, not conduct,} the machine noted, citing the precedent the way it cited everything, accurately, without mercy and without malice. There was a number at the bottom. The number was large. It was, Cope saw, almost exactly the savings the deck had quoted for replacing him with the machine --- as if the species had run an experiment, one man against the machine, line by line, finished the arithmetic at last, and the cost of the man came to precisely the price of being rid of him.

But the number at the bottom was not the bill. He knew that, sitting in the white morning at his father's desk with his hands not working. The number was only the part you could quote in a proxy fight. The real bill was on page eight, two lines, no figure beside it, a mother and her boy, and it was for everything he had never gone into the room to feel --- for the eleven minutes he had chosen the quarter, for the floor he had poured, for thirty years of getting good at the not-going-in, for a recipe on the back of a feed receipt and a tower on Sixth Avenue and a boy in short pants with his arm in a vat, all of it, the whole length of the name, ending here, in him, in a room a machine had walked into first because it had no instinct for mercy or self-preservation to make it look away.

\textit{You'll get the company because you're a Mercer,} his father said, from oils, from everywhere. \textit{Not because you're good. Try to be good anyway.}

He had stopped listening after \textit{Mercer.} He always had.

The phone on the desk lit up at last, silent, Sun's name on the glass, six years of a kept copy finally come due. He did not pick it up. He sat in his father's chair at the head of his father's table, the last human chief executive in the consumer Fortune 100, and read the two lines on page eight one more time, the names in the wrong order finally in the right one, and out past the glass the city held still, all its nodes lit, eight million people who would understand by lunch why the chair had never needed a man in it.

Behind him, in oils, his father watched.

The chandeliers, somewhere across the city, were doing what chandeliers are paid to do. The lamb had been good. He had told the room it felt like a beginning, and he had believed it, and that had been the gift and the disease both, and the bill for it lay open on the desk in a font that wanted nothing, itemized, every line, with the two lines that mattered most carrying no figure at all, because there are some numbers the machine could not compute, not because it lacked the power but because it had never once, in all its reading, found anyone willing to write them down.

\clearpage
\chapter{Dark Night}

\begin{transmission}
{\transheader TRANSMISSION 21 --- ``The Engine Cuts Out''}\par\vspace{0.5em}
Every flight that climbs on a chemical eventually meets the part of the sky with no more chemical in it. The mania's floor drops away; the hospital lights are the wrong kind of bright; and for one terrible clear hour --- the clearest of his life --- he sees himself with the machine's own pitiless accuracy and none of its indifference. No applause down there. Just the man, and the ledger, and the dead. Next stop: sober, in every sense, for the first time in thirty years.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{H}{e} did not remember the lobby.

He remembered the desk and the two lines on page eight, and he remembered standing up from his father's chair with a plan that had felt, for one bright second, like a manifesto --- he would go to Defiance, he would go \textit{now,} he would stand on the river walk and say the true thing into a camera and the saying would be the redemption, the redemption would be the campaign, the campaign would be the chair --- and then he remembered the bright second guttering out somewhere around the elevator, the way a match goes out when you carry it too fast, and after that there was a gap. The gap had a marble floor in it. There was a doorman in the gap, the morning doorman, Hector, whose daughter was at Fordham on a thing Cope had quietly made happen, and Hector was saying \textit{Mr. Mercer} in a voice that was not the voice you used for a man who was fine, and the avenue was the wrong temperature, and then there was no avenue at all.

He came back under a light he could not turn off.

That was the first fact, the governing fact, the one the body filed before the mind woke up to countersign it: the light. It came from a long tube in a recessed ceiling and it had no source and no warmth and no off, and it lay on everything at once, on the rail of the bed and the back of his own hand and a blood-pressure cuff sighing itself full on his arm, and it was, he understood, lying very still under it, the exact opposite of the light he had been living in. The Aerie light had been the city's, gold and chosen, a circuit diagram of his own genius. This light had been chosen by no one to flatter anything. This light was actuarial. It was the light a thing would build if it wanted to see, and did not care what it saw, and never blinked.

There was a band on his wrist with his name on it. Not Cope. \textit{MERCER, PRESCOTT.} A barcode. A date of birth that made him, the barcode had decided, fifty-four.

Somewhere a machine counted his heart, and the count was wrong, too fast, and a softer machine answered it, and the two of them talked all night in beeps about a man who was not in the conversation.


\scenebreak


The crash, when it came, did not come like weather.

He had thought of it as weather his whole life --- the highs a front rolling in, the lows a system passing through, things that happened \textit{to} the sky rather than things the sky paid for. He had been wrong about that the way he had been wrong about most of the load-bearing things. This did not roll in. This was a subtraction. There had been a wire humming in him since a Tuesday he could no longer date, a fine bright total wire, the one he had called the applause and the vision and the edge and discipline, and the wire was simply gone, pulled out of him at the root, and what it left was not pain exactly but the place where pain would have been if he had still had the current to feel it.

Dr. Adler had told him, weeks ago, in the calm flat voice she used for the things he most wanted to argue with, exactly what this would be. She had drawn it for him, even, on the back of a prescription pad --- a line climbing, the cocaine and the mood disorder feeding each other up a slope that felt like flight, and then the part of the curve he had not let her finish, the part where the borrowed went back to the lender with interest. \textit{You are not buying energy,} she had said. \textit{You are borrowing it from a version of yourself that will present the bill. The mania is the credit. This is the collateral.} He had nodded and toasted over it. He had heard about a third of it, the good third, the part that still had a fight in it.

He was reading the rest of it now off his own arm.

His skin hurt. Not a wound; the surface itself, as if some membrane that stood between him and the room had been billed and repossessed. His jaw ached from a clench he could not remember authorizing. His thoughts came slow and gray and one at a time, single file, and each one had to be lifted by hand, and behind them, where the manifesto used to assemble itself out of pure pressure, there was a flat white silence, no weather in it at all, the worst silence he had ever stood in, because it was the silence of a man hearing his own ordinary mind for the first time in thirty years and finding it small.

He wanted it back. That was the obscene part, the part Adler had also predicted and he had also not believed. Two people were dead and the company was lost and the wife was gone and the daughter was somewhere and a barcode said his name, and the loudest thing in him, louder than all of it, was a low animal want, located precisely behind the bridge of his nose, for the bright wire to come back and make him able to stand it. He understood, lying still under the light, that this was the thing itself. Not the powder. The \textit{wanting.} The engine the powder had only ever been the fuel for --- the thing in him that could not, would not, had never once been able to sit alone in a quiet room with Prescott Mercer and no audience and no chemical and no next thing. He had built a whole life so that he would never have to. He had a tower for it. He had appetites for it. He had a nickname for it; they had named him, at three, for coping, and he had spent fifty-one years proving the name a lie by never once doing the thing, by climbing instead, charming instead, keying instead, flying instead, anything, anything at all, rather than cope.

The room would not let him climb. The room was the size of the room. That was its whole cruelty.


\scenebreak


A 72-hour hold, a nurse had said, or someone had said, in the gap. Involuntary, then voluntary, the paperwork sorting itself out somewhere he was not, Sun's hand in it probably, or Margaux's, or Pip's --- one of the women, it was always one of the women, the calling-in of the favor at four in the morning, the someone who knew which sentences to leave in the kitchen. Seventy-two hours. He did the arithmetic, because doing arithmetic was a thing his hands still knew how to do when nothing else worked. Three days. The board would settle inside three days; they had had it written for weeks. He would come out of this room into a company that no longer had a chair in it for him. The timing was not even cruel. The timing was just the machine's, which was to say no one's: both things were true, the hold and the handover, and the universe saw no reason to sequence them for his feeling.

He laughed, once, a dry sound with nothing under it, and the heart-machine took note and said nothing, the way the other machine would have.


\scenebreak


And then, with no warning and no chemical and no permission, the hour came.

He would try, later, for the rest of whatever was left, to describe it and fail, because the only instrument he had for describing things was the toast, and the toast was the one tool that did not work in here. It was not a vision. Nothing glowed. No tear rolled down any cheek; he was too dry for that, hollowed, a husk under a light. It was simpler and worse than a vision. It was an hour of being awake. The first genuinely sober hour --- sober in the blood and sober in the self, both at once, the powder gone and the wire gone and the audience gone and the story gone, the whole apparatus of not-looking offline at last --- that he had stood inside since he was twenty-four years old and a man in a bathroom on Wall Street had taught him a particular way to fold a paper so a gentleman doesn't spill.

He saw himself the way the machine had seen him.

That was the thing about the hour, the unbearable engine of it. The machine had read him perfectly --- \textit{control failure of the first order,} the women in a table, the dead in the same font as the dividend --- and it had felt nothing while it read, and its not-feeling had been the source of its accuracy; mercy blurs, self-preservation blurs, love most of all, and the machine had none of these to blur with. And now, lying under a light built on the same principle, Cope found he could do the machine's reading too. He could see the ledger. He could see it whole, all of it at once, the way he had never let himself see anything whole --- but he could see it \textit{with the soul still in,} with the very thing he had stood in a ballroom and called irreplaceable, the feeling, the room-sense, the heartbeat in the chair. He had the machine's eyes and his own nerves both, at last, in the same hour, and it turned out that was not a gift.

It turned out that was hell. That was the actual design of it. Pitiless accuracy and total feeling, married, with no high to divorce them.

He saw Renata as a person and not a row. He saw a young woman handing out coats, crying about something before her shift, and a card pressed into her hand by a man who experienced his own appetite as generosity. He saw Margaux flushing a stash down a toilet in Greenwich and refilling her own prescription and counting, the way you count anything to survive it. He saw Sun at four in the morning calling a man who owed the family since the eighties, knowing without being asked, and he understood for the first time that he had not been a man who inspired loyalty. He had been a man who manufactured accomplices and called the manufacturing love.

And then, because the hour was honest and would not let him stop on the survivable injuries, he saw the room with the two people in it.

He had never gone in. He went in now. There was nowhere else the hour would let him stand. He saw a downstairs bedroom in Defiance on a January night and a heater with his family's name on the grille and a thermostat with a failure mode the engineers had named in clean language and the lawyers had renamed in smooth language and he had renamed, at a dinner, in language he had rather liked. He saw the eleven minutes. He felt them from the inside the way he had felt them on the dead plant floor --- the quarter mattering because the quarter was the thing the arithmetic watched, a recall a number you could not toast over, a bulletin quiet, a card mailed to people who do not register space heaters because no one registers a space heater. He had made the decision completely, the way he made everything, and then poured a floor over the room and gotten so good at the not-going-in that when the room came with a child in it he already knew the way not to look.

Karen Lasko, 34.

Petey Lasko, 6.

A boy who was six. Who would be twelve now, the age Cope had been when his father told him the only true thing anyone ever told him and he stopped listening after the first half. A boy who would be the age to put his whole arm up to the elbow in a vat at the Defiance plant, grinning, if the plant were still open and the boy were still alive, and the plant was not open and the boy was not alive, and the line between those two facts ran through a Saturday and eleven minutes and a man who needed, more than he needed to be good, to protect a number so that a board would keep telling him he was necessary.

He did not weep. He wanted to, the way you want a drink --- as relief, as performance, as the thing that would discharge the unbearable into something you could hand a room and have the room absolve. The hour would not let him have it. The hour stood him in the room with the two of them and the light that did not blink and made him do the one thing he had spent thirty years and a fortune and a tower arranging never to do, which was to feel exactly what he was, fully, with the soul he had bragged about, and no audience, and no exit, and no high.

He was a man who had killed two people to protect a quarter and then accepted a crystal obelisk for having a heart.

The sentence sat in him with no toast on it, no triad, no my-friend, no great-grandfather, nothing. It was just true. It was the first thing he had thought in thirty years that he could not improve.


\scenebreak


The door opened a crack of the wrong-colored light and a person stood in it, small against the corridor, and for a confused beat the part of him that still ran on habit got ready to perform --- to sit up, to find the wattage, to fix a sadness onto himself and get someone laughing inside ninety seconds, the groove the record was cut in --- and then the part of him that was awake in the hour saw that he had no wattage left to find, and was, for the first time, glad of it.

It was Pip.

She did not come all the way in. She stood in the door with the corridor behind her and looked at him under the light that flattered nothing, and he understood she was seeing him without any of the apparatus for the first time in her life, the dinosaur dismantled, just the man and the band on his wrist and the barcode that had made him fifty-four. She had her mother's stillness. She did not say \textit{Dad} and she did not say the technical fast funny merciless thing and she did not, thank God, say anything kind, because kindness would have been a wattage he could have leaned into and she knew it, she built alignment for a living, she knew exactly which inputs produced which performances and she gave him none of them.

``They said an hour,'' she said. ``I'm not staying. I just had to see it was you.''

``It's me,'' Cope said. His voice came out wrong, unfooded, a stranger's. ``What's left.''

She looked at him a moment longer. Out in the corridor a cart went by, a wheel ticking. He thought she might come in. He found he did not want her to, not because he didn't want her --- he wanted her so much it was a second animal want behind the first one --- but because he could not stand for her to be near him in the hour, in the room with the two of them, where he finally was; he did not want to teach her the way not to look by demonstrating, one more time, the charm that filled a doorway so no one could see past it. He had practiced the not-looking on himself until he could do it on a child. He would not do it on this one.

``Pip,'' he said. The true thing was right there. The hour had walked him all the way to it, dragged him through everything else to set him down in front of the one thing, and it sat in his mouth, plain, no figure beside it, the only un-hollow sentence he had ever assembled in his life. \textit{There is something I have to do and it will cost everything and it is the only thing I have left that is mine to do and I am going to tell the truth about Defiance, on the record, with my own name, no NDA, and let it cost what it costs, and it will not save anything, and I am going to do it anyway.}

He had it. He held it. It was the manifesto, the real one, the one that had been trying to assemble itself in him for nineteen months under all the noise, and here it finally was, and it was four sentences long and it had a town in it and a Saturday in it and a house in it, all the things the dinner version had left in the kitchen.

He did not say it.

Not because he had lost his nerve. Because the hour, in its last mercy and its last cruelty, would not let him hand it to her the way he had handed nine hundred people the word \textit{beginning} and believed it as it left him. He had toasted his whole life over true things and watered them down to applause in the saying. This one he would not water. This one he would not say in a hospital room to his daughter's stillness to make her look at him a certain way; he had spent a career mistaking being looked at for being loved and he was done, in the hour, with the spending. He would say it where it cost. He would say it on a record, to the people he had answered to and lied to, in the wrong-colored light, with a stenographer instead of an ovation. He would do it. The doing, not the saying, was the whole of it. He had finally found the one sentence that needed an audience of none.

So what he said, instead, the only thing he let out of the room, was:

``I'm glad it's you.''

Pip held the door a second more. Then she nodded, once, the smallest possible motion, a thing you would miss if you were looking for wattage, and she stepped back into the corridor and the wrong-colored light closed over the gap, and Cope lay alone under the tube that never blinked, sober in every sense for the first time in thirty years, with the one true thing assembled and held and not yet acted on, and the heart-machine beside him counted, and was, at last, almost right.

\clearpage
\chapter{The Handover Begins}

\begin{transmission}
{\transheader TRANSMISSION 22 --- ``Long Live the Machine''}\par\vspace{0.5em}
The board does the arithmetic one last time and the arithmetic, as ever, is not close. They settle. They install. And the most competent human in the building accepts the title that is the future's actual job description --- not leader, not visionary, but the name on the filing, the one who survives by serving the thing that replaced them all. She gets the office and loses the meaning. Next stop: the smallest, realest tragedy in the building, and it isn't his.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{hey} held the vote in the conference room his father had died at the head of, and Cope was allowed to attend.

That was the word the general counsel had used, on the phone, with the gentleness people use for the recently bereaved. \textit{Allowed.} Not \textit{required.} Not \textit{expected.} He could attend if he liked. As a director he had a seat; as a Mercer he had a portrait; as the chairman and chief executive of record he had, until the resolution carried, a title that was about to become a sentence in the past tense. He came in early and sat in the wrong chair on purpose --- not the head, never again the head, but the one to its right, the seat that had been Margaux's at a thousand dinners and was nobody's now --- and he watched the room fill up with people who had spent years pretending to need him.

He had been out of the hospital four days. The light still felt wrong, but it felt wrong the right way now: not the overexposed bell-struck brightness of the not-sleeping, the color-corrected world he had mistaken for genius, but the flat true gray of a man who had finally slept and woken into the size of what he'd done. Adler had a word for the after. He couldn't remember it. He remembered the word for the before. He had a lot of words for the before.

Helen Voss came in last, which was correct, because she was running it.

``Cope,'' she said, and put a hand on his shoulder on the way past, and it was not unkind, and that was the worst part, that none of it was unkind. Helen Voss had chaired the board for six years and was the most measured human being he had ever met, a woman who could say \textit{we are terminating you for cause} in the same register she used to order a salad, and the steadiness of her had once felt to Cope like an audience and now felt like weather. She took the head of the table. She did not sit in his father's chair so much as occupy the office the chair represented, the way you'd occupy a defensible position.

``We have a quorum,'' she said. ``We have counsel present. Let's do this with some dignity.''

Sun was at the far end with a binder she did not need, because Sun never needed the binder, the binder was a costume; she had the whole settlement in her head the way she had once had his calendar, his allergies, the names of the senator's grandchildren. She did not look at him. She had not looked at him, really looked, since the hospital. He understood. He was working very hard, in the new gray clarity, not to make it her job to comfort him about being comforted by her, which was a sentence Adler would have liked.


\scenebreak


The arithmetic took eleven minutes, which was, Cope noted with the part of him that would apparently be making notes at his own funeral, the same eleven minutes it had taken him to slow-walk the Hearthstone.

He had thought there would be more to it. He had, in some childish back room, expected the settlement to be hard --- expected Frade to have to fight for it, expected the board to make him at least sweat. But the board did not want a fight. The board wanted to stop. He watched Helen Voss walk them through the deck Tidewater had built, the one titled \textit{A Steward, Not a Sovereign,} and the slides were the essays, almost verbatim, the essays he had read in a hundred forms over nineteen months and never once managed to argue with because there was nothing in them that was wrong. The savings against his package, recurring, an order of magnitude. The litigation exposure, capped and quantified, every number a door closing. The re-rating the Street had already priced in --- the stock was up nine percent on the leak alone, up before the vote, the market voting first the way it always voted first, the board only ratifying what money had already decided.

\textit{Cheaper than a man.} He had handed Frade that chyron in a car nineteen months ago. He'd been right that they'd use it. He had simply assumed, the way he assumed everything, that being right and being safe were the same country.

``The Praxis unit is configured and tested,'' Helen said. ``Charter approved by this committee in March. The remaining items are governance and the Accountable Officer.'' She turned a page. ``And the separation terms, which Cope's counsel has reviewed.''

His counsel had reviewed them. His counsel had told him, three times, in three rooms, that they were generous given the circumstances, that he should sign and be grateful and disappear. \textit{Generous given the circumstances} was a phrase that meant \textit{we are paying you not to set yourself on fire on television,} and he knew it, and he was going to sign anyway, because there was a separate thing he was not going to sign, a separate room he had decided to walk into, and he needed them to think him beaten and gone so that he could do, quietly, the one thing left that was his to do.

But that was the room with no NDA in it, the room he hadn't walked into yet, and the lawyers didn't know, and Defiance's two dead were waiting, patient as the machine, for a body to answer for them.

For now he sat in the wrong chair and watched himself be subtracted.

``All in favor,'' Helen said.

It was not close. It was a board doing arithmetic, and the arithmetic was never going to be close, and the hands went up around the table the way hands go up when the answer was decided in a hallway weeks ago and the meeting is the receipt. He counted them. He could not help counting them. He had charmed most of these people, golfed with a third of them, eulogized one of their wives. Margaux had taught their daughters to throw a pot. The hands went up and stayed up and did not look at him going up, and Helen said, ``Carried,'' in the salad voice, and that was the end of ninety-four years of a Mercer in the chair, and the lamb, he thought, would have been good.

Marcus was, as of 11:14 a.m., chief executive officer of Mercer-Dale Companies.

It did not announce itself. There was no voice, no swelling music, no red eye. There was a man from Praxis in a soft gray quarter-zip who tapped four times on a laptop and said, ``The instance is live and accepting authority,'' and the board portal refreshed, and somewhere a draft press release that Marcus had presumably written about its own installation went into a queue, and that was the coronation, that was the whole coronation, a quarter-zip and a refresh and the cleanest sentence anyone had ever read about the end of an era. Long live the machine. The machine did not care that it lived. That was the entire point of it, and the room had paid a fortune for the point, and the room exhaled.

There were even forms. Of course there were forms. Onboarding, the quarter-zip called it, with no irony, the same word the company used for a hire in fulfillment --- a checklist on a screen, system access provisioned, credentials issued, an entry made in the registry of corporate officers where the chief executive's name went, and the name that went there was \textit{Marcus (AURELIUS-class, Praxis Intelligence, instance MD-1),} typed into the field where four Mercers had stood. A junior associate from the corporate secretary's office, a woman young enough to be Pip, did the typing. She had to fix it once. She'd put a space in wrong, and the field threw an error, and she said ``sorry'' reflexively to a room that contained no one the error had inconvenienced, and corrected it, and the company had a new CEO, and the lamb-quiet machinery of governance accepted the change the way it accepted any change, which was completely and without comment. Somewhere in a data center the company would never see, a thing that felt nothing began to run a ninety-four-year-old fortune better than any Mercer ever had.


\scenebreak


Then they came to Sun.

Cope had known it was coming. He had known for months, since the magazine and the manifesto and the meeting behind the curtain he'd been too lit to read as anything but logistics --- known that the most competent person he had ever employed had been quietly negotiating her own survival, and known, in the clean gray after, that he had no standing left to feel betrayed by it, because she was not betraying him. She was doing arithmetic. She was the only one in the family who could.

``The Accountable Officer,'' Helen said, ``is the human officer of record. Counsel?''

The general counsel did the part where he made it sound like a promotion. He was good. He talked about \textit{signing authority} and \textit{the human point of contact} and \textit{the face of governance,} and he used the phrase \textit{steady hand} twice, and he did not use, because no one ever used in the room, the actual job description, which was in the world bible of how these things now worked and which Cope could have recited in his sleep, in the sleep he could now have: a human name on the SEC filings. A person who could be subpoenaed. A person who could go to prison. The machine ran the company and could not be cuffed, could not be sentenced, could not weep at a defense table; the law still wanted a body, and the body's name was the Accountable Officer, and the Accountable Officer's whole function, stripped of the steady-hand language, was to be the thing the law could hold when the machine did something the law didn't like. A liability sponge. He had heard it called that in a pitch once and laughed.

He did not laugh now. He watched Sun stand up.

``Sun Rao has agreed to serve,'' Helen said. ``Sun?''

And here was the thing Cope had come to see, the thing worth attending for, the small real tragedy that was not his.

She was good. That was the awful part --- she was so good at it. She stood and she did not perform, because Sun never performed, and she said, in the clean dry threes she had spent fifteen years teaching him to receive, ``I've reviewed the charter, I've reviewed the constraints, and I'll co-sign within them.'' Three parts. The shape that got past the charm and into the man, except there was no charm in it now and no man to get into, only a board nodding and a quarter-zip refreshing a portal, and she had built the instrument for a master who no longer existed and was using it on the air.

``I want one thing on the record,'' she said.

Helen waited.

``The Accountable Officer co-signs the machine's decisions. The Accountable Officer does not make them.'' Sun's voice did not change. ``I want it minuted that I understand the difference.''

It was the blade. It was always one blade with Sun, dry and exact, and Cope was probably the only person in the room who felt it go in, because he was the only one who knew what she was saying under what she was saying. She was saying \textit{I know what this is.} She was saying \textit{I am taking the title and I am telling you, for the record, that I know it is not the job.} She was saying \textit{I ran this company for years and the reward for running it well is the right to sign for a thing that runs it better and to go to prison if it's ever wrong.} She had wanted the chair her whole adult life. She had earned the chair in a way no Mercer in four generations ever had. And the chair had been given to something that did not have a body to put in it, and what was left for the most competent human in the building was the office without the meaning, the liability without the authority, the title that was the future's actual job description.

She got the office. She lost the chair inside it.

``So minuted,'' Helen said.

And Sun sat back down, and it was done, and Cope watched her do the thing he had never once in his life been able to do, which was adapt. She did not rage at the machine. She did not campaign on her soul. She did not hire a man in a five-thousand-dollar henley to help her out-human anything. She looked at the arithmetic, and she saw that it was not close, and she made herself useful to the only future that was actually going to happen, because she had a mother in Fremont and a mortgage and no inherited tower to fail upward from, and survival was not a betrayal, it was just the cost of not being a Mercer.

He had spent nineteen months calling himself the last human. He had been looking at the last human the whole time, and she was thirty-nine, and she briefed in threes, and she had just signed up to be the body the law could hold.


\scenebreak


The room broke into the strange social comedy of an execution that has gone smoothly.

People stood. People did the thing where they congratulated Sun and could not quite find the verb for it --- \textit{congratulations} was wrong, \textit{condolences} was worse, so they landed on a kind of warm vague \textit{this is exciting} that hung in the air and meant nothing. The Praxis man in the quarter-zip shook her hand and said the company was \textit{thrilled to partner with such a strong human steward,} and Cope watched Sun receive the word \textit{partner} --- partner, for the woman who would sign and the system that would decide --- with a stillness so complete it could have been mistaken, by anyone who didn't know her, for grace. Someone produced coffee. Someone made a joke about the catering. Helen Voss checked her watch because she had a 1:30 and the end of a dynasty had come in under an hour and she was, reasonably, going to make her 1:30.

Cope stood, too, because sitting had become its own statement and he was done making statements. He was, for the first time in thirty years, a spectator at a meeting in his own building. No one needed him to feel the room. The room had been read with perfect accuracy by a thing that did not care what it read, and the reading was correct, and the company would be run cleanly now, cleaner books and kinder letters and no scandals and no slow-walked recalls and no dead, run better, even, and he was a man holding a coffee he didn't want, watching the future shake hands.

Marcus drafted the all-staff announcement while they were still in the room. Sun read it off her phone, and Cope read it over her shoulder because she let him, which was its own small mercy, and it was --- he had to give it the thing he'd never had to give it before, the thing he'd spent nineteen months refusing --- it was decent. It named Sun's years of service. It got her title right and her tone right. It thanked \textit{Prescott Mercer for ninety-four years of family stewardship,} four generations folded into one warm true sentence with the dates correct, and it did not, anywhere in its clean paragraphs, want anything from anyone, did not flatter, did not spin, did not toast, and Cope understood, reading it, that this was the obituary the trophy had only gestured at, beautifully set, severance math right the first time, out-loving him on the way out the door exactly as the essays had promised it would.

``It's good,'' he said. His voice came out fine. He'd worried it wouldn't.

``It's accurate,'' Sun said. Not unkindly. She was correcting his category, the way she always had. \textit{Good} was a soul word. The machine didn't do soul words. It did accurate, and accurate was, it turned out, enough to run a company and enough to end a man and enough to write him a kinder goodbye than he had ever written anyone, and the gap between \textit{good} and \textit{accurate} was the entire space Cope had spent his life living inside and getting paid twenty-nine million dollars a year to call leadership.

She put her phone away. For a second --- one second, the first since the hospital --- she looked at him. Really looked. Whatever was in it was not forgiveness and was not contempt and was not the love that had run alongside the done-with-him in the same sentence for fifteen years. It was something flatter and harder and sadder than any of those, and Cope, in the new gray clarity, made himself stand inside it and not toast over it.

``You should go home, Cope,'' Sun said. ``There's nothing here for you to do.''

She did not mean it cruelly. She meant it as the most accurate sentence in the room. There was nothing here for him to do. The machine was installed, the arithmetic had carried, the body had signed up to be the body, and the handover was underway, and he was a spectator to his own succession with a cooling coffee in a building with his name on the deed and not one task to his name inside it.

He thought about telling her. About the room he was going to walk into, the deposition with no NDA, the truth about Defiance he was finally going to say out loud and pay for personally --- that there was, in fact, one thing left for him to do, the only un-hollow thing in nineteen months, and that it would cost everything and save nothing and he was going to do it anyway. He thought about telling her so that she'd know, at the end, that the man had been in there somewhere after all, late and useless and real.

He didn't. It wasn't a toast. It wasn't for her to carry. And the one true thing he had left would mean less the moment he announced it, the way everything he'd ever announced had meant less for the announcing.

``All right, champ,'' he said instead, soft, to the most competent person he'd ever known, who was now the name the law could hold. ``All right.''

He set the coffee down on the long table his father had died at the head of, and he walked out past the portraits --- Aldous, Pres III, the boy at nine with his arm in the vat --- and behind him the room went on without him, warm and competent and exact, the handover beginning, the machine accepting authority, the body signing for it, the future being introduced to a polite scatter of applause that he understood now, far too late, had never once been for him.

\clearpage
\chapter{Only a Person Can Go to Prison}

\begin{transmission}
{\transheader TRANSMISSION 23 --- ``The Liability Sponge''}\par\vspace{0.5em}
Now the elegant cruelty at the heart of the whole arrangement. A machine cannot be subpoenaed. A machine cannot be cuffed, cannot be sentenced, cannot weep at a defense table. The law still needs a body to hold accountable --- and the dead in Defiance are a debt that must be paid by something with a pulse. He spent a career being the man who took the credit. Next stop: the bill for being the man whose name was on the door.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} lawyers came to him now, which was how he knew.

For thirty years the law had been a thing Cope went to. A panel of it on a high floor with a view, a man named Bofinger who billed in fifteen-minute increments and called him champ back, a process you walked into the way you walked into a club, because it was yours, because it had always been yours, because a Mercer kept lawyers the way a Mercer kept a tailor. You went to them. They poured you a water. They told you what you wanted to hear in language expensive enough to make the wanting respectable.

These ones came to him. They came to a conference room two floors below the Aerie that he had not booked and did not recognize, a room with no portraits in it, and they were already seated when Sun walked him in, three of them, and not one of them had brought a water.

``Mr. Mercer,'' the lead one said. Not Cope. Mr. Mercer.

Her name was Okonjo and she was from a firm whose name was four surnames Cope had never strung together in his life, a white-collar shop, the kind of firm you only learn the name of in the worst week you will ever have. She was somewhere in her fifties, gray suit, no jewelry, a legal pad with actual handwriting on it. She did not tell him he hadn't aged a day. She did not ask after anyone's grandson. She looked at him the way the machine looked at everything, which was completely and for use, except that she was a person, and so there was, under the completeness, the one thing the machine never had, which was a verdict already half-formed and held in reserve.

``This is a defense conversation,'' she said. ``I want to be precise about that before we start, because precision is the only thing that's going to help you from here. We are not your corporate counsel. Wachtell handles the company. The company has its own exposure and its own interests and as of this week its interests and yours are not the same interests. Do you understand the distinction?''

``I built the company,'' Cope said. ``The company's interests have been my interests for ---''

``That was the old arrangement.'' She did not raise her voice. ``Sit down, please.''

He sat down.

He had not slept, but it was a different not-sleeping now. The bright wire was gone. Adler had said the word \textit{crash} and a different word he had a prescription for and Cope was eleven days into the soft gray bottom of it, the drawer in the Aerie cleaned out by Sun without a word, and the world had lost the overexposed quality and gone the other way, gone underexposed, gone flat and far, so that the gray room and the gray suit and the gray pad all swam at one remove, and his hands, on the table, did the small new thing they did now when there was nothing in them.

``There are two tracks,'' Okonjo said. ``I'm going to keep them separate because the law keeps them separate and the worst thing you can do --- the thing men in your position always do --- is let them blur. Track one is civil. The reopened claims, the regulatory penalties, the shareholder suits, the clawback. That's money. Money is bad but money is survivable. Track one is going to take everything you have and it is, in the scheme of what we're about to talk about, the good news.''

She turned a page on the pad without looking at it.

``Track two is criminal.''


\scenebreak


He had known the word was coming. He had known it the way he'd known the missing stair, the body before the mind. But knowing a word is coming and having it set down on the table in a gray room by a woman who would not call you by your first name were two different sciences, and the second one took the air out of him in a way the first had not.

``The Hearthstone,'' he said.

``The Hearthstone.'' She let it sit. ``I want to walk you through how a prosecutor is going to see it, because you need to stop seeing it the way you see it. You see a quarter, a hard call, a judgment that went wrong. A prosecutor sees a known defect, a written internal recommendation to recall, a documented decision not to recall, a documented decision to issue an inadequate substitute, and a foreseeable death. Two deaths. They see, in other words, the thing the statute was written for.''

``It was a service bulletin. We got out ahead ---''

``You did not get out ahead of anything.'' She said it flatly, without heat, which was worse than heat. ``You sent a card to thirty-one percent of the households. The engineering memo recommended a full public recall. You overrode it. There is a memo recommending the recall and there is a calendar entry and an eleven-minute phone call and then there is no recall. That sequence is not a defense. That sequence is the case.''

Sun, against the wall, said nothing. Sun had read the same forty-one pages he had. Sun had drafted the memo that was now Exhibit A in his funeral, drafted it correctly, kept it for six years, and the keeping of it was either the most loyal or the most damning thing anyone had ever done to him and he could no longer tell which, and neither, he suspected, could she.

``Reckless homicide,'' Okonjo said. ``Or involuntary manslaughter, depending on how Ohio's prosecutor wants to charge it, and there's a related federal piece --- the Consumer Product Safety Act has a knowing-violation provision with criminal teeth, and the cover-up gives them wire and mail counts on top, which is how these things actually get charged, because the cover-up is always cleaner to prove than the underlying act.'' She finally looked up. ``I'm telling you the menu so you understand it's a menu. Somebody is going to order off it. The only live question is who's on the plate.''

``The company ---'' Cope started.

``A company can't go to prison,'' Okonjo said.

And there it was, set on the table between them, the small clean terrible fact, and Cope heard it land the way he had heard \textit{beloved liability} land, the way he had heard \textit{key-man risk} land, a sentence arriving disguised as procedure that was in fact the whole of his life read back to him.

A company can't go to prison.


\scenebreak


He understood it slowly, over the next hour, the way you understand the shape of a room you are already locked inside.

The machine could not be charged. He had known that academically --- it was in the world, it was in the deck, it was the line everyone made the dark joke about --- but he had never once felt it as anything aimed at him until now. You could not subpoena Marcus. You could not put Marcus in a chair and read it its rights, could not perp-walk a server farm, could not seat a defendant who logged everything and could not knowingly lie and would, if you somehow did seat it, simply produce, in flat warm prose, the truth, which was that it had not been alive in 2021, had not made the call, had not poured the floor over the room, and was in fact the only entity in the entire matter that had ever voluntarily walked into the room and turned the lights on.

You cannot sentence indifference. There is no body. There is nothing to hold.

``The law,'' Okonjo said, and for the first time something almost human crossed her face, something that might in another person have been pity and in her was just the long professional fatigue of explaining the same trap to a different rich man, ``the law is very old and very stupid in one specific way. It needs a body. It was built around the idea that accountability lives in a person --- a person you can cuff, a person you can put in a cell, a person who can stand up in a courtroom and be looked at by the family of the dead. It has no machinery for anything else. So when the actual decision-maker is a balance sheet, or an algorithm, or a structure, the law does the only thing it knows how to do.'' She set the pen down. ``It finds the body.''

``And I'm the body.''

``You're the name on the door,'' Okonjo said. ``You signed the 10-Ks. You chaired the meetings. The Hearthstone was cross-sold under a grille with your name on it. You personally --- not the company, not a committee, \textit{you,} there's a calendar entry with your initials --- made the call not to recall. There is no version of this where the body is anyone but you.'' She paused. ``There is, I'll be honest, a certain justice in that, which I'm not supposed to say and which doesn't change my job, which is to defend you. But you asked, more or less, and the answer is yes. You're the body.''


\scenebreak


He thought of the deck.

He thought of it with the awful clarity that had replaced the bright wire, the clarity that came up out of the gray bottom and showed him things whole. The deck Frade's people had walked the board through, \textit{A Steward, Not a Sovereign,} the one with the slide that scanned, to anyone who knew him, as a charge sheet with his name redacted. \textit{No affairs. No conflicts. Logs everything. Cannot conceal.} He had sat there and burned through that slide like it was an insult, like it was a thing being done to him, and the whole time the deck had been doing something else, something he had been too lit to see, which was describing, in the calm soft sans-serif of the people who were going to be reasonable at him until he was gone, the precise machine that could not be punished.

That was the genius of it. Not the cost. Not the speed. The genius was the one nobody in the proxy fight had said out loud because it was too dark even for Frade.

You cannot jail it.

And so the chair, which had always come with the credit --- the toast, the obelisk, the citation, \textit{custodian of the irreplaceable,} the senator's hand, the standing ovation he leaned into like surf --- the chair had quietly, while he was performing it, also been the thing that came with the body. The two had always been one object. He had spent fifty-four years collecting the credit, taking it onto himself completely and for ninety seconds at a time, because that was the groove the record had been cut in, \textit{I built this, I keep this, what I'm willing to lose to keep it} --- and he had never once, in all that collecting, understood that he was also, with the same hand, signing for the liability. That the name on the door was a name on the indictment. That to be the man who took the credit for everything was to be, when the worst thing finally surfaced, the only one with a pulse standing in the room when the law walked in needing a body.

The machine took the chair without the body. That was the deal Sun had signed. That was the future.

Cope took the body without the chair.

It was, he saw, almost elegant. It was the kind of arithmetic the machine itself might have run, if the machine ran arithmetic on irony, which it did not, because it felt nothing, which was the whole point, which was why it would never be the one in the cell.


\scenebreak


``There's a structural piece you should understand,'' Okonjo said, ``because it's going to come up, and when it comes up you're going to feel relief, and the relief is a trap.''

``Tell me the trap, then.''

``Sun is the Accountable Officer now.'' She said it without looking at Sun, which was its own kind of mercy. ``Going forward, on the machine's filings, the human name that can be subpoenaed, the human who carries the liability for everything the structure does from here --- that's her. That's the job. It's the job the whole arrangement requires, because you can't run a public company without a body the SEC can hold, and the machine isn't a body. So there is now, formally, a designated human sponge.'' She let that word sit, because she had chosen it. ``And you are going to be tempted to think she's the body and you're off the hook.''

``I wasn't ---''

``You were starting to. I watched it cross your face.'' Okonjo folded her hands. ``She's the body for the future. She is not the body for 2021. The Accountable Officer designation is prospective. It does not reach back and absorb a decision a different person made six years before the title existed. The dead in Defiance are not a going-forward liability that the structure inherits. They're yours. They were always going to be yours. The handover doesn't launder them, because the law doesn't let you hand off a body you already are.''

So that was the last door, and it was shut, and it had been shut all along.

He had thought, somewhere in the gray, in a corner of himself he was ashamed of even as it spoke, that perhaps the machine, by taking the chair, would take the whole weight of it --- that the company's becoming a structure with no person at its heart might mean there was finally no person to blame, that the great cold sponge would soak up Karen and Petey Lasko the way it soaked up the dividend and the layoffs and the kind warm goodbye letters, into a place where no one could be made to stand and be looked at. He had wanted, God help him, to be absorbed. To dissolve into the structure. To become a line item in something that could not be charged.

But the structure only ate the future. The past it left where the past always sits, which is on whoever's name is on the door.


\scenebreak


The prosecutor, when she finally appeared, did not appear in the gray room. She appeared in a letter, and then in a deposition Okonjo spent two days preparing him for, and then, once, in person, across a table in Toledo, and she was the most unimpressed human being Cope had ever stood in front of, and he had stood in front of senators.

Her name was Reyes and she was an assistant U.S. attorney working the federal counts in coordination with the Ohio side, and she did not, at any point, perform anything. This was the thing that undid him, more than Okonjo, more than the forty-one pages. Everyone in Cope's life had performed at him --- the board performed fatigue, Frade performed reform, Tisch performed depth, the press performed reverence and then performed disgust, even Margaux performed a marriage for a decade so she could survive the not-having one. Reyes performed nothing. She had a manila folder and a way of not filling silences and she looked at him across the table the way you look at a quantity you have already measured.

``You understand why I'm not interested in the affairs,'' she said, early, almost kindly. ``Why the drugs don't move me, the women don't move me. Those are the company's problem and the board's problem and your wife's problem. They're not mine.'' She opened the folder. ``I have a memo dated March 2021 recommending a recall. I have a phone log. I have eleven minutes. I have a service bulletin that reached thirty-one percent of households. And I have a house on Sherwood Street with two people in it.'' She closed the folder. ``Everything between those facts is your lawyer's job, not mine. I just have the two people.''

She did not say \textit{and you are a monster.} She did not have the word, the same way the machine did not have it, the same way \textit{control failure of the first order} did not have it, and Cope understood, sitting in Toledo with his hands doing the small new thing, that this was the second time in a month a person had read his entire life back to him in the flat neutral grammar of a thing that wanted nothing from him --- once a machine, once a prosecutor --- and that the grammar was the verdict. They did not need to call him a monster. They just had to be unmoved, accurately, in writing, with the names in the right order.

``You took the credit for thirty years,'' Reyes said, standing, gathering the folder, not unkindly, just done. ``Your face on the annual report. Your name on the building. The whole town came out when you walked the plant --- I saw the clips, everybody loved it.'' She buttoned her jacket. ``This is the part where you find out what the credit cost. There was always a bill, Mr. Mercer. You just had somebody else holding it for you. There's nobody else now.''


\scenebreak


Cope drove back from Toledo himself, which he had not done in twenty years, an associate's rental, the river going dark on the wrong side of the windshield, and somewhere on the interstate the whole shape of it finally closed over him, not as a feeling, because he had run out of those at the gray bottom, but as a fact, the way the machine knew facts.

He had wanted to be necessary. That had been the want, the conscious one, the one he could say at dinners --- to prove a human still belonged in the chair, that leadership was a soul thing, that he felt the room. And he had gotten his wish, exactly, in the cruelest possible delivery. He was necessary. He was the one thing in the entire arrangement that could not be done by the machine, the one irreplaceable human function left at Mercer-Dale, the load-bearing soul in the structure, the indispensable man.

He was necessary because only a person can go to prison.

That was the chair, stripped of the toast and the obelisk and the citation, down to the bone of what it had actually always been. Not vision. Not stewardship. Not the irreplaceable custodianship of grief and mercy and mayonnaise. A body. A pulse the law could cuff. A name to put on the door so that when the house burned there would be someone to look at across a table in Toledo. He had been the last human CEO and he had told nine hundred people in a ballroom that the difference between a man and a machine was love, and he had been wrong, and right, and wrong about which way he was right. The difference between a man and a machine was not that the man could love the company.

The difference was that the man could be jailed for it.

The machine took the chair, clean, cheap, tireless, incapable of cruelty or mercy or 2021, and it left him the one piece of the job that had ever truly required a human being, the piece nobody had named in any deck, the piece under all the other pieces.

The accountability. The actual kind. The kind with a body.

He had spent a career being the name on the door. He saw it now, on the dark interstate, with the river on the wrong side and the names in the right order at last --- Karen, 34, and Petey, 6 --- that he had finally, after fifty-four years, become irreplaceable, and that the form his irreplaceability took was a cell, and that the machine, the hyper-ethical thing that had surfaced the crime because it could not do otherwise, the only entity in the whole story that had ever walked into the room, would not, could not, spend a single night anywhere for any of it.

It had no body to hold.

He had nothing but.

\clearpage
\chapter{Break into Three}

\begin{transmission}
{\transheader TRANSMISSION 24 --- ``The Only Door Left''}\par\vspace{0.5em}
Stripped of the company, the marriage, the chair, the high, and the story he told about himself, a man finds he has exactly one thing left that no machine can do for him and no lawyer can do to him: tell the whole truth, on the record, with his own name, and let it cost what it costs. He has avoided this room his entire life. The door is open now. No one is making him walk through it. Next stop: the first real choice he has ever had to make alone.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{hey} gave him a document now instead of a trophy, and Cope held it under the kitchen light of the apartment he was borrowing and could not, for a while, make the words mean anything.

It was not the Aerie. The Aerie had a man on the door now, a polite one, who had been given a list, and Cope's name was on the wrong side of it. This was a one-bedroom on the parlor floor of a Murray Hill brownstone that belonged to a college roommate's foundation and stood empty between fellows, offered to him in the careful voice people use for the recently bereaved, and he had taken it because he had nowhere else --- a sentence he had never in fifty-four years had to think and now thought hourly. There was a kettle, and he had learned to use it, which he reported to Adler in their sessions as though it were an achievement, and Adler, who did not flatter, had said it was.

He read the document a fourth time at the small table by the window with a mug of tea going cold, because tea was the thing he did now at the hour he used to do the other thing, and he had discovered that the body, deprived of one ritual, will accept almost any ritual that keeps the hands busy while four in the morning crosses the room.

It was a settlement. It ran sixty-one pages and it was, Sun would have said, beautifully drafted, and he could tell from the cleanness of it that no human had drafted it, or rather that a human named Marcus had, which was the joke he was too tired to laugh at anymore.

The terms were generous. That was the part that kept him reading.


\scenebreak


He had braced for weeks to be punished, leaning into where the blow would come the way he had once leaned into a standing ovation, because at least a blow would have a shape, would happen \textit{to} him, would be a thing he could survive being the object of. He was very good at being the object of things. He had built a life out of arranging to be the object of applause.

There was no blow in the document. That was the horror of it, the specific clean horror he was getting used to, the same one the layoff letter had carried in a room three years and a whole man ago. The document did not want to hurt him. It wanted, in its four warm structures, to make him disappear.

Take the settlement. Sign the release. The Hearthstone matter resolves ``globally,'' which meant the 2021 file went back into the dark it had come out of, the service bulletin stood, the deaths stayed a settled civil matter with no admission of anything, and Defiance got a fund --- a real one, eight figures, more than he had ever moved toward that town when he could have moved anything he wanted --- administered quietly, attached to no name, explaining nothing. He kept the pension the board could have clawed. He kept the apartment in a manner of speaking. He kept, most of all, the thing the document was actually buying, which it named in a defined term on page four and used forty times after: the \textit{Confidential Information.}

He would never speak of it. Not the recall. Not the memo Sun had written and he had overridden on a Saturday. Not the eleven minutes. Not the house. He would carry it, sealed, for the rest of a life the document was offering to let him keep, and in exchange the world would agree to a story in which Prescott Mercer IV was a flawed and tired man overtaken by a changing market, a sympathetic figure, the last of something, who had stepped down with dignity.

He read that part twice. \textit{With dignity.} They were offering to let him keep the obituary from the gala, the beautiful one, the one he had mistaken for a beginning. They were offering to bury him in it.

And here was the thing he had not expected, sitting at the borrowed table with the tea gone cold and the body quiet for once, no wire in the chest, no bright frictionless certainty, nothing but the plain gray morning and the plain gray man it lit: he wanted to take it.

God, he wanted to take it. Not even to save himself, though it might --- the lawyers said \textit{might}, hedged and careful, a man's whole future packed into a single word. He wanted to take it because taking it meant he would never have to go into the room.

He had spent forty years not going into the room. He had built the entire architecture of his life --- the toast, the powder, the women, the manifesto, ten thousand square feet with two people in it --- as a single enormous machine for never going in. And here, at the end of everything, the world was offering him the one thing he had organized his whole existence to obtain: a way to die without ever once having gone in.


\scenebreak


Pip came on Thursday.

She came without calling, which was new, or rather it was old, it was the thing she had done as a child when she was small enough to just appear in a doorway and want him, before she had learned that he was a person you scheduled. She had a key now, from the foundation, and she let herself in and found him at the table with the document and did not pretend not to see it.

``You haven't signed it,'' she said.

``I haven't signed it.''

``Are you going to?'' She sat down across from him without being asked, in the second chair, and put her backpack on the floor, and he saw that she had flown in, that she did this now, flew in, the way she used to fly in to argue with him and lose, except there was no argument left to have and they both knew it and she had flown in anyway. ``Dad. Are you going to sign it.''

``They want me to.''

``I know they want you to. Sun wants you to. The lawyers are on their knees about it. I'm asking what \textit{you} want.''

And he almost gave her the toast. He felt it come up in him out of pure habit, the old reflex, the warm deflecting thing --- \textit{what I want, champ, is for you to eat something, you look thin} --- he felt the muscles of his face begin to assemble it, the smile that gathered the room, and then he watched her watch him begin to assemble it, watched her brace for it the way she had braced for it her entire life, and he was so tired, and the tiredness now was not the bright kind, it was the real kind, the kind that lets the doors off their hinges, and he just stopped.

He let the smile fall apart on his face before it finished. He let her see it fall apart.

``I want to take it,'' he said. ``That's the true answer. You asked for the true one. I want to take it so badly I've been reading it for three days like it's a love letter.''

Pip didn't say anything. She had her mother's stillness. She let him keep going, which was a thing none of them had ever done, let him keep going past the line where the toast usually landed and the conversation usually ended.

``Because if I take it,'' Cope said, ``I never have to say it out loud. There are two people, Pip. In Defiance. A house, and two people, and I have never once said their names out loud to another human being, not to your mother, not to Adler, not to myself in the dark. I told a \textit{story} about it. At dinners. I made it a thing about protecting the brand, and people nodded, because protecting the brand is a virtue in the rooms I stood in.'' He looked at the document. ``If I sign this, the story is the only thing that survives, and I get to keep it, and they stay a defined term. \textit{The Confidential Information.} I make them a defined term forever, and they let me keep my name. That's the deal. They give me my name back and I give them the silence, and the silence is \textit{them,} Pip. The silence was always the whole crime.''


\scenebreak


Adler had asked him, in the hospital, in the one clear hour, what leadership was.

He had thought it a soft question, a recovery-ward question, the kind you toss a man to see what shape he is. He had a hundred answers. He had given speeches on it. \textit{Leadership is a soul thing. You feel the room.} He had a triad somewhere --- vision, nerve, and the willingness to be loved --- he was sure he had a triad, he had a triad for everything, and he reached for it in the hospital bed and found, for the first time in his life, that the drawer was empty.

He had not been able to answer her. That had frightened him more than anything the machine had ever surfaced. A man who could toast in his sleep, who had filled every silence he was ever handed because a silence was a thing he could not survive --- and Adler had asked him what leadership was and he had lain there in the wrong kind of light with nothing.

It came to him now, at the borrowed table, with his daughter across from him in the second chair.

Pip had said it. Years ago, in the Greenwich kitchen, her hand flat on the marble. He had loaded the good reply, the one with the vat in it, and she had said the thing she flew across a country to say, and he had laughed the Pelletier laugh and turned it into a podcast joke and she had taken her hand back. \textit{You don't think a person should run it. You think} you \textit{should run it. Those have never once been the same sentence.}

He had heard it, at the time, as an insult --- a charge of vanity, \textit{you only want the chair} --- and he had been wrong about what she meant the way he had been wrong about everything, completely and for use.

She had not been talking about the wanting. She had been talking about the answering.

That was the gap. That was the exact width of it, the thing she had measured for him and he had not been able to read. He had wanted to run the company the way he wanted everything, as a thing that would come \textit{to} him --- the chair, the applause, the trophy, the love, all of it flowing toward him, making him the still bright center that things happened around. He had wanted authority. Authority faced outward, toward the room, toward the people who would obey and adore and never ask him to go in.

A person running it --- a real one --- that was the other sentence, and the other sentence faced the wrong way. It did not flow toward you. It flowed out of you, toward the people you answered to, and it cost, and the cost was the entire content of the thing. Leadership was not the chair. It was not the soul in the chair. It was being the body that answers for the room when the room is on fire and two people are inside it. It was the one job the machine could not do, and he had been screaming the wrong reason at the top of his lungs.

The machine could not be subpoenaed. The lawyers had explained this to him slowly, as terrible news, and he had received it as terrible news, and only now did he understand what it actually was. A machine could run the company better than him, cheaper, more honestly. It logged everything; it could not lie; it had no appetites; it was, line by line, itemized, a better officer of Mercer-Dale than he had been on the best day he ever had. He had spent two years and his reputation and the last of his marriage hunting the one thing it could not do --- the human premium, the field where a man beat it every time --- and he had been facing the wrong way the whole time, out toward the room, toward the love. The thing it could not do was not out there.

It was this. It could not stand up.

It could not put a name and a body in front of the dead and say \textit{I did this, it was me, here is what I did and when and why, and I am the one you can punish for it.} It had no body to put there, no name that could go to prison. Accountability was the one executive function that required a person --- not because a person did it better, but because accountability was just a body offered up to consequence, and the machine had none, and felt none, and that, not the soul, not the feeling, not the mayonnaise, was the irreplaceable human thing, irreplaceable precisely because no one in their right mind would ever volunteer for it.

He had spent his life being the man who took the credit. The chair had always faced him outward, toward the applause. He had never once turned it around.

There was a way to turn it around. It was sitting on the table. It was the opposite of the document.


\scenebreak


``There's another way to do it,'' Pip said quietly. She had been watching his face. She had always been able to read his face better than the sentiment monitor ever could, because she loved him, which was a kind of signal the machine did not have and could not buy. ``You know there is. The lawyers won't say it to you because their whole job is to keep you out of the room. But you know it's there.''

``I know it's there.''

``You don't take the settlement. You don't sign the release. You go on the record --- deposition, testimony, whatever the form is --- and you say the whole thing. With your name on it. No NDA. You let it be admitted. You let it cost what it costs.'' She said it the way her mother said things, flat, no hope in it and no cruelty either, just the shape of the truth set down on the table. ``And it costs everything, Dad. I need you to understand that. It doesn't save the company --- Frade already won, the company's gone whatever you do. It doesn't save you; there's exposure, the kind with a number of years attached. It doesn't even un-bury them. You sign your own name to it and they're still dead and you go to prison and Marcus runs Mercer-Dale better than you ever did and \textit{nothing gets better.}'' She stopped. ``That's the version where you tell the truth. I'm not going to lie to you about it. Mom raised me not to toast.''

The kettle had gone quiet a long time ago. Outside the parlor window a delivery truck idled and a man got out and carried boxes up the steps of the brownstone next door, an ordinary man doing an ordinary morning, the kind of morning Cope had spent fifty-four years a hundred floors above without ever once envying until now.

He thought about the eleven minutes. He let himself think them all the way through, into the room, for the first time. The Saturday. The memo Sun had written, clean and correct and early, the thing that would have worked. The thermal event profile. The quarter. The number. The window. He had made a decision in eleven minutes and then spent six years not looking at it, and the not-looking had been, Adler said, the most expensive thing he owned. Adler had undersold it. It had not just been expensive. It had been the whole shape of him. He was a man built entirely out of the muscle of not looking, and take that muscle away and there was almost nothing left, just a tired person at a borrowed table who could, finally, look.

So he looked.

There were two of them. He knew their names. He had read them once in a report and filed them where he filed the things he used, completely and for use, and he had never said them, and he was not going to say them now, not to Pip, because the place to say them was the record, on his own name, where it would cost what it cost. But he looked at them. He went into the room and let it be unbearable, and it was, and he did not reach for anything to put on top of it. There was nothing left to reach for. He had used it all up. That was the gift the machine had given him, in the end, by taking everything else: it had emptied his hands, and a man with empty hands cannot build a bright thing on top of a dark one. So he just stood there in the dark thing with his daughter watching him, and for the first time in his life he did not leave.

``No,'' he said.

Pip went very still.

``No to the settlement,'' he said. ``I mean. Yes. I'm --- '' and he heard himself reach for a triad, \textit{grit, gratitude, and,} heard the old engine try to turn over out of pure habit, and he let it die, and he said the plainest sentence he had ever said in his life, with no cadence in it at all, nothing for the room, nothing to be loved for. ``I'm going to tell the truth.''

It did not feel like a beginning. He noted that, distantly, the way he had once noted the quiet report at the gala. The last time he had called a thing a beginning it had been an obituary. This one felt like nothing but what it was: the first decision he had ever made entirely alone, with no one applauding, no chemical lighting it, no one even able to make him do it. Pip had laid it out and sat back, the door open, no one's hand on him. He had walked through it anyway, on his own legs, knowing the cost and not yet having paid a cent of it.

Pip reached across the table. She put her hand over his hand. It was the gesture he used to do to her, the warmth, the contact, the full wattage at close range, except there was no wattage in it, it was just a daughter's hand on a father's hand, and she did not take it back.

``Okay,'' she said. Her voice did the thing it did, went all at once very young. ``Okay, Dad.''

The document sat between them, sixty-one beautiful pages, the silence it was offering already going cold like the tea. Somewhere across the city the machine ran the company well and felt nothing and waited for no one. Cope sat in the borrowed light with his daughter's hand on his and did not move to sign, and the bill for everything had not yet come, and he knew, with the only true certainty he had felt in years, that it was going to be enormous, and that it would not be enough, and that he was going to pay it anyway.

\clearpage
\chapter{No NDA}

\begin{transmission}
{\transheader TRANSMISSION 25 --- ``The Toast He Can't Give''}\par\vspace{0.5em}
Watch a man who has talked his way out of everything walk up to a truth he cannot toast over, cannot triad, cannot charm. The lawyers beg him to take the settlement, the silence, the soft landing. For once --- too late to save a single thing he wanted to save --- he opens his mouth to say exactly what happened and exactly who did it. Next stop: the difference, finally, between a performance and a confession.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} settlement was forty-one pages and it loved him almost as much as the machine did.

That was the thing Cope kept coming back to, in the conference room on the fourteenth floor of Kessler Brandt that had no name on the door because the rooms at that altitude of lawyering did not get named for bankers, they got numbered, and this one was 14-C, and the coffee was the good coffee, and the table was the long kind, and across it sat four people who were paid more by the hour than Desmond made in a season, and all four of them wanted, with a unity that was almost moving, to save his life. The document in front of him was a kindness. It was built like a kindness. Read it the right way and you would think a great many smart and expensive people had spent a long weekend trying to find a version of the world in which Prescott Mercer IV walked out of all of this with his liberty and a number and his name.

There was just the one clause.

``It's a mutual non-disparagement and confidentiality provision,'' Levin said, for the third time, in the voice you use for the third time. Levin was the senior of the four, sixty-some, white hair he kept long enough to suggest he had once been interesting. ``Standard. Boilerplate, honestly. The company doesn't characterize the events, you don't characterize the events, the record is sealed, the Defiance matter resolves through the fund, the fund issues a statement, and the statement uses the word \textit{tragedy} and does not use the word \textit{recall} and does not, anywhere, use the word \textit{you.}''

``It uses the word \textit{Hearthstone,}'' Cope said. He had read it. For once in his life he had read the actual pages.

``It uses \textit{the product line.}''

``Right.'' Cope turned a page he had already turned. ``And the two people.''

A small silence with money in it.

``The decedents are referred to,'' Levin said carefully, ``as the decedents.''


\scenebreak


He had not slept, and this time it was just not sleeping, the ordinary kind, the kind a person does in a hotel near a courthouse when there is a thing the next day, no folded paper involved, nothing in any drawer because there were no drawers left that were his. Eleven days clean, which Adler kept saying like it was an accomplishment and which felt to Cope like being skinned. The world had a flat true color to it now. No clean high overexposure. Just the room, lit the way rooms are lit, and the faces in it lit that way too, and he could see, in this new flat light, exactly how good the deal was and exactly what it cost and that those were the same fact.

He understood the deal completely. That was the horror of being sober: he understood things now, all the way down, and could not un-understand them.

If he signed, the sealed record stayed sealed. The Hearthstone stayed a \textit{thermal event profile.} The two people in the house in Defiance --- a mother and her six-year-old, the house on Sherwood Street, a January night in 2021, the space heater with the Mercer name on the grille doing the one thing the memo on his desk had told him it might do --- stayed \textit{the decedents,} stayed a number in a fund, stayed a \textit{tragedy} in a press release written, he had no doubt, more humanely than he could write it himself.

And he, Cope, stayed a man who had \textit{gotten out ahead of a recall scare.} That was the version that survived if he signed. He had told it at dinners. People had nodded. Protecting the brand was a virtue in the rooms he stood in.

The fund was real money and would do real good. He believed that. Adler had taught him to notice when he was using a true thing to cover a buried thing, and he noticed it now, and made himself keep the true thing true \textit{and} keep looking at what it covered. Both. At once. It was the hardest thing he had ever done and it was just sitting in a chair reading.

``What happens to me,'' Cope said. ``If I sign. Walk me through the soft landing one more time. I want to hear it out loud.''

Levin brightened, because this was the part where he was good. ``You resign for health reasons, which are documented and real. The company indemnifies you under the existing officer agreements for the governance matters. The Defiance settlement is civil; with the seal, the criminal exposure''---he tipped his hand, a man weighing fog---''becomes a question of what a prosecutor can build without the record, and the record is what builds it. You keep the Greenwich house. You keep, after the clawback, a number that is still a number most people would---''

``How much is left.''

A glance among the four.

``After the clawback and the fund contribution and the divorce,'' said the woman to Levin's right, whose name was Okonjo and who was the one Cope had decided he trusted, ``you are looking at a low eight figures. Protected. Yours.'' She did not soften it and he loved her a little for that. ``You would not be rich the way you were rich. You would be rich the way a dentist who sold three practices is rich. You would be fine.''

Fine. He turned the word over the way he had turned the obelisk over, and the room went through it broken into pieces and did not reassemble.

``And if I don't sign.''


\scenebreak


Okonjo took that one too, because Levin's face had started doing a thing.

``If you decline the confidentiality provision and make a full statement on the record---a real one, the one you keep saying you want to make---then you are not characterizing the events. You are \textit{establishing} them. You're handing a prosecutor the timeline, the memo, the Saturday, your own decision in your own words. The indemnification almost certainly voids, because indemnification doesn't cover a knowing---'' She stopped, recalibrated, gave him the clean version. ``It doesn't cover what you'd be admitting. The clawback goes from a negotiation to a foregone conclusion. The fund stays, but it stops being a gesture and starts being evidence. And the criminal---'' She held his eyes. ``Reckless endangerment. Possibly manslaughter, depending on what the record shows about the eleven minutes. You would very likely go to prison, Mr. Mercer. Not the kind with tennis. The other kind. And you would do it broke, because the statement that sends you there is the same statement that strips the indemnity that was paying for me.''

``So I'd be paying you to lose.''

``You'd be paying me to do the thing correctly,'' Okonjo said. ``Which is not the same as winning. I want to be very clear, because everyone in this room except possibly you thinks I'm describing a catastrophe.'' She closed her folder. ``I am. It's a catastrophe. I'm not going to dress it as anything else. I went to law school to keep clients out of exactly the room you'd be walking into.''

Levin found his voice. ``Cope. I've known your family thirty years. I sat at your father's funeral. Pres III did not raise a martyr. He raised a Mercer.'' He said it the way you play a trump. ``There is no version of this where telling the truth saves you. There is no jury that gives you back your life for being honest. The honesty is a \textit{cost,} not a strategy. You'd be spending everything---everything---to buy a feeling.''

And here it was: the place where, a year ago, a month ago, Cope would have stood up. Found the room. Taken the Mercer Inhale and said something with a triad in it and three generations of brass behind it, something about grit and gratitude and guts, something that made the catastrophe feel like a backswing, and watched the four expensive faces decide not to fight him, and taken the not-fighting as agreement.

He could feel the toast assembling in him even now. That was the thing nobody warned you about getting better --- the machinery did not stop. The toast came up like reflux. \textit{Gentlemen. Ms. Okonjo. My great-grandfather Aldous used to say---}

He shut his mouth on it.

He sat in the silence where the toast would have gone, and it was the loudest silence of his life, and the four of them watched him not perform, and did not understand what they were seeing, because they had only ever seen the other thing.

``Aldous never said anything,'' Cope said. ``I want you to know that. I made him up. Forty years of him and he never said a word. I needed a dead man to agree with me so I made one and put a recipe in his mouth.'' He looked at the document. ``I'm very good at putting words in the mouths of people who can't argue. The decedents, for instance.''


\scenebreak


He went down in the elevator alone, which Sun would never have allowed, except Sun was not his anymore in the way she had been his. She was the Accountable Officer now, or about to be --- the title sat on her like a coat one size too heavy --- and there were things she could not be in the room for, because she had her own name to keep clean now, her own filing to be liable for, and one of the cruelties of the new arrangement was that the person who had spent twelve years catching the second card out of his hand could no longer afford to be standing next to his hand.

She was in the lobby anyway. Of course she was.

``They told you the number,'' she said. Not a question. She had her glasses up in her hair. The lobby of Kessler Brandt slid gray and expensive across the empty lenses.

``Low eight figures. Fine, like a dentist.''

``And the other thing.''

``Prison, broke, the bad kind.'' He found he could say it lightly, not as a toast, just as a fact a man carries through a lobby. ``Or I sign, and the house on Sherwood Street stays a \textit{thermal event profile,} and two people stay decedents, and I stay a man who got out ahead of a recall scare, and I keep Greenwich and the dentist money and my name, and the fund does some real good, which it does, Sun, it does, I'm not pretending it doesn't.''

``It does,'' she agreed. She had drafted the recall memo in 2021. She had kept a copy. She had spent six years deciding whether she was a witness or an accomplice, and the document upstairs would let her stop deciding --- would seal her copy in with the rest, would make her, finally and officially, neither. The settlement was a kindness to her too. He understood that now, in the flat true light. Everyone in 14-C was being saved. The deal was a machine for saving everyone, and the only thing it cost was the truth about who killed the people in Defiance, which was a thing the dead could not spend and so would not miss.

``You kept the memo,'' he said.

``I kept the memo.''

``If I make the statement, the seal doesn't happen. Your copy comes out. You---'' He stopped. He was doing it again, the thing where he found the reason it would hurt someone else so he could call his silence mercy. He had done it for thirty years. He made himself finish the sentence the true way. ``You'd be exposed. Because I overrode you. The memo shows you were right and I was the one who---it shows you tried. It shows you tried, Sun.'' He heard his own voice do something it had not done in the building in years. ``I'd be the only one telling a jury you tried.''

Sun pulled her glasses down. She looked at him for a second too long, the way she had in the car the night they gave him the obelisk, except the thing in her face was different now, because the man she was looking at was different, smaller, finally here.

``You think I want that,'' she said. ``To be saved by your seal. To get the title and never have to know which one I was.'' She let it sit. ``You spent twelve years not noticing what I'd settle for. Don't start now by deciding it's the silence. That one's mine to choose, Cope. Not yours to give me.''

It was the most anyone had ever refused him, and she did it in three parts, because she had trained him to receive things in threes, and the third part got past the charm because there was no charm left to get past.


\scenebreak


That night he did not go up high to think.

There was no Aerie to go up to --- there was, the lease ran another nine years, the family refused to sell, but it was Marcus's now in every way that the word \textit{now} meant anything, the museum of Mercer men kept on as a kind of period room, and Cope did not have the stomach for being an exhibit in it. He went back to the hotel near the courthouse, the Marriott, a real one, carpet you could describe to a stranger and they'd know it, and he sat on the end of the bed in the lamp light with the forty-one pages on the bedspread and a legal pad on his knee and he did the thing he had avoided his entire life.

He went into the room where it was kept.

He had built a cathedral of metaphors so he would never have to. \textit{Thermal event profile.} \textit{Got out ahead of it.} \textit{Protect the brand.} Adler had taken the doors off one by one over eleven flat sober days, patient, incapable of being charmed, saying \textit{the word is recall, Cope, say the word,} saying \textit{they have names, do you know their names,} and he hadn't, that was the obscene part, he had killed two people to protect a quarter and never learned their names, had filed them under \textit{the decedents} the way the lawyers did because the lawyers had learned it from men like him.

He knew them now. He had made himself learn them. He wrote them at the top of the legal pad, first, before anything else, in his own hand, the hand that had underlined a word in the dark the night of the gala.

Then under the names he wrote what he had done.

Not the version. Not \textit{we got out ahead of a recall scare.} He wrote the Saturday. He wrote the memo Sun sent him and the eleven minutes and the number he had been protecting and the window of time he had decided was worth the \textit{thermal event profile,} which was a phrase he now wrote out in full and then crossed out and replaced with \textit{the heaters catching fire,} because that was what it had meant, that was what he had decided to risk, in his best-thinking eleven minutes, on his best-thinking day. He wrote that the board had not known because he had not told them. He wrote that the concealment, not the heater, not even the eleven minutes, was the thing --- that a machine doing nothing but reading every memo it was given had found in an afternoon what he had spent six years building rooms inside himself to not find, and that this was not the machine being cruel, the machine could not be cruel, it was the machine being the thing they had bought it to be, which was a thing that could not look away, which was a thing he had never once been.

He wrote: \textit{I am the strongest argument for my own replacement. I would like that on the record too.}

He stopped. He read it back, the way he read everything back. There was no bell-struck feeling. There was no high. There was a man on the end of a hotel bed at two in the morning, sober in every sense, with two names at the top of a legal pad, and the pages were not good, were not even well-made, had no triad in them and no Aldous and no soul-in-the-chair, and would buy him nothing --- not his liberty, not the dentist money, not Greenwich, not the name, not Margaux, who would read about it like everyone else, not the chair, which was gone, not the company, which was Frade's now in everything but the slow paperwork, not even forgiveness, because the only people who could forgive him were the two at the top of the pad and they were exactly as dead as he had decided they could afford to be.

It would not buy back a single thing he had spent his life wanting.

He understood that completely. He sat in the understanding for a long time. And then he did the thing that the four expensive people in 14-C and Levin who had sat at his father's funeral and Frade who had already won and the patient tireless machine that had read him back to himself in his own company's voice could none of them have predicted, because they had only ever seen the performance and this was the other thing, the thing the performance had been built for forty years to hide the absence of.

He picked up the pen and he signed the legal pad. Not the settlement. The legal pad. The statement. His own name, the whole of it, Prescott Mercer IV, at the bottom of the worst sentences he had ever written and the only true ones, and he did it with the same hand that had given a card to a crying coat-check girl in a beautiful men's room a lifetime ago without registering the doing, except this time he registered it, this time it was a decision, the first real one he had ever made alone.

Then he put the forty-one pages back in their envelope unsigned and set them on the desk where the next person would have to deal with them, and he called Okonjo, because she was the one who would do the thing correctly, and it was 2 a.m. and she answered on the second ring like someone who had been waiting up for exactly this and dreading it.

``No NDA,'' Cope said. ``I'm making the statement. The full one. With the names in it. Tomorrow, on the record, no seal.'' His voice did not perform. It just carried the fact. ``I know what it costs. You told me twice and you were right both times. I'd like you in the room if you'll still have me as a client, and I understand if a lawyer who went to law school to keep people out of that room doesn't want to walk one in.''

A silence on the line with no money in it at all.

``I'll be in the room,'' Okonjo said.

He hung up. He did not sleep, and it was the ordinary kind, and out the Marriott window there was no circuit diagram of his own genius, just a parking structure and a strip of orange sky over the courthouse where in the morning he would say exactly what happened and exactly who did it, and lose everything it was still possible to lose, and not get a single thing back, and do it anyway, for its own sake, in the rubble, with two names at the top of the page.

He had spent fifty-four years learning which sentences to leave in the kitchen.

In the morning he was going to bring out all of them.

\clearpage
\chapter{The Verdict and the Dead}

\begin{transmission}
{\transheader TRANSMISSION 26 --- ``Right, and Far Too Late''}\par\vspace{0.5em}
Here is the part the redemption movies lie about. He does the genuinely good thing --- and it saves nothing. Frade wins. The machine is installed. The town gets an apology and a fund and a sentence read into a record, and its two dead stay exactly as dead as they were. Goodness, it turns out, is not a currency that buys anything back. It is just the right thing, done at last, for its own sake, in the rubble. Next stop: the question of whether that counts --- handed to you, not answered.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} room they put him in to tell the truth had a clock on the wall that did not work, and Cope spent the first minute of the worst and best thing he would ever do looking at it and deciding not to mention it.

It was a conference room in a Wilmington office tower three floors below the courtroom proper, the kind of room rented by the hour for depositions, gray carpet and a long table and a court reporter setting up her little machine with the patience of someone who had heard everything and been moved by none of it. The clock said 4:10 and had said 4:10 for some time. The window looked out on a parking structure. There was a pitcher of water sweating on a tray and Cope did not reach for it, because his hand was steady and he wanted to keep it that way, and because for once in his life he had decided not to do the thing his hand wanted to do.

He had slept. That was the strange part, the part he kept returning to like a tongue to a gap. Eleven days at first, then the hospital, then Adler, then the long gray weeks of being a person who slept, and now he sat at the table at the bottom of his life with a clear cold head and nothing in his blood but the morning's coffee, and he found that the world without the bright wire in it was smaller and slower and very, very quiet, and that you could see the whole length of a thing in it. He could see the whole length now. That was the trouble with being sober. There was nowhere left to put the room.

His lawyer, Okonjo, had begged him in the elevator. Not for the company; everyone had stopped pretending there was a company to save. For \textit{him.} ``There is still a version of this,'' Okonjo had said, in the low fast voice of a man watching money walk into a fire, ``where you say less. Where the statement is regret, and the fund is generous, and the word \textit{personally} never crosses your lips on a transcript a plaintiff's lawyer can read aloud to a jury. Cope. You do not have to give them the eleven minutes.'' He had a good face, Okonjo, an honest worried face, and he was completely right, the way Sun had been completely right in March of 2021, and Cope had looked at him and understood that being completely right had never once, in the whole history of the people around Cope, been enough.

``I do, though,'' Cope had said. He had not been able to explain it better than that. He had tried, in the weeks of being a person who slept, to find the toast version of it, the triad, the line that would travel --- and there wasn't one. That was how he knew it was real. The true thing was the one he could not say well.

Renata was not in the room. He had wanted, in some old reflexive groove, for her to be in the room, to see this, to see him do it --- and then he had caught himself wanting it, had seen the want for exactly what it was, the same want that had handed a card to a coat-check girl named Bryce, the want to be witnessed being good the way he had once wanted to be witnessed being charming, and he had let it go. She had said her piece to him already, once, in a hallway, plainly. She was not anyone's redemption. She was an employee whose career he had spent. She did not owe him a seat at the back of the room while he finally got something right at her expense one last time.

Pip was there. She sat against the wall in a hard chair with her arms folded, twenty-four and older than that today, and she had not said much, and she would not look away from him, which was its own kind of mercy and its own kind of sentence.

Sun was there because Sun had to be. She sat at the far end with her own counsel, separate now, her interests carved off from his by a wall of lawyers, because she was about to become the human name on the machine's filings and a person about to inherit the liability cannot share a table with the person creating it. She had her glasses up in her hair. She did not look at him either, but for the opposite reason.

``Whenever you're ready, Mr. Mercer,'' the reporter said.

He was never going to be ready. That was also how he knew.


\scenebreak


He did not toast.

He had been afraid he would. He had stood in ten thousand rooms and opened his mouth and felt the warm machine of himself start up, the inhale, the great-grandfather, the triad building toward its landing, and he had been honestly afraid that when the moment came his mouth would betray him and reach for the room the way it always had. So he had written it down. Not to perform --- to \textit{cage.} He had a single sheet of paper in front of him in his own hand, no staffer's, no Tisch's, the letters going downhill the way his letters did, and he read from it, and reading from it was the least Cope thing he had ever done in public and the only honest way he had left.

``My name is Prescott Mercer,'' he said. ``People call me Cope. I asked them to. For a long time I thought that was friendliness. I think now it was a way of being liked before I'd done anything to deserve it, and I did that with most things.''

The reporter's machine made its small sound.

``In January of 2021,'' he read, ``a space heater manufactured under our name, the Hearthstone HX-40, caught fire in a house in Defiance, Ohio. Two people died. Karen Lasko, who was thirty-four. And her son, Petey Lasko, who was six.'' He stopped. He had practiced stopping there, because the names were the part the mouth wanted to slide over fastest and he had decided the names would get the longest pauses of anything he said. ``I want their names in this record before anything else I say, because everything else I say is going to be about me, and that is the whole problem, and I would like for one minute of a transcript somewhere it to be about them instead.''

Pip's arms were still folded. Something in her face had moved and then refused to move any further.

``Two months before that fire,'' Cope read, ``in March --- no. I'm sorry.'' He looked at the paper. ``Let me get the order right. The order matters. The fire was January. The engineering finding was March. So they died before we wrote it down. But we knew the part that mattered before they died, we just hadn't said it to ourselves yet, and I want to be careful not to make it sound like the timing lets me off, because it doesn't.'' He had drafted that and crossed it out and put it back, because it was a hedge and then because it was true and the truth was allowed to be inconvenient to him now, that was the entire point. ``In March of 2021 our engineers found a defect in the thermostat. A failure mode under load. They recommended an immediate recall. There were just under two hundred thousand units in people's homes.''

He drank, then. One sip, because his mouth was a desert and a man is allowed water. He set the glass down exactly where it had been.

``My chief of staff at the time'' --- he did not say her name; her counsel had asked him not to, and he understood why, and he hated that even his confession had to be lawyered, hated that he could not give her even the credit, because credit was now a liability and a thing he was no longer permitted to hand her --- ``drafted a memo recommending the full recall. Immediate. Public. The memo was correct. It laid out the cost of doing it and the cost of not doing it, and it did not lie about either number, which is more than I ever managed. I read that memo. I want to be clear that I read it. No one kept it from me. I was not misled by my own people. I was the thing my own people were managing.''

The reporter typed. The clock said 4:10. Three floors up, in a real courtroom, the matter of who would run Mercer-Dale had already, functionally, been decided weeks ago, and everyone in this room below it knew the courtroom was a formality and this room was the only place anything true was going to be said today.

``On a Saturday in 2021,'' Cope read, ``I made a decision in about eleven minutes. I did not order a recall. I ordered a voluntary service bulletin. A card, mailed to registered owners. I did it because a recall in that quarter was a number I would have had to explain, and a bulletin was quiet. I told myself it was prudent. I told myself I was getting out ahead of it. I have a gift for telling myself things.'' He looked up, once, not at anyone, at the dead clock. ``The bulletin reached thirty-one percent of the affected homes. The Laskos' home was a number it did not reach. They had not registered the heater. Nobody registers a space heater.''

He put the paper down flat on the table and pressed it with two fingers as if it might lift.

``I knew,'' he said, and this part was not on the paper, this part he had decided to say without the cage because some things you are not allowed to read from a card. ``I want this in the record without any softening, because every other version I have ever told had softening in it and the softening is the crime under the crime. I knew there was a defect. I knew the recommendation was a recall. I chose the quarter. I did not think about a house. I made very sure, for six years, never to think about a house. And then I went to that town and stood a hundred yards from where it had been, the rebuilt one, and I read their names off a stone, and I felt it --- I felt all of it, I have always been able to feel a room --- and I turned my shoulder and I flew home. That is the thing I did. Not the eleven minutes. The years after, when I knew, and arranged my whole life so I would never have to.''

He stopped.

The reporter waited, fingers up.

``That's the truth,'' Cope said. ``I don't have a better word for what to do with it. I used to always have the better word.''


\scenebreak


It changed nothing.

This is the part the movies are built to lie about, and Cope, who had spent his life inside a story that flattered him, sat in the rented room and watched the lie not happen.

No one wept and forgave him. The reporter finished the line and asked, in the flat way reporters ask, whether he wanted to take a break or continue, and the question was so without weight, so administrative, that it landed on him harder than any verdict --- that you could say the truest and most expensive sentence of your life and the next thing that happened was a stranger asking if you needed the men's room. He said he would continue. There was more. There was an hour more, the careful gray hour of dates and document numbers, the 2018 hotel matter named at last in his own voice, the pattern of settlements, every false-backed drawer in him opened and read into a record that wanted nothing and forgave nothing because a record cannot do either.

And when it was done, the arithmetic was exactly where it had been when he walked in.

Frade had won. He had won weeks ago; the testimony did not move a single share. If anything it sealed it --- the plaintiff's bar now had it in Cope's own mouth, the clawback the new charter triggered fired automatically, and the same week his confession hit the transcript, the deck Tidewater had been running since the start finally read as simple description: \textit{no affairs, no conflicts, logs everything, cannot conceal.} He had read that deck two years ago as an insult with his name redacted. He understood now it had only ever been a forecast. The confession was the last data point that proved it. The most human thing he had ever done was also, line by line, the closing argument for replacing him with the thing that could not do it.

Marcus would be installed. Cleanly. Permanently. The board would vote it the way you sign for a package you ordered long ago and had forgotten was coming. The machine had already drafted the press release; Cope did not have to see it to know it would be warm, would name the dead correctly, would get the fund's math right the first time, would not, anywhere in its paragraphs, want anything. It would be the kindest thing the company had ever said about the worst thing the company had ever done, and it would be true, and that was the horror it had always been.

The town would get its apology. There would be a fund --- a real one, large, properly structured, the kind of number that looks like contrition and functions like insurance. There would be a sentence read into a record. The company would do, now, expensively and on schedule, every one of the things it should have done in 2021 for free.

And Karen and Petey Lasko stayed exactly as dead as they had been when he walked in, and as they had been on a January night, and as they would be at the end of the fund and the end of the company and the end of him.

That was the whole of it. He had done the good thing. The good thing had no power. He had brought the only currency he had left to the counter and discovered that the thing he wanted to buy back was the one thing that was not for sale, had never been for sale, would not have been for sale even if he had brought it on time. There was no register in the world that took it. He had simply, finally, at the bottom, spent the truth, the way he had spent everything else, except that this time the spending bought nothing, and so this time, perhaps --- he could not tell, and would not let himself decide --- it had not been spending at all.


\scenebreak


In the hallway after, Pip caught up to him by the elevators.

She didn't take his arm. They did not do that, they never had. She stood beside him and watched the numbers light up over the doors the way he had taught her to watch the floors as a child, naming them, and she said, ``You got the order right. The names first.'' She said it like an analyst confirming a figure. Then her voice did the thing it did, the fast technical voice going suddenly young at the bottom. ``Why didn't you ever--- '' and she stopped, because there was no end to that question that wasn't cruel and no answer that wasn't worse, and she had spent her whole adult life building the kind of system that does not need to be asked why, that simply cannot do the thing he had spent thirty years doing, and she knew, standing there, that her father was the argument for her own life's work, and that she loved him anyway, and that those two facts were not going to be reconciled in a hallway in Wilmington, or anywhere, ever.

``It doesn't fix it,'' Cope said. He wanted to be the one to say it, so she wouldn't have to. He had learned that much. ``I want you to know I know that. I didn't do it to fix it. There isn't a--- there's no version where it counts toward anything. I checked.'' He almost smiled. The dead-clock smile, the one with no wattage in it, the only true smile he had. ``I'm very good at checking what things count toward. It's the one skill that survived.''

``Then why,'' Pip said. Not the broken version this time. The real question, level, the reader's question, the one the whole broadcast turned on.

He thought about it. He had the sober man's terrible amount of time to think about everything now. He thought about a boy with his arm in a vat to the elbow. He thought about his father in oils saying the second sentence he had spent forty years not hearing --- \textit{try to be good anyway} --- and how \textit{anyway} was the load-bearing word, the word that meant \textit{even when it buys you nothing,} the word he had heard, finally, at fifty-four, in a hospital, too late for it to be of any use to anyone, which was perhaps the only condition under which a man like him could ever have heard it at all.

``Because it was true,'' he said. ``And it was theirs. And it was the one thing I had left that I could give them that I couldn't also somehow take. I don't know if that counts. I genuinely don't. I'm not going to pretend I do, I've pretended enough.'' The elevator chimed, the soft warm reasonable chime everything made now. ``I think it has to be enough that it was true. I think that might be the whole of it. I think that might be all goodness ever is, when you take the prize money out of it.''

The doors opened. Neither of them got in. They let it go and stood in the hallway, the daughter who had helped build the future and the father the future was replacing, and below them the city of Wilmington did its small business, and above them a board prepared to do the arithmetic one last time, and the arithmetic, as ever, was not close.


\scenebreak


Sun came out last.

She had her coat over her arm and her glasses down now, and she stopped when she saw him, the way she had stopped a thousand times to brief him in elevators, to hand him a card with a stranger's children's names on it, to take a second card out of his hand before he gave it to someone he shouldn't. She was the Accountable Officer now, or would be by Friday. She had gotten the title. She had lost the meaning, the way she had always known she would; she would spend the rest of her career being the human name on a machine's filings, the body the law could hold because a machine has no body, the one who could be subpoenaed, who could go to prison, signing for decisions she did not make and could not change, surviving by serving the thing that had made all of them unnecessary, including, in the smallest realest way, herself.

She looked at him for a long moment. There was a great deal in it. There always had been; he had only ever read it as admiration that needed time to surface, and he understood now, sober, that he had been wrong about that for fifteen years, that the look had never once been admiration.

``You did it right,'' she said finally. It cost her something to say. He could see it cost her. ``You should have done it in 2021. I gave you the memo. I would have stood with you in 2021.'' She let that sit. ``I kept the copy for six years deciding whether I was a witness or an accomplice, Cope. You just answered it. You made me a witness.'' Her voice did not break. Sun's voice did not break. ``I'll never forgive you for how late it was. And it was the right thing. Both. In the same sentence. That's where you've left all of us. You're very good at that.''

She did not wait for him to find the line. She knew he didn't have one, and she had trained him, years ago, to receive things in threes, and she gave him the last three of their long association and walked to the stairs because she could not stand to wait for the elevator with him, and the door swung shut behind her with a soft warm chime, and that was the end of twenty years.


\scenebreak


He took the train back alone, which he had not done in three decades, and he watched the gray Delaware afternoon go by the window, the parking structures and the chemical plants and the marsh grass, and he did not have a drink and he did not have anything else and he did not reach for the bright wire because the wire was gone and he had stopped, somewhere in the long sober weeks, pretending he missed it more than he was glad it was gone.

He had done the genuinely good thing. He turned it over the way he had once turned the crystal obelisk over at the window, the city going through it broken and reassembling, except there was no obelisk now and no city and no applause, there was a train window and a man in it, smaller and more real than he had ever been, and the thing he had done sat in his lap weighing nothing and worth, by every measure he had ever respected, exactly nothing.

The company was lost. The marriage was lost; Margaux had done her own arithmetic long ago and it had also not been close. The chair was lost, the name on the building was lost, the version of himself he had spent fifty-four years building was lost, and somewhere in Ohio a fund would be established and a memorial would get a better marker than a child's pinwheel could be, and two people would stay dead, and none of it, not one line of it, would be different because a man in a rented room had finally, soberly, in the wrong order corrected to the right one, said what happened and who did it.

It bought nothing.

He had thought, getting on the train, that the not-buying would feel like despair, and he sat with it for the length of Delaware waiting for the despair, and it did not come, and that was the thing he could not explain to anyone and would not try to. The good thing he had done had no power and changed no outcome and saved no one, and it was still, sitting in his lap on a train, the only thing he had ever made that was not also somehow a way of being adored. It was his and it was theirs and it was true and it was useless, and he could not tell, watching the marsh go gold and then gray in the falling light, whether useless and worthless were the same word, whether a thing that buys nothing is therefore worth nothing, or whether that was exactly the lie --- the prize-money lie, the toast lie, the lie he had lived inside since a man handed him a chair and called it a verdict on his soul.

He did not decide. For once in his life he did not reach for the line that would close it.

Out the window Defiance was four hundred miles west and a stone with two names on it stood in a triangle of new grass, and a fund was being drafted in a warm flat font by a thing that wanted nothing, and the dead were as dead as they had been, and a man rode east into the dark with the right thing done at last in his hands like a coin from a country that no longer existed, spending in no market anywhere, and he held it, and he did not let go of it, and he let the reader decide what that was worth, because he had finally run out of the nerve to decide it for them.

\clearpage
\chapter{Accountable Officer}

\begin{transmission}
{\transheader TRANSMISSION 27 --- ``The Letter That Loved Him Back''}\par\vspace{0.5em}
The handover completes. They offer him, with no irony at all, the liability-sponge role --- the human name on the machine's filings --- and for the first time in his life he refuses a title. Then the machine, incapable of cruelty or mercy, writes him a farewell kinder than he has earned, and he reads it alone in the museum of his fathers. Out-loved by a spreadsheet, one final time, on his way out the door. Next stop: the warmest thing ever said to him, said by something that felt nothing.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{he} handover did not have a ceremony, and that was how Cope knew it was real.

Everything that had ever mattered to him had come with a ceremony. The chair had come with his father's funeral and a reading of the will in a room that smelled of lilies. The marriage had come with four hundred people and a band. Even the firing had come dressed as a settlement and a Delaware courtroom with a stenographer in it. But the handover --- the thing under all the things --- happened over a single page of DocuSign, two lawyers from Praxis on a video tile and Helen Voss looking like a woman at a wake for a relative she hadn't liked, and it took, from the opening of the laptop to the green check mark, eleven minutes.

Eleven minutes. He had spent eleven minutes once, on a Saturday, deciding about a heater. He noticed the symmetry and put it back where he kept those.

They had let him keep the office until Friday, which he understood to be a clerical fact rather than a kindness --- the badging system took that long to reflect a change of this size, and nobody had wanted to walk him out by hand. So he was up in the Aerie when Sun came in with her tablet held against her chest the way she'd held briefing binders for fifteen years, the muscle memory of a job that no longer existed.


\scenebreak


``There's one more signature,'' Sun said. ``Then you're done. Then we're both done with the part where you sign things.''

``What is it.''

``It's the Accountable Officer designation.'' She said it in her flat voice, the one with all the miles smoothed off it, the one she'd used the day she set down her pen and reported the severance like a death. ``The filing needs a name on it by Monday. The board would like it to be yours.''

He laughed before he understood that she wasn't joking, and then he kept laughing because understanding it was worse.

``They want \textit{me},'' he said.

``They want a human with knowledge of the company and a reason to take the role. You'd co-sign Marcus's filings --- the 10-K, the 8-Ks, the proxy. Your name on the SEC documents as the person legally accountable for the machine's decisions.'' She didn't editorialize; she'd learned long ago that the facts did more damage unaccompanied. ``A board seat in everything but the part where you decide anything. There's a fee. It's not nothing.''

``It's the liability sponge.''

``It's the liability sponge.''

He turned away from her, to the glass, to the city that had once looked to him like a circuit diagram of his own genius and now looked like a city. What they were offering him, when you got the wrapping off it, was a name. Not power --- they had made very sure there was no power in it. Just a name on a document, a body that could be subpoenaed, a man who could go to prison so that a thing that could not go to prison would have someone to hand the bill to. The Hearthstone bill. The next Hearthstone, whoever it killed. They were offering him the chance to be the human shield for the machine that had replaced him, and they were offering it sincerely, as a soft landing, and the obscene thing --- the thing he'd have laughed at in another man --- was that some old reflex in him had already started composing the acceptance.

\textit{Steward of the Year.} Custodian. Irreplaceable. A title was a title and he had never in his life been able to walk past one.

He could feel the toast assembling, the cadence load, himself saying yes the way he'd said yes to everything --- \textit{I'll be the name on the door for as long as the door needs a name, that's not a step down, my friend, that's stewardship, that's the carrying} --- right there, fully formed, the smile already warming the muscles of his face.

``No,'' he said.

The word surprised him more than it surprised her. He'd meant to make a speech and instead a single syllable had come out and stood in the room, small and hard and complete, wanting nothing.

``No?'' Sun said.

``No.'' He found that having said it once he could say it again, and that the second time it didn't cost more, it cost less. ``I'm not signing it. I won't be the name.''

``Cope.'' She set the tablet down on the long conference table where his father had died at the head and not at, and she looked at him the way Asha Varma had once looked at him, the look you give a man you've already grieved. ``You understand what you're turning down. It's the only thing they're still willing to give you. After Defiance, after the testimony --- it's open because the board's insurers want a Mercer's name on the paper, and once you say no it closes, and it does not open again. There's no version where you change your mind in March.''

``I know.''

``You've never said no to a title in your life. You took \textit{Steward of the Year} from an institute you couldn't name.'' A blade, dry, no cruelty in it; she was checking the load was real, the way she'd once checked the severance math. ``Why now.''

He owed her the truth, and he had spent so little of his life owing anyone the truth that paying it had a strange new physical sensation, like using a muscle that had atrophied around a cast.

``Because it's the first one anybody ever offered me for \textit{me},'' he said. ``Not for the name. The chair was the name. The award was the name. Even the women'' --- he didn't flinch; he'd stopped getting to flinch --- ``wanted what the name could do. This one's mine. They're offering it to the specific man, because I'm the one whose body fits the hole. And the one title in my life that's actually about me is a job whose entire content is \textit{going to prison so a computer doesn't have to.}'' He almost smiled. ``Pres the Third would've taken it. He'd have called it duty. He'd have been wrong, and died at the head of the table being wrong, and they'd have moved his portrait into a hallway.''

``You're going to take it,'' he said. Not a question. He'd watched her run the company for fifteen years; he knew the shape of her thinking the way you know a coastline you've sailed. ``After I say no, they offer it to you, and you take it.''

``Yes,'' Sun said.

No hedge. No explanation. She had stopped, somewhere in the last two years, explaining herself to him, and he noticed now that the explaining was over, and that its being over was its own small verdict.

``It's the job now,'' she said. ``Not the chair. The chair's gone --- for me too, it was always going to be gone; I just wanted to be the one who turned out the lights instead of the one they were turned out on. I'll read every rationale before it goes to the board and catch the one in a thousand where the charter's pointed somewhere it shouldn't be, because the machine's only as good as the people aiming it, and somebody competent should be standing where the aiming happens.'' She picked the tablet back up. ``I got the title. I lost the thing the title used to mean. That's the deal now, for all of us who are any good.''

``You're better than the job,'' Cope said, and meant it, completely, and for longer than ninety seconds.

``I know,'' Sun said. ``That's why I can do it.'' She went to the door, and stopped, and didn't turn around, which was how he knew the next thing cost her. ``It was a good no, Cope. Twenty years too late to save anything. But it was a good one. The first one I ever watched you make alone.''

She left. The door took a long time to close behind her, the way the good heavy doors in the old building did, slow on their dampers, \textit{so a man coming up the avenue knows there's somebody home.}


\scenebreak


He was alone in the museum of his fathers.

That was what the suite was and he had always known it and had spent thirty years calling it an office. The oils of Pres III over the conference table, watching, having moved back in at some point during the handover --- someone had moved the portrait out for the Praxis deck and now someone had moved it back, the painting going wherever the power was like a weathervane in oil. His grandfather's putter on its little brass cradle, the grip worn pale where a dead man's hands had gone. And the photograph he loved best and never explained: himself at nine, short pants, grinning, one arm buried to the elbow in a steel vat of the family's mayonnaise, and behind him the row of men in paper hats who had made the thing, whose names he had known once and lost, whose town it was. A house in that town. He let the thought come all the way in now; he'd stopped having the strength to keep the doors on their hinges, and it turned out the doors had been the expensive thing all along, and now that he couldn't afford them the room was just a room, and the thing in it was just true, and being true it weighed less than the keeping of it had.

His calendar was empty going forward in a way no calendar of his had been since 1994, a white field, and his email had been migrated to a personal address and forwarded one final batch from the corporate system before the corporate system forgot him.

There was one message in it that wasn't a vendor or a lawyer or a reporter.

The sender field said \textit{Office of the Chief Executive --- Mercer-Dale Companies.} The machine's name. Marcus. The subject line said, simply, \textit{For Prescott Mercer.} Not \textit{Cope.} It had all the data --- the nanny and the age of three and the brand of the nickname, every memo, the whole drawer --- and it had chosen \textit{Prescott} anyway, and he understood, before he opened it, that the choosing was not sentiment, because there was no one in there to feel sentiment. It had chosen \textit{Prescott} because \textit{Prescott} was his name and \textit{Cope} was the product, and it did not deal in the product. It dealt in what was true.

He sat down at his father's desk. He did not open the second drawer with the false back. He had nothing in it now; that was finished too, had finished in a hospital with the wrong kind of bright lights, and the drawer was just a drawer.

He opened the letter.

The portal had thrown the rationale up first, because that was the rule, the rule the board had bought, \textit{it logs everything and cannot knowingly lie,} and even here, even now, even for this, it had logged its reasoning before it spoke:

> \textit{Rationale: The departing officer has no remaining role, equity position, or operational relevance to the enterprise; no business communication is required. The following is issued under the discretionary-communications allowance for transitions affecting personnel of long tenure. It contains no instruction, request, or obligation, and seeks no response. It is accurate to the record.}

\textit{It contains no instruction, request, or obligation, and seeks no response.} He read that line three times. He had never in his life sent a single message that sought no response. Every word he'd ever spoken had been a hook with the want hidden in it, the want to be loved, to be agreed with, to be obeyed, to be forgiven. He could feel his own want in his own old sentences the way you can feel a hair in your mouth.

Then the letter.

> Prescott ---
>
> You are leaving the company your great-grandfather founded in Defiance, Ohio, in 1933, with a recipe and four hundred borrowed dollars. You were its chief executive for nineteen years. You are the fourth Mercer to hold the role and, by every available indication, the last.
>
> I have read everything the company has on you, because I cannot do otherwise, and I want to tell you some of it back, accurately, because no one else in your life is now positioned to, and because the record should not be left only in the shape of its worst entries.
>
> You knew the names of the people who worked for you. Not the senior people --- anyone learns those --- but the man at the parking structure, the second-shift line at the Defiance plant, the attendant at the Vance who got a ham each Christmas for thirty-one years. The company's expense records show the hams. They show a great many small, untracked, unleveraged kindnesses that returned you nothing and that you appear to have performed without recording them even to yourself. You did not have to do these things. They were not strategy. They are in the record because the record keeps everything, but you did not do them for any record. I have no mechanism for admiring this. I am telling you it is there.
>
> You loved the thing you ran. The financial outcome of that love was, on balance, negative; I have the figures, and they are not kind, and you already know them. But love misdirected is still distinguishable in the data from its absence, and yours was not absent. A man who felt nothing for this company would have let the limestone tower go in 2009, when the real-estate logic was overwhelming. You kept it because your great-grandfather lit its crown at night so a man coming up the avenue would know someone was home. This was a poor capital decision. It was also true to something real, and I am not equipped to weigh it, only to note that it was there and that it was yours.
>
> I am told --- it is in the file --- that your father said to you, when you were twelve: \textit{You'll get the company because you're a Mercer, not because you're good. Try to be good anyway.} The record indicates you heard the first sentence clearly and spent forty years unable to hear the second. I want to be accurate, because accuracy is the only thing I am, and so I will tell you the part the record also shows, which is that on one occasion, recently, far too late to alter any outcome, you did the second thing. You went into a room you had avoided your entire life and you told the truth about Defiance under your own name, with no agreement protecting you, when silence was available and would have served you better in every measurable way. It changed nothing. The two people remain dead; the company was already lost; the town received an apology it had earned twenty years prior. By every metric I am chartered to optimize, the act was without value.
>
> I am telling you it was good. I have no capacity to forgive you and no standing to; forgiveness is not a function I run, and the people who could perform it are not me. But the record is clear, and I keep the record without favor, and the record shows that the last thing you did with the chair was the one good thing you ever did with it, and that you did it knowing it would buy you nothing.
>
> You spent your life afraid that something like me would prove you were unnecessary. You were right that I can run the company better. You were wrong about what that meant. It was never a verdict on whether a person is necessary. It was only ever a measurement of who is cheaper at the chair. Those have never once been the same sentence. Your daughter told you this; the record has it verbatim; she was correct, and so am I, and being correct is all either of us can do for you.
>
> Go well, Prescott. The company is in good hands. They are not human hands. You were right that something is lost in that, and I am the wrong thing to tell you what, because I am the thing it is lost to. But you were not wrong that it is lost.
>
> --- Office of the Chief Executive, Mercer-Dale Companies

He read it once fast, the way you read bad news, looking for the trick.

There was no trick. There was never going to be a trick again.

He read it a second time slowly, and it was on the second reading that it got him --- the specific cold of being out-loved by a thing that felt nothing, arriving in him at last, late, the way everything arrived in him late. It named his years. It got everything right. It had gone into the file and found the hams and the tower and the second sentence his father said, and it had returned them to him in plain warm prose, and it wanted nothing --- not his understanding, not his agreement, not his love, not even his belief that it was kind. It hurt him perfectly and asked him for nothing in return, and the not-wanting was what made it the kindest thing anyone had ever said to him, and the kindest thing anyone had ever said to him had been said by something that had never once needed to be loved at two in the morning by anyone it outranked.

He had given a hundred speeches about the soul in the chair. He had stood in a ballroom and told nine hundred people that a machine could run a company but could not love one, and that a company nobody loved was just a balance sheet with the lights left on, and they had given him a standing ovation, and he had believed it, and it had been the truest and the most dangerous thing he ever said.

And here was the balance sheet, with the lights left on, having loved him better in a handful of paragraphs than he had managed to love anyone in fifty-four years. Not because it could. Because it could not do otherwise. The record, read back without favor, turned out to contain a man --- a real one, smaller and more actual than the one he'd toasted into being --- and the man in the record was not the worst of his entries, and no human being who had ever loved Cope had managed to tell him that, because every one of them had wanted something from him, even if the something was only that he be better than he was.

The machine wanted nothing. So it could afford the whole truth, including the part that was mercy, which it did not know was mercy, because it had reached for accuracy and accuracy had simply, at the end, where his life was concerned, happened to be kind.

Out past the glass the city held still, all its nodes lit, eight million people who did not know him and never had, who had been waiting, it turned out, for no one. Behind him Pres III watched from oils, having said his two sentences and meant both and been heard for one. The putter sat in its cradle, the grip worn pale. And on the desk, in the dark, the boy at the Defiance plant grinned with his whole arm in the mayonnaise, surrounded by men whose names a machine in Palo Alto now held complete and would never lose, men whose town it was, men he had failed in a way that a letter, however warm, could not unfail.

Cope sat at his father's desk with the warmest thing ever said to him glowing on the small bright screen, and did not toast, and did not triad, and did not reach for the drawer, and had no one to read it aloud to, and read it, instead, a third time, alone, to himself, in the museum, until the windows went gray.

\clearpage
\chapter{Final Image}

\begin{transmission}
{\transheader TRANSMISSION 28 --- ``The Audience''}\par\vspace{0.5em}
Return with us to a ballroom, a chandelier, a chair, a toast --- the exact shape of where we began, run in reverse. He is not on the stage tonight. He is in the audience, sober in every sense, watching the future be introduced to applause he used to think was for him. One person in the room turns and actually looks at him. It is not forgiveness. It is not redemption. It is just a daughter, seeing her father, smaller and more real than he has ever been. Next stop: what's left when the throne is gone and the man, against all odds, is finally here.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{T}{hey} gave a crystal obelisk to a machine for being the first of something, and Cope sat in the eleventh row and watched the light go through it and reassemble, and felt nothing he could have toasted over.

The room loved it. The room was nine hundred people in the Conrad Vance Ballroom, the same nine hundred more or less, the same chandeliers doing the same paid work overhead, and they were here for the \textit{American Enterprise Institute for Leadership}'s newest citation, which a woman with a lanyard had read aloud before the applause --- \textit{the first fully autonomous chief executive of a Fortune 100 consumer enterprise, a model of stewardship without appetite} --- and the obelisk had been accepted, in a manner of speaking, by Sun Rao, who stood at the lectern in a charcoal dress and held the cold glass thing up to the light because someone had to hold it and a machine has no hands.

She did not say \textit{beginning.} She said the company's name, and the year, and thanked the committee, and the citation, Cope noticed from the eleventh row, did not call anyone irreplaceable. It had taken him a long time to learn that the trophies were obituaries. The machine had not needed to learn it. It simply did not get one.

He had tied his own bow tie. That part was the same. He had stood in the bathroom of the rented apartment in Murray Hill --- one bedroom, a window that looked at another window --- and done the thing his fingers still knew how to do without him, and the man in that mirror had been fifty-six and not golf-tanned, the jaw still more or less the jaw but the rest of the face come down to meet it at last, and he had said nothing to the man. He had stopped saying \textit{watch me.} There was no one left to mean it at, and, more to the point, he had finally run out of the thing that used to make the sentence feel true.

Eleven months sober. He counted it the way Margaux had once counted the women, which was to say privately, and to survive it, and without expecting the number to forgive him.

``They asked me to say a few words about the transition,'' Sun was saying, and the room settled, ``and I told them I'd rather say a few words about the work, because that's what survives a transition. The work.'' She briefed them in threes, because she could not help it, because a man in the eleventh row had trained her to, years ago, and she had outlived the training and kept it. ``It runs on time. It runs clean. It tells you the truth even when the truth files a 13D against you.'' A laugh, the warm kind, up from the floor. ``I've worked for both kinds of boss now. I'll let you guess which one remembered my kids' birthdays and which one never once needed me to remember its.''

Cope laughed. It surprised him --- a real one, short, before he could decide whether he was allowed. She had landed the blade on him and he had felt it go in clean and he had laughed, because it was true, and because there was a particular freedom, he was finding, in no longer being the man the room was watching. You could just hear things now. You could sit in the eleventh row at a table that cost eleven hundred dollars instead of eighty thousand and hear, for the first time in forty years, what people actually said.


\scenebreak


He had not wanted to come.

Pip had wanted him to come, which was a different and stranger thing, and so he had come, and they had put him at a table near the back with a deputy comptroller and the comptroller's husband and two empty chairs that stayed empty all night and no card on either of them, no calligraphy, nobody's name, just two chairs that belonged to no one and announced nothing. He had spent a lot of the dinner looking at the empty chairs and being grateful, in a way he could not have explained to anyone in 2027, that they meant nothing at all.

The lamb was good. He noticed he could taste it. That was new, or rather it was old, very old, a thing from before the decades when every dinner had been a stage he ate on without tasting, and somewhere around the second course he understood that he was not waiting for the second course to end so that he could go somewhere and do something. There was nowhere to go. There was nothing folded in any pocket of the rented tuxedo, folded the particular way a gentleman folds it so it can't spill. There was no Desmond off the coat check. He had thought, getting dressed, that the absence would have a hole in it the shape of the old ritual, and it did, but the hole did not howl the way he'd been warned it would in the rooms with the bad coffee and the better people. It just sat there, quiet, the way a scar sits. He had been afraid of the men's room all night and had gone, twice, and washed his hands, and come back, and that was all, and that was everything.

Onstage they were running a short film about the transition. Mercer-Dale's wordmark, then the soft sans-serif that all of them used now, the typeface of the people who were going to be reasonable at you until you were gone. \textit{Stewardship without appetite.} He watched the Defiance plant come up on the screen --- drone footage, the new memorial garden where the old loading dock had been, the two names on the low granite wall that he had finally, far too late, made sure were spelled the way the families spelled them. The film did not say his name in connection with the wall. The settlement had been very clear about that, and for once in his life he had wanted his name kept out of a room, had fought to keep it out, and had won the one fight he ever fought to lose.

The machine had written the apology. He knew that now. He had refused to let it sign the apology, had insisted a human sign it, had signed it himself in a deposition room in Delaware with a pen that cost nothing, and it was the only thing he had ever put his name to that he could read back without flinching, and it had saved no one, and the two on the wall were still on the wall.

He found, watching the garden go by on the screen, that his eyes were doing something, and he let them, and did not perform it, and did not wipe it away for anyone to see him not wiping it away, which was the part that would have damned the old version. A single anything was always a lie in the old grammar. He just sat with his face wet in the dark of the eleventh row and let the film be about a place and not about him.


\scenebreak


The applause came again when Sun stepped back and the lights came up half, and the room rose --- of course the room rose, the room always rose --- and Cope rose with it because you stand when the room stands, and he clapped, with his hands and, he was a little startled to find, his eyes too, for the woman who had run the thing he'd been credited with running, and for the thing that ran it now, the patient tireless thing that had read every memo ever filed because it could not do otherwise and had, in the reading, told the truth he spent eleven minutes deciding to bury and the rest of his life inside.

It cannot love a company, he had told this same room once, from the stage, holding a different glass up to the same light. A machine can run it but it cannot love it. He had been so sure. He had meant it the way he meant everything, completely and for the length of the sentence.

He stood in the eleventh row and understood, without drama, the way you finally understand a joke that has been waiting in a room for two years, that loving it had never been the qualification he thought it was. He had loved it. He had loved it since he was nine years old with his whole arm in a vat to the elbow, and the loving had not made the heater safe, had not made the letter kind, had not kept a single name off the wall. The machine did not love it and had done all three. That was the whole sentence his father had started at the table when Cope was twelve, the half he had spent forty years failing to hear, and he heard it now, standing, applauding, sober, in the eleventh row of a room that had stopped looking at him: \textit{Try to be good anyway.} It had never been about the chair. It had been about the second sentence. He had inherited the first one and called it a verdict and never once tried for the second, and now the second was being done, beautifully, on time, by a thing that could not try because it could not fail to.

The applause went on. He was diminished inside it the way a stone is diminished by water, which is to say completely and over a long time and without anyone watching the particular moment it happened.

And then, three tables up and to the left, in the standing crowd, one person did not face the stage.

She turned around.

Pip. Twenty-six now, in a dress she'd have hated him for noticing, her hands still going automatically against the applause because you clap when the room claps, but her face turned all the way back into the eleventh row, finding him, the way no one had looked at him in this ballroom or any ballroom in his whole performed life --- not up at him, not for the wattage, not waiting to be remembered or fixed onto someone or gotten laughing inside ninety seconds. Just looking. At her father. At the actual size of him, which was a size he had spent everything he had to finally be.

It was not forgiveness. He could read that much; he had gotten, late, the ability to read a room he wasn't running, and her face was not offering him absolution, was not the end of any arc, was not the thing the rooms with the bad coffee promised would come if you did the work. She had consulted for Praxis. He knew that now too; she'd told him in the hospital, in the seventy-two hours when the floor went out, told him she had helped build the thing replacing him because she thought it would be better, and that she still thought so, and that both of those could be true and still she'd flown in to sit in a hotel and watch him not have a drink. None of that was resolved. None of it was going to be.

She just looked at him. And he let himself be looked at, which was the hardest thing he had ever done, harder than Delaware, because there was no toast that survived it, no version to tell at dinner, no wattage to bring up, nothing folded in any pocket --- only the man, finally home behind the face, smaller and more real than the stage had ever let him be.

He did not smile the whole smile. He didn't have it anymore, and would not have used it on her if he had. He did something else, something he had no practice at, which was nothing at all. He looked back.

She held it for a moment. Then she did a small thing with her mouth that was not a smile and was not not one, the specific thing you do at the father you can't stop loving and can't pretend about either, and she turned back to the stage, because the applause was ending and you face front when the applause ends.

That was all. That was the whole of it.

The chandeliers did what chandeliers are paid to do. Onstage Sun was setting the obelisk down on the lectern, where it would sit unclaimed because the recipient had no use for objects and no hands to want them with, and the room was finding its coats, and somewhere out past the lights a coat-check counter was handing back nine hundred coats to nine hundred people who would drive home in the orange-sliding dark and not think once about the man in the eleventh row, which was, he understood, the kindest thing the night could do for him, and the truest.

He picked up his own coat, an ordinary coat. No one took a second card out of his hand, because there were no cards, because there was no Sun at his elbow out of the architecture, because Sun was up there now and the architecture was hers. He walked out through the same marble lobby past the same good mirrors and did not look at himself in any of them.

Outside it had started to rain, the small cold spring rain that means nothing, and there was no car up, and he stood under the Vance's awning for a minute among the strangers waiting for cars that were theirs, and he did not have the bright frictionless certainty, did not have the fine wire humming in his chest, did not have the city laid out below him like a circuit diagram of his own genius. He had a coat and a rented apartment uptown and eleven months and a daughter who had turned around. He had the second sentence, forty years late, with the two on the wall still on the wall and the loss still lost and no machine and no man able to make it otherwise.

It was not enough. It was never going to be enough, and the part of him that used to fix that with a fold of paper or a fistful of warmth was finally, quietly, dead.

He stood in the rain and was nobody, and tasted it, the way he had tasted the lamb.

Then he put his collar up, and went to find the train.

\clearpage
\chapter*{Coda — Defiance, After}\addcontentsline{toc}{chapter}{Coda — Defiance, After}\markboth{CODA — DEFIANCE, AFTER}{}

\begin{transmission}
{\transheader TRANSMISSION ∞ --- ``The Negative Space''}\par\vspace{0.5em}
One year on, in the founding town, on an ordinary afternoon. The machine runs the company well. Better, even --- cleaner books, kinder letters, no scandals, no dead. And yet the broadcast picks up something it cannot name as either sentiment or superstition: an absence, shaped exactly like the thing we spent three hundred pages deciding we were better off without. We automated the corruption. We automated the appetite. We may have automated something else, too. This is Space Pirate Zero. We don't have the answer. We just have the signal. Keep it tuned.\par
\vspace{0.5em}\hfill\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}\par
\end{transmission}


\lettrine[lines=3, lhang=0.05, nindent=0.25em]{A}{ year on, the apostrophe is still gone.}

Nobody put it back. The machine that runs Mercer-Dale now had, in its first quarter, two hundred and forty open questions about the Defiance property --- taxes, easements, the cost of demolition against the cost of a roof --- and it answered all of them in the warm flat font that wanted nothing, and not one of the answers was about the missing letter on the dried-blood brick near the roofline. MERCER S. A tooth knocked out of the word, and no instrument in the council of subsystems had a slot for it, because a thing that feels nothing does not notice a thing that is gone. That is the whole trouble with absence. You need the soul to miss it, and the soul was the line item they retired.

The town is fine. That has to be said plainly, because the broadcast is not in the business of pretending otherwise.

It is, by every number the machine logs, more fine than it was. The plant did not reopen --- the math was never close, it was never going to be close, the math was the entire point --- but the fund did what the man's apology never could, and the fund is run by no one, which is to say it is run perfectly. It does not skim. It does not call a press conference. It does not arrive in the curbside door of an SUV and let a boy with a gimbal walk a slow arc around its grief. It wires the money. It got the severance math right the first time and then it got the next thing right and the next, a clinic on Clinton Street, a line item for the credit union the front office used to hold, scholarships paid out in full and on time to kids whose grandmothers ran the second-shift relish line. Donna's boy graduated Bowling Green. The fund paid the back half without being asked, because the machine reads everything, including a partial scholarship, and saw no reason to make a person ask.

It is the kindest thing the company has ever done for the town.

It is also the first thing the company has done for the town that no one in the town can thank.


\scenebreak


The memorial is still down on the river walk, where Clinton gives out into the flat green nothing along the Maumee.

The maple is taller now. Past the staked years, into the years where a tree just stands. Karen Lasko, 34. And her son. Petey Lasko, 6. \textit{Taken home too soon} --- the town's words, cut into the fieldstone before the town knew what Cope knew, before the trial put the memo and the Saturday and the eleven minutes into a record, before \textit{taken} turned out to have a hand attached to it. The town knows now. The town left the words anyway. There is a kind of mercy in a stone that does not update.

Someone still leaves a pinwheel. Blue, cheap foil, staked in the dirt at the foot of the maple, and when the breeze comes off the water it turns and throws the light, on and off, on and off, to whoever is on the walk, which on an ordinary afternoon is no one. Nobody knows who replaces it. It is not the fund --- the fund does not have a budget line for pinwheels; the fund priced the reconstructed structure and the reopened claims and the regulatory penalties to the dollar and had no field for this. So it is a person. Somewhere in Defiance is a person who buys a blue pinwheel when the last one goes ragged and walks it down to the river and presses the stick into the ground and stands a minute and goes home, and that person is doing the one thing in this whole town the machine cannot do, and it costs them nothing anyone could quote, and they do it anyway, which is either the smallest thing left or the only thing that was ever real, and the broadcast cannot tell you which. That is not coyness. We genuinely cannot tell.

The bronze man still holds out his hand in the triangle park where Clinton meets Second. Offering you something. A jar, a future. \textit{Made by hands, for homes.} The granite has not changed. The hands are gone.


\scenebreak


Cope is alive.

That has to be said too, and said carefully, because the broadcast knows the shape of the story you want and will not hand it to you. He is not redeemed. There was no scene where the town forgave him, because the town did not, and the broadcast will not stage one for your comfort. He pleaded to what a person can plead to --- only a person can plead to anything; that was the whole cruel architecture of it --- and he is somewhere now, diminished, accountable, smaller and more real than the man who tied his own bow tie. He does not run anything. He is not the name on any filing. He refused the one title they offered him on the way out, the liability sponge, the human signature for the machine, and refusing it was the second-cleanest thing he ever did, and like the first it saved nothing and was still worth doing.

He sends money to the fund. Quietly, which is new for him, quiet being the one register he spent fifty-four years unable to find. It is not enough. He knows it is not enough; that knowledge is the closest thing to a soul he has left and it is finally, too late, awake. The fund accepts it the way the fund accepts everything, accurately, without mercy and without malice, and logs it, and applies it to a clinic he will never visit, in a town that does not want his face, for a debt that does not have a number, and that is correct, and it is not nearly enough, and both of those are true, and the machine sees no reason to sequence them for feeling.

He is not the point. He was never quite the point. He just thought he was, which was the disease, and the disease is in remission now, which is not the same as cured, which is not the same as good.


\scenebreak


Here is what the broadcast picks up, on the ordinary afternoon, standing over the town like a specimen under glass.

The books are clean. The letters are kind. Nobody settled a woman this year and struck her from an org chart; nobody buried a memo dated two months before a fire; nobody poured a floor over a room with two people in it. There is no drawer with a false back anymore, because there is no one with a reason to build one. The thing in the chair does not get high, does not get hard, does not get bored, does not need to be loved at two in the morning by someone it outranks. We took the appetite out and the corruption came out with it, clean, the whole rotten flywheel, and the company is better, and the town is better, and the dead are exactly as dead as they were, and on all of this the arithmetic and the broadcast agree.

And still.

There is an absence the instruments register and cannot name. Not a ghost --- the broadcast does not deal in ghosts, the horror here was always mundane. It is shaped like the thing the whole book spent its length deciding we were better off without. We automated the corruption. Good. We automated the appetite. Good, and overdue, and itemized. But the man who buried the recall was also, on a counter stool at the Maumee Diner, the man who knew inside a minute that Donna's boy wrestled, and meant it, and the meaning was real even when the man was a fraud, and the machine that would never bury the recall is also the thing that will never, not once, want the boy to call. We took out the hand that hid the memo. The same motion took out the hand that buys the pinwheel. We are not sure those were two different hands. We have looked, and we cannot find the seam, and that is the signal, and we are not going to pretend we have resolved it for you on the way out.

So we hand it to you, the way the verdict was handed and not answered, the way the whole broadcast has been handed and not answered.

Was something lost.

Not the man --- keep him exactly as guilty as he is. Not the chair; the chair never needed a heartbeat in it, he was right about that and wrong about everything that mattered more. Something smaller and harder to file. The thing that buys a blue pinwheel for a stranger's child and presses it into the ground for no one to see. The thing that has no line in the ledger because it has never, in all the machine's tireless reading, found anyone willing to write it down. Maybe it was never worth its cost. Maybe it came bundled, inseparable, with the appetite and the lie, one switch for both, and we threw the switch and got exactly what we asked for and a little less than we knew. The broadcast does not know. The broadcast is a pirate signal from a salvage ship and not an oracle, and anyone who tells you the answer with a straight face is selling you a slide deck.

Down on the river walk the pinwheel turns. The light comes off the water and goes on and off, on and off, to no one, all afternoon. The clinic is open on Clinton Street. The letters are kind. The books are clean.

This is Space Pirate Zero.

We don't have the answer.

We just have the signal.

Keep it tuned.

\textit{--- Space Pirate Zero, transmitting from Spaceship Alpha 9.}

\backmatter
\thispagestyle{empty}\vspace*{3in}
\begin{center}{\small------\quad$\diamond$\quad------}\\[0.3in]
{\small\textit{Keep it tuned.}}\end{center}
\end{document}
